### 2021-03-04 Rmd/Report cleaning.Rmd
Start a Rmd and more updates

---
title: "Flatiron report"
author: "Christelle Colin-Leitzinger"
date: `r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    # keep_md: true
---

<style type="text/css">
.figure {
   margin-top: 25px;
   <!-- margin-bottom: 100px; -->
}

table {
    margin-top: 25px;
    <!-- margin-bottom: 100px !important; -->
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

# Report
<br>
<br>

***

```{r library, include=FALSE}
library(drake)
```

```{r}
loadd(clinical_data, vitals, drugs, auc, creatinine)
```

## Creatinine cleaning
.  
```{r creatinine}

```

### 2021-03-04 R/2.data cleaning.R

@@ -270,7 +270,10 @@ clinical_data <- clinical_data %>%
   )) %>% 
   # mutate(aprox_month_at_os = followuptime/30.417) %>% 
   mutate(aprox_month_at_os = interval(start = diagnosisdate, end = followupdate)/
-           duration(n=1, units = "months"))
+           duration(n=1, units = "months")) %>% 
+  mutate(stagecat = na_if(stagecat, "Unk Stage")) %>% 
+  mutate(across(.cols = c(histology, groupstage, tstage), ~na_if(., "Unknown/not documented")))
+
 
   # mutate(raceeth = case_when(
   #   str_detect(race, "NHBlack")  ~ "Non-Hispanic Black", # Black Hispanic are others?
@@ -419,18 +422,11 @@ therapy1 <- therapy %>%
   mutate(drug_count_perline = n()) %>%
   mutate(skipped_cycle_indays1 = ifelse(
     (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
-  )) # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
+  )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
   # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
   group_by(patientid) %>% 
   mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
   ungroup()
-
-
-# FDB58481AFFBB Need to fix cycle interval if 1 drug only
-# May try if drug_count_perline == max(cycle_increment) do ...
-
-
-
 
 
 rm(drugs, drugs1, therapy)
@@ -442,27 +438,27 @@ rm(drugs, drugs1, therapy)
 Treatment <- 
   # Merge with creatinine
   left_join(therapy1, creatinine, by = "patientid") %>%
-  mutate(interval = abs(interval(start= creat_date, end= cycle_date)/                      
+  mutate(interval = abs(interval(start= creat_date, end= cycle_start_date)/                      
                           duration(n=1, unit="days"))) %>% 
   arrange(interval) %>% 
   distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
-           cycle_date, .keep_all = TRUE) %>% 
+           cycle_start_date, .keep_all = TRUE) %>% 
   
   # Merge with height
   left_join(. , height,  by = "patientid") %>%
[…]

### 2021-03-04 R/3.clinical mining.R

@@ -27,13 +27,13 @@ analysis_data %>% distinct(patientid, .keep_all = TRUE) %>%
            "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown", 
            
            "hrd_tissue", "gis_tissue")) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_p() %>% add_overall()
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
 
 
 #################################################################################################### II ### Treatment Mining
 # 1.	Determining frontline treatment regimen
 
-Treatment %>% distinct(patientid, .keep_all = TRUE) %>% 
+analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
   filter(exclude != "1") %>% 
   ggplot(aes(x= therapy))+
   geom_bar()+
@@ -41,7 +41,7 @@ Treatment %>% distinct(patientid, .keep_all = TRUE) %>%
   labs(title = "Frontline treatment")+
   coord_flip()
 
-Treatment %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>% 
+analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>% 
   filter(exclude != "1") %>% 
   group_by(chemotherapy_type) %>% 
   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
@@ -52,7 +52,7 @@ Treatment %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>%
   guides(fill = FALSE) +
   coord_flip()
 
-# Treatment %>% distinct(patientid, .keep_all = TRUE) %>% 
+# analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
 #   ggplot(aes(x= chemo))+
 #   geom_bar()+
 #   theme_minimal()+
@@ -60,32 +60,34 @@ Treatment %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>%
 
 # What are the RDI distribution for each type of chemo
 summary(analysis_data$relative_dose_intensity)
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
[…]

### 2021-03-04 Rmd/Report cleaning.Rmd
Start report

@@
 ---
-title: "Flatiron report"
+title: "Flatiron data cleaning and analysis report"
 author: "Christelle Colin-Leitzinger"
-date: `r Sys.Date()`'
+date: '`r Sys.Date()`'
 output: 
@@
     toc_collapsed: false
-    theme: cerulean #darkly
+    theme: flatly
     highlight: pygments
-    # keep_md: true
+    df_print: paged
 ---
@@
 
-# Report
+# Data cleaning
+***
 <br>
-<br>
-
-***
 
@@
 library(drake)
+library(tidyverse)
+library(data.table)
+library(lubridate)
+library(ggplot2)
+library(gtsummary)
+library(survminer)
+library(survival)
 ```
 
-```{r}
+```{r loadd}
 loadd(clinical_data, vitals, drugs, auc, creatinine)
@@
 ## Creatinine cleaning
-.  
-```{r creatinine}
 
+Only creatinine from blood and serum are being used. All units are correct (mg/dL).  
+Here an sample of the non-cleaned data with really low `testresultcleaned`.
+
+```{r creatinine, rows.print=15, max.print=15}
+creatinine %>% filter(str_detect(labcomponent, "blood|serum")) %>% 
+arrange(testresultcleaned)
 ```
+All `testresultcleaned` and `testresult` variable are cleaned as :  
+-creat < 0.8 is set at 0.8  
+-creat > 3 are eliminated  
+To create the final `creatinine` variable ,`testresultcleaned` and `testresult` are both used but `testresultcleaned` is used over `testresult` when both are available.
+
+Here a sample of the cleaned data
+```{r creatinine1, rows.print=15, max.print=15}
+creatinine <- creatinine %>%
+  # remove creatine urine
+  filter(str_detect(labcomponent, "blood|serum")) %>% 
+  mutate(creatinine = case_when(
+    testresultcleaned < 0.8        ~ 0.8,
+    testresultcleaned > 3          ~ NA_real_,
+    TRUE                           ~ testresultcleaned
+  )) %>% 
+  # F092F8B827DDC kept umol/L as they actually are mg/dL range 45 to 90 μmol/L (0.5 to 1.0 mg/dL) for women.
+  mutate(creatinine1 = case_when(
+    testresult < 0.8               ~ 0.8,
+    testresult > 3                 ~ NA_real_,
+    TRUE                           ~ testresult
+  )) %>% 
+  mutate(creatinine = coalesce(creatinine, creatinine1)) %>% 
+  filter(!is.na(creatinine)) %>% 
+  mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
+  select(c("patientid", creat_date = "testdate", "creatinine", creat_units = "testunitscleaned"))
+creatinine %>% distinct(patientid, .keep_all = TRUE)
+
+vitals <- vitals %>% 
+  mutate(testdate = as.Date(testdate, format = "%m/%d/%y"))
+body_surface_area <- vitals %>% 
+  filter(labcomponent == "Body Surface Area (BSA)")
+```
+<br>
+
+## Body surface area cleaning
+
+`testresultcleaned` is all within expected range but only few data is available (`r NROW(body_surface_area %>% filter(!is.na(testresultcleaned)) %>% distinct(patientid, .keep.all=TRUE))` patients).
+Even less with an associated date!
+
+```{r bsa}
+body_surface_area
+```
+
+By using `testresult` and before cleaning only `r NROW(body_surface_area %>% filter(!is.na(body_surface_area$testresult)) %>% distinct(patientid, .keep.all=TRUE))` patients have data for their BSA.
+So I will also use the height and weight of patients to calculate their BSA by using the Du Bois formula.
+
+To create the final `BSA` variable ,`testresultcleaned` is used over `testresult` when both are available.  
+`testresult` was further cleaned as data < 0.418 and > 4.14 are eliminated. These values were calculated from the biggest and the smallest individuals recorded.  
+I also remove the outliers within patient (2 examples here).
+
+```{r}
+vitals %>% 
+  filter(labcomponent == "Body Surface Area (BSA)" & patientid == "F2D5A8748B268") %>% 
+  select(patientid, testdate, testresult, testresultcleaned)
+vitals %>% 
+  filter(labcomponent == "Body Surface Area (BSA)" & patientid == "F875EA1B044F0") %>% 
+  select(patientid, testdate, testresult, testresultcleaned)
+# F3AE4546B5D12
+```
+
+Here a sample of the cleaned data
+
+```{r bsa1, rows.print=15, max.print=15}
+body_surface_area <- vitals %>% 
+  filter(labcomponent == "Body Surface Area (BSA)") %>% # only 399 patients data
+  # Limit max = 4.14, min = 0.418 calculated for biggest to smallest person
+  mutate(testresult = ifelse(testresult < 0.418 | testresult > 4.14, NA_real_, testresult)) %>% 
+  group_by(patientid) %>%
+  # I used the median to remove outlier within a patient
+  mutate(median_testresult = median(testresult)) %>% 
+  ungroup() %>% 
+  mutate(BSA = case_when(
+    testresult > (median_testresult + 0.4) |
+      testresult < (median_testresult - 0.4)      ~ NA_real_,
+    TRUE                                          ~ testresult
+  )) %>% 
+  mutate(BSA = coalesce(testresultcleaned, BSA)) %>% 
+  filter(!is.na(BSA)) %>% 
+  mutate(BSA_units = "m2") %>% 
+  select(c("patientid", bsa_date = "testdate", "BSA", "BSA_units"))
+
+body_surface_area %>% distinct(patientid, .keep_all = TRUE)
+```
+<br>
+
+## Height
+
+Height data complicated. Again you have `testresultcleaned` and `testresult` with `testresultcleaned` which will prioritized.  
+`testresultcleaned` has units in cm but some data are wrong. `testresult` has results in cm, ft or in. It is pretty easy to clean data between these 3 units because the measurement cannot overlap.
+Both are cleaned as < 120 or > 231 are eliminated. These value are for the shortest and tallest women recorded.
+The units can be filled by patients when absent.
+
+```{r height}
+vitals %>% 
+  filter(test == "body height" & patientid == "FCB6DAAFF6527")
+# FC109A6F719E7
+# FC106805F9AB9
+# F91590CB83EC8 weird
+```
+
+Outliers are eliminated as much as possible.
+
+```{r height1}
+vitals %>% 
+  filter(test == "body height") %>% 
+  # To get more data, I have data from testresult that can be used
+  # But need to fill up testunits, transfer in kg and coalesce.
+  group_by(patientid) %>% 
+  fill(testunits, .direction = "downup") %>% # F004D683A1695 have testresult, F615C37BF1470 is wrong, Otherwise I checked them all to see we can do that
+  ungroup() %>% 
+  # Clean up outliers compare to tallest ans smallest record
+  mutate(testresultcleaned = case_when(
+    testresultcleaned > 231 | # Tallest women height
+      testresultcleaned < 120 # Average height dwarf = 122 cm, 4 feet, I take 120 by loooking at the data
+                                     ~ NA_real_,
+    TRUE                             ~ testresultcleaned
+  )) %>% 
+  mutate(testresult = case_when(
+    testresult > 231 & testunits == "cm" |
+      testresult < 100 & testunits == "cm" |
+      testresult > 7.58 & testunits == "ft" |
+      testresult < 3.28 & testunits == "ft" |
+      testresult > 90.94 & testunits == "in" |
+      testresult < 39.37 & testunits == "in"|
+      testresult == 0
+                                     ~ NA_real_,
+    TRUE                             ~ testresult
+  )) %>% 
+  # Clean up outliers within patient by using the median for each patients/unit. Eliminate the ones with too much variation.
+  group_by(patientid) %>%
+  mutate(median_testresultcleaned = median(testresultcleaned)) %>% 
+  ungroup() %>% 
+  mutate(testresultcleaned_verified = case_when(
+    testresultcleaned > (median_testresultcleaned + 5) | # choose 5 cm by default
+      testresultcleaned < (median_testresultcleaned - 5)      ~ NA_real_, # F01413C06D921 weird
+    TRUE                                                      ~ testresultcleaned
+  )) %>% 
+  filter(patientid == "F01413C06D921") %>% 
+  select(c("patientid", testdate, testresultcleaned, median_testresultcleaned, testresultcleaned_verified,
+           testunitscleaned, testunits, testresult))
+```
+
+PB: Some patient don't have dates but have data. Should I take a mean of all the height measured or the first one - If I have to choose I would take the mean (patients shouldn't grow or shorten much)?
+If all dates are NA for a patients, I cannot combined `height` with `episodedate` of the drug data.
+
+Here a samples of the data.
+```{r height2, rows.print=15, max.print=15}
+height <- vitals %>% 
+  filter(test == "body height") %>% 
+  # To get more data, I have data from testresult that can be used
+  # But need to fill up testunits, transfer in kg and coalesce.
+  group_by(patientid) %>% 
+  fill(testunits, .direction = "downup") %>% # F004D683A1695 have testresult, F615C37BF1470 is wrong, Otherwise I checked them all to see we can do that
+  ungroup() %>% 
+  # Clean up outliers compare to tallest ans smallest record
+  mutate(testresultcleaned = case_when(
+    testresultcleaned > 231 | # Tallest women height
+      testresultcleaned < 120 # Average height dwarf = 122 cm, 4 feet, I take 120 by loooking at the data
+                                     ~ NA_real_,
+    TRUE                             ~ testresultcleaned
+  )) %>% 
+  mutate(testresult = case_when(
+    testresult > 231 & testunits == "cm" |
+      testresult < 100 & testunits == "cm" |
+      testresult > 7.58 & testunits == "ft" |
+      testresult < 3.28 & testunits == "ft" |
+      testresult > 90.94 & testunits == "in" |
+      testresult < 39.37 & testunits == "in"|
+      testresult == 0
+                                     ~ NA_real_,
+    TRUE                             ~ testresult
+  )) %>% 
+  # Clean up outliers within patient by using the median for each patients/unit. Eliminate the ones with too much variation.
+  group_by(patientid) %>%
+  mutate(median_testresultcleaned = median(testresultcleaned)) %>% 
+  ungroup() %>% 
+  mutate(testresultcleaned_verified = case_when(
+    testresultcleaned > (median_testresultcleaned + 5) | # choose 5 cm by default
+      testresultcleaned < (median_testresultcleaned - 5)      ~ NA_real_, # F01413C06D921 weird
+    TRUE                                                      ~ testresultcleaned
+  )) %>% 
+  # select(c("patientid", testdate, testresultcleaned, median_testresultcleaned, testresultcleaned_verified, 
+  #          testunitscleaned, testunits, testresult)) %>%
+
+  group_by(patientid, testunits) %>%
+  mutate(median_testresult = median(testresult)) %>% 
+  ungroup() %>% 
+  mutate(testresult_verified = case_when(
+    testresult > (median_testresult + 3) & 
+      testunits == "in" |
+      testresult < (median_testresult - 3) & 
+      testunits == "in"                         ~ NA_real_,
+    testresult > (median_testresult + 5) & 
+      testunits == "cm" |
+      testresult < (median_testresult - 5) & 
+      testunits == "cm"                         ~ NA_real_,
+    TRUE                                        ~ testresult
+  )) %>% 
+  # select(c("patientid", testdate, testresult, median_testresult, testresult_verified,
+  #          testunits, testunitscleaned, testresultcleaned, testresultcleaned_verified))
+
+  mutate(height = case_when(
+    !is.na(testresultcleaned_verified)          ~ round(testresultcleaned_verified / 100, 3), # cm to m
+    testunits == "cm"                           ~ round(testresult_verified / 100, 3),
+    testunits == "ft"                           ~ round(testresult_verified / 3.281, 3), # ft to m
+    testunits == "in" | 
+      !is.na(testresult)                        ~ round(testresult_verified / 39.37, 3) # in to m
+    )) %>% 
+  filter(!is.na(height)) %>% 
+  mutate(height_units = "m") %>% 
+  select(c("patientid", height_date = "testdate", "height", "height_units"))
+
+height %>% distinct(patientid, .keep_all = TRUE)
+```
+`r emo::ji("check")`
+
+<br>
+
+## Weight
+
+The more complex cleaning (before the drugs...`r emo::ji("sad")`). Contrary to height with in cm, ft or in which don't overlap. Weight has data in kg.......
+
+```{r weight}
+vitals %>%
+  filter(test == "body weight") %>% 
+  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
+  # 1.Clean testresultcleaned
+  group_by(patientid) %>%
+  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(weight1 = case_when(
+    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
+      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
+      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
+         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
+    TRUE ~ NA_real_
+  ))
+```
+
+## Drugs
+
+`r emo::ji("face_screaming_in_fear")`

### 2021-03-04 R/2.data cleaning.R

@@ -50,7 +50,7 @@ height <- vitals %>%
   # To get more data, I have data from testresult that can be used
   # But need to fill up testunits, transfer in kg and coalesce.
   group_by(patientid) %>% 
-  fill(testunits, .direction = "downup") %>% # F004D683A1695 have testresult, F615C37BF1470 is wrong
+  fill(testunits, .direction = "downup") %>% # F004D683A1695 have testresult, F615C37BF1470 is wrong, Otherwise I checked them all to see we can do that
   ungroup() %>% 
   # Clean up outliers compare to tallest ans smallest record
   mutate(testresultcleaned = case_when(

### 2021-03-10 Rmd/Report cleaning.Rmd
Add more cleaning explanation to the rmd

@@
 
-The more complex cleaning (before the drugs...`r emo::ji("sad")`). Contrary to height with in cm, ft or in which don't overlap. Weight has data in kg.......
-
-```{r weight}
+The more complex cleaning (before the drugs...`r emo::ji("sad")`).
+Contrary to height with units which don't overlap.
+Weight has data in `kg` in `testresultcleaned` and `kg`, `lb`, `oz` in `testresult`which are overlapping (a person can be 150lbs or 150kg).
+Cleanup of `testresultcleaned`...  
+```{r}
 vitals %>%
@@
     TRUE ~ NA_real_
+  )) %>% filter(patientid == "F0027D3926C88")
+```
+... and eliminate the outliers (36.4 kg can be normal for FF5268589DBE2, 39.5 F54F47F4419E0) 37.7 not F4A3B1B659865, F6CA354D599AA.
+I have an idea on how to improve that better `r emo::ji("cross_mark")``r emo::ji("light_bulb")``r emo::ji("bookmark")`
+```{r}
+vitals %>%
+  filter(test == "body weight") %>% 
+  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
+  # 1.Clean testresultcleaned
+  group_by(patientid) %>%
+  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(weight1 = case_when(
+    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
+      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
+      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
+         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
+    TRUE ~ NA_real_
+  )) %>% filter(str_detect(patientid, "F6CA354D599AA|F4A3B1B659865|FF5268589DBE2|F93CEAE4BF764|F1493F8F5A924|F18E68D19D10F|F54F47F4419E0"))
+```
+
+Cleanup of `testresult` for each units separately because can have 2 units per patients which can be correct or not.
+Plus try to rescue the units when some are `NA` but not all and eliminate the outliers.
+```{r}
+vitals %>%
+  filter(test == "body weight") %>% 
+  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
+  # 1.Clean testresultcleaned
+  group_by(patientid) %>%
+  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(weight1 = case_when(
+    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
+      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
+      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
+         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
+    TRUE ~ NA_real_
+  )) %>% 
+  # mutate(difference = (median_testresultcleaned)-testresultcleaned) # Can improve by > 30 and > 10 from previous measure so need to create a gap var ---------
+  # 2.Clean testresult to be used to find max and min
+  mutate(testresult = case_when(
+    testunits == "lb" &
+      testresult > 12 &
+      testresult < 643            ~ testresult,
+    testunits == "kg" &
+      testresult >= 5.5 &
+      testresult < 292            ~ testresult,
+    testunits == "oz" &
+      testresult > 194 &
+      testresult < 10286          ~ testresult,
+    is.na(testunits) & 
+    testresult > 5.5 & 
+      testresult < 10286          ~ testresult, # combine oz, kg, lbs for when units is NA
+    TRUE                          ~ NA_real_
+  )) %>% filter(str_detect(patientid, "F0027D3926C88"))
+
+weight <- vitals %>%
+  filter(test == "body weight") %>% 
+  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
+  # 1.Clean testresultcleaned
+  group_by(patientid) %>%
+  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(weight1 = case_when(
+    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
+      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
+      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
+         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
+    TRUE ~ NA_real_
+  )) %>% 
+  # mutate(difference = (median_testresultcleaned)-testresultcleaned) # Can improve by > 30 and > 10 from previous measure so need to create a gap var ---------
+  # 2.Clean testresult to be used to find max and min
+  mutate(testresult = case_when(
+    testunits == "lb" &
+      testresult > 12 &
+      testresult < 643            ~ testresult,
+    testunits == "kg" &
+      testresult >= 5.5 &
+      testresult < 292            ~ testresult,
+    testunits == "oz" &
+      testresult > 194 &
+      testresult < 10286          ~ testresult,
+    is.na(testunits) & 
+    testresult > 5.5 & 
+      testresult < 10286          ~ testresult, # combine oz, kg, lbs for when units is NA
+    TRUE                          ~ NA_real_
   ))
+```
+```{r}
+weight %>% 
+  # 3. Calculate median for each units and remove data outside range for each patients/unit
+  # 3. help distinguishing lbs to kg for same patient when unit is NA
+  group_by(patientid, testunits) %>%
+  mutate(median_testresult = median(testresult, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  mutate(testresult_verified = case_when(       # Can improve by > 30 and > 10 from previous measure so need to create a gap var --------
+    testunits == "kg" &
+    (testresult > (median_testresult + 38.5) | # choose 38.5 cm by default could do 32 if not for F534F9C4FF968
+       # 12 F2F31607FD6AD , FA7C8143AEE58 gain 37kg, F847A533FAE7E gain 38, FBE6E66AB2C95 gain 41, FC09E942CB0D7 gain 49
+       # F5B18C17A28F5 and F98077E9119EC FA53D0F672C7D FCFF0EDFE278F, FEF3273967DB3 wrong in cleaned too
+      testresult < (median_testresult - 38.5))         ~ NA_real_, 
+    testunits == "lb" &
+      (testresult > (median_testresult + 99) | # choose 99 cm by default, # Problem when wrong first value FCC755E4F8722 (94.8) keep in case close to first dosinf
+         testresult < (median_testresult - 99))      ~ NA_real_, # 91 for F00C16FEE3F74
+    TRUE                                             ~ testresult
+  )) %>% filter(str_detect(patientid, "FEF3273967DB3|F181950A26A19|F14EBD0D0FA81|F4A3B1B659865"))
+
+weight1 <- weight %>% 
+  # 3. Calculate median for each units and remove data outside range for each patients/unit
+  # 3. help distinguishing lbs to kg for same patient when unit is NA
+  group_by(patientid, testunits) %>%
+  mutate(median_testresult = median(testresult, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  mutate(testresult_verified = case_when(       # Can improve by > 30 and > 10 from previous measure so need to create a gap var --------
+    testunits == "kg" &
+    (testresult > (median_testresult + 38.5) | # choose 38.5 cm by default could do 32 if not for F534F9C4FF968
+       # 12 F2F31607FD6AD , FA7C8143AEE58 gain 37kg, F847A533FAE7E gain 38, FBE6E66AB2C95 gain 41, FC09E942CB0D7 gain 49
+       # F5B18C17A28F5 and F98077E9119EC FA53D0F672C7D FCFF0EDFE278F, FEF3273967DB3 wrong in cleaned too
+      testresult < (median_testresult - 38.5))         ~ NA_real_, 
+    testunits == "lb" &
+      (testresult > (median_testresult + 99) | # choose 99 cm by default, # Problem when wrong first value FCC755E4F8722 (94.8) keep in case close to first dosinf
+         testresult < (median_testresult - 99))      ~ NA_real_, # 91 for F00C16FEE3F74
+    TRUE                                             ~ testresult
+  )) %>%  # FCC755E4F8722 keep the first value anyway, eliminate that F8CB4CAB1073A (has 96 lbs difference-median) ?
+  # mutate(cal = testresult-median_testresult)
+  # mutate(difference = (median_testresultcleaned)-testresultcleaned)
+
+  # 4. Rescue testunits when testresult_verified is close 
+  # Calculate max and min to limit value for each patient-Choose 20
+  group_by(patientid, testunits) %>%
+  mutate(max_kg = case_when(
+    testunits == "kg" ~ max(testresult_verified, na.rm = TRUE) + 20 # F181950A26A19
+  )) %>%
+  mutate(min_kg = case_when(
+    testunits == "kg" ~ min(testresult_verified, na.rm = TRUE) - 20
+  )) %>%
+  mutate(max_lbs = case_when(
+    testunits == "lb" ~ max(testresult_verified, na.rm = TRUE) + 30 # F14EBD0D0FA81
+  )) %>%
+  mutate(min_lbs = case_when(
+    testunits == "lb" ~ min(testresult_verified, na.rm = TRUE) - 30
+  )) %>%
+  ungroup() %>% 
+  group_by(patientid) %>% 
+  fill(max_kg, min_kg, max_lbs, min_lbs, .direction = "downup") %>% # min_kg, max_lbs
+  ungroup() %>%
+
+  mutate(testunits_rescue = case_when(
+    is.na(testunits) &
+      testresult_verified < max_kg        ~ "kg", # Good doesn't work with F16847515CAF4 , Perfect for F8A3DD629CDA6
+    is.na(testunits) & # FE8DBCAC6DAFB
+      testresult_verified > min_lbs      ~ "lb" # F004D683A1695, F10CAD0F4EC48, FC109A6F719E7, FD25ED170CF07, FE06FF7C3E108, F044601199C5D
+  ))
+weight1 %>% filter(str_detect(patientid, "FEF3273967DB3|F181950A26A19|F14EBD0D0FA81|F4A3B1B659865"))
+```
+
+Sometimes `testunits` is wrong or change so try to rescue the unit within the same patient.
+Rescue units for when value is twice a `kg` value, it is `lb` value. 
+```{r}
+weight2 <- weight1 %>% 
+  group_by(patientid) %>% 
+  # 5. Rescue testunits when testresult_verified is twice or /2 means that lb or kg 
+  # if is 2 times the weight in kg add lb F14EBD0D0FA81
+  mutate(testunits_rescue1 = case_when(
+    is.na(testunits) &
+      testresult_verified < (max_kg * 2.205) &
+      testresult_verified > (min_kg * 2.205)         ~ "lb",
+    is.na(testunits) &
+      testresult_verified < (max_lbs / 2.205) &
+      testresult_verified > (min_lbs / 2.205)        ~ "kg"
+  )) %>% 
+  ungroup() %>% 
+  mutate(testunits = coalesce(testunits, testunits_rescue, testunits_rescue1)) %>% 
+  select(c("patientid", "testdate", "testunits", "testresult", "testresult_verified", "testunitscleaned", "testresultcleaned", "weight1"))
+weight1 %>% filter(str_detect(patientid, "F14EBD0D0FA81|F534F9C4FF968"))
+weight2 %>% filter(str_detect(patientid, "F14EBD0D0FA81|F534F9C4FF968"))
+```
+
+Can finally recalculate weight.
+
+F0027D3926C88
+```{r}
+weight <- weight2 %>% 
+  # 6.Fill up weight with new testresult_verified cleaned
+  mutate(weight2 = case_when(
+    is.na(testresultcleaned) &
+      testunits == "kg"         ~ testresult_verified, # F0027D3926C88, FE8DBCAC6DAFB, F8A3DD629CDA6, F020C6A8B9E50, F16847515CAF4
+    is.na(testresultcleaned) & # F044601199C5D
+      testunits == "lb"         ~ (testresult_verified / 2.205), # FCB918617347C, F5E3D88009911, F14EBD0D0FA81, F16847515CAF4, FABC474931881
+  )) %>% 
+  mutate(weight = coalesce(weight1, weight2)) %>% 
+  filter(!is.na(weight)) %>% 
+  mutate(weight_units = "kg") %>% 
+  select(c("patientid", weight_date = "testdate", "weight", "weight_units"))
+weight
+```
+
+## AUC
+
+I selected only AUC collected for the taxel and platin drugs but can have really high and low number.
+```{r}
+auc %>% 
+  filter(str_detect(drugname, "taxel|platin")) %>% 
+  filter(!is.na(relativeorderedamount)) %>% arrange(relativeorderedamount)
+auc %>% 
+  filter(str_detect(drugname, "taxel|platin")) %>% 
+  filter(!is.na(relativeorderedamount)) %>% arrange(desc(relativeorderedamount))
+```
+I clean the data up by keeping the `relativeorderedamount`:  
+- >= 50 & <= 175 for taxel  and with a unit in `mg/m2`  
+- >= 2  & <= 6   for platin and with a unit in `AUC`
+But few example for taxel
+```{r}
+auc %>% 
+  filter(str_detect(drugname, "taxel|platin")) %>% 
+  filter(!is.na(relativeorderedamount)) %>% 
+  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
+  #          "relativeorderedunits", "drugname", iscanceled)) %>%
+  mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
+    # relativeorderedunits == "mg/kg" |
+    #   relativeorderedunits == "mg" |
+    #   relativeorderedunits == "m"         ~ NA_real_,
+    str_detect(drugname, "taxel") &
+      relativeorderedunits == "mg/m2" &
+      relativeorderedamount >= 50 &
+      relativeorderedamount <= 175        ~ relativeorderedamount, # F21904E0D872F we should open more? F11B625154B62
+    str_detect(drugname, "platin") &
+      relativeorderedunits == "AUC" &
+      relativeorderedamount >= 2 &
+      relativeorderedamount <= 6          ~ relativeorderedamount, # F4E8C8717878B, FE3FF3A5AC465, F853DC24CD5E8
+    TRUE                                  ~ NA_real_
+  )) %>% filter(str_detect(patientid, "F21904E0D872F|F11B625154B62"))
+```
+
+But few example for platin
+```{r}
+auc %>% 
+  filter(str_detect(drugname, "taxel|platin")) %>% 
+  filter(!is.na(relativeorderedamount)) %>% 
+  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
+  #          "relativeorderedunits", "drugname", iscanceled)) %>%
+  mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
+    # relativeorderedunits == "mg/kg" |
+    #   relativeorderedunits == "mg" |
+    #   relativeorderedunits == "m"         ~ NA_real_,
+    str_detect(drugname, "taxel") &
+      relativeorderedunits == "mg/m2" &
+      relativeorderedamount >= 50 &
+      relativeorderedamount <= 175        ~ relativeorderedamount, # F21904E0D872F we should open more? F11B625154B62
+    str_detect(drugname, "platin") &
+      relativeorderedunits == "AUC" &
+      relativeorderedamount >= 2 &
+      relativeorderedamount <= 6          ~ relativeorderedamount, # F4E8C8717878B, FE3FF3A5AC465, F853DC24CD5E8
+    TRUE                                  ~ NA_real_
+  )) %>% filter(str_detect(patientid, "F4E8C8717878B|FE3FF3A5AC465|F853DC24CD5E8"))
+```
+
+Also we will see later that a lot of patients don't have any AUC.
+We talked and you advice to use the formula but I think that if we take the dose that a patient receive to reverse calculate the AUC we will automatically bias our results as we will create a AUC witch fit to the dose they received.
+Let me know if I misunderstood!!
+The result data
+```{r AUC}
+areaUC <- auc %>% 
+  filter(str_detect(drugname, "taxel|platin")) %>% 
+  filter(!is.na(relativeorderedamount)) %>% 
+  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
+  #          "relativeorderedunits", "drugname", iscanceled)) %>%
+  mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
+    # relativeorderedunits == "mg/kg" |
+    #   relativeorderedunits == "mg" |
+    #   relativeorderedunits == "m"         ~ NA_real_,
+    str_detect(drugname, "taxel") &
+      relativeorderedunits == "mg/m2" &
+      relativeorderedamount >= 50 &
+      relativeorderedamount <= 175        ~ relativeorderedamount, # F21904E0D872F we should open more? F11B625154B62
+    str_detect(drugname, "platin") &
+      relativeorderedunits == "AUC" &
+      relativeorderedamount >= 2 &
+      relativeorderedamount <= 6          ~ relativeorderedamount, # F4E8C8717878B, FE3FF3A5AC465, F853DC24CD5E8
+    TRUE                                  ~ NA_real_
+  )) %>%
+  select(c("patientid", auc_date = "expectedstartdate", "target_auc", 
+           auc_units = "relativeorderedunits", "drugname")) %>% 
+  filter(!is.na(target_auc))
+areaUC
+```
+
+## Clinical
+```{r}
+clinical_data
+```
+
+I cleaned up `race` as I think we want `Hispanic` to be in the `White` category. I aslo calculate `aprox_month_at_os` with `diagnosisdate` and `followupdate` (not complete date).
+```{r}
+clinical_data <- clinical_data %>% 
+  mutate(race = case_when(
+    str_detect(race, "Black")    ~ "Black",
+    str_detect(race, "Hispanic") ~ "White",
+    TRUE                         ~ race
+  )) %>% 
+  mutate(ethnicity = (str_remove(ethnicity, " or Latino"))) %>% 
+  unite(raceeth1, c(race,ethnicity), sep = " ", remove = FALSE, na.rm = TRUE) %>% 
+  mutate(vital = case_when(
+    vitalstatus == 0     ~ "Alive",
+    vitalstatus == 1     ~ "Dead"
+  )) %>% 
+  mutate(aprox_month_at_os = interval(start = diagnosisdate, end = followupdate)/
+           duration(n=1, units = "months")) %>% 
+  mutate(stagecat = na_if(stagecat, "Unk Stage")) %>% 
+  mutate(across(.cols = c(histology, groupstage, tstage), ~na_if(., "Unknown/not documented")))
+clinical_data
 ```
@@
 `r emo::ji("face_screaming_in_fear")`
+
+```{r}
+
+```
+
+`r  emo::ji("party_popper")`

### 2021-03-10 R/2.data cleaning.R

@@ -126,6 +126,7 @@ weight <- vitals %>%
          testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
     TRUE ~ NA_real_
   )) %>% 
+  # mutate(difference = (median_testresultcleaned)-testresultcleaned) # Can improve by > 30 and > 10 from previous measure so need to create a gap var ---------
   # 2.Clean testresult to be used to find max and min
   mutate(testresult = case_when(
     testunits == "lb" &
@@ -158,7 +159,7 @@ weight1 <- weight %>%
   group_by(patientid, testunits) %>%
   mutate(median_testresult = median(testresult, na.rm = TRUE)) %>% 
   ungroup() %>% 
-  mutate(testresult_verified = case_when(
+  mutate(testresult_verified = case_when(       # Can improve by > 30 and > 10 from previous measure so need to create a gap var --------
     testunits == "kg" &
     (testresult > (median_testresult + 38.5) | # choose 38.5 cm by default could do 32 if not for F534F9C4FF968
        # 12 F2F31607FD6AD , FA7C8143AEE58 gain 37kg, F847A533FAE7E gain 38, FBE6E66AB2C95 gain 41, FC09E942CB0D7 gain 49
@@ -170,6 +171,7 @@ weight1 <- weight %>%
     TRUE                                             ~ testresult
   )) %>%  # FCC755E4F8722 keep the first value anyway, eliminate that F8CB4CAB1073A (has 96 lbs difference-median) ?
   # mutate(cal = testresult-median_testresult)
+  # mutate(difference = (median_testresultcleaned)-testresultcleaned)
 
   # 4. Rescue testunits when testresult_verified is close 
   # Calculate max and min to limit value for each patient-Choose 20

### 2021-03-11 Rmd/Report cleaning.Rmd
Start drug cleaning explanation

@@
 
-`r emo::ji("face_screaming_in_fear")`
+Here is the fun`r emo::ji("face_screaming_in_fear")`!  
+The first cleanup step is to only keep the drugs which were administered to patients and removing the maintenance drugs, I also filtered "taxel" and "platin" drugs administered by "intravenous" or "peritoneal" route.
+Comments: Done like that I automatically remove the line with only
+main as 1 or sec
+<span style='color: red;'>Is that a problem?</span>
 
+I guess it is perfect for F71460509E771  
+Looks ok for F9E61D896E2FE FA550FA15524A  but please take a look just to make sure
 ```{r}
-
+drugs %>% filter(str_detect(patientid, "F9E61D896E2FE|FA550FA15524A|F71460509E771"))
 ```
 
+One thing I saw is that patients can have multiple records (rows) for the same drug (different amount for what I saw) on the same day.
+After out talk last time we decided to combined multiple amount of drug given the same day 
+FYI, I found that on the Flatiron website:
+
+*# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day.
+We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day.
+Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data.
+Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
+# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
+# Three administrations of the same drug were listed on a Friday.
+The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.
+# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.*
+
+It may be 205 patients row like that (over 145517 total rows). Example here:
+```{r}
+drugs %>% 
+  filter(episodedatasource == "Administrations" & ismaintenancetherapy == "FALSE" & !is.na(amount)) %>%
+  filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% 
+  select(-c(ismaintenancetherapy, enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
+  filter(str_detect(patientid, "FCF86329BB40C|F4E6EE1910940"))
+```
+
+In the `amount` variable I found `mg`, `ug`, `ml`, `Ea`, `AUC` and `NA`.
+They all look in the range but `AUC` which sometimes < 10 (someone probably enter the real AUC!) so I removed these ones and convert `ug` amount into `mg`.
+I also filtered out patients who had `issurgery` == "Yes" but no `surgerydate` associated (10 patients).
+```{r drugs1}
+drugs1 <- drugs %>% 
+  # 1. Filtering----
+  filter(episodedatasource == "Administrations" & ismaintenancetherapy == "FALSE" & !is.na(amount)) %>%
+  filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% 
+  select(-c(ismaintenancetherapy, enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
+  group_by(patientid, linename, linenumber, linestartdate, lineenddate,episodedate, drugname, units) %>%
+  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
+  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
+           fill = "right") %>%
+  purrr::keep(~!all(is.na(.))) %>%
+  ungroup() %>% 
+  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
+         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
+  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
+  # Found ug, ml, Ea, AUC and NA they are all good, but the AUC & < at 10 are wrong and ug need conversion
+  mutate(amount =  case_when(
+    units == "ug"               ~ amount / 10, # I checked all of them
+    units == "AUC" &
+      amount < 10               ~ NA_real_,
+    TRUE                        ~ amount
+  )) %>%
+
+  # 3.bind with clinical----
+  full_join(., clinical_data %>% select(-c(primaryphysicianid)),
+            by = "patientid") %>% 
+  # Limit to the patients we have date of surgery when had surgery
+  filter(!(issurgery == "Yes" & is.na(surgerydate)))
+```
+
+Then the `linenumber` coding starts!!
+
+Just to make sure when we talked, you said that we don't want to increase the line number when it is a change in drug. Example:
+```{r}
+drugs1 %>% filter(str_detect(patientid, "F9E61D896E2FE|FA550FA15524A|F71460509E771"))
+```
+
+1- Change linenumber when surgery
+I had to built the new_linenumber on top of the old one because of some patients who has a change of drug but are still line 1.
+```{r}
+drugs1 %>% 
+  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
+  mutate(chemotherapy_type = case_when(
+    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
+    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
+    episodedate > surgerydate         ~ "Adjuvant",
+    issurgery == "No/unknown" &
+      !is.na(episodedate)             ~ "Chemotherapy only",
+    issurgery == "Yes" &
+      is.na(episodedate)              ~ "Surgery only"
+    )) %>% 
+  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
+  group_by(patientid) %>% 
+  mutate(therapy = case_when(
+    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only"
+  )) %>% 
+  fill(therapy, .direction = "downup") %>% 
+  mutate(therapy1 = case_when(
+    chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
+  )) %>% 
+  fill(therapy1, .direction = "downup") %>% 
+  mutate(therapy = coalesce(therapy, therapy1)) %>% 
+  select( -therapy1) %>%
+
+  # 5.Redefine line number based on the original linenumber variable and the surgery date----
+  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>% 
+  select(patientid, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, linename)
+```
+
+Change of cyle/drugs (I don't think it happen often)
+F071D61E6FB93
+
+Change in cycle
+F1775A21CC4DB
+
 `r  emo::ji("party_popper")`

### 2021-03-11 R/2.data cleaning.R

@@ -313,7 +313,7 @@ drugs1 <- drugs %>%
   mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
          amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
   mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
-  # Found ug, ml, Ea, AUC and NA they are all good, but the AUC & < at 10 are wrong and ug need consersion
+  # Found ug, ml, Ea, AUC and NA they are all good, but the AUC & < at 10 are wrong and ug need conversion
   mutate(amount =  case_when(
     units == "ug"               ~ amount / 10, # I checked all of them
     units == "AUC" &
@@ -340,6 +340,10 @@ therapy <- drugs1 %>%
     )) %>% 
   mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
   group_by(patientid) %>% 
+  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
+  fill(had_neo, .direction = "updown") %>% 
+  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
+  fill(had_adj, .direction = "updown") %>% 
   mutate(therapy = case_when(
     chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
     chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
@@ -355,6 +359,7 @@ therapy <- drugs1 %>%
   
   # 5.Redefine line number based on the original linenumber variable and the surgery date----
   mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803, F95D860690A93 still weird FA019D2071321 no has big jump
+  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
   ungroup() %>% 
   
   # 6.Add a 30 day rule to switch linenumber----

### 2021-03-11 Rmd/Report cleaning.Rmd
Add treatment_sequence + add more on drugs in rmd

@@
 
-Just to make sure when we talked, you said that we don't want to increase the line number when it is a change in drug. Example:
+Just to make sure when we talked, you said that we don't want to increase the line number when it is a change in cycle/drug (I don't think it happen often). Example:
 ```{r}
-drugs1 %>% filter(str_detect(patientid, "F9E61D896E2FE|FA550FA15524A|F71460509E771"))
+drugs1 %>% filter(str_detect(patientid, "F071D61E6FB93"))
+```
+Also what when a change of cycle:
+```{r}
+drugs1 %>% filter(str_detect(patientid, "F1775A21CC4DB"))
 ```
 
-1- Change linenumber when surgery
-I had to built the new_linenumber on top of the old one because of some patients who has a change of drug but are still line 1.
+1- Increase `linenumber` when surgery
+I had to built the `new_linenumber` on top of the old one if we want to keep these change of drug within line.
 ```{r}
@@
   group_by(patientid) %>% 
+  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
+  fill(had_neo, .direction = "updown") %>% 
+  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
+  fill(had_adj, .direction = "updown") %>% 
+  mutate(treatment_sequence = case_when(
+    had_neo == "Yes" &
+      had_adj == "Yes"                           ~ "neo + surg + adj",
+    had_neo == "Yes" &
+      is.na(had_adj)                             ~ "neo + surg",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "surg + adj",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only"
+  )) %>% 
   mutate(therapy = case_when(
@@
     chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
-    chemotherapy_type == "Surgery only"          ~ "Surgery only"
+    chemotherapy_type == "Surgery only"          ~ "Surgery only",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "Upfront Surgery"
   )) %>% 
   fill(therapy, .direction = "downup") %>% 
-  mutate(therapy1 = case_when(
-    chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
-  )) %>% 
-  fill(therapy1, .direction = "downup") %>% 
-  mutate(therapy = coalesce(therapy, therapy1)) %>% 
-  select( -therapy1) %>%
-
   # 5.Redefine line number based on the original linenumber variable and the surgery date----
-  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>% 
-  select(patientid, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, linename)
+  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803, F95D860690A93 still weird FA019D2071321 no has big jump
+  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
+  ungroup() %>% 
+  select(patientid, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, linename, treatment_sequence) %>%
+  filter()
 ```
 
-Change of cyle/drugs (I don't think it happen often)
-F071D61E6FB93
-
-Change in cycle
-F1775A21CC4DB
-
 `r  emo::ji("party_popper")`

### 2021-03-11 R/2.data cleaning.R

@@ -344,18 +344,30 @@ therapy <- drugs1 %>%
   fill(had_neo, .direction = "updown") %>% 
   mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
   fill(had_adj, .direction = "updown") %>% 
-  mutate(therapy = case_when(
-    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
+  mutate(treatment_sequence = case_when(
+    had_neo == "Yes" &
+      had_adj == "Yes"                           ~ "neo + surg + adj",
+    had_neo == "Yes" &
+      is.na(had_adj)                             ~ "neo + surg",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "surg + adj",
     chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
     chemotherapy_type == "Surgery only"          ~ "Surgery only"
   )) %>% 
-  fill(therapy, .direction = "downup") %>% 
-  mutate(therapy1 = case_when(
-    chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
+  mutate(therapy = case_when(
+    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "Upfront Surgery"
   )) %>% 
-  fill(therapy1, .direction = "downup") %>% 
-  mutate(therapy = coalesce(therapy, therapy1)) %>% 
-  select( -therapy1) %>% 
+  fill(therapy, .direction = "downup") %>% 
+  # mutate(therapy1 = case_when(
+  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
+  # )) %>% 
+  # fill(therapy1, .direction = "downup") %>% 
+  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
+  # select( -therapy1) %>% 
   
   # 5.Redefine line number based on the original linenumber variable and the surgery date----
   mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803, F95D860690A93 still weird FA019D2071321 no has big jump

### 2021-03-11 R/3.clinical mining.R

@@ -52,6 +52,17 @@ analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE)
   guides(fill = FALSE) +
   coord_flip()
 
+analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>% 
+  filter(exclude != "1") %>% 
+  group_by(treatment_sequence) %>% 
+  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
+  geom_bar(stat="identity")+
+  labs(x = "", title = "The treatment_sequence") +
+  theme_minimal()+
+  guides(fill = FALSE) +
+  coord_flip()
+
 # analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
 #   ggplot(aes(x= chemo))+
 #   geom_bar()+

### 2021-03-12 Rmd/Report cleaning.Rmd
Finished Rmd explanation cleaning

--- 2021-03-10 Rmd/Report cleaning.Rmd
@@
 ```{r creatinine, rows.print=15, max.print=15}
-creatinine %>% filter(str_detect(labcomponent, "blood|serum")) %>% 
+creatinine %>% filter(str_detect(labcomponent, "blood|serum")) %>% select(-c(loinc, test, labcomponent)) %>% 
 arrange(testresultcleaned)
@@
 All `testresultcleaned` and `testresult` variable are cleaned as :  
--creat < 0.8 is set at 0.8  
--creat > 3 are eliminated  
-To create the final `creatinine` variable ,`testresultcleaned` and `testresult` are both used but `testresultcleaned` is used over `testresult` when both are available.
+- creat < 0.8 was set at 0.8  
+- creat > 3 are eliminated  
+To create the final `creatinine` variable ,`testresultcleaned` and `testresult` are both used but `testresultcleaned` was used over `testresult` when both are available.
 
@@
 ```
+`r emo::ji("check")`
 <br>
@@
 `testresultcleaned` is all within expected range but only few data is available (`r NROW(body_surface_area %>% filter(!is.na(testresultcleaned)) %>% distinct(patientid, .keep.all=TRUE))` patients).
-Even less with an associated date!
+Probably even less with an associated date.
 
 ```{r bsa}
-body_surface_area
+body_surface_area %>% select(-c(loinc, test, labcomponent))
 ```
@@
 By using `testresult` and before cleaning only `r NROW(body_surface_area %>% filter(!is.na(body_surface_area$testresult)) %>% distinct(patientid, .keep.all=TRUE))` patients have data for their BSA.
-So I will also use the height and weight of patients to calculate their BSA by using the Du Bois formula.
+This was improved by using the Du Bois formula to calculate more BSA value as you will see later.
 
-To create the final `BSA` variable ,`testresultcleaned` is used over `testresult` when both are available.  
+To create the final `BSA` variable ,`testresultcleaned` was used over `testresult` when both are available.  
 `testresult` was further cleaned as data < 0.418 and > 4.14 are eliminated. These values were calculated from the biggest and the smallest individuals recorded.  
-I also remove the outliers within patient (2 examples here).
+I also remove the outliers within patient (2 examples here where we have outliers).
 
@@
 
-Here a sample of the cleaned data
+Here the cleaned data
 
-```{r bsa1, rows.print=15, max.print=15}
+```{r bsa1}
 body_surface_area <- vitals %>% 
@@
 
-body_surface_area %>% distinct(patientid, .keep_all = TRUE)
+body_surface_area %>% distinct(patientid, .keep_all = TRUE) %>% arrange(patientid, bsa_date)
 ```
+`r emo::ji("check")`
 <br>
@@
 
-Height data complicated. Again you have `testresultcleaned` and `testresult` with `testresultcleaned` which will prioritized.  
-`testresultcleaned` has units in cm but some data are wrong. `testresult` has results in cm, ft or in. It is pretty easy to clean data between these 3 units because the measurement cannot overlap.
+Height data is pretty complicated. Again I used `testresultcleaned` and `testresult` with `testresultcleaned` which was prioritized.  
+`testresultcleaned` has units in cm but some data are wrong. `testresult` has results in cm, ft or in. It was pretty easy to clean data between these 3 units because the measurement cannot overlap.
 Both are cleaned as < 120 or > 231 are eliminated. These value are for the shortest and tallest women recorded.
@@
 vitals %>% 
-  filter(test == "body height" & patientid == "FCB6DAAFF6527")
+  filter(test == "body height" & patientid == "FCB6DAAFF6527") %>% select(-c(loinc, test, labcomponent, resultdate))
 # FC109A6F719E7
@@
   filter(patientid == "F01413C06D921") %>% 
-  select(c("patientid", testdate, testresultcleaned, median_testresultcleaned, testresultcleaned_verified,
+  select(c("patientid", testdate, testresultcleaned, testresultcleaned_verified,median_testresultcleaned, 
            testunitscleaned, testunits, testresult))
 ```
+`r  emo::ji("question_mark")`
+PB: Some patients have height but don't have dates associated. If all dates are `NA` for a patient, I cannot combined a specific `height` with a closest date to `episodedate` of the drug data.
+Should I take a mean of all the height values measured or the first one - If I have to choose I would take the mean (patients shouldn't grow up or shorten much)?
 
-PB: Some patient don't have dates but have data. Should I take a mean of all the height measured or the first one - If I have to choose I would take the mean (patients shouldn't grow or shorten much)?
-If all dates are NA for a patients, I cannot combined `height` with `episodedate` of the drug data.
-
-Here a samples of the data.
-```{r height2, rows.print=15, max.print=15}
+Here is the data.
+```{r height2}
 height <- vitals %>% 
@@
 ```
-`r emo::ji("check")`
+Beside my question it is `r emo::ji("check")`
 
@@
 
-The more complex cleaning (before the drugs...`r emo::ji("sad")`).
-Contrary to height with units which don't overlap.
-Weight has data in `kg` in `testresultcleaned` and `kg`, `lb`, `oz` in `testresult`which are overlapping (a person can be 150lbs or 150kg).
+The more complex cleaning (before the drugs...`r  emo::ji("loudly_crying_face")`).
+Contrary to height with units which don't overlap, weight has data in `kg` in `testresultcleaned` and `kg`, `lb`, `oz` in `testresult` which are overlapping (a person can be 150lbs or 150kg).
 Cleanup of `testresultcleaned`...  
@@
   filter(test == "body weight") %>% 
-  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
+  select(c("patientid", "testdate", "testunitscleaned", "testresultcleaned")) %>%
   # 1.Clean testresultcleaned
@@
 ```
-... and eliminate the outliers (36.4 kg can be normal for FF5268589DBE2, 39.5 F54F47F4419E0) 37.7 not F4A3B1B659865, F6CA354D599AA.
-I have an idea on how to improve that better `r emo::ji("cross_mark")``r emo::ji("light_bulb")``r emo::ji("bookmark")`
+...
+and eliminate the outliers (a patient gaining 36.4 kg can be normal for FF5268589DBE2, 39.5kg F54F47F4419E0) but 37.7 doesn't look normal F4A3B1B659865, F6CA354D599AA.
+My present cleaning save some data but not everything...
+I just had an idea on how to improve that better while doing the report.  
+`r emo::ji("cross_mark")``r emo::ji("light_bulb")``r emo::ji("bookmark")`
 ```{r}
@@
 
-Cleanup of `testresult` for each units separately because can have 2 units per patients which can be correct or not.
-Plus try to rescue the units when some are `NA` but not all and eliminate the outliers.
+I had to clean `testresult` for each units separately within a patients because I saw patients with 2 units in their records.
+I also rescued the units when some are `NA` but not all and eliminate the outliers.
+
 ```{r}
-vitals %>%
-  filter(test == "body weight") %>% 
-  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
-  # 1.Clean testresultcleaned
-  group_by(patientid) %>%
-  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(weight1 = case_when(
-    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
-      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
-      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
-         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
-    TRUE ~ NA_real_
-  )) %>% 
-  # mutate(difference = (median_testresultcleaned)-testresultcleaned) # Can improve by > 30 and > 10 from previous measure so need to create a gap var ---------
-  # 2.Clean testresult to be used to find max and min
-  mutate(testresult = case_when(
-    testunits == "lb" &
-      testresult > 12 &
-      testresult < 643            ~ testresult,
-    testunits == "kg" &
-      testresult >= 5.5 &
-      testresult < 292            ~ testresult,
-    testunits == "oz" &
-      testresult > 194 &
-      testresult < 10286          ~ testresult,
-    is.na(testunits) & 
-    testresult > 5.5 & 
-      testresult < 10286          ~ testresult, # combine oz, kg, lbs for when units is NA
-    TRUE                          ~ NA_real_
-  )) %>% filter(str_detect(patientid, "F0027D3926C88"))
+# vitals %>%
+#   filter(test == "body weight") %>% 
+#   select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
+#   # 1.Clean testresultcleaned
+#   group_by(patientid) %>%
+#   mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
+#   ungroup() %>%
+#   mutate(weight1 = case_when(
+#     testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
+#       testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
+#       (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
+#          testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
+#     TRUE ~ NA_real_
+#   )) %>% 
+#   # mutate(difference = (median_testresultcleaned)-testresultcleaned) # Can improve by > 30 and > 10 from previous measure so need to create a gap var ---------
+#   # 2.Clean testresult to be used to find max and min
+#   mutate(testresult = case_when(
+#     testunits == "lb" &
+#       testresult > 12 &
+#       testresult < 643            ~ testresult,
+#     testunits == "kg" &
+#       testresult >= 5.5 &
+#       testresult < 292            ~ testresult,
+#     testunits == "oz" &
+#       testresult > 194 &
+#       testresult < 10286          ~ testresult,
+#     is.na(testunits) & 
+#     testresult > 5.5 & 
+#       testresult < 10286          ~ testresult, # combine oz, kg, lbs for when units is NA
+#     TRUE                          ~ NA_real_
+#   )) %>% filter(str_detect(patientid, "F0027D3926C88")) %>% 
+#   select(c("patientid", "testdate", "testunits", "testresult",)
 
@@
 
-Sometimes `testunits` is wrong or change so try to rescue the unit within the same patient.
-Rescue units for when value is twice a `kg` value, it is `lb` value. 
+Sometimes `testunits` was wrong or changed so try to rescue the unit within the same patient.
+For example these 2 patients have data in `kg` and earlier data with no units but doubled values so I assumed these data where on `lb.`
+
 ```{r}
@@
 weight1 %>% filter(str_detect(patientid, "F14EBD0D0FA81|F534F9C4FF968"))
+```
+
+The units are rescued here.
+```{r}
 weight2 %>% filter(str_detect(patientid, "F14EBD0D0FA81|F534F9C4FF968"))
@@
 
-F0027D3926C88
+<!-- F0027D3926C88 -->
 ```{r}
@@
 
+I can probably improve my cleaning the same way as height but beside that is it `r emo::ji("check")`
+<br>
+
 ## AUC
 
-I selected only AUC collected for the taxel and platin drugs but can have really high and low number.
-```{r}
+I selected only AUC collected for the "taxel" and "platin" drugs but can have really high and low values.
+```{r, rows.print=15, max.print=15}
 auc %>% 
   filter(str_detect(drugname, "taxel|platin")) %>% 
-  filter(!is.na(relativeorderedamount)) %>% arrange(relativeorderedamount)
+  filter(!is.na(relativeorderedamount)) %>% arrange(relativeorderedamount) %>% select(patientid, relativeorderedamount, orderedamount, orderedunits, everything())
 auc %>% 
   filter(str_detect(drugname, "taxel|platin")) %>% 
-  filter(!is.na(relativeorderedamount)) %>% arrange(desc(relativeorderedamount))
+  filter(!is.na(relativeorderedamount)) %>% arrange(desc(relativeorderedamount)) %>% select(patientid, relativeorderedamount, orderedamount, orderedunits, everything())
 ```
@@
 - >= 2  & <= 6   for platin and with a unit in `AUC`
-But few example for taxel
+`r  emo::ji("question_mark")` But few example for taxel are remove for a `relativeorderedamount` at 36. Should we open it up a little more?
 ```{r}
@@
   filter(!is.na(relativeorderedamount)) %>% 
-  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
-  #          "relativeorderedunits", "drugname", iscanceled)) %>%
   mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
-    # relativeorderedunits == "mg/kg" |
-    #   relativeorderedunits == "mg" |
-    #   relativeorderedunits == "m"         ~ NA_real_,
     str_detect(drugname, "taxel") &
@@
     TRUE                                  ~ NA_real_
-  )) %>% filter(str_detect(patientid, "F21904E0D872F|F11B625154B62"))
+  )) %>% filter(str_detect(patientid, "F21904E0D872F|F11B625154B62")) %>% select(patientid, drugname, relativeorderedamount,relativeorderedunits, target_auc, orderedamount, orderedunits, expectedstartdate)
 ```
 
-But few example for platin
+`r  emo::ji("question_mark")` Same for platin?
 ```{r}
@@
     TRUE                                  ~ NA_real_
-  )) %>% filter(str_detect(patientid, "F4E8C8717878B|FE3FF3A5AC465|F853DC24CD5E8"))
+  )) %>% filter(str_detect(patientid, "F4E8C8717878B|FE3FF3A5AC465|F853DC24CD5E8")) %>% select(patientid, drugname, relativeorderedamount,relativeorderedunits, target_auc, orderedamount, orderedunits, expectedstartdate)
 ```
 
-Also we will see later that a lot of patients don't have any AUC.
+`r  emo::ji("question_mark")` Also we will see later that a lot of patients don't have any `relativeorderedamount`.
 We talked and you advice to use the formula but I think that if we take the dose that a patient receive to reverse calculate the AUC we will automatically bias our results as we will create a AUC witch fit to the dose they received.
 Let me know if I misunderstood!!
-The result data
+`r  emo::ji("question_mark")` One other idea could be to calculate `relativeorderedamount` from `orderedamount` which look like it is just divided by bsa... Is that correct?
+The resulted data
 ```{r AUC}
@@
 ```
+Beside my question it is `r emo::ji("check")`
+<br>
 
@@
 
-I cleaned up `race` as I think we want `Hispanic` to be in the `White` category. I aslo calculate `aprox_month_at_os` with `diagnosisdate` and `followupdate` (not complete date).
+I cleaned up `race` as I think we want `Hispanic` to be in the `White` category. I also calculate `month_at_os` with `diagnosisdate` and `followupdate`.
 ```{r}
@@
   )) %>% 
-  mutate(aprox_month_at_os = interval(start = diagnosisdate, end = followupdate)/
+  mutate(month_at_os = interval(start = diagnosisdate, end = followupdate)/
            duration(n=1, units = "months")) %>% 
@@
 ```
+`r emo::ji("check")`
+<br>
 
@@
 
-`r emo::ji("face_screaming_in_fear")`
+Here is the fun`r emo::ji("face_screaming_in_fear")`!  
+The first cleanup step is to only keep the drugs which were **administered** to patients and removing the **maintenance** drugs, I also filtered **"taxel" and "platin"** drugs administered by **"intravenous" or "peritoneal"** route.
+`r  emo::ji("question_mark")` Done like that, I automatically remove the maintenance part within line which include non-maintenance drugs. 
+<span style='color: red;'>I just want to make sure this is ok</span>
 
+<!-- F71460509E771 is an example where it works perfectly     -->
+Here are 2 examples where my code will remove the maintenance part within the first line but please take a look just to make sure.
 ```{r}
+drugs %>% filter(str_detect(patientid, "F9E61D896E2FE|FA550FA15524A")) %>% filter(episodedatasource == "Administrations") %>% 
+  arrange(patientid, episodedate) %>% select(patientid,  linenumber, ismaintenancetherapy, drugname,linename, episodedate,  everything())
+```
+
+Another thing I saw is that patients can have multiple records (rows) for the same drug (usually with different amount) on the same day.  
+After our talk last time we decided to combined these multiple amount of drug given the same day. 
+FYI, I found that on the Flatiron website:
+
+*"There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day.
+We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day.
+Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data.
+Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
+For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.  
+Three administrations of the same drug were listed on a Friday.
+The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.
+Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol."*
+
+It may be only 205 patients row like that (over 145517 total rows). Example here:
+```{r}
+drugs %>% 
+  filter(episodedatasource == "Administrations" & ismaintenancetherapy == "FALSE" & !is.na(amount)) %>%
+  filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% 
+  select(-c(ismaintenancetherapy, enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
+  filter(str_detect(patientid, "FCF86329BB40C|F4E6EE1910940")) %>% 
+  select(patientid, episodedate, drugname, amount, everything())
+```
+
+In the `amount` variable I found `mg`, `ug`, `ml`, `Ea`, `AUC` and `NA`.
+They all look in the range (ug for ug and mg for everything else) but `AUC` has sometimes values < 10 (someone probably enter the real AUC!) so I removed these ones and convert `ug` amount into `mg`.
+I also filtered out patients who had `issurgery` == "Yes" but no `surgerydate` associated (10 patients).
+```{r drugs1}
+drugs1 <- drugs %>% 
+  # 1. Filtering----
+  filter(episodedatasource == "Administrations" & ismaintenancetherapy == "FALSE" & !is.na(amount)) %>%
+  filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% 
+  select(-c(ismaintenancetherapy, enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
+  group_by(patientid, linename, linenumber, linestartdate, lineenddate,episodedate, drugname, units) %>%
+  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
+  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
+           fill = "right") %>%
+  purrr::keep(~!all(is.na(.))) %>%
+  ungroup() %>% 
+  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
+         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
+  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
+  # Found ug, ml, Ea, AUC and NA they are all good, but the AUC & < at 10 are wrong and ug need conversion
+  mutate(amount =  case_when(
+    units == "ug"               ~ amount / 10, # I checked all of them
+    units == "AUC" &
+      amount < 10               ~ NA_real_,
+    TRUE                        ~ amount
+  )) %>%
+
+  # 3.bind with clinical----
+  full_join(., clinical_data %>% select(-c(primaryphysicianid)),
+            by = "patientid") %>% 
+  # Limit to the patients we have date of surgery when had surgery
+  filter(!(issurgery == "Yes" & is.na(surgerydate)))
+```
+
+Then the `linenumber` coding starts!!
+
+`r  emo::ji("question_mark")` Just to make sure, when we talked, you said that we don't want to increase the line number when it is a change in cycle/drug (I don't think it happens often).
+2 Examples here.
+The change of cycle type for the first patient happens in the second line and in the first line for the second patient.
+Is that still good?
+```{r}
+drugs1 %>% filter(str_detect(patientid, "F071D61E6FB93|F001443D8B85C")) %>% select(patientid, linename, linenumber, drugname, episodedate, everything())
+```
+`r  emo::ji("question_mark")` For this example, it is a change of drug and cycle type. I guess the patients didn't react well...but I still want to make sure it is ok.
+```{r}
+drugs1 %>% filter(str_detect(patientid, "F1775A21CC4DB")) %>% select(patientid, linename, linenumber, drugname, episodedate, everything())
+```
+<br>
+
+### 1. Increase `linenumber` when surgery
+I had to built the `new_linenumber` on top of the old one if we want to keep the type of change of drug within line that we saw above.
+```{r}
+drugs1 %>% 
+  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
+  mutate(chemotherapy_type = case_when(
+    episodedate <= surgerydate        ~ "Neoadjuvant", 
+    episodedate > surgerydate         ~ "Adjuvant",
+    issurgery == "No/unknown" &
+      !is.na(episodedate)             ~ "Chemotherapy only",
+    issurgery == "Yes" &
+      is.na(episodedate)              ~ "Surgery only"
+    )) %>% 
+  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
+  group_by(patientid) %>% 
+  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
+  fill(had_neo, .direction = "updown") %>% 
+  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
+  fill(had_adj, .direction = "updown") %>% 
+  mutate(treatment_sequence = case_when(
+    had_neo == "Yes" &
+      had_adj == "Yes"                           ~ "neo + surg + adj",
+    had_neo == "Yes" &
+      is.na(had_adj)                             ~ "neo + surg",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "surg + adj",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only"
+  )) %>% 
+  mutate(therapy = case_when(
+    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "Upfront Surgery"
+  )) %>% 
+  fill(therapy, .direction = "downup") %>% 
+  # 5.Redefine line number based on the original linenumber variable and the surgery date----
+  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump
+  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
+  ungroup() %>% 
+  select(patientid, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, linename, treatment_sequence)%>%
+  filter(str_detect(patientid, "F0000AD999ABF|F1C68CFAC2AF3|FBCF69031DFF8|F95D860690A93")) # F95D860690A93 still weird
+```
+`r emo::ji("check")`
+<br>
+
+### 2. Add a 30 days rule to increase the line number.
+We may want to increase to a 40 days rule...
+```{r}
+therapy <- drugs1 %>% 
+  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
+  mutate(chemotherapy_type = case_when(
+    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
+    episodedate > surgerydate         ~ "Adjuvant",
+    issurgery == "No/unknown" &
+      !is.na(episodedate)             ~ "Chemotherapy only",
+    issurgery == "Yes" &
+      is.na(episodedate)              ~ "Surgery only"
+    )) %>% 
+  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
+  group_by(patientid) %>% 
+  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
+  fill(had_neo, .direction = "updown") %>% 
+  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
+  fill(had_adj, .direction = "updown") %>% 
+  mutate(treatment_sequence = case_when(
+    had_neo == "Yes" &
+      had_adj == "Yes"                           ~ "neo + surg + adj",
+    had_neo == "Yes" &
+      is.na(had_adj)                             ~ "neo + surg",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "surg + adj",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only"
+  )) %>% 
+  mutate(therapy = case_when(
+    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "Upfront Surgery"
+  )) %>% 
+  fill(therapy, .direction = "downup") %>% 
+  # mutate(therapy1 = case_when(
+  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
+  # )) %>% 
+  # fill(therapy1, .direction = "downup") %>% 
+  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
+  # select( -therapy1) %>%
+
+  # 5.Redefine line number based on the original linenumber variable and the surgery date----
+  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803, F95D860690A93 still weird FA019D2071321 no has big jump
+  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
+  ungroup() %>%
+
+  # 6.Add a 30 day rule to switch linenumber----
+  group_by(patientid, linenumber_new) %>% 
+  arrange(episodedate) %>% 
+  mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
+  mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
+  ungroup() %>% 
+  group_by(patientid) %>% 
+  mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
+  mutate(linenumber_new = linenumber_new + jump_line) %>% 
+  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37
+
+  # 7.Calculate cycle for each line----
+  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>% 
+  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION
+  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
+  ungroup()
+
+therapy %>% select(patientid, linenumber, linenumber_new, drugname, episodedate, episode_interval, jump_line, chemotherapy_type, linename, treatment_sequence) %>%
+  filter(str_detect(patientid, "F002DD2953889|F005602DA4DF0"))
+```
+
+`r  emo::ji("question_mark")` What to do when cycle type change?  
+In this example the patient had surgery so my `linenumber_new` junp at "2" but a little before that the patient cycle change from carbo+pacli+pacli to pacli+carbo. Is that still good?
+```{r}
+therapy %>% select(patientid, linenumber, linenumber_new, drugname, episodedate, episode_interval, jump_line, chemotherapy_type, linename, treatment_sequence) %>%
+  filter(patientid == "F003F2BEEDB37")
+```
+Beside my questions it is `r emo::ji("check")`
+<br>
+
+### 3. Code cycle
+I was able to code a `cycle_increment`.
+```{r therapy}
+therapy1 <- therapy %>% 
+  select(-c("linenumber")) %>%
+  arrange(episodedate) %>% 
+  group_by(patientid, linenumber_new) %>%
+  mutate(cycle_count_perline = min(drugname_count_perline)) %>% 
+  mutate(cycle_drugname = case_when(
+    cycle_count_perline == drugname_count_perline          ~ drugname,
+    TRUE                                                   ~ NA_character_
+  )) %>% 
+  group_by(patientid, linenumber_new, cycle_drugname) %>%
+  mutate(cycle_inc = row_number(cycle_drugname)) %>%
+
+  group_by(patientid, linenumber_new, cycle_inc) %>%
+  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
+  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>%  # Problem for F001443D8B85C (make a code before recoding linenumber_new like if drugname is not in the linename remove linename)
+  arrange(patientid, episodedate, cycle_inc) %>% 
+  group_by(patientid, linenumber_new) %>%
+  mutate(cycle_increment = cycle_inc) %>% 
+  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
+  # cycle date
+  group_by(patientid, linenumber_new, cycle_increment) %>% 
+  mutate(cycle_start_date = min(episodedate)) %>% 
+  # select(patientid, linename, linenumber_new, drugname, episodedate, episode_interval,
+  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>%
+
+  group_by(patientid, linenumber_new) %>% 
+  mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
+         cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
+
+  # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
+  mutate(n = row_number(drugname)) %>%
+
+  mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
+  fill(base_days_between_cycle, .direction = "downup") %>% 
+  mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
+                                       (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
+  # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
+  group_by(patientid, linenumber_new) %>%
+  mutate(drug_count_perline = n()) %>%
+  mutate(skipped_cycle_indays1 = ifelse(
+    (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
+  )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
+  # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
+  group_by(patientid) %>% 
+  mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
+  ungroup()
+
+therapy1 %>% select(patientid, linenumber_new, drugname, episodedate, cycle_increment, cycle_start_date, cycle_interval, chemotherapy_type, linename) %>%
+  filter(str_detect(patientid, "F003F2BEEDB37|F0000AD999ABF"))
 
@@
 
-`r  emo::ji("party_popper")`
+`r  emo::ji("question_mark")` Can we consider docetaxel as = paclitaxel, and carboplatin = cisplatin for cycle determination?  
+The first example switch between paclitaxel and docetaxel so my code doesn't detect the different cycle. The second example switch between cisplatin and carboplatin.
+```{r}
+therapy1 %>% select(patientid, linenumber_new, drugname, episodedate, cycle_increment, cycle_start_date, cycle_interval, chemotherapy_type, linename) %>%
+  filter(str_detect(patientid, "FBB5186A15CD9|FE593EDF5586A"))
+```
+
+We are good with drugs!!!!! `r  emo::ji("party_popper")`... after updating the code based on your answers.
+<br>
+<br>
+
+***
+<br>
+
+# Calculation for analysis
+```{r}
+Treatment <- 
+  # Merge with creatinine
+  left_join(therapy1, creatinine, by = "patientid") %>%
+  mutate(interval = abs(interval(start= creat_date, end= cycle_start_date)/                      
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Merge with height
+  left_join(. , height,  by = "patientid") %>%
+  mutate(interval = abs(interval(start= height_date, end= cycle_start_date)/                      
+           duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Merge with weight
+  left_join(. , weight, by = "patientid") %>%
+  mutate(interval = abs(interval(start= weight_date, end= cycle_start_date)/                      
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Calculate bmi
+  mutate(bmi = weight / (height * height)) %>% 
+  mutate(bmi_cat = case_when(
+    bmi < 25                    ~ "Underweight and normal weight",
+    bmi >= 25 &
+      bmi < 30                  ~ "Overweight",
+    bmi >= 30                   ~ "Obese"
+  )) %>% 
+  # Calculate CrCl
+  mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
+
+  # Merge with body_surface_area
+  left_join(., body_surface_area, by = "patientid") %>%
+  mutate(interval = abs(interval(start= bsa_date, end= cycle_start_date)/                      
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>% 
+  # Calculate more bsa value with height and weight using Du Bois formula
+  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
+  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>% 
+  select(-bsa_du_bois) %>%
+
+  # Merge with auc
+  left_join(., areaUC, by = c("patientid", "drugname")) %>%
+  mutate(interval = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>% 
+  select(-interval) %>%
+
+  # Calculate expected dose
+  mutate(expected_dose = case_when(
+    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
+    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
+    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
+  )) %>% 
+  mutate(expected_dose = case_when(
+    expected_dose > 900 &
+      target_auc == 6              ~ 900,
+    expected_dose > 750 &
+      target_auc == 5              ~ 750,
+    TRUE                           ~ expected_dose
+  )) %>% 
+  arrange(patientid, episodedate)
+
+Frontline <- Treatment %>% 
+  mutate(relative_dose_intensity = round(amount/expected_dose, 3)) %>%
+  group_by(patientid, chemotherapy_type, drugname) %>% 
+  mutate(mean_rdi_per_drug = mean(relative_dose_intensity)) %>% 
+  ungroup() %>% 
+  mutate(RDI_grp = as.factor(findInterval(relative_dose_intensity, c(0.75, 0.85, 1, 1.5, 2) ))) %>% 
+  mutate(RDI_grp = factor(RDI_grp, 
+                          levels = c("0", "1","2","3", "4", "5"), 
+                          labels = c("0 < RDI < 0.75", "0.75 <= RDI < 0.85", "0.85 >= RDI < 1", "1 <= RDI < 1.5", 
+                                     "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
+  mutate(delay_incare_dx_to_treat = case_when(
+    str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
+      duration(n=1, units = "days")),
+    str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
+      duration(n=1, units = "days"))
+  ))
+```
+
+I joined each drug administration row to the closest `creatinine`, `height`, `weight`, `BSA`, `target_auc` in date.
+I used the Du Bois formula to increase the number of data for `BSA` using weight and height now `r NROW(Frontline %>% filter(!is.na(BSA)) %>% distinct(patientid, .keep.all=TRUE))` patients vs a maximum of `r NROW(body_surface_area %>% filter(!is.na(BSA)) %>% distinct(patientid, .keep.all=TRUE))` at the start.
+$$bsa\_du\_bois = 0.007184 * (height*100)^{0.725} * weight^{0.425}$$
+
+So I was able to calculate `bmi`, `CrCl`, `expected_dose`.  
+`expected_dose` is:  
+-`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
+-`BSA` * `target_auc`           -> for `drugname` == "taxel" or "platin"  
+It was fixed to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5.
+
+Then I calculate $$relative\_dose\_intensity = \frac{amount}{expected\_dose}$$
+
+I was also able to calculate the delay between diagnosis and treatment. Here is the final data:
+```{r}
+Frontline
+```
+
+That deserve a party!!!  
+<font size="10"> `r  emo::ji("party_popper")``r  emo::ji("balloon")``r  emo::ji("clinking_glasses")``r  emo::ji("confetti")`</font>
+
+Another file will be coming soon (hopefully in the next couple of weeks) with the plots and analysis I already have.
+Let me know what you think about the cleaning part!

### 2021-03-12 R/2.data cleaning.R

@@ -271,7 +271,7 @@ clinical_data <- clinical_data %>%
     vitalstatus == 1     ~ "Dead"
   )) %>% 
   # mutate(aprox_month_at_os = followuptime/30.417) %>% 
-  mutate(aprox_month_at_os = interval(start = diagnosisdate, end = followupdate)/
+  mutate(month_at_os = interval(start = diagnosisdate, end = followupdate)/
            duration(n=1, units = "months")) %>% 
   mutate(stagecat = na_if(stagecat, "Unk Stage")) %>% 
   mutate(across(.cols = c(histology, groupstage, tstage), ~na_if(., "Unknown/not documented")))
@@ -370,7 +370,7 @@ therapy <- drugs1 %>%
   # select( -therapy1) %>% 
   
   # 5.Redefine line number based on the original linenumber variable and the surgery date----
-  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803, F95D860690A93 still weird FA019D2071321 no has big jump
+  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird
   select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
   ungroup() %>% 
   
@@ -386,8 +386,8 @@ therapy <- drugs1 %>%
   #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37
   
   # 7.Calculate cycle for each line----
-  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>% 
-  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION
+  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
[…]

### 2021-03-17 Rmd/Report analysis 03172021.Rmd
New Rmd Flatiron analysis

--- 2021-03-11 Rmd/Report cleaning.Rmd
@@
 ---
-title: "Flatiron data cleaning and analysis report"
+title: "Flatiron analysis"
 author: "Christelle Colin-Leitzinger"
-date: '`r Sys.Date()`'
+date: "3/17/2021"
 output: 
@@
 
-# Data cleaning
+# Analysis
 ***
@@
 
-## Creatinine cleaning
-
-Only creatinine from blood and serum are being used. All units are correct (mg/dL).  
-Here an sample of the non-cleaned data with really low `testresultcleaned`.
-
-```{r creatinine, rows.print=15, max.print=15}
-creatinine %>% filter(str_detect(labcomponent, "blood|serum")) %>% 
-arrange(testresultcleaned)
-```
-All `testresultcleaned` and `testresult` variable are cleaned as :  
--creat < 0.8 is set at 0.8  
--creat > 3 are eliminated  
-To create the final `creatinine` variable ,`testresultcleaned` and `testresult` are both used but `testresultcleaned` is used over `testresult` when both are available.
-
-Here a sample of the cleaned data
-```{r creatinine1, rows.print=15, max.print=15}
-creatinine <- creatinine %>%
-  # remove creatine urine
-  filter(str_detect(labcomponent, "blood|serum")) %>% 
-  mutate(creatinine = case_when(
-    testresultcleaned < 0.8        ~ 0.8,
-    testresultcleaned > 3          ~ NA_real_,
-    TRUE                           ~ testresultcleaned
-  )) %>% 
-  # F092F8B827DDC kept umol/L as they actually are mg/dL range 45 to 90 μmol/L (0.5 to 1.0 mg/dL) for women.
-  mutate(creatinine1 = case_when(
-    testresult < 0.8               ~ 0.8,
-    testresult > 3                 ~ NA_real_,
-    TRUE                           ~ testresult
-  )) %>% 
-  mutate(creatinine = coalesce(creatinine, creatinine1)) %>% 
-  filter(!is.na(creatinine)) %>% 
-  mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
-  select(c("patientid", creat_date = "testdate", "creatinine", creat_units = "testunitscleaned"))
-creatinine %>% distinct(patientid, .keep_all = TRUE)
-
-vitals <- vitals %>% 
-  mutate(testdate = as.Date(testdate, format = "%m/%d/%y"))
-body_surface_area <- vitals %>% 
-  filter(labcomponent == "Body Surface Area (BSA)")
-```
-<br>
-
-## Body surface area cleaning
-
-`testresultcleaned` is all within expected range but only few data is available (`r NROW(body_surface_area %>% filter(!is.na(testresultcleaned)) %>% distinct(patientid, .keep.all=TRUE))` patients).
-Even less with an associated date!
-
-```{r bsa}
-body_surface_area
-```
-
-By using `testresult` and before cleaning only `r NROW(body_surface_area %>% filter(!is.na(body_surface_area$testresult)) %>% distinct(patientid, .keep.all=TRUE))` patients have data for their BSA.
-So I will also use the height and weight of patients to calculate their BSA by using the Du Bois formula.
-
-To create the final `BSA` variable ,`testresultcleaned` is used over `testresult` when both are available.  
-`testresult` was further cleaned as data < 0.418 and > 4.14 are eliminated. These values were calculated from the biggest and the smallest individuals recorded.  
-I also remove the outliers within patient (2 examples here).
-
-```{r}
-vitals %>% 
-  filter(labcomponent == "Body Surface Area (BSA)" & patientid == "F2D5A8748B268") %>% 
-  select(patientid, testdate, testresult, testresultcleaned)
-vitals %>% 
-  filter(labcomponent == "Body Surface Area (BSA)" & patientid == "F875EA1B044F0") %>% 
-  select(patientid, testdate, testresult, testresultcleaned)
-# F3AE4546B5D12
-```
-
-Here a sample of the cleaned data
-
-```{r bsa1, rows.print=15, max.print=15}
-body_surface_area <- vitals %>% 
-  filter(labcomponent == "Body Surface Area (BSA)") %>% # only 399 patients data
-  # Limit max = 4.14, min = 0.418 calculated for biggest to smallest person
-  mutate(testresult = ifelse(testresult < 0.418 | testresult > 4.14, NA_real_, testresult)) %>% 
-  group_by(patientid) %>%
-  # I used the median to remove outlier within a patient
-  mutate(median_testresult = median(testresult)) %>% 
-  ungroup() %>% 
-  mutate(BSA = case_when(
-    testresult > (median_testresult + 0.4) |
-      testresult < (median_testresult - 0.4)      ~ NA_real_,
-    TRUE                                          ~ testresult
-  )) %>% 
-  mutate(BSA = coalesce(testresultcleaned, BSA)) %>% 
-  filter(!is.na(BSA)) %>% 
-  mutate(BSA_units = "m2") %>% 
-  select(c("patientid", bsa_date = "testdate", "BSA", "BSA_units"))
-
-body_surface_area %>% distinct(patientid, .keep_all = TRUE)
-```
-<br>
-
-## Height
-
-Height data complicated. Again you have `testresultcleaned` and `testresult` with `testresultcleaned` which will prioritized.  
-`testresultcleaned` has units in cm but some data are wrong. `testresult` has results in cm, ft or in. It is pretty easy to clean data between these 3 units because the measurement cannot overlap.
-Both are cleaned as < 120 or > 231 are eliminated. These value are for the shortest and tallest women recorded.
-The units can be filled by patients when absent.
-
-```{r height}
-vitals %>% 
-  filter(test == "body height" & patientid == "FCB6DAAFF6527")
-# FC109A6F719E7
-# FC106805F9AB9
-# F91590CB83EC8 weird
-```
-
-Outliers are eliminated as much as possible.
-
-```{r height1}
-vitals %>% 
-  filter(test == "body height") %>% 
-  # To get more data, I have data from testresult that can be used
-  # But need to fill up testunits, transfer in kg and coalesce.
-  group_by(patientid) %>% 
-  fill(testunits, .direction = "downup") %>% # F004D683A1695 have testresult, F615C37BF1470 is wrong, Otherwise I checked them all to see we can do that
-  ungroup() %>% 
-  # Clean up outliers compare to tallest ans smallest record
-  mutate(testresultcleaned = case_when(
-    testresultcleaned > 231 | # Tallest women height
-      testresultcleaned < 120 # Average height dwarf = 122 cm, 4 feet, I take 120 by loooking at the data
-                                     ~ NA_real_,
-    TRUE                             ~ testresultcleaned
-  )) %>% 
-  mutate(testresult = case_when(
-    testresult > 231 & testunits == "cm" |
-      testresult < 100 & testunits == "cm" |
-      testresult > 7.58 & testunits == "ft" |
-      testresult < 3.28 & testunits == "ft" |
-      testresult > 90.94 & testunits == "in" |
-      testresult < 39.37 & testunits == "in"|
-      testresult == 0
-                                     ~ NA_real_,
-    TRUE                             ~ testresult
-  )) %>% 
-  # Clean up outliers within patient by using the median for each patients/unit. Eliminate the ones with too much variation.
-  group_by(patientid) %>%
-  mutate(median_testresultcleaned = median(testresultcleaned)) %>% 
-  ungroup() %>% 
-  mutate(testresultcleaned_verified = case_when(
-    testresultcleaned > (median_testresultcleaned + 5) | # choose 5 cm by default
-      testresultcleaned < (median_testresultcleaned - 5)      ~ NA_real_, # F01413C06D921 weird
-    TRUE                                                      ~ testresultcleaned
-  )) %>% 
-  filter(patientid == "F01413C06D921") %>% 
-  select(c("patientid", testdate, testresultcleaned, median_testresultcleaned, testresultcleaned_verified,
-           testunitscleaned, testunits, testresult))
-```
-
-PB: Some patient don't have dates but have data. Should I take a mean of all the height measured or the first one - If I have to choose I would take the mean (patients shouldn't grow or shorten much)?
-If all dates are NA for a patients, I cannot combined `height` with `episodedate` of the drug data.
-
-Here a samples of the data.
-```{r height2, rows.print=15, max.print=15}
-height <- vitals %>% 
-  filter(test == "body height") %>% 
-  # To get more data, I have data from testresult that can be used
-  # But need to fill up testunits, transfer in kg and coalesce.
-  group_by(patientid) %>% 
-  fill(testunits, .direction = "downup") %>% # F004D683A1695 have testresult, F615C37BF1470 is wrong, Otherwise I checked them all to see we can do that
-  ungroup() %>% 
-  # Clean up outliers compare to tallest ans smallest record
-  mutate(testresultcleaned = case_when(
-    testresultcleaned > 231 | # Tallest women height
-      testresultcleaned < 120 # Average height dwarf = 122 cm, 4 feet, I take 120 by loooking at the data
-                                     ~ NA_real_,
-    TRUE                             ~ testresultcleaned
-  )) %>% 
-  mutate(testresult = case_when(
-    testresult > 231 & testunits == "cm" |
-      testresult < 100 & testunits == "cm" |
-      testresult > 7.58 & testunits == "ft" |
-      testresult < 3.28 & testunits == "ft" |
-      testresult > 90.94 & testunits == "in" |
-      testresult < 39.37 & testunits == "in"|
-      testresult == 0
-                                     ~ NA_real_,
-    TRUE                             ~ testresult
-  )) %>% 
-  # Clean up outliers within patient by using the median for each patients/unit. Eliminate the ones with too much variation.
-  group_by(patientid) %>%
-  mutate(median_testresultcleaned = median(testresultcleaned)) %>% 
-  ungroup() %>% 
-  mutate(testresultcleaned_verified = case_when(
-    testresultcleaned > (median_testresultcleaned + 5) | # choose 5 cm by default
-      testresultcleaned < (median_testresultcleaned - 5)      ~ NA_real_, # F01413C06D921 weird
-    TRUE                                                      ~ testresultcleaned
-  )) %>% 
-  # select(c("patientid", testdate, testresultcleaned, median_testresultcleaned, testresultcleaned_verified, 
-  #          testunitscleaned, testunits, testresult)) %>%
-
-  group_by(patientid, testunits) %>%
-  mutate(median_testresult = median(testresult)) %>% 
-  ungroup() %>% 
-  mutate(testresult_verified = case_when(
-    testresult > (median_testresult + 3) & 
-      testunits == "in" |
-      testresult < (median_testresult - 3) & 
-      testunits == "in"                         ~ NA_real_,
-    testresult > (median_testresult + 5) & 
-      testunits == "cm" |
-      testresult < (median_testresult - 5) & 
-      testunits == "cm"                         ~ NA_real_,
-    TRUE                                        ~ testresult
-  )) %>% 
-  # select(c("patientid", testdate, testresult, median_testresult, testresult_verified,
-  #          testunits, testunitscleaned, testresultcleaned, testresultcleaned_verified))
-
-  mutate(height = case_when(
-    !is.na(testresultcleaned_verified)          ~ round(testresultcleaned_verified / 100, 3), # cm to m
-    testunits == "cm"                           ~ round(testresult_verified / 100, 3),
-    testunits == "ft"                           ~ round(testresult_verified / 3.281, 3), # ft to m
-    testunits == "in" | 
-      !is.na(testresult)                        ~ round(testresult_verified / 39.37, 3) # in to m
-    )) %>% 
-  filter(!is.na(height)) %>% 
-  mutate(height_units = "m") %>% 
-  select(c("patientid", height_date = "testdate", "height", "height_units"))
-
-height %>% distinct(patientid, .keep_all = TRUE)
-```
-`r emo::ji("check")`
-
-<br>
-
-## Weight
-
-The more complex cleaning (before the drugs...`r emo::ji("sad")`).
-Contrary to height with units which don't overlap.
-Weight has data in `kg` in `testresultcleaned` and `kg`, `lb`, `oz` in `testresult`which are overlapping (a person can be 150lbs or 150kg).
-Cleanup of `testresultcleaned`...  
-```{r}
-vitals %>%
-  filter(test == "body weight") %>% 
-  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
-  # 1.Clean testresultcleaned
-  group_by(patientid) %>%
-  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(weight1 = case_when(
-    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
-      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
-      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
-         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
-    TRUE ~ NA_real_
-  )) %>% filter(patientid == "F0027D3926C88")
-```
-... and eliminate the outliers (36.4 kg can be normal for FF5268589DBE2, 39.5 F54F47F4419E0) 37.7 not F4A3B1B659865, F6CA354D599AA.
-I have an idea on how to improve that better `r emo::ji("cross_mark")``r emo::ji("light_bulb")``r emo::ji("bookmark")`
-```{r}
-vitals %>%
-  filter(test == "body weight") %>% 
-  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
-  # 1.Clean testresultcleaned
-  group_by(patientid) %>%
-  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(weight1 = case_when(
-    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
-      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
-      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
-         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
-    TRUE ~ NA_real_
-  )) %>% filter(str_detect(patientid, "F6CA354D599AA|F4A3B1B659865|FF5268589DBE2|F93CEAE4BF764|F1493F8F5A924|F18E68D19D10F|F54F47F4419E0"))
-```
-
-Cleanup of `testresult` for each units separately because can have 2 units per patients which can be correct or not.
-Plus try to rescue the units when some are `NA` but not all and eliminate the outliers.
-```{r}
-vitals %>%
-  filter(test == "body weight") %>% 
-  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
-  # 1.Clean testresultcleaned
-  group_by(patientid) %>%
-  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(weight1 = case_when(
-    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
-      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
-      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
-         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
-    TRUE ~ NA_real_
-  )) %>% 
-  # mutate(difference = (median_testresultcleaned)-testresultcleaned) # Can improve by > 30 and > 10 from previous measure so need to create a gap var ---------
-  # 2.Clean testresult to be used to find max and min
-  mutate(testresult = case_when(
-    testunits == "lb" &
-      testresult > 12 &
-      testresult < 643            ~ testresult,
-    testunits == "kg" &
-      testresult >= 5.5 &
-      testresult < 292            ~ testresult,
-    testunits == "oz" &
-      testresult > 194 &
-      testresult < 10286          ~ testresult,
-    is.na(testunits) & 
-    testresult > 5.5 & 
-      testresult < 10286          ~ testresult, # combine oz, kg, lbs for when units is NA
-    TRUE                          ~ NA_real_
-  )) %>% filter(str_detect(patientid, "F0027D3926C88"))
-
-weight <- vitals %>%
-  filter(test == "body weight") %>% 
-  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
-  # 1.Clean testresultcleaned
-  group_by(patientid) %>%
-  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(weight1 = case_when(
-    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
-      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
-      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
-         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
-    TRUE ~ NA_real_
-  )) %>% 
-  # mutate(difference = (median_testresultcleaned)-testresultcleaned) # Can improve by > 30 and > 10 from previous measure so need to create a gap var ---------
-  # 2.Clean testresult to be used to find max and min
-  mutate(testresult = case_when(
-    testunits == "lb" &
-      testresult > 12 &
-      testresult < 643            ~ testresult,
-    testunits == "kg" &
-      testresult >= 5.5 &
-      testresult < 292            ~ testresult,
-    testunits == "oz" &
-      testresult > 194 &
-      testresult < 10286          ~ testresult,
-    is.na(testunits) & 
-    testresult > 5.5 & 
-      testresult < 10286          ~ testresult, # combine oz, kg, lbs for when units is NA
-    TRUE                          ~ NA_real_
-  ))
-```
-```{r}
-weight %>% 
-  # 3. Calculate median for each units and remove data outside range for each patients/unit
-  # 3. help distinguishing lbs to kg for same patient when unit is NA
-  group_by(patientid, testunits) %>%
-  mutate(median_testresult = median(testresult, na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  mutate(testresult_verified = case_when(       # Can improve by > 30 and > 10 from previous measure so need to create a gap var --------
-    testunits == "kg" &
-    (testresult > (median_testresult + 38.5) | # choose 38.5 cm by default could do 32 if not for F534F9C4FF968
-       # 12 F2F31607FD6AD , FA7C8143AEE58 gain 37kg, F847A533FAE7E gain 38, FBE6E66AB2C95 gain 41, FC09E942CB0D7 gain 49
-       # F5B18C17A28F5 and F98077E9119EC FA53D0F672C7D FCFF0EDFE278F, FEF3273967DB3 wrong in cleaned too
-      testresult < (median_testresult - 38.5))         ~ NA_real_, 
-    testunits == "lb" &
-      (testresult > (median_testresult + 99) | # choose 99 cm by default, # Problem when wrong first value FCC755E4F8722 (94.8) keep in case close to first dosinf
-         testresult < (median_testresult - 99))      ~ NA_real_, # 91 for F00C16FEE3F74
-    TRUE                                             ~ testresult
-  )) %>% filter(str_detect(patientid, "FEF3273967DB3|F181950A26A19|F14EBD0D0FA81|F4A3B1B659865"))
-
-weight1 <- weight %>% 
-  # 3. Calculate median for each units and remove data outside range for each patients/unit
-  # 3. help distinguishing lbs to kg for same patient when unit is NA
-  group_by(patientid, testunits) %>%
-  mutate(median_testresult = median(testresult, na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  mutate(testresult_verified = case_when(       # Can improve by > 30 and > 10 from previous measure so need to create a gap var --------
-    testunits == "kg" &
-    (testresult > (median_testresult + 38.5) | # choose 38.5 cm by default could do 32 if not for F534F9C4FF968
-       # 12 F2F31607FD6AD , FA7C8143AEE58 gain 37kg, F847A533FAE7E gain 38, FBE6E66AB2C95 gain 41, FC09E942CB0D7 gain 49
-       # F5B18C17A28F5 and F98077E9119EC FA53D0F672C7D FCFF0EDFE278F, FEF3273967DB3 wrong in cleaned too
-      testresult < (median_testresult - 38.5))         ~ NA_real_, 
-    testunits == "lb" &
-      (testresult > (median_testresult + 99) | # choose 99 cm by default, # Problem when wrong first value FCC755E4F8722 (94.8) keep in case close to first dosinf
-         testresult < (median_testresult - 99))      ~ NA_real_, # 91 for F00C16FEE3F74
-    TRUE                                             ~ testresult
-  )) %>%  # FCC755E4F8722 keep the first value anyway, eliminate that F8CB4CAB1073A (has 96 lbs difference-median) ?
-  # mutate(cal = testresult-median_testresult)
-  # mutate(difference = (median_testresultcleaned)-testresultcleaned)
-
-  # 4. Rescue testunits when testresult_verified is close 
-  # Calculate max and min to limit value for each patient-Choose 20
-  group_by(patientid, testunits) %>%
-  mutate(max_kg = case_when(
-    testunits == "kg" ~ max(testresult_verified, na.rm = TRUE) + 20 # F181950A26A19
-  )) %>%
-  mutate(min_kg = case_when(
-    testunits == "kg" ~ min(testresult_verified, na.rm = TRUE) - 20
-  )) %>%
-  mutate(max_lbs = case_when(
-    testunits == "lb" ~ max(testresult_verified, na.rm = TRUE) + 30 # F14EBD0D0FA81
-  )) %>%
-  mutate(min_lbs = case_when(
-    testunits == "lb" ~ min(testresult_verified, na.rm = TRUE) - 30
-  )) %>%
-  ungroup() %>% 
-  group_by(patientid) %>% 
-  fill(max_kg, min_kg, max_lbs, min_lbs, .direction = "downup") %>% # min_kg, max_lbs
-  ungroup() %>%
-
-  mutate(testunits_rescue = case_when(
-    is.na(testunits) &
-      testresult_verified < max_kg        ~ "kg", # Good doesn't work with F16847515CAF4 , Perfect for F8A3DD629CDA6
-    is.na(testunits) & # FE8DBCAC6DAFB
-      testresult_verified > min_lbs      ~ "lb" # F004D683A1695, F10CAD0F4EC48, FC109A6F719E7, FD25ED170CF07, FE06FF7C3E108, F044601199C5D
-  ))
-weight1 %>% filter(str_detect(patientid, "FEF3273967DB3|F181950A26A19|F14EBD0D0FA81|F4A3B1B659865"))
-```
-
-Sometimes `testunits` is wrong or change so try to rescue the unit within the same patient.
-Rescue units for when value is twice a `kg` value, it is `lb` value. 
-```{r}
-weight2 <- weight1 %>% 
-  group_by(patientid) %>% 
-  # 5. Rescue testunits when testresult_verified is twice or /2 means that lb or kg 
-  # if is 2 times the weight in kg add lb F14EBD0D0FA81
-  mutate(testunits_rescue1 = case_when(
-    is.na(testunits) &
-      testresult_verified < (max_kg * 2.205) &
-      testresult_verified > (min_kg * 2.205)         ~ "lb",
-    is.na(testunits) &
-      testresult_verified < (max_lbs / 2.205) &
-      testresult_verified > (min_lbs / 2.205)        ~ "kg"
-  )) %>% 
-  ungroup() %>% 
-  mutate(testunits = coalesce(testunits, testunits_rescue, testunits_rescue1)) %>% 
-  select(c("patientid", "testdate", "testunits", "testresult", "testresult_verified", "testunitscleaned", "testresultcleaned", "weight1"))
-weight1 %>% filter(str_detect(patientid, "F14EBD0D0FA81|F534F9C4FF968"))
-weight2 %>% filter(str_detect(patientid, "F14EBD0D0FA81|F534F9C4FF968"))
-```
-
-Can finally recalculate weight.
-
-F0027D3926C88
-```{r}
-weight <- weight2 %>% 
-  # 6.Fill up weight with new testresult_verified cleaned
-  mutate(weight2 = case_when(
-    is.na(testresultcleaned) &
-      testunits == "kg"         ~ testresult_verified, # F0027D3926C88, FE8DBCAC6DAFB, F8A3DD629CDA6, F020C6A8B9E50, F16847515CAF4
-    is.na(testresultcleaned) & # F044601199C5D
-      testunits == "lb"         ~ (testresult_verified / 2.205), # FCB918617347C, F5E3D88009911, F14EBD0D0FA81, F16847515CAF4, FABC474931881
-  )) %>% 
-  mutate(weight = coalesce(weight1, weight2)) %>% 
-  filter(!is.na(weight)) %>% 
-  mutate(weight_units = "kg") %>% 
-  select(c("patientid", weight_date = "testdate", "weight", "weight_units"))
-weight
-```
-
-## AUC
-
-I selected only AUC collected for the taxel and platin drugs but can have really high and low number.
-```{r}
-auc %>% 
-  filter(str_detect(drugname, "taxel|platin")) %>% 
-  filter(!is.na(relativeorderedamount)) %>% arrange(relativeorderedamount)
-auc %>% 
-  filter(str_detect(drugname, "taxel|platin")) %>% 
-  filter(!is.na(relativeorderedamount)) %>% arrange(desc(relativeorderedamount))
-```
-I clean the data up by keeping the `relativeorderedamount`:  
-- >= 50 & <= 175 for taxel  and with a unit in `mg/m2`  
-- >= 2  & <= 6   for platin and with a unit in `AUC`
-But few example for taxel
-```{r}
-auc %>% 
-  filter(str_detect(drugname, "taxel|platin")) %>% 
-  filter(!is.na(relativeorderedamount)) %>% 
-  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
-  #          "relativeorderedunits", "drugname", iscanceled)) %>%
-  mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
-    # relativeorderedunits == "mg/kg" |
-    #   relativeorderedunits == "mg" |
-    #   relativeorderedunits == "m"         ~ NA_real_,
-    str_detect(drugname, "taxel") &
-      relativeorderedunits == "mg/m2" &
-      relativeorderedamount >= 50 &
-      relativeorderedamount <= 175        ~ relativeorderedamount, # F21904E0D872F we should open more? F11B625154B62
-    str_detect(drugname, "platin") &
-      relativeorderedunits == "AUC" &
-      relativeorderedamount >= 2 &
-      relativeorderedamount <= 6          ~ relativeorderedamount, # F4E8C8717878B, FE3FF3A5AC465, F853DC24CD5E8
-    TRUE                                  ~ NA_real_
-  )) %>% filter(str_detect(patientid, "F21904E0D872F|F11B625154B62"))
-```
-
-But few example for platin
-```{r}
-auc %>% 
-  filter(str_detect(drugname, "taxel|platin")) %>% 
-  filter(!is.na(relativeorderedamount)) %>% 
-  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
-  #          "relativeorderedunits", "drugname", iscanceled)) %>%
-  mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
-    # relativeorderedunits == "mg/kg" |
-    #   relativeorderedunits == "mg" |
-    #   relativeorderedunits == "m"         ~ NA_real_,
-    str_detect(drugname, "taxel") &
-      relativeorderedunits == "mg/m2" &
-      relativeorderedamount >= 50 &
-      relativeorderedamount <= 175        ~ relativeorderedamount, # F21904E0D872F we should open more? F11B625154B62
-    str_detect(drugname, "platin") &
-      relativeorderedunits == "AUC" &
-      relativeorderedamount >= 2 &
-      relativeorderedamount <= 6          ~ relativeorderedamount, # F4E8C8717878B, FE3FF3A5AC465, F853DC24CD5E8
-    TRUE                                  ~ NA_real_
-  )) %>% filter(str_detect(patientid, "F4E8C8717878B|FE3FF3A5AC465|F853DC24CD5E8"))
-```
-
-Also we will see later that a lot of patients don't have any AUC.
-We talked and you advice to use the formula but I think that if we take the dose that a patient receive to reverse calculate the AUC we will automatically bias our results as we will create a AUC witch fit to the dose they received.
-Let me know if I misunderstood!!
-The result data
-```{r AUC}
-areaUC <- auc %>% 
-  filter(str_detect(drugname, "taxel|platin")) %>% 
-  filter(!is.na(relativeorderedamount)) %>% 
-  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
-  #          "relativeorderedunits", "drugname", iscanceled)) %>%
-  mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
-    # relativeorderedunits == "mg/kg" |
-    #   relativeorderedunits == "mg" |
-    #   relativeorderedunits == "m"         ~ NA_real_,
-    str_detect(drugname, "taxel") &
-      relativeorderedunits == "mg/m2" &
-      relativeorderedamount >= 50 &
-      relativeorderedamount <= 175        ~ relativeorderedamount, # F21904E0D872F we should open more? F11B625154B62
-    str_detect(drugname, "platin") &
-      relativeorderedunits == "AUC" &
-      relativeorderedamount >= 2 &
-      relativeorderedamount <= 6          ~ relativeorderedamount, # F4E8C8717878B, FE3FF3A5AC465, F853DC24CD5E8
-    TRUE                                  ~ NA_real_
-  )) %>%
-  select(c("patientid", auc_date = "expectedstartdate", "target_auc", 
-           auc_units = "relativeorderedunits", "drugname")) %>% 
-  filter(!is.na(target_auc))
-areaUC
-```
-
-## Clinical
-```{r}
-clinical_data
-```
-
-I cleaned up `race` as I think we want `Hispanic` to be in the `White` category. I aslo calculate `aprox_month_at_os` with `diagnosisdate` and `followupdate` (not complete date).
-```{r}
-clinical_data <- clinical_data %>% 
-  mutate(race = case_when(
-    str_detect(race, "Black")    ~ "Black",
-    str_detect(race, "Hispanic") ~ "White",
-    TRUE                         ~ race
-  )) %>% 
-  mutate(ethnicity = (str_remove(ethnicity, " or Latino"))) %>% 
-  unite(raceeth1, c(race,ethnicity), sep = " ", remove = FALSE, na.rm = TRUE) %>% 
-  mutate(vital = case_when(
-    vitalstatus == 0     ~ "Alive",
-    vitalstatus == 1     ~ "Dead"
-  )) %>% 
-  mutate(aprox_month_at_os = interval(start = diagnosisdate, end = followupdate)/
-           duration(n=1, units = "months")) %>% 
-  mutate(stagecat = na_if(stagecat, "Unk Stage")) %>% 
-  mutate(across(.cols = c(histology, groupstage, tstage), ~na_if(., "Unknown/not documented")))
-clinical_data
-```
-
-## Drugs
-
-Here is the fun`r emo::ji("face_screaming_in_fear")`!  
-The first cleanup step is to only keep the drugs which were administered to patients and removing the maintenance drugs, I also filtered "taxel" and "platin" drugs administered by "intravenous" or "peritoneal" route.
-Comments: Done like that I automatically remove the line with only
-main as 1 or sec
-<span style='color: red;'>Is that a problem?</span>
-
-I guess it is perfect for F71460509E771  
-Looks ok for F9E61D896E2FE FA550FA15524A  but please take a look just to make sure
-```{r}
-drugs %>% filter(str_detect(patientid, "F9E61D896E2FE|FA550FA15524A|F71460509E771"))
-```
-
-One thing I saw is that patients can have multiple records (rows) for the same drug (different amount for what I saw) on the same day.
-After out talk last time we decided to combined multiple amount of drug given the same day 
-FYI, I found that on the Flatiron website:
-
-*# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day.
-We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day.
-Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data.
-Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
-# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
-# Three administrations of the same drug were listed on a Friday.
-The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.
-# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.*
-
-It may be 205 patients row like that (over 145517 total rows). Example here:
-```{r}
-drugs %>% 
-  filter(episodedatasource == "Administrations" & ismaintenancetherapy == "FALSE" & !is.na(amount)) %>%
-  filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% 
-  select(-c(ismaintenancetherapy, enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
-  filter(str_detect(patientid, "FCF86329BB40C|F4E6EE1910940"))
-```
-
-In the `amount` variable I found `mg`, `ug`, `ml`, `Ea`, `AUC` and `NA`.
-They all look in the range but `AUC` which sometimes < 10 (someone probably enter the real AUC!) so I removed these ones and convert `ug` amount into `mg`.
-I also filtered out patients who had `issurgery` == "Yes" but no `surgerydate` associated (10 patients).
-```{r drugs1}
-drugs1 <- drugs %>% 
-  # 1. Filtering----
-  filter(episodedatasource == "Administrations" & ismaintenancetherapy == "FALSE" & !is.na(amount)) %>%
-  filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% 
-  select(-c(ismaintenancetherapy, enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
-  group_by(patientid, linename, linenumber, linestartdate, lineenddate,episodedate, drugname, units) %>%
-  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
-  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
-           fill = "right") %>%
-  purrr::keep(~!all(is.na(.))) %>%
-  ungroup() %>% 
-  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
-         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
-  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
-  # Found ug, ml, Ea, AUC and NA they are all good, but the AUC & < at 10 are wrong and ug need conversion
-  mutate(amount =  case_when(
-    units == "ug"               ~ amount / 10, # I checked all of them
-    units == "AUC" &
-      amount < 10               ~ NA_real_,
-    TRUE                        ~ amount
-  )) %>%
-
-  # 3.bind with clinical----
-  full_join(., clinical_data %>% select(-c(primaryphysicianid)),
-            by = "patientid") %>% 
-  # Limit to the patients we have date of surgery when had surgery
-  filter(!(issurgery == "Yes" & is.na(surgerydate)))
-```
-
-Then the `linenumber` coding starts!!
-
-Just to make sure when we talked, you said that we don't want to increase the line number when it is a change in drug. Example:
-```{r}
-drugs1 %>% filter(str_detect(patientid, "F9E61D896E2FE|FA550FA15524A|F71460509E771"))
-```
-
-1- Change linenumber when surgery
-I had to built the new_linenumber on top of the old one because of some patients who has a change of drug but are still line 1.
-```{r}
-drugs1 %>% 
-  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
-  mutate(chemotherapy_type = case_when(
-    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
-    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
-    episodedate > surgerydate         ~ "Adjuvant",
-    issurgery == "No/unknown" &
-      !is.na(episodedate)             ~ "Chemotherapy only",
-    issurgery == "Yes" &
-      is.na(episodedate)              ~ "Surgery only"
-    )) %>% 
-  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
-  group_by(patientid) %>% 
-  mutate(therapy = case_when(
-    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
-    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
-    chemotherapy_type == "Surgery only"          ~ "Surgery only"
-  )) %>% 
-  fill(therapy, .direction = "downup") %>% 
-  mutate(therapy1 = case_when(
-    chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
-  )) %>% 
-  fill(therapy1, .direction = "downup") %>% 
-  mutate(therapy = coalesce(therapy, therapy1)) %>% 
-  select( -therapy1) %>%
-
-  # 5.Redefine line number based on the original linenumber variable and the surgery date----
-  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>% 
-  select(patientid, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, linename)
-```
-
-Change of cyle/drugs (I don't think it happen often)
-F071D61E6FB93
-
-Change in cycle
-F1775A21CC4DB
-
-`r  emo::ji("party_popper")`
+##

### 2021-03-17 Rmd/Report cleaning.Rmd
New Rmd Flatiron analysis

@@
 ---
-title: "Flatiron data cleaning and analysis report"
+title: "Flatiron data cleaning report and questions"
 author: "Christelle Colin-Leitzinger"

### 2021-03-17 R/4.Analysis.R
Update gitignore and typo

@@ -528,14 +528,15 @@ tbl2 <- tbl_regression(model, exponentiate = TRUE)
 tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
 
 model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
-               filter(drugname == "carboplatin" & chemotherapy_type == "Neodjuvant") %>% 
+               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
                distinct(patientid, .keep_all = TRUE) %>% 
                filter(exclude != "1"), family = binomial)
 tbl1 <- tbl_regression(model)
 tbl2 <- tbl_regression(model, exponentiate = TRUE)
 tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
 
-tbl5 <- tbl_merge(list(tbl3, tbl4), tab_spanner = c("**Adjuvant**", "**Neodjuvant**"))
+# tbl5 <- 
+  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**Adjuvant**", "**Neoadjuvant**"))
 
 #  for taxel
 model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
@@ -547,14 +548,15 @@ tbl2 <- tbl_regression(model, exponentiate = TRUE)
 tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
 
 model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
-               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neodjuvant")) %>% 
+               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")) %>% 
                distinct(patientid, .keep_all = TRUE) %>% 
                filter(exclude != "1"), family = binomial)
 tbl1 <- tbl_regression(model)
 tbl2 <- tbl_regression(model, exponentiate = TRUE)
 tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
 
[…]

### 2021-03-17 Rmd/Report analysis 03172021.Rmd
Update Rmd analysis

@@
 <br>
+For all these analysis, I excluded the patients Lauren said to remove from the analysis.
 
@@
 
-##
+```{r}
+#################################################################################################### I ### Basic Clinical Cleaning----
+#################################################################################################### 1 ### Cleanup of creatinine----
+creatinine <- creatinine %>%
+  # remove creatine urine
+  filter(str_detect(labcomponent, "blood|serum")) %>% 
+  mutate(creatinine = case_when(
+    testresultcleaned < 0.8        ~ 0.8,
+    testresultcleaned > 3          ~ NA_real_,
+    TRUE                           ~ testresultcleaned
+  )) %>% 
+  # F092F8B827DDC kept umol/L as they actually are mg/dL range 45 to 90 μmol/L (0.5 to 1.0 mg/dL) for women.
+  mutate(creatinine1 = case_when(
+    testresult < 0.8               ~ 0.8,
+    testresult > 3                 ~ NA_real_,
+    TRUE                           ~ testresult
+  )) %>% 
+  mutate(creatinine = coalesce(creatinine, creatinine1)) %>% 
+  filter(!is.na(creatinine)) %>% 
+  mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
+  select(c("patientid", creat_date = "testdate", "creatinine", creat_units = "testunitscleaned"))
+
+# body_surface_area, height and weight are all coming from vitals
+vitals <- vitals %>% 
+  mutate(testdate = as.Date(testdate, format = "%m/%d/%y"))
+
+#################################################################################################### 2 ### Cleanup of BSA----
+body_surface_area <- vitals %>% 
+  filter(labcomponent == "Body Surface Area (BSA)") %>% # only 399 patients data
+  # Limit max = 4.14, min = 0.418 calculated for biggest to smallest person
+  mutate(testresult = ifelse(testresult < 0.418 | testresult > 4.14, NA_real_, testresult)) %>% 
+  group_by(patientid) %>%
+  # I used the median to remove outlier within a patient
+  mutate(median_testresult = median(testresult)) %>% 
+  ungroup() %>% 
+  mutate(BSA = case_when(
+    testresult > (median_testresult + 0.4) |
+      testresult < (median_testresult - 0.4)      ~ NA_real_,
+    TRUE                                          ~ testresult
+  )) %>% 
+  mutate(BSA = coalesce(testresultcleaned, BSA)) %>% 
+  filter(!is.na(BSA)) %>% 
+  mutate(BSA_units = "m2") %>% 
+  select(c("patientid", bsa_date = "testdate", "BSA", "BSA_units"))
+
+#################################################################################################### 3 ### Cleanup of Height----
+height <- vitals %>% 
+  filter(test == "body height") %>% 
+  # To get more data, I have data from testresult that can be used
+  # But need to fill up testunits, transfer in kg and coalesce.
+  group_by(patientid) %>% 
+  fill(testunits, .direction = "downup") %>% # F004D683A1695 have testresult, F615C37BF1470 is wrong, Otherwise I checked them all to see we can do that
+  ungroup() %>% 
+  # Clean up outliers compare to tallest ans smallest record
+  mutate(testresultcleaned = case_when(
+    testresultcleaned > 231 | # Tallest women height
+      testresultcleaned < 120 # Average height dwarf = 122 cm, 4 feet, I take 120 by loooking at the data
+                                     ~ NA_real_,
+    TRUE                             ~ testresultcleaned
+  )) %>% 
+  mutate(testresult = case_when(
+    testresult > 231 & testunits == "cm" |
+      testresult < 100 & testunits == "cm" |
+      testresult > 7.58 & testunits == "ft" |
+      testresult < 3.28 & testunits == "ft" |
+      testresult > 90.94 & testunits == "in" |
+      testresult < 39.37 & testunits == "in"|
+      testresult == 0
+                                     ~ NA_real_,
+    TRUE                             ~ testresult
+  )) %>% 
+  # Clean up outliers within patient by using the median for each patients/unit. Eliminate the ones with too much variation.
+  group_by(patientid) %>%
+  mutate(median_testresultcleaned = median(testresultcleaned)) %>% 
+  ungroup() %>% 
+  mutate(testresultcleaned_verified = case_when(
+    testresultcleaned > (median_testresultcleaned + 5) | # choose 5 cm by default
+      testresultcleaned < (median_testresultcleaned - 5)      ~ NA_real_, # F01413C06D921 weird
+    TRUE                                                      ~ testresultcleaned
+  )) %>% 
+  # select(c("patientid", testdate, testresultcleaned, median_testresultcleaned, testresultcleaned_verified, 
+  #          testunitscleaned, testunits, testresult)) %>%
+
+  group_by(patientid, testunits) %>%
+  mutate(median_testresult = median(testresult)) %>% 
+  ungroup() %>% 
+  mutate(testresult_verified = case_when(
+    testresult > (median_testresult + 3) & 
+      testunits == "in" |
+      testresult < (median_testresult - 3) & 
+      testunits == "in"                         ~ NA_real_,
+    testresult > (median_testresult + 5) & 
+      testunits == "cm" |
+      testresult < (median_testresult - 5) & 
+      testunits == "cm"                         ~ NA_real_,
+    TRUE                                        ~ testresult
+  )) %>% 
+  # select(c("patientid", testdate, testresult, median_testresult, testresult_verified,
+  #          testunits, testunitscleaned, testresultcleaned, testresultcleaned_verified))
+
+  mutate(height = case_when(
+    !is.na(testresultcleaned_verified)          ~ round(testresultcleaned_verified / 100, 3), # cm to m
+    testunits == "cm"                           ~ round(testresult_verified / 100, 3),
+    testunits == "ft"                           ~ round(testresult_verified / 3.281, 3), # ft to m
+    testunits == "in" | 
+      !is.na(testresult)                        ~ round(testresult_verified / 39.37, 3) # in to m
+    )) %>% 
+  filter(!is.na(height)) %>% 
+  mutate(height_units = "m") %>% 
+  select(c("patientid", height_date = "testdate", "height", "height_units"))
+
+#################################################################################################### 4 ### Cleanup of weight----
+weight <- vitals %>%
+  filter(test == "body weight") %>% 
+  select(c("patientid", "testdate", "testunits", "testresult", "testunitscleaned", "testresultcleaned")) %>%
+  # 1.Clean testresultcleaned
+  group_by(patientid) %>%
+  mutate(median_testresultcleaned = median(testresultcleaned, na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(weight1 = case_when(
+    testresultcleaned >= 27 &       # Biggest recorded 291.6 kg (642.9 lbs, 10286 oz)
+      testresultcleaned < 292 &     # lightest 5.5 kg (12 lbs, 194 oz)  F0027D3926C88
+      (testresultcleaned > (median_testresultcleaned - 39.6) & # F1493F8F5A924, F54F47F4419E0, F18E68D19D10F
+         testresultcleaned < (median_testresultcleaned + 39.6))     ~ testresultcleaned, 
+    TRUE ~ NA_real_
+  )) %>% 
+  # mutate(difference = (median_testresultcleaned)-testresultcleaned) # Can improve by > 30 and > 10 from previous measure so need to create a gap var ---------
+  # 2.Clean testresult to be used to find max and min
+  mutate(testresult = case_when(
+    testunits == "lb" &
+      testresult > 12 &
+      testresult < 643            ~ testresult,
+    testunits == "kg" &
+      testresult >= 5.5 &
+      testresult < 292            ~ testresult,
+    testunits == "oz" &
+      testresult > 194 &
+      testresult < 10286          ~ testresult,
+    is.na(testunits) & 
+    testresult > 5.5 & 
+      testresult < 10286          ~ testresult, # combine oz, kg, lbs for when units is NA
+    TRUE                          ~ NA_real_
+  ))
+
+# remove_outliers <- function(x, na.rm = TRUE, ...) { ##################### Too restrictive
+#   qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
+#   H <- 1 * IQR(x, na.rm = na.rm) # 1.5 remove non outliers
+#   y <- x
+#   y[x < (qnt[1] - H)] <- NA
+#   y[x > (qnt[2] + H)] <- NA
+#   y
+# }
+
+weight1 <- weight %>% 
+  # 3. Calculate median for each units and remove data outside range for each patients/unit
+  # 3. help distinguishing lbs to kg for same patient when unit is NA
+  group_by(patientid, testunits) %>%
+  mutate(median_testresult = median(testresult, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  mutate(testresult_verified = case_when(       # Can improve by > 30 and > 10 from previous measure so need to create a gap var --------
+    testunits == "kg" &
+    (testresult > (median_testresult + 38.5) | # choose 38.5 cm by default could do 32 if not for F534F9C4FF968
+       # 12 F2F31607FD6AD , FA7C8143AEE58 gain 37kg, F847A533FAE7E gain 38, FBE6E66AB2C95 gain 41, FC09E942CB0D7 gain 49
+       # F5B18C17A28F5 and F98077E9119EC FA53D0F672C7D FCFF0EDFE278F, FEF3273967DB3 wrong in cleaned too
+      testresult < (median_testresult - 38.5))         ~ NA_real_, 
+    testunits == "lb" &
+      (testresult > (median_testresult + 99) | # choose 99 cm by default, # Problem when wrong first value FCC755E4F8722 (94.8) keep in case close to first dosinf
+         testresult < (median_testresult - 99))      ~ NA_real_, # 91 for F00C16FEE3F74
+    TRUE                                             ~ testresult
+  )) %>%  # FCC755E4F8722 keep the first value anyway, eliminate that F8CB4CAB1073A (has 96 lbs difference-median) ?
+  # mutate(cal = testresult-median_testresult)
+  # mutate(difference = (median_testresultcleaned)-testresultcleaned)
+
+  # 4. Rescue testunits when testresult_verified is close 
+  # Calculate max and min to limit value for each patient-Choose 20
+  group_by(patientid, testunits) %>%
+  mutate(max_kg = case_when(
+    testunits == "kg" ~ max(testresult_verified, na.rm = TRUE) + 20 # F181950A26A19
+  )) %>%
+  mutate(min_kg = case_when(
+    testunits == "kg" ~ min(testresult_verified, na.rm = TRUE) - 20
+  )) %>%
+  mutate(max_lbs = case_when(
+    testunits == "lb" ~ max(testresult_verified, na.rm = TRUE) + 30 # F14EBD0D0FA81
+  )) %>%
+  mutate(min_lbs = case_when(
+    testunits == "lb" ~ min(testresult_verified, na.rm = TRUE) - 30
+  )) %>%
+  ungroup() %>% 
+  group_by(patientid) %>% 
+  fill(max_kg, min_kg, max_lbs, min_lbs, .direction = "downup") %>% # min_kg, max_lbs
+  ungroup() %>%
+
+  mutate(testunits_rescue = case_when(
+    is.na(testunits) &
+      testresult_verified < max_kg        ~ "kg", # Good doesn't work with F16847515CAF4 , Perfect for F8A3DD629CDA6
+    is.na(testunits) & # FE8DBCAC6DAFB
+      testresult_verified > min_lbs      ~ "lb" # F004D683A1695, F10CAD0F4EC48, FC109A6F719E7, FD25ED170CF07, FE06FF7C3E108, F044601199C5D
+  ))
+
+weight2 <- weight1 %>% 
+  group_by(patientid) %>% 
+  # 5. Rescue testunits when testresult_verified is twice or /2 means that lb or kg 
+  # if is 2 times the weight in kg add lb F14EBD0D0FA81
+  mutate(testunits_rescue1 = case_when(
+    is.na(testunits) &
+      testresult_verified < (max_kg * 2.205) &
+      testresult_verified > (min_kg * 2.205)         ~ "lb",
+    is.na(testunits) &
+      testresult_verified < (max_lbs / 2.205) &
+      testresult_verified > (min_lbs / 2.205)        ~ "kg"
+  )) %>% 
+  ungroup() %>% 
+  mutate(testunits = coalesce(testunits, testunits_rescue, testunits_rescue1)) %>% 
+  select(c("patientid", "testdate", "testunits", "testresult", "testresult_verified", "testunitscleaned", "testresultcleaned", "weight1"))
+
+weight <- weight2 %>% 
+  # 6.Fill up weight with new testresult_verified cleaned
+  mutate(weight2 = case_when(
+    is.na(testresultcleaned) &
+      testunits == "kg"         ~ testresult_verified, # F0027D3926C88, FE8DBCAC6DAFB, F8A3DD629CDA6, F020C6A8B9E50, F16847515CAF4
+    is.na(testresultcleaned) & # F044601199C5D
+      testunits == "lb"         ~ (testresult_verified / 2.205), # FCB918617347C, F5E3D88009911, F14EBD0D0FA81, F16847515CAF4, FABC474931881
+  )) %>% 
+  mutate(weight = coalesce(weight1, weight2)) %>% 
+  filter(!is.na(weight)) %>% 
+  mutate(weight_units = "kg") %>% 
+  select(c("patientid", weight_date = "testdate", "weight", "weight_units"))
+
+rm(weight1, weight2, vitals)
+
+#################################################################################################### 5 ### Cleanup of AUC----
+areaUC <- auc %>% 
+  filter(str_detect(drugname, "taxel|platin")) %>% 
+  filter(!is.na(relativeorderedamount)) %>% 
+  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
+  #          "relativeorderedunits", "drugname", iscanceled)) %>%
+  mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
+    # relativeorderedunits == "mg/kg" |
+    #   relativeorderedunits == "mg" |
+    #   relativeorderedunits == "m"         ~ NA_real_,
+    str_detect(drugname, "taxel") &
+      relativeorderedunits == "mg/m2" &
+      relativeorderedamount >= 50 &
+      relativeorderedamount <= 175        ~ relativeorderedamount, # F21904E0D872F we should open more? F11B625154B62
+    str_detect(drugname, "platin") &
+      relativeorderedunits == "AUC" &
+      relativeorderedamount >= 2 &
+      relativeorderedamount <= 6          ~ relativeorderedamount, # F4E8C8717878B, FE3FF3A5AC465, F853DC24CD5E8
+    TRUE                                  ~ NA_real_
+  )) %>%
+  select(c("patientid", auc_date = "expectedstartdate", "target_auc", 
+           auc_units = "relativeorderedunits", "drugname")) %>% 
+  filter(!is.na(target_auc))
+
+#################################################################################################### II ### Clinical Cleaning----
+clinical_data <- clinical_data %>% 
+  mutate(race = case_when(
+    str_detect(race, "Black")    ~ "Black",
+    str_detect(race, "Hispanic") ~ "White",
+    TRUE                         ~ race
+  )) %>% 
+  mutate(ethnicity = (str_remove(ethnicity, " or Latino"))) %>% 
+  unite(raceeth1, c(race,ethnicity), sep = " ", remove = FALSE, na.rm = TRUE) %>% 
+  mutate(vital = case_when(
+    vitalstatus == 0     ~ "Alive",
+    vitalstatus == 1     ~ "Dead"
+  )) %>% 
+  # mutate(aprox_month_at_os = followuptime/30.417) %>% 
+  mutate(month_at_os = interval(start = diagnosisdate, end = followupdate)/
+           duration(n=1, units = "months")) %>% 
+  mutate(stagecat = na_if(stagecat, "Unk Stage")) %>% 
+  mutate(across(.cols = c(histology, groupstage, tstage), ~na_if(., "Unknown/not documented")))
+
+  # mutate(raceeth = case_when(
+  #   str_detect(race, "NHBlack")  ~ "Non-Hispanic Black", # Black Hispanic are others?
+  #   str_detect(race, "Hispanic") ~ "Hispanic White",
+  #   str_detect(race, "NHWhite")  ~ "Non-Hispanic White",
+  #   TRUE                         ~ raceeth
+  # )) %>%
+
+# which(duplicated(drugs1))
+# a <- (unique(drugs1$patientid))
+
+#################################################################################################### II ### Treatment Cleaning----
+# considered maintenance therapy : bevacizumab , olaparib, rucaparib, niraparib, gemcitabine
+# Just use taxel and platin for now
+# Precleaning
+drugs1 <- drugs %>% 
+  # 1. Filtering----
+  filter(episodedatasource == "Administrations" & ismaintenancetherapy == "FALSE" & !is.na(amount)) %>%
+  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
+  filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% 
+  select(-c(ismaintenancetherapy, enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
+  # 2. Combined Multiple Administrations----
+  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
+# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day.
+We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day.
+Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data.
+Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
+# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
+# Three administrations of the same drug were listed on a Friday.
+The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.
+# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
+  group_by(patientid, linename, linenumber, linestartdate, lineenddate,episodedate, drugname, units) %>%
+  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
+  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
+           fill = "right") %>%
+  purrr::keep(~!all(is.na(.))) %>%
+  ungroup() %>% 
+  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
+         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
+  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
+  # Found ug, ml, Ea, AUC and NA they are all good, but the AUC & < at 10 are wrong and ug need conversion
+  mutate(amount =  case_when(
+    units == "ug"               ~ amount / 10, # I checked all of them
+    units == "AUC" &
+      amount < 10               ~ NA_real_,
+    TRUE                        ~ amount
+  )) %>%
+
+  # 3.bind with clinical----
+  full_join(., clinical_data %>% select(-c(primaryphysicianid)),
+            by = "patientid") %>% 
+  # Limit to the patients we have date of surgery when had surgery
+  filter(!(issurgery == "Yes" & is.na(surgerydate)))
+
+therapy <- drugs1 %>% 
+  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
+  mutate(chemotherapy_type = case_when(
+    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
+    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
+    episodedate > surgerydate         ~ "Adjuvant",
+    issurgery == "No/unknown" &
+      !is.na(episodedate)             ~ "Chemotherapy only",
+    issurgery == "Yes" &
+      is.na(episodedate)              ~ "Surgery only"
+    )) %>% 
+  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
+  group_by(patientid) %>% 
+  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
+  fill(had_neo, .direction = "updown") %>% 
+  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
+  fill(had_adj, .direction = "updown") %>% 
+  mutate(treatment_sequence = case_when(
+    had_neo == "Yes" &
+      had_adj == "Yes"                           ~ "neo + surg + adj",
+    had_neo == "Yes" &
+      is.na(had_adj)                             ~ "neo + surg",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "surg + adj",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only"
+  )) %>% 
+  mutate(therapy = case_when(
+    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "Upfront Surgery"
+  )) %>% 
+  fill(therapy, .direction = "downup") %>% 
+  # mutate(therapy1 = case_when(
+  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
+  # )) %>% 
+  # fill(therapy1, .direction = "downup") %>% 
+  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
+  # select( -therapy1) %>%
+
+  # 5.Redefine line number based on the original linenumber variable and the surgery date----
+  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird
+  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
+  ungroup() %>%
+
+  # 6.Add a 30 day rule to switch linenumber----
+  group_by(patientid, linenumber_new) %>% 
+  arrange(episodedate) %>% 
+  mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
+  mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
+  ungroup() %>% 
+  group_by(patientid) %>% 
+  mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
+  mutate(linenumber_new = linenumber_new + jump_line) %>% 
+  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37
+
+  # 7.Calculate cycle for each line----
+  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
+  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
+  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
+  ungroup()
+
+# plot mediacation as fromtline, pie?
+# Next bind the dose from orders to get AUC
+
+therapy1 <- therapy %>% 
+  select(-c("linenumber")) %>%
+  arrange(episodedate) %>% 
+  group_by(patientid, linenumber_new) %>%
+  mutate(cycle_count_perline = min(drugname_count_perline)) %>% 
+  mutate(cycle_drugname = case_when(
+    cycle_count_perline == drugname_count_perline          ~ drugname,
+    TRUE                                                   ~ NA_character_
+  )) %>% 
+  # select(-drugname_count_perline) %>% 
+  group_by(patientid, linenumber_new, cycle_drugname) %>%
+  mutate(cycle_inc = row_number(cycle_drugname)) %>%
+
+  # + What to do when it is a cycle change F003F2BEEDB37 ,
+
+  group_by(patientid, linenumber_new, cycle_inc) %>%
+  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
+  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>%  # Problem for F001443D8B85C (make a code before recoding linenumber_new like if drugname is not in the linename remove linename)
+  arrange(patientid, episodedate, cycle_inc) %>% 
+  group_by(patientid, linenumber_new) %>%
+  mutate(cycle_increment = cycle_inc) %>% 
+  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
+  # cycle date
+  group_by(patientid, linenumber_new, cycle_increment) %>% 
+  mutate(cycle_start_date = min(episodedate)) %>% 
+  # select(patientid, linename, linenumber_new, drugname, episodedate, episode_interval,
+  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>%
+
+  group_by(patientid, linenumber_new) %>% 
+  mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
+         cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
+
+  # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
+  mutate(n = row_number(drugname)) %>%
+
+  mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
+  fill(base_days_between_cycle, .direction = "downup") %>% 
+  mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
+                                       (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
+  # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
+  group_by(patientid, linenumber_new) %>%
+  mutate(drug_count_perline = n()) %>%
+  mutate(skipped_cycle_indays1 = ifelse(
+    (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
+  )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
+  # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
+  group_by(patientid) %>% 
+  mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
+  ungroup()
+
+rm(drugs, drugs1, therapy)
+
+#################################################################################################### III ### Merging----
+# For each feature, binding with the variable, calculate an interval between cycle date and feature dates, 
+# select the smallest interval
+Treatment <- 
+  # Merge with creatinine
+  left_join(therapy1, creatinine, by = "patientid") %>%
+  mutate(interval = abs(interval(start= creat_date, end= cycle_start_date)/                      
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Merge with height
+  left_join(. , height,  by = "patientid") %>%
+  mutate(interval = abs(interval(start= height_date, end= cycle_start_date)/                      
+           duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Merge with weight
+  left_join(. , weight, by = "patientid") %>%
+  mutate(interval = abs(interval(start= weight_date, end= cycle_start_date)/                      
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Calculate bmi
+  mutate(bmi = weight / (height * height)) %>% 
+  mutate(bmi_cat = case_when(
+    bmi < 25                    ~ "Underweight and normal weight",
+    bmi >= 25 &
+      bmi < 30                  ~ "Overweight",
+    bmi >= 30                   ~ "Obese"
+  )) %>% 
+  # Calculate CrCl
+  mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
+
+  # Merge with body_surface_area
+  left_join(., body_surface_area, by = "patientid") %>%
+  mutate(interval = abs(interval(start= bsa_date, end= cycle_start_date)/                      
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>% 
+  # Calculate more bsa value with height and weight using Du Bois formula
+  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
+  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>% 
+  select(-bsa_du_bois) %>%
+
+  # Merge with auc
+  left_join(., areaUC, by = c("patientid", "drugname")) %>%
+  mutate(interval = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>% 
+  select(-interval) %>%
+
+  # Calculate expected dose
+  mutate(expected_dose = case_when(
+    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
+    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
+    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
+  )) %>% 
+  mutate(expected_dose = case_when(
+    expected_dose > 900 &
+      target_auc == 6              ~ 900,
+    expected_dose > 750 &
+      target_auc == 5              ~ 750,
+    TRUE                           ~ expected_dose
+  )) %>% 
+  arrange(patientid, episodedate)
+
+# Treatment1 <- Treatment %>% 
+#   select(c(patientid, "linename", "drugname", "cycle_increment", "amount", "target_auc", "auc_units", "expected_dose"))
+
+# OrderedAmount and Quantity
+# In the MedicationOrder table, ordered quantities are represented differently depending on their source.
+For example, orders that are placed via e-prescribing and/or flowsheet typically have OrderedAmount populated with corresponding OrderedUnits, while other medications recorded in the patient’s history typically have Quantity populated.
+In the majority of cases, the Quantity variable is used for medications ordered from sources other than the flowsheet and are frequently oral medications.
+In a relatively small number of cases, all three variables may contain distinct information; for example, an order for tamoxifen might include 20 (OrderedAmount) mg (OrderedUnits) and 30 (Quantity) capsules.
+# OrderedAmount: Typically represents the dosage in mg
+# Quantity: Typically represents the quantity of drug ordered in tablets or capsules
+# RelativeOrderedAmount: Typically represents an order scaled to a patient’s size (for example, an order based on patient weight)
+# While these variables cannot be combined, business rules can be implemented to impute the blank fields (for example, assume the recommended dose or most common days supply).
+
+#################################################################################################### III ### Merging nand RDI----
+Frontline <- Treatment %>% 
+  # filter(therapy == "Upfront Chemo" | therapy == "Chemotherapy only") %>% 
+  mutate(relative_dose_intensity = round(amount/expected_dose, 3)) %>%
+  group_by(patientid, chemotherapy_type, drugname) %>% 
+  mutate(mean_rdi_per_drug = mean(relative_dose_intensity)) %>% 
+  ungroup() %>% 
+  mutate(RDI_grp = as.factor(findInterval(relative_dose_intensity, c(0.75, 0.85, 1, 1.5, 2) ))) %>% 
+  mutate(RDI_grp = factor(RDI_grp, 
+                          levels = c("0", "1","2","3", "4", "5"), 
+                          labels = c("0 < RDI < 0.75", "0.75 <= RDI < 0.85", "0.85 >= RDI < 1", "1 <= RDI < 1.5", 
+                                     "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
+  mutate(delay_incare_dx_to_treat = case_when(
+    str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
+      duration(n=1, units = "days")),
+    str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
+      duration(n=1, units = "days"))
+  ))
+
+```
+
+## Clinical summary table
+```{r}
+analysis_data <- Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  filter(exclude != "1")
+```
+<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
+```{r}
+analysis_data %>% 
+  select(c(race, raceeth, ethnicity, "vital",
+           agecat, "ageatdx",
+
+           "bmi", bmi_cat, "BSA",
+
+           "histology", "groupstage", "tstage", "stagecat",
+
+           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
+           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
+
+           "hrd_tissue", "gis_tissue")) %>% 
+  tbl_summary() %>% bold_labels()
+```
+
+<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
+```{r}
+analysis_data %>% 
+  select(c(race, raceeth, ethnicity, "vital",
+           agecat, "ageatdx",
+
+           "bmi", bmi_cat, "BSA",
+
+           "histology", "groupstage", "tstage", "stagecat",
+
+           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
+           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
+
+           "hrd_tissue", "gis_tissue")) %>% 
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
+```
+
+## Treatment summary table
+<span style="color:green">**Table 3 Summary treatment data by race**</span>
+
+```{r}
+tbl1 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+  filter(exclude != "1") %>% 
+  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
+           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
+           "chemotherapy_type", "therapy", "relative_dose_intensity", "RDI_grp")) %>% 
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
+tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+  filter(exclude != "1") %>% 
+  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
+           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
+           "chemotherapy_type", "therapy", "treatment_sequence", "relative_dose_intensity", "RDI_grp")) %>% 
+  tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p()
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
+```
+
+<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
+```{r}
+# Treatment & demo
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl3 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl4 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl5 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl6 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl3, tbl4, tbl5, tbl6))
+```
+
+## Survivals
+### OS by clinical
+
+<span style="color:green">**Survival plots**</span>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by race
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by histology
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ tstage, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+</div>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by brca1_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca1_germline
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca2_germline
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+</div>
+
+### OS by treatment
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by issurgery
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by extentofdebulking
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by residualdiseasestatus
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+</div>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by chemotherapy_type
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by chemo
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+</div>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by RDI_grp
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "platin")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by RDI_grp for taxel
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "taxel")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+</div>
+
+## HR
+<span style="color:green">**Table 5 HR**</span>
+
+```{r, echo=TRUE}
+model <- coxph(Surv(time = month_at_os, 
+                     event = vitalstatus)~RDI_grp, 
+                data = Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "taxel")) %>%
+                     distinct(patientid, .keep_all = TRUE))
+summary(model)
+```
+
+## Regression
+
+```{r include=TRUE}
+# Regression vital status prediction
+model <- glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# extentofdebulking + residualdiseasestatus +
+
+model <- glm(vitalstatus ~ 
+               histology + tstage + brca1_tumor + brca2_tumor + 
+             issurgery +
+             chemotherapy_type, 
+             data = analysis_data, family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# Regression RDI prediction
+model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline %>% 
+               distinct(patientid, .keep_all = TRUE) %>% 
+               filter(exclude != "1"), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+#  for carbo
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
+               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+               distinct(patientid, .keep_all = TRUE) %>% 
+               filter(exclude != "1"), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
+               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+               distinct(patientid, .keep_all = TRUE) %>% 
+               filter(exclude != "1"), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# tbl5 <- 
+  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**Adjuvant**", "**Neoadjuvant**"))
+
+#  for taxel
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
+               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")) %>% 
+               distinct(patientid, .keep_all = TRUE) %>% 
+               filter(exclude != "1"), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>% 
+               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")) %>% 
+               distinct(patientid, .keep_all = TRUE) %>% 
+               filter(exclude != "1"), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# tbl6 <- 
+  tbl_merge(list(tbl4, tbl3), tab_spanner = c("**Adjuvant**", "**Neoadjuvant**"))
+```
+
+## Extra plots linenumber 1
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+analysis_data %>%
+  filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= therapy))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+analysis_data %>% 
+    filter(linenumber_new == "1") %>% 
+  group_by(chemotherapy_type) %>% 
+  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
+  geom_bar(stat="identity")+
+  labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
+  theme_minimal()+
+  guides(fill = FALSE) +
+  coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+analysis_data %>% 
+  filter(linenumber_new == "1") %>% 
+  group_by(treatment_sequence) %>% 
+  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
+  geom_bar(stat="identity")+
+  labs(x = "", title = "The treatment_sequence") +
+  theme_minimal()+
+  guides(fill = FALSE) +
+  coord_flip()
+
+# analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+#   ggplot(aes(x= chemo))+
+#   geom_bar()+
+#   theme_minimal()+
+#   coord_flip()
+```
+</div>
+</div>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+# What are the RDI distribution for each type of chemo
+print("A quick summary for the RDI repartition")
+analysis_data2 <- analysis_data %>% filter(linenumber_new == "1")
+summary(analysis_data2$relative_dose_intensity)
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(exclude != "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  geom_boxplot()+
+  geom_jitter(shape=16)+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal()
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  # geom_boxplot()+
+  ylim(c(-.5, 3.5))+
+  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal() +
+  guides(color=FALSE)
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  geom_violin()+
+  ylim(c(-.5, 3.5))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+# What are the RDI distribution for each drug
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= drugname, y= relative_dose_intensity))+
+  geom_violin(aes(color=relative_dose_intensity<0.85))+
+  ylim(c(-.5, 5.5))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()+
+  coord_flip()
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp, fill = drugname))+
+  geom_bar()+
+  theme_minimal()+
+  coord_flip()
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp, fill = drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  coord_flip()
+```
+</div>
+</div>
+
+## Extra plots all line together
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+analysis_data %>%
+  filter(exclude != "1") %>% 
+  ggplot(aes(x= therapy))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>% 
+  filter(exclude != "1") %>% 
+  group_by(chemotherapy_type) %>% 
+  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
+  geom_bar(stat="identity")+
+  labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
+  theme_minimal()+
+  guides(fill = FALSE) +
+  coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>% 
+  filter(exclude != "1") %>% 
+  group_by(treatment_sequence) %>% 
+  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
+  geom_bar(stat="identity")+
+  labs(x = "", title = "The treatment_sequence") +
+  theme_minimal()+
+  guides(fill = FALSE) +
+  coord_flip()
+
+# analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+#   ggplot(aes(x= chemo))+
+#   geom_bar()+
+#   theme_minimal()+
+#   coord_flip()
+```
+</div>
+</div>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+# What are the RDI distribution for each type of chemo
+print("A quick summary for the RDI repartition")
+summary(analysis_data$relative_dose_intensity)
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(exclude != "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  geom_boxplot()+
+  geom_jitter(shape=16)+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(exclude != "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  # geom_boxplot()+
+  ylim(c(-.5, 3.5))+
+  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal() +
+  guides(color=FALSE)
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(exclude != "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  geom_violin()+
+  ylim(c(-.5, 3.5))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()
+```
+</div>
+</div>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+# What are the RDI distribution for each drug
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(exclude != "1") %>% 
+  ggplot(aes(x= drugname, y= relative_dose_intensity))+
+  geom_violin(aes(color=relative_dose_intensity<0.85))+
+  ylim(c(-.5, 5.5))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()+
+  coord_flip()
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(exclude != "1") %>% 
+  ggplot(aes(x= RDI_grp, fill = drugname))+
+  geom_bar()+
+  theme_minimal()+
+  coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  filter(exclude != "1") %>% 
+  ggplot(aes(x= RDI_grp, fill = drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  coord_flip()
+```
+</div>
+</div>

### 2021-03-19 R/2.data cleaning.R
Update code

@@ -487,6 +487,7 @@ Treatment <-
       bmi < 30                  ~ "Overweight",
     bmi >= 30                   ~ "Obese"
   )) %>% 
+  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>% 
   # Calculate CrCl
   mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
   
@@ -541,19 +542,34 @@ Frontline <- Treatment %>%
   # filter(therapy == "Upfront Chemo" | therapy == "Chemotherapy only") %>% 
   mutate(relative_dose_intensity = round(amount/expected_dose, 3)) %>%
   group_by(patientid, chemotherapy_type, drugname) %>% 
-  mutate(mean_rdi_per_drug = mean(relative_dose_intensity)) %>% 
+  mutate(mean_RDI_per_drug_chemotype = mean(relative_dose_intensity)) %>% 
   ungroup() %>% 
-  mutate(RDI_grp = as.factor(findInterval(relative_dose_intensity, c(0.75, 0.85, 1, 1.5, 2) ))) %>% 
+  mutate(RDI_grp = as.factor(findInterval(mean_RDI_per_drug_chemotype, c(0.85) ))) %>% 
   mutate(RDI_grp = factor(RDI_grp, 
-                          levels = c("0", "1","2","3", "4", "5"), 
-                          labels = c("0 < RDI < 0.75", "0.75 <= RDI < 0.85", "0.85 >= RDI < 1", "1 <= RDI < 1.5", 
+                           levels = c("1", "0"), 
+                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
+  mutate(RDI_grp1 = as.factor(findInterval(mean_RDI_per_drug_chemotype, c(0.75, 0.85, 1, 1.5, 2) ))) %>% 
+  mutate(RDI_grp1 = factor(RDI_grp1, 
+                          levels = c("3", "0", "1","2","4", "5"), 
+                          labels = c("0.85 >= RDI < 1", "0 < RDI < 0.75", "0.75 <= RDI < 0.85", "1 <= RDI < 1.5", 
                                      "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
   mutate(delay_incare_dx_to_treat = case_when(
     str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
       duration(n=1, units = "days")),
[…]

### 2021-03-19 R/3.clinical mining.R

@@ -1,6 +1,6 @@
 Frontline <- read_rds("Frontline.rds")
 analysis_data <- Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
+  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
   filter(exclude != "1")
 #################################################################################################### I ### Clinical Mining
 analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 

### 2021-03-19 Rmd/Report analysis 03172021.Rmd
Finished Rmd prelim results

--- 2021-03-17 Rmd/Report analysis 03172021.Rmd
@@
 author: "Christelle Colin-Leitzinger"
-date: "3/17/2021"
+date: 'r Sys.Date()`'
 output: 
@@
    margin-top: 25px;
-   <!-- margin-bottom: 100px; -->
+   margin-bottom: 100px;
 }
@@
 table {
-    margin-top: 25px;
-    <!-- margin-bottom: 100px !important; -->
+    margin-top: 1px;
+    margin-bottom: 25px;
 }
@@
 loadd(clinical_data, vitals, drugs, auc, creatinine)
+Frontline <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/Frontline.rds")
 ```
 
-##
+## Clinical summary table
+```{r analysis_data}
+analysis_data <- Frontline %>% 
+  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
+  filter(exclude != "1")
+```
+
+<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
+```{r Table 1}
+analysis_data %>% 
+  select(c(race, raceeth, ethnicity, "vital",
+           agecat, "ageatdx",
+
+           "bmi", bmi_cat, "BSA",
+
+           "histology", "groupstage", "tstage", "stagecat",
+
+           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
+           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
+
+           "hrd_tissue", "gis_tissue")) %>% 
+  tbl_summary() %>% bold_labels()
+```
+
+<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
+```{r Table 2}
+analysis_data %>% 
+  select(c(race, raceeth, ethnicity, "vital",
+           agecat, "ageatdx",
+
+           "bmi", bmi_cat, "BSA",
+
+           "histology", "groupstage", "tstage", "stagecat",
+
+           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
+           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
+
+           "hrd_tissue", "gis_tissue")) %>% 
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
+```
+<br>
+
+## Treatment summary table
+<span style="color:green">**Table 3 Summary treatment data by race**</span>
+
+```{r Table 3}
+tbl1 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+  filter(exclude != "1") %>% 
+  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
+           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
+           "chemotherapy_type", "therapy", "mean_RDI_per_drug_chemotype", "RDI_grp")) %>% 
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
+tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+  filter(exclude != "1") %>% 
+  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
+           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
+           "chemotherapy_type", "therapy", "treatment_sequence", "mean_RDI_per_drug_chemotype", "RDI_grp")) %>% 
+  tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p()
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
+```
+
+<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
+
+```{r Table 4}
+# Treatment & demo
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl3 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl4 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl5 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl6 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl3, tbl4, tbl5, tbl6))
+```
+<br>
+
+## Survivals
+### OS by clinical
+
+<span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the left**</span>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by race
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by histology
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ tstage, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca1_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by race
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by histology
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ histology, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ tstage, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca1_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+</div>
+
+<br>
+
+### OS by treatment
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by extentofdebulking
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by residualdiseasestatus
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by chemotherapy_type
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by treatment_sequence
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by RDI_grp
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "platin")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by RDI_grp for taxel
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "taxel")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by extentofdebulking
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by residualdiseasestatus
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by chemotherapy_type
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by treatment_sequence
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by RDI_grp
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "platin")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by RDI_grp for taxel
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "taxel")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+```
+</div>
+</div>
+
+<br>
+
+## Hazard Ratio
+
+<span style="color:green">**Table 5 HR**</span>  
+`coxph(Surv(time = month_at_os, event = vitalstatus)~variables`
+```{r}
+# tbl1 <- analysis_data %>% 
+#   select(bmi_cat) %>% 
+#   tbl_summary(#by = vitalstatus,
+#               statistic = all_categorical() ~ "{analysis_data %>% filter(vital == 'Dead') %>% NROW()} death ({n})"
+#               )
+# tbl2 <- coxph(Surv(time = month_at_os,
+#                      event = vitalstatus)~bmi_cat,
+#                 data = analysis_data) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# 
+# tbl_merge(list(tbl1, tbl2))
+# 
+# coxph(Surv(time = month_at_os, 
+#                      event = vitalstatus)~RDI_grp, 
+#                 data = analysis_data) %>% 
+#   tbl_uvregression(y = vitalstatus, exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
+analysis_data %>% select(vitalstatus, bmi, bmi_cat, raceeth) %>% 
+tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = analysis_data$month_at_os, event = analysis_data$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
+  bold_labels() %>% italicize_levels() #%>%  modify_spanning_header(all_stat_cols() ~ "**Treatment Received**")
+
+tbl1 <- analysis_data %>% 
+  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+tbl1 <- tbl1 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl2 <- analysis_data %>% 
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
+tbl2 <- tbl2 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl3 <- analysis_data %>% 
+  filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
+tbl3 <- tbl3 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>% 
+  bold_labels() %>%
+  italicize_levels()
+# Platin
+tbl4 <- analysis_data %>% 
+  filter(str_detect(drugname,"platin") & chemotherapy_type == "Neoadjuvant")
+tbl4 <- tbl4 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl5 <- analysis_data %>% 
+  filter(str_detect(drugname,"platin") & chemotherapy_type == "Adjuvant")
+tbl5 <- tbl5 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl6 <- analysis_data %>% 
+  filter(str_detect(drugname,"platin") & str_detect(chemotherapy_type, "Chemo"))
+tbl6 <- tbl6 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl4, tbl5, tbl6),
+          group_header = c("platin/Neoadjuvant", "platin/Adjuvant", "platin/Chemo only")) %>% 
+  bold_labels() %>%
+  italicize_levels()
+
+tbl7 <- analysis_data %>% 
+  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Neoadjuvant")
+tbl7 <- tbl7 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl8 <- analysis_data %>% 
+  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Adjuvant")
+tbl8 <- tbl8 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
+  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+tbl9 <- analysis_data %>% 
+  filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
+tbl9 <- tbl9 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl7, tbl8, tbl9),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant", "paclitaxel/Chemo only")) %>% 
+  bold_labels() %>%
+  italicize_levels()
+
+tbl10 <- analysis_data %>% 
+  filter(str_detect(drugname, "paclitaxel") & chemotherapy_type == "Neoadjuvant")
+tbl10 <- tbl10 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl11 <- analysis_data %>% 
+  filter(str_detect(drugname, "paclitaxel") & chemotherapy_type == "Adjuvant")
+tbl11 <- tbl11 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
+  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+tbl12 <- analysis_data %>% 
+  filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
+tbl12 <- tbl12 %>% 
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl10, tbl11, tbl12),
+          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>% 
+  bold_labels() %>%
+  italicize_levels()
+```
+
+## Regression
+### By clinical, demo
+`glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)`
+```{r}
+# Regression vital status prediction
+model <- glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+```
+
+`glm(vitalstatus ~ histology + tstage + brca1_tumor + brca2_tumor + issurgery + chemotherapy_type, data = analysis_data, family = binomial)`
+```{r}
+model <- glm(vitalstatus ~ 
+               histology + tstage + brca1_tumor + brca2_tumor + 
+             issurgery +
+             chemotherapy_type, 
+             data = analysis_data, family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+```
+
+`glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)`
+```{r}
+# Regression RDI prediction
+model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+```
+
+### By drug
+```{r}
+#  for carbo
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# tbl5 <- 
+  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
+
+#  for taxel
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# tbl6 <- 
+  tbl_merge(list(tbl4, tbl3), tab_spanner = c("**taxel/Adjuvant**", "**taxel/Neoadjuvant**"))
+```
+
+## Plots for first treatment
+For RDI, it is calculated for neoadjuvant and adjuvant when a patient got both.
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+analysis_data %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= therapy))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+# analysis_data %>% 
+#   arrange(episodedate) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   group_by(chemotherapy_type) %>% 
+#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
+#   geom_bar(stat="identity")+
+#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
+#   theme_minimal()+
+#   guides(fill = FALSE) +
+#   coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  group_by(treatment_sequence) %>% 
+  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
+  geom_bar(stat="identity")+
+  labs(x = "", title = "The treatment_sequence") +
+  theme_minimal()+
+  guides(fill = FALSE) +
+  coord_flip()
+
+# analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+#   ggplot(aes(x= chemo))+
+#   geom_bar()+
+#   theme_minimal()+
+#   coord_flip()
+```
+</div>
+</div>
+
+A quick summary for the RDI repartition
+```{r}
+analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
+summary(analysis_data2$mean_RDI_per_drug_chemotype)
+```
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
+  geom_boxplot()+
+  ylim(c(-.25, 3.5))+
+  geom_jitter(shape=16)+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
+  geom_violin()+
+  ylim(c(-.25, 3.5))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  theme_minimal()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
+  geom_violin()+
+  ylim(c(-.25, 3.5))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  theme_minimal()+
+  coord_flip()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp, fill = drugname))+
+  geom_bar()+
+  theme_minimal()+
+  coord_flip()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp1, fill = drugname))+
+  geom_bar()+
+  theme_minimal()+
+  coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
+  # geom_boxplot()+
+  ylim(c(-.25, 3.5))+
+  geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal() +
+  guides(color=FALSE)
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, color = mean_RDI_per_drug_chemotype<0.85))+
+  geom_violin()+
+  ylim(c(-.25, 2.5))+
+  scale_colour_discrete(name=NULL, labels=c("<0.85",">=0.85"))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  theme_minimal()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
+  geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  ylim(c(-.25, 2.5))+
+  scale_colour_discrete(name=NULL, labels=c("<0.85",">=0.85"))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  theme_minimal()+
+  coord_flip()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp, fill = drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  coord_flip()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp1, fill = drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  coord_flip()
+```
+</div>
+</div>
+
+<!-- ## Extra plots all line together -->
+
+<!-- <div class = "row"> -->
+<!-- <div class = "col-md-6"> -->
+<!-- ```{r} -->
+<!-- analysis_data %>% -->
+<!--   filter(exclude != "1") %>%  -->
+<!--   ggplot(aes(x= therapy))+ -->
+<!--   geom_bar()+ -->
+<!--   theme_minimal()+ -->
+<!--   labs(title = "Frontline treatment")+ -->
+<!--   coord_flip() -->
+
+<!-- analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>%  -->
+<!--   filter(exclude != "1") %>%  -->
+<!--   group_by(chemotherapy_type) %>%  -->
+<!--   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>% -->
+<!--   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+ -->
+<!--   geom_bar(stat="identity")+ -->
+<!--   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") + -->
+<!--   theme_minimal()+ -->
+<!--   guides(fill = FALSE) + -->
+<!--   coord_flip() -->
+<!-- ``` -->
+<!-- </div> -->
+
+<!-- <div class = "col-md-6"> -->
+<!-- ```{r} -->
+<!-- analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>%  -->
+<!--   filter(exclude != "1") %>%  -->
+<!--   group_by(treatment_sequence) %>%  -->
+<!--   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>% -->
+<!--   ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+ -->
+<!--   geom_bar(stat="identity")+ -->
+<!--   labs(x = "", title = "The treatment_sequence") + -->
+<!--   theme_minimal()+ -->
+<!--   guides(fill = FALSE) + -->
+<!--   coord_flip() -->
+
+<!-- # analysis_data %>% distinct(patientid, .keep_all = TRUE) %>%  -->
+<!-- #   ggplot(aes(x= chemo))+ -->
+<!-- #   geom_bar()+ -->
+<!-- #   theme_minimal()+ -->
+<!-- #   coord_flip() -->
+<!-- ``` -->
+<!-- </div> -->
+<!-- </div> -->
+
+<!-- <div class = "row"> -->
+<!-- <div class = "col-md-6"> -->
+<!-- ```{r} -->
+<!-- # What are the RDI distribution for each type of chemo -->
+<!-- print("A quick summary for the RDI repartition") -->
+<!-- summary(analysis_data$mean_RDI_per_drug_chemotype) -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
+<!--   filter(exclude != "1") %>%  -->
+<!--   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+ -->
+<!--   geom_boxplot()+ -->
+<!--   geom_jitter(shape=16)+ -->
+<!--   labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") + -->
+<!--   theme_minimal() -->
+<!-- ``` -->
+<!-- </div> -->
+
+<!-- <div class = "col-md-6"> -->
+<!-- ```{r} -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
+<!--   filter(exclude != "1") %>%  -->
+<!--   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+ -->
+<!--   # geom_boxplot()+ -->
+<!--   ylim(c(-.5, 3.5))+ -->
+<!--   geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+ -->
+<!--   labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") + -->
+<!--   theme_minimal() + -->
+<!--   guides(color=FALSE) -->
+
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
+<!--   filter(exclude != "1") %>%  -->
+<!--   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+ -->
+<!--   geom_violin()+ -->
+<!--   ylim(c(-.5, 3.5))+ -->
+<!--   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+ -->
+<!--   theme_minimal() -->
+<!-- ``` -->
+<!-- </div> -->
+<!-- </div> -->
+
+<!-- <div class = "row"> -->
+<!-- <div class = "col-md-6"> -->
+<!-- ```{r} -->
+<!-- # What are the RDI distribution for each drug -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
+<!--   filter(exclude != "1") %>%  -->
+<!--   ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+ -->
+<!--   geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+ -->
+<!--   ylim(c(-.5, 5.5))+ -->
+<!--   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+ -->
+<!--   theme_minimal()+ -->
+<!--   coord_flip() -->
+
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
+<!--   filter(exclude != "1") %>%  -->
+<!--   ggplot(aes(x= RDI_grp, fill = drugname))+ -->
+<!--   geom_bar()+ -->
+<!--   theme_minimal()+ -->
+<!--   coord_flip() -->
+<!-- ``` -->
+<!-- </div> -->
+
+<!-- <div class = "col-md-6"> -->
+<!-- ```{r} -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
+<!--   filter(exclude != "1") %>%  -->
+<!--   ggplot(aes(x= RDI_grp, fill = drugname))+ -->
+<!--   geom_bar(position = "fill")+ -->
+<!--   theme_minimal()+ -->
+<!--   coord_flip() -->
+<!-- ``` -->
+<!-- </div> -->
+<!-- </div> -->

### 2021-03-24 R/2.data cleaning.R
update and finish creatinine and bsa

@@ -5,7 +5,7 @@ creatinine <- creatinine %>%
   filter(str_detect(labcomponent, "blood|serum")) %>% 
   mutate(creatinine = case_when(
     testresultcleaned < 0.8        ~ 0.8,
-    testresultcleaned > 3          ~ NA_real_,
+    testresultcleaned > 3          ~ NA_real_, # F006DBE0C7A5E is an example of slow increase past 3, F641A8DC820C7 super high
     TRUE                           ~ testresultcleaned
   )) %>% 
   # F092F8B827DDC kept umol/L as they actually are mg/dL range 45 to 90 μmol/L (0.5 to 1.0 mg/dL) for women.
@@ -21,7 +21,8 @@ creatinine <- creatinine %>%
 
 # body_surface_area, height and weight are all coming from vitals
 vitals <- vitals %>% 
-  mutate(testdate = as.Date(testdate, format = "%m/%d/%y"))
+  mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
+  select(-c(loinc, test, testbasename))
 
 
 #################################################################################################### 2 ### Cleanup of BSA----
@@ -35,10 +36,11 @@ body_surface_area <- vitals %>%
   ungroup() %>% 
   mutate(BSA = case_when(
     testresult > (median_testresult + 0.4) |
-      testresult < (median_testresult - 0.4)      ~ NA_real_,
+      testresult < (median_testresult - 0.4)      ~ NA_real_, # Checked all the removed 0.3 would be bad
     TRUE                                          ~ testresult
   )) %>% 
   mutate(BSA = coalesce(testresultcleaned, BSA)) %>% 
+  # mutate(resultdate = as.POSIXct(resultdate, format = "%m/%d/%y"))
   filter(!is.na(BSA)) %>% 
   mutate(BSA_units = "m2") %>% 
   select(c("patientid", bsa_date = "testdate", "BSA", "BSA_units"))

### 2021-03-24 R/2.data cleaning.R
Start re-check height cleaning

@@ -22,7 +22,7 @@ creatinine <- creatinine %>%
 # body_surface_area, height and weight are all coming from vitals
 vitals <- vitals %>% 
   mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
-  select(-c(loinc, test, testbasename))
+  select(-c(loinc, test, testbasename, resultdate))
 
 
 #################################################################################################### 2 ### Cleanup of BSA----
@@ -48,31 +48,38 @@ body_surface_area <- vitals %>%
 
 #################################################################################################### 3 ### Cleanup of Height----
 height <- vitals %>% 
-  filter(test == "body height") %>% 
-  # To get more data, I have data from testresult that can be used
-  # But need to fill up testunits, transfer in kg and coalesce.
-  group_by(patientid) %>% 
-  fill(testunits, .direction = "downup") %>% # F004D683A1695 have testresult, F615C37BF1470 is wrong, Otherwise I checked them all to see we can do that
-  ungroup() %>% 
-  # Clean up outliers compare to tallest ans smallest record
+  select(-c(minnorm, minnormcleaned, maxnorm, maxnormcleaned)) %>% 
+  filter(labcomponent == "Body Height") %>% 
+  # 1. Clean up outliers compare to tallest ans smallest record
+  # testresultcleaned has all testunitscleaned associated with value
   mutate(testresultcleaned = case_when(
     testresultcleaned > 231 | # Tallest women height
-      testresultcleaned < 120 # Average height dwarf = 122 cm, 4 feet, I take 120 by loooking at the data
+      testresultcleaned < 120 # Average height dwarf = 122 cm, 4 feet, I take 120 by looking at the data
                                      ~ NA_real_,
     TRUE                             ~ testresultcleaned
   )) %>% 
+  
+  # To get more data, I have data from testresult that can be used
+  # also have missing testunits F004D683A1695 
+  # fill up testunits within patients before removing outliers           then transfer in kg and coalesce with testresultcleaned.
+  group_by(patientid) %>% 
+  fill(testunits, .direction = "downup") %>% 
+  ungroup() %>% 
+  # Even if mistake was added FAAAACDA1754E it will be removed in the next step
   mutate(testresult = case_when(
-    testresult > 231 & testunits == "cm" |
+    testresult > 231 & testunits == "cm" | 
       testresult < 100 & testunits == "cm" |
       testresult > 7.58 & testunits == "ft" |
       testresult < 3.28 & testunits == "ft" |
[…]

### 2021-03-25 R/2.data cleaning.R
Increase the variation for height to accept

@@ -81,31 +81,31 @@ height <- vitals %>%
   
   # 2. Clean up outliers within patient by using the median for each patients/unit. Eliminate the ones with too much variation.
   group_by(patientid) %>%
-  mutate(median_testresultcleaned = median(testresultcleaned)) %>% 
-  ungroup() %>% 
+  mutate(mean_testresultcleaned = mean(testresultcleaned)) %>% # FEBB819DF1D8F, FCC755E4F8722 - 12, F45BCB24511B8 - 25, F02BBE6E30D4A
+  ungroup() %>% # F5B1E2D059869?????? F5B1E2D059869 , keep FAC12EC567E3E = 50 FF683865721AE
   mutate(testresultcleaned_verified = case_when(
-    testresultcleaned > (median_testresultcleaned + 5) | # choose 5 cm by default
-      testresultcleaned < (median_testresultcleaned - 5)      ~ NA_real_, # F01413C06D921 weird
+    testresultcleaned > (mean_testresultcleaned + 23.1) | # choose 5 cm by default
+      testresultcleaned < (mean_testresultcleaned - 23.1)      ~ NA_real_, # F01413C06D921 weird F355C8B80BFE9 50% height 124 50% 144cm
     TRUE                                                      ~ testresultcleaned
   )) %>% 
-  # select(c("patientid", testdate, testresultcleaned, median_testresultcleaned, testresultcleaned_verified, 
+  # select(c("patientid", testdate, testresultcleaned, mean_testresultcleaned, testresultcleaned_verified, 
   #          testunitscleaned, testunits, testresult)) %>% 
   
   group_by(patientid, testunits) %>%
-  mutate(median_testresult = median(testresult)) %>% 
+  mutate(mean_testresult = mean(testresult)) %>% 
   ungroup() %>% 
   mutate(testresult_verified = case_when(
-    testresult > (median_testresult + 3) & 
+    testresult > (mean_testresult + 10) & 
       testunits == "in" |
-      testresult < (median_testresult - 3) & 
-      testunits == "in"                         ~ NA_real_,
-    testresult > (median_testresult + 5) & 
+      testresult < (mean_testresult - 10) & 
+      testunits == "in"                         ~ NA_real_, # F5B1E2D059869 = 10 keep FAC12EC567E3E FF683865721AE
+    testresult > (mean_testresult + 10) & 
       testunits == "cm" |
-      testresult < (median_testresult - 5) & 
[…]

### 2021-03-25 R/2.data cleaning.R
Update clinical and frontline

@@ -271,10 +271,20 @@ clinical_data <- clinical_data %>%
   mutate(race = case_when(
     str_detect(race, "Black")    ~ "Black",
     str_detect(race, "Hispanic") ~ "White",
+    str_detect(race, "Other")    ~ "Other",
     TRUE                         ~ race
   )) %>% 
   mutate(ethnicity = (str_remove(ethnicity, " or Latino"))) %>% 
-  unite(raceeth1, c(race,ethnicity), sep = " ", remove = FALSE, na.rm = TRUE) %>% 
+  mutate(new_eth = case_when(
+    is.na(ethnicity) &
+      is.na(race)              ~ "Other or Uk",
+    is.na(ethnicity) &
+      !is.na(race)             ~ "NH",
+    ethnicity == "Hispanic"    ~ "Hispanic"
+  )) %>% 
+  unite(new_raceeth, c(new_eth, race), sep = " ", remove = FALSE, na.rm = TRUE) %>% 
+  mutate(new_raceeth1 = ifelse(str_detect(new_raceeth, "Black|Hispanic"), "Minority", new_raceeth)) %>%  # min = Asian Hisp
+  
   mutate(vital = case_when(
     vitalstatus == 0     ~ "Alive",
     vitalstatus == 1     ~ "Dead"
@@ -285,17 +295,12 @@ clinical_data <- clinical_data %>%
   mutate(stagecat = na_if(stagecat, "Unk Stage")) %>% 
   mutate(across(.cols = c(histology, groupstage, tstage), ~na_if(., "Unknown/not documented")))
 
+# ? Where does Asian Hispanic go, Black hispanic, NA race and H eth?
+# Sweta said to remove Asian but what for Hispanic Asian?
+# a <- clinical_data %>% select(patientid, raceeth, race, ethnicity, new_eth, new_raceeth, new_raceeth1)
 
-  # mutate(raceeth = case_when(
-  #   str_detect(race, "NHBlack")  ~ "Non-Hispanic Black", # Black Hispanic are others?
-  #   str_detect(race, "Hispanic") ~ "Hispanic White",
-  #   str_detect(race, "NHWhite")  ~ "Non-Hispanic White",
-  #   TRUE                         ~ raceeth
-  # )) %>% 
-  
 
-# which(duplicated(drugs1))
-# a <- (unique(drugs1$patientid))
+
 
 #################################################################################################### II ### Treatment Cleaning----
 # considered maintenance therapy : bevacizumab , olaparib, rucaparib, niraparib, gemcitabine
[…]

### 2021-03-25 Rmd/Report analysis update.Rmd
New analysis report

--- 2021-03-19 Rmd/Report analysis 03172021.Rmd
@@
 analysis_data <- Frontline %>% 
-  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
+  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
   filter(exclude != "1")
@@
            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
-           "chemotherapy_type", "therapy", "mean_RDI_per_drug_chemotype", "RDI_grp")) %>% 
+           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
+           )) %>% 
   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
@@
            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
-           "chemotherapy_type", "therapy", "treatment_sequence", "mean_RDI_per_drug_chemotype", "RDI_grp")) %>% 
+           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
+           )) %>% 
   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p()
@@
 
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl5 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_p()
+tbl6 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl4, tbl3, tbl5, tbl6))
+
 tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
@@
 
-tbl_stack(list(tbl3, tbl4, tbl5, tbl6))
+tbl_stack(list(tbl5, tbl6))
 ```
@@
 # OS by race
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 
-# OS by brca2_tumor
+# OS by brca_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca1_g
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
@@
 
-# OS by brca2_tumor
+# OS by brca2_g
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca_g
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by race
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 
-# OS by brca2_tumor
+# OS by brca_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+# OS by brca1_g
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
@@
 
-# OS by brca2_tumor
+# OS by brca2_g
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 2))
+
+# OS by brca_g
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
   italicize_levels()
-# Platin
+# Cisplatin
 tbl4 <- analysis_data %>% 
-  filter(str_detect(drugname,"platin") & chemotherapy_type == "Neoadjuvant")
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
 tbl4 <- tbl4 %>% 
@@
 tbl5 <- analysis_data %>% 
-  filter(str_detect(drugname,"platin") & chemotherapy_type == "Adjuvant")
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
 tbl5 <- tbl5 %>% 
@@
 tbl6 <- analysis_data %>% 
-  filter(str_detect(drugname,"platin") & str_detect(chemotherapy_type, "Chemo"))
+  filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
 tbl6 <- tbl6 %>% 
@@
 tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("platin/Neoadjuvant", "platin/Adjuvant", "platin/Chemo only")) %>% 
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant", "cisplatin/Chemo only")) %>% 
   bold_labels() %>%
@@
 tbl10 <- analysis_data %>% 
-  filter(str_detect(drugname, "paclitaxel") & chemotherapy_type == "Neoadjuvant")
+  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
 tbl10 <- tbl10 %>% 
@@
 tbl11 <- analysis_data %>% 
-  filter(str_detect(drugname, "paclitaxel") & chemotherapy_type == "Adjuvant")
+  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
 tbl11 <- tbl11 %>% 
@@
 `glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)`
+!!!! Prediction of RDI all drug together!!!!
 ```{r}
@@
 ### By drug
+!!! But sometimes we had a switch between cisplatin/carboplatin
 ```{r}
@@
 
+#  for Cisplatim
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+               filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+               filter(drugname == "cisplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
+tbl1 <- tbl_regression(model)
+tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# tbl5 <- 
+  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
+
 #  for taxel
@@
 analysis_data %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
+  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
   ggplot(aes(x= therapy))+
@@
 
-A quick summary for the RDI repartition
-```{r}
-analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
-summary(analysis_data2$mean_RDI_per_drug_chemotype)
-```
-
 <div class = "row">
@@
 
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= RDI_grp1, fill = drugname))+
-  geom_bar()+
-  theme_minimal()+
-  coord_flip()
 ```
@@
 
+```
+</div>
+</div>
+
+A quick summary for the RDI repartition
+```{r}
+analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
+summary(analysis_data2$mean_RDI_per_drug_chemotype)
+```
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp1, fill = drugname))+
+  geom_bar()+
+  theme_minimal()+
+  coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
 analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
@@
 </div>
+
+<!-- <div class = "row"> -->
+<!-- <div class = "col-md-6"> -->
+<!-- ```{r} -->
+
+<!-- ``` -->
+<!-- </div> -->
+
+<!-- <div class = "col-md-6"> -->
+<!-- ```{r} -->
+
+<!-- ``` -->
+<!-- </div> -->
+<!-- </div> -->
 

### 2021-04-01 Rmd/Report analysis update.Rmd
Analysis report

@@
 author: "Christelle Colin-Leitzinger"
-date: 'r Sys.Date()`'
+date: '`r Sys.Date()`'
 output: 
@@
     df_print: paged
+editor_options: 
+  chunk_output_type: console
 ---
@@
 ```
-
-# Analysis
+<br>
+
 ***
-<br>
+# Analysis Clinical
+
 For all these analysis, I excluded the patients Lauren said to remove from the analysis.
@@
            "hrd_tissue", "gis_tissue")) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
 ```
@@
 
+## Plots for first treatment
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= bmi_cat))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "BMI category")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= histology))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Histology")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= stagecat))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Stage")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= agecat))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Age cat")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= brca_germline))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "BRCA gernline")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= brca_tumor))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "BRCA tumor")+
+  coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill = bmi_cat))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "BMI category")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= histology, fill = raceeth))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "Histology")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= stagecat, fill = raceeth))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "Stage")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= agecat, fill = raceeth))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "Age cat")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= brca_germline, fill = raceeth))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "BRCA germline")+
+  coord_flip()
+
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= brca_tumor, fill = raceeth))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "BRCA tumor")+
+  coord_flip()
+```
+</div>
+</div>
+
+<br>
+
+## Survivals by clinical
+
+<span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the right**</span>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r clinical from dx, fig.height = 7}
+# OS by race
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by histology
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca1_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca1_g
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca2_g
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca_g
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r clinical from first treatment, fig.height = 7}
+# OS by race
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by histology
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ histology, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca1_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+# OS by brca1_g
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca2_g
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca_g
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+</div>
+
+<br>
+<br>
+
+***
+# Analysis Treatment
+
 ## Treatment summary table
+
 <span style="color:green">**Table 3 Summary treatment data by race**</span>
@@
 ```{r Table 3}
-tbl1 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+# tbl1 <- 
+  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
   filter(exclude != "1") %>% 
@@
            )) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p()
-tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
-  filter(exclude != "1") %>% 
-  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
-           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
-           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
-           )) %>% 
-  tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p()
-tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
-```
-
-<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
-
-```{r Table 4}
-# Treatment & demo
-tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl3 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl4 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl5 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl6 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl4, tbl3, tbl5, tbl6))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl5 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_p()
-tbl6 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl5, tbl6))
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+#   filter(exclude != "1") %>% 
+#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
+#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
+#            "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
+#            )) %>% 
+#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
 ```
@@
 
-## Survivals
-### OS by clinical
-
-<span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the left**</span>
-
-<div class = "row">
-<div class = "col-md-6">
-```{r, fig.height = 7}
-# OS by race
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by histology
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by tstage
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ tstage, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca1_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca2_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca1_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca2_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-# OS by race
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by histology
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ histology, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by tstage
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ tstage, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca1_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca2_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-# OS by brca1_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca2_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by brca_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-```
-</div>
-</div>
-
-<br>
-
-### OS by treatment
+## Survivals by treatment
 
@@
            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
 
@@
            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by extentofdebulking
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by residualdiseasestatus
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by chemotherapy_type
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by treatment_sequence
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 3))
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+</div>
+
+<br>
+<br>
+
+***
+# RDI
+
+## RDI summary table
+
+<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
+
+```{r Table 4}
+
+Frontline %>% group_by(chemotherapy_type, drugname) %>% summarize(average_RDI =mean(mean_RDI_per_drug_chemotype, na.rm = TRUE))
+
+# Treatment & demo
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl3 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl4 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl5, tbl6), quiet = TRUE)
+```
+<br>
+
+# Plots for first treatment
+For RDI, it is calculated for neoadjuvant and adjuvant when a patient got both.
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+analysis_data %>%
+  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
+  ggplot(aes(x= therapy))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+# analysis_data %>% 
+#   arrange(episodedate) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   group_by(chemotherapy_type) %>% 
+#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
+#   geom_bar(stat="identity")+
+#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
+#   theme_minimal()+
+#   guides(fill = FALSE) +
+#   coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  group_by(treatment_sequence) %>% 
+  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
+  geom_bar(stat="identity")+
+  labs(x = "", title = "The treatment_sequence") +
+  theme_minimal()+
+  guides(fill = FALSE) +
+  coord_flip()
+
+# analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+#   ggplot(aes(x= chemo))+
+#   geom_bar()+
+#   theme_minimal()+
+#   coord_flip()
+```
+</div>
+</div>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
+  geom_boxplot()+
+  ylim(c(-.25, 3.5))+
+  geom_jitter(shape=16)+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
+  geom_violin()+
+  ylim(c(-.25, 3.5))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  theme_minimal()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
+  geom_violin()+
+  ylim(c(-.25, 3.5))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  theme_minimal()+
+  coord_flip()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp, fill = drugname))+
+  geom_bar()+
+  theme_minimal()+
+  coord_flip()
+
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
+  # geom_boxplot()+
+  ylim(c(-.25, 3.5))+
+  geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal() +
+  guides(color=FALSE)
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, color = mean_RDI_per_drug_chemotype<0.85))+
+  geom_violin()+
+  ylim(c(-.25, 2.5))+
+  scale_colour_discrete(name=NULL, labels=c("<0.85",">=0.85"))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  theme_minimal()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
+  geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  ylim(c(-.25, 2.5))+
+  scale_colour_discrete(name=NULL, labels=c("<0.85",">=0.85"))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  theme_minimal()+
+  coord_flip()
+
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp, fill = drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  coord_flip()
+
+```
+</div>
+</div>
+
+A quick summary for the RDI repartition
+```{r}
+analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
+summary(analysis_data2$mean_RDI_per_drug_chemotype)
+```
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp1, fill = drugname))+
+  geom_bar()+
+  theme_minimal()+
+  coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= RDI_grp1, fill = drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  coord_flip()
+```
+</div>
+</div>
+
+<br>
+
+## Survivals by RDI
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
 # OS by RDI_grp
@@
                      filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
+           title = "OS from date of diagnosis Overall RDI", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "platin")) %>%
+                     filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>%
 
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
+           title = "OS from date of diagnosis carboplatin", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from date of diagnosis cisplatin", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
 
@@
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
+           title = "OS from date of diagnosis all taxel", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
 ```
@@
 ```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by extentofdebulking
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by residualdiseasestatus
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by chemotherapy_type
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by treatment_sequence
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
-
 # OS by RDI_grp
@@
                      filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
+           title = "OS from date of from first treatment overall RDI", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "platin")) %>%
+                     filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>%
 
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
+           title = "OS from date of from first treatment carboplatin", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from date of from first treatment cisplatin", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
 
@@
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 4.5, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 2))
+           title = "OS from date of from first treatment all taxel", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
 ```
@@
 <br>
-
-## Hazard Ratio
+<br>
+
+***
+# Hazard Ratio
 
@@
 `coxph(Surv(time = month_at_os, event = vitalstatus)~variables`
-```{r}
+```{r Table 5 HR}
 # tbl1 <- analysis_data %>% 
@@
 ```
-
-## Regression
-### By clinical, demo
+<br>
+<br>
+
+***
+# Regression
+## By clinical, demo
 `glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)`
@@
 model <- glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)
-tbl1 <- tbl_regression(model)
-tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
 tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
@@
              data = analysis_data, family = binomial)
-tbl1 <- tbl_regression(model)
-tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
 tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
@@
 model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)
-tbl1 <- tbl_regression(model)
-tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
 tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
@@
                filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
-tbl1 <- tbl_regression(model)
-tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
 tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
@@
                filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
-tbl1 <- tbl_regression(model)
-tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
 tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
@@
                filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
-tbl1 <- tbl_regression(model)
-tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
 tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
 
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+model <- glm(RDI_grp ~ agecat + bmi_cat, data = analysis_data %>% 
                filter(drugname == "cisplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
-tbl1 <- tbl_regression(model)
-tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
 tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
@@
 # tbl5 <- 
-  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
+  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**cisplatin/Adjuvant**", "**cisplatin/Neoadjuvant**"))
 
@@
                filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
-tbl1 <- tbl_regression(model)
-tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
 tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
@@
                filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
-tbl1 <- tbl_regression(model)
-tbl2 <- tbl_regression(model, exponentiate = TRUE)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
 tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
@@
 ```
-
-## Plots for first treatment
-For RDI, it is calculated for neoadjuvant and adjuvant when a patient got both.
-<div class = "row">
-<div class = "col-md-6">
-```{r}
-analysis_data %>%
-  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
-  ggplot(aes(x= therapy))+
-  geom_bar()+
-  theme_minimal()+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-# analysis_data %>% 
-#   arrange(episodedate) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   group_by(chemotherapy_type) %>% 
-#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
-#   geom_bar(stat="identity")+
-#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
-#   theme_minimal()+
-#   guides(fill = FALSE) +
-#   coord_flip()
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  group_by(treatment_sequence) %>% 
-  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
-  geom_bar(stat="identity")+
-  labs(x = "", title = "The treatment_sequence") +
-  theme_minimal()+
-  guides(fill = FALSE) +
-  coord_flip()
-
-# analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
-#   ggplot(aes(x= chemo))+
-#   geom_bar()+
-#   theme_minimal()+
-#   coord_flip()
-```
-</div>
-</div>
-
-<div class = "row">
-<div class = "col-md-6">
-```{r}
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
-  geom_boxplot()+
-  ylim(c(-.25, 3.5))+
-  geom_jitter(shape=16)+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
-  theme_minimal()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
-  geom_violin()+
-  ylim(c(-.25, 3.5))+
-  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  theme_minimal()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
-  geom_violin()+
-  ylim(c(-.25, 3.5))+
-  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  theme_minimal()+
-  coord_flip()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= RDI_grp, fill = drugname))+
-  geom_bar()+
-  theme_minimal()+
-  coord_flip()
-
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
-  # geom_boxplot()+
-  ylim(c(-.25, 3.5))+
-  geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
-  theme_minimal() +
-  guides(color=FALSE)
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, color = mean_RDI_per_drug_chemotype<0.85))+
-  geom_violin()+
-  ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c("<0.85",">=0.85"))+
-  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  theme_minimal()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
-  geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c("<0.85",">=0.85"))+
-  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  theme_minimal()+
-  coord_flip()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= RDI_grp, fill = drugname))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  coord_flip()
-
-```
-</div>
-</div>
-
-A quick summary for the RDI repartition
-```{r}
-analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
-summary(analysis_data2$mean_RDI_per_drug_chemotype)
-```
-
-<div class = "row">
-<div class = "col-md-6">
-```{r}
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= RDI_grp1, fill = drugname))+
-  geom_bar()+
-  theme_minimal()+
-  coord_flip()
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= RDI_grp1, fill = drugname))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  coord_flip()
-```
-</div>
-</div>
+<br>
+<br>
+
+***
 

### 2021-04-01 R/2.data cleaning.R

@@ -245,13 +245,13 @@ rm(weight1, weight2, vitals)
 areaUC <- auc %>% 
   filter(str_detect(drugname, "taxel|platin")) %>% 
   filter(!is.na(relativeorderedamount)) %>% 
-  # select(c("patientid", "expectedstartdate", orderedamount, orderedunits, "relativeorderedamount",
-  #          "relativeorderedunits", "drugname", iscanceled)) %>%
+  select(c("patientid", "expectedstartdate", "orderedamount", "orderedunits", "relativeorderedamount",
+           "relativeorderedunits", "drugname", "iscanceled")) %>%
   mutate(target_auc = case_when( # F7D7377578248 what for the patients who have order amount
     # relativeorderedunits == "mg/kg" |
     #   relativeorderedunits == "mg" |
     #   relativeorderedunits == "m"         ~ NA_real_,
-    str_detect(drugname, "taxel") &
+    str_detect(drugname, "taxel|cisplatin") &
       relativeorderedunits == "mg/m2" &
       relativeorderedamount >= 50 &
       relativeorderedamount <= 175        ~ relativeorderedamount, # F21904E0D872F we should open more? F11B625154B62
@@ -556,8 +556,8 @@ Frontline <- Treatment %>%
   # filter(therapy == "Upfront Chemo" | therapy == "Chemotherapy only") %>% 
   # group_by(patientid, linenumber_new, cycle_increment, drugname) %>% # ! -----------------------Change drugname if combine taxel....
   # mutate(amount_cycle = sum(amount)) %>% 
-  select(patientid, linenumber_new, cycle_increment, drugname, amount, amount_cycle, 
-         target_auc, expected_dose, everything()) %>% # F01E4E6DD63C5, F1FA39C41A087 ----------- No we have xpected dose for each episode
+  # select(patientid, linenumber_new, cycle_increment, drugname, amount, amount_cycle, 
+  #        target_auc, expected_dose, everything()) %>% # F01E4E6DD63C5, F1FA39C41A087 ----------- No we have xpected dose for each episode
   # ungroup() %>% 
   # distinct(patientid, linenumber_new, cycle_increment, drugname, .keep_all = TRUE) %>% 
   

### 2021-04-02 Rmd/Report analysis 04022021.Rmd
Finished analysis html report

--- 2021-04-01 Rmd/Report analysis update.Rmd
@@
 ***
-# Analysis Clinical
+# I.Analysis Clinical
 
@@
 
-## Clinical summary table
+## 1.Clinical summary table
 ```{r analysis_data}
@@
 
-## Plots for first treatment
+## 2.Plots Clinical
 <div class = "row">
@@
 
-## Survivals by clinical
+## 3.Survivals by clinical
 
@@
 ***
-# Analysis Treatment
-
-## Treatment summary table
+# II.Analysis Treatment
+
+## 1.Treatment summary table
 
@@
            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
+           had_neo, had_adj,
            "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
@@
 
-## Survivals by treatment
-
-<div class = "row">
-<div class = "col-md-6">
-```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by extentofdebulking
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by residualdiseasestatus
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by chemotherapy_type
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by treatment_sequence
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by extentofdebulking
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by residualdiseasestatus
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by chemotherapy_type
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by treatment_sequence
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 3))
-
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-</div>
-
-<br>
-<br>
-
-***
-# RDI
-
-## RDI summary table
-
-<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
-
-```{r Table 4}
-
-Frontline %>% group_by(chemotherapy_type, drugname) %>% summarize(average_RDI =mean(mean_RDI_per_drug_chemotype, na.rm = TRUE))
-
-# Treatment & demo
-tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl3 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl4 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl5, tbl6), quiet = TRUE)
-```
-<br>
-
-# Plots for first treatment
-For RDI, it is calculated for neoadjuvant and adjuvant when a patient got both.
+## 2.Plots Treatment
 <div class = "row">
@@
 analysis_data %>%
-  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= therapy))+
@@
   distinct(patientid, .keep_all = TRUE) %>% 
-  group_by(treatment_sequence) %>% 
-  summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-  ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+
-  geom_bar(stat="identity")+
+  # group_by(treatment_sequence) %>% 
+  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= treatment_sequence,
+             # y= percent, 
+             fill = treatment_sequence))+
+  geom_bar(
+    # stat="identity"
+    )+
   labs(x = "", title = "The treatment_sequence") +
@@
 </div>
+
+<br>
+
+## 3.Survivals by treatment
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by extentofdebulking
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by residualdiseasestatus
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by chemotherapy_type
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by treatment_sequence
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by extentofdebulking
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by residualdiseasestatus
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by chemotherapy_type
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by treatment_sequence
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(nrow = 3))
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE) %>% 
+                     filter(exclude != "1")),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+</div>
+
+<br>
+<br>
+
+***
+# III.RDI
+
+## 1.RDI summary table
+
+<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
+
+```{r Table 4}
+
+Frontline %>% group_by(chemotherapy_type, drugname) %>% summarize(average_RDI =mean(mean_RDI_per_drug_chemotype, na.rm = TRUE))
+
+# Treatment & demo
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl3 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl4 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
+              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+  filter(exclude != "1") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <- 
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl5, tbl6), quiet = TRUE)
+```
+<br>
+
+## 2.Plots RDI
+For RDI boxplot and violin, it is calculated for neoadjuvant and adjuvant when a patient got both (need to find another way of plotting to do by drug - maybe a wrap).
 
@@
   ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c("<0.85",">=0.85"))+
+  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
@@
 </div>
+
+```{r}
+analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+  # filter(linenumber_new == "1") %>% 
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, alpha = mean_RDI_per_drug_chemotype<0.85))+
+  geom_violin(aes(fill = drugname))+
+  ylim(c(-.25, 2.5))+
+  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+  theme_minimal()
+```
 
@@
 
-## Survivals by RDI
+## 3.Survivals by RDI
 
@@
                      filter(exclude != "1")),
-           title = "OS from date of diagnosis Overall RDI", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
+           title = "OS from diagnosis Overall RDI", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+
            # Add risk table
@@
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of diagnosis carboplatin", 
+           title = "OS from diagnosis carboplatin", 
            font.main = c(24, "bold", "black"), 
@@
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of diagnosis cisplatin", 
+           title = "OS from diagnosis cisplatin", 
            font.main = c(24, "bold", "black"), 
@@
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of diagnosis all taxel", 
+           title = "OS from diagnosis all taxel", 
            font.main = c(24, "bold", "black"), 
@@
                      filter(exclude != "1")),
-           title = "OS from date of from first treatment overall RDI", 
+           title = "OS from first treatment overall RDI", 
            font.main = c(24, "bold", "black"), 
@@
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of from first treatment carboplatin", 
+           title = "OS from first treatment carboplatin", 
            font.main = c(24, "bold", "black"), 
@@
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of from first treatment cisplatin", 
+           title = "OS from first treatment cisplatin", 
            font.main = c(24, "bold", "black"), 
@@
                      distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from date of from first treatment all taxel", 
+           title = "OS from from first treatment all taxel", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+</div>
+
+<br>
+
+## Survivals RDI by chemotherapy type
+**On the left are Neoadjuvant, on the right are Adjuvant**
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
+                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from first treatment carboplatin", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
+                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from first treatment cisplatin", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by RDI_grp for taxel
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "taxel"),
+                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from from first treatment all taxel", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
+                            str_detect(chemotherapy_type, "Adjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from first treatment carboplatin", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
+                            str_detect(chemotherapy_type, "Adjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from first treatment cisplatin", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by RDI_grp for taxel
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+                     filter((exclude != "1") & str_detect(drugname, "taxel"),
+                            str_detect(chemotherapy_type, "Adjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)), 
+           title = "OS from from first treatment all taxel", 
            font.main = c(24, "bold", "black"), 
@@
 ***
-# Hazard Ratio
+# IV.Hazard Ratio
 
@@
 ***
-# Regression
+# V.Regression
 ## By clinical, demo

### 2021-04-02 R/2.data cleaning.R

@@ -268,6 +268,7 @@ areaUC <- auc %>%
 
 #################################################################################################### II ### Clinical Cleaning----
 clinical_data <- clinical_data %>% 
+  mutate(raceeth = factor(raceeth, levels = c("NHWhite", "NHBlack", "Hispanic", "Other"))) %>% 
   mutate(race = case_when(
     str_detect(race, "Black")    ~ "Black",
     str_detect(race, "Hispanic") ~ "White",

### 2021-09-08 Rmd/Report 2021.Rmd
Update cleaning and start report

--- 2021-04-02 Rmd/Report analysis 04022021.Rmd
@@
 ```{r analysis_data}
-analysis_data <- Frontline %>% 
+
+Treatment %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  filter(exclude == "1") %>%
+  nrow()
+
+analysis_data <- Treatment %>% 
   distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
@@
 ```{r Table 1}
+
+library(naniar)
 analysis_data %>%
-  select(c(race, raceeth, ethnicity, "vital",
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
+  gg_miss_upset()
+
+analysis_data %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
+  gg_miss_upset()
+
+is.na(analysis_data$CrCl) %>% sum()
+is.na(analysis_data$amount) %>% sum()
+is.na(analysis_data$target_auc) %>% sum()
+
+analysis_data %>% filter(!is.na(target_auc) & !is.na(expected_dose)) %>%
+    distinct(patientid, .keep_all = TRUE) %>% nrow()
+
+# How should I filter??????????????????///
+analysis_data %>% 
+  select(c(raceeth, "vital",
            agecat, "ageatdx",
 
-           "bmi", bmi_cat, "BSA",
+           bmi_at_dx, bmi_cat, 
+           weight_at_dx, height_at_dx, bsa_at_dx,
 
@@
            "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
-           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
-
-           "hrd_tissue", "gis_tissue")) %>% 
+           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown")) %>% 
   tbl_summary() %>% bold_labels()
@@
 analysis_data %>% 
-  select(c(race, raceeth, ethnicity, "vital",
+  select(c(raceeth, "vital",
            agecat, "ageatdx",

### 2021-09-08 R/2.data cleaning.R

@@ -17,7 +17,19 @@ creatinine <- creatinine %>%
   mutate(creatinine = coalesce(creatinine, creatinine1)) %>% 
   filter(!is.na(creatinine)) %>% 
   mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
-  select(c("patientid", creat_date = "testdate", "creatinine", creat_units = "testunitscleaned"))
+  left_join(., clinical_data %>% 
+              select(patientid, diagnosisdate), 
+            by = "patientid") %>% 
+  mutate(interval = abs(interval(start= testdate, end= diagnosisdate)/
+                          duration(n=1, unit="days"))) %>%
+  group_by(patientid) %>% 
+  mutate(interval_creat_x = min(interval)) %>% 
+  mutate(creatinine_at_dx = case_when(
+    interval == interval_creat_x          ~ creatinine
+  )) %>% 
+  fill(creatinine_at_dx, .direction = "updown") %>% 
+  select(c(patientid, creat_date = "testdate", creatinine, 
+           creat_units = "testunitscleaned", creatinine_at_dx, interval_creat_x))
 
 # body_surface_area, height and weight are all coming from vitals
 vitals <- vitals %>% 
@@ -42,7 +54,19 @@ body_surface_area <- vitals %>%
   mutate(BSA = coalesce(testresultcleaned, BSA)) %>% 
   filter(!is.na(BSA)) %>% 
   mutate(BSA_units = "m2") %>% 
-  select(c("patientid", bsa_date = "testdate", "BSA", "BSA_units"))
+  left_join(., clinical_data %>% 
+              select(patientid, diagnosisdate), 
+            by = "patientid") %>% 
+  mutate(interval = abs(interval(start= testdate, end= diagnosisdate)/
+                          duration(n=1, unit="days"))) %>%
+  group_by(patientid) %>% 
+  mutate(interval_bsa_dx = min(interval)) %>% 
+  mutate(bsa_at_dx = case_when(
+    interval == interval_bsa_dx          ~ BSA
+  )) %>% 
+  fill(bsa_at_dx, .direction = "updown") %>% 
+  select(c(patientid, bsa_date = "testdate", BSA, 
+           BSA_units, bsa_at_dx, interval_bsa_dx))
 
 
 #################################################################################################### 3 ### Cleanup of Height----
@@ -115,7 +139,19 @@ height <- vitals %>%
     )) %>% 
[…]

### 2021-09-09 R/2.data cleaning.R
Update clinical cleaning and creatinine

@@ -4,13 +4,13 @@ creatinine <- creatinine %>%
   # remove creatine urine
   filter(str_detect(labcomponent, "blood|serum")) %>% 
   mutate(creatinine = case_when(
-    testresultcleaned < 0.8        ~ 0.8,
+    testresultcleaned < 0.7        ~ 0.7,
     testresultcleaned > 3          ~ NA_real_, # F006DBE0C7A5E is an example of slow increase past 3, F641A8DC820C7 super high
     TRUE                           ~ testresultcleaned
   )) %>% 
   # F092F8B827DDC kept umol/L as they actually are mg/dL range 45 to 90 μmol/L (0.5 to 1.0 mg/dL) for women.
   mutate(creatinine1 = case_when(
-    testresult < 0.8               ~ 0.8,
+    testresult < 0.7               ~ 0.7,
     testresult > 3                 ~ NA_real_,
     TRUE                           ~ testresult
   )) %>% 
@@ -537,10 +537,9 @@ areaUC <- auc %>%
 #################################################################################################### II ### Clinical Cleaning----
 clinical_data <- clinical_data %>% 
   # Limit to the patients to the ones we have date of surgery when had surgery
-  filter(!(issurgery == "Yes" & is.na(surgerydate))) %>% 
-  # create variable to help filtering when bind everything together
-  # mutate(inclusion = "patients included") %>% 
-  # recode
+  filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%  # loss 17
+  filter(!(histology == "Unknown/not documented")) %>% # loss 287
+  # Recode
   mutate(raceeth = factor(raceeth, levels = c("NHWhite", "NHBlack", "Hispanic", "Other"))) %>% 
   mutate(race = case_when(
     str_detect(race, "Black")    ~ "Black",
@@ -557,7 +556,7 @@ clinical_data <- clinical_data %>%
     ethnicity == "Hispanic"    ~ "Hispanic"
   )) %>% 
   unite(new_raceeth, c(new_eth, race), sep = " ", remove = FALSE, na.rm = TRUE) %>% 
-  mutate(new_raceeth1 = ifelse(str_detect(new_raceeth, "Black|Hispanic"), "Minority", new_raceeth)) %>%  # min = Asian Hisp
+  mutate(new_raceeth1 = ifelse(str_detect(new_raceeth, "Black|Hispanic"), "Minority", new_raceeth)) %>% 
   # Lauren recoded followupdate to have the days of death with Flatiron rules
[…]

### 2021-09-09 Rmd/Report 2021.Rmd
Update clinical cleaning and creatinine
Add more drug cleaning, plots, tables in rmd

@@
 ***
-# I.Analysis Clinical
-
-For all these analysis, I excluded the patients Lauren said to remove from the analysis.
 
@@
 ```{r loadd}
-loadd(clinical_data, vitals, drugs, auc, creatinine)
-Frontline <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/Frontline.rds")
-```
-
-## 1.Clinical summary table
+loadd(drugs)
+creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
+weight <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/weight.rds")
+height <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/height.rds")
+body_surface_area <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/body_surface_area.rds")
+areaUC <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/areaUC.rds")
+clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
+```
+
+At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.
+
+# I. Drug episode questions
+
+```{r drugs episode cleanup}
+drugs1 <- drugs %>% 
+  filter(episodedatasource == "Administrations" & 
+           ismaintenancetherapy == "FALSE") %>%
+  # 1. 60 days rule between diagnosis and treatment # Loss 1
+  # bind with clinical
+  inner_join(., clinical_data, #%>% select("patientid", "diagnosisdate", "surgerydate"),
+          by = "patientid") %>% 
+  arrange(patientid, episodedate) %>% 
+  group_by(patientid) %>% 
+  mutate(first_drug_date = first(episodedate)) %>% 
+  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
+           duration(n=1, units = "months")) %>% 
+  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
+           duration(n=1, units = "months")) %>% 
+  ungroup()
+
+drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()
+drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()
+```
+
+Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
+
+```{r}
+drugs1 <- drugs1 %>% 
+  filter(days_at_first_drug >= 0 &
+           (is.na(surgerydate) | days_at_surg >= 0)
+         )
+drugs1 %>% distinct(patientid) %>% nrow()
+```
+
+60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded 
+```{r}
+remove_60daysrule <- drugs1 %>% 
+  filter((days_at_first_drug > 60 | days_at_surg > 60)) %>% 
+  distinct(patientid)
+remove_60daysrule <- paste(remove_60daysrule$patientid, collapse = "|")
+
+drugs1 <- drugs1 %>% 
+  # remove these patients who 60 days rule
+  filter(!str_detect(patientid, remove_60daysrule))
+
+drugs1 %>% distinct(patientid) %>% nrow()
+```
+
+Remove linename that doesn't include platin or taxels -> later, need to recode linenumber first
+```{r}
+# drugs1 <- drugs1 %>% 
+#   # 2. Filtering----
+#   filter(episodedatasource == "Administrations" & 
+#            # ismaintenancetherapy == "FALSE" & 
+#            !is.na(amount) &
+#            (days_at_drug < 60 | days_at_surg < 60) &
+#            
+#            days_at_drug >= 0 &
+#            (is.na(surgerydate) | days_at_surg >= 0)
+#          )
+
+drugs1 %>% 
+  filter(linenumber == 1) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linename) %>% 
+  tbl_summary(sort = list(everything() ~ "frequency"))
+```
+
+```{r combine amount same drug one day}
+drugs1 <- drugs1 %>% 
+  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
+  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
+  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
+  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route,
+            diagnosisdate)) %>%
+
+  # 3. Combined Multiple Administrations----
+  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
+# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day.
+We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day.
+Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data.
+Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
+# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
+# Three administrations of the same drug were listed on a Friday.
+The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.
+# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
+  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_drug, days_at_surg) %>%
+  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
+  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
+           fill = "right") %>%
+  purrr::keep(~!all(is.na(.))) %>%
+  ungroup() %>% 
+  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
+         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
+  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
+  # Found ug, ml, Ea, and NA they are all good, but 
+  # ug need conversion
+  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
+  mutate(amount =  case_when(
+    units == "ug"               ~ amount / 10, # I checked all of them
+    units == "AUC" &
+      amount < 10               ~ NA_real_,
+    TRUE                        ~ amount
+  )) %>%
+
+  mutate(drugname_type = case_when(
+    str_detect(drugname, "platin")       ~ "platin",
+    str_detect(drugname, "taxel")        ~ "taxel"
+  ))
+```
+
+Recode linenumber depending on surgery date
+```{r line coding}
+therapy_line <- drugs1 %>% 
+  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
+  mutate(chemotherapy_type = case_when(
+    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
+    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
+    episodedate > surgerydate         ~ "Adjuvant",
+    is.na(surgerydate) &
+      !is.na(episodedate)             ~ "Chemotherapy only",
+    !is.na(surgerydate) &
+      is.na(episodedate)              ~ "Surgery only"
+    )) %>% 
+  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
+  group_by(patientid) %>% 
+  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
+  fill(had_neo, .direction = "updown") %>% 
+  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
+  fill(had_adj, .direction = "updown") %>% 
+  mutate(treatment_sequence = case_when(
+    had_neo == "Yes" &
+      had_adj == "Yes"                           ~ "neo + surg + adj",
+    had_neo == "Yes" &
+      is.na(had_adj)                             ~ "neo + surg",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "surg + adj",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only"
+  )) %>% 
+  mutate(therapy = case_when(
+    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
+    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Surgery only"          ~ "Surgery only",
+    is.na(had_neo) &
+      had_adj == "Yes"                           ~ "Upfront Surgery"
+  )) %>% 
+  fill(therapy, .direction = "downup") %>% 
+  # mutate(therapy1 = case_when(
+  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
+  # )) %>% 
+  # fill(therapy1, .direction = "downup") %>% 
+  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
+  # select( -therapy1) %>%
+
+  # 5.Redefine line number based on the original linenumber variable and the surgery date----
+  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird
+  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
+  ungroup() %>%
+
+  # 6.Add a 30 day rule to switch linenumber----
+  # group_by(patientid, linenumber_new) %>% 
+  # arrange(episodedate) %>% 
+  # mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
+  # mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
+  # ungroup() %>% 
+  # group_by(patientid) %>% 
+  # mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
+  # mutate(linenumber_new = linenumber_new + jump_line) %>% 
+  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37
+
+  # 7.Calculate cycle for each line----
+  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
+  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
+  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
+  ungroup() %>% 
+  mutate(across(c("linenumber", "linenumber_new"), as.factor))
+
+# Number of patient with a jump line in the first line # 60 would have
+# therapy_line %>% 
+#   filter(linenumber == 1 & linenumber_new == 2) %>% 
+#   arrange(desc(jump_line)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(jump_line) %>% 
+#   tbl_summary()
+```
+
+# Number of patient who switch line because of surgery from line 1 to adjuvant line
+```{r line coding}
+therapy_line %>% 
+  mutate(change_line = case_when(
+    linenumber == 1 & 
+      linenumber_new == 2 &
+      chemotherapy_type == "Adjuvant" &
+      treatment_sequence == "neo + surg + adj"     ~ 1,
+    TRUE                                           ~ 0
+  )) %>% 
+  arrange(desc(change_line)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(change_line) %>% 
+  tbl_summary()
+```
+
+# How many lines patient got as Neo
+```{r}
+therapy_line %>% 
+  filter(chemotherapy_type == "Neoadjuvant") %>% 
+  arrange(desc(linenumber_new)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linenumber_new) %>% 
+  tbl_summary()
+
+therapy_line %>% 
+  filter(chemotherapy_type == "Neoadjuvant" &
+           linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5) %>% 
+  select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
+         drugname, episodedate, surgerydate, chemotherapy_type) %>%
+  arrange(patientid, episodedate)
+```
+
+# Remove patients with more than 1 line as Neo -34
+```{r}
+remove_morethan1_neo <- therapy_line %>% 
+  filter(chemotherapy_type == "Neoadjuvant" &
+           linenumber_new != 1)
+remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")
+
+therapy_line <- therapy_line %>% 
+  # Remove patients with more than 1 line as Neo
+  filter(!str_detect(patientid, remove_morethan1_neo))
+
+therapy_line %>% distinct(patientid) %>% nrow()
+```
+
+# Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
+```{r}
+# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
+therapy_line %>% 
+  filter(str_detect(linename, "Car") &
+           drugname == "cisplatin") %>%
+  distinct(patientid) %>% nrow()
+
+therapy_line %>% 
+  filter(str_detect(linename, "Cisplatin") &
+           drugname == "carboplatin") %>%
+  distinct(patientid) %>% nrow()
+
+remove_switch <- therapy_line %>% 
+  filter(
+    (str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
+  (str_detect(linename, "Cisplatin") & drugname == "carboplatin")
+  ) %>%
+  distinct(patientid)
+remove_switch <- paste(remove_switch$patientid, collapse = "|")
+
+therapy_line <- therapy_line %>% 
+  # remove these patients who switched C > C 
+  filter(!str_detect(patientid, remove_switch))
+therapy_line %>% distinct(patientid) %>% nrow()
+```
+
+Should I do the same between paclitaxel and docetaxel? Remember I pacli == pacli protein bound
+
+If a patient had carbo, pacli, carbo, pacli, docetaxel in a Cabo-Pacli line : Could be annoying when I code cycle
+
+In 1 cycle we can have taxel multiple times, is it possible for carbo or cisplatin?
+```{r}
+# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
+therapy_line %>% 
+  filter(str_detect(linename, "Pacli") &
+           drugname == "docetaxel") %>%
+  distinct(patientid) %>% nrow()
+therapy_line %>% 
+  filter(str_detect(linename, "Doce") &
+           drugname == "Paclitaxel") %>%
+  distinct(patientid) %>% nrow()
+```
+
+# Code cycle
+```{r cycle coding}
+# Code cycle number
+therapy_cycle <- therapy_line %>%
+
+  arrange(patientid, episodedate) %>% 
+  group_by(patientid, linenumber_new) %>%
+  # Need the number of time of the "major" drug is seen in the line
+  mutate(cycle_count_perline = min(drugname_count_perline)) %>%
+  mutate(cycle_drugname = case_when(
+    cycle_count_perline == drugname_count_perline          ~ drugname,
+    TRUE                                                   ~ NA_character_
+  )) %>% 
+  # select(-drugname_count_perline) %>% 
+  group_by(patientid, linenumber_new, cycle_drugname) %>%
+  mutate(cycle_inc = row_number(cycle_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
+
+  # + What to do when it is a cycle change F003F2BEEDB37 ,
+
+  # group_by(patientid, linenumber_new, cycle_inc) %>%
+  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
+  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
+  arrange(patientid, episodedate, cycle_inc) %>% 
+  group_by(patientid, linenumber_new) %>%
+  mutate(cycle_increment = cycle_inc) %>% 
+  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
+  # cycle date
+  group_by(patientid, linenumber_new, cycle_increment) %>% 
+  mutate(cycle_start_date = min(episodedate)) %>% 
+  # select(patientid, linename, linenumber_new, drugname, episodedate,
+  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>%
+
+  group_by(patientid, linenumber_new) %>% 
+  mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
+         cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
+
+  # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
+  mutate(n = row_number(drugname)) %>%
+
+  mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
+  fill(base_days_between_cycle, .direction = "downup") %>% 
+  mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
+                                       (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
+  # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
+  group_by(patientid, linenumber_new) %>%
+  mutate(drug_count_perline = n()) %>%
+  mutate(skipped_cycle_indays1 = ifelse(
+    (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
+  )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
+  # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
+  group_by(patientid) %>% 
+  mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
+  ungroup()
+```
+
+## Bind everything together and calculating target_auc and expected dose
+
+When I bind things together I take the closest date of BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`. it can be days in between or more. Do we need a max?
+Precision when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
+```{r target_auc and expected dose}
+Treatment <- 
+  # Merge with creatinine
+  left_join(therapy_cycle, creatinine, by = "patientid") %>%
+  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval_creat) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Merge with height
+  left_join(. , height,  by = "patientid") %>%
+  mutate(interval_height = abs(interval(start= height_date, end= cycle_start_date)/
+           duration(n=1, unit="days"))) %>%
+  arrange(interval_height) %>%
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Merge with weight
+  left_join(. , weight, by = "patientid") %>%
+  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
+                        duration(n=1, unit="days"))) %>%
+  arrange(interval_weight) %>%
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
+         cycle_start_date, .keep_all = TRUE) %>%
+
+  # Calculate bmi
+  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
+  mutate(bmi_cat = case_when(
+    bmi_at_dx < 25                    ~ "Underweight and normal weight",
+    bmi_at_dx >= 25 &
+      bmi_at_dx < 30                  ~ "Overweight",
+    bmi_at_dx >= 30                   ~ "Obese"
+  )) %>%
+  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
+  # Calculate CrCl
+  # inner_join(., clinical_data %>% select(-c("diagnosisdate", "surgerydate")),
+  #            by = "patientid") %>% 
+  mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
+  mutate(CrCl = case_when(
+    CrCl > 125                        ~ 125,
+    TRUE                              ~ CrCl
+  )) %>%
+
+  # Merge with body_surface_area
+  left_join(., body_surface_area, by = "patientid") %>%
+  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
+                          duration(n=1, unit="days"))) %>%
+  arrange(interval_bsa) %>%
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
+           cycle_start_date, .keep_all = TRUE) %>%
+  # Calculate more bsa value with height and weight using Du Bois formula
+  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
+  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
+  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
+  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
+  select(-bsa_du_bois) %>%
+
+  # Merge with auc
+  left_join(., areaUC, by = c("patientid", "drugname")) %>%
+  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
+                          duration(n=1, unit="days"))) %>% 
+  arrange(interval_auc) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Calculate expected dose
+  mutate(expected_dose = case_when(
+    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
+    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
+    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
+  )) %>% 
+  mutate(expected_dose = case_when(
+    expected_dose > 900 &
+      target_auc == 6              ~ 900,
+    expected_dose > 750 &
+      target_auc == 5              ~ 750,
+    TRUE                           ~ expected_dose
+  )) %>% 
+  mutate(first_treatment_date = case_when(
+    str_detect(therapy, "Chemo")                      ~ min(episodedate),
+    str_detect(therapy, "Surgery")                    ~ surgerydate,
+  )) %>% 
+  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
+                   duration(n=1, units = "months")) %>% 
+  arrange(patientid, episodedate)
+```
+
+```{r plot interval}
+Treatment %>% 
+  ggplot(aes(x= interval_creat)) +
+  geom_bar() +
+  coord_cartesian(ylim=c(0,50))
+Treatment %>% 
+  ggplot(aes(x= interval_height)) +
+  geom_bar() +
+  coord_cartesian(ylim=c(0,50))
+Treatment %>% 
+  ggplot(aes(x= interval_weight)) +
+  geom_bar() +
+  coord_cartesian(ylim=c(0,50))
+Treatment %>% 
+  ggplot(aes(x= interval_bsa)) +
+  geom_bar() +
+  coord_cartesian(ylim=c(0,50))
+Treatment %>% 
+  ggplot(aes(x= interval_auc)) +
+  geom_bar() +
+  coord_cartesian(ylim=c(0,50))
+```
+
+# Number of patients
+```{r}
+Treatment %>% distinct(patientid) %>% nrow()
+```
+
+Number of line in neo
+```{r}
+Treatment %>% 
+  filter(chemotherapy_type == "Neoadjuvant") %>% 
+  arrange(desc(linenumber_new)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linenumber_new) %>% 
+  tbl_summary()
+```
+Number of line in Adj neo + surg + adj
+```{r}
+Treatment %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  mutate(n = dense_rank(linenumber_new)) %>% 
+  arrange(desc(n)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(n) %>% 
+  tbl_summary()
+```
+Number of line in Adj surg + adj
+```{r}
+Treatment %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
+  mutate(n = dense_rank(linenumber_new)) %>% 
+  arrange(desc(n)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(n) %>% 
+  tbl_summary()
+```
+Number of line in neo
+```{r}
+Treatment %>% 
+  filter(chemotherapy_type == "Chemotherapy only") %>% 
+  arrange(desc(linenumber_new)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linenumber_new) %>% 
+  tbl_summary()
+```
+
+# Final dataset
 ```{r analysis_data}
-
-Treatment %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
-  filter(exclude == "1") %>%
-  nrow()
-
 analysis_data <- Treatment %>% 
-  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
+  # distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
   filter(exclude != "1")
@@
 
-<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
-```{r Table 1}
-
+After excluding exclude == "1" patients, we have `r analysis_data %>% distinct(patientid) %>% nrow()` patients.
+
+```{r}
 library(naniar)
@@
 
-analysis_data %>% filter(!is.na(target_auc) & !is.na(expected_dose)) %>%
-    distinct(patientid, .keep_all = TRUE) %>% nrow()
+# analysis_data %>% filter(is.na(amount)) %>%
+#     distinct(patientid, .keep_all = TRUE) %>% nrow()
+# 
+# analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
+#     distinct(patientid, .keep_all = TRUE) %>% nrow()
+```
+If we remove patients who have at least 1 missing amount administrered, we lose `r analysis_data %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
+
+If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
+
+# CALCULATE RDI
+
+```{r}
+Frontline <- Treatment %>% 
+  # filter(therapy == "Upfront Chemo" | therapy == "Chemotherapy only") %>% 
+  # group_by(patientid, linenumber_new, cycle_increment, drugname) %>% # ! -----------------------Change drugname if combine taxel....
+  # mutate(amount_cycle = sum(amount)) %>% 
+  # select(patientid, linenumber_new, cycle_increment, drugname, amount, amount_cycle, 
+  #        target_auc, expected_dose, everything()) %>% # F01E4E6DD63C5, F1FA39C41A087 ----------- No we have xpected dose for each episode
+  # ungroup() %>% 
+  # distinct(patientid, linenumber_new, cycle_increment, drugname, .keep_all = TRUE) %>%
+
+  # Create a linenumber restating at 1 for adj to be able to calculate RDI for first line of Adjuvant
+    group_by(patientid, chemotherapy_type) %>% 
+  mutate(linenumber_adj = dense_rank(linenumber_new)) %>%
+
+  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
+  mutate(relative_dose_intensity = case_when(
+    chemotherapy_type == "Adjuvant" &
+      linenumber_adj == 1                  ~ amount/expected_dose,
+    chemotherapy_type == "Neoadjuvant"     ~ amount/expected_dose
+  )) %>%
+  # select(patientid, linenumber_new, chemotherapy_type, drugname_type, drugname,
+  #        relative_dose_intensity, linenumber_adj) %>%
+
+  # Average RDI by taxel or platin by line (will combine pacli-doce and cis-carbo-oxalo)
+  group_by(patientid, chemotherapy_type, drugname_type) %>%
+  mutate(mean_RDI_per_chemotype_drug = case_when(
+    chemotherapy_type == "Adjuvant" &
+      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
+    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  )) %>% 
+  ungroup() %>%
+
+  # Then let's see if we need to average that for the whole Neo BUT 
+  # For now average rdi over whole neo, average rdi for the first line over adjuvant
+  # when plot meed 1 rdi per drugname_type per chemotherapy_type aka distinct(patientid, chemotherapy_type, drugname_type)
+
+  # group_by(patientid, chemotherapy_type, drugname_type) %>% 
+  # mutate(RDI_neo = case_when(
+  #   # chemotherapy_type == "Adjuvant"       ~ first(mean_RDI_per_drug_line), # F002B429BE6C6
+  #   chemotherapy_type == "Adjuvant" &
+  #     linenumber_adj == 1                  ~ mean(mean_RDI_per_drug_line),
+  #   chemotherapy_type == "Neoadjuvant"     ~ mean(mean_RDI_per_drug_line) # F0040EA299CF0
+  # )) %>%
+
+  # mutate(RDI_adj = case_when(
+  #   chemotherapy_type == "Adjuvant" &
+  #     linenumber_adj == 1                  ~ mean(mean_RDI_per_drug_line), # F002B429BE6C6
+  #   # chemotherapy_type == "Neoadjuvant"     ~ mean(mean_RDI_per_drug_line) # F0040EA299CF0
+  # )) %>% 
+  # mutate(RDI = coalesce(RDI_neo, RDI_adj))
+
+  # group_by(patientid, chemotherapy_type, drugname) %>% # ------------------------ Or should I do by cycle, then avg again
+  # mutate(mean_RDI_per_drug_chemotype = mean(relative_dose_intensity)) %>% 
+  # ungroup() %>% 
+  mutate(RDI_grp = as.factor(findInterval(mean_RDI_per_chemotype_drug, c(0.85) ))) %>% 
+  mutate(RDI_grp = factor(RDI_grp, 
+                           levels = c("1", "0"), 
+                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
+  mutate(RDI_grp1 = as.factor(findInterval(mean_RDI_per_chemotype_drug, c(0.75, 0.85, 1, 1.5, 2) ))) %>% 
+  mutate(RDI_grp1 = factor(RDI_grp1, 
+                          levels = c("3", "0", "1","2","4", "5"), 
+                          labels = c("0.85 >= RDI < 1", "0 < RDI < 0.75", "0.75 <= RDI < 0.85", "1 <= RDI < 1.5", 
+                                     "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
+  # mutate(delay_incare_dx_to_treat = case_when(
+  #   str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
+  #     duration(n=1, units = "days")),
+  #   str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
+  #     duration(n=1, units = "days"))
+  # )) %>% 
+  # group_by(patientid) %>% 
+  # mutate(first_treatment_date = case_when(
+  #   treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
+  #   str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
+  #   treatment_sequence == "surg + adj"                    ~ surgerydate,
+  #   treatment_sequence == "Surgery only"                  ~ surgerydate
+  # )) %>% 
+  group_by(patientid) %>% 
+  mutate(first_treatment_date = case_when(
+    str_detect(therapy, "Chemo")                      ~ min(episodedate),
+    str_detect(therapy, "Surgery")                    ~ surgerydate,
+  )) %>% 
+  mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
+                                          duration(n=1, units = "days")) %>% 
+  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
+                   duration(n=1, units = "months")) %>% 
+  ungroup() %>% 
+  # %>% 
+  # select(patientid, linenumber_new, drugname, surgerydate, episodedate, treatment_sequence, first_treatment_date, month_at_os_from_treatment)
+  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
+           duration(n=1, units = "days"), 
+         thirty_days_exclusion = ifelse(thirty_days_exclusion <= 30, "Exclude", NA_character_))
+
+```
+
+# Analysis
+
+## 1.Clinical summary table
+
+<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
+```{r Table 1}
 
 # How should I filter??????????????????///
-analysis_data %>% 
-  select(c(raceeth, "vital",
+analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, 
            agecat, "ageatdx",
@@
 
-           "histology", "groupstage", "tstage", "stagecat",
+           "histology", "stagecat",
 
@@
 
-           "bmi", bmi_cat, "BSA",
+           "bmi_at_dx", bmi_cat, "BSA",
 
@@
 # OS by race
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by histology
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by tstage
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca1_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca2_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca1_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca2_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by race
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by histology
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ histology, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ histology, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by tstage
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca1_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca2_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca1_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca2_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by brca_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
   filter(exclude != "1") %>% 
-  select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
+  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
@@
 ```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by extentofdebulking
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by residualdiseasestatus
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by chemotherapy_type
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ chemotherapy_type, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by treatment_sequence
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by therapy
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 ```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by extentofdebulking
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by residualdiseasestatus
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by chemotherapy_type
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ chemotherapy_type, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ chemotherapy_type, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by treatment_sequence
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 # OS by therapy
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=analysis_data %>% 
                      distinct(patientid, .keep_all = TRUE) %>% 
@@
 
-Frontline %>% group_by(chemotherapy_type, drugname) %>% summarize(average_RDI =mean(mean_RDI_per_drug_chemotype, na.rm = TRUE))
-
-# Treatment & demo
-tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl3 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl4 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
-              label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
-  filter(exclude != "1") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <- 
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl5, tbl6), quiet = TRUE)
+# Frontline %>% group_by(chemotherapy_type, drugname) %>% summarize(average_RDI =mean(mean_RDI_per_drug_chemotype, na.rm = TRUE)) 
+# 
+# # Treatment & demo
+# tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(raceeth,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(bmi_cat,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl3 <- 
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl4 <- 
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl5 <- 
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = raceeth,
+#               type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
+#               label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = bmi_cat,
+#               type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
+#               label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl6 <- 
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
+# 
+# 
+# 
+# tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl5 <- 
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
+#   filter(exclude != "1") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl6 <- 
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl_stack(list(tbl5, tbl6), quiet = TRUE)
 ```
@@
 ```{r}
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
-  geom_boxplot()+
-  ylim(c(-.25, 3.5))+
-  geom_jitter(shape=16)+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
-  theme_minimal()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
-  geom_violin()+
-  ylim(c(-.25, 3.5))+
-  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  theme_minimal()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
-  geom_violin()+
-  ylim(c(-.25, 3.5))+
-  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  theme_minimal()+
-  coord_flip()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= RDI_grp, fill = drugname))+
-  geom_bar()+
-  theme_minimal()+
-  coord_flip()
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
+#   geom_boxplot()+
+#   ylim(c(-.25, 3.5))+
+#   geom_jitter(shape=16)+
+#   labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+#   theme_minimal()
+# 
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
+#   geom_violin()+
+#   ylim(c(-.25, 3.5))+
+#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+#   theme_minimal()
+# 
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
+#   geom_violin()+
+#   ylim(c(-.25, 3.5))+
+#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+#   theme_minimal()+
+#   coord_flip()
+# 
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= RDI_grp, fill = drugname))+
+#   geom_bar()+
+#   theme_minimal()+
+#   coord_flip()
 
@@
 ```{r}
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
-  # geom_boxplot()+
-  ylim(c(-.25, 3.5))+
-  geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
-  theme_minimal() +
-  guides(color=FALSE)
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, color = mean_RDI_per_drug_chemotype<0.85))+
-  geom_violin()+
-  ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
+#   # geom_boxplot()+
+#   ylim(c(-.25, 3.5))+
 #   geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  theme_minimal()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
-  geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  theme_minimal()+
-  coord_flip()
-
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= RDI_grp, fill = drugname))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  coord_flip()
+#   labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+#   theme_minimal() +
+#   guides(color=FALSE)
+# 
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, color = mean_RDI_per_drug_chemotype<0.85))+
+#   geom_violin()+
+#   ylim(c(-.25, 2.5))+
+#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+#   theme_minimal()
+# 
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
+#   geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+
+#   ylim(c(-.25, 2.5))+
+#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+#   theme_minimal()+
+#   coord_flip()
+# 
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= RDI_grp, fill = drugname))+
+#   geom_bar(position = "fill")+
+#   theme_minimal()+
+#   coord_flip()
+#
 
@@
 ```{r}
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, alpha = mean_RDI_per_drug_chemotype<0.85))+
-  geom_violin(aes(fill = drugname))+
-  ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-  theme_minimal()
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, alpha = mean_RDI_per_drug_chemotype<0.85))+
+#   geom_violin(aes(fill = drugname))+
+#   ylim(c(-.25, 2.5))+
+#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+#   theme_minimal()
 ```
@@
 ```{r}
-analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
-summary(analysis_data2$mean_RDI_per_drug_chemotype)
+# analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
+# summary(analysis_data2$mean_RDI_per_drug_chemotype)
 ```
@@
 ```{r}
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= RDI_grp1, fill = drugname))+
-  geom_bar()+
-  theme_minimal()+
-  coord_flip()
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= RDI_grp1, fill = drugname))+
+#   geom_bar()+
+#   theme_minimal()+
+#   coord_flip()
 ```
@@
 ```{r}
-analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-  # filter(linenumber_new == "1") %>% 
-  ggplot(aes(x= RDI_grp1, fill = drugname))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  coord_flip()
+# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+#   # filter(linenumber_new == "1") %>% 
+#   ggplot(aes(x= RDI_grp1, fill = drugname))+
+#   geom_bar(position = "fill")+
+#   theme_minimal()+
+#   coord_flip()
 ```
@@
 # OS by RDI_grp
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from diagnosis Overall RDI", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for platin
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from diagnosis carboplatin", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from diagnosis cisplatin", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for taxel
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "taxel")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from diagnosis all taxel", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE) %>% 
+#                      filter(exclude != "1")),
+#            title = "OS from diagnosis Overall RDI", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+# 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for platin
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from diagnosis carboplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from diagnosis cisplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for taxel
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from diagnosis all taxel", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
 ```
@@
 ```{r, fig.height = 7}
-# OS by RDI_grp
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from first treatment overall RDI", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for platin
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from first treatment carboplatin", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from first treatment cisplatin", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for taxel
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "taxel")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from from first treatment all taxel", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
+# # OS by RDI_grp
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE) %>% 
+#                      filter(exclude != "1")),
+#            title = "OS from first treatment overall RDI", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for platin
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from first treatment carboplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from first treatment cisplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for taxel
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from from first treatment all taxel", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
 ```
@@
 ```{r, fig.height = 7}
-# OS by RDI_grp for platin
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
-                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from first treatment carboplatin", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
-                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from first treatment cisplatin", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for taxel
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "taxel"),
-                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from from first treatment all taxel", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
+# # OS by RDI_grp for platin
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "carboplatin"),
+#                             str_detect(chemotherapy_type, "Neoadjuvant")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from first treatment carboplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "cisplatin"),
+#                             str_detect(chemotherapy_type, "Neoadjuvant")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from first treatment cisplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for taxel
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "taxel"),
+#                             str_detect(chemotherapy_type, "Neoadjuvant")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from from first treatment all taxel", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
 ```
@@
 ```{r, fig.height = 7}
-# OS by RDI_grp for platin
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
-                            str_detect(chemotherapy_type, "Adjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from first treatment carboplatin", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
-                            str_detect(chemotherapy_type, "Adjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from first treatment cisplatin", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for taxel
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-                     filter((exclude != "1") & str_detect(drugname, "taxel"),
-                            str_detect(chemotherapy_type, "Adjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)), 
-           title = "OS from from first treatment all taxel", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
+# # OS by RDI_grp for platin
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "carboplatin"),
+#                             str_detect(chemotherapy_type, "Adjuvant")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from first treatment carboplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "cisplatin"),
+#                             str_detect(chemotherapy_type, "Adjuvant")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from first treatment cisplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for taxel
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "taxel"),
+#                             str_detect(chemotherapy_type, "Adjuvant")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from from first treatment all taxel", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
 ```
@@
 ```{r Table 5 HR}
+# # tbl1 <- analysis_data %>% 
+# #   select(bmi_cat) %>% 
+# #   tbl_summary(#by = vitalstatus,
+# #               statistic = all_categorical() ~ "{analysis_data %>% filter(vital == 'Dead') %>% NROW()} death ({n})"
+# #               )
+# # tbl2 <- coxph(Surv(time = month_at_os,
+# #                      event = vitalstatus)~bmi_cat,
+# #                 data = analysis_data) %>%
+# #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# # 
+# # tbl_merge(list(tbl1, tbl2))
+# # 
+# # coxph(Surv(time = month_at_os, 
+# #                      event = vitalstatus)~RDI_grp, 
+# #                 data = analysis_data) %>% 
+# #   tbl_uvregression(y = vitalstatus, exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# 
+# analysis_data %>% select(vitalstatus, bmi, bmi_cat, raceeth) %>% 
+# tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = analysis_data$month_at_os, event = analysis_data$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
+#   bold_labels() %>% italicize_levels() #%>%  modify_spanning_header(all_stat_cols() ~ "**Treatment Received**")
+# 
 # tbl1 <- analysis_data %>% 
-#   select(bmi_cat) %>% 
-#   tbl_summary(#by = vitalstatus,
-#               statistic = all_categorical() ~ "{analysis_data %>% filter(vital == 'Dead') %>% NROW()} death ({n})"
-#               )
-# tbl2 <- coxph(Surv(time = month_at_os,
-#                      event = vitalstatus)~bmi_cat,
-#                 data = analysis_data) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# 
-# tbl_merge(list(tbl1, tbl2))
-# 
-# coxph(Surv(time = month_at_os, 
-#                      event = vitalstatus)~RDI_grp, 
-#                 data = analysis_data) %>% 
-#   tbl_uvregression(y = vitalstatus, exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-
-analysis_data %>% select(vitalstatus, bmi, bmi_cat, raceeth) %>% 
-tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = analysis_data$month_at_os, event = analysis_data$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
-  bold_labels() %>% italicize_levels() #%>%  modify_spanning_header(all_stat_cols() ~ "**Treatment Received**")
-
-tbl1 <- analysis_data %>% 
-  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-tbl1 <- tbl1 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl2 <- analysis_data %>% 
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
-tbl2 <- tbl2 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl3 <- analysis_data %>% 
-  filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
-tbl3 <- tbl3 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>% 
-  bold_labels() %>%
-  italicize_levels()
-# Cisplatin
-tbl4 <- analysis_data %>% 
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
-tbl4 <- tbl4 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl5 <- analysis_data %>% 
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
-tbl5 <- tbl5 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl6 <- analysis_data %>% 
-  filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
-tbl6 <- tbl6 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant", "cisplatin/Chemo only")) %>% 
-  bold_labels() %>%
-  italicize_levels()
-
-tbl7 <- analysis_data %>% 
-  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Neoadjuvant")
-tbl7 <- tbl7 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl8 <- analysis_data %>% 
-  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Adjuvant")
-tbl8 <- tbl8 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
-  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl9 <- analysis_data %>% 
-  filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
-tbl9 <- tbl9 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant", "paclitaxel/Chemo only")) %>% 
-  bold_labels() %>%
-  italicize_levels()
-
-tbl10 <- analysis_data %>% 
-  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
-tbl10 <- tbl10 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl11 <- analysis_data %>% 
-  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
-tbl11 <- tbl11 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
-  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl12 <- analysis_data %>% 
-  filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
-tbl12 <- tbl12 %>% 
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl10, tbl11, tbl12),
-          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>% 
-  bold_labels() %>%
-  italicize_levels()
+#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+# tbl1 <- tbl1 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl2 <- analysis_data %>% 
+#   filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
+# tbl2 <- tbl2 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl3 <- analysis_data %>% 
+#   filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
+# tbl3 <- tbl3 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl_stack(list(tbl1, tbl2, tbl3),
+#           group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>% 
+#   bold_labels() %>%
+#   italicize_levels()
+# # Cisplatin
+# tbl4 <- analysis_data %>% 
+#   filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
+# tbl4 <- tbl4 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl5 <- analysis_data %>% 
+#   filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
+# tbl5 <- tbl5 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl6 <- analysis_data %>% 
+#   filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
+# tbl6 <- tbl6 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl_stack(list(tbl4, tbl5, tbl6),
+#           group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant", "cisplatin/Chemo only")) %>% 
+#   bold_labels() %>%
+#   italicize_levels()
+# 
+# 
+# tbl7 <- analysis_data %>% 
+#   filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Neoadjuvant")
+# tbl7 <- tbl7 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl8 <- analysis_data %>% 
+#   filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Adjuvant")
+# tbl8 <- tbl8 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+#   tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
+#   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+# tbl9 <- analysis_data %>% 
+#   filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
+# tbl9 <- tbl9 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl_stack(list(tbl7, tbl8, tbl9),
+#           group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant", "paclitaxel/Chemo only")) %>% 
+#   bold_labels() %>%
+#   italicize_levels()
+# 
+# tbl10 <- analysis_data %>% 
+#   filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
+# tbl10 <- tbl10 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl11 <- analysis_data %>% 
+#   filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
+# tbl11 <- tbl11 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+#   tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
+#   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+# tbl12 <- analysis_data %>% 
+#   filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
+# tbl12 <- tbl12 %>% 
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
+#                  y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+# tbl_stack(list(tbl10, tbl11, tbl12),
+#           group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>% 
+#   bold_labels() %>%
+#   italicize_levels()
 ```
@@
 # Regression vital status prediction
-model <- glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)
+model <- glm(vitalstatus ~ bmi_at_dx + bmi_cat + #RDI_grp + 
+               raceeth, data = analysis_data, family = binomial)
 tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
@@
 `glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)`
-!!!! Prediction of RDI all drug together!!!!
+<!-- !!!! Prediction of RDI all drug together!!!! -->
 ```{r}
 # Regression RDI prediction
-model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-```
-
-### By drug
-!!! But sometimes we had a switch between cisplatin/carboplatin
+# model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+```
+
+<!-- ### By drug -->
+<!-- !!! But sometimes we had a switch between cisplatin/carboplatin -->
 ```{r}
-#  for carbo
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
-               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
-               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-# tbl5 <- 
-  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
-
-#  for Cisplatim
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
-               filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-model <- glm(RDI_grp ~ agecat + bmi_cat, data = analysis_data %>% 
-               filter(drugname == "cisplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-# tbl5 <- 
-  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**cisplatin/Adjuvant**", "**cisplatin/Neoadjuvant**"))
-
-#  for taxel
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
-               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
-               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-# tbl6 <- 
-  tbl_merge(list(tbl4, tbl3), tab_spanner = c("**taxel/Adjuvant**", "**taxel/Neoadjuvant**"))
+# #  for carbo
+# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+#                filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+# 
+# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+#                filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+# 
+# # tbl5 <- 
+#   tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
+#   
+# #  for Cisplatim
+# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+#                filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+# 
+# model <- glm(RDI_grp ~ agecat + bmi_cat, data = analysis_data %>% 
+#                filter(drugname == "cisplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+# 
+# # tbl5 <- 
+#   tbl_merge(list(tbl3, tbl4), tab_spanner = c("**cisplatin/Adjuvant**", "**cisplatin/Neoadjuvant**"))
+# 
+# #  for taxel
+# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+#                filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+# 
+# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
+#                filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+# 
+# # tbl6 <- 
+#   tbl_merge(list(tbl4, tbl3), tab_spanner = c("**taxel/Adjuvant**", "**taxel/Neoadjuvant**"))
 ```

### 2021-09-09 R/2.data cleaning.R

@@ -30,6 +30,8 @@ creatinine <- creatinine %>%
   fill(creatinine_at_dx, .direction = "updown") %>% 
   select(c(patientid, creat_date = "testdate", creatinine, 
            creat_units = "testunitscleaned", creatinine_at_dx, interval_creat_x))
+write_rds(creatinine, "creatinine.rds")
+
 
 # body_surface_area, height and weight are all coming from vitals
 vitals <- vitals %>% 
@@ -68,6 +70,7 @@ body_surface_area <- vitals %>%
   select(c(patientid, bsa_date = "testdate", BSA, 
            BSA_units, bsa_at_dx, interval_bsa_dx))
 
+write_rds(body_surface_area, "body_surface_area.rds")
 
 #################################################################################################### 3 ### Cleanup of Height----
 height <- vitals %>% 
@@ -152,6 +155,7 @@ height <- vitals %>%
   fill(height_at_dx, .direction = "updown") %>% 
   select(c(patientid, height_date = "testdate", height, 
            height_units, height_at_dx, interval_height_dx))
+write_rds(height, "height.rds")
 
 
 #################################################################################################### 4 ### Cleanup of weight----
@@ -283,6 +287,7 @@ weight <- weight2 %>%
   fill(weight_at_dx, .direction = "updown") %>% 
   select(c(patientid, weight_date = "testdate", weight, 
            weight_units, weight_at_dx, interval_weight_dx))
+write_rds(weight, "weight.rds")
 
 
 rm(weight1, weight2, vitals)
@@ -444,7 +449,8 @@ areaUC <- auc %>%
           "drugname")) %>% 
   filter(!is.na(target_auc))
   
-  
+write_rds(areaUC, "areaUC.rds")
+
   
   
   
@@ -573,6 +579,7 @@ clinical_data <- clinical_data %>%
   filter(month_at_os > 1) %>% # Loss 198 patients
   mutate(stagecat = na_if(stagecat, "Unk Stage")) %>% 
   mutate(across(.cols = c(histology, groupstage, tstage), ~na_if(., "Unknown/not documented")))
+write_rds(clinical_data, "clinical_data.rds")
 
 
 #################################################################################################### II ### Treatment Cleaning----

### 2021-09-10 Rmd/Report 2021.Rmd
update

@@
 At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.  
+- exclude the patients who had surgery but we don't have a date  
+- exclude patients whose histology is unknown  
+- exclude patients who didn't survive 1 month
+
+Also height, weight, bsa, creatinine is cleaned and ready. Creatinine minimum is now capped at 0.7 and not 0.8.  
+Creatinine clearance maximum is capped at 125.
+
+Now drug cleaning!
 
@@
 
+**We start with a number of patient who has drug info of `r drugs %>% distinct(patientid) %>% nrow()`.**
+
+## Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
 ```{r drugs episode cleanup}
@@
 
-Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
-
 ```{r}
@@
 
+## 60 days rule between diagnosis and treatment
 60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded 
@@
 
-Remove linename that doesn't include platin or taxels -> later, need to recode linenumber first
+Remove linename that doesn't include platin or taxels -> later in the process, need first to recode linenumber with all the drugs in.
 ```{r}
@@
 #            !is.na(amount) &
-#            (days_at_drug < 60 | days_at_surg < 60) &
-#            
-#            days_at_drug >= 0 &
+#            (days_at_first_drug < 60 | days_at_surg < 60) &
+#            
+#            days_at_first_drug >= 0 &
 #            (is.na(surgerydate) | days_at_surg >= 0)
@@
 
+## Combine multiple administrations of the same drug at the same date
 ```{r combine amount same drug one day}
@@
   # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
-  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route,
-            diagnosisdate)) %>%
+  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
 
@@
 # Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
-  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_drug, days_at_surg) %>%
+  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg) %>%
   summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
@@
 
-Recode linenumber depending on surgery date
+## Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
 ```{r line coding}
@@
 
-# Number of patient who switch line because of surgery from line 1 to adjuvant line
-```{r line coding}
+## Number of patient who switch line because of surgery from line 1 to adjuvant line
+```{r Number of patient who switch line}
 therapy_line %>% 
@@
 ```
-
-# How many lines patient got as Neo
+## Here I want to plot the lengh of the line 1 which got brought to Adjuvant...
+
+## How many lines patient got as Neo
 ```{r}
@@
 
-# Remove patients with more than 1 line as Neo -34
+## Remove patients with more than 1 line as Neo -34
 ```{r}
@@
 
-# Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
+## Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
 ```{r}
@@
 ```
+
+`r emo::ji("question_mark")`
 
@@
 
-# Code cycle
+## Code cycle
 ```{r cycle coding}
@@
 
-When I bind things together I take the closest date of BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`. it can be days in between or more. Do we need a max?
+When I bind things together I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`.
+it can be days in between or more.
+Do we need a max?
 Precision when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
@@
   # Calculate CrCl
-  # inner_join(., clinical_data %>% select(-c("diagnosisdate", "surgerydate")),
-  #            by = "patientid") %>% 
+  inner_join(., clinical_data %>% select(-surgerydate),
+             by = "patientid") %>% 
   mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
@@
 
-# Number of patients
-```{r}
-Treatment %>% distinct(patientid) %>% nrow()
-```
-
+## We have `r Treatment %>% distinct(patientid) %>% nrow()` patients with drug and clinical info but
+
+## Exclude exclude == "1" coded by Lauren due to Flatiron rule
+
+```{r analysis_data}
+analysis_data <- Treatment %>% 
+  filter(exclude != "1")
+```
+
+# **Number of patients in almost final dataset is `r analysis_data %>% distinct(patientid) %>% nrow()`**
+
+## Explore the dataset
 Number of line in neo
 ```{r}
-Treatment %>% 
+analysis_data %>% 
   filter(chemotherapy_type == "Neoadjuvant") %>% 
@@
 ```{r}
-Treatment %>% 
+analysis_data %>% 
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
@@
 ```{r}
-Treatment %>% 
+analysis_data %>% 
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
@@
 ```
-Number of line in neo
+Number of line in Chemotherapy only
 ```{r}
-Treatment %>% 
+analysis_data %>% 
   filter(chemotherapy_type == "Chemotherapy only") %>% 
@@
 
-# Final dataset
-```{r analysis_data}
-analysis_data <- Treatment %>% 
-  # distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
-  filter(exclude != "1")
-```
-
-After excluding exclude == "1" patients, we have `r analysis_data %>% distinct(patientid) %>% nrow()` patients.
+#
 
@@
 If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
+
+# STOP HERE
 

### 2021-09-15 Rmd/Report 2021.Rmd
Update code

@@
 
-## Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
+### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
 ```{r drugs episode cleanup}
@@
 
-drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()
-drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()
-```
+```
+We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis.
+Patients left :
 
@@
 
-## 60 days rule between diagnosis and treatment
-60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded 
+### step 2: 60 days rule between diagnosis and treatment
+60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded. Patients left :
 ```{r}
@@
 
-Remove linename that doesn't include platin or taxels -> later in the process, need first to recode linenumber with all the drugs in.
+### step 3: 30 days rule excluding patient whith less than 30 days between diagnosis and death
+```{r}
+drugs1 %>% 
+  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
+           duration(n=1, units = "days"), 
+         thirty_days_exclusion = case_when(
+           thirty_days_exclusion <= 30                  ~ "Exclude"
+         )) %>% 
+  filter(thirty_days_exclusion == "Exclude") %>% 
+  distinct(patientid) %>% 
+  nrow
+
+drugs11 <- drugs1 %>% 
+  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
+           duration(n=1, units = "days"), 
+         thirty_days_exclusion = case_when(
+           thirty_days_exclusion <= 30                  ~ "Exclude",
+           thirty_days_exclusion > 30                   ~ "Include",
+           is.na(dateofdeath)                           ~ "Include"
+         )) %>% 
+  filter(thirty_days_exclusion != "Exclude")
+
+drugs11 %>% distinct(patientid) %>% nrow()
+
+```
+In the data, `r drugs1 %>% mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/duration(n=1, units = "days"), thirty_days_exclusion = case_when(thirty_days_exclusion <= 30~ "Exclude")) %>% filter(thirty_days_exclusion == "Exclude") %>% distinct(patientid) %>% nrow` are excluded so we still have `r drugs11 %>% distinct(patientid) %>% nrow()` patients.
+
+### step 3: Remove linename that doesn't include platin or taxels in first line -> later in the process, need first to recode linenumber with all the drugs in.
 ```{r}
@@
 
-## Combine multiple administrations of the same drug at the same date
+### step 4: Combine multiple administrations of the same drug at the same date
 ```{r combine amount same drug one day}
@@
 
-## Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
+### step 5: Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
 ```{r line coding}
@@
 
-## Number of patient who switch line because of surgery from line 1 to adjuvant line
+### step 6: Remove linename that doesn't include platin or taxels in first line
+```{r}
+# F0017FB3A8828 starts with gemcitabine then have carbo
+therapy_line <- therapy_line %>%
+  arrange(patientid, episodedate) %>% 
+  mutate(remove_linename_other = case_when(
+    linenumber_new == 1 &
+      str_detect(linename, "platin|taxel")      ~ "keep",
+    linenumber_new == 1 &
+      !str_detect(linename, "platin|taxel")     ~ "remove",
+  )) %>% 
+  group_by(patientid) %>% 
+  fill(remove_linename_other, .direction = "down") %>% 
+  ungroup() %>% 
+  filter(remove_linename_other == "keep") %>% 
+  select(-remove_linename_other)
+
+therapy_line %>% 
+  filter(linenumber_new == 1) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linename) %>% 
+  tbl_summary(sort = list(everything() ~ "frequency"))
+
+therapy_line %>% distinct(patientid) %>% nrow()
+```
+
+We now have `r therapy_line %>% distinct(patientid) %>% nrow()` patients.
+
+#### Number of patient who switch line because of surgery from line 1 to adjuvant line
 ```{r Number of patient who switch line}
@@
   tbl_summary()
-```
-## Here I want to plot the lengh of the line 1 which got brought to Adjuvant...
-
-## How many lines patient got as Neo
+
+# Problem F0000AD999ABF but would be good for F003F2BEEDB37
+therapy_line %>% 
+  filter(str_detect(patientid, "F0000AD999ABF|F003F2BEEDB37")) %>% 
+  arrange(patientid, episodedate) %>% 
+  select(patientid, linenumber, linenumber_new, episodedate, chemotherapy_type)
+
+therapy_line %>% 
+  mutate(change_line = case_when(
+    linenumber == 1 & 
+      linenumber_new == 2 &
+      chemotherapy_type == "Adjuvant" &
+      treatment_sequence == "neo + surg + adj"     ~ 1,
+    TRUE                                           ~ 0
+  )) %>% 
+  filter(change_line == 1) %>% 
+  group_by(patientid) %>% 
+  mutate(firstdate = first(episodedate)) %>% 
+  mutate(lastdate = last(episodedate)) %>% 
+  ungroup() %>% 
+  mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x=time_of_switch_line, fill = ..count..))+
+  geom_histogram(binwidth = 7)+
+  theme_minimal()+
+  ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
+  scale_y_continuous(#breaks=c(0, 50, 100, 150),
+                     minor_breaks=c(10, 20, 30, 40)#,
+                     #labels = c(0, 50, 100, 150)
+  )
+```
+
+#### How many lines patient got as Neo
 ```{r}
@@
 
-## Remove patients with more than 1 line as Neo -34
+### step 7: Remove patients with more than 1 line as Neo -34
 ```{r}
@@
 
-## Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
+### step 8: Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
 ```{r}
@@
 
-Should I do the same between paclitaxel and docetaxel? Remember I pacli == pacli protein bound
-
-If a patient had carbo, pacli, carbo, pacli, docetaxel in a Cabo-Pacli line : Could be annoying when I code cycle
-
-In 1 cycle we can have taxel multiple times, is it possible for carbo or cisplatin?
+<span style="color:red">**Should I do the same between paclitaxel and docetaxel?**</span>
+
+Remember that I coded "paclitaxel" == "paclitaxel protein bound"
+
+If a patient had carbo, pacli, carbo, pacli, docetaxel in a Carboplatin-Paclitaxel line : It makes the coding for cycle number more difficult
+
+I think it would be worth it and this operation would remove these patients:
+
 ```{r}
@@
 ```
-
-## Code cycle
+<br>
+
+`r emo::ji("question_mark")`  
+<span style="color:red">**Random question : within 1 cycle we can have taxel multiple times, is it possible for carboplatin or cisplatin?**</span>
+
+<br>
+
+### step 9: Code cycle
 ```{r cycle coding}
@@
 
-## Bind everything together and calculating target_auc and expected dose
-
-When I bind things together I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`.
-it can be days in between or more.
-Do we need a max?
+### step 10: Bind everything together and calculating target_auc and expected dose
+
+When I bind things together I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`. it can be days in between or more. 
+`r emo::ji("question_mark")`  
+<span style="color:red">**Do we need a maximun?**</span>
+
+As you can see on the plots, the gap can be pretty big so :  
+<span style="color:red">**Can we take a creatinine value to bind it to a drug when a year long as past between each other?**</span>  
+<span style="color:red">**Same question for height, weight, bsa and corresponding AUC**</span>
+
 Precision when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
@@
 
-## Exclude exclude == "1" coded by Lauren due to Flatiron rule
+### step 11: Exclude exclude == "1" coded by Lauren due to Flatiron rule
 
@@
 
-# STOP HERE
-
 # CALCULATE RDI
 
+`r emo::ji("question_mark")`  
+<span style="color:red">**I need confirmation : we calculate 1 RDI per drug per patient for the first (unique) line of neoadjuvant and 1 RDI per drug per patient for the ALL the lines of adjuvant which are not maintenance.
+Is that correct**</span>
+
+## Calculate RDI by drug by cycle by patient
+Here few examples
+```{r, rows.print=15, max.print=30}
+Frontline <- Treatment %>% 
+  # Calculate RDI for each drug per cycle per patients
+  mutate(relative_dose_intensity = amount/expected_dose) %>% 
+  group_by(patientid, linenumber_new, cycle_drugname,  chemotherapy_type, linestartdate, lineenddate, cycle_increment) %>% 
+  summarise(across(relative_dose_intensity, mean, na.rm = TRUE))
+
+Frontline
+```
+
+## Calculate RDI by drug by line by patient
+Here few examples
+```{r, rows.print=15, max.print=30}
+Frontline <- Frontline %>% 
+  # Calculate RDI for each drug per line per patients
+  group_by(patientid, linenumber_new, cycle_drugname,  chemotherapy_type, linestartdate, lineenddate) %>% 
+  summarise(across(relative_dose_intensity, mean, na.rm = TRUE))
+
+Frontline
+```
+
+## Calculate RDI by drug by patient
+Here few examples
+```{r, rows.print=15, max.print=30}
+Frontline <- Frontline %>% 
+  # Calculate RDI for each drug per patients
+  group_by(patientid, cycle_drugname, chemotherapy_type) %>% 
+  summarise(across(relative_dose_intensity, mean, na.rm = TRUE)) %>% 
+  ungroup()
+
+Frontline
+
+Frontline %>% 
+  ggplot(aes(x = relative_dose_intensity, fill = cycle_drugname))+
+  geom_histogram(alpha = 0.5)+
+  theme_minimal()+
+  facet_wrap(.~ chemotherapy_type, scales = "free")
+
+Frontline %>% 
+  ggplot(aes(x = relative_dose_intensity, y = chemotherapy_type, fill = cycle_drugname))+
+  geom_boxplot()+
+  geom_vline(xintercept = 1, color = "red")+
+  theme_minimal()
+```
+
 ```{r}
-Frontline <- Treatment %>% 
-  # filter(therapy == "Upfront Chemo" | therapy == "Chemotherapy only") %>% 
-  # group_by(patientid, linenumber_new, cycle_increment, drugname) %>% # ! -----------------------Change drugname if combine taxel....
-  # mutate(amount_cycle = sum(amount)) %>% 
-  # select(patientid, linenumber_new, cycle_increment, drugname, amount, amount_cycle, 
-  #        target_auc, expected_dose, everything()) %>% # F01E4E6DD63C5, F1FA39C41A087 ----------- No we have xpected dose for each episode
-  # ungroup() %>% 
-  # distinct(patientid, linenumber_new, cycle_increment, drugname, .keep_all = TRUE) %>%
-
-  # Create a linenumber restating at 1 for adj to be able to calculate RDI for first line of Adjuvant
-    group_by(patientid, chemotherapy_type) %>% 
-  mutate(linenumber_adj = dense_rank(linenumber_new)) %>%
-
-  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
-  mutate(relative_dose_intensity = case_when(
-    chemotherapy_type == "Adjuvant" &
-      linenumber_adj == 1                  ~ amount/expected_dose,
-    chemotherapy_type == "Neoadjuvant"     ~ amount/expected_dose
+Frontline <- Frontline %>%
+
+  mutate(RDI_grp = case_when(
+    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
+    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85"
   )) %>% 
-  # select(patientid, linenumber_new, chemotherapy_type, drugname_type, drugname,
-  #        relative_dose_intensity, linenumber_adj) %>%
-
-  # Average RDI by taxel or platin by line (will combine pacli-doce and cis-carbo-oxalo)
-  group_by(patientid, chemotherapy_type, drugname_type) %>%
-  mutate(mean_RDI_per_chemotype_drug = case_when(
-    chemotherapy_type == "Adjuvant" &
-      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
-    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  mutate(RDI_grp = factor(RDI_grp, 
+                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
+  mutate(RDI_grp1 = case_when(
+    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
+    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85",
+    relative_dose_intensity >= 0.85         ~ "0.85 <= RDI < 1",
+    relative_dose_intensity >= 0.85         ~ "1 <= RDI < 1.5",
+    relative_dose_intensity >= 0.85         ~ "1.5 <= RDI < 2",
+    relative_dose_intensity >= 0.85         ~ "RDI >= 2",
   )) %>% 
-  ungroup() %>%
-
-  # Then let's see if we need to average that for the whole Neo BUT 
-  # For now average rdi over whole neo, average rdi for the first line over adjuvant
-  # when plot meed 1 rdi per drugname_type per chemotherapy_type aka distinct(patientid, chemotherapy_type, drugname_type)
-
-  # group_by(patientid, chemotherapy_type, drugname_type) %>% 
-  # mutate(RDI_neo = case_when(
-  #   # chemotherapy_type == "Adjuvant"       ~ first(mean_RDI_per_drug_line), # F002B429BE6C6
-  #   chemotherapy_type == "Adjuvant" &
-  #     linenumber_adj == 1                  ~ mean(mean_RDI_per_drug_line),
-  #   chemotherapy_type == "Neoadjuvant"     ~ mean(mean_RDI_per_drug_line) # F0040EA299CF0
-  # )) %>%
-
-  # mutate(RDI_adj = case_when(
-  #   chemotherapy_type == "Adjuvant" &
-  #     linenumber_adj == 1                  ~ mean(mean_RDI_per_drug_line), # F002B429BE6C6
-  #   # chemotherapy_type == "Neoadjuvant"     ~ mean(mean_RDI_per_drug_line) # F0040EA299CF0
-  # )) %>% 
-  # mutate(RDI = coalesce(RDI_neo, RDI_adj))
-
-  # group_by(patientid, chemotherapy_type, drugname) %>% # ------------------------ Or should I do by cycle, then avg again
-  # mutate(mean_RDI_per_drug_chemotype = mean(relative_dose_intensity)) %>% 
-  # ungroup() %>% 
-  mutate(RDI_grp = as.factor(findInterval(mean_RDI_per_chemotype_drug, c(0.85) ))) %>% 
-  mutate(RDI_grp = factor(RDI_grp, 
-                           levels = c("1", "0"), 
-                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
-  mutate(RDI_grp1 = as.factor(findInterval(mean_RDI_per_chemotype_drug, c(0.75, 0.85, 1, 1.5, 2) ))) %>% 
   mutate(RDI_grp1 = factor(RDI_grp1, 
-                          levels = c("3", "0", "1","2","4", "5"), 
                           labels = c("0.85 >= RDI < 1", "0 < RDI < 0.75", "0.75 <= RDI < 0.85", "1 <= RDI < 1.5", 
@@
   # )) %>% 
-  group_by(patientid) %>% 
-  mutate(first_treatment_date = case_when(
-    str_detect(therapy, "Chemo")                      ~ min(episodedate),
-    str_detect(therapy, "Surgery")                    ~ surgerydate,
-  )) %>% 
-  mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
-                                          duration(n=1, units = "days")) %>% 
+  # group_by(patientid) %>% 
+  # mutate(first_treatment_date = case_when(
+  #   str_detect(therapy, "Chemo")                      ~ min(episodedate),
+  #   str_detect(therapy, "Surgery")                    ~ surgerydate,
+  # )) %>% 
+  # mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
+  #                                         duration(n=1, units = "days")) %>% 
   mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                    duration(n=1, units = "months")) %>% 
-  ungroup() %>% 
-  # %>% 
-  # select(patientid, linenumber_new, drugname, surgerydate, episodedate, treatment_sequence, first_treatment_date, month_at_os_from_treatment)
-  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
-           duration(n=1, units = "days"), 
-         thirty_days_exclusion = ifelse(thirty_days_exclusion <= 30, "Exclude", NA_character_))
-
-```
+  ungroup()
+
+```
+
+# STOP HERE
 

### 2021-09-16 Rmd/Report 2021.Rmd
Fix bug

@@
     relative_dose_intensity < 0.85          ~ "RDI < 0.85",
-    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85",
-    relative_dose_intensity >= 0.85         ~ "0.85 <= RDI < 1",
-    relative_dose_intensity >= 0.85         ~ "1 <= RDI < 1.5",
-    relative_dose_intensity >= 0.85         ~ "1.5 <= RDI < 2",
-    relative_dose_intensity >= 0.85         ~ "RDI >= 2",
+    # relative_dose_intensity >= 0.85         ~ "RDI >= 0.85",
+    relative_dose_intensity >= 0.85 &
+      relative_dose_intensity <= 1          ~ "0.85 <= RDI <= 1",
+    relative_dose_intensity > 1 &
+      relative_dose_intensity <= 1.5        ~ "1 < RDI <= 1.5",
+    relative_dose_intensity > 1.5 &
+      relative_dose_intensity <= 2          ~ "1.5 < RDI <= 2",
+    relative_dose_intensity > 2             ~ "RDI > 2",
   )) %>% 
   mutate(RDI_grp1 = factor(RDI_grp1, 
-                          labels = c("0.85 >= RDI < 1", "0 < RDI < 0.75", "0.75 <= RDI < 0.85", "1 <= RDI < 1.5", 
-                                     "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
+                          labels = c("RDI < 0.85", 
+                                     "0.85 >= RDI <= 1", 
+                                     "1 < RDI <= 1.5", 
+                                     "1.5 < RDI <= 2", 
+                                     "RDI > 2"))) %>% 
   # mutate(delay_incare_dx_to_treat = case_when(
@@
   # )) %>% 
-  # group_by(patientid) %>% 
-  # mutate(first_treatment_date = case_when(
-  #   treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
-  #   str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
-  #   treatment_sequence == "surg + adj"                    ~ surgerydate,
-  #   treatment_sequence == "Surgery only"                  ~ surgerydate
-  # )) %>% 
+  left_join(., Treatment) %>% 
+  group_by(patientid) %>%
+  mutate(first_treatment_date = case_when(
+    treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
+    str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
+    treatment_sequence == "surg + adj"                    ~ surgerydate,
+    treatment_sequence == "Surgery only"                  ~ surgerydate
+  )) %>%
   # group_by(patientid) %>% 
@@
   analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
-  filter(exclude != "1") %>% 
   select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,

### 2021-09-16 Rmd/Report 2021.Rmd
Update report, fix bug and add viz

@@
 
-drugs1 %>% 
-  filter(linenumber == 1) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename) %>% 
-  tbl_summary(sort = list(everything() ~ "frequency"))
+# drugs1 %>% 
+#   filter(linenumber == 1) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(linename) %>% 
+#   tbl_summary(sort = list(everything() ~ "frequency"))
 ```
@@
 
-# **Number of patients in almost final dataset is `r analysis_data %>% distinct(patientid) %>% nrow()`**
+## **Number of patients in final dataset is `r analysis_data %>% distinct(patientid) %>% nrow()`**
+
+<br>
+
+***
+
+<br>
 
@@
 ```{r, rows.print=15, max.print=30}
-Frontline <- Treatment %>% 
+analysis_data <- analysis_data %>% 
   # Calculate RDI for each drug per cycle per patients
@@
 
-Frontline
+analysis_data
 ```
@@
 ```{r, rows.print=15, max.print=30}
-Frontline <- Frontline %>% 
+analysis_data <- analysis_data %>% 
   # Calculate RDI for each drug per line per patients
@@
 ```{r, rows.print=15, max.print=30}
-Frontline <- Frontline %>% 
+analysis_data <- analysis_data %>% 
   # Calculate RDI for each drug per patients
@@
 
-Frontline
-
-Frontline %>% 
+analysis_data
+
+analysis_data %>% 
   ggplot(aes(x = relative_dose_intensity, fill = cycle_drugname))+
@@
 
-Frontline %>% 
+analysis_data %>% 
   ggplot(aes(x = relative_dose_intensity, y = chemotherapy_type, fill = cycle_drugname))+
@@
 ```{r}
-Frontline <- Frontline %>%
+analysis_data <- analysis_data %>%
 
@@
 
-# STOP HERE
-
 # Analysis
@@
 ```{r Table 1}
-
-# How should I filter??????????????????///
 analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
@@
            "bmi_at_dx", bmi_cat, "BSA",
-
-           "histology", "groupstage", "tstage", "stagecat",
+           "stagecat",
 
@@
 # OS by race
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=analysis_data),
+#            title = "OS from date of diagnosis", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 # OS by histology
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=analysis_data %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of diagnosis", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 # OS by race
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=analysis_data %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of first treatment", 
@@
 # OS by histology
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ histology, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ histology, data=analysis_data %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of first treatment", 
@@
 ***
+
+<br>
+
 # II.Analysis Treatment
@@
            had_neo, had_adj,
-           "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
+           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
            )) %>% 
@@
 #            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
-#            "chemotherapy_type", "therapy", "treatment_sequence"#, "mean_RDI_per_drug_chemotype", "RDI_grp"
+#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
 #            )) %>% 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ chemotherapy_type, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of diagnosis", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of from first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of from first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of from first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ chemotherapy_type, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of from first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of from first treatment", 
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE) %>% 
-                     filter(exclude != "1")),
+                     distinct(patientid, .keep_all = TRUE)),
            title = "OS from date of from first treatment", 
@@
 ***
+
+<br>
+
 # III.RDI
@@
 
-# Frontline %>% group_by(chemotherapy_type, drugname) %>% summarize(average_RDI =mean(mean_RDI_per_drug_chemotype, na.rm = TRUE)) 
-# 
-# # Treatment & demo
-# tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(raceeth,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(bmi_cat,  "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug_chemotype ~ "carb/adjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl3 <- 
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug_chemotype ~ "carb/neoadjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl4 <- 
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/adjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl5 <- 
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = raceeth,
-#               type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
-#               label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = bmi_cat,
-#               type = list(mean_RDI_per_drug_chemotype ~ 'continuous'),
-#               label = list(mean_RDI_per_drug_chemotype ~ "cisplatin/neoadjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl6 <- 
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
-# 
-# 
-# 
-# tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug_chemotype ~ "taxel/adjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl5 <- 
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(raceeth, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>% 
-#   filter(exclude != "1") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(bmi_cat, "mean_RDI_per_drug_chemotype", RDI_grp)) %>% 
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug_chemotype ~ "taxel/neoadjuvant \nRDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl6 <- 
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl_stack(list(tbl5, tbl6), quiet = TRUE)
+# Treatment & demo
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl3 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl4 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              type = list(relative_dose_intensity ~ 'continuous'),
+              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              type = list(relative_dose_intensity ~ 'continuous'),
+              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl5, tbl6), quiet = TRUE)
 ```
@@
 
+# CAN TAKE A LOOK BUT NEED TO VERIFY ALL THE REST
+
+<br>
+
+***
+
+<br>
+
 ## 2.Plots RDI
-For RDI boxplot and violin, it is calculated for neoadjuvant and adjuvant when a patient got both (need to find another way of plotting to do by drug - maybe a wrap).
 
@@
 ```{r}
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
-#   geom_boxplot()+
-#   ylim(c(-.25, 3.5))+
-#   geom_jitter(shape=16)+
-#   labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
-#   theme_minimal()
-# 
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   # filter(linenumber_new == "1") %>% 
-#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
-#   geom_violin()+
-#   ylim(c(-.25, 3.5))+
-#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-#   theme_minimal()
-# 
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   # filter(linenumber_new == "1") %>% 
-#   ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
-#   geom_violin()+
-#   ylim(c(-.25, 3.5))+
-#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-#   theme_minimal()+
-#   coord_flip()
-# 
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   # filter(linenumber_new == "1") %>% 
-#   ggplot(aes(x= RDI_grp, fill = drugname))+
-#   geom_bar()+
-#   theme_minimal()+
-#   coord_flip()
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  geom_boxplot()+
+  ylim(c(-.25, 3.5))+
+  geom_jitter(shape=16)+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal()+
+  facet_wrap(.~ cycle_drugname)
+
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  geom_violin()+
+  ylim(c(-.25, 3.5))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()
+
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= cycle_drugname, y= relative_dose_intensity, color = chemotherapy_type))+
+  geom_violin()+
+  ylim(c(-.25, 3.5))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()+
+  coord_flip()
+
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
+  geom_bar()+
+  theme_minimal()+
+  facet_wrap(.~ chemotherapy_type)
 
@@
 ```{r}
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  # geom_boxplot()+
+  ylim(c(-.25, 3.5))+
+  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal() +
+  guides(color=FALSE)+
+  facet_wrap(.~ cycle_drugname)
+
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = relative_dose_intensity<0.85))+
+  geom_violin()+
+  ylim(c(-.25, 2.5))+
+  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()+
+  facet_wrap(.~ cycle_drugname)
+
+# analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
 #   # filter(linenumber_new == "1") %>%
-#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+
-#   # geom_boxplot()+
-#   ylim(c(-.25, 3.5))+
-#   geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-#   labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
-#   theme_minimal() +
-#   guides(color=FALSE)
-# 
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   # filter(linenumber_new == "1") %>% 
-#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, color = mean_RDI_per_drug_chemotype<0.85))+
-#   geom_violin()+
+#   ggplot(aes(x= cycle_drugname, y= relative_dose_intensity))+
+#   geom_violin(aes(color=relative_dose_intensity<0.85))+
 #   ylim(c(-.25, 2.5))+
 #   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
+#   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
 #   theme_minimal()
-# 
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   # filter(linenumber_new == "1") %>% 
-#   ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+
-#   geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+
-#   ylim(c(-.25, 2.5))+
-#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-#   theme_minimal()+
-#   coord_flip()
-# 
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   # filter(linenumber_new == "1") %>% 
-#   ggplot(aes(x= RDI_grp, fill = drugname))+
-#   geom_bar(position = "fill")+
-#   theme_minimal()+
-#   coord_flip()
-#
+
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  facet_wrap(.~ chemotherapy_type)
 
@@
 ```{r}
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   # filter(linenumber_new == "1") %>% 
-#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype, alpha = mean_RDI_per_drug_chemotype<0.85))+
-#   geom_violin(aes(fill = drugname))+
-#   ylim(c(-.25, 2.5))+
-#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+
-#   theme_minimal()
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, alpha = relative_dose_intensity<0.85))+
+  geom_violin(aes(fill = cycle_drugname))+
+  ylim(c(-.25, 2.5))+
+  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()+
+  facet_wrap(.~ raceeth)
 ```
@@
 ```{r}
-# analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
-# summary(analysis_data2$mean_RDI_per_drug_chemotype)
+analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
+summary(analysis_data2$relative_dose_intensity)
 ```
@@
 ```{r}
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   # filter(linenumber_new == "1") %>% 
-#   ggplot(aes(x= RDI_grp1, fill = drugname))+
-#   geom_bar()+
-#   theme_minimal()+
-#   coord_flip()
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
+  geom_bar()+
+  theme_minimal()+
+  facet_wrap(.~ chemotherapy_type)
 ```
@@
 ```{r}
-# analysis_data %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>%
-#   # filter(linenumber_new == "1") %>% 
-#   ggplot(aes(x= RDI_grp1, fill = drugname))+
-#   geom_bar(position = "fill")+
-#   theme_minimal()+
-#   coord_flip()
+analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  coord_flip()+
+  facet_wrap(.~ chemotherapy_type)
 ```
@@
 ```{r, fig.height = 7}
-# # OS by RDI_grp for platin
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "carboplatin"),
-#                             str_detect(chemotherapy_type, "Neoadjuvant")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from first treatment carboplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "cisplatin"),
-#                             str_detect(chemotherapy_type, "Neoadjuvant")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from first treatment cisplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for taxel
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "taxel"),
-#                             str_detect(chemotherapy_type, "Neoadjuvant")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from from first treatment all taxel", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
+                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
+                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from first treatment carboplatin",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
+                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
+                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from first treatment cisplatin",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by RDI_grp for taxel
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
+                     filter((exclude != "1") & str_detect(drugname, "taxel"),
+                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from from first treatment all taxel",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
 ```
@@
 ```{r, fig.height = 7}
-# # OS by RDI_grp for platin
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "carboplatin"),
-#                             str_detect(chemotherapy_type, "Adjuvant")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from first treatment carboplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "cisplatin"),
-#                             str_detect(chemotherapy_type, "Adjuvant")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from first treatment cisplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for taxel
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "taxel"),
-#                             str_detect(chemotherapy_type, "Adjuvant")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from from first treatment all taxel", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
+                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
+                            str_detect(chemotherapy_type, "Adjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from first treatment carboplatin",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
+                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
+                            str_detect(chemotherapy_type, "Adjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from first treatment cisplatin",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by RDI_grp for taxel
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
+                     filter((exclude != "1") & str_detect(drugname, "taxel"),
+                            str_detect(chemotherapy_type, "Adjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from from first treatment all taxel",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
 ```
@@
 ```{r Table 5 HR}
-# # tbl1 <- analysis_data %>% 
-# #   select(bmi_cat) %>% 
-# #   tbl_summary(#by = vitalstatus,
-# #               statistic = all_categorical() ~ "{analysis_data %>% filter(vital == 'Dead') %>% NROW()} death ({n})"
-# #               )
-# # tbl2 <- coxph(Surv(time = month_at_os,
-# #                      event = vitalstatus)~bmi_cat,
-# #                 data = analysis_data) %>%
-# #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# # 
-# # tbl_merge(list(tbl1, tbl2))
-# # 
-# # coxph(Surv(time = month_at_os, 
-# #                      event = vitalstatus)~RDI_grp, 
-# #                 data = analysis_data) %>% 
-# #   tbl_uvregression(y = vitalstatus, exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# 
+# tbl1 <- analysis_data %>%
+#   select(bmi_cat) %>%
+#   tbl_summary(#by = vitalstatus,
+#               statistic = all_categorical() ~ "{analysis_data %>% filter(vital == 'Dead') %>% NROW()} death ({n})"
+#               )
+# tbl2 <- coxph(Surv(time = month_at_os,
+#                      event = vitalstatus)~bmi_cat,
+#                 data = analysis_data) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+#
+# tbl_merge(list(tbl1, tbl2))
+#
+# coxph(Surv(time = month_at_os,
+#                      event = vitalstatus)~RDI_grp,
+#                 data = analysis_data) %>%
+#   tbl_uvregression(y = vitalstatus, exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
 # analysis_data %>% select(vitalstatus, bmi, bmi_cat, raceeth) %>%
@@
 #   bold_labels() %>% italicize_levels() #%>%  modify_spanning_header(all_stat_cols() ~ "**Treatment Received**")
-# 
-# tbl1 <- analysis_data %>% 
-#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-# tbl1 <- tbl1 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl2 <- analysis_data %>% 
-#   filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
-# tbl2 <- tbl2 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl3 <- analysis_data %>% 
-#   filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
-# tbl3 <- tbl3 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl_stack(list(tbl1, tbl2, tbl3),
-#           group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>% 
-#   bold_labels() %>%
-#   italicize_levels()
-# # Cisplatin
-# tbl4 <- analysis_data %>% 
-#   filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
-# tbl4 <- tbl4 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl5 <- analysis_data %>% 
-#   filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
-# tbl5 <- tbl5 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl6 <- analysis_data %>% 
-#   filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
-# tbl6 <- tbl6 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl_stack(list(tbl4, tbl5, tbl6),
-#           group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant", "cisplatin/Chemo only")) %>% 
-#   bold_labels() %>%
-#   italicize_levels()
-# 
-# 
-# tbl7 <- analysis_data %>% 
-#   filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Neoadjuvant")
-# tbl7 <- tbl7 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl8 <- analysis_data %>% 
-#   filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Adjuvant")
-# tbl8 <- tbl8 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% 
-#   tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
-#   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-# tbl9 <- analysis_data %>% 
-#   filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
-# tbl9 <- tbl9 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl_stack(list(tbl7, tbl8, tbl9),
-#           group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant", "paclitaxel/Chemo only")) %>% 
-#   bold_labels() %>%
-#   italicize_levels()
-# 
-# tbl10 <- analysis_data %>% 
-#   filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
-# tbl10 <- tbl10 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl11 <- analysis_data %>% 
-#   filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
-# tbl11 <- tbl11 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% 
-#   tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>% 
-#   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-# tbl12 <- analysis_data %>% 
-#   filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
-# tbl12 <- tbl12 %>% 
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph, 
-#                  y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl_stack(list(tbl10, tbl11, tbl12),
-#           group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>% 
-#   bold_labels() %>%
-#   italicize_levels()
+
+tbl1 <- analysis_data %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+tbl1 <- tbl1 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl2 <- analysis_data %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
+tbl2 <- tbl2 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl3 <- analysis_data %>%
+  filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
+tbl3 <- tbl3 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>%
+  bold_labels() %>%
+  italicize_levels()
+# Cisplatin
+tbl4 <- analysis_data %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
+tbl4 <- tbl4 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl5 <- analysis_data %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
+tbl5 <- tbl5 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl6 <- analysis_data %>%
+  filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
+tbl6 <- tbl6 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl4, tbl5, tbl6),
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant", "cisplatin/Chemo only")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+tbl7 <- analysis_data %>%
+  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Neoadjuvant")
+tbl7 <- tbl7 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl8 <- analysis_data %>%
+  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Adjuvant")
+tbl8 <- tbl8 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+tbl9 <- analysis_data %>%
+  filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
+tbl9 <- tbl9 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl7, tbl8, tbl9),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant", "paclitaxel/Chemo only")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+tbl10 <- analysis_data %>%
+  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
+tbl10 <- tbl10 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl11 <- analysis_data %>%
+  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
+tbl11 <- tbl11 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+tbl12 <- analysis_data %>%
+  filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
+tbl12 <- tbl12 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl10, tbl11, tbl12),
+          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>%
+  bold_labels() %>%
+  italicize_levels()
 ```
@@
 model <- glm(vitalstatus ~ bmi_at_dx + bmi_cat + #RDI_grp + 
-               raceeth, data = analysis_data, family = binomial)
+               raceeth, data = analysis_data %>% 
+               distinct(patientid, .keep_all = TRUE), 
+             family = binomial)
 tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
@@
              chemotherapy_type, 
-             data = analysis_data, family = binomial)
+             data = analysis_data %>% 
+               distinct(patientid, .keep_all = TRUE), 
+             family = binomial)
 tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
@@
 
-<!-- ### By drug -->
+### By drug
 <!-- !!! But sometimes we had a switch between cisplatin/carboplatin -->
 ```{r}
-# #  for carbo
-# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
-#                filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-# 
-# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
-#                filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-# 
-# # tbl5 <- 
-#   tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
-#   
-# #  for Cisplatim
+#  for carbo
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
+               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
+               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# tbl5 <-
+  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
+
+#  for Cisplatim
 # model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
@@
 # tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-# 
+
 # model <- glm(RDI_grp ~ agecat + bmi_cat, data = analysis_data %>%
@@
 #   tbl_merge(list(tbl3, tbl4), tab_spanner = c("**cisplatin/Adjuvant**", "**cisplatin/Neoadjuvant**"))
-# 
-# #  for taxel
-# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
-#                filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-# 
-# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>% 
-#                filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-# 
-# # tbl6 <- 
-#   tbl_merge(list(tbl4, tbl3), tab_spanner = c("**taxel/Adjuvant**", "**taxel/Neoadjuvant**"))
+
+#  for taxel
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
+               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
+               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# tbl6 <-
+  tbl_merge(list(tbl4, tbl3), tab_spanner = c("**taxel/Adjuvant**", "**taxel/Neoadjuvant**"))
 ```
@@
 ***
-
-<!-- <div class = "row"> -->
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-
-<!-- ``` -->
-<!-- </div> -->
-
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-
-<!-- ``` -->
-<!-- </div> -->
-<!-- </div> -->
-
-<!-- ## Extra plots all line together -->
-
-<!-- <div class = "row"> -->
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-<!-- analysis_data %>% -->
-<!--   filter(exclude != "1") %>%  -->
-<!--   ggplot(aes(x= therapy))+ -->
-<!--   geom_bar()+ -->
-<!--   theme_minimal()+ -->
-<!--   labs(title = "Frontline treatment")+ -->
-<!--   coord_flip() -->
-
-<!-- analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>%  -->
-<!--   filter(exclude != "1") %>%  -->
-<!--   group_by(chemotherapy_type) %>%  -->
-<!--   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>% -->
-<!--   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+ -->
-<!--   geom_bar(stat="identity")+ -->
-<!--   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") + -->
-<!--   theme_minimal()+ -->
-<!--   guides(fill = FALSE) + -->
-<!--   coord_flip() -->
-<!-- ``` -->
-<!-- </div> -->
-
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-<!-- analysis_data %>% arrange(episodedate) %>% distinct(patientid, .keep_all = TRUE) %>%  -->
-<!--   filter(exclude != "1") %>%  -->
-<!--   group_by(treatment_sequence) %>%  -->
-<!--   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>% -->
-<!--   ggplot(aes(x= treatment_sequence, y= percent, fill = treatment_sequence))+ -->
-<!--   geom_bar(stat="identity")+ -->
-<!--   labs(x = "", title = "The treatment_sequence") + -->
-<!--   theme_minimal()+ -->
-<!--   guides(fill = FALSE) + -->
-<!--   coord_flip() -->
-
-<!-- # analysis_data %>% distinct(patientid, .keep_all = TRUE) %>%  -->
-<!-- #   ggplot(aes(x= chemo))+ -->
-<!-- #   geom_bar()+ -->
-<!-- #   theme_minimal()+ -->
-<!-- #   coord_flip() -->
-<!-- ``` -->
-<!-- </div> -->
-<!-- </div> -->
-
-<!-- <div class = "row"> -->
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-<!-- # What are the RDI distribution for each type of chemo -->
-<!-- print("A quick summary for the RDI repartition") -->
-<!-- summary(analysis_data$mean_RDI_per_drug_chemotype) -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
-<!--   filter(exclude != "1") %>%  -->
-<!--   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+ -->
-<!--   geom_boxplot()+ -->
-<!--   geom_jitter(shape=16)+ -->
-<!--   labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") + -->
-<!--   theme_minimal() -->
-<!-- ``` -->
-<!-- </div> -->
-
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
-<!--   filter(exclude != "1") %>%  -->
-<!--   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+ -->
-<!--   # geom_boxplot()+ -->
-<!--   ylim(c(-.5, 3.5))+ -->
-<!--   geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+ -->
-<!--   labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") + -->
-<!--   theme_minimal() + -->
-<!--   guides(color=FALSE) -->
-
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
-<!--   filter(exclude != "1") %>%  -->
-<!--   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug_chemotype))+ -->
-<!--   geom_violin()+ -->
-<!--   ylim(c(-.5, 3.5))+ -->
-<!--   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+ -->
-<!--   theme_minimal() -->
-<!-- ``` -->
-<!-- </div> -->
-<!-- </div> -->
-
-<!-- <div class = "row"> -->
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-<!-- # What are the RDI distribution for each drug -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
-<!--   filter(exclude != "1") %>%  -->
-<!--   ggplot(aes(x= drugname, y= mean_RDI_per_drug_chemotype))+ -->
-<!--   geom_violin(aes(color=mean_RDI_per_drug_chemotype<0.85))+ -->
-<!--   ylim(c(-.5, 5.5))+ -->
-<!--   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug_chemotype<0.85))+ -->
-<!--   theme_minimal()+ -->
-<!--   coord_flip() -->
-
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
-<!--   filter(exclude != "1") %>%  -->
-<!--   ggplot(aes(x= RDI_grp, fill = drugname))+ -->
-<!--   geom_bar()+ -->
-<!--   theme_minimal()+ -->
-<!--   coord_flip() -->
-<!-- ``` -->
-<!-- </div> -->
-
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug_chemotype)) %>% -->
-<!--   filter(exclude != "1") %>%  -->
-<!--   ggplot(aes(x= RDI_grp, fill = drugname))+ -->
-<!--   geom_bar(position = "fill")+ -->
-<!--   theme_minimal()+ -->
-<!--   coord_flip() -->
-<!-- ``` -->
-<!-- </div> -->
-<!-- </div> -->

### 2021-09-22 Rmd/Report 2021.Rmd
New report for meeting

@@
   ungroup()
-
 ```
@@
 
-### step 2: 60 days rule between diagnosis and treatment
-60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded. Patients left :
-```{r}
-remove_60daysrule <- drugs1 %>% 
-  filter((days_at_first_drug > 60 | days_at_surg > 60)) %>% 
+### step 2: 90 days rule between diagnosis and treatment
+
+Flatiron propose a conceptual instruction on the 90-day-gap : 90 days between diagnosis and treatment.  
+It is meant to exclude patients who didn't get treatment for 90 days which would most likely mean that some treatment data are missing. Patients left after this step:
+```{r}
+remove_90daysrule <- drugs1 %>% 
+  filter((days_at_first_drug > 90 | days_at_surg > 90)) %>% 
   distinct(patientid)
-remove_60daysrule <- paste(remove_60daysrule$patientid, collapse = "|")
+remove_90daysrule <- paste(remove_90daysrule$patientid, collapse = "|")
 
 drugs1 <- drugs1 %>% 
-  # remove these patients who 60 days rule
-  filter(!str_detect(patientid, remove_60daysrule))
+  # remove these patients who 90 days rule
+  filter(!str_detect(patientid, remove_90daysrule))
 
@@
 
-### step 3: 30 days rule excluding patient whith less than 30 days between diagnosis and death
-```{r}
-drugs1 %>% 
-  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
-           duration(n=1, units = "days"), 
-         thirty_days_exclusion = case_when(
-           thirty_days_exclusion <= 30                  ~ "Exclude"
-         )) %>% 
-  filter(thirty_days_exclusion == "Exclude") %>% 
-  distinct(patientid) %>% 
-  nrow
-
-drugs11 <- drugs1 %>% 
+### step 3: 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis
+
+This is something that Flatiron strongly recommends, but does not require. Flatiron proposal reviewers will likely provide comments on this if not incorporated into a proposal. 
+```{r}
+# drugs1 %>% 
+#   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
+#            duration(n=1, units = "days"), 
+#          thirty_days_exclusion = case_when(
+#            thirty_days_exclusion <= 30                  ~ "Exclude"
+#          )) %>% 
+#   filter(thirty_days_exclusion == "Exclude") %>% 
+#   distinct(patientid) %>% 
+#   nrow
+
+drugs1 <- drugs1 %>% 
   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
@@
 
-drugs11 %>% distinct(patientid) %>% nrow()
-
-```
-In the data, `r drugs1 %>% mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/duration(n=1, units = "days"), thirty_days_exclusion = case_when(thirty_days_exclusion <= 30~ "Exclude")) %>% filter(thirty_days_exclusion == "Exclude") %>% distinct(patientid) %>% nrow` are excluded so we still have `r drugs11 %>% distinct(patientid) %>% nrow()` patients.
-
-### step 3: Remove linename that doesn't include platin or taxels in first line -> later in the process, need first to recode linenumber with all the drugs in.
+# drugs1 %>% distinct(patientid) %>% nrow()
+
+```
+In the data, `r drugs1 %>% mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/duration(n=1, units = "days"), thirty_days_exclusion = case_when(thirty_days_exclusion <= 30~ "Exclude")) %>% filter(thirty_days_exclusion == "Exclude") %>% distinct(patientid) %>% nrow` are excluded so we still have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.
+
+### step 4: Exclude exclude == "1" coded by Lauren
+
+Are excluded :  
+-	Borderline cases (not invasive ovarian cancer)  
+-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
+-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)
+Patients left after this step:
+
+```{r}
+drugs1 <- drugs1 %>% 
+  filter(exclude != "1")
+
+drugs1 %>% distinct(patientid) %>% nrow()
+```
+
+<!-- ### step .: Remove linename that doesn't include platin or taxanes in first line -> later in the process, need first to recode linenumber with all the drugs in. -->
 ```{r}
@@
 
-### step 4: Combine multiple administrations of the same drug at the same date
+### step 5: Combine multiple administrations of the same drug at the same date
 ```{r combine amount same drug one day}
@@
            fill = "right") %>%
+  ungroup() %>% 
+  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
   purrr::keep(~!all(is.na(.))) %>%
-  ungroup() %>% 
-  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
-         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
+  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
+  # mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
+  #        amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
   mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
@@
 
-### step 5: Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
+### step 6: Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
 ```{r line coding}
@@
 
-### step 6: Remove linename that doesn't include platin or taxels in first line
+### step 7: Remove linename that doesn't include platinum or taxanes in first line
+
+`r emo::ji("question_mark")`  
+Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes.  
+<span style="color:red">**Should we include patients who got a single drug lot/line?**</span> like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
+<span style="color:red">**Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?**</span>  
+<span style="color:red">**Should we exclude patients who received platinum/taxane +"Clinical Study Drug" if we don't don't if they are platinum or taxanes drugs?**</span>  
 ```{r}
@@
 
-therapy_line %>% distinct(patientid) %>% nrow()
+# therapy_line %>% distinct(patientid) %>% nrow()
 ```
@@
 
-#### Number of patient who switch line because of surgery from line 1 to adjuvant line
+#### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line
 ```{r Number of patient who switch line}
@@
   tbl_summary()
-
+```
+
+595 patients had part of their first line a switch of line but we have examples of patients for who the switched line last a really short time.  
+Easy example (sorry for the poor looking table `r emo::ji("face_with_raised_eyebrow")`):  
+In this example, 1 cycle is switched from the initial line 1 coded by flatiron to a linenumber_new 2
+
+<br>
+
+| linenumber (coded by flatiron) |  surgery |  linenumber_new that I coded   |  drug    |  
+| ------------------------------ | -------- | ------------------------------ | -------- |  
+|             1                  |          |             1                  | taxel    |  
+| ------------------------------ | -------- | ------------------------------ | -------- |  
+|             1                  |          |             1                  | platin   |  
+| ------------------------------ | -------- | ------------------------------ | -------- |  
+|             1                  |          |             1                  | taxel    |  
+| ------------------------------ | -------- | ------------------------------ | -------- |  
+|             1                  |          |             1                  | platin   |  
+| ------------------------------ | -------- | ------------------------------ | -------- |  
+|             1                  |          |             1                  | taxel    |  
+| ------------------------------ | -------- | ------------------------------ | -------- |  
+|             1                  |          |             1                  | platin   |  
+| ------------------------------ | -------- | ------------------------------ | -------- |  
+|             1                  |          |             1                  | taxel    |  
+| ------------------------------ | -------- | ------------------------------ | -------- |  
+|             1                  | happened |             2                  | platin   |  
+| ------------------------------ | -------- | ------------------------------ | -------- |  
+|             1                  |          |             2                  | taxel    |  
+| ------------------------------ | -------- | ------------------------------ | -------- |
+
+<br>
+
+Here a real example of this type of patient : initial `linenumber` = 1 but had surgery in September so part of this line in moved to `linenumber_new` = 2 and then coded as adjuvant line.  
+So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle. <span style="color:red">**Is that correct?**</span>  
+```{r Number of patient who switch line2, rows.print=30}
 # Problem F0000AD999ABF but would be good for F003F2BEEDB37
 therapy_line %>% 
-  filter(str_detect(patientid, "F0000AD999ABF|F003F2BEEDB37")) %>% 
+  filter(str_detect(patientid, "F41E15E18E008")) %>% 
   arrange(patientid, episodedate) %>% 
-  select(patientid, linenumber, linenumber_new, episodedate, chemotherapy_type)
-
+  select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
+```
+
+Here an example a little more complicated because the patient had the same type of switch but then had a 3rd line (used to be line 2 in flatiron) (had surgery in May if you are interested to know).  
+So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle switched to adjuvant and not the longer line witch was coded 2 by flatiron.
+<span style="color:red">**Is that correct?**</span>
+```{r, rows.print=30}
 therapy_line %>% 
-  mutate(change_line = case_when(
-    linenumber == 1 & 
-      linenumber_new == 2 &
-      chemotherapy_type == "Adjuvant" &
-      treatment_sequence == "neo + surg + adj"     ~ 1,
-    TRUE                                           ~ 0
-  )) %>% 
-  filter(change_line == 1) %>% 
-  group_by(patientid) %>% 
-  mutate(firstdate = first(episodedate)) %>% 
-  mutate(lastdate = last(episodedate)) %>% 
-  ungroup() %>% 
-  mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x=time_of_switch_line, fill = ..count..))+
-  geom_histogram(binwidth = 7)+
-  theme_minimal()+
-  ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
-  scale_y_continuous(#breaks=c(0, 50, 100, 150),
-                     minor_breaks=c(10, 20, 30, 40)#,
-                     #labels = c(0, 50, 100, 150)
-  )
-```
-
-#### How many lines patient got as Neo
+  filter(str_detect(patientid, "FC9D28216FEBE")) %>% 
+  arrange(patientid, episodedate) %>% 
+  select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
+
+# therapy_line %>% 
+#   mutate(change_line = case_when(
+#     linenumber == 1 & 
+#       linenumber_new == 2 &
+#       chemotherapy_type == "Adjuvant" &
+#       treatment_sequence == "neo + surg + adj"     ~ 1,
+#     TRUE                                           ~ 0
+#   )) %>% 
+#   filter(change_line == 1) %>% 
+#   group_by(patientid) %>% 
+#   mutate(firstdate = first(episodedate)) %>% 
+#   mutate(lastdate = last(episodedate)) %>% 
+#   ungroup() %>% 
+#   mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   ggplot(aes(x=time_of_switch_line, fill = ..count..))+
+#   geom_histogram(binwidth = 7)+
+#   theme_minimal()+
+#   ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
+#   scale_y_continuous(#breaks=c(0, 50, 100, 150),
+#                      minor_breaks=c(10, 20, 30, 40)#,
+#                      #labels = c(0, 50, 100, 150)
+#   )
+```
+`r emo::ji("question_mark")`  
+<span style="color:red">**So the bigger question is : Is it acceptable to include the patients who have a switched line?**</span>
+
+<br>
+
+#### How many lines did patients received as Neoadjuvant
+`r emo::ji("question_mark")`  
+Here are all the number of line that patients received as Neoadjuvant containing platinum or taxanes.  
+<span style="color:red">**Should we include patients who got more than 1 line as Neoadjuvant?**</span>
+
 ```{r}
@@
   tbl_summary()
-
+```
+
+### step 8: Remove patients with more than 1 line as Neo
+We are removing the 34 patients who received multiple Neoadjuvant line.   
+`r emo::ji("question_mark")`  
+<span style="color:red">**Can you confirm we are doing the good thing by excluding these patients?**</span>  
+Here the lines for the 34 patient.
+```{r, rows.print = 40}
 therapy_line %>% 
   filter(chemotherapy_type == "Neoadjuvant" &
-           linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5) %>% 
+           (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
   select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
          drugname, episodedate, surgerydate, chemotherapy_type) %>%
-  arrange(patientid, episodedate)
-```
-
-### step 7: Remove patients with more than 1 line as Neo -34
-```{r}
+  arrange(patientid, episodedate) %>% 
+  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
+  select(-linenumber)
+
 remove_morethan1_neo <- therapy_line %>% 
@@
   filter(!str_detect(patientid, remove_morethan1_neo))
-
+```
+
+Patients left:
+```{r}
 therapy_line %>% distinct(patientid) %>% nrow()
@@
 
-### step 8: Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
+### step 9: Remove patients who switch drug within a line
+
+`r therapy_line %>% filter(str_detect(linename, "Car") & drugname == "cisplatin") %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.  
+`r therapy_line %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin") %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.
+
+Patients left:
 ```{r}
 # But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
-therapy_line %>% 
-  filter(str_detect(linename, "Car") &
-           drugname == "cisplatin") %>%
-  distinct(patientid) %>% nrow()
-
-therapy_line %>% 
-  filter(str_detect(linename, "Cisplatin") &
-           drugname == "carboplatin") %>%
-  distinct(patientid) %>% nrow()
+# therapy_line %>% 
+#   filter(str_detect(linename, "Car") &
+#            drugname == "cisplatin") %>%
+#   distinct(patientid) %>% nrow()
+# 
+# therapy_line %>% 
+#   filter(str_detect(linename, "Cisplatin") &
+#            drugname == "carboplatin") %>%
+#   distinct(patientid) %>% nrow()
 
@@
 
+```{r}
+# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
+# therapy_line %>% 
+#   filter(str_detect(linename, "Pacli") &
+#            drugname == "docetaxel") %>%
+#   distinct(patientid) %>% nrow()
+# therapy_line %>% 
+#   filter(str_detect(linename, "Doce") &
+#            drugname == "Paclitaxel") %>%
+#   distinct(patientid) %>% nrow()
+```
+`r therapy_line %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel") %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.  
+I am removing these patients as the recoding for the cycle number would be messed up in these cases.
+
 `r emo::ji("question_mark")`
 
-<span style="color:red">**Should I do the same between paclitaxel and docetaxel?**</span>
-
-Remember that I coded "paclitaxel" == "paclitaxel protein bound"
-
-If a patient had carbo, pacli, carbo, pacli, docetaxel in a Carboplatin-Paclitaxel line : It makes the coding for cycle number more difficult
-
-I think it would be worth it and this operation would remove these patients:
-
-```{r}
-# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
-therapy_line %>% 
-  filter(str_detect(linename, "Pacli") &
-           drugname == "docetaxel") %>%
-  distinct(patientid) %>% nrow()
-therapy_line %>% 
-  filter(str_detect(linename, "Doce") &
-           drugname == "Paclitaxel") %>%
-  distinct(patientid) %>% nrow()
-```
+<span style="color:red">**Are you good with thatl?**</span>
+
+Patients left:
+```{r}
+remove_switch1 <- therapy_line %>% 
+  filter(
+    str_detect(linename, "Pacli") & drugname == "docetaxel"
+  ) %>%
+  distinct(patientid)
+remove_switch1 <- paste(remove_switch1$patientid, collapse = "|")
+
+therapy_line <- therapy_line %>% 
+  # remove these patients who switched C > C 
+  filter(!str_detect(patientid, remove_switch1))
+therapy_line %>% distinct(patientid) %>% nrow()
+```
+
 <br>
 
-`r emo::ji("question_mark")`  
-<span style="color:red">**Random question : within 1 cycle we can have taxel multiple times, is it possible for carboplatin or cisplatin?**</span>
-
-<br>
-
-### step 9: Code cycle
+<!-- `r emo::ji("question_mark")`   -->
+<!-- <span style="color:red">**Random question : within 1 cycle we can have taxanes multiple times, is it possible for carboplatin or cisplatin?**</span>   -->
+
+### step 10: Code cycle
 ```{r cycle coding}
@@
 
-### step 10: Bind everything together and calculating target_auc and expected dose
-
-When I bind things together I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`. it can be days in between or more. 
+### step 11: Bind everything together and calculating target_auc and expected dose
+
+When I bind the data together (drug + creatinine + ...
+at the "same" date), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, `target_dose` for cisplatin and taxanes and their `expected_dose`.
+But it can be days in between or more.
+Precision : when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
+
 `r emo::ji("question_mark")`  
-<span style="color:red">**Do we need a maximun?**</span>
-
-As you can see on the plots, the gap can be pretty big so :  
-<span style="color:red">**Can we take a creatinine value to bind it to a drug when a year long as past between each other?**</span>  
-<span style="color:red">**Same question for height, weight, bsa and corresponding AUC**</span>
-
-Precision when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
+As you can see on the plots, the interval in days can be pretty big so :  
+<span style="color:red">**Can we take a creatinine value to bind it to a drug when a year long as past between each other?  
+Do we need to set up a maximun gap?  
+Same question for height, weight, bsa and corresponding AUC  
+Let me know your advise, I will try to update that for our next meeting**</span> `r emo::ji("smiling_face")`
+
 ```{r target_auc and expected dose}
@@
   coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_height)) +
-  geom_bar() +
-  coord_cartesian(ylim=c(0,50))
+# Treatment %>% 
+#   ggplot(aes(x= interval_height)) +
+#   geom_bar() +
+#   coord_cartesian(ylim=c(0,50))
 Treatment %>% 
@@
 
-## We have `r Treatment %>% distinct(patientid) %>% nrow()` patients with drug and clinical info but
-
-### step 11: Exclude exclude == "1" coded by Lauren due to Flatiron rule
-
-```{r analysis_data}
-analysis_data <- Treatment %>% 
-  filter(exclude != "1")
-```
-
-## **Number of patients in final dataset is `r analysis_data %>% distinct(patientid) %>% nrow()`**
+### If we keep as is, the
+## **Number of patients in final dataset is `r Treatment %>% distinct(patientid) %>% nrow()`**
 
@@
 ## Explore the dataset
-Number of line in neo
+
+```{r}
+analysis_data <- Treatment
+```
+
+Number of Neoadjuvant line in patients with upfront neo
 ```{r}
@@
 ```
-Number of line in Adj neo + surg + adj
+Number of Adjuvant line in patients with upfront neo
 ```{r}
@@
 ```
-Number of line in Adj surg + adj
+Number of Adjuvant line in patients with upfront surgery
 ```{r}
@@
 
-#
-
+# Missingness
+Here some representation of missingness in our data
+- In the first plot (horizontal bar), `r is.na(analysis_data$height_at_dx) %>% sum()` data is missing for height at dx but `r analysis_data %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
+Because these parameters overlap only 25 patients will have missing value for all of them.
+- In the second plot (horizontal bar), `r is.na(analysis_data$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(analysis_data$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation).
+the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
 ```{r}
@@
 
-is.na(analysis_data$CrCl) %>% sum()
-is.na(analysis_data$amount) %>% sum()
-is.na(analysis_data$target_auc) %>% sum()
+# is.na(analysis_data$CrCl) %>% sum()
+# is.na(analysis_data$amount) %>% sum()
+# is.na(analysis_data$target_auc) %>% sum()
 

### 2021-09-22 Rmd/Report October 2021.Rmd
New report for meeting

--- 2021-09-22 Rmd/Report 2021.Rmd
@@
 ---
-title: "Flatiron analysis"
+title: "Flatiron cleaning"
 author: "Christelle Colin-Leitzinger"
@@
 
-# CALCULATE RDI
-
-`r emo::ji("question_mark")`  
-<span style="color:red">**I need confirmation : we calculate 1 RDI per drug per patient for the first (unique) line of neoadjuvant and 1 RDI per drug per patient for the ALL the lines of adjuvant which are not maintenance.
-Is that correct**</span>
-
-## Calculate RDI by drug by cycle by patient
-Here few examples
-```{r, rows.print=15, max.print=30}
-analysis_data <- analysis_data %>% 
-  # Calculate RDI for each drug per cycle per patients
-  mutate(relative_dose_intensity = amount/expected_dose) %>% 
-  group_by(patientid, linenumber_new, cycle_drugname,  chemotherapy_type, linestartdate, lineenddate, cycle_increment) %>% 
-  summarise(across(relative_dose_intensity, mean, na.rm = TRUE))
-
-analysis_data
-```
-
-## Calculate RDI by drug by line by patient
-Here few examples
-```{r, rows.print=15, max.print=30}
-analysis_data <- analysis_data %>% 
-  # Calculate RDI for each drug per line per patients
-  group_by(patientid, linenumber_new, cycle_drugname,  chemotherapy_type, linestartdate, lineenddate) %>% 
-  summarise(across(relative_dose_intensity, mean, na.rm = TRUE))
-
-analysis_data
-```
-
-## Calculate RDI by drug by patient
-Here few examples
-```{r, rows.print=15, max.print=30}
-analysis_data <- analysis_data %>% 
-  # Calculate RDI for each drug per patients
-  group_by(patientid, cycle_drugname, chemotherapy_type) %>% 
-  summarise(across(relative_dose_intensity, mean, na.rm = TRUE)) %>% 
-  ungroup()
-
-analysis_data
-
-analysis_data %>% 
-  ggplot(aes(x = relative_dose_intensity, fill = cycle_drugname))+
-  geom_histogram(alpha = 0.5)+
-  theme_minimal()+
-  facet_wrap(.~ chemotherapy_type, scales = "free")
-
-analysis_data %>% 
-  ggplot(aes(x = relative_dose_intensity, y = chemotherapy_type, fill = cycle_drugname))+
-  geom_boxplot()+
-  geom_vline(xintercept = 1, color = "red")+
-  theme_minimal()
-```
-
-```{r}
-analysis_data <- analysis_data %>%
-
-  mutate(RDI_grp = case_when(
-    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
-    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85"
-  )) %>% 
-  mutate(RDI_grp = factor(RDI_grp, 
-                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
-  mutate(RDI_grp1 = case_when(
-    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
-    # relative_dose_intensity >= 0.85         ~ "RDI >= 0.85",
-    relative_dose_intensity >= 0.85 &
-      relative_dose_intensity <= 1          ~ "0.85 <= RDI <= 1",
-    relative_dose_intensity > 1 &
-      relative_dose_intensity <= 1.5        ~ "1 < RDI <= 1.5",
-    relative_dose_intensity > 1.5 &
-      relative_dose_intensity <= 2          ~ "1.5 < RDI <= 2",
-    relative_dose_intensity > 2             ~ "RDI > 2",
-  )) %>% 
-  mutate(RDI_grp1 = factor(RDI_grp1, 
-                          labels = c("RDI < 0.85", 
-                                     "0.85 >= RDI <= 1", 
-                                     "1 < RDI <= 1.5", 
-                                     "1.5 < RDI <= 2", 
-                                     "RDI > 2"))) %>% 
-  # mutate(delay_incare_dx_to_treat = case_when(
-  #   str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
-  #     duration(n=1, units = "days")),
-  #   str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
-  #     duration(n=1, units = "days"))
-  # )) %>% 
-  left_join(., Treatment) %>% 
-  group_by(patientid) %>%
-  mutate(first_treatment_date = case_when(
-    treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
-    str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
-    treatment_sequence == "surg + adj"                    ~ surgerydate,
-    treatment_sequence == "Surgery only"                  ~ surgerydate
-  )) %>%
-  # group_by(patientid) %>% 
-  # mutate(first_treatment_date = case_when(
-  #   str_detect(therapy, "Chemo")                      ~ min(episodedate),
-  #   str_detect(therapy, "Surgery")                    ~ surgerydate,
-  # )) %>% 
-  # mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
-  #                                         duration(n=1, units = "days")) %>% 
-  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
-                   duration(n=1, units = "months")) %>% 
-  ungroup()
-
-```
-
 # Analysis
@@
 
-## 2.Plots Clinical
-<div class = "row">
-<div class = "col-md-6">
-```{r}
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= bmi_cat))+
-  geom_bar()+
-  theme_minimal()+
-  labs(title = "BMI category")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= histology))+
-  geom_bar()+
-  theme_minimal()+
-  labs(title = "Histology")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= stagecat))+
-  geom_bar()+
-  theme_minimal()+
-  labs(title = "Stage")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= agecat))+
-  geom_bar()+
-  theme_minimal()+
-  labs(title = "Age cat")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= brca_germline))+
-  geom_bar()+
-  theme_minimal()+
-  labs(title = "BRCA gernline")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= brca_tumor))+
-  geom_bar()+
-  theme_minimal()+
-  labs(title = "BRCA tumor")+
-  coord_flip()
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = bmi_cat))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  labs(title = "BMI category")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= histology, fill = raceeth))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  labs(title = "Histology")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= stagecat, fill = raceeth))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  labs(title = "Stage")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= agecat, fill = raceeth))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  labs(title = "Age cat")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= brca_germline, fill = raceeth))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  labs(title = "BRCA germline")+
-  coord_flip()
-
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= brca_tumor, fill = raceeth))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  labs(title = "BRCA tumor")+
-  coord_flip()
-```
-</div>
-</div>
-
-<br>
-
-## 3.Survivals by clinical
-
-<span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the right**</span>
-
-<div class = "row">
-<div class = "col-md-6">
-```{r clinical from dx, fig.height = 7}
-# OS by race
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=analysis_data),
-#            title = "OS from date of diagnosis", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-
-# OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by histology
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=analysis_data %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of diagnosis", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-
-# OS by tstage
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca1_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca2_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca1_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca2_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r clinical from first treatment, fig.height = 7}
-# OS by race
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=analysis_data %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of first treatment", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-
-# OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by histology
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ histology, data=analysis_data %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of first treatment", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-
-# OS by tstage
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca1_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca2_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-# OS by brca1_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca2_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-</div>
-
-<br>
-<br>
-
 ***
@@
   select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
-           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
-           had_neo, had_adj,
+           "debulking",
            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
@@
 
-## 2.Plots Treatment
-<div class = "row">
-<div class = "col-md-6">
-```{r}
-analysis_data %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= therapy))+
-  geom_bar()+
-  theme_minimal()+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-# analysis_data %>% 
-#   arrange(episodedate) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   group_by(chemotherapy_type) %>% 
-#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
-#   geom_bar(stat="identity")+
-#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
-#   theme_minimal()+
-#   guides(fill = FALSE) +
-#   coord_flip()
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  # group_by(treatment_sequence) %>% 
-  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-  ggplot(aes(x= treatment_sequence,
-             # y= percent, 
-             fill = treatment_sequence))+
-  geom_bar(
-    # stat="identity"
-    )+
-  labs(x = "", title = "The treatment_sequence") +
-  theme_minimal()+
-  guides(fill = FALSE) +
-  coord_flip()
-
-# analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
-#   ggplot(aes(x= chemo))+
-#   geom_bar()+
-#   theme_minimal()+
-#   coord_flip()
-```
-</div>
-</div>
-
-<br>
-
-## 3.Survivals by treatment
-
-<div class = "row">
-<div class = "col-md-6">
-```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by extentofdebulking
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by residualdiseasestatus
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by chemotherapy_type
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ chemotherapy_type, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by treatment_sequence
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by extentofdebulking
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by residualdiseasestatus
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by chemotherapy_type
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ chemotherapy_type, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by treatment_sequence
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(nrow = 3))
-
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=analysis_data %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-</div>
-
-<br>
-<br>
-
 ***
-
-<br>
-
-# III.RDI
-
-## 1.RDI summary table
-
-<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
-
-```{r Table 4}
-
-# Treatment & demo
-tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl3 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl4 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              type = list(relative_dose_intensity ~ 'continuous'),
-              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              type = list(relative_dose_intensity ~ 'continuous'),
-              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- analysis_data %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl5, tbl6), quiet = TRUE)
-```
-<br>
-
-# CAN TAKE A LOOK BUT NEED TO VERIFY ALL THE REST
-
-<br>
-
-***
-
-<br>
-
-## 2.Plots RDI
-
-<div class = "row">
-<div class = "col-md-6">
-```{r}
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
-  geom_boxplot()+
-  ylim(c(-.25, 3.5))+
-  geom_jitter(shape=16)+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
-  theme_minimal()+
-  facet_wrap(.~ cycle_drugname)
-
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
-  geom_violin()+
-  ylim(c(-.25, 3.5))+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal()
-
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= cycle_drugname, y= relative_dose_intensity, color = chemotherapy_type))+
-  geom_violin()+
-  ylim(c(-.25, 3.5))+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal()+
-  coord_flip()
-
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
-  geom_bar()+
-  theme_minimal()+
-  facet_wrap(.~ chemotherapy_type)
-
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
-  # geom_boxplot()+
-  ylim(c(-.25, 3.5))+
-  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
-  theme_minimal() +
-  guides(color=FALSE)+
-  facet_wrap(.~ cycle_drugname)
-
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = relative_dose_intensity<0.85))+
-  geom_violin()+
-  ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal()+
-  facet_wrap(.~ cycle_drugname)
-
-# analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-#   # filter(linenumber_new == "1") %>%
-#   ggplot(aes(x= cycle_drugname, y= relative_dose_intensity))+
-#   geom_violin(aes(color=relative_dose_intensity<0.85))+
-#   ylim(c(-.25, 2.5))+
-#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-#   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-#   theme_minimal()
-
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  facet_wrap(.~ chemotherapy_type)
-
-```
-</div>
-</div>
-
-```{r}
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, alpha = relative_dose_intensity<0.85))+
-  geom_violin(aes(fill = cycle_drugname))+
-  ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal()+
-  facet_wrap(.~ raceeth)
-```
-
-A quick summary for the RDI repartition
-```{r}
-analysis_data2 <- analysis_data# %>% filter(linenumber_new == "1")
-summary(analysis_data2$relative_dose_intensity)
-```
-
-<div class = "row">
-<div class = "col-md-6">
-```{r}
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
-  geom_bar()+
-  theme_minimal()+
-  facet_wrap(.~ chemotherapy_type)
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-analysis_data %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
-  geom_bar(position = "fill")+
-  theme_minimal()+
-  coord_flip()+
-  facet_wrap(.~ chemotherapy_type)
-```
-</div>
-</div>
-
-<br>
-
-## 3.Survivals by RDI
-
-<div class = "row">
-<div class = "col-md-6">
-```{r, fig.height = 7}
-# OS by RDI_grp
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE) %>% 
-#                      filter(exclude != "1")),
-#            title = "OS from diagnosis Overall RDI", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-# 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for platin
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from diagnosis carboplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from diagnosis cisplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for taxel
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from diagnosis all taxel", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-# # OS by RDI_grp
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE) %>% 
-#                      filter(exclude != "1")),
-#            title = "OS from first treatment overall RDI", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for platin
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from first treatment carboplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from first treatment cisplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for taxel
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from from first treatment all taxel", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-</div>
-
-<br>
-
-## Survivals RDI by chemotherapy type
-**On the left are Neoadjuvant, on the right are Adjuvant**
-
-<div class = "row">
-<div class = "col-md-6">
-```{r, fig.height = 7}
-# OS by RDI_grp for platin
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
-                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
-                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from first treatment carboplatin",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
-                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
-                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from first treatment cisplatin",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for taxel
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
-                     filter((exclude != "1") & str_detect(drugname, "taxel"),
-                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from from first treatment all taxel",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-# OS by RDI_grp for platin
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
-                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
-                            str_detect(chemotherapy_type, "Adjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from first treatment carboplatin",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
-                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
-                            str_detect(chemotherapy_type, "Adjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from first treatment cisplatin",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for taxel
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=analysis_data %>%
-                     filter((exclude != "1") & str_detect(drugname, "taxel"),
-                            str_detect(chemotherapy_type, "Adjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from from first treatment all taxel",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-</div>
-
-<br>
-<br>
-
-***
-# IV.Hazard Ratio
-
-<span style="color:green">**Table 5 HR**</span>  
-`coxph(Surv(time = month_at_os, event = vitalstatus)~variables`
-```{r Table 5 HR}
-# tbl1 <- analysis_data %>%
-#   select(bmi_cat) %>%
-#   tbl_summary(#by = vitalstatus,
-#               statistic = all_categorical() ~ "{analysis_data %>% filter(vital == 'Dead') %>% NROW()} death ({n})"
-#               )
-# tbl2 <- coxph(Surv(time = month_at_os,
-#                      event = vitalstatus)~bmi_cat,
-#                 data = analysis_data) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-#
-# tbl_merge(list(tbl1, tbl2))
-#
-# coxph(Surv(time = month_at_os,
-#                      event = vitalstatus)~RDI_grp,
-#                 data = analysis_data) %>%
-#   tbl_uvregression(y = vitalstatus, exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-
-# analysis_data %>% select(vitalstatus, bmi, bmi_cat, raceeth) %>%
-# tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = analysis_data$month_at_os, event = analysis_data$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
-#   bold_labels() %>% italicize_levels() #%>%  modify_spanning_header(all_stat_cols() ~ "**Treatment Received**")
-
-tbl1 <- analysis_data %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-tbl1 <- tbl1 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl2 <- analysis_data %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
-tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl3 <- analysis_data %>%
-  filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
-tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>%
-  bold_labels() %>%
-  italicize_levels()
-# Cisplatin
-tbl4 <- analysis_data %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
-tbl4 <- tbl4 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl5 <- analysis_data %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
-tbl5 <- tbl5 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl6 <- analysis_data %>%
-  filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
-tbl6 <- tbl6 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant", "cisplatin/Chemo only")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-tbl7 <- analysis_data %>%
-  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Neoadjuvant")
-tbl7 <- tbl7 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl8 <- analysis_data %>%
-  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Adjuvant")
-tbl8 <- tbl8 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
-  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl9 <- analysis_data %>%
-  filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
-tbl9 <- tbl9 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant", "paclitaxel/Chemo only")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-tbl10 <- analysis_data %>%
-  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
-tbl10 <- tbl10 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl11 <- analysis_data %>%
-  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
-tbl11 <- tbl11 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
-  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl12 <- analysis_data %>%
-  filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
-tbl12 <- tbl12 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl10, tbl11, tbl12),
-          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<br>
-<br>
-
-***
-# V.Regression
-## By clinical, demo
-`glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = analysis_data, family = binomial)`
-```{r}
-# Regression vital status prediction
-model <- glm(vitalstatus ~ bmi_at_dx + bmi_cat + #RDI_grp + 
-               raceeth, data = analysis_data %>% 
-               distinct(patientid, .keep_all = TRUE), 
-             family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-```
-
-`glm(vitalstatus ~ histology + tstage + brca1_tumor + brca2_tumor + issurgery + chemotherapy_type, data = analysis_data, family = binomial)`
-```{r}
-model <- glm(vitalstatus ~ 
-               histology + tstage + brca1_tumor + brca2_tumor + 
-             issurgery +
-             chemotherapy_type, 
-             data = analysis_data %>% 
-               distinct(patientid, .keep_all = TRUE), 
-             family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-```
-
-`glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)`
-<!-- !!!! Prediction of RDI all drug together!!!! -->
-```{r}
-# Regression RDI prediction
-# model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = analysis_data, family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-```
-
-### By drug
-<!-- !!! But sometimes we had a switch between cisplatin/carboplatin -->
-```{r}
-#  for carbo
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
-               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
-               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-# tbl5 <-
-  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
-
-#  for Cisplatim
-# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
-#                filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-# model <- glm(RDI_grp ~ agecat + bmi_cat, data = analysis_data %>%
-#                filter(drugname == "cisplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-# 
-# # tbl5 <-
-#   tbl_merge(list(tbl3, tbl4), tab_spanner = c("**cisplatin/Adjuvant**", "**cisplatin/Neoadjuvant**"))
-
-#  for taxel
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
-               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = analysis_data %>%
-               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-# tbl6 <-
-  tbl_merge(list(tbl4, tbl3), tab_spanner = c("**taxel/Adjuvant**", "**taxel/Neoadjuvant**"))
-```
-<br>
-<br>
-
-***
+<br>
+
+# `r emo::ji("question_mark")` Reminders/Questions of each capping and calculations:
+
+Creatinine data are capped as :  
+- creat < 0.7 was set at 0.7  
+- creat > 3 are eliminated
+
+CrCl calculation :
+
+$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle * 0.85}$$
+<br>
+
+Calculating more BSA values :
+$$bsa\_du\_bois = 0.007184 * (height*100)^{0.725} * weight^{0.425}$$
+<br>
+
+I clean the data up by keeping the `relativeorderedamount`:  
+- >= 50 & <= 175 for taxel and cisplatin  and with a unit in `mg/m2`  
+- >= 2  & <= 6   for platin and with a unit in `AUC`
+
+<br>
+
+`expected_dose` is:  
+-`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
+-`BSA` * `target_auc`           -> for `drugname` == "taxel" or "cisplatin"  
+(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
+It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).
+
+<br>
+
+Then I calculate $$relative\_dose\_intensity = \frac{amount}{expected\_dose}$$
+
+<br>
+
+<span style="color:red">**Please confirm everything is correct**</span>
+
+<font size="10">Thanks! `r  emo::ji("party_popper")`</font>

### 2021-09-23 Rmd/Report October 2021.Rmd
typo and text changes

@@
 `r emo::ji("question_mark")`  
-Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes.  
-<span style="color:red">**Should we include patients who got a single drug lot/line?**</span> like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
+Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
+<span style="color:red">**Should we include patients who got a single drug as lot/line?**</span> like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
 <span style="color:red">**Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?**</span>  
-<span style="color:red">**Should we exclude patients who received platinum/taxane +"Clinical Study Drug" if we don't don't if they are platinum or taxanes drugs?**</span>  
+<span style="color:red">**Should we exclude patients who received a platinum + Clinical study drug or a taxane + clinical study drug as we don’t know what the clinical study drug is – is it possible that it could include a platinum or taxane based drug?**</span>
 ```{r}
@@
 
-#### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line
+### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line
 ```{r Number of patient who switch line}
@@
 
-Here a real example of this type of patient : initial `linenumber` = 1 but had surgery in September so part of this line in moved to `linenumber_new` = 2 and then coded as adjuvant line.  
+Here a real example of this type of patient : initial `linenumber` = 1 but had surgery in 09/2019 so part of this line in moved to `linenumber_new` = 2 and then coded as adjuvant line.  
 So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle. <span style="color:red">**Is that correct?**</span>  
@@
 
-Here an example a little more complicated because the patient had the same type of switch but then had a 3rd line (used to be line 2 in flatiron) (had surgery in May if you are interested to know).  
+Here an example a little more complicated because the patient had surgery 05/2017 and the same type of switch but then had a 3rd line (used to be line 2 in flatiron).    
 So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle switched to adjuvant and not the longer line witch was coded 2 by flatiron.
@@
 
-#### How many lines did patients received as Neoadjuvant
+### How many lines did patients received as Neoadjuvant
 `r emo::ji("question_mark")`  
@@
 
-`r therapy_line %>% filter(str_detect(linename, "Car") & drugname == "cisplatin") %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.  
-`r therapy_line %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin") %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.
+`r therapy_line %>% filter(str_detect(linename, "Car") & drugname == "cisplatin") %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line and were removed.  
+`r therapy_line %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin") %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line and were removed.
 
@@
 `r therapy_line %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel") %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.  
-I am removing these patients as the recoding for the cycle number would be messed up in these cases.
+I am removing these patients for now but <span style="color:red">**Do we need to remove the patients that switch from paclitaxel to docetaxel and vice versa since the dosing calculating is the same for both?**</span>
 
@@
 
-When I bind the data together (drug + creatinine + ...
-at the "same" date), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, `target_dose` for cisplatin and taxanes and their `expected_dose`.
-But it can be days in between or more.
-Precision : when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
+(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column called `target_auc` for a tidy data organisation - You can find the calculations formula at the end of the document)
+When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, cisplatin and taxanes and their `expected_dose`.
+It can be days in between but it can also be more.
 
@@
 Do we need to set up a maximun gap?  
-Same question for height, weight, bsa and corresponding AUC  
+Same question for height, weight, bsa and corresponding AUC/target_dose  
 Let me know your advise, I will try to update that for our next meeting**</span> `r emo::ji("smiling_face")`
@@
              by = "patientid") %>% 
-  mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
+  mutate(CrCl = (
+       (
+    ((140 - ageatdx) * weight) /
+    (72 * creatinine)
+       ) *
+    0.85)
+  ) %>% 
   mutate(CrCl = case_when(
@@
 
+# A little of data analysis
 ## Explore the dataset
@@
 
-Number of Neoadjuvant line in patients with upfront neo
+Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)
 ```{r}
@@
 ```
+<span style="color:red">**Do we keep in the chemotherapy only patients?**</span>  
+<br>
 
 # Missingness
-Here some representation of missingness in our data  
-- In the first plot (horizontal bar), `r is.na(analysis_data$height_at_dx) %>% sum()` data is missing for height at dx but `r analysis_data %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
+Here some representation of missingness in our data:  
+- In the first plot (horizontal bar), `r is.na(analysis_data$height_at_dx) %>% sum()` data is missing for height closest to dx but `r analysis_data %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
 Because these parameters overlap only 25 patients will have missing value for all of them.
@@
 ```
-If we remove patients who have at least 1 missing amount administrered, we lose `r analysis_data %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
+If we remove patients who have at least 1 missing amount administered, we lose `r analysis_data %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
 
@@
 analysis_data %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
   select(c(raceeth, "vital",
@@
 
-# II.Analysis Treatment
+<!-- # II.Analysis Treatment -->
 
@@
 
-$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle * 0.85}$$
+$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
+and is capped at 125.  
 <br>

### 2021-10-06 Rmd/Report October 2021.Rmd
Update cleaning and add analysis

@@
 
+### step 5: Remove chemotherapy only patients
+```{r}
+drugs1 <- drugs1 %>%
+  filter(!is.na(surgerydate))
+drugs1 %>% distinct(patientid) %>% nrow()
+```
+
 ### step 5: Combine multiple administrations of the same drug at the same date
@@
 <span style="color:red">**Should we include patients who got a single drug as lot/line?**</span> like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
-<span style="color:red">**Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?**</span>  
-<span style="color:red">**Should we exclude patients who received a platinum + Clinical study drug or a taxane + clinical study drug as we don’t know what the clinical study drug is – is it possible that it could include a platinum or taxane based drug?**</span>
+<span style="color:red">**Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?**</span> `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev**</span>
+
 ```{r}
 # F0017FB3A8828 starts with gemcitabine then have carbo
-therapy_line <- therapy_line %>%
+therapy_line1 <- therapy_line %>%
   arrange(patientid, episodedate) %>% 
+  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
+  select(patientid, linename, linenumber, linenumber_new, drug_count, drugname, therapy, treatment_sequence) %>%
+
   mutate(remove_linename_other = case_when(
-    linenumber_new == 1 &
+    linenumber == 1 &
+      # treatment_sequence == "neo + surg + adj" &
+      drug_count == 1 &
       str_detect(linename, "platin|taxel")       ~ "keep",
-    linenumber_new == 1 &
-      !str_detect(linename, "platin|taxel")     ~ "remove",
+    linenumber == 1 &
+      drug_count == 2 &
+      (
+      (str_detect(linename, "platin") &
+      str_detect(linename, "taxel")) |
+      (str_detect(linename, "platin") &
+      str_detect(linename, "Bev")) |
+        (str_detect(linename, "taxel") &
+      str_detect(linename, "Bev"))
+      )                                           ~ "keep",
+    linenumber == 1 &
+      drug_count == 3 &
+      str_detect(linename, "platin") &
+      str_detect(linename, "taxel") &
+      str_detect(linename, "Bev")                 ~ "keep",
+
+    TRUE                                          ~ NA_character_,
   )) %>% 
@@
 
-therapy_line %>% 
-  filter(linenumber_new == 1) %>% 
+therapy_line1 %>% 
+  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
+         ) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linename) %>% 
+  tbl_summary(sort = list(everything() ~ "frequency"))
+
+therapy_line1 %>% 
+  filter(linenumber == 2, treatment_sequence == "neo + surg + adj") %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
@@
 We are removing the 34 patients who received multiple Neoadjuvant line.   
-`r emo::ji("question_mark")`  
-<span style="color:red">**Can you confirm we are doing the good thing by excluding these patients?**</span>  
+`r emo::ji("check")`
+
 Here the lines for the 34 patient.

### 2021-10-06 Rmd/rdi analysis.Rmd
Update cleaning and add analysis

--- 2021-10-06 Rmd/Report October 2021.Rmd
@@
 
+# `r emo::ji("question_mark")` Reminders/Questions of each capping and calculations:
+
+Creatinine data are capped as :  
+- creat < 0.7 was set at 0.7  
+- creat > 3 are eliminated
+
+CrCl calculation :
+
+$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
+and is capped at 125.  
+<br>
+
+Calculating more BSA values :
+$$bsa\_du\_bois = 0.007184 * (height*100)^{0.725} * weight^{0.425}$$
+<br>
+
+I clean the data up by keeping the `relativeorderedamount`:  
+- >= 50 & <= 175 for taxel and cisplatin  and with a unit in `mg/m2`  
+- >= 2  & <= 6   for platin and with a unit in `AUC`
+
+<br>
+
+`expected_dose` is:  
+-`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
+-`BSA` * `target_auc`           -> for `drugname` == "taxel" or "cisplatin"  
+(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
+It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).
+
+<br>
+
+Then I calculate $$relative\_dose\_intensity = \frac{amount}{expected\_dose}$$
+
+<br>
+
+<span style="color:red">**Please confirm everything is correct**</span>
+
+***
 At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.  
@@
 
+### How many lines did patients received as Neoadjuvant
+`r emo::ji("question_mark")`  
+Here are all the number of line that patients received as Neoadjuvant containing platinum or taxanes.  
+<span style="color:red">**Should we include patients who got more than 1 line as Neoadjuvant?**</span>
+
+```{r}
+therapy_line %>% 
+  filter(chemotherapy_type == "Neoadjuvant") %>% 
+  arrange(desc(linenumber_new)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linenumber_new) %>% 
+  tbl_summary()
+```
+
+### step 8: Remove patients with more than 1 line as Neo
+We are removing the 34 patients who received multiple Neoadjuvant line.   
+`r emo::ji("check")`
+
+Here the lines for the 34 patient.
+```{r, rows.print = 40}
+therapy_line %>% 
+  filter(chemotherapy_type == "Neoadjuvant" &
+           (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
+  select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
+         drugname, episodedate, surgerydate, chemotherapy_type) %>%
+  arrange(patientid, episodedate) %>% 
+  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
+  select(-linenumber)
+
+remove_morethan1_neo <- therapy_line %>% 
+  filter(chemotherapy_type == "Neoadjuvant" &
+           linenumber_new != 1)
+remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")
+
+therapy_line <- therapy_line %>% 
+  # Remove patients with more than 1 line as Neo
+  filter(!str_detect(patientid, remove_morethan1_neo))
+```
+
+Patients left:
+```{r}
+therapy_line %>% distinct(patientid) %>% nrow()
+```
+
 ### step 7: Remove linename that doesn't include platinum or taxanes in first line
@@
 therapy_line1 %>% 
-  filter(linenumber == 2, treatment_sequence == "neo + surg + adj") %>% 
+  filter(linenumber_new == 2, treatment_sequence == "neo + surg + adj") %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
@@
 
-### How many lines did patients received as Neoadjuvant
-`r emo::ji("question_mark")`  
-Here are all the number of line that patients received as Neoadjuvant containing platinum or taxanes.  
-<span style="color:red">**Should we include patients who got more than 1 line as Neoadjuvant?**</span>
-
-```{r}
-therapy_line %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
-  arrange(desc(linenumber_new)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new) %>% 
-  tbl_summary()
-```
-
-### step 8: Remove patients with more than 1 line as Neo
-We are removing the 34 patients who received multiple Neoadjuvant line.   
-`r emo::ji("check")`
-
-Here the lines for the 34 patient.
-```{r, rows.print = 40}
-therapy_line %>% 
-  filter(chemotherapy_type == "Neoadjuvant" &
-           (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
-  select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
-         drugname, episodedate, surgerydate, chemotherapy_type) %>%
-  arrange(patientid, episodedate) %>% 
-  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
-  select(-linenumber)
-
-remove_morethan1_neo <- therapy_line %>% 
-  filter(chemotherapy_type == "Neoadjuvant" &
-           linenumber_new != 1)
-remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")
-
-therapy_line <- therapy_line %>% 
-  # Remove patients with more than 1 line as Neo
-  filter(!str_detect(patientid, remove_morethan1_neo))
-```
-
-Patients left:
-```{r}
-therapy_line %>% distinct(patientid) %>% nrow()
-```
-
 ### step 9: Remove patients who switch drug within a line
@@
 
-# `r emo::ji("question_mark")` Reminders/Questions of each capping and calculations:
-
-Creatinine data are capped as :  
-- creat < 0.7 was set at 0.7  
-- creat > 3 are eliminated
-
-CrCl calculation :
-
-$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
-and is capped at 125.  
-<br>
-
-Calculating more BSA values :
-$$bsa\_du\_bois = 0.007184 * (height*100)^{0.725} * weight^{0.425}$$
-<br>
-
-I clean the data up by keeping the `relativeorderedamount`:  
-- >= 50 & <= 175 for taxel and cisplatin  and with a unit in `mg/m2`  
-- >= 2  & <= 6   for platin and with a unit in `AUC`
-
-<br>
-
-`expected_dose` is:  
--`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
--`BSA` * `target_auc`           -> for `drugname` == "taxel" or "cisplatin"  
-(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
-It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).
-
-<br>
-
-Then I calculate $$relative\_dose\_intensity = \frac{amount}{expected\_dose}$$
-
-<br>
-
-<span style="color:red">**Please confirm everything is correct**</span>
-
 <font size="10">Thanks! `r  emo::ji("party_popper")`</font>
+
+***
+
+<br>
+<br>
+
+***
+
+<br>
+
+# RDI calculation
+
+RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.
+
+```{r}
+Frontline <- Treatment %>% 
+  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
+    group_by(patientid, chemotherapy_type) %>% 
+  mutate(linenumber_adj = dense_rank(linenumber_new)) %>%
+
+  filter(chemotherapy_type == "Neoadjuvant" |
+           (chemotherapy_type == "Adjuvant" &
+              linenumber_adj == 1)) %>%
+
+  mutate(relative_dose_intensity = case_when(
+    chemotherapy_type == "Adjuvant" &
+      linenumber_adj == 1                  ~ amount/expected_dose,
+    chemotherapy_type == "Neoadjuvant"     ~ amount/expected_dose
+  )) %>%
+
+  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
+  #        relative_dose_intensity, linenumber_adj) %>%
+
+  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
+  group_by(patientid, chemotherapy_type, drugname_type) %>%
+  mutate(mean_RDI_per_chemotype_drug = case_when(
+    chemotherapy_type == "Adjuvant" &
+      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
+    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  )) %>% 
+  ungroup() %>% 
+  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE)
+```
+
+```{r}
+Frontline %>% distinct(patientid) %>% nrow()
+```
+
+# Analysis
+
+## 2.Plots Clinical
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= bmi_cat))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "BMI category")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= histology))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Histology")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= stagecat))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Stage")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= agecat))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Age cat")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= brca_germline))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "BRCA gernline")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= brca_tumor))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "BRCA tumor")+
+  coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill = bmi_cat))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "BMI category")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill = histology))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "Histology")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill = stagecat))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "Stage")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill = agecat))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "Age cat")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill = brca_germline))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "BRCA germline")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill = brca_tumor))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  labs(title = "BRCA tumor")+
+  coord_flip()
+```
+</div>
+</div>
+
+<br>
+
+## 3.Survivals by clinical
+
+<span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the right**</span>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r clinical from dx, fig.height = 7}
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca1_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca_tumor
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca1_g
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca2_g
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca_g
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r clinical from first treatment, fig.height = 7}
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca1_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca2_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca_tumor
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+# OS by brca1_g
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca2_g
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by brca_g
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+</div>
+
+<br>
+<br>
+
+***
+
+<br>
+
+# II.Analysis Treatment
+
+## 1.Treatment summary table
+
+<span style="color:green">**Table 3 Summary treatment data by race**</span>
+
+```{r Table 3}
+# tbl1 <- 
+  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
+           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
+           had_neo, had_adj,
+           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
+           )) %>% 
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p(
+    # test.args = all_tests("chisq.test") ~ list(workspace=2e9)
+    ) %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+#   filter(exclude != "1") %>% 
+#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
+#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
+#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
+#            )) %>% 
+#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
+```
+<br>
+
+## 2.Plots Treatment
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= therapy))+
+  geom_bar()+
+  theme_minimal()+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+# Frontline %>% 
+#   arrange(episodedate) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   group_by(chemotherapy_type) %>% 
+#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
+#   geom_bar(stat="identity")+
+#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
+#   theme_minimal()+
+#   guides(fill = FALSE) +
+#   coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  # group_by(treatment_sequence) %>% 
+  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= treatment_sequence,
+             # y= percent, 
+             fill = treatment_sequence))+
+  geom_bar(
+    # stat="identity"
+    )+
+  labs(x = "", title = "The treatment_sequence") +
+  theme_minimal()+
+  guides(fill = FALSE) +
+  coord_flip()
+
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill= therapy))+
+  geom_bar(position ="fill")+
+  theme_minimal()+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  # group_by(treatment_sequence) %>% 
+  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+  ggplot(aes(x= raceeth,
+             # y= percent, 
+             fill = treatment_sequence))+
+  geom_bar(
+    position ="fill"
+    )+
+  labs(x = "", title = "The treatment_sequence") +
+  theme_minimal()+
+  # guides(fill = FALSE) +
+  coord_flip()
+
+# Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+#   ggplot(aes(x= chemo))+
+#   geom_bar()+
+#   theme_minimal()+
+#   coord_flip()
+```
+</div>
+</div>
+
+<br>
+
+## 3.Survivals by treatment
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by extentofdebulking
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+# OS by residualdiseasestatus
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+# OS by treatment_sequence
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by extentofdebulking
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+# OS by residualdiseasestatus
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+# OS by treatment_sequence
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+```
+</div>
+</div>
+
+<br>
+<br>
+
+***
+
+<br>
+
+# III.RDI
+
+## 1.RDI summary table
+
+<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
+
+```{r Table 4}
+# Treatment & demo
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl3 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl4 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              type = list(relative_dose_intensity ~ 'continuous'),
+              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              type = list(relative_dose_intensity ~ 'continuous'),
+              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl5, tbl6), quiet = TRUE)
+```
+<br>
+
+# CAN TAKE A LOOK BUT NEED TO VERIFY ALL THE REST
+
+<br>
+
+***
+
+<br>
+
+## 2.Plots RDI
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  geom_boxplot()+
+  ylim(c(-.25, 3.5))+
+  geom_jitter(shape=16)+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal()+
+  facet_wrap(.~ cycle_drugname)
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  geom_violin()+
+  ylim(c(-.25, 3.5))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= cycle_drugname, y= relative_dose_intensity, color = chemotherapy_type))+
+  geom_violin()+
+  ylim(c(-.25, 3.5))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()+
+  coord_flip()
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
+  geom_bar()+
+  theme_minimal()+
+  facet_wrap(.~ chemotherapy_type)
+
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  # geom_boxplot()+
+  ylim(c(-.25, 3.5))+
+  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  theme_minimal() +
+  guides(color=FALSE)+
+  facet_wrap(.~ cycle_drugname)
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = relative_dose_intensity<0.85))+
+  geom_violin()+
+  ylim(c(-.25, 2.5))+
+  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()+
+  facet_wrap(.~ cycle_drugname)
+
+# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+#   # filter(linenumber_new == "1") %>%
+#   ggplot(aes(x= cycle_drugname, y= relative_dose_intensity))+
+#   geom_violin(aes(color=relative_dose_intensity<0.85))+
+#   ylim(c(-.25, 2.5))+
+#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+#   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+#   theme_minimal()
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  facet_wrap(.~ chemotherapy_type)
+
+```
+</div>
+</div>
+
+```{r}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, alpha = relative_dose_intensity<0.85))+
+  geom_violin(aes(fill = cycle_drugname))+
+  ylim(c(-.25, 2.5))+
+  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal()+
+  facet_wrap(.~ raceeth)
+```
+
+A quick summary for the RDI repartition
+```{r}
+Frontline2 <- Frontline# %>% filter(linenumber_new == "1")
+summary(Frontline2$relative_dose_intensity)
+```
+
+<div class = "row">
+<div class = "col-md-6">
+```{r}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
+  geom_bar()+
+  theme_minimal()+
+  facet_wrap(.~ chemotherapy_type)
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
+  geom_bar(position = "fill")+
+  theme_minimal()+
+  coord_flip()+
+  facet_wrap(.~ chemotherapy_type)
+```
+</div>
+</div>
+
+<br>
+
+## 3.Survivals by RDI
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by RDI_grp
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE) %>% 
+#                      filter(exclude != "1")),
+#            title = "OS from diagnosis Overall RDI", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+# 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for platin
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from diagnosis carboplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from diagnosis cisplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for taxel
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from diagnosis all taxel", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# # OS by RDI_grp
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE) %>% 
+#                      filter(exclude != "1")),
+#            title = "OS from first treatment overall RDI", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for platin
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from first treatment carboplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from first treatment cisplatin", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by RDI_grp for taxel
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
+#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
+#                      
+#                      distinct(patientid, .keep_all = TRUE)), 
+#            title = "OS from from first treatment all taxel", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+</div>
+
+<br>
+
+## Survivals RDI by chemotherapy type
+**On the left are Neoadjuvant, on the right are Adjuvant**
+
+<div class = "row">
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
+                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
+                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from first treatment carboplatin",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
+                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
+                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from first treatment cisplatin",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by RDI_grp for taxel
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
+                     filter((exclude != "1") & str_detect(drugname, "taxel"),
+                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from from first treatment all taxel",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
+                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
+                            str_detect(chemotherapy_type, "Adjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from first treatment carboplatin",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
+                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
+                            str_detect(chemotherapy_type, "Adjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from first treatment cisplatin",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by RDI_grp for taxel
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
+                     filter((exclude != "1") & str_detect(drugname, "taxel"),
+                            str_detect(chemotherapy_type, "Adjuvant")) %>%
+
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from from first treatment all taxel",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+</div>
+
+<br>
+<br>
+
+***
+# IV.Hazard Ratio
+
+<span style="color:green">**Table 5 HR**</span>  
+`coxph(Surv(time = month_at_os, event = vitalstatus)~variables`
+```{r Table 5 HR}
+# tbl1 <- Frontline %>%
+#   select(bmi_cat) %>%
+#   tbl_summary(#by = vitalstatus,
+#               statistic = all_categorical() ~ "{Frontline %>% filter(vital == 'Dead') %>% NROW()} death ({n})"
+#               )
+# tbl2 <- coxph(Surv(time = month_at_os,
+#                      event = vitalstatus)~bmi_cat,
+#                 data = Frontline) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+#
+# tbl_merge(list(tbl1, tbl2))
+#
+# coxph(Surv(time = month_at_os,
+#                      event = vitalstatus)~RDI_grp,
+#                 data = Frontline) %>%
+#   tbl_uvregression(y = vitalstatus, exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
+# Frontline %>% select(vitalstatus, bmi, bmi_cat, raceeth) %>%
+# tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = Frontline$month_at_os, event = Frontline$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+#   bold_labels() %>% italicize_levels() #%>%  modify_spanning_header(all_stat_cols() ~ "**Treatment Received**")
+
+tbl1 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+tbl1 <- tbl1 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl2 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
+tbl2 <- tbl2 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl3 <- Frontline %>%
+  filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
+tbl3 <- tbl3 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>%
+  bold_labels() %>%
+  italicize_levels()
+# Cisplatin
+tbl4 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
+tbl4 <- tbl4 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl5 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
+tbl5 <- tbl5 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl6 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
+tbl6 <- tbl6 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl4, tbl5, tbl6),
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant", "cisplatin/Chemo only")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+tbl7 <- Frontline %>%
+  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Neoadjuvant")
+tbl7 <- tbl7 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl8 <- Frontline %>%
+  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Adjuvant")
+tbl8 <- tbl8 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+tbl9 <- Frontline %>%
+  filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
+tbl9 <- tbl9 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl7, tbl8, tbl9),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant", "paclitaxel/Chemo only")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+tbl10 <- Frontline %>%
+  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
+tbl10 <- tbl10 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl11 <- Frontline %>%
+  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
+tbl11 <- tbl11 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+tbl12 <- Frontline %>%
+  filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
+tbl12 <- tbl12 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl10, tbl11, tbl12),
+          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
+***
+# V.Regression
+## By clinical, demo
+`glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = Frontline, family = binomial)`
+```{r}
+# Regression vital status prediction
+model <- glm(vitalstatus ~ bmi_at_dx + bmi_cat + #RDI_grp + 
+               raceeth, data = Frontline %>% 
+               distinct(patientid, .keep_all = TRUE), 
+             family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+```
+
+`glm(vitalstatus ~ histology + tstage + brca1_tumor + brca2_tumor + issurgery + chemotherapy_type, data = Frontline, family = binomial)`
+```{r}
+model <- glm(vitalstatus ~ 
+               histology + tstage + brca1_tumor + brca2_tumor + 
+             issurgery +
+             chemotherapy_type, 
+             data = Frontline %>% 
+               distinct(patientid, .keep_all = TRUE), 
+             family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+```
+
+`glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline, family = binomial)`
+<!-- !!!! Prediction of RDI all drug together!!!! -->
+```{r}
+# Regression RDI prediction
+# model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline, family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+```
+
+### By drug
+<!-- !!! But sometimes we had a switch between cisplatin/carboplatin -->
+```{r}
+#  for carbo
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
+               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
+               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# tbl5 <-
+  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
+
+#  for Cisplatim
+# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
+#                filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# model <- glm(RDI_grp ~ agecat + bmi_cat, data = Frontline %>%
+#                filter(drugname == "cisplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+# 
+# # tbl5 <-
+#   tbl_merge(list(tbl3, tbl4), tab_spanner = c("**cisplatin/Adjuvant**", "**cisplatin/Neoadjuvant**"))
+
+#  for taxel
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
+               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
+               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
+tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+
+# tbl6 <-
+  tbl_merge(list(tbl4, tbl3), tab_spanner = c("**taxel/Adjuvant**", "**taxel/Neoadjuvant**"))
+```
+<br>
+<br>
+
+***

### 2021-10-07 Rmd/rdi analysis.Rmd
Cleaning step 7 - decrease number too much

@@
 
-# `r emo::ji("question_mark")` Reminders/Questions of each capping and calculations:
+# `r emo::ji("question_mark")` Reminders of each capping and formula:
 
@@
     )) %>% 
-  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
+  mutate(chemotherapy_type = 
+           factor(chemotherapy_type, levels = 
+                    c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
   group_by(patientid) %>% 
@@
 
+  group_by(patientid, chemotherapy_type) %>% 
+  mutate(linenumber_adj = dense_rank(linenumber_new)) %>% 
+  ungroup() %>% 
   # 6.Add a 30 day rule to switch linenumber----
@@
   ungroup() %>% 
-  mutate(across(c("linenumber", "linenumber_new"), as.factor))
+  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor))
 
@@
 
+```{r}
+therapy_line %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(chemotherapy_type, therapy, treatment_sequence) %>% 
+  tbl_summary(by = therapy)
+```
+
 ### How many lines did patients received as Neoadjuvant
@@
 Here are all the number of line that patients received as Neoadjuvant containing platinum or taxanes.
-<span style="color:red">**Should we include patients who got more than 1 line as Neoadjuvant?**</span>
 
@@
 
-Here the lines for the 34 patient.
+<!-- Here the lines for the 34 patient. -->
 ```{r, rows.print = 40}
-therapy_line %>% 
-  filter(chemotherapy_type == "Neoadjuvant" &
-           (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
-  select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
-         drugname, episodedate, surgerydate, chemotherapy_type) %>%
-  arrange(patientid, episodedate) %>% 
-  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
-  select(-linenumber)
+# therapy_line %>% 
+#   filter(chemotherapy_type == "Neoadjuvant" &
+#            (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
+#   select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
+#          drugname, episodedate, surgerydate, chemotherapy_type) %>%
+#   arrange(patientid, episodedate) %>% 
+#   distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
+#   select(-linenumber)
 
@@
 Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
-<span style="color:red">**Should we include patients who got a single drug as lot/line?**</span> like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
-<span style="color:red">**Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?**</span> `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev**</span>
+Should we include patients who got a single drug as lot/line? like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
+Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?
+`r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>
 
@@
 # F0017FB3A8828 starts with gemcitabine then have carbo
-therapy_line1 <- therapy_line %>%
+remove_linename_other <- therapy_line %>%
   arrange(patientid, episodedate) %>% 
   mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
-  select(patientid, linename, linenumber, linenumber_new, drug_count, drugname, therapy, treatment_sequence) %>%
+  select(patientid, linename, linenumber, linenumber_new, linenumber_adj, drug_count, 
+         drugname, chemotherapy_type, therapy, treatment_sequence, episodedate) %>%
 
   mutate(remove_linename_other = case_when(
-    linenumber == 1 &
-      # treatment_sequence == "neo + surg + adj" &
+    # keep these drugs in line 1 of upfront chemo and upfront surg
+    linenumber_new == 1 & 
       drug_count == 1 &
-      str_detect(linename, "platin|taxel")       ~ "keep",
-    linenumber == 1 &
+       !str_detect(linename, "platin|taxel")                                 ~ "remove",
+    linenumber_new == 1 &
       drug_count == 2 &
       (
-      (str_detect(linename, "platin") &
-      str_detect(linename, "taxel")) |
-      (str_detect(linename, "platin") &
-      str_detect(linename, "Bev")) |
-        (str_detect(linename, "taxel") &
-      str_detect(linename, "Bev"))
-      )                                           ~ "keep",
-    linenumber == 1 &
-      drug_count == 3 &
-      str_detect(linename, "platin") &
-      str_detect(linename, "taxel") &
-      str_detect(linename, "Bev")                 ~ "keep",
-
-    TRUE                                          ~ NA_character_,
+      !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
+      str_detect(linename, "platin") & str_detect(linename, "Bev") |
+      str_detect(linename, "taxel") & str_detect(linename, "Bev"))
+      )                                                                      ~ "remove",
+    linenumber_new == 1 &
+      drug_count >= 3 &
+      !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
+
+                                                                             ~ "remove",
+    # weird one
+    linenumber_new == 1 &
+      drug_count >= 3 &
+      str_detect(linename, "Niraparib|Gemcitabine")                          ~ "remove",
+
+    # keep these drugs in line 2 of upfront chemo from when line switch
+    linenumber_new == 2 &
+      therapy == "Upfront Chemo" &
+      drug_count == 1 &
+       !str_detect(linename, "platin|taxel")  ~ "remove",
+
+    linenumber_new == 2 &
+      therapy == "Upfront Chemo" &
+      drug_count == 2 &
+      (
+      !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
+      str_detect(linename, "platin") & str_detect(linename, "Bev") |
+      str_detect(linename, "taxel") & str_detect(linename, "Bev"))
+      ) ~ "remove",
+
+    linenumber_new == 2 &
+      therapy == "Upfront Chemo" &
+      drug_count >= 3 &
+      !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
+      # !str_detect(linename, "taxel") &
+      # !str_detect(linename, "Bev")
+                        ~ "remove",
+
+    TRUE                                           ~ NA_character_
   )) %>% 
-  group_by(patientid) %>% 
-  fill(remove_linename_other, .direction = "down") %>% 
-  ungroup() %>% 
-  filter(remove_linename_other == "keep") %>% 
-  select(-remove_linename_other)
-
-therapy_line1 %>% 
+  # group_by(patientid) %>% 
+  # fill(remove_linename_other, .direction = "down") %>% 
+  # ungroup() %>% 
+  arrange(patientid, episodedate) #%>%
+
+remove_linename_other <- remove_linename_other %>% 
+  filter(remove_linename_other == "remove") %>% 
+  distinct(patientid, .keep_all = T)
+
+# remove_linename_other# <- therapy_line %>% 
+  # filter(chemotherapy_type == "Neoadjuvant" &
+  #          linenumber_new != 1)
+remove_linename_other <- paste(remove_linename_other$patientid, collapse = "|")
+
+therapy_line %>% 
   filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
@@
 
-therapy_line1 %>% 
-  filter(linenumber_new == 2, treatment_sequence == "neo + surg + adj") %>% 
+therapy_line %>% 
+  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linename) %>% 
+  tbl_summary(sort = list(everything() ~ "frequency"))
+
+# therapy_line %>% distinct(patientid) %>% nrow()
+
+therapy_line <- therapy_line %>% 
+  # Remove patients with other linename
+  filter(!str_detect(patientid, remove_linename_other)) %>% 
+  arrange(patientid, episodedate)
+# example of keep
+```
+
+```{r}
+therapy_line %>% 
+  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
+         ) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linename) %>% 
+  tbl_summary(sort = list(everything() ~ "frequency"))
+
+therapy_line %>% 
+  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
@@
 ```
-Number of line in Chemotherapy only
-```{r}
-analysis_data %>% 
-  filter(chemotherapy_type == "Chemotherapy only") %>% 
-  arrange(desc(linenumber_new)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new) %>% 
-  tbl_summary()
-```
-<span style="color:red">**Do we keep in the chemotherapy only patients?**</span>  
 <br>
@@
 ***
-<br>
-
-<font size="10">Thanks! `r  emo::ji("party_popper")`</font>
+
+<br>
+<br>
 
@@
 <br>
-<br>
-
-***
-
-<br>
 
@@
 
-```{r}
+```{r RDI calculation}
 Frontline <- Treatment %>% 
   # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
-    group_by(patientid, chemotherapy_type) %>% 
-  mutate(linenumber_adj = dense_rank(linenumber_new)) %>%
+  #   group_by(patientid, chemotherapy_type) %>% 
+  # mutate(linenumber_adj = dense_rank(linenumber_new)) %>%
 
@@
   ungroup() %>% 
-  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE)
+  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
+  mutate(RDI_grp = case_when(
+    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
+    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
+  )) %>% 
+  mutate(RDI_grp = factor(RDI_grp, 
+                           labels = c("correct", "underdose"))) %>% 
+  mutate(RDI_grp1 = case_when(
+    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
+    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
+    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
+    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
+    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
+    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
+  )) %>% 
+  mutate(RDI_grp1 = factor(RDI_grp1, 
+                          labels = c("highly underdose", "underdose", "correct", "perfect", "higher dose", "overdose")))
 ```
@@
 <div class = "col-md-6">
-```{r}
+```{r plot clinical}
 Frontline %>% 
@@
 
-<span style="color:green">**Table 3 Summary treatment data by race**</span>
-
-```{r Table 3}
+<span style="color:green">**Table . Summary treatment data by race**</span>
+
+```{r treatment table}
 # tbl1 <- 
@@
 <div class = "col-md-6">
-```{r}
+```{r treatment plots}
 Frontline %>%
@@
 <div class = "col-md-6">
-```{r, fig.height = 7}
+```{r treatment survival, fig.height = 7}
 # OS by extentofdebulking
@@
 # Treatment & demo
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
   filter(exclude != "1") %>%
@@
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
   filter(exclude != "1") %>%
@@
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
 tbl3 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl4 <-
   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
@@
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl4 <-
+tbl5 <-
   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
 
-tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
+tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
   filter(exclude != "1") %>%
@@
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
+tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
   filter(exclude != "1") %>%
@@
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <-
+tbl7 <-
   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
@@
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <-
+tbl8 <-
   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
 
-tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
+tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
+
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
   filter(exclude != "1") %>%
@@
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
   filter(exclude != "1") %>%
@@
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl3 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl4 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
 
-tbl1 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>%
+tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
   filter(exclude != "1") %>%
@@
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant") %>%
+tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
   filter(exclude != "1") %>%
@@
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "taxel/neoadjuvant \nRDI")) %>%
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
 
-tbl_stack(list(tbl5, tbl6), quiet = TRUE)
-```
-<br>
-
-# CAN TAKE A LOOK BUT NEED TO VERIFY ALL THE REST
+tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl7 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
+  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl8 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
+```
+<br>
 
@@
 <div class = "col-md-6">
-```{r}
+```{r rdi plots}
 Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
@@
 <div class = "col-md-6">
-```{r, fig.height = 7}
+```{r rdi survival, fig.height = 7}
 # OS by RDI_grp
@@
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
-tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant", "carboplatin/Chemo only")) %>%
+# tbl3 <- Frontline %>%
+#   filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
+# tbl3 <- tbl3 %>%
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl1, tbl2),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant")) %>%
   bold_labels() %>%
@@
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl6 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
-tbl6 <- tbl6 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant", "cisplatin/Chemo only")) %>%
+# tbl6 <- Frontline %>%
+#   filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
+# tbl6 <- tbl6 %>%
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl4, tbl5),
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant")) %>%
   bold_labels() %>%
@@
   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl9 <- Frontline %>%
-  filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
-tbl9 <- tbl9 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant", "paclitaxel/Chemo only")) %>%
+# tbl9 <- Frontline %>%
+#   filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
+# tbl9 <- tbl9 %>%
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl7, tbl8),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant")) %>%
   bold_labels() %>%
@@
   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl12 <- Frontline %>%
-  filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
-tbl12 <- tbl12 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl10, tbl11, tbl12),
-          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant", "taxel/Chemo only")) %>%
+# tbl12 <- Frontline %>%
+#   filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
+# tbl12 <- tbl12 %>%
+#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl10, tbl11),
+          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant")) %>%
   bold_labels() %>%
@@
 `glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = Frontline, family = binomial)`
-```{r}
+```{r regression}
 # Regression vital status prediction
@@
 ```{r}
-model <- glm(vitalstatus ~ 
-               histology + tstage + brca1_tumor + brca2_tumor + 
-             issurgery +
-             chemotherapy_type, 
-             data = Frontline %>% 
-               distinct(patientid, .keep_all = TRUE), 
-             family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
+# model <- glm(vitalstatus ~ 
+#                histology + tstage + brca1_tumor + brca2_tumor + 
+#              issurgery +
+#              chemotherapy_type, 
+#              data = Frontline %>% 
+#                distinct(patientid, .keep_all = TRUE), 
+#              family = binomial)
+# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
+# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
+# tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
 ```
@@
 ***
+
+<br>
+
+<font size="10">Yay! `r  emo::ji("party_popper")`</font>
+
+***

### 2021-10-08 Rmd/rdi analysis.Rmd
Fix bug removing line and clean interval of data to bind

@@
     # keep these drugs in line 1 of upfront chemo and upfront surg
-    linenumber_new == 1 & 
-      drug_count == 1 &
-       !str_detect(linename, "platin|taxel")                                 ~ "remove",
-    linenumber_new == 1 &
-      drug_count == 2 &
-      (
-      !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
-      str_detect(linename, "platin") & str_detect(linename, "Bev") |
-      str_detect(linename, "taxel") & str_detect(linename, "Bev"))
-      )                                                                      ~ "remove",
-    linenumber_new == 1 &
-      drug_count >= 3 &
-      !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
-
-                                                                             ~ "remove",
+    # linenumber_new == 1 & 
+    #   drug_count == 1 &
+    #    !str_detect(linename, "platin|taxel")                                 ~ "remove",
+    # linenumber_new == 1 &
+    #   drug_count == 2 &
+    #   (
+    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
+    #   str_detect(linename, "platin") & str_detect(linename, "Bev") |
+    #   str_detect(linename, "taxel") & str_detect(linename, "Bev"))
+    #   )                                                                      ~ "remove",
+    # linenumber_new == 1 &
+    #   drug_count >= 3 &
+    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
+    # 
+    #                                                                          ~ "remove",
     # weird one
     linenumber_new == 1 &
-      drug_count >= 3 &
-      str_detect(linename, "Niraparib|Gemcitabine")                          ~ "remove",
-
-    # keep these drugs in line 2 of upfront chemo from when line switch
+      str_detect(linename, 
+                 "parib|bine|Dox|T|F|Clinical|Cyclo|lumab|Tra|ximab|zole|Aza|trex|Gos|lide|Pem")                       
+                                                                         ~ "remove",
+    linenumber_new == 1 & linename == "Bevacizumab"                      ~ "remove",
     linenumber_new == 2 &
       therapy == "Upfront Chemo" &
-      drug_count == 1 &
-       !str_detect(linename, "platin|taxel")  ~ "remove",
-
+      str_detect(linename, 
+                 "parib|bine|Dox|T|F|Clinical|Cyclo")                       
+                                                                         ~ "remove",
     linenumber_new == 2 &
-      therapy == "Upfront Chemo" &
-      drug_count == 2 &
-      (
-      !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
-      str_detect(linename, "platin") & str_detect(linename, "Bev") |
-      str_detect(linename, "taxel") & str_detect(linename, "Bev"))
-      ) ~ "remove",
-
-    linenumber_new == 2 &
-      therapy == "Upfront Chemo" &
-      drug_count >= 3 &
-      !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
-      # !str_detect(linename, "taxel") &
-      # !str_detect(linename, "Bev")
-                        ~ "remove",
+      therapy == "Upfront Chemo" & linename == "Bevacizumab"             ~ "remove",
+    # keep these drugs in line 2 of upfront chemo from when line switch
+    # linenumber_new == 2 &
+    #   therapy == "Upfront Chemo" &
+    #   drug_count == 1 &
+    #    !str_detect(linename, "platin|taxel")  ~ "remove",
+    #   
+    #   
+    # linenumber_new == 2 &
+    #   therapy == "Upfront Chemo" &
+    #   drug_count == 2 &
+    #   (
+    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
+    #   str_detect(linename, "platin") & str_detect(linename, "Bev") |
+    #   str_detect(linename, "taxel") & str_detect(linename, "Bev"))
+    #   ) ~ "remove",
+    #   
+    #   
+    # linenumber_new == 2 &
+    #   therapy == "Upfront Chemo" &
+    #   drug_count >= 3 &
+    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
+    #   # !str_detect(linename, "taxel") &
+    #   # !str_detect(linename, "Bev")
+    #                     ~ "remove",
 
@@
 
-therapy_line %>% 
-  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
-         ) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename) %>% 
-  tbl_summary(sort = list(everything() ~ "frequency"))
-
-therapy_line %>% 
-  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename) %>% 
-  tbl_summary(sort = list(everything() ~ "frequency"))
+# therapy_line %>% 
+#   filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
+#          ) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(linename) %>% 
+#   tbl_summary(sort = list(everything() ~ "frequency"))
+# 
+# therapy_line %>% 
+#   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(linename) %>% 
+#   tbl_summary(sort = list(everything() ~ "frequency"))
 
@@
 
+First table is frontline Neo, second table is frontline Adj.
 ```{r}
@@
       chemotherapy_type == "Adjuvant" &
-      treatment_sequence == "neo + surg + adj"     ~ 1,
+      therapy == "Upfront Chemo"                   ~ 1,
     TRUE                                           ~ 0
@@
 
-595 patients had part of their first line a switch of line but we have examples of patients for who the switched line last a really short time.  
-Easy example (sorry for the poor looking table `r emo::ji("face_with_raised_eyebrow")`):  
-In this example, 1 cycle is switched from the initial line 1 coded by flatiron to a linenumber_new 2
-
-<br>
-
-| linenumber (coded by flatiron) |  surgery |  linenumber_new that I coded   |  drug    |  
-| ------------------------------ | -------- | ------------------------------ | -------- |  
-|             1                  |          |             1                  | taxel    |  
-| ------------------------------ | -------- | ------------------------------ | -------- |  
-|             1                  |          |             1                  | platin   |  
-| ------------------------------ | -------- | ------------------------------ | -------- |  
-|             1                  |          |             1                  | taxel    |  
-| ------------------------------ | -------- | ------------------------------ | -------- |  
-|             1                  |          |             1                  | platin   |  
-| ------------------------------ | -------- | ------------------------------ | -------- |  
-|             1                  |          |             1                  | taxel    |  
-| ------------------------------ | -------- | ------------------------------ | -------- |  
-|             1                  |          |             1                  | platin   |  
-| ------------------------------ | -------- | ------------------------------ | -------- |  
-|             1                  |          |             1                  | taxel    |  
-| ------------------------------ | -------- | ------------------------------ | -------- |  
-|             1                  | happened |             2                  | platin   |  
-| ------------------------------ | -------- | ------------------------------ | -------- |  
-|             1                  |          |             2                  | taxel    |  
-| ------------------------------ | -------- | ------------------------------ | -------- |
-
-<br>
-
-Here a real example of this type of patient : initial `linenumber` = 1 but had surgery in 09/2019 so part of this line in moved to `linenumber_new` = 2 and then coded as adjuvant line.  
-So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle. <span style="color:red">**Is that correct?**</span>  
+Some patients had part of their first line switched to Adjuvant line. How long is this adjuvant line?
+```{r}
+therapy_line %>% 
+  mutate(line_duration = interval(start = linestartdate, end = lineenddate)/ 
+           duration(n = 1, units = "days")) %>% 
+  filter(linenumber == 1 & linenumber_new == 2) %>% 
+  select(patientid, linenumber, linenumber_new, linenumber_adj, 
+         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= line_duration))+
+  geom_bar(color = "slateblue") +
+  theme_minimal()+
+  ggforce::facet_zoom(xlim = c(0, 200), zoom.size = 1)
+```
+
+<!-- Easy example (sorry for the poor looking table `r emo::ji("face_with_raised_eyebrow")`):   -->
+<!-- In this example, 1 cycle is switched from the initial line 1 coded by flatiron to a linenumber_new 2 -->
+
+<!-- <br> -->
+
+<!-- | linenumber (coded by flatiron) |  surgery |  linenumber_new that I coded   |  drug    |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+<!-- |             1                  |          |             1                  | taxel    |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+<!-- |             1                  |          |             1                  | platin   |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+<!-- |             1                  |          |             1                  | taxel    |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+<!-- |             1                  |          |             1                  | platin   |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+<!-- |             1                  |          |             1                  | taxel    |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+<!-- |             1                  |          |             1                  | platin   |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+<!-- |             1                  |          |             1                  | taxel    |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+<!-- |             1                  | happened |             2                  | platin   |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+<!-- |             1                  |          |             2                  | taxel    |   -->
+<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
+
+<!-- <br> -->
+
+<!-- Here a real example of this type of patient : initial `linenumber` = 1 but had surgery in 09/2019 so part of this line in moved to `linenumber_new` = 2 and then coded as adjuvant line.   -->
+<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle. <span style="color:red">**Is that correct?**</span>   -->
 ```{r Number of patient who switch line2, rows.print=30}
 # Problem F0000AD999ABF but would be good for F003F2BEEDB37
-therapy_line %>% 
-  filter(str_detect(patientid, "F41E15E18E008")) %>% 
-  arrange(patientid, episodedate) %>% 
-  select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
-```
-
-Here an example a little more complicated because the patient had surgery 05/2017 and the same type of switch but then had a 3rd line (used to be line 2 in flatiron).    
-So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle switched to adjuvant and not the longer line witch was coded 2 by flatiron.
-<span style="color:red">**Is that correct?**</span>
+# therapy_line %>% 
+#   filter(str_detect(patientid, "F41E15E18E008")) %>% 
+#   arrange(patientid, episodedate) %>% 
+#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
+```
+
+<!-- Here an example a little more complicated because the patient had surgery 05/2017 and the same type of switch but then had a 3rd line (used to be line 2 in flatiron).     -->
+<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle switched to adjuvant and not the longer line witch was coded 2 by flatiron.
+<span style="color:red">**Is that correct?**</span>   -->
 ```{r, rows.print=30}
-therapy_line %>% 
-  filter(str_detect(patientid, "FC9D28216FEBE")) %>% 
-  arrange(patientid, episodedate) %>% 
-  select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
+# therapy_line %>% 
+#   filter(str_detect(patientid, "FC9D28216FEBE")) %>% 
+#   arrange(patientid, episodedate) %>% 
+#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
 
@@
 ```
-`r emo::ji("question_mark")`  
-<span style="color:red">**So the bigger question is : Is it acceptable to include the patients who have a switched line?**</span>
+<!-- `r emo::ji("question_mark")`   -->
+<!-- <span style="color:red">**So the bigger question is : Is it acceptable to include the patients who have a switched line?**</span> -->
 
@@
 
-`r emo::ji("question_mark")`  
-As you can see on the plots, the interval in days can be pretty big so :  
-<span style="color:red">**Can we take a creatinine value to bind it to a drug when a year long as past between each other?  
-Do we need to set up a maximun gap?  
-Same question for height, weight, bsa and corresponding AUC/target_dose  
-Let me know your advise, I will try to update that for our next meeting**</span> `r emo::ji("smiling_face")`
+`r emo::ji("check")`  
+We decided to take the creatine, weight, bsa measured within a month and in the same cycle of the administration.
 
@@
                           duration(n=1, unit="days"))) %>% 
+  mutate(interval_creat = case_when(
+    interval_creat < 31 &
+      creat_date > linestartdate &
+      creat_date < lineenddate             ~ interval_creat,
+    TRUE                                   ~ NA_real_
+  )) %>% 
   arrange(interval_creat) %>% 
@@
                         duration(n=1, unit="days"))) %>%
+  mutate(interval_weight = case_when(
+    interval_weight < 31 &
+      weight_date > linestartdate &
+      weight_date < lineenddate             ~ interval_weight,
+    TRUE                                    ~ NA_real_
+  )) %>% 
   arrange(interval_weight) %>%
@@
                           duration(n=1, unit="days"))) %>%
+  mutate(interval_bsa = case_when(
+    interval_bsa < 31 &
+      bsa_date > linestartdate &
+      bsa_date < lineenddate               ~ interval_bsa,
+    TRUE                                   ~ NA_real_
+  )) %>% 
   arrange(interval_bsa) %>%
@@
                           duration(n=1, unit="days"))) %>% 
+  mutate(interval_auc = case_when(
+    interval_auc < 31 &
+      auc_date > linestartdate &
+      auc_date < lineenddate               ~ interval_auc,
+    TRUE                                   ~ NA_real_
+  )) %>% 
   arrange(interval_auc) %>% 
@@
   ggplot(aes(x= interval_creat)) +
-  geom_bar() +
-  coord_cartesian(ylim=c(0,50))
+  geom_bar() #+
+  # coord_cartesian(ylim=c(0,50))
 # Treatment %>% 
@@
   ggplot(aes(x= interval_weight)) +
-  geom_bar() +
-  coord_cartesian(ylim=c(0,50))
+  geom_bar() #+
+  # coord_cartesian(ylim=c(0,50))
 Treatment %>% 
   ggplot(aes(x= interval_bsa)) +
-  geom_bar() +
-  coord_cartesian(ylim=c(0,50))
+  geom_bar() #+
+  # coord_cartesian(ylim=c(0,50))
 Treatment %>% 
   ggplot(aes(x= interval_auc)) +
-  geom_bar() +
-  coord_cartesian(ylim=c(0,50))
+  geom_bar() #+
+  # coord_cartesian(ylim=c(0,50))
 ```

### 2021-10-08 Rmd/rdi analysis.Rmd
Fix bug removing line and clean interval of data to bind

@@
 tbl10 <- Frontline %>%
-  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
 tbl10 <- tbl10 %>%
@@
 tbl11 <- Frontline %>%
-  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant")
 tbl11 <- tbl11 %>%
@@
 tbl_stack(list(tbl10, tbl11),
-          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant")) %>%
+          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant")) %>%
   bold_labels() %>%

### 2021-10-13 Rmd/rdi analysis.Rmd
Add model, fix typo/text, add cleaning

@@
   distinct(patientid, .keep_all = TRUE) %>% 
-  select(chemotherapy_type, therapy, treatment_sequence) %>% 
+  select(had_neo, had_adj, therapy) %>% 
+  tbl_summary(by = therapy,
+              type = list(had_neo ~ "dichotomous", 
+                          had_adj ~ "dichotomous"),
+              missing = "no")
+therapy_line %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(therapy, treatment_sequence) %>% 
   tbl_summary(by = therapy)
@@
 `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>
-
+`r emo::ji("check")`   
 ```{r}
@@
 
-Some patients had part of their first line switched to Adjuvant line. How long is this adjuvant line?
+Patients with part of their first line switched to Adjuvant line because of surgery. How long is this adjuvant line?
 ```{r}
@@
   geom_bar(color = "slateblue") +
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   ggforce::facet_zoom(xlim = c(0, 200), zoom.size = 1)
+
 ```
@@
 #   geom_histogram(binwidth = 7)+
-#   theme_minimal()+
+#   theme_minimal(base_size = 14)+
 #   ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
@@
   mutate(interval_creat = case_when(
-    interval_creat < 31 &
+    abs(interval_creat) < 31 &
       creat_date > linestartdate &
@@
   mutate(interval_weight = case_when(
-    interval_weight < 31 &
+    abs(interval_weight) < 31 &
       weight_date > linestartdate &
@@
   mutate(interval_bsa = case_when(
-    interval_bsa < 31 &
+    abs(interval_bsa) < 31 &
       bsa_date > linestartdate &
@@
   mutate(interval_auc = case_when(
-    interval_auc < 31 &
+    abs(interval_auc) < 31 &
       auc_date > linestartdate &
@@
 
-# A little of data analysis
+# II.Data analysis
 ## Explore the dataset
@@
 
+### Number of line in treatment and cycle in frontline (more cleaning needs to be done here)
 Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
+in upfront neo
 ```{r}
 analysis_data %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
   arrange(desc(linenumber_new)) %>% 
@@
   select(linenumber_new) %>% 
+  tbl_summary()
+analysis_data %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  filter(linenumber_new == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
+  tbl_summary()
+analysis_data %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  filter(linenumber_new == 1) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
+  tbl_summary()
+```
+Don't forget we have that "neo + surg"
+```{r}
+analysis_data %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
+  filter(linenumber_new == 1) %>% 
+  arrange(desc(linenumber_new)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linenumber_new) %>% 
+  tbl_summary()
+
+analysis_data %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
+  filter(linenumber_new == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
   tbl_summary()
@@
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  mutate(n = dense_rank(linenumber_new)) %>% 
-  arrange(desc(n)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(n) %>% 
+  arrange(desc(linenumber_adj)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(linenumber_adj) %>% 
+  tbl_summary()
+
+analysis_data %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  filter(linenumber_adj == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
   tbl_summary()
@@
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
-  mutate(n = dense_rank(linenumber_new)) %>% 
-  arrange(desc(n)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(n) %>% 
+  arrange(desc(linenumber_adj)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(linenumber_adj) %>% 
+  tbl_summary()
+
+analysis_data %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
+  filter(linenumber_adj == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
   tbl_summary()
@@
 analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, 
+  select(c(vital, raceeth, 
            agecat, "ageatdx",
@@
 # tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
-#   filter(exclude != "1") %>% 
 #   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
@@
                           labels = c("highly underdose", "underdose", "correct", "perfect", "higher dose", "overdose")))
-```
-
-```{r}
-Frontline %>% distinct(patientid) %>% nrow()
+
+Frontline <- Frontline %>% 
+  filter(str_detect(drugname, "platin|taxel"))
 ```
@@
   geom_bar()+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "BMI category")+
@@
   geom_bar()+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "Histology")+
@@
   geom_bar()+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "Stage")+
@@
   geom_bar()+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "Age cat")+
@@
   geom_bar()+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "BRCA gernline")+
@@
   geom_bar()+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "BRCA tumor")+
@@
   geom_bar(position = "fill")+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "BMI category")+
@@
   geom_bar(position = "fill")+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "Histology")+
@@
   geom_bar(position = "fill")+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "Stage")+
@@
   geom_bar(position = "fill")+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "Age cat")+
@@
   geom_bar(position = "fill")+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "BRCA germline")+
@@
   geom_bar(position = "fill")+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "BRCA tumor")+
@@
   select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
-           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
-           had_neo, had_adj,
-           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
+           "issurgery", "resdz", "debulking", "diff_surg_dx",
+           # had_neo, had_adj,
+           "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
            )) %>% 
@@
 # tbl2 <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-#   filter(exclude != "1") %>% 
 #   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
@@
   distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= issurgery))+
+  geom_bar()+
+  theme_minimal(base_size = 14)+
+  labs(title = "Surgery")+
+  coord_flip()
+
+Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= therapy))+
   geom_bar()+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "Frontline treatment")+
@@
 #   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
-#   theme_minimal()+
+#   theme_minimal(base_size = 14)+
 #   guides(fill = FALSE) +
@@
   labs(x = "", title = "The treatment_sequence") +
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   guides(fill = FALSE) +
@@
   ggplot(aes(x= raceeth, fill= therapy))+
+  geom_bar()+
+  theme_minimal(base_size = 14)+
+  labs(title = "Surgery")+
+  coord_flip()
+
+Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill= therapy))+
   geom_bar(position ="fill")+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   labs(title = "Frontline treatment")+
@@
   labs(x = "", title = "The treatment_sequence") +
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   # guides(fill = FALSE) +
@@
 #   geom_bar()+
-#   theme_minimal()+
+#   theme_minimal(base_size = 14)+
 #   coord_flip()
@@
 ```{r treatment survival, fig.height = 7}
-# OS by extentofdebulking
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 # OS by residualdiseasestatus
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of diagnosis", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 1))
 
@@
 ```{r, fig.height = 7}
-# OS by extentofdebulking
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-# OS by residualdiseasestatus
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
+# # OS by residualdiseasestatus
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of from first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 1))
 
@@
 
-<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>
-
-```{r Table 4}
+Platin  
+```{r Table summary Platin}
 # Treatment & demo
 tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  filter(exclude != "1") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels()
+
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels()
+
+tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels()
+
+tbl4 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels()
+
+tbl5 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels()
+
+tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              type = list(relative_dose_intensity ~ 'continuous'),
+              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
+```
+
+Taxanes
+```{r Table summary Taxanes}
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels()
+
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels()
+
+tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
+  bold_labels()
+
+tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels()
+
+tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels()
+
+tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
+  bold_labels()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
+```
+<br>
+
+<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
+Platin  
+```{r Table4 summary Platin}
+# Treatment & demo
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
 tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
 tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
-
+```
+
+Taxanes
+```{r Table4 summary Taxanes}
 tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-  filter(exclude != "1") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 
-tbl_stack(list(tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
+tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
 ```
@@
   geom_jitter(shape=16)+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
-  theme_minimal()+
-  facet_wrap(.~ cycle_drugname)
+  labs(x = "", title = "Warning 1 dot = RDI for 1 patient") +
+  theme_minimal(base_size = 14)+
+  facet_wrap(.~ drugname, ncol = 2)
 
@@
   # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= cycle_drugname, y= relative_dose_intensity, color = chemotherapy_type))+
+  ggplot(aes(x= drugname, y= relative_dose_intensity, color = chemotherapy_type))+
   geom_violin()+
@@
   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   coord_flip()
@@
   # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
+  ggplot(aes(x= RDI_grp, fill = drugname))+
   geom_bar()+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   facet_wrap(.~ chemotherapy_type)
@@
   geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 drugname per patient") +
+  labs(x = "", title = "Warning 1 dot = RDI for 1 patient") +
   theme_minimal() +
   guides(color=FALSE)+
-  facet_wrap(.~ cycle_drugname)
+  facet_wrap(.~ drugname, ncol = 2)
 
@@
   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal()+
-  facet_wrap(.~ cycle_drugname)
+  theme_minimal(base_size = 14)+
+  facet_wrap(.~ drugname, ncol = 2)
 
@@
   # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp, fill = cycle_drugname))+
+  ggplot(aes(x= RDI_grp, fill = drugname))+
   geom_bar(position = "fill")+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   facet_wrap(.~ chemotherapy_type)
@@
 
-```{r}
+```{r, fig.width=12}
 Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
@@
   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal()+
-  facet_wrap(.~ raceeth)
-```
-
-A quick summary for the RDI repartition
-```{r}
-Frontline2 <- Frontline# %>% filter(linenumber_new == "1")
-summary(Frontline2$relative_dose_intensity)
-```
-
-<div class = "row">
-<div class = "col-md-6">
+  theme_minimal(base_size = 14)+
+  facet_wrap(.~ raceeth, ncol = 1)
+```
+
 ```{r}
@@
   # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
-  geom_bar()+
-  theme_minimal()+
+  ggplot(aes(x= RDI_grp1, fill = drugname))+
+  geom_bar(position = position_dodge())+
+  theme_minimal(base_size = 14)+
   facet_wrap(.~ chemotherapy_type)
 ```
-</div>
-
-<div class = "col-md-6">
+
+```{r}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  ggplot(aes(x= drugname, fill = RDI_grp1))+
+  geom_bar(position = position_dodge())+
+  theme_minimal(base_size = 14)+
+  facet_wrap(.~ chemotherapy_type)+
+  coord_flip()
+```
+
 ```{r}
@@
   # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp1, fill = cycle_drugname))+
+  ggplot(aes(x= drugname, fill = RDI_grp1))+
   geom_bar(position = "fill")+
-  theme_minimal()+
+  theme_minimal(base_size = 14)+
   coord_flip()+
@@
 ```
-</div>
-</div>
+<br>
+<br>
+
+***
 
@@
 
+### Survivals RDI by chemotherapy type
 <div class = "row">
 <div class = "col-md-6">
-```{r rdi survival, fig.height = 7}
+```{r OS dx RDI, fig.height = 7}
 # OS by RDI_grp
 # ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>%
-#                      distinct(patientid, .keep_all = TRUE) %>% 
-#                      filter(exclude != "1")),
+#                      distinct(patientid, .keep_all = TRUE)
+#                      ),
 #            title = "OS from diagnosis Overall RDI",
@@
 #            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for platin
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from diagnosis carboplatin", 
+# ) + guides(colour = guide_legend(ncol = 1))
+
+# OS by RDI_grp for platin
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "carboplatin") & 
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis carboplatin Neo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "cisplatin") & 
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis carboplatin Neo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(drugname == "paclitaxel" & 
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis paclitaxel Neo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "protein") & 
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis PPB Neo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "carboplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis carboplatin Adj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "cisplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis cisplatin Adj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(drugname == "paclitaxel" & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis carboplatin Adj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "protein") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis PPB Adj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "carboplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis carboplatin Adj Upfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "cisplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis cisplatin Adj Upfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(drugname == "paclitaxel" & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis carboplatin Adj Upfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+#                    data=Frontline %>% 
+#                      filter(str_detect(drugname, "proetin") & 
+#                               chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#                      distinct(patientid, .keep_all = TRUE)
+#                    ),
+#            title = "OS from diagnosis PPB Adj Upfront Chemo",
 #            font.main = c(24, "bold", "black"),
@@
 #            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from diagnosis cisplatin", 
+# ) + guides(colour = guide_legend(ncol = 1))
+```
+</div>
+
+<div class = "col-md-6">
+```{r OS treatment RDI, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "carboplatin") & 
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment carboplatin Neo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "cisplatin") & 
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment carboplatin Neo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(drugname == "paclitaxel" & 
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment paclitaxel Neo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "protein") & 
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment PPB Neo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "carboplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment carboplatin Adj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "cisplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment cisplatin Adj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(drugname == "paclitaxel" & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment carboplatin Adj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "protein") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment PPB Adj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "carboplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment carboplatin Adj Upfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "cisplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment cisplatin Adj Upfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(drugname == "paclitaxel" & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment carboplatin Adj Upfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+#                    data=Frontline %>% 
+#                      filter(str_detect(drugname, "proetin") & 
+#                               chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#                      distinct(patientid, .keep_all = TRUE)
+#                    ),
+#            title = "OS from first treatment PPB Adj Upfront Chemo",
 #            font.main = c(24, "bold", "black"),
@@
 #            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for taxel
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from diagnosis all taxel", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-# # OS by RDI_grp
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE) %>% 
-#                      filter(exclude != "1")),
-#            title = "OS from first treatment overall RDI", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for platin
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "carboplatin")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from first treatment carboplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "cisplatin")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from first treatment cisplatin", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by RDI_grp for taxel
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>% 
-#                      filter((exclude != "1") & str_detect(drugname, "taxel")) %>% 
-#                      
-#                      distinct(patientid, .keep_all = TRUE)), 
-#            title = "OS from from first treatment all taxel", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
+# ) + guides(colour = guide_legend(ncol = 1))
 ```
@@
 <br>
-
-## Survivals RDI by chemotherapy type
-**On the left are Neoadjuvant, on the right are Adjuvant**
-
-<div class = "row">
-<div class = "col-md-6">
-```{r, fig.height = 7}
-# OS by RDI_grp for platin
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
-                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
-                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from first treatment carboplatin",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
-                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
-                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from first treatment cisplatin",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for taxel
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
-                     filter((exclude != "1") & str_detect(drugname, "taxel"),
-                            str_detect(chemotherapy_type, "Neoadjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from from first treatment all taxel",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-# OS by RDI_grp for platin
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
-                     filter((exclude != "1") & str_detect(drugname, "carboplatin"),
-                            str_detect(chemotherapy_type, "Adjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from first treatment carboplatin",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
-                     filter((exclude != "1") & str_detect(drugname, "cisplatin"),
-                            str_detect(chemotherapy_type, "Adjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from first treatment cisplatin",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by RDI_grp for taxel
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, data=Frontline %>%
-                     filter((exclude != "1") & str_detect(drugname, "taxel"),
-                            str_detect(chemotherapy_type, "Adjuvant")) %>%
-
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from from first treatment all taxel",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-</div>
-
-<br>
 <br>
@@
 ***
+
 # IV.Hazard Ratio
@@
 <span style="color:green">**Table 5 HR**</span>  
-`coxph(Surv(time = month_at_os, event = vitalstatus)~variables`
+## Univariable
 ```{r Table 5 HR}
-# tbl1 <- Frontline %>%
-#   select(bmi_cat) %>%
-#   tbl_summary(#by = vitalstatus,
-#               statistic = all_categorical() ~ "{Frontline %>% filter(vital == 'Dead') %>% NROW()} death ({n})"
-#               )
-# tbl2 <- coxph(Surv(time = month_at_os,
-#                      event = vitalstatus)~bmi_cat,
-#                 data = Frontline) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-#
-# tbl_merge(list(tbl1, tbl2))
-#
-# coxph(Surv(time = month_at_os,
-#                      event = vitalstatus)~RDI_grp,
-#                 data = Frontline) %>%
-#   tbl_uvregression(y = vitalstatus, exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-
-# Frontline %>% select(vitalstatus, bmi, bmi_cat, raceeth) %>%
-# tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = Frontline$month_at_os, event = Frontline$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
-#   bold_labels() %>% italicize_levels() #%>%  modify_spanning_header(all_stat_cols() ~ "**Treatment Received**")
-
+# Carbo
 tbl1 <- Frontline %>%
@@
 tbl1 <- tbl1 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
                  y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
@@
 tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant")
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
 tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
                  y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl3 <- Frontline %>%
-#   filter(drugname == "carboplatin" & str_detect(chemotherapy_type, "Chemo"))
-# tbl3 <- tbl3 %>%
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl1, tbl2),
-          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant")) %>%
+tbl3 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl3 <- tbl3 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
   bold_labels() %>%
   italicize_levels()
+
 # Cisplatin
@@
 tbl4 <- tbl4 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
                  y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
@@
 tbl5 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant")
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
 tbl5 <- tbl5 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
                  y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-# tbl6 <- Frontline %>%
-#   filter(str_detect(drugname,"cisplatin") & str_detect(chemotherapy_type, "Chemo"))
-# tbl6 <- tbl6 %>%
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl4, tbl5),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant")) %>%
+
+tbl6 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl6 <- tbl6 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl4, tbl5, tbl6),
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
   bold_labels() %>%
@@
 
+# Pacli
 tbl7 <- Frontline %>%
-  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Neoadjuvant")
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
 tbl7 <- tbl7 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
                  y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
@@
 tbl8 <- Frontline %>%
-  filter(str_detect(drugname,"paclitaxel") & chemotherapy_type == "Adjuvant")
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
 tbl8 <- tbl8 %>%
@@
   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-# tbl9 <- Frontline %>%
-#   filter(str_detect(drugname,"paclitaxel") & str_detect(chemotherapy_type, "Chemo"))
-# tbl9 <- tbl9 %>%
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl7, tbl8),
-          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant")) %>%
+tbl9 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl9 <- tbl9 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+tbl_stack(list(tbl7, tbl8, tbl9),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
   bold_labels() %>%
@@
 
+# PPB
 tbl10 <- Frontline %>%
@@
 tbl10 <- tbl10 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
+  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
                  y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
@@
 tbl11 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant")
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
 tbl11 <- tbl11 %>%
@@
                  y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
-  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-# tbl12 <- Frontline %>%
-#   filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
-# tbl12 <- tbl12 %>%
-#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
-tbl_stack(list(tbl10, tbl11),
-          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant")) %>%
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl12 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl12 <- tbl12 %>%
+  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl10, tbl11, tbl12),
+          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+## Multivariable
+`coxph(Surv(time = month_at_os, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` (ageatdx or agecat?)
+```{r Table 5 HR adjusted}
+# Carbo
+tbl1 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+tbl1 <- 
+  coxph(Surv(time = tbl1$month_at_os, 
+             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl1) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
+tbl2 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os, 
+             event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl3 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os, 
+             event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Cisplatin
+tbl4 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
+tbl4 <- 
+  coxph(Surv(time = tbl4$month_at_os, 
+             event = tbl4$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl4) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl5 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl5 <- 
+  coxph(Surv(time = tbl5$month_at_os, 
+             event = tbl5$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl5) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
+tbl6 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl6 <- 
+  coxph(Surv(time = tbl6$month_at_os, 
+             event = tbl6$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl6) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl4, tbl5, tbl6),
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+tbl7 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+tbl7 <- 
+  coxph(Surv(time = tbl7$month_at_os, 
+             event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl7) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl8 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl8 <- 
+  coxph(Surv(time = tbl8$month_at_os, 
+             event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl8) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl9 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl9 <- 
+  coxph(Surv(time = tbl9$month_at_os, 
+             event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl9) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl7, tbl8, tbl9),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# PPB
+tbl10 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
+tbl10 <- 
+  coxph(Surv(time = tbl10$month_at_os, 
+             event = tbl10$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl10) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl11 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl11 <- 
+  coxph(Surv(time = tbl11$month_at_os, 
+             event = tbl11$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl11) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl12 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl12 <- 
+  coxph(Surv(time = tbl12$month_at_os, 
+             event = tbl12$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl12) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl10, tbl11, tbl12),
+          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
   bold_labels() %>%
@@
 
-`glm(vitalstatus ~ histology + tstage + brca1_tumor + brca2_tumor + issurgery + chemotherapy_type, data = Frontline, family = binomial)`
+<!-- `glm(vitalstatus ~ histology + tstage + brca1_tumor + brca2_tumor + issurgery + chemotherapy_type, data = Frontline, family = binomial)` -->
 ```{r}
@@
 
-`glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline, family = binomial)`
+<!-- `glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline, family = binomial)` -->
 <!-- !!!! Prediction of RDI all drug together!!!! -->
@@
 ### By drug
-<!-- !!! But sometimes we had a switch between cisplatin/carboplatin -->
+`RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat`
 ```{r}

### 2021-10-14 Rmd/rdi analysis.Rmd
Update RDI analysis

@@
 
-### How many lines did patients received as Neoadjuvant
-`r emo::ji("question_mark")`  
-Here are all the number of line that patients received as Neoadjuvant containing platinum or taxanes.
-
-```{r}
-therapy_line %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
-  arrange(desc(linenumber_new)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new) %>% 
-  tbl_summary()
-```
-
 ### step 8: Remove patients with more than 1 line as Neo
@@
 
-`r emo::ji("question_mark")`  
-Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
-Should we include patients who got a single drug as lot/line? like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
 Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?
@@
   mutate(remove_linename_other = case_when(
-    # keep these drugs in line 1 of upfront chemo and upfront surg
-    # linenumber_new == 1 & 
-    #   drug_count == 1 &
-    #    !str_detect(linename, "platin|taxel")                                 ~ "remove",
-    # linenumber_new == 1 &
-    #   drug_count == 2 &
-    #   (
-    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
-    #   str_detect(linename, "platin") & str_detect(linename, "Bev") |
-    #   str_detect(linename, "taxel") & str_detect(linename, "Bev"))
-    #   )                                                                      ~ "remove",
-    # linenumber_new == 1 &
-    #   drug_count >= 3 &
-    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
-    # 
-    #                                                                          ~ "remove",
-    # weird one
     linenumber_new == 1 &
@@
       therapy == "Upfront Chemo" & linename == "Bevacizumab"             ~ "remove",
-    # keep these drugs in line 2 of upfront chemo from when line switch
-    # linenumber_new == 2 &
-    #   therapy == "Upfront Chemo" &
-    #   drug_count == 1 &
-    #    !str_detect(linename, "platin|taxel")  ~ "remove",
-    #   
-    #   
-    # linenumber_new == 2 &
-    #   therapy == "Upfront Chemo" &
-    #   drug_count == 2 &
-    #   (
-    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
-    #   str_detect(linename, "platin") & str_detect(linename, "Bev") |
-    #   str_detect(linename, "taxel") & str_detect(linename, "Bev"))
-    #   ) ~ "remove",
-    #   
-    #   
-    # linenumber_new == 2 &
-    #   therapy == "Upfront Chemo" &
-    #   drug_count >= 3 &
-    #   !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
-    #   # !str_detect(linename, "taxel") &
-    #   # !str_detect(linename, "Bev")
-    #                     ~ "remove",
-
     TRUE                                           ~ NA_character_
   )) %>% 
-  # group_by(patientid) %>% 
-  # fill(remove_linename_other, .direction = "down") %>% 
-  # ungroup() %>% 
-  arrange(patientid, episodedate) #%>%
+  arrange(patientid, episodedate)
 
@@
 
-# remove_linename_other# <- therapy_line %>% 
-  # filter(chemotherapy_type == "Neoadjuvant" &
-  #          linenumber_new != 1)
 remove_linename_other <- paste(remove_linename_other$patientid, collapse = "|")
-
-# therapy_line %>% 
-#   filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
-#          ) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(linename) %>% 
-#   tbl_summary(sort = list(everything() ~ "frequency"))
-# 
-# therapy_line %>% 
-#   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(linename) %>% 
-#   tbl_summary(sort = list(everything() ~ "frequency"))
-
-# therapy_line %>% distinct(patientid) %>% nrow()
 
@@
   arrange(patientid, episodedate)
-# example of keep
 ```
@@
 therapy_line %>% 
-  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
+  filter(linenumber == 1
          ) %>% 
@@
 
-`r therapy_line %>% filter(str_detect(linename, "Car") & drugname == "cisplatin") %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line and were removed.  
-`r therapy_line %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin") %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line and were removed.
+`r therapy_line %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line and were removed.
+`r therapy_line %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line and were removed.
 
@@
 ```{r}
-# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
-# therapy_line %>% 
-#   filter(str_detect(linename, "Car") &
-#            drugname == "cisplatin") %>%
-#   distinct(patientid) %>% nrow()
-# 
-# therapy_line %>% 
-#   filter(str_detect(linename, "Cisplatin") &
-#            drugname == "carboplatin") %>%
-#   distinct(patientid) %>% nrow()
+# switch cispl vs carbo  Car > Cis F1BF7208F0E96
 
 remove_switch <- therapy_line %>% 
-  filter(
-    (str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
-  (str_detect(linename, "Cisplatin") & drugname == "carboplatin")
+  filter(linenumber_adj == 1 &
+    ((str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
+  (str_detect(linename, "Cisplatin") & drugname == "carboplatin"))
   ) %>%
@@
 
-```{r}
-# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
-# therapy_line %>% 
-#   filter(str_detect(linename, "Pacli") &
-#            drugname == "docetaxel") %>%
-#   distinct(patientid) %>% nrow()
-# therapy_line %>% 
-#   filter(str_detect(linename, "Doce") &
-#            drugname == "Paclitaxel") %>%
-#   distinct(patientid) %>% nrow()
-```
-`r therapy_line %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel") %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.  
-I am removing these patients for now but <span style="color:red">**Do we need to remove the patients that switch from paclitaxel to docetaxel and vice versa since the dosing calculating is the same for both?**</span>
-
-`r emo::ji("question_mark")`
-
-<span style="color:red">**Are you good with thatl?**</span>
+`r therapy_line %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.
+I am removing these patients
 
@@
   filter(
-    str_detect(linename, "Pacli") & drugname == "docetaxel"
+    str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1
   ) %>%
@@
 `r emo::ji("check")`  
-We decided to take the creatine, weight, bsa measured within a month and in the same cycle of the administration.
+We decided to take the creatinine, weight, bsa measured within a month and in the same cycle of the administration AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line
 
@@
   mutate(interval_creat = case_when(
-    abs(interval_creat) < 31 &
-      creat_date > linestartdate &
-      creat_date < lineenddate             ~ interval_creat,
+    (therapy == "Upfront Surgery" &
+       interval_creat < 31 &
+       creat_date < lineenddate &
+       creat_date > surgerydate)                  ~ interval_creat,
+
+    therapy == "Upfront Chemo" &
+      (
+        (chemotherapy_type == "Neoadjuvant" &
+           interval_creat < 31 &
+           creat_date < surgerydate) |
+          (chemotherapy_type == "Adjuvant" &
+             interval_creat < 31 &
+             creat_date < lineenddate &
+             creat_date > surgerydate)
+      )                                          ~ interval_creat,
     TRUE                                         ~ NA_real_
@@
   mutate(interval_weight = case_when(
-    abs(interval_weight) < 31 &
-      weight_date > linestartdate &
-      weight_date < lineenddate             ~ interval_weight,
+    (therapy == "Upfront Surgery" &
+       interval_weight < 31 &
+       weight_date < lineenddate &
+       weight_date > surgerydate)                  ~ interval_weight,
+
+    therapy == "Upfront Chemo" &
+      (
+        (chemotherapy_type == "Neoadjuvant" &
+           interval_weight < 31 &
+           weight_date < surgerydate) |
+          (chemotherapy_type == "Adjuvant" &
+             interval_weight < 31 &
+             weight_date < lineenddate &
+             weight_date > surgerydate)
+      )                                          ~ interval_weight,
     TRUE                                         ~ NA_real_
@@
   mutate(interval_bsa = case_when(
-    abs(interval_bsa) < 31 &
-      bsa_date > linestartdate &
-      bsa_date < lineenddate               ~ interval_bsa,
+    (therapy == "Upfront Surgery" &
+       interval_bsa < 31 &
+       bsa_date < lineenddate &
+       bsa_date > surgerydate)                  ~ interval_bsa,
+
+    therapy == "Upfront Chemo" &
+      (
+        (chemotherapy_type == "Neoadjuvant" &
+           interval_bsa < 31 &
+           bsa_date < surgerydate) |
+          (chemotherapy_type == "Adjuvant" &
+             interval_bsa < 31 &
+             bsa_date < lineenddate &
+             bsa_date > surgerydate)
+      )                                          ~ interval_bsa,
     TRUE                                         ~ NA_real_
@@
   mutate(interval_auc = case_when(
-    abs(interval_auc) < 31 &
-      auc_date > linestartdate &
-      auc_date < lineenddate               ~ interval_auc,
+    (therapy == "Upfront Surgery" &
+       interval_auc < 31 &
+       auc_date < lineenddate &
+       auc_date > surgerydate)                  ~ interval_auc,
+
+    therapy == "Upfront Chemo" &
+      (
+        (chemotherapy_type == "Neoadjuvant" &
+           interval_auc < 31 &
+           auc_date < surgerydate) |
+          (chemotherapy_type == "Adjuvant" &
+             interval_auc < 31 &
+             auc_date < lineenddate &
+             auc_date > surgerydate)
+      )                                          ~ interval_auc,
     TRUE                                         ~ NA_real_
@@
 ## **Number of patients in final dataset is `r Treatment %>% distinct(patientid) %>% nrow()`**
-
-<br>
-
-***
-
-<br>
-
-# II.Data analysis
-## Explore the dataset
-
-```{r}
-analysis_data <- Treatment
-```
-
-### Number of line in treatment and cycle in frontline (more cleaning needs to be done here)
-Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
-in upfront neo
-```{r}
-analysis_data %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  arrange(desc(linenumber_new)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new) %>% 
-  tbl_summary()
-analysis_data %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  filter(linenumber_new == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
-analysis_data %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  filter(linenumber_new == 1) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
-```
-Don't forget we have that "neo + surg"
-```{r}
-analysis_data %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
-  filter(linenumber_new == 1) %>% 
-  arrange(desc(linenumber_new)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new) %>% 
-  tbl_summary()
-
-analysis_data %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
-  filter(linenumber_new == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
-```
-Number of Adjuvant line in patients with upfront neo
-```{r}
-analysis_data %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  arrange(desc(linenumber_adj)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(linenumber_adj) %>% 
-  tbl_summary()
-
-analysis_data %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  filter(linenumber_adj == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
-```
-Number of Adjuvant line in patients with upfront surgery
-```{r}
-analysis_data %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
-  arrange(desc(linenumber_adj)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(linenumber_adj) %>% 
-  tbl_summary()
-
-analysis_data %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
-  filter(linenumber_adj == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
-```
-<br>
-
-# Missingness
-Here some representation of missingness in our data:  
-- In the first plot (horizontal bar), `r is.na(analysis_data$height_at_dx) %>% sum()` data is missing for height closest to dx but `r analysis_data %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
-Because these parameters overlap only 25 patients will have missing value for all of them.
-- In the second plot (horizontal bar), `r is.na(analysis_data$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(analysis_data$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation).
-the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
-```{r}
-library(naniar)
-analysis_data %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
-  gg_miss_upset()
-
-analysis_data %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
-  gg_miss_upset()
-
-# is.na(analysis_data$CrCl) %>% sum()
-# is.na(analysis_data$amount) %>% sum()
-# is.na(analysis_data$target_auc) %>% sum()
-
-# analysis_data %>% filter(is.na(amount)) %>%
-#     distinct(patientid, .keep_all = TRUE) %>% nrow()
-# 
-# analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
-#     distinct(patientid, .keep_all = TRUE) %>% nrow()
-```
-If we remove patients who have at least 1 missing amount administered, we lose `r analysis_data %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
-
-If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r analysis_data %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
-
-# Analysis
-
-## 1.Clinical summary table
-
-<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
-```{r Table 1}
-analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(vital, raceeth, 
-           agecat, "ageatdx",
-
-           bmi_at_dx, bmi_cat, 
-           weight_at_dx, height_at_dx, bsa_at_dx,
-
-           "histology", "stagecat",
-
-           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
-           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown")) %>% 
-  tbl_summary() %>% bold_labels()
-```
-
-<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
-```{r Table 2}
-analysis_data %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "vital",
-           agecat, "ageatdx",
-
-           "bmi_at_dx", bmi_cat, "BSA",
-           "stagecat",
-
-           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
-           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
-
-           "hrd_tissue", "gis_tissue")) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-```
-<br>
-
-***
-
-<br>
-
-<!-- # II.Analysis Treatment -->
-
-## 1.Treatment summary table
-
-<span style="color:green">**Table 3 Summary treatment data by race**</span>
-
-```{r Table 3}
-# tbl1 <- 
-  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
-           "debulking",
-           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
-           )) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
-#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
-#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
-#            )) %>% 
-#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
-```
-<br>
-
-***
-
-<br>
-<br>
-
-***
-
-<br>
-
-# RDI calculation
-
-RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.
 
@@
   mutate(RDI_grp1 = factor(RDI_grp1, 
-                          labels = c("highly underdose", "underdose", "correct", "perfect", "higher dose", "overdose")))
+                          labels = c("correct", "highly underdose", "underdose", "perfect", "higher dose", "overdose")))
 
@@
 ```
-
-# Analysis
-
-## 2.Plots Clinical
+<br>
+<br>
+<br>
+
+***
+
+<br>
+
+# II.Data analysis
+## Explore the dataset
+
+### Number of line in treatment and cycle in frontline (more cleaning needs to be done here)
+Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
+in upfront neo
+```{r}
+Frontline %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  arrange(desc(linenumber_new)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linenumber_new) %>% 
+  tbl_summary()
+Frontline %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  filter(linenumber_new == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
+  tbl_summary()
+Frontline %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  filter(linenumber_new == 1) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
+  tbl_summary()
+```
+Don't forget we have that "neo + surg"
+```{r}
+Frontline %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
+  filter(linenumber_new == 1) %>% 
+  arrange(desc(linenumber_new)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linenumber_new) %>% 
+  tbl_summary()
+
+Frontline %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
+  filter(linenumber_new == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
+  tbl_summary()
+```
+Number of Adjuvant line in patients with upfront neo
+```{r}
+Frontline %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  arrange(desc(linenumber_adj)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(linenumber_adj) %>% 
+  tbl_summary()
+
+Frontline %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  filter(linenumber_adj == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
+  tbl_summary()
+```
+Number of Adjuvant line in patients with upfront surgery
+```{r}
+Frontline %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
+  arrange(desc(linenumber_adj)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(linenumber_adj) %>% 
+  tbl_summary()
+
+Frontline %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
+  filter(linenumber_adj == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(cycle_increment) %>% 
+  tbl_summary()
+```
+<br>
+
+## Missingness
+Here some representation of missingness in our data:  
+- In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
+Because these parameters overlap only 25 patients will have missing value for all of them.
+- In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation).
+the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
+```{r}
+library(naniar)
+Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
+  gg_miss_upset()
+
+Frontline %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
+  gg_miss_upset()
+
+# is.na(Frontline$CrCl) %>% sum()
+# is.na(Frontline$amount) %>% sum()
+# is.na(Frontline$target_auc) %>% sum()
+
+# Frontline %>% filter(is.na(amount)) %>%
+#     distinct(patientid, .keep_all = TRUE) %>% nrow()
+# 
+# Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
+#     distinct(patientid, .keep_all = TRUE) %>% nrow()
+```
+If we remove patients who have at least 1 missing amount administered, we lose `r Frontline %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
+
+If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
+
+# Clinical Analysis
+
+## 1.Clinical summary table
+
+<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
+```{r Table 1}
+Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(vital, raceeth, 
+           agecat, "ageatdx",
+
+           bmi_at_dx, bmi_cat, 
+           weight_at_dx, height_at_dx, bsa_at_dx,
+
+           "histology", "stagecat",
+
+           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
+           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown")) %>% 
+  tbl_summary() %>% bold_labels()
+```
+
+<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
+```{r Table 2}
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "vital",
+           agecat, "ageatdx",
+
+           "bmi_at_dx", bmi_cat, "BSA",
+           "stagecat",
+
+           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
+           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
+
+           "hrd_tissue", "gis_tissue")) %>% 
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+```
+<br>
+
+## 2.Clinical Plots
 <div class = "row">
@@
 
-# II.Analysis Treatment
+# II.Treatment Analysis
 
@@
 
-<span style="color:green">**Table . Summary treatment data by race**</span>
-
-```{r treatment table}
+<span style="color:green">**Table 3 Summary treatment data by race**</span>
+```{r Table 3}
 # tbl1 <- 
   Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
-           "issurgery", "resdz", "debulking", "diff_surg_dx",
-           # had_neo, had_adj,
-           "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
+  select(c(raceeth,
+           "debulking", "therapy", "treatment_sequence"
            )) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p(
-    # test.args = all_tests("chisq.test") ~ list(workspace=2e9)
-    ) %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
-#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
-#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
-#            )) %>% 
-#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
-```
-<br>
-
-## 2.Plots Treatment
+  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+```
+<br>
+
+## 2.Treatment Plots
 <div class = "row">
@@
 ```{r treatment plots}
-Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= issurgery))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Surgery")+
-  coord_flip()
-
 Frontline %>%
@@
   # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-  ggplot(aes(x= treatment_sequence,
-             # y= percent, 
-             fill = treatment_sequence))+
+  ggplot(aes(x= treatment_sequence))+
   geom_bar(
@@
 ```{r}
-Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill= therapy))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Surgery")+
-  coord_flip()
-
 Frontline %>%
@@
 ```{r treatment survival, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=Frontline %>%
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 ```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ issurgery, data=Frontline %>%
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 # III.RDI
-
-## 1.RDI summary table
-
-Platin  
-```{r Table summary Platin}
-# Treatment & demo
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels()
-
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels()
-
-tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels()
-
-tbl4 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels()
-
-tbl5 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels()
-
-tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              type = list(relative_dose_intensity ~ 'continuous'),
-              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels()
-
-tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
-```
-
-Taxanes
-```{r Table summary Taxanes}
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels()
-
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels()
-
-tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
-  bold_labels()
-
-tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels()
-
-tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels()
-
-tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
-  bold_labels()
-
-tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
-```
-<br>
-
-<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
-Platin  
-```{r Table4 summary Platin}
-# Treatment & demo
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl3 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl4 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl7 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              type = list(relative_dose_intensity ~ 'continuous'),
-              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              type = list(relative_dose_intensity ~ 'continuous'),
-              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl8 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
-```
-
-Taxanes
-```{r Table4 summary Taxanes}
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl3 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl4 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl7 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl8 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
-```
-<br>
-
-<br>
-
-***
-
-<br>
-
-## 2.Plots RDI
+RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.
+
+```{r echo=TRUE}
+# RDI_grp = case_when(
+#     mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
+#     mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
+#   ))
+```
+Start with plotting :
+
+## 1.Plots RDI
 
@@
 <div class = "col-md-6">
-```{r rdi plots}
+```{r rdi plots, fig.height=10}
 Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
@@
   geom_boxplot()+
-  ylim(c(-.25, 3.5))+
+  # ylim(c(-.25, 3.5))+
   geom_jitter(shape=16)+
@@
 
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height=10}
 Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
-  geom_violin()+
-  ylim(c(-.25, 3.5))+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal()
-
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= drugname, y= relative_dose_intensity, color = chemotherapy_type))+
-  geom_violin()+
-  ylim(c(-.25, 3.5))+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal(base_size = 14)+
-  coord_flip()
-
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp, fill = drugname))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  facet_wrap(.~ chemotherapy_type)
-
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
   ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
@@
 
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = relative_dose_intensity<0.85))+
-  geom_violin()+
-  ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal(base_size = 14)+
-  facet_wrap(.~ drugname, ncol = 2)
+# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+#   # filter(linenumber_new == "1") %>%
+#   ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = relative_dose_intensity<0.85))+
+#   geom_violin()+
+#   ylim(c(-.25, 2.5))+
+#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+#   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+#   theme_minimal(base_size = 14)+
+#   facet_wrap(.~ drugname, ncol = 2)
 
@@
 
+```
+</div>
+</div>
+
+```{r}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+  geom_violin()+
+  # ylim(c(-.25, 2.5))+
+  theme_minimal(base_size = 14)+
+  facet_wrap(.~ drugname, ncol = 2, scales = "free_y")
+
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  ggplot(aes(x= drugname, fill = RDI_grp))+
+  geom_bar(position = position_dodge())+
+  theme_minimal(base_size = 14)+
+  facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
+  coord_flip()
+
 Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
   # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp, fill = drugname))+
-  geom_bar(position = "fill")+
+  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = chemotherapy_type))+
+  geom_violin()+
+  ylim(c(-.25, 3.5))+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
   theme_minimal(base_size = 14)+
-  facet_wrap(.~ chemotherapy_type)
-
-```
-</div>
-</div>
-
-```{r, fig.width=12}
+  coord_flip()+
+  facet_wrap(drugname ~ RDI_grp, ncol = 2)
+
 Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
   # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, alpha = relative_dose_intensity<0.85))+
-  geom_violin(aes(fill = cycle_drugname))+
-  ylim(c(-.25, 2.5))+
-  scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal(base_size = 14)+
-  facet_wrap(.~ raceeth, ncol = 1)
-```
-
-```{r}
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= RDI_grp1, fill = drugname))+
-  geom_bar(position = position_dodge())+
-  theme_minimal(base_size = 14)+
-  facet_wrap(.~ chemotherapy_type)
-```
-
-```{r}
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  ggplot(aes(x= drugname, fill = RDI_grp1))+
-  geom_bar(position = position_dodge())+
+  ggplot(aes(x= drugname, fill = RDI_grp))+
+  geom_bar(position = "fill")+
   theme_minimal(base_size = 14)+
@@
   coord_flip()
+```
+
+```{r, fig.width=12, fig.height=20}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= raceeth, y= relative_dose_intensity#, alpha = relative_dose_intensity<0.85
+             ))+
+  geom_boxplot(aes(fill = drugname))+
+  ylim(c(0, 2))+
+  scale_colour_discrete()+
+  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  theme_minimal(base_size = 14)+
+  facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")
+```
+
+As you will saw, we have a big spread of RDI (it is more than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI or being underdose or overdose
+
+```{r echo=TRUE}
+# (RDI_grp1 = case_when(
+#     mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
+#     mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
+#     mean_RDI_per_chemotype_drug < 1                  ~ "correct",
+#     mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
+#     mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
+#     mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
+#   ))
+```
+
+```{r, fig.width=12}
+Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+  ggplot(aes(x= RDI_grp1, fill = drugname))+
+  geom_bar(position = position_dodge())+
+  theme_minimal(base_size = 10)+
+  facet_wrap(drugname~ chemotherapy_type, ncol = 2, scales = "free")+
+  coord_flip()
+```
+
+```{r, fig.width=12}
+# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+#   ggplot(aes(x= drugname, fill = RDI_grp1))+
+#   geom_bar(position = position_dodge())+
+#   theme_minimal(base_size = 10)+
+#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
+#   coord_flip()
 ```
@@
   geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
+  theme_minimal(base_size = 10)+
   coord_flip()+
@@
 <br>
+<br>
+
+## 1.RDI summary table
+
+<span style="color:green">**Platin**</span>  
+```{r Table summary Platin}
+# Treatment & demo
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels()
+
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels()
+
+tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels()
+
+tbl4 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels()
+
+tbl5 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels()
+
+tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              type = list(relative_dose_intensity ~ 'continuous'),
+              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
+```
+
+<span style="color:green">**Taxanes**</span>  
+```{r Table summary Taxanes}
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels()
+
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels()
+
+tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
+  bold_labels()
+
+tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels()
+
+tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels()
+
+tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(
+              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
+  bold_labels()
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
+```
+<br>
+
+<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
+Platin  
+```{r Table4 summary Platin}
+# Treatment & demo
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl3 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl4 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl7 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              type = list(relative_dose_intensity ~ 'continuous'),
+              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              type = list(relative_dose_intensity ~ 'continuous'),
+              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl8 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
+```
+
+Taxanes
+```{r Table4 summary Taxanes}
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl3 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl4 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl5 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl6 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl7 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl8 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
+```
+<br>
+
+<br>
+
+***
+
 <br>
@@
                    ),
-           title = "OS from diagnosis carboplatin Neo",
+           title = "OS from diagnosis cisplatin Neo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis carboplatin Adj Upfront Surgery",
+           title = "OS from diagnosis carboplatin Adj \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis cisplatin Adj Upfront Surgery",
+           title = "OS from diagnosis cisplatin Adj \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis carboplatin Adj Upfront Surgery",
+           title = "OS from diagnosis paclitaxel Adj \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis PPB Adj Upfront Surgery",
+           title = "OS from diagnosis PPB Adj \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis carboplatin Adj Upfront Chemo",
+           title = "OS from diagnosis carboplatin Adj \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis cisplatin Adj Upfront Chemo",
+           title = "OS from diagnosis cisplatin Adj \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis carboplatin Adj Upfront Chemo",
+           title = "OS from diagnosis paclitaxel Adj \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment carboplatin Neo",
+           title = "OS from first treatment cisplatin Neo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment carboplatin Adj Upfront Surgery",
+           title = "OS from first treatment carboplatin Adj \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment cisplatin Adj Upfront Surgery",
+           title = "OS from first treatment cisplatin Adj \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment carboplatin Adj Upfront Surgery",
+           title = "OS from first treatment paclitaxel Adj \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment PPB Adj Upfront Surgery",
+           title = "OS from first treatment PPB Adj \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment carboplatin Adj Upfront Chemo",
+           title = "OS from first treatment carboplatin Adj \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment cisplatin Adj Upfront Chemo",
+           title = "OS from first treatment cisplatin Adj \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment carboplatin Adj Upfront Chemo",
+           title = "OS from first treatment pacliatxel Adj \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 <span style="color:green">**Table 5 HR**</span>
+
 ## Univariable

### 2021-10-15 Rmd/rdi analysis.Rmd
Fix bug

@@
   )) %>% 
+  group_by(patientid) %>%
   mutate(first_treatment_date = case_when(
@@
   )) %>% 
+  ungroup() %>% 
   mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
@@
 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ 1, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
 # OS by therapy
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),

### 2021-10-20 Rmd/rdi analysis.Rmd
Fix cleaning and calculation

@@
 
-# `r emo::ji("question_mark")` Reminders of each capping and formula:
+# `r emo::ji("spiral_notepad")` This report is using **actual weight**
+
+***
+
+# `r emo::ji("spiral_notepad")` Reminders of each capping and formula:
 
@@
 
-**We start with a number of patient who has drug info of `r drugs %>% distinct(patientid) %>% nrow()`.**
+**We start with a number of patient who have drug info of `r drugs %>% distinct(patientid) %>% nrow()`.**
 
@@
   ungroup() %>% 
-  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor))
+  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
+  group_by(patientid, linenumber_new) %>% 
+  mutate(linestartdate_new = first(episodedate)) %>% 
+  mutate(lineenddate_new = last(episodedate)) %>% 
+  ungroup()
 
@@
 ```
+
+`r emo::ji("question_mark")` **Are we keeping the patients who had Neo + surgery without Adjuvant?**
 
@@
 
-Patients with part of their first line switched to Adjuvant line because of surgery. How long is this adjuvant line?
+For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line?
 ```{r}
 therapy_line %>% 
-  mutate(line_duration = interval(start = linestartdate, end = lineenddate)/ 
+  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
            duration(n = 1, units = "days")) %>% 
@@
   ggplot(aes(x= line_duration))+
-  geom_bar(color = "slateblue") +
+  geom_histogram(color = "slateblue", fill = "grey", binwidth = 7) +
   theme_minimal(base_size = 14)+
-  ggforce::facet_zoom(xlim = c(0, 200), zoom.size = 1)
-
+  labs(x="Line duration", 
+       y="Number of Patient",
+       caption = "Each bar represents 7 days, bottom plot is zoomed in")+
+  ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
+
+```
+Several patients have a short line.  
+`r emo::ji("question_mark")` **Should me remove the patient with a line during less than a cycle
+
+```{r}
+therapy_line %>% 
+  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
+           duration(n = 1, units = "days")) %>% 
+  filter(linenumber == 1 & linenumber_new == 2) %>% 
+  select(patientid, drugname, episodedate, line_duration, 
+         chemotherapy_type, therapy, 
+         linenumber, linenumber_new, linenumber_adj) %>% 
+  filter(line_duration < 30)
 ```
@@
 therapy_cycle <- therapy_line %>% 
+  filter(str_detect(drugname, "taxel|platin")) %>% # Need to that now for patient who got Bev only once per line F02D8628A5394
 
@@
   mutate(cycle_drugname = case_when(
-    cycle_count_perline == drugname_count_perline          ~ drugname,
+    cycle_count_perline == drugname_count_perline          ~ cycle_drugname,
     TRUE                                                   ~ NA_character_
@@
   group_by(patientid, linenumber_new, cycle_drugname) %>%
-  mutate(cycle_inc = row_number(cycle_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
+  mutate(cycle_increment = row_number(cycle_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
+  # F01D908A013B7 has more pacli at the end but in the same line
 
@@
   # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
-  arrange(patientid, episodedate, cycle_inc) %>% 
+  arrange(patientid, episodedate, cycle_increment) %>% 
   group_by(patientid, linenumber_new) %>%
-  mutate(cycle_increment = cycle_inc) %>% 
+  # mutate(cycle_increment = cycle_inc) %>% 
   fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
@@
 
-  group_by(patientid, linenumber_new) %>% 
-  mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
-         cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
-
-  # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
-  mutate(n = row_number(drugname)) %>%
-
-  mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
-  fill(base_days_between_cycle, .direction = "downup") %>% 
-  mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
-                                       (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
-  # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
-  group_by(patientid, linenumber_new) %>%
-  mutate(drug_count_perline = n()) %>%
-  mutate(skipped_cycle_indays1 = ifelse(
-    (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
-  )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
-  # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
-  group_by(patientid) %>% 
-  mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
+  # # CODE FOR SKIPPED CYCLE
+  # group_by(patientid, linenumber_new) %>% 
+  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
+  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
+  # 
+  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
+  # mutate(n = row_number(drugname)) %>%
+  # 
+  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
+  # fill(base_days_between_cycle, .direction = "downup") %>% 
+  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
+  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
+  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
+  # group_by(patientid, linenumber_new) %>%
+  # mutate(drug_count_perline = n()) %>%
+  # mutate(skipped_cycle_indays1 = ifelse(
+  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
+  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
+  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
+  # group_by(patientid) %>% 
+  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
   ungroup()
@@
 `r emo::ji("check")`  
-We decided to take the creatinine, weight, bsa measured within a month and in the same cycle of the administration AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line
+We decided to take the creatinine, weight, bsa measured within a month of the cycle start date AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line
 
@@
        interval_creat < 31 &
-       creat_date < lineenddate &
+       # creat_date < lineenddate &
        creat_date > surgerydate)                  ~ interval_creat,
@@
              interval_creat < 31 &
-             creat_date < lineenddate &
+             # creat_date < lineenddate &
              creat_date > surgerydate)
@@
        interval_weight < 31 &
-       weight_date < lineenddate &
+       # weight_date < lineenddate &
        weight_date > surgerydate)                  ~ interval_weight,
@@
              interval_weight < 31 &
-             weight_date < lineenddate &
+             # weight_date < lineenddate &
              weight_date > surgerydate)
@@
        interval_bsa < 31 &
-       bsa_date < lineenddate &
+       # bsa_date < lineenddate &
        bsa_date > surgerydate)                  ~ interval_bsa,
@@
              interval_bsa < 31 &
-             bsa_date < lineenddate &
+             # bsa_date < lineenddate &
              bsa_date > surgerydate)
@@
        interval_auc < 31 &
-       auc_date < lineenddate &
+       # auc_date < lineenddate &
        auc_date > surgerydate)                  ~ interval_auc,
@@
              interval_auc < 31 &
-             auc_date < lineenddate &
+             # auc_date < lineenddate &
              auc_date > surgerydate)
@@
                           labels = c("correct", "highly underdose", "underdose", "perfect", "higher dose", "overdose")))
-
-Frontline <- Frontline %>% 
-  filter(str_detect(drugname, "platin|taxel"))
 ```
@@
 
-### Number of line in treatment and cycle in frontline (more cleaning needs to be done here)
+### Number of line in treatment and cycle in frontline  
 Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
@@
 ```{r}
-Frontline %>% 
+Treatment %>% 
   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
@@
   tbl_summary()
-Frontline %>% 
+Treatment %>% 
   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
@@
 ```{r}
-Frontline %>% 
+Treatment %>% 
   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
@@
 
-Frontline %>% 
+Treatment %>% 
   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
@@
 ```{r}
-Frontline %>% 
+Treatment %>% 
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
@@
 
-Frontline %>% 
+Treatment %>% 
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
@@
 ```{r}
-Frontline %>% 
+Treatment %>% 
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
@@
 
-Frontline %>% 
+Treatment %>% 
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
@@
 ```
-If we remove patients who have at least 1 missing amount administered, we lose `r Frontline %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
-
-If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
+<!-- If we remove patients who have at least 1 missing amount administered, we lose `r Frontline %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.   -->
+
+<!-- If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
+-->
 
@@
 ```{r treatment survival, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ 1, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ debulking, data=Frontline %>%
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ 1, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-
 # OS by therapy
@@
 ```{r, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ debulking, data=Frontline %>%
@@
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),

### 2021-10-20 Rmd/rdi analysis.Rmd
Update RDI and plots

@@
 Frontline <- Treatment %>% 
-  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
-  #   group_by(patientid, chemotherapy_type) %>% 
-  # mutate(linenumber_adj = dense_rank(linenumber_new)) %>%
-
   filter(chemotherapy_type == "Neoadjuvant" |
@@
 
-  mutate(relative_dose_intensity = case_when(
-    chemotherapy_type == "Adjuvant" &
-      linenumber_adj == 1                  ~ amount/expected_dose,
-    chemotherapy_type == "Neoadjuvant"     ~ amount/expected_dose
-  )) %>%
-
+  mutate(relative_dose_intensity = amount / expected_dose
+  ) %>%
   # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
@@
 
-  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
-  group_by(patientid, chemotherapy_type, drugname_type) %>%
-  mutate(mean_RDI_per_chemotype_drug = case_when(
-    chemotherapy_type == "Adjuvant" &
-      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
-    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
-  )) %>% 
+  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
+  group_by(patientid, chemotherapy_type, drugname) %>%
+  # mutate(mean_RDI_per_drug = case_when(
+  #   chemotherapy_type == "Adjuvant" &
+  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
+  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  # )) %>% 
+  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  ) %>% 
   ungroup() %>% 
@@
   mutate(RDI_grp = case_when(
-    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
-    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
+    mean_RDI_per_drug >= 0.85              ~ "correct",
+    mean_RDI_per_drug < 0.85               ~ "underdose"
   )) %>% 
   mutate(RDI_grp = factor(RDI_grp, 
-                           labels = c("correct", "underdose"))) %>% 
+                           levels = c("correct", "underdose"))) %>% 
   mutate(RDI_grp1 = case_when(
-    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
-    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
-    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
-    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
-    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
-    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
+    mean_RDI_per_drug < 0.75               ~ "highly underdose",
+    mean_RDI_per_drug >= 0.75 &
+      mean_RDI_per_drug < 0.85             ~ "underdose",
+    mean_RDI_per_drug >= 0.85 &
+      mean_RDI_per_drug < 1                ~ "correct",
+    mean_RDI_per_drug == 1                 ~ "perfect",
+    mean_RDI_per_drug > 1 &
+      mean_RDI_per_drug < 1.5              ~ "higher dose",
+    mean_RDI_per_drug > 1.5               ~ "overdose"
   )) %>% 
   mutate(RDI_grp1 = factor(RDI_grp1, 
-                          labels = c("correct", "highly underdose", "underdose", "perfect", "higher dose", "overdose")))
+                          levels = c("perfect", "correct", "higher dose", 
+                                     "overdose", 
+                                     "highly underdose", "underdose")))
 ```
@@
 # RDI_grp = case_when(
-#     mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
-#     mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
+#     mean_RDI_per_drug >= 0.85              ~ "correct",
+#     mean_RDI_per_drug < 0.85               ~ "underdose"
 #   ))
@@
 <div class = "col-md-6">
-```{r rdi plots, fig.height=10}
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+```{r rdi plots, fig.height=10, fig.height=9}
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= drugname))+
+  geom_bar()+
+  theme_minimal(base_size = 14)+
+  coord_flip()+
+  facet_wrap(. ~ therapy)
+
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
   geom_boxplot()+
@@
   facet_wrap(.~ drugname, ncol = 2)
-
 ```
@@
 <div class = "col-md-6">
-```{r, fig.height=10}
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
+```{r, fig.height=10, fig.height=9}
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= drugname, fill= RDI_grp))+
+  geom_bar(position = "fill")+
+  theme_minimal(base_size = 14)+
+  coord_flip()+
+  facet_wrap(. ~ therapy)
+
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
   # geom_boxplot()+
-  ylim(c(-.25, 3.5))+
-  geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 patient") +
-  theme_minimal() +
+  ylim(c(-.25, 2))+
+  geom_jitter(shape=16, aes(color=RDI_grp))+
+  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
+  theme_minimal(base_size = 14) +
   guides(color=FALSE)+
@@
 
-# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
 #   # filter(linenumber_new == "1") %>%
-#   ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = relative_dose_intensity<0.85))+
+#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug, color = mean_RDI_per_drug<0.85))+
 #   geom_violin()+
@@
 #   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-#   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
 #   theme_minimal(base_size = 14)+
@@
 
-# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
 #   # filter(linenumber_new == "1") %>%
-#   ggplot(aes(x= cycle_drugname, y= relative_dose_intensity))+
-#   geom_violin(aes(color=relative_dose_intensity<0.85))+
+#   ggplot(aes(x= cycle_drugname, y= mean_RDI_per_drug))+
+#   geom_violin(aes(color=mean_RDI_per_drug<0.85))+
 #   ylim(c(-.25, 2.5))+
 #   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-#   # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
 #   theme_minimal()
@@
 ```{r}
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity))+
-  geom_violin()+
-  # ylim(c(-.25, 2.5))+
-  theme_minimal(base_size = 14)+
-  facet_wrap(.~ drugname, ncol = 2, scales = "free_y")
-
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  ggplot(aes(x= drugname, fill = RDI_grp))+
-  geom_bar(position = position_dodge())+
-  theme_minimal(base_size = 14)+
-  facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
-  coord_flip()
-
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= chemotherapy_type, y= relative_dose_intensity, color = chemotherapy_type))+
-  geom_violin()+
-  ylim(c(-.25, 3.5))+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
-  theme_minimal(base_size = 14)+
-  coord_flip()+
-  facet_wrap(drugname ~ RDI_grp, ncol = 2)
-
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
+#   geom_violin()+
+#   # ylim(c(-.25, 2.5))+
+#   theme_minimal(base_size = 14)+
+#   facet_wrap(.~ drugname, ncol = 2, scales = "free_y")
+
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= drugname, fill = RDI_grp))+
+#   geom_bar(position = position_dodge())+
+#   theme_minimal(base_size = 14)+
+#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
+#   coord_flip()
+
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   # filter(linenumber_new == "1") %>%
+#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug, color = chemotherapy_type))+
+#   geom_violin()+
+#   ylim(c(-.25, 3.5))+
+#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
+#   theme_minimal(base_size = 14)+
+#   coord_flip()+
+#   facet_wrap(drugname ~ RDI_grp, ncol = 2)
+
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
   ggplot(aes(x= drugname, fill = RDI_grp))+
@@
 
+### By Population
 ```{r, fig.width=12, fig.height=20}
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
   # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= raceeth, y= relative_dose_intensity#, alpha = relative_dose_intensity<0.85
+  ggplot(aes(x= raceeth, y= mean_RDI_per_drug#, alpha = mean_RDI_per_drug<0.85
              ))+
@@
   scale_colour_discrete()+
-  # geom_jitter(shape=16, aes(color=relative_dose_intensity<0.85))+
+  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
   theme_minimal(base_size = 14)+
@@
 
-As you will saw, we have a big spread of RDI (it is more than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI or being underdose or overdose
-
-```{r echo=TRUE}
-# (RDI_grp1 = case_when(
-#     mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
-#     mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
-#     mean_RDI_per_chemotype_drug < 1                  ~ "correct",
-#     mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
-#     mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
-#     mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
-#   ))
-```
-
-```{r, fig.width=12}
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  ggplot(aes(x= RDI_grp1, fill = drugname))+
-  geom_bar(position = position_dodge())+
-  theme_minimal(base_size = 10)+
-  facet_wrap(drugname~ chemotherapy_type, ncol = 2, scales = "free")+
-  coord_flip()
-```
-
-```{r, fig.width=12}
-# Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-#   ggplot(aes(x= drugname, fill = RDI_grp1))+
-#   geom_bar(position = position_dodge())+
-#   theme_minimal(base_size = 10)+
-#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
-#   coord_flip()
-```
-
-```{r}
-Frontline %>% filter(!is.na(relative_dose_intensity)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= drugname, fill = RDI_grp1))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 10)+
-  coord_flip()+
-  facet_wrap(.~ chemotherapy_type)
-```
-<br>
-<br>
+```{r ggridges, fig.width=16, fig.height=18}
+library(ggridges)
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(y=raceeth, x=mean_RDI_per_drug,  fill=raceeth
+             )) +
+    geom_density_ridges(alpha=0.5) +
+    theme_ridges()+
+  theme(text = element_text(size = 14),#axis.text.y = element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        strip.text.x = element_text(size = 8)
+    ) +
+  geom_vline(xintercept = 1, color = "red", linetype = 2)+
+
+  facet_wrap(therapy ~ drugname, ncol = 5, scales = "free_x")
+```
 
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels()
+
+tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
+              type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
 
-tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
-  tbl_summary(
-              type = list(relative_dose_intensity ~ 'continuous'),
-              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
-  bold_labels()
-
-tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
+tbl_stack(list(tbl3, tbl1, tbl2, tbl6, tbl4, tbl5),
+          group_header = c("carboplatin/Neoadjuvant", 
+                           "carboplatin/Adjuvant Upfront Surgery", 
+                           "carboplatin/Adjuvant Upfront Chemo",
+                           "cisplatin/Neoadjuvant", 
+                           "cisplatin/Adjuvant Upfront Surgery", 
+                           "cisplatin/Adjuvant Upfront Chemo"),
+          quiet = TRUE)
 ```
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
-
 tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
-
 tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c("relative_dose_intensity", RDI_grp)) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels()
+
+tbl7 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(
-              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels()
-
-tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6), quiet = TRUE)
+tbl8 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels()
+tbl9 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(#type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels()
+
+tbl_stack(list(tbl3, tbl1, tbl2, tbl6, tbl4, tbl5, tbl9, tbl7, tbl8),
+          group_header = c("paclitaxel/Neoadjuvant", 
+                           "paclitaxel/Adjuvant Upfront Surgery", 
+                           "paclitaxel/Adjuvant Upfront Chemo",
+                           "PBB/Neoadjuvant", 
+                           "PBB/Adjuvant Upfront Surgery", 
+                           "PBB/Adjuvant Upfront Chemo",
+                           "docetaxel/Neoadjuvant", 
+                           "docetaxel/Adjuvant Upfront Surgery", 
+                           "docetaxel/Adjuvant Upfront Chemo"),
+          quiet = TRUE)
 ```
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
+              type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nUpfront Chemo \nRDI")) %>%
+              type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              type = list(relative_dose_intensity ~ 'continuous'),
-              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+              type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              type = list(relative_dose_intensity ~ 'continuous'),
-              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
+              type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
 
-tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
-```
+tbl_stack(list(tbl5, tbl3, tbl4, tbl8, tbl6, tbl7),
+          group_header = c("carboplatin/Neoadjuvant", 
+                           "carboplatin/Adjuvant Upfront Surgery", 
+                           "carboplatin/Adjuvant Upfront Chemo",
+                           "cisplatin/Neoadjuvant", 
+                           "cisplatin/Adjuvant Upfront Surgery", 
+                           "cisplatin/Adjuvant Upfront Chemo"),
+          quiet = TRUE)
+```
+<br>
 
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "paclitaxel/adjuvant \nUpfront Chemo \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "paclitaxel/neoadjuvant \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Surgery \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "PPB/adjuvant \nUpfront Chemo \nRDI")) %>%
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = raceeth,
-              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
+              type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
   tbl_summary(by = bmi_cat,
-              label = list(relative_dose_intensity ~ "PPB/neoadjuvant \nRDI")) %>%
+              type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
 
-tbl_stack(list(tbl3, tbl4, tbl5, tbl6, tbl7, tbl8), quiet = TRUE)
+tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl9 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl10 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = raceeth,
+              # type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = bmi_cat,
+              # type = list(mean_RDI_per_drug ~ 'continuous'),
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+tbl11 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl5, tbl3, tbl4, tbl8, tbl6, tbl7, tbl11, tbl9, tbl10),
+          group_header = c("paclitaxel/Neoadjuvant", 
+                           "paclitaxel/Adjuvant Upfront Surgery", 
+                           "paclitaxel/Adjuvant Upfront Chemo",
+                           "PBB/Neoadjuvant", 
+                           "PBB/Adjuvant Upfront Surgery", 
+                           "PBB/Adjuvant Upfront Chemo",
+                           "docetaxel/Neoadjuvant", 
+                           "docetaxel/Adjuvant Upfront Surgery", 
+                           "docetaxel/Adjuvant Upfront Chemo"),
+          quiet = TRUE)
 ```
 <br>
-
-<br>
-
-***
-
 <br>
@@
                    ),
-           title = "OS from diagnosis carboplatin Neo",
+           title = "OS from diagnosis carboplatin \nNeo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis cisplatin Neo",
+           title = "OS from diagnosis cisplatin \nNeo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis paclitaxel Neo",
+           title = "OS from diagnosis paclitaxel \nNeo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis PPB Neo",
+           title = "OS from diagnosis PPB \nNeo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(str_detect(drugname, "docetaxel") & 
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis docetaxel \nNeo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis carboplatin Adj \nUpfront Surgery",
+           title = "OS from diagnosis carboplatin \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis cisplatin Adj \nUpfront Surgery",
+           title = "OS from diagnosis cisplatin \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis paclitaxel Adj \nUpfront Surgery",
+           title = "OS from diagnosis paclitaxel \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis PPB Adj \nUpfront Surgery",
+           title = "OS from diagnosis PPB \nAdj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp,
+                   data=Frontline %>%
+                     filter(str_detect(drugname, "docetaxel") &
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis docetaxel \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis carboplatin Adj \nUpfront Chemo",
+           title = "OS from diagnosis carboplatin \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis cisplatin Adj \nUpfront Chemo",
+           title = "OS from diagnosis cisplatin \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from diagnosis paclitaxel Adj \nUpfront Chemo",
+           title = "OS from diagnosis paclitaxel \nAdj Upfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(drugname == "docetaxel" & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis docetaxel \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment carboplatin Neo",
+           title = "OS from first treatment carboplatin \nNeo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment cisplatin Neo",
+           title = "OS from first treatment cisplatin \nNeo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment paclitaxel Neo",
+           title = "OS from first treatment paclitaxel \nNeo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment PPB Neo",
+           title = "OS from first treatment PPB \nNeo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp,
+                   data=Frontline %>%
+                     filter(str_detect(drugname, "docetaxel") &
+                              chemotherapy_type == "Neoadjuvant") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment docetaxel \nNeo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment carboplatin Adj \nUpfront Surgery",
+           title = "OS from first treatment carboplatin \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment cisplatin Adj \nUpfront Surgery",
+           title = "OS from first treatment cisplatin \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment paclitaxel Adj \nUpfront Surgery",
+           title = "OS from first treatment paclitaxel \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment PPB Adj \nUpfront Surgery",
+           title = "OS from first treatment PPB \nAdj Upfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp,
+                   data=Frontline %>%
+                     filter(str_detect(drugname, "docetaxel") &
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment docetaxel \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment carboplatin Adj \nUpfront Chemo",
+           title = "OS from first treatment carboplatin \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment cisplatin Adj \nUpfront Chemo",
+           title = "OS from first treatment cisplatin \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    ),
-           title = "OS from first treatment pacliatxel Adj \nUpfront Chemo",
+           title = "OS from first treatment pacliatxel \nAdj Upfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+                   data=Frontline %>% 
+                     filter(drugname == "docetaxel" & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from first treatment docetaxel \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 tbl1 <- tbl1 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  select(vitalstatus, RDI_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  select(vitalstatus, RDI_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  select(vitalstatus, RDI_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl4 <- tbl4 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  select(vitalstatus, RDI_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl5 <- tbl5 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  select(vitalstatus, RDI_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl6 <- tbl6 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  select(vitalstatus, RDI_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl7 <- tbl7 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  select(vitalstatus, RDI_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl8 <- tbl8 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  select(vitalstatus, RDI_grp) %>%
   tbl_uvregression(method = survival::coxph,
@@
 tbl9 <- tbl9 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  select(vitalstatus, RDI_grp) %>%
   tbl_uvregression(method = survival::coxph,
@@
 tbl10 <- tbl10 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>% 
+  select(vitalstatus, RDI_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl11 <- tbl11 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  select(vitalstatus, RDI_grp) %>%
   tbl_uvregression(method = survival::coxph,
@@
 tbl12 <- tbl12 %>%
-  select(vitalstatus, RDI_grp, RDI_grp1) %>%
+  select(vitalstatus, RDI_grp) %>%
   tbl_uvregression(method = survival::coxph,
@@
   italicize_levels()
+
+# docetaxel
+tbl13 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
+tbl13 <- tbl13 %>%
+  select(vitalstatus, RDI_grp) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl13$month_at_os, event = tbl13$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl14 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl14 <- tbl14 %>%
+  select(vitalstatus, RDI_grp) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl14$month_at_os, event = tbl14$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl15 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl15 <- tbl15 %>%
+  select(vitalstatus, RDI_grp) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl15$month_at_os, event = tbl15$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
+tbl_stack(list(tbl13, tbl14, tbl15),
+          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
 ```
@@
 ## Multivariable
-`coxph(Surv(time = month_at_os, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` (ageatdx or agecat?)
+`coxph(Surv(time = month_at_os, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
 ```{r Table 5 HR adjusted}
@@
   italicize_levels()
+
+# docetaxel
+tbl13 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
+tbl13 <- 
+  coxph(Surv(time = tbl13$month_at_os, 
+             event = tbl13$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl13) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl14 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl14 <- 
+  coxph(Surv(time = tbl14$month_at_os, 
+             event = tbl14$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl14) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl15 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl15 <- 
+  coxph(Surv(time = tbl15$month_at_os, 
+             event = tbl15$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl15) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl13, tbl14, tbl15),
+          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
 ```
@@
 ***
-# V.Regression
-## By clinical, demo
-`glm(vitalstatus ~ bmi + bmi_cat + RDI_grp + raceeth, data = Frontline, family = binomial)`
-```{r regression}
-# Regression vital status prediction
-model <- glm(vitalstatus ~ bmi_at_dx + bmi_cat + #RDI_grp + 
-               raceeth, data = Frontline %>% 
-               distinct(patientid, .keep_all = TRUE), 
-             family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-```
-
-<!-- `glm(vitalstatus ~ histology + tstage + brca1_tumor + brca2_tumor + issurgery + chemotherapy_type, data = Frontline, family = binomial)` -->
+
+<br>
+
+<font size="10">Yay! `r  emo::ji("party_popper")`</font>
+
+***
+
+# V.More precise RDI
+
+As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI or being underdosed or overdose
+
+```{r echo=TRUE}
+# RDI_grp1 = case_when(
+#     mean_RDI_per_drug < 0.75               ~ "highly underdose",
+#     mean_RDI_per_drug >= 0.75 &
+#       mean_RDI_per_drug < 0.85             ~ "underdose",
+#     mean_RDI_per_drug >= 0.85 &
+#       mean_RDI_per_drug < 1                ~ "correct",
+#     mean_RDI_per_drug == 1                 ~ "perfect",
+#     mean_RDI_per_drug > 1 &
+#       mean_RDI_per_drug < 1.5              ~ "higher dose",
+#     mean_RDI_per_drug >= 1.5               ~ "overdose"
+#   )) 
+```
+
+```{r, fig.width=12, fig.height=12}
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+
+  geom_point(alpha = 0.7, size = 0.75)+
+  theme_minimal(base_size = 10)+
+  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
+```
+
+```{r, fig.width=12, fig.height=12}
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= RDI_grp1, fill = drugname))+
+  geom_bar(position = position_dodge())+
+  theme_minimal(base_size = 10)+
+  facet_wrap(drugname~ chemotherapy_type, ncol = 2, scales = "free")+
+  coord_flip()
+```
+
+```{r, fig.width=12}
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= drugname, fill = RDI_grp1))+
+#   geom_bar(position = position_dodge())+
+#   theme_minimal(base_size = 10)+
+#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
+#   coord_flip()
+```
+
 ```{r}
-# model <- glm(vitalstatus ~ 
-#                histology + tstage + brca1_tumor + brca2_tumor + 
-#              issurgery +
-#              chemotherapy_type, 
-#              data = Frontline %>% 
-#                distinct(patientid, .keep_all = TRUE), 
-#              family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-```
-
-<!-- `glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline, family = binomial)` -->
-<!-- !!!! Prediction of RDI all drug together!!!! -->
-```{r}
-# Regression RDI prediction
-# model <- glm(RDI_grp ~ agecat + bmi_cat + raceeth + stagecat + histology + chemotherapy_type, data = Frontline, family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-```
-
-### By drug
-`RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat`
-```{r}
-#  for carbo
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
-               filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
-               filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-# tbl5 <-
-  tbl_merge(list(tbl3, tbl4), tab_spanner = c("**carboplatin/Adjuvant**", "**carboplatin/Neoadjuvant**"))
-
-#  for Cisplatim
-# model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
-#                filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant"), family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-# model <- glm(RDI_grp ~ agecat + bmi_cat, data = Frontline %>%
-#                filter(drugname == "cisplatin" & chemotherapy_type == "Neoadjuvant"), family = binomial)
-# tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-# tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-# tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-# 
-# # tbl5 <-
-#   tbl_merge(list(tbl3, tbl4), tab_spanner = c("**cisplatin/Adjuvant**", "**cisplatin/Neoadjuvant**"))
-
-#  for taxel
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
-               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Adjuvant")), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl3 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-model <- glm(RDI_grp ~ agecat + raceeth + stagecat + histology + bmi_cat, data = Frontline %>%
-               filter(str_detect(drugname,"taxel") & (chemotherapy_type == "Neoadjuvant")), family = binomial)
-tbl1 <- tbl_regression(model) %>% bold_p(t = .05)
-tbl2 <- tbl_regression(model) %>% bold_p(t = .05) %>% bold_p(t = .05)
-tbl4 <- tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Estimate**", "**Exp**"))
-
-# tbl6 <-
-  tbl_merge(list(tbl4, tbl3), tab_spanner = c("**taxel/Adjuvant**", "**taxel/Neoadjuvant**"))
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= drugname, fill = RDI_grp1))+
+  geom_bar(position = "fill")+
+  theme_minimal(base_size = 10)+
+  coord_flip()+
+  facet_wrap(.~ chemotherapy_type)
 ```
@@
 
+## Hazard Ratio RDI 2
+
+<span style="color:green">**Table HR**</span>
+
+### Univariable
+```{r HR RDI 2}
+# Carbo
+tbl1 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+tbl1 <- tbl1 %>%
+  select(vitalstatus, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl2 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl2 <- tbl2 %>%
+  select(vitalstatus, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl3 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl3 <- tbl3 %>%
+  select(vitalstatus, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Cisplatin
+tbl4 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
+tbl4 <- tbl4 %>%
+  select(vitalstatus, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl5 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl5 <- tbl5 %>%
+  select(vitalstatus, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
+tbl6 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl6 <- tbl6 %>%
+  select(vitalstatus, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl4, tbl5, tbl6),
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+tbl7 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+tbl7 <- tbl7 %>%
+  select(vitalstatus, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl8 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl8 <- tbl8 %>%
+  select(vitalstatus, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+tbl9 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl9 <- tbl9 %>%
+  select(vitalstatus, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
+tbl_stack(list(tbl7, tbl8, tbl9),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# PPB
+tbl10 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
+tbl10 <- tbl10 %>%
+  select(vitalstatus, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl11 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl11 <- tbl11 %>%
+  select(vitalstatus, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl12 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl12 <- tbl12 %>%
+  select(vitalstatus, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl10, tbl11, tbl12),
+          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# docetaxel
+tbl13 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
+tbl13 <- tbl13 %>%
+  select(vitalstatus, RDI_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl13$month_at_os, event = tbl13$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl14 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl14 <- tbl14 %>%
+  select(vitalstatus, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl14$month_at_os, event = tbl14$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl15 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl15 <- tbl15 %>%
+  select(vitalstatus, RDI_grp1) %>%
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl15$month_at_os, event = tbl15$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
+tbl_stack(list(tbl13, tbl14, tbl15),
+          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+### Multivariable
+`coxph(Surv(time = month_at_os, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
+```{r}
+# Carbo
+tbl1 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+tbl1 <- 
+  coxph(Surv(time = tbl1$month_at_os, 
+             event = tbl1$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl1) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
+tbl2 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os, 
+             event = tbl2$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl3 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os, 
+             event = tbl3$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Cisplatin
+tbl4 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
+tbl4 <- 
+  coxph(Surv(time = tbl4$month_at_os, 
+             event = tbl4$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx, data =  tbl4) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl5 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl5 <- 
+  coxph(Surv(time = tbl5$month_at_os, 
+             event = tbl5$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx, data =  tbl5) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+
+tbl6 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl6 <- 
+  coxph(Surv(time = tbl6$month_at_os, 
+             event = tbl6$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx, data =  tbl6) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl4, tbl5, tbl6),
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+tbl7 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+tbl7 <- 
+  coxph(Surv(time = tbl7$month_at_os, 
+             event = tbl7$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl7) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl8 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl8 <- 
+  coxph(Surv(time = tbl8$month_at_os, 
+             event = tbl8$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl8) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl9 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl9 <- 
+  coxph(Surv(time = tbl9$month_at_os, 
+             event = tbl9$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl9) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl7, tbl8, tbl9),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# PPB
+tbl10 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
+tbl10 <- 
+  coxph(Surv(time = tbl10$month_at_os, 
+             event = tbl10$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl10) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl11 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl11 <- 
+  coxph(Surv(time = tbl11$month_at_os, 
+             event = tbl11$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl11) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl12 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl12 <- 
+  coxph(Surv(time = tbl12$month_at_os, 
+             event = tbl12$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl12) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl10, tbl11, tbl12),
+          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# docetaxel
+tbl13 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
+tbl13 <- 
+  coxph(Surv(time = tbl13$month_at_os, 
+             event = tbl13$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl13) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl14 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl14 <- 
+  coxph(Surv(time = tbl14$month_at_os, 
+             event = tbl14$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl14) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl15 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl15 <- 
+  coxph(Surv(time = tbl15$month_at_os, 
+             event = tbl15$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl15) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+tbl_stack(list(tbl13, tbl14, tbl15),
+          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
 ***
-
-<br>
-
-<font size="10">Yay! `r  emo::ji("party_popper")`</font>
-
-***

### 2021-10-21 Rmd/rdi analysis.Rmd
Update report

@@
 
+  # Calculate ideal dody weight
+  mutate(ideal_weight = case_when(
+    height <= 1.524               ~ 45.5 + 2.3,
+    height > 1.524                ~ 45.5 + (2.3 * (((height - 1.524) / 0.0254)))
+  )) %>% 
+  mutate(adjusted_weight = ((weight - ideal_weight) * 0.40) + ideal_weight
+  ) %>% 
   # Calculate bmi
@@
   mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
+
+  mutate(actual_bmi = weight / (height * height)) %>%
+  mutate(actual_bmi_cat = case_when(
+    actual_bmi < 25                    ~ "Underweight and normal weight",
+    actual_bmi >= 25 &
+      actual_bmi < 30                  ~ "Overweight",
+    actual_bmi >= 30                   ~ "Obese"
+  )) %>%
+  mutate(actual_bmi_cat = factor(actual_bmi_cat, 
+                                  levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
+  # select(patientid, weight, height, bmi_at_dx, ideal_weight, adjusted_weight, adjusted_bmi)
   # Calculate CrCl
@@
     TRUE                              ~ CrCl
+  )) %>% 
+  mutate(adjusted_CrCl = case_when(
+    actual_bmi >= 25                  ~ CrCl,
+    actual_bmi < 25                   ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
+  )) %>% 
+  mutate(adjusted_CrCl = case_when(
+    adjusted_CrCl > 125               ~ 125,
+    TRUE                              ~ adjusted_CrCl
   )) %>%
@@
   )) %>% 
+  mutate(adjusted_expected_dose = case_when(
+    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
+    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
+    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
+  )) %>% 
+  mutate(adjusted_expected_dose = case_when(
+    adjusted_expected_dose > 900 &
+      target_auc == 6              ~ 900,
+    adjusted_expected_dose > 750 &
+      target_auc == 5              ~ 750,
+    TRUE                           ~ adjusted_expected_dose
+  )) %>% 
   group_by(patientid) %>%
@@
 
-  mutate(relative_dose_intensity = amount / expected_dose
+  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
   ) %>%
@@
     mean_RDI_per_drug >= 0.85 &
-      mean_RDI_per_drug < 1                ~ "correct",
-    mean_RDI_per_drug == 1                 ~ "perfect",
-    mean_RDI_per_drug > 1 &
-      mean_RDI_per_drug < 1.5              ~ "higher dose",
-    mean_RDI_per_drug > 1.5               ~ "overdose"
+      mean_RDI_per_drug <= 1                ~ "correct",
+    # mean_RDI_per_drug == 1                 ~ "perfect",
+    # mean_RDI_per_drug > 1 &
+    #   mean_RDI_per_drug < 1.5              ~ "higher dose",
+    mean_RDI_per_drug > 1               ~ "overdose"
   )) %>% 
   mutate(RDI_grp1 = factor(RDI_grp1, 
-                          levels = c("perfect", "correct", "higher dose", 
+                          levels = c("correct", #"perfect", #"higher dose", 
                                      "overdose", 
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl1$month_at_os, event = tbl1$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl2 <- Frontline %>%
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os, event = tbl2$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl3 <- Frontline %>%
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os, event = tbl3$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl1, tbl2, tbl3),
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl4$month_at_os, event = tbl4$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl4$month_at_os_from_treatment, event = tbl4$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl5 <- Frontline %>%
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl5$month_at_os, event = tbl5$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl5$month_at_os_from_treatment, event = tbl5$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl6$month_at_os, event = tbl6$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl6$month_at_os_from_treatment, event = tbl6$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl4, tbl5, tbl6),
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl7$month_at_os, event = tbl7$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl8 <- Frontline %>%
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl8$month_at_os, event = tbl8$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+                 y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl9$month_at_os, event = tbl9$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
+                 y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl10$month_at_os_from_treatment, event = tbl10$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl11 <- Frontline %>%
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl11$month_at_os_from_treatment, event = tbl11$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl12 <- Frontline %>%
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl12$month_at_os_from_treatment, event = tbl12$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl10, tbl11, tbl12),
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl13$month_at_os, event = tbl13$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl13$month_at_os_from_treatment, event = tbl13$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl14 <- Frontline %>%
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl14$month_at_os, event = tbl14$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl14$month_at_os_from_treatment, event = tbl14$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl15 <- Frontline %>%
@@
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl15$month_at_os, event = tbl15$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+                 y = (Surv(time = tbl15$month_at_os_from_treatment, event = tbl15$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
@@
 ## Multivariable
-`coxph(Surv(time = month_at_os, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
 ```{r Table 5 HR adjusted}
@@
 tbl1 <- 
-  coxph(Surv(time = tbl1$month_at_os, 
+  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
              event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl1) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
@@
 tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os, 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
              event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl3 <- Frontline %>%
@@
 tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os, 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
              event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl1, tbl2, tbl3),
@@
 tbl4 <- 
-  coxph(Surv(time = tbl4$month_at_os, 
+  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
              event = tbl4$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl4) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl5 <- Frontline %>%
@@
 tbl5 <- 
-  coxph(Surv(time = tbl5$month_at_os, 
+  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
              event = tbl5$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl5) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
@@
 tbl6 <- 
-  coxph(Surv(time = tbl6$month_at_os, 
+  coxph(Surv(time = tbl6$month_at_os_from_treatment, 
              event = tbl6$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl6) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl4, tbl5, tbl6),
@@
 tbl7 <- 
-  coxph(Surv(time = tbl7$month_at_os, 
+  coxph(Surv(time = tbl7$month_at_os_from_treatment, 
              event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl7) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl8 <- Frontline %>%
@@
 tbl8 <- 
-  coxph(Surv(time = tbl8$month_at_os, 
+  coxph(Surv(time = tbl8$month_at_os_from_treatment, 
              event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl8) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl9 <- Frontline %>%
@@
 tbl9 <- 
-  coxph(Surv(time = tbl9$month_at_os, 
+  coxph(Surv(time = tbl9$month_at_os_from_treatment, 
              event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl9) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl7, tbl8, tbl9),
@@
 tbl10 <- 
-  coxph(Surv(time = tbl10$month_at_os, 
+  coxph(Surv(time = tbl10$month_at_os_from_treatment, 
              event = tbl10$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl10) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl11 <- Frontline %>%
@@
 tbl11 <- 
-  coxph(Surv(time = tbl11$month_at_os, 
+  coxph(Surv(time = tbl11$month_at_os_from_treatment, 
              event = tbl11$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl11) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl12 <- Frontline %>%
@@
 tbl12 <- 
-  coxph(Surv(time = tbl12$month_at_os, 
+  coxph(Surv(time = tbl12$month_at_os_from_treatment, 
              event = tbl12$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl12) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl10, tbl11, tbl12),
@@
 tbl13 <- 
-  coxph(Surv(time = tbl13$month_at_os, 
+  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
              event = tbl13$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl13) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl14 <- Frontline %>%
@@
 tbl14 <- 
-  coxph(Surv(time = tbl14$month_at_os, 
+  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
              event = tbl14$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl14) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl15 <- Frontline %>%
@@
 tbl15 <- 
-  coxph(Surv(time = tbl15$month_at_os, 
+  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
              event = tbl15$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl15) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl13, tbl14, tbl15),
@@
 <br>
-
-***
-
-<br>
-
-<font size="10">Yay! `r  emo::ji("party_popper")`</font>
 
@@
 #     mean_RDI_per_drug == 1                 ~ "perfect",
-#     mean_RDI_per_drug > 1 &
-#       mean_RDI_per_drug < 1.5              ~ "higher dose",
-#     mean_RDI_per_drug >= 1.5               ~ "overdose"
+#     mean_RDI_per_drug > 1                  ~ "overdose"
 #   ))
@@
   facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
-```
-
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+
+  geom_jitter()+
+  theme_minimal(base_size = 10)+
+  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
+
+```
+Here I just wanted to see if we have more or less underdosing / overdosing with BMI
 ```{r, fig.width=12, fig.height=12}
@@
 ```
+As you can see above in green, we have a lot of patient who are overdose.
 <br>
@@
 ```
+Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference.
 
 ### Multivariable
-`coxph(Surv(time = month_at_os, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
 ```{r}
@@
 tbl1 <- 
-  coxph(Surv(time = tbl1$month_at_os, 
+  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
              event = tbl1$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl1) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
@@
 tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os, 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
              event = tbl2$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl3 <- Frontline %>%
@@
 tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os, 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
              event = tbl3$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl1, tbl2, tbl3),
@@
 tbl4 <- 
-  coxph(Surv(time = tbl4$month_at_os, 
+  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
              event = tbl4$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx, data =  tbl4) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl5 <- Frontline %>%
@@
 tbl5 <- 
-  coxph(Surv(time = tbl5$month_at_os, 
+  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
              event = tbl5$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx, data =  tbl5) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
@@
 tbl6 <- 
-  coxph(Surv(time = tbl6$month_at_os, 
+  coxph(Surv(time = tbl6$month_at_os_from_treatment, 
              event = tbl6$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx, data =  tbl6) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl4, tbl5, tbl6),
@@
 tbl7 <- 
-  coxph(Surv(time = tbl7$month_at_os, 
+  coxph(Surv(time = tbl7$month_at_os_from_treatment, 
              event = tbl7$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl7) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl8 <- Frontline %>%
@@
 tbl8 <- 
-  coxph(Surv(time = tbl8$month_at_os, 
+  coxph(Surv(time = tbl8$month_at_os_from_treatment, 
              event = tbl8$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl8) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl9 <- Frontline %>%
@@
 tbl9 <- 
-  coxph(Surv(time = tbl9$month_at_os, 
+  coxph(Surv(time = tbl9$month_at_os_from_treatment, 
              event = tbl9$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl9) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl7, tbl8, tbl9),
@@
 tbl10 <- 
-  coxph(Surv(time = tbl10$month_at_os, 
+  coxph(Surv(time = tbl10$month_at_os_from_treatment, 
              event = tbl10$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl10) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl11 <- Frontline %>%
@@
 tbl11 <- 
-  coxph(Surv(time = tbl11$month_at_os, 
+  coxph(Surv(time = tbl11$month_at_os_from_treatment, 
              event = tbl11$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl11) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl12 <- Frontline %>%
@@
 tbl12 <- 
-  coxph(Surv(time = tbl12$month_at_os, 
+  coxph(Surv(time = tbl12$month_at_os_from_treatment, 
              event = tbl12$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl12) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl10, tbl11, tbl12),
@@
 tbl13 <- 
-  coxph(Surv(time = tbl13$month_at_os, 
+  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
              event = tbl13$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl13) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl14 <- Frontline %>%
@@
 tbl14 <- 
-  coxph(Surv(time = tbl14$month_at_os, 
+  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
              event = tbl14$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl14) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl15 <- Frontline %>%
@@
 tbl15 <- 
-  coxph(Surv(time = tbl15$month_at_os, 
+  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
              event = tbl15$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl15) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl_stack(list(tbl13, tbl14, tbl15),
@@
 ```
+
 <br>
@@
 ***
+
+# VI. Adjusted by BMI
+
+```{r}
+Frontline_bmi <- Frontline %>%
+  filter(!is.na(bmi_cat))
+```
+
+## Multivariable
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` 
+```{r bmi HR adjusted}
+# Carbo
+tbl1 <- Frontline_bmi %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+tbl1 <- 
+  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
+             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+
+tbl2 <- Frontline_bmi %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl3 <- Frontline_bmi %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Cisplatin
+tbl4 <- Frontline_bmi %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
+tbl4 <- 
+  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
+             event = tbl4$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl4) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl5 <- Frontline_bmi %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl5 <- 
+  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
+             event = tbl5$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl5) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+
+tbl6 <- Frontline_bmi %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl6 <- 
+  coxph(Surv(time = tbl6$month_at_os_from_treatment, 
+             event = tbl6$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl6) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl4, tbl5, tbl6),
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+tbl7 <- Frontline_bmi %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+tbl7 <- 
+  coxph(Surv(time = tbl7$month_at_os_from_treatment, 
+             event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl8 <- Frontline_bmi %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl8 <- 
+  coxph(Surv(time = tbl8$month_at_os_from_treatment, 
+             event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl9 <- Frontline_bmi %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl9 <- 
+  coxph(Surv(time = tbl9$month_at_os_from_treatment, 
+             event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl7, tbl8, tbl9),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# PPB
+tbl10 <- Frontline_bmi %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
+tbl10 <- 
+  coxph(Surv(time = tbl10$month_at_os_from_treatment, 
+             event = tbl10$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl10) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl11 <- Frontline_bmi %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl11 <- 
+  coxph(Surv(time = tbl11$month_at_os_from_treatment, 
+             event = tbl11$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl11) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl12 <- Frontline_bmi %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl12 <- 
+  coxph(Surv(time = tbl12$month_at_os_from_treatment, 
+             event = tbl12$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl12) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl10, tbl11, tbl12),
+          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# docetaxel
+tbl13 <- Frontline_bmi %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
+tbl13 <- 
+  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
+             event = tbl13$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl13) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl14 <- Frontline_bmi %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl14 <- 
+  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
+             event = tbl14$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl14) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl15 <- Frontline_bmi %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl15 <- 
+  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
+             event = tbl15$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl15) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl13, tbl14, tbl15),
+          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
+***

### 2021-10-21 Rmd/rdi analysis adjusted weight.Rmd
report with adjusted weight

--- 2021-10-21 Rmd/rdi analysis.Rmd
@@
 
-# `r emo::ji("spiral_notepad")` This report is using **actual weight**
+# `r emo::ji("spiral_notepad")` This report is using **adjusted weight**
+
+```{r echo=TRUE}
+# # Calculate ideal dody weight
+#   mutate(ideal_weight = case_when(
+#     height <= 1.524               ~ 45.5 + 2.3,
+#     height > 1.524                ~ 45.5 + (2.3 * (((height - 1.524) / 0.0254)))
+#   )) %>% 
+#   mutate(adjusted_weight = ((weight - ideal_weight) * 0.40) + ideal_weight
+#   ) %>% 
+#   mutate(actual_bmi = weight / (height * height)) %>%
+#   mutate(actual_bmi_cat = case_when(
+#     actual_bmi < 25                    ~ "Underweight and normal weight",
+#     actual_bmi >= 25 &
+#       actual_bmi < 30                  ~ "Overweight",
+#     actual_bmi >= 30                   ~ "Obese"
+#   )) %>%
+#   mutate(actual_bmi_cat = factor(actual_bmi_cat, 
+#                                   levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
+#   # select(patientid, weight, height, bmi_at_dx, ideal_weight, adjusted_weight, adjusted_bmi)
+#   # Calculate CrCl
+#   inner_join(., clinical_data %>% select(-surgerydate),
+#              by = "patientid") %>% 
+#   mutate(CrCl = (
+#        (
+#     ((140 - ageatdx) * weight) /
+#     (72 * creatinine)
+#        ) *
+#     0.85)
+#   ) %>% 
+#   mutate(CrCl = case_when(
+#     CrCl > 125                        ~ 125,
+#     TRUE                              ~ CrCl
+#   )) %>% 
+#   mutate(adjusted_CrCl = case_when(
+#     actual_bmi >= 25                  ~ CrCl,
+#     actual_bmi < 25                   ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
+#   )) %>% 
+#   mutate(adjusted_CrCl = case_when(
+#     adjusted_CrCl > 125               ~ 125,
+#     TRUE                              ~ adjusted_CrCl
+#   )) 
+```
 
@@
 
-$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
+$$CrCl = \frac{(140 - ageatdx) * adjusted_weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
 and is capped at 125.  
@@
 
-  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
+  mutate(relative_dose_intensity = amount / adjusted_expected_dose
   ) %>%
@@
 
-           bmi_at_dx, bmi_cat, 
+           actual_bmi, actual_bmi_cat, 
            weight_at_dx, height_at_dx, bsa_at_dx,
@@
 
-           "bmi_at_dx", bmi_cat, "BSA",
+           actual_bmi, actual_bmi_cat, "BSA",
            "stagecat",
@@
   distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= bmi_cat))+
+  ggplot(aes(x= actual_bmi_cat))+
   geom_bar()+
@@
   distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = bmi_cat))+
+  ggplot(aes(x= raceeth, fill = actual_bmi_cat))+
   geom_bar(position = "fill")+
@@
 
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+# OS by actual_bmi_cat
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ actual_bmi_cat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+# OS by actual_bmi_cat
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ actual_bmi_cat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
+  select(c(actual_bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = actual_bmi_cat,
               label = list(mean_RDI_per_drug ~ "RDI")) %>%
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
+  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = actual_bmi_cat,
               label = list(mean_RDI_per_drug ~ "RDI")) %>%
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
+  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = actual_bmi_cat,
               type = list(mean_RDI_per_drug ~ 'continuous'),
@@
   distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
+  select(c(actual_bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(by = actual_bmi_cat,
               # type = list(mean_RDI_per_drug ~ 'continuous'),
@@
 Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+
+  ggplot(aes(x= actual_bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+
   geom_jitter()+
@@
 Frontline_bmi <- Frontline %>%
-  filter(!is.na(bmi_cat))
+  filter(!is.na(actual_bmi_cat))
 ```
@@
 ## Multivariable
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat` 
 ```{r bmi HR adjusted}
@@
   coxph(Surv(time = tbl1$month_at_os_from_treatment, 
-             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>%
+             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl1) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl7$month_at_os_from_treatment, 
-             event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>%
+             event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl7) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl8$month_at_os_from_treatment, 
-             event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>%
+             event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl8) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl9$month_at_os_from_treatment, 
-             event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>%
+             event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl9) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl10$month_at_os_from_treatment, 
-             event = tbl10$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl10) %>%
+             event = tbl10$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl10) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl11$month_at_os_from_treatment, 
-             event = tbl11$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl11) %>%
+             event = tbl11$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl11) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl12$month_at_os_from_treatment, 
-             event = tbl12$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl12) %>%
+             event = tbl12$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl12) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl13$month_at_os_from_treatment, 
-             event = tbl13$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl13) %>%
+             event = tbl13$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl13) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl14$month_at_os_from_treatment, 
-             event = tbl14$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl14) %>%
+             event = tbl14$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl14) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
@@
   coxph(Surv(time = tbl15$month_at_os_from_treatment, 
-             event = tbl15$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl15) %>%
+             event = tbl15$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + actual_bmi_cat, data =  tbl15) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

### 2021-10-21 Rmd/rdi analysis adjusted weight.Rmd
Add continous analysis

@@
 tbl1 <- tbl1 %>%
-  select(vitalstatus, RDI_grp) %>% 
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_grp) %>% 
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_grp) %>% 
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl4 <- tbl4 %>%
-  select(vitalstatus, RDI_grp) %>% 
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl5 <- tbl5 %>%
-  select(vitalstatus, RDI_grp) %>% 
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl6 <- tbl6 %>%
-  select(vitalstatus, RDI_grp) %>% 
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl7 <- tbl7 %>%
-  select(vitalstatus, RDI_grp) %>% 
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl8 <- tbl8 %>%
-  select(vitalstatus, RDI_grp) %>%
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
   tbl_uvregression(method = survival::coxph,
@@
 tbl9 <- tbl9 %>%
-  select(vitalstatus, RDI_grp) %>%
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
   tbl_uvregression(method = survival::coxph,
@@
 tbl10 <- tbl10 %>%
-  select(vitalstatus, RDI_grp) %>% 
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl11 <- tbl11 %>%
-  select(vitalstatus, RDI_grp) %>%
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
   tbl_uvregression(method = survival::coxph,
@@
 tbl12 <- tbl12 %>%
-  select(vitalstatus, RDI_grp) %>%
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
   tbl_uvregression(method = survival::coxph,
@@
 tbl13 <- tbl13 %>%
-  select(vitalstatus, RDI_grp) %>% 
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl14 <- tbl14 %>%
-  select(vitalstatus, RDI_grp) %>%
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
   tbl_uvregression(method = survival::coxph,
@@
 tbl15 <- tbl15 %>%
-  select(vitalstatus, RDI_grp) %>%
+  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
   tbl_uvregression(method = survival::coxph,
@@
 ## Multivariable
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
+### RDI group
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp + raceeth + ageatdx + stagecat` 
 ```{r Table 5 HR adjusted}
@@
 
+### Continous
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat` 
+```{r rdi continous}
+# Carbo
+tbl1 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+tbl1 <- 
+  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
+             event = tbl1$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl1) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+
+tbl2 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl3 <- Frontline %>%
+  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Cisplatin
+tbl4 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
+tbl4 <- 
+  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
+             event = tbl4$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx, data =  tbl4) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl5 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl5 <- 
+  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
+             event = tbl5$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx, data =  tbl5) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+
+tbl6 <- Frontline %>%
+  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl6 <- 
+  coxph(Surv(time = tbl6$month_at_os_from_treatment, 
+             event = tbl6$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx, data =  tbl6) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl4, tbl5, tbl6),
+          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+tbl7 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+tbl7 <- 
+  coxph(Surv(time = tbl7$month_at_os_from_treatment, 
+             event = tbl7$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl7) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl8 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl8 <- 
+  coxph(Surv(time = tbl8$month_at_os_from_treatment, 
+             event = tbl8$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl8) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl9 <- Frontline %>%
+  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl9 <- 
+  coxph(Surv(time = tbl9$month_at_os_from_treatment, 
+             event = tbl9$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl9) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl7, tbl8, tbl9),
+          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# PPB
+tbl10 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
+tbl10 <- 
+  coxph(Surv(time = tbl10$month_at_os_from_treatment, 
+             event = tbl10$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl10) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl11 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl11 <- 
+  coxph(Surv(time = tbl11$month_at_os_from_treatment, 
+             event = tbl11$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl11) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl12 <- Frontline %>%
+  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl12 <- 
+  coxph(Surv(time = tbl12$month_at_os_from_treatment, 
+             event = tbl12$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl12) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl10, tbl11, tbl12),
+          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# docetaxel
+tbl13 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
+tbl13 <- 
+  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
+             event = tbl13$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl13) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl14 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+tbl14 <- 
+  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
+             event = tbl14$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl14) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl15 <- Frontline %>%
+  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+tbl15 <- 
+  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
+             event = tbl15$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl15) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+tbl_stack(list(tbl13, tbl14, tbl15),
+          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
 ***
+
+<br>
 
@@
 
-# VI. Adjusted by BMI
+# VI. Adjusted by **actual_bmi_cat**
 

### 2021-10-21 Rmd/rdi analysis.Rmd
Add continous analysis

@@
 ```
+<br>
+<br>
 
 ## Multivariable
+### RDI group
 `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
-```{r Table 5 HR adjusted}
+```{r Table 5 HR adjusted rdi group}
 # Carbo
@@
 ### Multivariable
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp + raceeth + ageatdx + stagecat` 
 ```{r}
@@
 ```
-
 <br>
@@
 
-# VI. Adjusted by BMI
+# VI. Adjusted by **BMI at DX category**
 

### 2021-10-27 Rmd/rdi analysis adjusted weight.Rmd
Adding cleanup for cycle number and more

@@
 ```{r}
-therapy_line %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(had_neo, had_adj, therapy) %>% 
-  tbl_summary(by = therapy,
-              type = list(had_neo ~ "dichotomous", 
-                          had_adj ~ "dichotomous"),
-              missing = "no")
-therapy_line %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(therapy, treatment_sequence) %>% 
-  tbl_summary(by = therapy)
+# therapy_line %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(had_neo, had_adj, therapy) %>% 
+#   tbl_summary(by = therapy,
+#               type = list(had_neo ~ "dichotomous", 
+#                           had_adj ~ "dichotomous"),
+#               missing = "no")
+# therapy_line %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(therapy, treatment_sequence) %>% 
+#   tbl_summary(by = therapy)
 ```
@@
 ```{r}
-therapy_line %>% 
-  filter(linenumber == 1
-         ) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename) %>% 
-  tbl_summary(sort = list(everything() ~ "frequency"))
-
-therapy_line %>% 
-  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename) %>% 
-  tbl_summary(sort = list(everything() ~ "frequency"))
+# therapy_line %>% 
+#   filter(linenumber == 1
+#          ) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(linename) %>% 
+#   tbl_summary(sort = list(everything() ~ "frequency"))
+# 
+# therapy_line %>% 
+#   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(linename) %>% 
+#   tbl_summary(sort = list(everything() ~ "frequency"))
 
@@
 ```{r Number of patient who switch line}
-therapy_line %>% 
-  mutate(change_line = case_when(
-    linenumber == 1 & 
-      linenumber_new == 2 &
-      chemotherapy_type == "Adjuvant" &
-      therapy == "Upfront Chemo"                   ~ 1,
-    TRUE                                           ~ 0
-  )) %>% 
-  arrange(desc(change_line)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(change_line) %>% 
-  tbl_summary()
+# therapy_line %>% 
+#   mutate(change_line = case_when(
+#     linenumber == 1 & 
+#       linenumber_new == 2 &
+#       chemotherapy_type == "Adjuvant" &
+#       therapy == "Upfront Chemo"                   ~ 1,
+#     TRUE                                           ~ 0
+#   )) %>% 
+#   arrange(desc(change_line)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(change_line) %>% 
+#   tbl_summary()
 ```
@@
 ```{r}
-therapy_line %>% 
-  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
-           duration(n = 1, units = "days")) %>% 
-  filter(linenumber == 1 & linenumber_new == 2) %>% 
-  select(patientid, linenumber, linenumber_new, linenumber_adj, 
-         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= line_duration))+
-  geom_histogram(color = "slateblue", fill = "grey", binwidth = 7) +
-  theme_minimal(base_size = 14)+
-  labs(x="Line duration", 
-       y="Number of Patient",
-       caption = "Each bar represents 7 days, bottom plot is zoomed in")+
-  ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
+# therapy_line %>% 
+#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
+#            duration(n = 1, units = "days")) %>% 
+#   filter(linenumber == 1 & linenumber_new == 2) %>% 
+#   select(patientid, linenumber, linenumber_new, linenumber_adj, 
+#          drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   ggplot(aes(x= line_duration))+
+#   geom_histogram(color = "slateblue", fill = "grey", binwidth = 7) +
+#   theme_minimal(base_size = 14)+
+#   labs(x="Line duration", 
+#        y="Number of Patient",
+#        caption = "Each bar represents 7 days, bottom plot is zoomed in")+
+#   ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
 
@@
 ```{r}
-therapy_line %>% 
-  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
-           duration(n = 1, units = "days")) %>% 
-  filter(linenumber == 1 & linenumber_new == 2) %>% 
-  select(patientid, drugname, episodedate, line_duration, 
-         chemotherapy_type, therapy, 
-         linenumber, linenumber_new, linenumber_adj) %>% 
-  filter(line_duration < 30)
+# therapy_line %>% 
+#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
+#            duration(n = 1, units = "days")) %>% 
+#   filter(linenumber == 1 & linenumber_new == 2) %>% 
+#   select(patientid, drugname, episodedate, line_duration, 
+#          chemotherapy_type, therapy, 
+#          linenumber, linenumber_new, linenumber_adj) %>% 
+#   filter(line_duration < 30)
 ```
@@
 ```{r plot interval}
-Treatment %>% 
-  ggplot(aes(x= interval_creat)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
 # Treatment %>% 
-#   ggplot(aes(x= interval_height)) +
-#   geom_bar() +
-#   coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_weight)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_bsa)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_auc)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
+#   ggplot(aes(x= interval_creat)) +
+#   geom_bar() #+
+#   # coord_cartesian(ylim=c(0,50))
+# # Treatment %>% 
+# #   ggplot(aes(x= interval_height)) +
+# #   geom_bar() +
+# #   coord_cartesian(ylim=c(0,50))
+# Treatment %>% 
+#   ggplot(aes(x= interval_weight)) +
+#   geom_bar() #+
+#   # coord_cartesian(ylim=c(0,50))
+# Treatment %>% 
+#   ggplot(aes(x= interval_bsa)) +
+#   geom_bar() #+
+#   # coord_cartesian(ylim=c(0,50))
+# Treatment %>% 
+#   ggplot(aes(x= interval_auc)) +
+#   geom_bar() #+
+#   # coord_cartesian(ylim=c(0,50))
 ```
@@
 ```{r}
-Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  arrange(desc(linenumber_new)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new) %>% 
-  tbl_summary()
-Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  filter(linenumber_new == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment) %>% 
-  tbl_summary()
-Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  filter(linenumber_new == 1) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
-```
-Don't forget we have that "neo + surg"
+# Treatment %>% 
+#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+#   arrange(desc(linenumber_new)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(linenumber_new) %>% 
+#   tbl_summary()
+# Treatment %>% 
+#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+#   filter(linenumber_new == 1) %>% 
+#   mutate(cycle_increment = factor(cycle_increment)) %>% 
+#   arrange(desc(cycle_increment)) %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(cycle_increment) %>% 
+#   tbl_summary()
+# Treatment %>% 
+#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+#   filter(linenumber_new == 1) %>% 
+#   arrange(desc(cycle_increment)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(cycle_increment) %>% 
+#   tbl_summary()
+```
+<!-- Don't forget we have that "neo + surg" -->
 ```{r}
-Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
-  filter(linenumber_new == 1) %>% 
-  arrange(desc(linenumber_new)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new) %>% 
-  tbl_summary()
-
-Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
-  filter(linenumber_new == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
-```
-Number of Adjuvant line in patients with upfront neo
+# Treatment %>% 
+#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
+#   filter(linenumber_new == 1) %>% 
+#   arrange(desc(linenumber_new)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(linenumber_new) %>% 
+#   tbl_summary()
+# 
+# Treatment %>% 
+#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
+#   filter(linenumber_new == 1) %>% 
+#   mutate(cycle_increment = factor(cycle_increment)) %>% 
+#   arrange(desc(cycle_increment)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(cycle_increment) %>% 
+#   tbl_summary()
+```
+<!-- Number of Adjuvant line in patients with upfront neo -->
 ```{r}
-Treatment %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  arrange(desc(linenumber_adj)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(linenumber_adj) %>% 
-  tbl_summary()
-
-Treatment %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  filter(linenumber_adj == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
-```
-Number of Adjuvant line in patients with upfront surgery
+# Treatment %>% 
+#   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+#   arrange(desc(linenumber_adj)) %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(linenumber_adj) %>% 
+#   tbl_summary()
+# 
+# Treatment %>% 
+#   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+#   filter(linenumber_adj == 1) %>% 
+#   mutate(cycle_increment = factor(cycle_increment)) %>% 
+#   arrange(desc(cycle_increment)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(cycle_increment) %>% 
+#   tbl_summary()
+```
+<!-- Number of Adjuvant line in patients with upfront surgery -->
 ```{r}
-Treatment %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
-  arrange(desc(linenumber_adj)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(linenumber_adj) %>% 
-  tbl_summary()
-
-Treatment %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
-  filter(linenumber_adj == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
+# Treatment %>% 
+#   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
+#   arrange(desc(linenumber_adj)) %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(linenumber_adj) %>% 
+#   tbl_summary()
+# 
+# Treatment %>% 
+#   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
+#   filter(linenumber_adj == 1) %>% 
+#   mutate(cycle_increment = factor(cycle_increment)) %>% 
+#   arrange(desc(cycle_increment)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(cycle_increment) %>% 
+#   tbl_summary()
 ```
@@
 
-## Missingness
-Here some representation of missingness in our data:  
-- In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
+<!-- ## Missingness -->
+<!-- Here some representation of missingness in our data:   -->
+<!-- - In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
 Because these parameters overlap only 25 patients will have missing value for all of them.
-- In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation).
+-->
+<!-- - In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation).
 the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
+-->
 ```{r}
-library(naniar)
-Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
-  gg_miss_upset()
-
-Frontline %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
-  gg_miss_upset()
+# library(naniar)
+# Frontline %>%
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
+#   gg_miss_upset()
+# 
+# Frontline %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
+#   gg_miss_upset()
 

### 2021-10-27 Rmd/rdi analysis.Rmd
Adding cleanup for cycle number and more

@@
 - exclude patients who didn't survive 1 month
-
-Also height, weight, bsa, creatinine is cleaned and ready. Creatinine minimum is now capped at 0.7 and not 0.8.  
-Creatinine clearance maximum is capped at 125.
 
@@
   mutate(lineenddate_new = last(episodedate)) %>% 
-  ungroup()
+  ungroup() %>% 
+  filter(treatment_sequence == "neo + surg + adj" |
+           treatment_sequence == "surg + adj")
 
@@
 
-`r emo::ji("question_mark")` **Are we keeping the patients who had Neo + surgery without Adjuvant?**
+`r emo::ji("check")`
 
@@
 # F0017FB3A8828 starts with gemcitabine then have carbo
-remove_linename_other <- therapy_line %>%
-  arrange(patientid, episodedate) %>% 
-  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
-  select(patientid, linename, linenumber, linenumber_new, linenumber_adj, drug_count, 
-         drugname, chemotherapy_type, therapy, treatment_sequence, episodedate) %>%
-
-  mutate(remove_linename_other = case_when(
-    linenumber_new == 1 &
-      str_detect(linename, 
-                 "parib|bine|Dox|T|F|Clinical|Cyclo|lumab|Tra|ximab|zole|Aza|trex|Gos|lide|Pem")                       
-                                                                         ~ "remove",
-    linenumber_new == 1 & linename == "Bevacizumab"                      ~ "remove",
-    linenumber_new == 2 &
-      therapy == "Upfront Chemo" &
-      str_detect(linename, 
-                 "parib|bine|Dox|T|F|Clinical|Cyclo")                       
-                                                                         ~ "remove",
-    linenumber_new == 2 &
-      therapy == "Upfront Chemo" & linename == "Bevacizumab"             ~ "remove",
-    TRUE                                           ~ NA_character_
-  )) %>% 
-  arrange(patientid, episodedate)
-
-remove_linename_other <- remove_linename_other %>% 
-  filter(remove_linename_other == "remove") %>% 
-  distinct(patientid, .keep_all = T)
-
-remove_linename_other <- paste(remove_linename_other$patientid, collapse = "|")
 
@@
   # Remove patients with other linename
-  filter(!str_detect(patientid, remove_linename_other)) %>% 
-  arrange(patientid, episodedate)
+  filter((linenumber_new == 1 &
+           (linename == "Carboplatin,Paclitaxel" |
+           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
+           linename == "Carboplatin" |
+           linename == "Paclitaxel" |
+           linename == "Bevacizumab,Paclitaxel" |
+           linename == "Bevacizumab,Carboplatin")) |
+          (linenumber_new == 2 &
+          therapy == "Upfront Chemo" &
+           (linename == "Carboplatin,Paclitaxel" |
+           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
+           linename == "Carboplatin" |
+           linename == "Bevacizumab,Paclitaxel" |
+           linename == "Paclitaxel" |
+           linename == "Bevacizumab,Carboplatin"))
+         )
 ```
@@
   filter(linenumber == 1 & linenumber_new == 2) %>% 
-  select(patientid, drugname, episodedate, line_duration, 
+  select(patientid, surgerydate, episodedate, line_duration, drugname,
          chemotherapy_type, therapy, 
          linenumber, linenumber_new, linenumber_adj) %>% 
-  filter(line_duration < 30)
-```
-
-<!-- Easy example (sorry for the poor looking table `r emo::ji("face_with_raised_eyebrow")`):   -->
-<!-- In this example, 1 cycle is switched from the initial line 1 coded by flatiron to a linenumber_new 2 -->
-
-<!-- <br> -->
-
-<!-- | linenumber (coded by flatiron) |  surgery |  linenumber_new that I coded   |  drug    |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-<!-- |             1                  |          |             1                  | taxel    |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-<!-- |             1                  |          |             1                  | platin   |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-<!-- |             1                  |          |             1                  | taxel    |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-<!-- |             1                  |          |             1                  | platin   |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-<!-- |             1                  |          |             1                  | taxel    |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-<!-- |             1                  |          |             1                  | platin   |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-<!-- |             1                  |          |             1                  | taxel    |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-<!-- |             1                  | happened |             2                  | platin   |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-<!-- |             1                  |          |             2                  | taxel    |   -->
-<!-- | ------------------------------ | -------- | ------------------------------ | -------- |   -->
-
-<!-- <br> -->
+  filter(line_duration < 30) %>% 
+  arrange(line_duration, patientid, episodedate)
+```
 
@@
   fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
+  group_by(patientid, chemotherapy_type, cycle_increment) %>% 
+  mutate(is_dose_dense = row_number(cycle_increment),
+         is_dose_dense = ifelse(is_dose_dense == 1, 1, NA_real_)) %>% 
+  group_by(patientid) %>% 
+  mutate(total_cycle_increment = row_number(is_dose_dense)) %>% 
+  fill(total_cycle_increment, .direction = "downup") %>% 
   # cycle date
@@
   ungroup()
+therapy_cycle %>% distinct(patientid) %>% nrow()
+
+```
+
+```{r remove more than 9 cycle patients}
+too_much_cycle <- therapy_cycle %>% 
+  filter(
+    (therapy == "Upfront Surgery" & total_cycle_increment > 9) |
+      (therapy == "Upfront Chemo" & chemotherapy_type == "Neoadjuvant" & total_cycle_increment > 9)
+  ) %>%
+  distinct(patientid)
+too_much_cycle <- paste(too_much_cycle$patientid, collapse = "|")
+
+therapy_cycle <- therapy_cycle %>% 
+  # remove these patients who switched C > C 
+  filter(!str_detect(patientid, too_much_cycle))
+therapy_cycle %>% distinct(patientid) %>% nrow()
 ```
@@
 
-### If we keep as is, the
-## **Number of patients in final dataset is `r Treatment %>% distinct(patientid) %>% nrow()`**
+### **Number of patients : `r Treatment %>% distinct(patientid) %>% nrow()`**
 
@@
 <br>
-<br>
+
+# Remove patients who don't have any RDI
+```{r remove no RDI patients}
+no_rdi <- Frontline %>% 
+  arrange(RDI_grp) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% select(patientid, RDI_grp) %>% 
+  filter(is.na(RDI_grp))
+
+no_rdi <- paste(no_rdi$patientid, collapse = "|")
+
+Frontline <- Frontline %>% 
+  # remove these patients who switched C > C 
+  filter(!str_detect(patientid, no_rdi))
+Frontline %>% distinct(patientid) %>% nrow()
+```
+<br>
+
+### If we keep as is, the
+## **Number of patients in final dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
 
@@
 Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
   arrange(desc(linenumber_new)) %>% 
@@
 Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  filter(linenumber_new == 1) %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
   mutate(cycle_increment = factor(cycle_increment)) %>% 
@@
 Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
-  filter(linenumber_new == 1) %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
   arrange(desc(cycle_increment)) %>% 
+  mutate(cycle_increment = as.numeric(cycle_increment)) %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
@@
 ```
-Don't forget we have that "neo + surg"
-```{r}
-Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
-  filter(linenumber_new == 1) %>% 
-  arrange(desc(linenumber_new)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new) %>% 
-  tbl_summary()
-
-Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
-  filter(linenumber_new == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment) %>% 
-  tbl_summary()
-```
+
 Number of Adjuvant line in patients with upfront neo
@@
 Treatment %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
   arrange(desc(linenumber_adj)) %>%
@@
 Treatment %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
+  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
   filter(linenumber_adj == 1) %>% 
@@
   select(cycle_increment) %>% 
-  tbl_summary()
+  tbl_summary(label = list(cycle_increment ~ "cycle number during the adjuvant course in Upfront Chemo setting"))
+
+Treatment %>% 
+  filter(therapy == "Upfront Chemo") %>% 
+  filter(linenumber_adj == 1) %>% 
+  mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
+  arrange(desc(total_cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(total_cycle_increment) %>% 
+  tbl_summary(label = list(total_cycle_increment ~ "total cycle number in Upfront Chemo setting"))
 ```
@@
 library(naniar)
-Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
-  gg_miss_upset()
 
@@
            "bmi_at_dx", bmi_cat, "BSA",
-           "stagecat",
-
-           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
-           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
-
-           "hrd_tissue", "gis_tissue")) %>% 
+           "stagecat")) %>% 
   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
 
-# OS by brca1_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca2_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca_tumor
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca1_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca2_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca_g
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r clinical from first treatment, fig.height = 7}
-# OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by tstage
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca1_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca2_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca_tumor
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-# OS by brca1_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca2_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by brca_g
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-</div>
-
-<br>
-<br>
-
-***
-
-<br>
-
-# II.Treatment Analysis
-
-## 1.Treatment summary table
-
-<span style="color:green">**Table 3 Summary treatment data by race**</span>
-```{r Table 3}
-# tbl1 <- 
-  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth,
-           "debulking", "therapy", "treatment_sequence"
-           )) %>% 
-  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-```
-<br>
-
-## 2.Treatment Plots
-<div class = "row">
-<div class = "col-md-6">
-```{r treatment plots}
-Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= therapy))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-# Frontline %>% 
-#   arrange(episodedate) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   group_by(chemotherapy_type) %>% 
-#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
-#   geom_bar(stat="identity")+
-#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
-#   theme_minimal(base_size = 14)+
-#   guides(fill = FALSE) +
-#   coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  # group_by(treatment_sequence) %>% 
-  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-  ggplot(aes(x= treatment_sequence))+
-  geom_bar(
-    # stat="identity"
-    )+
-  labs(x = "", title = "The treatment_sequence") +
-  theme_minimal(base_size = 14)+
-  guides(fill = FALSE) +
-  coord_flip()
-
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill= therapy))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  # group_by(treatment_sequence) %>% 
-  # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-  ggplot(aes(x= raceeth,
-             # y= percent, 
-             fill = treatment_sequence))+
-  geom_bar(
-    position ="fill"
-    )+
-  labs(x = "", title = "The treatment_sequence") +
-  theme_minimal(base_size = 14)+
-  # guides(fill = FALSE) +
-  coord_flip()
-
-# Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-#   ggplot(aes(x= chemo))+
-#   geom_bar()+
-#   theme_minimal(base_size = 14)+
-#   coord_flip()
-```
-</div>
-</div>
-
-<br>
-
-## 3.Survivals by treatment
-
-<div class = "row">
-<div class = "col-md-6">
-```{r treatment survival, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ 1, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ debulking, data=Frontline %>%
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-# OS by residualdiseasestatus
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+# # OS by brca1_tumor
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
 #                      distinct(patientid, .keep_all = TRUE)),
@@
 #            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 1))
-
-# OS by treatment_sequence
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ debulking, data=Frontline %>%
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-# # OS by residualdiseasestatus
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by brca2_tumor
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
 #                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of from first treatment", 
+#            title = "OS from date of diagnosis", 
 #            font.main = c(24, "bold", "black"), 
@@
 #            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 1))
-
-# OS by treatment_sequence
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ treatment_sequence, data=Frontline %>% 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by brca_tumor
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of diagnosis", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by brca1_g
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of diagnosis", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by brca2_g
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of diagnosis", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by brca_g
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of diagnosis", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+
+<div class = "col-md-6">
+```{r clinical from first treatment, fig.height = 7}
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
+           title = "OS from date of first treatment", 
            font.main = c(24, "bold", "black"), 
@@
            legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# # OS by brca1_tumor
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by brca2_tumor
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by brca_tumor
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# # OS by brca1_g
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by brca2_g
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+# 
+# # OS by brca_g
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 2))
+```
+</div>
+</div>
+
+<br>
+<br>
+
+***
+
+<br>
+
+# II.Treatment Analysis
+
+## 1.Treatment summary table
+
+<span style="color:green">**Table 3 Summary treatment data by race**</span>
+```{r Table 3}
+# tbl1 <- 
+  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth,
+           "debulking", "therapy"
+           )) %>% 
+  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+```
+<br>
+
+## 2.Treatment Plots
+<div class = "row">
+<div class = "col-md-6">
+```{r treatment plots}
+Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= therapy))+
+  geom_bar()+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+# Frontline %>% 
+#   arrange(episodedate) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   group_by(chemotherapy_type) %>% 
+#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
+#   geom_bar(stat="identity")+
+#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
+#   theme_minimal(base_size = 14)+
+#   guides(fill = FALSE) +
+#   coord_flip()
+
+# Frontline %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   # group_by(treatment_sequence) %>% 
+#   # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+#   ggplot(aes(x= treatment_sequence))+
+#   geom_bar(
+#     # stat="identity"
+#     )+
+#   labs(x = "", title = "The treatment_sequence") +
+#   theme_minimal(base_size = 14)+
+#   guides(fill = FALSE) +
+#   coord_flip()
+
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill= therapy))+
+  geom_bar(position ="fill")+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+# Frontline %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   # group_by(treatment_sequence) %>% 
+#   # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
+#   ggplot(aes(x= raceeth,
+#              # y= percent, 
+#              fill = treatment_sequence))+
+#   geom_bar(
+#     position ="fill"
+#     )+
+#   labs(x = "", title = "The treatment_sequence") +
+#   theme_minimal(base_size = 14)+
+#   # guides(fill = FALSE) +
+#   coord_flip()
+
+# Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+#   ggplot(aes(x= chemo))+
+#   geom_bar()+
+#   theme_minimal(base_size = 14)+
+#   coord_flip()
+```
+</div>
+</div>
+
+<br>
+
+## 3.Survivals by treatment
+
+<div class = "row">
+<div class = "col-md-6">
+```{r treatment survival, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ 1, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
 ) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ debulking, data=Frontline %>%
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+# OS by residualdiseasestatus
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of diagnosis", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 1))
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of diagnosis", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ debulking, data=Frontline %>%
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+# # OS by residualdiseasestatus
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
+#                      distinct(patientid, .keep_all = TRUE)),
+#            title = "OS from date of from first treatment", 
+#            font.main = c(24, "bold", "black"), 
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+#            size = 1.5,
+#            
+#            pval=TRUE, 
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"), 
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+#            
+#            legend.title = "", xlab = "Time (in months)" 
+# ) + guides(colour = guide_legend(ncol = 1))
 
@@
 
-  facet_wrap(therapy ~ drugname, ncol = 5, scales = "free_x")
+  facet_wrap(therapy ~ drugname, ncol = 3, scales = "free_x")
 ```
@@
 
-tbl4 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-
-tbl5 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-
-tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-
-tbl_stack(list(tbl3, tbl1, tbl2, tbl6, tbl4, tbl5),
+# tbl4 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
+# 
+# tbl5 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
+# 
+# tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(
+#               type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
+
+tbl_stack(list(tbl3, tbl1, tbl2),
           group_header = c("carboplatin/Neoadjuvant", 
                            "carboplatin/Adjuvant Upfront Surgery", 
-                           "carboplatin/Adjuvant Upfront Chemo",
-                           "cisplatin/Neoadjuvant", 
-                           "cisplatin/Adjuvant Upfront Surgery", 
-                           "cisplatin/Adjuvant Upfront Chemo"),
+                           "carboplatin/Adjuvant Upfront Chemo"),
           quiet = TRUE)
@@
 
-tbl7 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-tbl8 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-tbl9 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(#type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-
-tbl_stack(list(tbl3, tbl1, tbl2, tbl6, tbl4, tbl5, tbl9, tbl7, tbl8),
+# tbl7 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
+# tbl8 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
+# tbl9 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(#type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
+
+tbl_stack(list(tbl3, tbl1, tbl2, tbl6, tbl4, tbl5),
           group_header = c("paclitaxel/Neoadjuvant", 
@@
                            "PBB/Adjuvant Upfront Surgery", 
-                           "PBB/Adjuvant Upfront Chemo",
-                           "docetaxel/Neoadjuvant", 
-                           "docetaxel/Adjuvant Upfront Surgery", 
-                           "docetaxel/Adjuvant Upfront Chemo"),
+                           "PBB/Adjuvant Upfront Chemo"),
           quiet = TRUE)
@@
 
-tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl7 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl8 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl5, tbl3, tbl4, tbl8, tbl6, tbl7),
+# tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl6 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl7 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl8 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl5, tbl3, tbl4),
           group_header = c("carboplatin/Neoadjuvant", 
                            "carboplatin/Adjuvant Upfront Surgery", 
-                           "carboplatin/Adjuvant Upfront Chemo",
-                           "cisplatin/Neoadjuvant", 
-                           "cisplatin/Adjuvant Upfront Surgery", 
-                           "cisplatin/Adjuvant Upfront Chemo"),
+                           "carboplatin/Adjuvant Upfront Chemo"),
           quiet = TRUE)
@@
 
-tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl6 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl7 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl8 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl9 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl10 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
+# tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl6 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl7 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
 #               type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
 #               type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl11 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl5, tbl3, tbl4, tbl8, tbl6, tbl7, tbl11, tbl9, tbl10),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl8 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl9 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl10 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# 
+# tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               # type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               # type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl11 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+
+tbl_stack(list(tbl5, tbl3, tbl4),
           group_header = c("paclitaxel/Neoadjuvant", 
                            "paclitaxel/Adjuvant Upfront Surgery", 
-                           "paclitaxel/Adjuvant Upfront Chemo",
-                           "PBB/Neoadjuvant", 
-                           "PBB/Adjuvant Upfront Surgery", 
-                           "PBB/Adjuvant Upfront Chemo",
-                           "docetaxel/Neoadjuvant", 
-                           "docetaxel/Adjuvant Upfront Surgery", 
-                           "docetaxel/Adjuvant Upfront Chemo"),
+                           "paclitaxel/Adjuvant Upfront Chemo"),
           quiet = TRUE)
@@
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "cisplatin") & 
+                     filter(drugname == "paclitaxel" & 
                               chemotherapy_type == "Neoadjuvant") %>%
@@
                    ),
-           title = "OS from diagnosis cisplatin \nNeo",
+           title = "OS from diagnosis paclitaxel \nNeo",
            font.main = c(24, "bold", "black"),
@@
                    data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Neoadjuvant") %>%
+                     filter(str_detect(drugname, "carboplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis paclitaxel \nNeo",
+           title = "OS from diagnosis carboplatin \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "protein") & 
-                              chemotherapy_type == "Neoadjuvant") %>%
+                     filter(drugname == "paclitaxel" & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis PPB \nNeo",
+           title = "OS from diagnosis paclitaxel \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "docetaxel") & 
-                              chemotherapy_type == "Neoadjuvant") %>%
+                     filter(str_detect(drugname, "carboplatin") & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis docetaxel \nNeo",
+           title = "OS from diagnosis carboplatin \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     filter(drugname == "paclitaxel" & 
+                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis carboplatin \nAdj Upfront Surgery",
+           title = "OS from diagnosis paclitaxel \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+```
+</div>
+
+<div class = "col-md-6">
+```{r OS treatment RDI, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "cisplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                     filter(str_detect(drugname, "carboplatin") & 
+                              chemotherapy_type == "Neoadjuvant") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis cisplatin \nAdj Upfront Surgery",
+           title = "OS from first treatment carboplatin \nNeo",
            font.main = c(24, "bold", "black"),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
                    data=Frontline %>% 
                      filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                              chemotherapy_type == "Neoadjuvant") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis paclitaxel \nAdj Upfront Surgery",
+           title = "OS from first treatment paclitaxel \nNeo",
            font.main = c(24, "bold", "black"),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "protein") & 
+                     filter(str_detect(drugname, "carboplatin") & 
                               chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
@@
                    ),
-           title = "OS from diagnosis PPB \nAdj Upfront Surgery",
+           title = "OS from first treatment carboplatin \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp,
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "docetaxel") &
+                     filter(drugname == "paclitaxel" & 
                               chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
@@
                    ),
-           title = "OS from diagnosis docetaxel \nAdj Upfront Surgery",
+           title = "OS from first treatment paclitaxel \nAdj Upfront Surgery",
            font.main = c(24, "bold", "black"),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
                    data=Frontline %>% 
@@
                    ),
-           title = "OS from diagnosis carboplatin \nAdj Upfront Chemo",
+           title = "OS from first treatment carboplatin \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "cisplatin") & 
+                     filter(drugname == "paclitaxel" & 
                               chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
@@
                    ),
-           title = "OS from diagnosis cisplatin \nAdj Upfront Chemo",
+           title = "OS from first treatment pacliatxel \nAdj Upfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis paclitaxel \nAdj Upfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(drugname == "docetaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis docetaxel \nAdj Upfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
-#                    data=Frontline %>% 
-#                      filter(str_detect(drugname, "proetin") & 
-#                               chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis PPB Adj Upfront Chemo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
-
-<div class = "col-md-6">
-```{r OS treatment RDI, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Neoadjuvant") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment carboplatin \nNeo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "cisplatin") & 
-                              chemotherapy_type == "Neoadjuvant") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment cisplatin \nNeo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Neoadjuvant") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment paclitaxel \nNeo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "protein") & 
-                              chemotherapy_type == "Neoadjuvant") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment PPB \nNeo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp,
-                   data=Frontline %>%
-                     filter(str_detect(drugname, "docetaxel") &
-                              chemotherapy_type == "Neoadjuvant") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment docetaxel \nNeo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment carboplatin \nAdj Upfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "cisplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment cisplatin \nAdj Upfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment paclitaxel \nAdj Upfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "protein") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment PPB \nAdj Upfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp,
-                   data=Frontline %>%
-                     filter(str_detect(drugname, "docetaxel") &
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment docetaxel \nAdj Upfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment carboplatin \nAdj Upfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "cisplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment cisplatin \nAdj Upfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment pacliatxel \nAdj Upfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(drugname == "docetaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment docetaxel \nAdj Upfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-#                    data=Frontline %>% 
-#                      filter(str_detect(drugname, "proetin") & 
-#                               chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from first treatment PPB Adj Upfront Chemo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
 ```
@@
 
-# Cisplatin
-tbl4 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
-tbl4 <- tbl4 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl4$month_at_os_from_treatment, event = tbl4$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl5 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl5 <- tbl5 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl5$month_at_os_from_treatment, event = tbl5$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl6 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl6 <- tbl6 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl6$month_at_os_from_treatment, event = tbl6$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
 # Pacli
@@
   italicize_levels()
-
-# PPB
-tbl10 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
-tbl10 <- tbl10 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl10$month_at_os_from_treatment, event = tbl10$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl11 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl11 <- tbl11 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl11$month_at_os_from_treatment, event = tbl11$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl12 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl12 <- tbl12 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl12$month_at_os_from_treatment, event = tbl12$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl10, tbl11, tbl12),
-          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# docetaxel
-tbl13 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
-tbl13 <- tbl13 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl13$month_at_os_from_treatment, event = tbl13$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl14 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl14 <- tbl14 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl14$month_at_os_from_treatment, event = tbl14$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl15 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl15 <- tbl15 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl15$month_at_os_from_treatment, event = tbl15$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl_stack(list(tbl13, tbl14, tbl15),
-          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
 ```
@@
           group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Cisplatin
-tbl4 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
-tbl4 <- 
-  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
-             event = tbl4$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl4) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl5 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl5 <- 
-  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
-             event = tbl5$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl5) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl6 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl6 <- 
-  coxph(Surv(time = tbl6$month_at_os_from_treatment, 
-             event = tbl6$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl6) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
   bold_labels() %>%
@@
   italicize_levels()
-
-# PPB
-tbl10 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
-tbl10 <- 
-  coxph(Surv(time = tbl10$month_at_os_from_treatment, 
-             event = tbl10$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl10) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl11 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl11 <- 
-  coxph(Surv(time = tbl11$month_at_os_from_treatment, 
-             event = tbl11$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl11) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl12 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl12 <- 
-  coxph(Surv(time = tbl12$month_at_os_from_treatment, 
-             event = tbl12$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl12) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl10, tbl11, tbl12),
-          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# docetaxel
-tbl13 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
-tbl13 <- 
-  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
-             event = tbl13$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl13) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl14 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl14 <- 
-  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
-             event = tbl14$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl14) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl15 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl15 <- 
-  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
-             event = tbl15$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl15) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl13, tbl14, tbl15),
-          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
 ```
@@
           group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Cisplatin
-tbl4 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
-tbl4 <- 
-  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
-             event = tbl4$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx, data =  tbl4) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl5 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl5 <- 
-  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
-             event = tbl5$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx, data =  tbl5) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl6 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl6 <- 
-  coxph(Surv(time = tbl6$month_at_os_from_treatment, 
-             event = tbl6$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx, data =  tbl6) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
   bold_labels() %>%
@@
           group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# PPB
-tbl10 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
-tbl10 <- 
-  coxph(Surv(time = tbl10$month_at_os_from_treatment, 
-             event = tbl10$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl10) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl11 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl11 <- 
-  coxph(Surv(time = tbl11$month_at_os_from_treatment, 
-             event = tbl11$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl11) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl12 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl12 <- 
-  coxph(Surv(time = tbl12$month_at_os_from_treatment, 
-             event = tbl12$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl12) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl10, tbl11, tbl12),
-          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# docetaxel
-tbl13 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
-tbl13 <- 
-  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
-             event = tbl13$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl13) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl14 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl14 <- 
-  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
-             event = tbl14$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl14) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl15 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl15 <- 
-  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
-             event = tbl15$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl15) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl13, tbl14, tbl15),
-          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
   bold_labels() %>%
@@
 
-# Cisplatin
-tbl4 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
-tbl4 <- tbl4 %>%
-  select(vitalstatus, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl4$month_at_os_from_treatment, event = tbl4$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl5 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl5 <- tbl5 %>%
-  select(vitalstatus, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl5$month_at_os_from_treatment, event = tbl5$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl6 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl6 <- tbl6 %>%
-  select(vitalstatus, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl6$month_at_os_from_treatment, event = tbl6$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
 # Pacli
@@
   italicize_levels()
-
-# PPB
-tbl10 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
-tbl10 <- tbl10 %>%
-  select(vitalstatus, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl10$month_at_os_from_treatment, event = tbl10$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl11 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl11 <- tbl11 %>%
-  select(vitalstatus, RDI_grp1) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl11$month_at_os_from_treatment, event = tbl11$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl12 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl12 <- tbl12 %>%
-  select(vitalstatus, RDI_grp1) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl12$month_at_os_from_treatment, event = tbl12$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl10, tbl11, tbl12),
-          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# docetaxel
-tbl13 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
-tbl13 <- tbl13 %>%
-  select(vitalstatus, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl13$month_at_os_from_treatment, event = tbl13$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl14 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl14 <- tbl14 %>%
-  select(vitalstatus, RDI_grp1) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl14$month_at_os_from_treatment, event = tbl14$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl15 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl15 <- tbl15 %>%
-  select(vitalstatus, RDI_grp1) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl15$month_at_os_from_treatment, event = tbl15$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl_stack(list(tbl13, tbl14, tbl15),
-          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
 ```
@@
           group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Cisplatin
-tbl4 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
-tbl4 <- 
-  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
-             event = tbl4$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx, data =  tbl4) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl5 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl5 <- 
-  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
-             event = tbl5$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx, data =  tbl5) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl6 <- Frontline %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl6 <- 
-  coxph(Surv(time = tbl6$month_at_os_from_treatment, 
-             event = tbl6$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx, data =  tbl6) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
   bold_labels() %>%
@@
   italicize_levels()
-
-# PPB
-tbl10 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
-tbl10 <- 
-  coxph(Surv(time = tbl10$month_at_os_from_treatment, 
-             event = tbl10$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl10) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl11 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl11 <- 
-  coxph(Surv(time = tbl11$month_at_os_from_treatment, 
-             event = tbl11$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl11) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl12 <- Frontline %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl12 <- 
-  coxph(Surv(time = tbl12$month_at_os_from_treatment, 
-             event = tbl12$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl12) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl10, tbl11, tbl12),
-          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# docetaxel
-tbl13 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
-tbl13 <- 
-  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
-             event = tbl13$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl13) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl14 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl14 <- 
-  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
-             event = tbl14$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl14) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl15 <- Frontline %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl15 <- 
-  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
-             event = tbl15$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl15) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl13, tbl14, tbl15),
-          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
 ```
@@
           group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Cisplatin
-tbl4 <- Frontline_bmi %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
-tbl4 <- 
-  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
-             event = tbl4$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl4) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl5 <- Frontline_bmi %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl5 <- 
-  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
-             event = tbl5$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl5) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl6 <- Frontline_bmi %>%
-  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl6 <- 
-  coxph(Surv(time = tbl6$month_at_os_from_treatment, 
-             event = tbl6$vitalstatus) ~ RDI_grp + raceeth + ageatdx, data =  tbl6) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl4, tbl5, tbl6),
-          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
   bold_labels() %>%
@@
   italicize_levels()
-
-# PPB
-tbl10 <- Frontline_bmi %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
-tbl10 <- 
-  coxph(Surv(time = tbl10$month_at_os_from_treatment, 
-             event = tbl10$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl10) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl11 <- Frontline_bmi %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl11 <- 
-  coxph(Surv(time = tbl11$month_at_os_from_treatment, 
-             event = tbl11$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl11) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl12 <- Frontline_bmi %>%
-  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl12 <- 
-  coxph(Surv(time = tbl12$month_at_os_from_treatment, 
-             event = tbl12$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl12) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl10, tbl11, tbl12),
-          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# docetaxel
-tbl13 <- Frontline_bmi %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
-tbl13 <- 
-  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
-             event = tbl13$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl13) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl14 <- Frontline_bmi %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
-tbl14 <- 
-  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
-             event = tbl14$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl14) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl15 <- Frontline_bmi %>%
-  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
-tbl15 <- 
-  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
-             event = tbl15$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl15) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl13, tbl14, tbl15),
-          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
 ```

### 2021-11-02 Rmd/rdi analysis.Rmd
Fix levels, models, therapy groups, etc

@@
 # Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
-  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg) %>%
+  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg, diagnosisdate) %>%
   summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
@@
 
+### stwp " remove patients with adj too far from sutgery
+```{r}
+remove_delayed_drug <- therapy_line %>% 
+  mutate(interval = case_when(
+    chemotherapy_type == "Adjuvant" & 
+      linenumber_adj == 1       ~interval(start = surgerydate, end = linestartdate_new) / duration(n= 1, units = "months")),
+  ) %>% select(patientid, episodedate, surgerydate, diagnosisdate, linenumber_new, linenumber_adj, interval, therapy, chemotherapy_type) %>% arrange(patientid, episodedate) %>% 
+  filter(interval > 3) %>% 
+  distinct(patientid, .keep_all = TRUE)
+remove_delayed_drug <- paste(remove_delayed_drug$patientid, collapse = "|")
+
+therapy_line <- therapy_line %>% 
+  # Remove patients with more than 1 line as Neo
+  filter(!str_detect(patientid, remove_delayed_drug))
+therapy_line %>% distinct(patientid) %>% nrow()
+
+```
+
 ### step 8: Remove patients with more than 1 line as Neo
@@
     drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
-    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
+    drugname == "paclitaxel"                  ~ BSA * target_auc 
     # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
@@
     drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
-    str_detect(drugname, "taxel|platin")      ~ BSA * target_auc 
+    drugname == "paclitaxel"                  ~ BSA * target_auc 
     # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
@@
   mutate(RDI_grp = case_when(
-    mean_RDI_per_drug >= 0.85              ~ "correct",
-    mean_RDI_per_drug < 0.85               ~ "underdose"
+    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
+    mean_RDI_per_drug < 0.85               ~ "Underdosed"
   )) %>% 
   mutate(RDI_grp = factor(RDI_grp, 
-                           levels = c("correct", "underdose"))) %>% 
+                           levels = c("Adequate dosing", "Underdosed"))) %>% 
   mutate(RDI_grp1 = case_when(
-    mean_RDI_per_drug < 0.75               ~ "highly underdose",
+    mean_RDI_per_drug < 0.75               ~ "Highly underdosed",
     mean_RDI_per_drug >= 0.75 &
-      mean_RDI_per_drug < 0.85             ~ "underdose",
+      mean_RDI_per_drug < 0.85             ~ "Underdosed",
     mean_RDI_per_drug >= 0.85 &
-      mean_RDI_per_drug <= 1                ~ "correct",
-    # mean_RDI_per_drug == 1                 ~ "perfect",
-    # mean_RDI_per_drug > 1 &
-    #   mean_RDI_per_drug < 1.5              ~ "higher dose",
-    mean_RDI_per_drug > 1               ~ "overdose"
+      mean_RDI_per_drug < 1.15             ~ "Adequate dosing",
+    mean_RDI_per_drug >= 1.15              ~ "Overdosing"
   )) %>% 
   mutate(RDI_grp1 = factor(RDI_grp1, 
-                          levels = c("correct", #"perfect", #"higher dose", 
-                                     "overdose", 
-                                     "highly underdose", "underdose")))
+                          levels = c("Adequate dosing",
+                                     "Underdosed", 
+                                     "Highly underdosed",
+                                     "Overdosing")))
 ```
@@
 
-# Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-#   ggplot(aes(x= chemo))+
-#   geom_bar()+
-#   theme_minimal(base_size = 14)+
-#   coord_flip()
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>%
+  ggplot(aes(x= raceeth, fill= therapy))+
+  geom_bar(position ="fill")+
+  theme_minimal(base_size = 14)+
+  coord_flip()+
+  facet_wrap(. ~ drugname)
 ```
@@
 Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
+  ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
   geom_boxplot()+
@@
   geom_jitter(shape=16)+
-  labs(x = "", title = "Warning 1 dot = RDI for 1 patient") +
+  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
   theme_minimal(base_size = 14)+
@@
 Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
+  ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
   # geom_boxplot()+
@@
   theme_minimal(base_size = 14)+
-  facet_wrap(.~ chemotherapy_type)+
+  facet_wrap(.~ therapy)+
   coord_flip()
@@
   theme_minimal(base_size = 14)+
-  facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")
+  facet_wrap(drugname ~ therapy, ncol = 2, scales = "free")
 ```
@@
 
-  facet_wrap(therapy ~ drugname, ncol = 3, scales = "free_x")
+  facet_wrap(therapy ~ drugname, ncol = 2, scales = "free_x")
 ```
@@
 ## 1.RDI summary table
+Do you want them together in 1 table?
 
@@
 # Treatment & demo
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & 
+                               # chemotherapy_type == "Adjuvant" & 
+                               therapy == "Upfront Surgery") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & 
+                               # chemotherapy_type == "Adjuvant" & 
+                               therapy == "Upfront Chemo") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 
-tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
+# tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
 
@@
 
-tbl_stack(list(tbl3, tbl1, tbl2),
-          group_header = c("carboplatin/Neoadjuvant", 
-                           "carboplatin/Adjuvant Upfront Surgery", 
-                           "carboplatin/Adjuvant Upfront Chemo"),
+tbl_stack(list(tbl1, tbl2),
+          group_header = c(
+                           "carboplatin/Upfront Surgery", 
+                           "carboplatin/Upfront Chemo"),
           quiet = TRUE)
@@
 ```{r Table summary Taxanes}
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & 
+                               # chemotherapy_type == "Adjuvant" & 
+                               therapy == "Upfront Surgery") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & 
+                               # chemotherapy_type == "Adjuvant" & 
+                               therapy == "Upfront Chemo") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 
-tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-
-tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
+# tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
+
+# tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
+# tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
+# tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels()
 
@@
 
-tbl_stack(list(tbl3, tbl1, tbl2, tbl6, tbl4, tbl5),
-          group_header = c("paclitaxel/Neoadjuvant", 
-                           "paclitaxel/Adjuvant Upfront Surgery", 
-                           "paclitaxel/Adjuvant Upfront Chemo",
-                           "PBB/Neoadjuvant", 
-                           "PBB/Adjuvant Upfront Surgery", 
-                           "PBB/Adjuvant Upfront Chemo"),
+tbl_stack(list(tbl1, tbl2),
+          group_header = c(
+                           "paclitaxel/Upfront Surgery", 
+                           "paclitaxel/Upfront Chemo"),
           quiet = TRUE)
@@
 <span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
+Removing the overall on the right side? Or do you want the tables separated?
 Platin  
@@
 # Treatment & demo
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+tbl1 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+tbl2 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl5 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
 
@@
 
-tbl_stack(list(tbl5, tbl3, tbl4),
-          group_header = c("carboplatin/Neoadjuvant", 
-                           "carboplatin/Adjuvant Upfront Surgery", 
-                           "carboplatin/Adjuvant Upfront Chemo"),
+tbl_stack(list(tbl3, tbl4),
+          group_header = c(
+                           "carboplatin/Upfront Surgery", 
+                           "carboplatin/Upfront Chemo"),
           quiet = TRUE)
@@
 ```{r Table4 summary Taxanes}
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Surgery") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Surgery") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Chemo") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Chemo") %>%
   distinct(patientid, .keep_all = TRUE) %>%
@@
 
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl5 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+# tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = raceeth,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
+#   tbl_summary(by = bmi_cat,
+#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
+#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+# tbl5 <-
+#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
 
@@
 
-tbl_stack(list(tbl5, tbl3, tbl4),
-          group_header = c("paclitaxel/Neoadjuvant", 
-                           "paclitaxel/Adjuvant Upfront Surgery", 
-                           "paclitaxel/Adjuvant Upfront Chemo"),
+tbl_stack(list(tbl3, tbl4),
+          group_header = c(
+                           "paclitaxel/Upfront Surgery", 
+                           "paclitaxel/Upfront Chemo"),
           quiet = TRUE)
@@
 # OS by RDI_grp for platin
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+#                    data=Frontline %>% 
+#                      filter(str_detect(drugname, "carboplatin") & 
+#                               chemotherapy_type == "Neoadjuvant") %>%
+#                      distinct(patientid, .keep_all = TRUE)
+#                    ),
+#            title = "OS from diagnosis carboplatin \nNeo",
+#            font.main = c(24, "bold", "black"),
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+#            size = 1.5,
+# 
+#            pval=TRUE,
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"),
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+# 
+#            legend.title = "", xlab = "Time (in months)"
+# ) + guides(colour = guide_legend(ncol = 1))
+
+# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+#                    data=Frontline %>% 
+#                      filter(drugname == "paclitaxel" & 
+#                               chemotherapy_type == "Neoadjuvant") %>%
+#                      distinct(patientid, .keep_all = TRUE)
+#                    ),
+#            title = "OS from diagnosis paclitaxel \nNeo",
+#            font.main = c(24, "bold", "black"),
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+#            size = 1.5,
+# 
+#            pval=TRUE,
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"),
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+# 
+#            legend.title = "", xlab = "Time (in months)"
+# ) + guides(colour = guide_legend(ncol = 1))
+
 ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
@@
                      filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Neoadjuvant") %>%
+                             therapy == "Upfront Surgery") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis carboplatin \nNeo",
+           title = "OS from diagnosis carboplatin \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                      filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Neoadjuvant") %>%
+                              therapy == "Upfront Surgery") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis paclitaxel \nNeo",
+           title = "OS from diagnosis paclitaxel \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
                      filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                              therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis carboplatin \nAdj Upfront Surgery",
+           title = "OS from diagnosis carboplatin \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                      filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
+                              therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis paclitaxel \nAdj Upfront Surgery",
+           title = "OS from diagnosis paclitaxel \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+```
+</div>
+
+<div class = "col-md-6">
+```{r OS treatment RDI, fig.height = 7}
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+#                    data=Frontline %>% 
+#                      filter(str_detect(drugname, "carboplatin") & 
+#                               chemotherapy_type == "Neoadjuvant") %>%
+#                      distinct(patientid, .keep_all = TRUE)
+#                    ),
+#            title = "OS from first treatment carboplatin \nNeo",
+#            font.main = c(24, "bold", "black"),
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+#            size = 1.5,
+# 
+#            pval=TRUE,
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"),
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+# 
+#            legend.title = "", xlab = "Time (in months)"
+# ) + guides(colour = guide_legend(ncol = 1))
+
+# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+#                    data=Frontline %>% 
+#                      filter(drugname == "paclitaxel" & 
+#                               chemotherapy_type == "Neoadjuvant") %>%
+#                      distinct(patientid, .keep_all = TRUE)
+#                    ),
+#            title = "OS from first treatment paclitaxel \nNeo",
+#            font.main = c(24, "bold", "black"),
+#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+#            size = 1.5,
+# 
+#            pval=TRUE,
+#            # legend.labs=c(""),
+#            # palette = c("black", "green","blue", "red"),
+#            # Add risk table
+#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+#            tables.theme = theme_survminer(base_size = 5,
+#                                           font.main = c(16, "bold", "black"),
+#                                           font.x = c(16, "bold", "black"),
+#                                           font.y = c(16, "bold", "transparent"),
+#                                           font.tickslab = c(19, "bold", "black")
+#            ),
+# 
+#            legend.title = "", xlab = "Time (in months)"
+# ) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
                    data=Frontline %>% 
                      filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                              therapy == "Upfront Surgery") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis carboplatin \nAdj Upfront Chemo",
+           title = "OS from first treatment carboplatin \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
                    data=Frontline %>% 
                      filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
+                              therapy == "Upfront Surgery") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis paclitaxel \nAdj Upfront Chemo",
+           title = "OS from first treatment paclitaxel \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
-
-<div class = "col-md-6">
-```{r OS treatment RDI, fig.height = 7}
+
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
@@
                      filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Neoadjuvant") %>%
+                              therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from first treatment carboplatin \nNeo",
+           title = "OS from first treatment carboplatin \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
                      filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Neoadjuvant") %>%
+                              therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from first treatment paclitaxel \nNeo",
+           title = "OS from first treatment pacliatxel \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment carboplatin \nAdj Upfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment paclitaxel \nAdj Upfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment carboplatin \nAdj Upfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-                   data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from first treatment pacliatxel \nAdj Upfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
 ```
@@
 # Carbo
-tbl1 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-tbl1 <- tbl1 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl1 <- Frontline %>%
+#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+# tbl1 <- tbl1 %>%
+#   select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
+#   tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
 tbl2 <- tbl2 %>%
@@
                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
 tbl3 <- tbl3 %>%
@@
                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
   bold_labels() %>%
@@
 # Pacli
-tbl7 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-tbl7 <- tbl7 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl7 <- Frontline %>%
+#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+# tbl7 <- tbl7 %>%
+#   select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
+#   tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
 tbl8 <- tbl8 %>%
@@
                  y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
 tbl9 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
 tbl9 <- tbl9 %>%
@@
                  y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+tbl_stack(list(tbl8, tbl9),
+          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
   bold_labels() %>%
@@
 # Carbo
-tbl1 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-tbl1 <- 
-  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
-             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl1) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl1 <- Frontline %>%
+#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+# tbl1 <- 
+#   coxph(Surv(time = tbl1$month_at_os_from_treatment, 
+#              event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl1) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
 tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
 tbl2 <- 
@@
              event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
 tbl3 <- 
@@
              event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
   bold_labels() %>%
@@
 # Pacli
-tbl7 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-tbl7 <- 
-  coxph(Surv(time = tbl7$month_at_os_from_treatment, 
-             event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl7) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl7 <- Frontline %>%
+#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+# tbl7 <- 
+#   coxph(Surv(time = tbl7$month_at_os_from_treatment, 
+#              event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl7) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
 tbl8 <- 
@@
              event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl8) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl9 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
 tbl9 <- 
@@
              event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl9) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl8, tbl9),
+          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
   bold_labels() %>%
@@
 # Carbo
-tbl1 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-tbl1 <- 
-  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
-             event = tbl1$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl1) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl1 <- Frontline %>%
+#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+# tbl1 <- 
+#   coxph(Surv(time = tbl1$month_at_os_from_treatment, 
+#              event = tbl1$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl1) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
 tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
 tbl2 <- 
@@
              event = tbl2$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
 tbl3 <- 
@@
              event = tbl3$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
   bold_labels() %>%
@@
 # Pacli
-tbl7 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-tbl7 <- 
-  coxph(Surv(time = tbl7$month_at_os_from_treatment, 
-             event = tbl7$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl7) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl7 <- Frontline %>%
+#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+# tbl7 <- 
+#   coxph(Surv(time = tbl7$month_at_os_from_treatment, 
+#              event = tbl7$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl7) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
 tbl8 <- 
@@
              event = tbl8$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl8) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl9 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
 tbl9 <- 
@@
              event = tbl9$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl9) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl8, tbl9),
+          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
   bold_labels() %>%
@@
 
-As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI or being underdosed or overdose
+As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed
 
 ```{r echo=TRUE}
-# RDI_grp1 = case_when(
-#     mean_RDI_per_drug < 0.75               ~ "highly underdose",
-#     mean_RDI_per_drug >= 0.75 &
-#       mean_RDI_per_drug < 0.85             ~ "underdose",
-#     mean_RDI_per_drug >= 0.85 &
-#       mean_RDI_per_drug < 1                ~ "correct",
-#     mean_RDI_per_drug == 1                 ~ "perfect",
-#     mean_RDI_per_drug > 1                  ~ "overdose"
-#   ))
-```
-
+# Highly underdosed: < 0.75
+# Underdosed: >= 0.75 to <0.85
+# Adequate dosing: >= 0.85 to <1.15
+# Overdosing: >=1.15
+```
+Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI)
 ```{r, fig.width=12, fig.height=12}
@@
   theme_minimal(base_size = 10)+
-  facet_wrap(drugname~ chemotherapy_type, ncol = 2, scales = "free")+
+  facet_wrap(. ~ therapy, ncol = 2, scales = "free")+
   coord_flip()
@@
   coord_flip()+
-  facet_wrap(.~ chemotherapy_type)
+  facet_wrap(.~ therapy)
 ```
@@
 # Carbo
-tbl1 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-tbl1 <- tbl1 %>%
-  select(vitalstatus, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl1 <- Frontline %>%
+#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+# tbl1 <- tbl1 %>%
+#   select(vitalstatus, RDI_grp1) %>% 
+#   tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
 tbl2 <- tbl2 %>%
@@
 # Pacli
-tbl7 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-tbl7 <- tbl7 %>%
-  select(vitalstatus, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl7 <- Frontline %>%
+#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+# tbl7 <- tbl7 %>%
+#   select(vitalstatus, RDI_grp1) %>% 
+#   tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
 tbl8 <- tbl8 %>%
@@
 # Carbo
-tbl1 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-tbl1 <- 
-  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
-             event = tbl1$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl1) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl1 <- Frontline %>%
+#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+# tbl1 <- 
+#   coxph(Surv(time = tbl1$month_at_os_from_treatment, 
+#              event = tbl1$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl1) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
 tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
 tbl2 <- 
@@
              event = tbl2$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
 tbl3 <- 
@@
              event = tbl3$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
   bold_labels() %>%
@@
 # Pacli
-tbl7 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-tbl7 <- 
-  coxph(Surv(time = tbl7$month_at_os_from_treatment, 
-             event = tbl7$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl7) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl7 <- Frontline %>%
+#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+# tbl7 <- 
+#   coxph(Surv(time = tbl7$month_at_os_from_treatment, 
+#              event = tbl7$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl7) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
 tbl8 <- 
@@
              event = tbl8$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl8) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl9 <- Frontline %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
 tbl9 <- 
@@
              event = tbl9$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl9) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl8, tbl9),
+          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
   bold_labels() %>%
@@
 # Carbo
-tbl1 <- Frontline_bmi %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-tbl1 <- 
-  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
-             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl1 <- Frontline_bmi %>%
+#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
+# tbl1 <- 
+#   coxph(Surv(time = tbl1$month_at_os_from_treatment, 
+#              event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 
 tbl2 <- Frontline_bmi %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
 tbl2 <- 
@@
              event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl3 <- Frontline_bmi %>%
-  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
 tbl3 <- 
@@
              event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
   bold_labels() %>%
@@
 # Pacli
-tbl7 <- Frontline_bmi %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-tbl7 <- 
-  coxph(Surv(time = tbl7$month_at_os_from_treatment, 
-             event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+# tbl7 <- Frontline_bmi %>%
+#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
+# tbl7 <- 
+#   coxph(Surv(time = tbl7$month_at_os_from_treatment, 
+#              event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl8 <- Frontline_bmi %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
 tbl8 <- 
@@
              event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl9 <- Frontline_bmi %>%
-  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
+  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
 tbl9 <- 
@@
              event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl8, tbl9),
+          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
   bold_labels() %>%

### 2021-11-02 R/2.data cleaning.R

@@ -577,7 +577,13 @@ clinical_data <- clinical_data %>%
            duration(n=1, units = "months")) %>% 
   # 30 days rule for patient who didn't survive more than 30 days after diagnosis
   filter(month_at_os > 1) %>% # Loss 198 patients
-  mutate(stagecat = na_if(stagecat, "Unk Stage")) %>% 
+  mutate(#stagecat = na_if(stagecat, "Unk Stage"),
+         stagecat = case_when(
+           stagecat == "Stage 1" |
+             stagecat == "Stage 2"              ~ "Early stage",
+           stagecat == "Stage 3" |
+             stagecat == "Stage 4"              ~ "Late stage"
+         )) %>% 
   mutate(across(.cols = c(histology, groupstage, tstage), ~na_if(., "Unknown/not documented")))
 write_rds(clinical_data, "clinical_data.rds")
 

### 2021-11-17 Rmd/rdi analysis.Rmd
Update

@@
 drugs1 <- drugs %>% 
-  filter(episodedatasource == "Administrations" & 
-           ismaintenancetherapy == "FALSE") %>%
+  filter(episodedatasource == "Administrations" #& 
+           # ismaintenancetherapy == "FALSE"
+         ) %>%
   # 1. 60 days rule between diagnosis and treatment # Loss 1
@@
 # Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
-  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg, diagnosisdate) %>%
+  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg, diagnosisdate, ismaintenancetherapy) %>%
   summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
@@
 
-### stwp " remove patients with adj too far from sutgery
+<!-- ### step : remove patients with adj too far from surgery -->
 ```{r}
-remove_delayed_drug <- therapy_line %>% 
-  mutate(interval = case_when(
-    chemotherapy_type == "Adjuvant" & 
-      linenumber_adj == 1       ~interval(start = surgerydate, end = linestartdate_new) / duration(n= 1, units = "months")),
-  ) %>% select(patientid, episodedate, surgerydate, diagnosisdate, linenumber_new, linenumber_adj, interval, therapy, chemotherapy_type) %>% arrange(patientid, episodedate) %>% 
-  filter(interval > 3) %>% 
-  distinct(patientid, .keep_all = TRUE)
-remove_delayed_drug <- paste(remove_delayed_drug$patientid, collapse = "|")
-
-therapy_line <- therapy_line %>% 
-  # Remove patients with more than 1 line as Neo
-  filter(!str_detect(patientid, remove_delayed_drug))
-therapy_line %>% distinct(patientid) %>% nrow()
+# remove_delayed_drug <- therapy_line %>% 
+#   mutate(interval = case_when(
+#     chemotherapy_type == "Adjuvant" & 
+#       linenumber_adj == 1       ~interval(start = surgerydate, end = linestartdate_new) / duration(n= 1, units = "months")),
+#   ) %>% select(patientid, episodedate, surgerydate, diagnosisdate, linenumber_new, linenumber_adj, interval, therapy, chemotherapy_type) %>% arrange(patientid, episodedate) %>% 
+#   filter(interval > 3) %>% 
+#   distinct(patientid, .keep_all = TRUE)
+# remove_delayed_drug <- paste(remove_delayed_drug$patientid, collapse = "|")
+# 
+# therapy_line <- therapy_line %>% 
+#   # Remove patients with more than 1 line as Neo
+#   filter(!str_detect(patientid, remove_delayed_drug))
+# therapy_line %>% distinct(patientid) %>% nrow()
 
@@
 
-<!-- `r emo::ji("question_mark")`   -->
+`r emo::ji("question_mark")`
+<span style="color:red">**Patients have maintenance as first line Adjuvant then recurrent treatment : Should I remove these patients or keep them for the Neoadjuvant RDI??**</span>
+```{r}
+therapy_line %>% 
+  filter(linenumber_adj == 1) %>% 
+  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
+  select(ismaintenancetherapy, linename) %>% 
+  tbl_summary(by = linename)
+```
+
 <!-- <span style="color:red">**Random question : within 1 cycle we can have taxanes multiple times, is it possible for carboplatin or cisplatin?**</span>   -->
@@
   mutate(cycle_count_perline = min(drugname_count_perline)) %>%
-  mutate(cycle_drugname = case_when(
+  mutate(cycle_major_drugname = case_when(
     cycle_count_perline == drugname_count_perline          ~ cycle_drugname,
@@
   # select(-drugname_count_perline) %>% 
-  group_by(patientid, linenumber_new, cycle_drugname) %>%
-  mutate(cycle_increment = row_number(cycle_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
+  group_by(patientid, linenumber_new, cycle_major_drugname) %>%
+  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
   # F01D908A013B7 has more pacli at the end but in the same line
@@
   mutate(cycle_start_date = min(episodedate)) %>%
-  # select(patientid, linename, linenumber_new, drugname, episodedate,
-  #        cycle_count_perline, cycle_drugname, drugname_count_perline, cycle_increment, cycle_start_date) %>%
+
+  # Look at dose dense
+  group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
+  mutate(dose_dense = n()) %>% 
+  mutate(dose_dense = max(dose_dense)) %>%  # too much cycle
+  ungroup() # %>% 
+  # select(patientid, linename, linenumber_new, drugname, episodedate, chemotherapy_type, cycle_increment, dose_dense,
+  #        is_dose_dense,cycle_major_drugname, cycle_drugname,
+  #        cycle_count_perline, cycle_major_drugname, drugname_count_perline, cycle_start_date) #%>%  # F002DD2953889, F003F2BEEDB37 only 1+2
 
@@
   # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
-  ungroup()
+  # ungroup()
 therapy_cycle %>% distinct(patientid) %>% nrow()
@@
 
+# Remove too much cycle
 ```{r remove more than 9 cycle patients}
+therapy_cycle %>% 
+  filter(linenumber_new == 1) %>% 
+  arrange(patientid, linenumber_new, desc(dose_dense)) %>% 
+  mutate(dose_dense = as.factor(dose_dense)) %>%  # too much cycle
+  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
+  select(dose_dense, linename) %>% 
+  tbl_summary(by = linename)
+
 too_much_cycle <- therapy_cycle %>%

### 2021-11-18 Rmd/rdi analysis.Rmd
Add question, ready for live modif and add HR adjusted by drug

@@
   # bind with clinical
-  inner_join(., clinical_data, #%>% select("patientid", "diagnosisdate", "surgerydate"),
+  inner_join(., clinical_data, 
           by = "patientid") %>% 
@@
 
-### step 2: 90 days rule between diagnosis and treatment
+### step 2: Flatiron recommendation cleanup
+#### 90 days rule between diagnosis and treatment
 
@@
 
-### step 3: 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis
+#### 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis
 
@@
 
-### step 4: Exclude exclude == "1" coded by Lauren
+#### Exclude exclude == "1" coded by Lauren
 
@@
 
-### step 5: Remove chemotherapy only patients
+### step 3: Remove chemotherapy only patients
 ```{r}
@@
 
-### step 5: Combine multiple administrations of the same drug at the same date
+#### Combine multiple administrations of the same drug at the same date
 ```{r combine amount same drug one day}
@@
   # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
-  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%
+  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory)) %>%
 
@@
 # Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
-  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg, diagnosisdate, ismaintenancetherapy) %>%
-  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
+  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, 
+           drugname, units, surgerydate, days_at_first_drug, days_at_surg, 
+           diagnosisdate, ismaintenancetherapy) %>%
+  summarise_at(vars(route, amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
+  mutate(route = case_when(
+    str_detect(route, ";")            ~ "Intravenous",
+    TRUE                              ~ route
+  )) %>% 
   separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
@@
 
-### step 6: Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
+#### Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
 ```{r line coding}
@@
   group_by(patientid, linenumber_new) %>% 
-  mutate(linestartdate_new = first(episodedate)) %>% 
-  mutate(lineenddate_new = last(episodedate)) %>% 
+  mutate(linestartdate_new = min(episodedate)) %>% 
+  mutate(lineenddate_new = max(episodedate)) %>% 
   ungroup() %>% 
@@
               missing = "no")
-therapy_line %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(therapy, treatment_sequence) %>% 
-  tbl_summary(by = therapy)
+# therapy_line %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(therapy, treatment_sequence) %>% 
+#   tbl_summary(by = therapy)
 ```
@@
 
-<!-- ### step : remove patients with adj too far from surgery -->
-```{r}
-# remove_delayed_drug <- therapy_line %>% 
-#   mutate(interval = case_when(
-#     chemotherapy_type == "Adjuvant" & 
-#       linenumber_adj == 1       ~interval(start = surgerydate, end = linestartdate_new) / duration(n= 1, units = "months")),
-#   ) %>% select(patientid, episodedate, surgerydate, diagnosisdate, linenumber_new, linenumber_adj, interval, therapy, chemotherapy_type) %>% arrange(patientid, episodedate) %>% 
-#   filter(interval > 3) %>% 
-#   distinct(patientid, .keep_all = TRUE)
-# remove_delayed_drug <- paste(remove_delayed_drug$patientid, collapse = "|")
-# 
-# therapy_line <- therapy_line %>% 
-#   # Remove patients with more than 1 line as Neo
-#   filter(!str_detect(patientid, remove_delayed_drug))
-# therapy_line %>% distinct(patientid) %>% nrow()
-
-```
-
-### step 8: Remove patients with more than 1 line as Neo
-We are removing the 34 patients who received multiple Neoadjuvant line.   
-`r emo::ji("check")`
-
-<!-- Here the lines for the 34 patient. -->
-```{r, rows.print = 40}
-# therapy_line %>% 
-#   filter(chemotherapy_type == "Neoadjuvant" &
-#            (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
-#   select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
-#          drugname, episodedate, surgerydate, chemotherapy_type) %>%
-#   arrange(patientid, episodedate) %>% 
-#   distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
-#   select(-linenumber)
-
-remove_morethan1_neo <- therapy_line %>% 
-  filter(chemotherapy_type == "Neoadjuvant" &
-           linenumber_new != 1)
-remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")
-
-therapy_line <- therapy_line %>% 
-  # Remove patients with more than 1 line as Neo
-  filter(!str_detect(patientid, remove_morethan1_neo))
-```
-
-Patients left:
-```{r}
-therapy_line %>% distinct(patientid) %>% nrow()
-```
-
-### step 7: Remove linename that doesn't include platinum or taxanes in first line
+### step 4: Remove linename that doesn't include platinum or taxanes in first line
 
@@
   tbl_summary(sort = list(everything() ~ "frequency"))
-
+```
+
+We now have `r therapy_line %>% distinct(patientid) %>% nrow()` patients.
+
+### step 5: remove patients with maintenance as first line adjuvant?????
+`r emo::ji("question_mark")`
+<span style="color:red">**Patients have maintenance as first line Adjuvant then recurrent treatment : Should I remove these patients or keep them for the Neoadjuvant RDI??**</span>
+```{r}
+therapy_line %>% 
+  filter(linenumber_adj == 1) %>% 
+  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
+  select(ismaintenancetherapy, linename) %>% 
+  tbl_summary(by = linename)
+therapy_line %>% 
+  filter(linenumber_adj == 1) %>%
+  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
+  select(ismaintenancetherapy, chemotherapy_type) %>% 
+  tbl_summary(by = chemotherapy_type)
+therapy_line %>% 
+  filter(linenumber_adj == 1, chemotherapy_type == "Neoadjuvant") %>%
+  arrange(desc(ismaintenancetherapy)) %>% 
+  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
+  select(ismaintenancetherapy, chemotherapy_type) %>% 
+  tbl_summary(by = chemotherapy_type)
+```
+
+#### remove only the maintenance line in neo or adj
+```{r remove only the maintenance line in neo or adj}
+# therapy_line <- therapy_line %>% 
+#   filter(!(ismaintenancetherapy == TRUE & linenumber_adj == 1))
 # therapy_line %>% distinct(patientid) %>% nrow()
@@
 
-We now have `r therapy_line %>% distinct(patientid) %>% nrow()` patients.
+#### OR remove patients with maintenance in neo
+```{r remove patients with maintenance in neo}
+# remove_neo_patients_maintenance <- therapy_line %>% 
+#   filter(linenumber_adj == 1, chemotherapy_type == "Neoadjuvant", ismaintenancetherapy == TRUE) %>%
+#   arrange(desc(ismaintenancetherapy)) %>% 
+#   distinct(patientid)
+# 
+# therapy_line <- therapy_line %>%
+#   filter(!str_detect(patientid, paste(remove_neo_patients_maintenance$patientid, collapse = "|")))
+# therapy_line %>% distinct(patientid) %>% nrow()
+```
+
+#### OR remove totally patients with maintenance in frontline neo or adj
+```{r remove totally patients with maintenance in neo or adj}
+remove_patients_maintenance <- therapy_line %>% 
+  filter(linenumber_adj == 1 & ismaintenancetherapy == TRUE) %>%
+  arrange(desc(ismaintenancetherapy)) %>% 
+  distinct(patientid)
+
+therapy_line <- therapy_line %>%
+  filter(!str_detect(patientid, paste(remove_patients_maintenance$patientid, collapse = "|")))
+therapy_line %>% distinct(patientid) %>% nrow()
+```
+
+### step 6: remove patients with long gap between surgery and adjuvant start ????
+Depending on the answers:
+
+#### remove patients with more than 9 cycles total in upfront chemo or upfront surgery
+Did a gap of 3 months
+```{r}
+remove_delayed_drug <- therapy_line %>%
+  mutate(interval = case_when(
+      chemotherapy_type == "Adjuvant" &
+        linenumber_adj == 1       
+      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
+    ),
+  ) %>% 
+  arrange(patientid, episodedate) %>%
+  filter(interval > 3) %>%
+  distinct(patientid, .keep_all = TRUE)
+
+therapy_line <- therapy_line %>%
+  # Remove patients with more than 1 line as Neo
+  filter(!str_detect(patientid, paste(remove_delayed_drug$patientid, collapse = "|")))
+therapy_line %>% distinct(patientid) %>% nrow()
+```
+
+### step 7: Remove patients with more than 1 line as Neo
+We are removing the 34 patients who received multiple Neoadjuvant line.   
+`r emo::ji("check")`
+
+<!-- Here the lines for the 34 patient. -->
+```{r, rows.print = 40}
+# therapy_line %>% 
+#   filter(chemotherapy_type == "Neoadjuvant" &
+#            (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
+#   select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
+#          drugname, episodedate, surgerydate, chemotherapy_type) %>%
+#   arrange(patientid, episodedate) %>% 
+#   distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
+#   select(-linenumber)
+
+remove_morethan1_neo <- therapy_line %>% 
+  filter(chemotherapy_type == "Neoadjuvant" &
+           linenumber_new != 1) %>% 
+  distinct(patientid)
+
+therapy_line <- therapy_line %>% 
+  # Remove patients with more than 1 line as Neo
+  filter(!str_detect(patientid, paste(remove_morethan1_neo$patientid, collapse = "|")))
+```
+
+Patients left:
+```{r}
+therapy_line %>% distinct(patientid) %>% nrow()
+```
 
@@
   filter(linenumber == 1 & linenumber_new == 2) %>% 
-  select(patientid, linenumber, linenumber_new, linenumber_adj, 
-         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
+  # select(patientid, linenumber, linenumber_new, linenumber_adj, 
+  #        drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= line_duration))+
-  geom_histogram(color = "slateblue", fill = "grey", binwidth = 7) +
+  geom_histogram(color = "slateblue", aes(fill = route), binwidth = 7) +
   theme_minimal(base_size = 14)+
@@
   ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
-
 ```
 Several patients have a short line.  
-`r emo::ji("question_mark")` **Should me remove the patient with a line during less than a cycle
+`r emo::ji("question_mark")` **Should me remove the patient with a line during less than a cycle** We said during October meeting to check at IP
 
@@
          chemotherapy_type, therapy, 
-         linenumber, linenumber_new, linenumber_adj) %>% 
+         linenumber, linenumber_new, route, amount) %>% 
   filter(line_duration < 30) %>% 
   arrange(line_duration, patientid, episodedate)
+```
+
+#### Remove peritoneal administration
+```{r}
+therapy_line <- therapy_line %>% 
+  filter(route == "Intravenous")
 ```
@@
 
-### step 9: Remove patients who switch drug within a line
+### step 8: Remove patients who switch drug within a line
 
@@
 
-`r emo::ji("question_mark")`
-<span style="color:red">**Patients have maintenance as first line Adjuvant then recurrent treatment : Should I remove these patients or keep them for the Neoadjuvant RDI??**</span>
-```{r}
-therapy_line %>% 
-  filter(linenumber_adj == 1) %>% 
-  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
-  select(ismaintenancetherapy, linename) %>% 
-  tbl_summary(by = linename)
-```
-
 <!-- <span style="color:red">**Random question : within 1 cycle we can have taxanes multiple times, is it possible for carboplatin or cisplatin?**</span>   -->
 
-### step 10: Code cycle
+#### Code cycle
 ```{r cycle coding}
@@
   ungroup() # %>% 
-  # select(patientid, linename, linenumber_new, drugname, episodedate, chemotherapy_type, cycle_increment, dose_dense,
+  # select(patientid, linename, linenumber_new, drugname, episodedate, chemotherapy_type, cycle_increment, dose_dense, amount, ismaintenancetherapy,
   #        is_dose_dense,cycle_major_drugname, cycle_drugname,
@@
 
-# Remove too much cycle
-```{r remove more than 9 cycle patients}
+### step 9: Remove too much cycle
+```{r more than 9 cycle patients}
 therapy_cycle %>% 
-  filter(linenumber_new == 1) %>% 
+  filter(therapy == "Upfront Chemo") %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(cycle_increment, chemotherapy_type) %>% 
+  tbl_summary(by = chemotherapy_type)
+therapy_cycle %>% 
+  filter(therapy == "Upfront Surgery") %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(cycle_increment, chemotherapy_type) %>% 
+  tbl_summary(by = chemotherapy_type)
+```
+We said to remove patients with more than 9 total cycle but maybe we can save some....
+
+#### What is dose dense / or unnoted maintenance (example in ppt) 
+2 in the dose dense would mean 1 carbo + 2 pacli  
+3 in the dose dense would mean 1 carbo + 3 pacli  
+etc
+```{r what is dose dense}
+therapy_cycle %>% 
+  filter(linenumber_adj == 1) %>% 
   arrange(patientid, linenumber_new, desc(dose_dense)) %>% 
-  mutate(dose_dense = as.factor(dose_dense)) %>%  # too much cycle
+  mutate(dose_dense = as.factor(dose_dense)) %>% 
   distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
@@
   tbl_summary(by = linename)
-
+```
+
+#### Remove wrong dose dense patients (>3) ???
+```{r remove wrong dose dense patients}
+wrong_dose_dense <- therapy_cycle %>% 
+  filter(linenumber_adj == 1 & dose_dense > 3) %>% 
+  distinct(patientid)
+
+therapy_cycle <- therapy_cycle %>%
+  filter(!str_detect(patientid, paste(wrong_dose_dense$patientid, collapse = "|")))
+therapy_cycle %>% distinct(patientid) %>% nrow()
+```
+
+#### OR Remove only the extra administration from 1+3 dose dense???
+```{r remove only the extra administration from 1+3 dose dense}
+therapy_cycle <- therapy_cycle %>%
+  filter(dose_dense <= 3)
+therapy_cycle %>% distinct(patientid) %>% nrow()
+```
+
+#### Then
+#### Remove totally the patients with more than 9 cycle total
+```{r more than 9 cycle patients same code}
+therapy_cycle %>% 
+  filter(therapy == "Upfront Chemo") %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(cycle_increment, chemotherapy_type) %>% 
+  tbl_summary(by = chemotherapy_type)
+therapy_cycle %>% 
+  filter(therapy == "Upfront Surgery") %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  arrange(desc(cycle_increment)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(cycle_increment, chemotherapy_type) %>% 
+  tbl_summary(by = chemotherapy_type)
+```
+
+```{r remove more than 9 cycle patients}
 too_much_cycle <- therapy_cycle %>%
@@
   distinct(patientid)
-too_much_cycle <- paste(too_much_cycle$patientid, collapse = "|")
 
@@
   # remove these patients who switched C > C
-  filter(!str_detect(patientid, too_much_cycle))
+  filter(!str_detect(patientid, paste(too_much_cycle$patientid, collapse = "|")))
 therapy_cycle %>% distinct(patientid) %>% nrow()
@@
 
-### step 11: Bind everything together and calculating target_auc and expected dose
+#### OR remove only the extra cycle????
+```{r remove only the extra cycle}
+therapy_cycle <- therapy_cycle %>%
+  filter(total_cycle_increment <= 9)
+therapy_cycle %>% distinct(patientid) %>% nrow()
+```
+
+### step 10: Bind everything together and calculating target_auc and expected dose
 
@@
   ungroup() %>% 
-  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
+  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE)
+```
+
+```{r RDI calculation 1 per patient}
+Frontline <- Frontline %>% 
+  group_by(patientid, drugname) %>%
+  mutate(mean_RDI_per_drug = round(mean(mean_RDI_per_drug, na.rm = TRUE), 3)
+  ) %>% 
+  ungroup() %>% 
+  distinct(patientid, drugname_type, .keep_all = TRUE)
+```
+
+```{r RDI calculation continuation}
+Frontline <- Frontline %>% 
+  # general
   mutate(RDI_grp = case_when(
@@
     mean_RDI_per_drug >= 0.85 &
-      mean_RDI_per_drug < 1.15             ~ "Adequate dosing",
-    mean_RDI_per_drug >= 1.15              ~ "Overdosing"
+      mean_RDI_per_drug < 1.1              ~ "Adequate dosing",
+    mean_RDI_per_drug >= 1.1               ~ "Overdosing"
   )) %>% 
   mutate(RDI_grp1 = factor(RDI_grp1, 
+                          levels = c("Adequate dosing",
+                                     "Underdosed", 
+                                     "Highly underdosed",
+                                     "Overdosing"))) %>% 
+  # separated
+  mutate(RDI_carbo = case_when(
+    drugname == "carboplatin"               ~ mean_RDI_per_drug,
+    TRUE                                    ~ NA_real_
+  )) %>% 
+  mutate(RDI_pacli = case_when(
+    drugname == "paclitaxel"               ~ mean_RDI_per_drug,
+    TRUE                                    ~ NA_real_
+  )) %>% 
+  mutate(RDI_carbo_grp = case_when(
+    RDI_carbo >= 0.85              ~ "Adequate dosing",
+    RDI_carbo < 0.85               ~ "Underdosed"
+  )) %>% 
+  mutate(RDI_carbo_grp = factor(RDI_carbo_grp, 
+                           levels = c("Adequate dosing", "Underdosed"))) %>% 
+  mutate(RDI_carbo_grp1 = case_when(
+    RDI_carbo < 0.75               ~ "Highly underdosed",
+    RDI_carbo >= 0.75 &
+      RDI_carbo < 0.85             ~ "Underdosed",
+    RDI_carbo >= 0.85 &
+      RDI_carbo < 1.1              ~ "Adequate dosing",
+    RDI_carbo >= 1.1               ~ "Overdosing"
+  )) %>% 
+  mutate(RDI_carbo_grp1 = factor(RDI_carbo_grp1, 
+                          levels = c("Adequate dosing",
+                                     "Underdosed", 
+                                     "Highly underdosed",
+                                     "Overdosing"))) %>% 
+  mutate(RDI_pacli_grp = case_when(
+    RDI_pacli >= 0.85              ~ "Adequate dosing",
+    RDI_pacli < 0.85               ~ "Underdosed"
+  )) %>% 
+  mutate(RDI_pacli_grp = factor(RDI_pacli_grp, 
+                           levels = c("Adequate dosing", "Underdosed"))) %>% 
+  mutate(RDI_pacli_grp1 = case_when(
+    RDI_pacli < 0.75               ~ "Highly underdosed",
+    RDI_pacli >= 0.75 &
+      RDI_pacli < 0.85             ~ "Underdosed",
+    RDI_pacli >= 0.85 &
+      RDI_pacli < 1.1              ~ "Adequate dosing",
+    RDI_pacli >= 1.1               ~ "Overdosing"
+  )) %>% 
+  mutate(RDI_pacli_grp1 = factor(RDI_pacli_grp1, 
                           levels = c("Adequate dosing",
@@
 
-tbl_stack(list(tbl1, tbl2),
+####
+tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & 
+                               therapy == "Upfront Surgery" &
+                               dose_dense == 3) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels()
+
+tbl4 <- Frontline %>% filter(drugname == "paclitaxel" & 
+                               therapy == "Upfront Chemo" &
+                               dose_dense == 3) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("mean_RDI_per_drug", RDI_grp)) %>%
+  tbl_summary(
+              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+  bold_labels()
+
+tbl5 <- tbl_merge(list(tbl1, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))
+tbl6 <- tbl_merge(list(tbl2, tbl4))
+
+tbl_stack(list(tbl5, tbl6),
           group_header = c(
@@
 <br>
+
+<span style="color:green">**Taxanes dose dense**</span>
 
@@
 
+## Adjusted by other drug
+### RDI group
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_grp + RDI_pacli_grp + raceeth + ageatdx + stagecat` 
+```{r Table 5 HR adjusted rdi group adjusted by other drug}
+Frontline_adjusted <- Frontline %>% 
+  group_by(patientid) %>% 
+  fill(RDI_carbo, RDI_carbo_grp, RDI_carbo_grp1, RDI_pacli, RDI_pacli_grp, RDI_pacli_grp1, .direction = "downup") %>% 
+  distinct(patientid, .keep_all = TRUE)
+
+tbl2 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Surgery")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_grp + RDI_pacli_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Chemo")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_grp + RDI_pacli_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Surgery", "Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
+### Continous
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo + RDI_pacli + raceeth + ageatdx + stagecat` 
+```{r rdi continous adjusted by other drug}
+
+tbl2 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Surgery")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo + RDI_pacli + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Chemo")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo + RDI_pacli + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Surgery", "Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
 ***
@@
 ### Multivariable
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp1 + raceeth + ageatdx + stagecat` 
 ```{r}
@@
 
+## Adjusted by other drug
+### RDI group
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_grp1 + RDI_pacli_grp1 + raceeth + ageatdx + stagecat` 
+```{r Table 5 HR adjusted rdi group adjusted by other drug 2}
+tbl2 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Surgery")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_grp1 + RDI_pacli_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Chemo")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_grp1 + RDI_pacli_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Surgery", "Upfront Chemo")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
 ***

### 2021-12-01 Rmd/rdi analysis.Rmd
Reorganize steps of cleaning and filtering for step 1 and 2

@@
 ***
-At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.  
-- exclude the patients who had surgery but we don't have a date  
-- exclude patients whose histology is unknown  
-- exclude patients who didn't survive 1 month
-
-Now drug cleaning!
-
-# I. Drug episode questions
-
-**We start with a number of patient who have drug info of `r drugs %>% distinct(patientid) %>% nrow()`.**
-
-### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
+
+# I. Drug episode cleaning
+
 ```{r drugs episode cleanup}
-drugs1 <- drugs %>% 
+drugs <- drugs %>% 
   filter(episodedatasource == "Administrations" #& 
-           # ismaintenancetherapy == "FALSE"
+           # ismaintenancetherapy == "FALSE" # keep maintenance for a correct recoding of line number
          ) %>%
-  # 1. 60 days rule between diagnosis and treatment # Loss 1
   # bind with clinical
@@
           by = "patientid") %>% 
-  arrange(patientid, episodedate) %>% 
+  arrange(patientid, episodedate)
+```
+
+**We start with a number of `r drugs %>% distinct(patientid) %>% nrow()` patients who received treatment and for who their clinical info are available.**
+
+## 1. step 1: Flatiron recommendation cleanup
+
+This step is to remove patients from the population that don't follow flatiron recommendations.
+
+- 90 days rule between diagnosis and treatment  
+Flatiron propose a conceptual instruction on the 90-day-gap : 90 days between diagnosis and treatment.  
+It is meant to exclude patients who didn't get treatment for 90 days which would most likely mean that some treatment data are missing. Patients left after this step:
+
+- 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis  
+This is something that Flatiron strongly recommends, but does not require. Flatiron proposal reviewers will likely provide comments on this if not incorporated into a proposal.
+
+- Exclude exclude == "1" coded by Lauren
+
+Are excluded :  
+-	Borderline cases (not invasive ovarian cancer)  
+-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
+-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)
+
+```{r rule between diagnosis and treatment}
+drugs1 <- drugs %>% 
+  # 1. 60 days rule between diagnosis and treatment # Loss 1
   group_by(patientid) %>% 
@@
            duration(n=1, units = "months")) %>% 
-  ungroup()
-```
+  ungroup() %>% 
+  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
+           duration(n=1, units = "days")
+  )
+```
+
+```{r}
+drugs1 <- drugs1 %>% 
+  mutate(flatiron_rules = case_when(
+    days_at_first_drug > 90 | 
+      days_at_surg > 90                          ~ "exclude",
+    thirty_days_exclusion <= 30                  ~ "exclude",
+    exclude == "1"                               ~ "exclude"
+  )) %>%
+  group_by(patientid) %>% 
+  fill(flatiron_rules, .direction = "downup")
+
+drugs1 <- drugs1 %>% 
+  filter(is.na(flatiron_rules))
+```
+
+**At the end of the step 1, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
+
+<br>
+
+## 2. step 2: Filter patients with cinical characteristics fitting to the study
+
+- exclude patients whose histology is unknown  
+- remove chemotherapy only patients
+```{r}
+drugs1 <- drugs1 %>% 
+  filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs
+```
+
+```{r}
+drugs1 <- drugs1 %>%
+  filter(!is.na(surgerydate))
+```
+
+**At the end of the step 2, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
+
+<br>
+
+## 3. step 3: Filter out patients with missing data
+
+- exclude the patients who had surgery but we don't have a date of surgery
+
+```{r}
+drugs1 <- drugs1 %>% 
+  filter(!(issurgery == "Yes" & is.na(surgerydate))) 
+```
+
+### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
 We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis.
 Patients left :
-
 ```{r}
@@
          )
-drugs1 %>% distinct(patientid) %>% nrow()
-```
-
-### step 2: Flatiron recommendation cleanup
-#### 90 days rule between diagnosis and treatment
-
-Flatiron propose a conceptual instruction on the 90-day-gap : 90 days between diagnosis and treatment.  
-It is meant to exclude patients who didn't get treatment for 90 days which would most likely mean that some treatment data are missing. Patients left after this step:
-```{r}
-remove_90daysrule <- drugs1 %>% 
-  filter((days_at_first_drug > 90 | days_at_surg > 90)) %>% 
-  distinct(patientid)
-remove_90daysrule <- paste(remove_90daysrule$patientid, collapse = "|")
-
-drugs1 <- drugs1 %>% 
-  # remove these patients who 90 days rule
-  filter(!str_detect(patientid, remove_90daysrule))
-
-drugs1 %>% distinct(patientid) %>% nrow()
-```
-
-#### 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis
-
-This is something that Flatiron strongly recommends, but does not require. Flatiron proposal reviewers will likely provide comments on this if not incorporated into a proposal. 
-```{r}
-# drugs1 %>% 
-#   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
-#            duration(n=1, units = "days"), 
-#          thirty_days_exclusion = case_when(
-#            thirty_days_exclusion <= 30                  ~ "Exclude"
-#          )) %>% 
-#   filter(thirty_days_exclusion == "Exclude") %>% 
-#   distinct(patientid) %>% 
-#   nrow
-
-drugs1 <- drugs1 %>% 
-  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
-           duration(n=1, units = "days"), 
-         thirty_days_exclusion = case_when(
-           thirty_days_exclusion <= 30                  ~ "Exclude",
-           thirty_days_exclusion > 30                   ~ "Include",
-           is.na(dateofdeath)                           ~ "Include"
-         )) %>% 
-  filter(thirty_days_exclusion != "Exclude")
-
-# drugs1 %>% distinct(patientid) %>% nrow()
-
-```
-In the data, `r drugs1 %>% mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/duration(n=1, units = "days"), thirty_days_exclusion = case_when(thirty_days_exclusion <= 30~ "Exclude")) %>% filter(thirty_days_exclusion == "Exclude") %>% distinct(patientid) %>% nrow` are excluded so we still have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.
-
-#### Exclude exclude == "1" coded by Lauren
-
-Are excluded :  
--	Borderline cases (not invasive ovarian cancer)  
--	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
--	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)
-Patients left after this step:
-
-```{r}
-drugs1 <- drugs1 %>% 
-  filter(exclude != "1")
-
-drugs1 %>% distinct(patientid) %>% nrow()
-```
-
-<!-- ### step .: Remove linename that doesn't include platin or taxanes in first line -> later in the process, need first to recode linenumber with all the drugs in. -->
-```{r}
-# drugs1 <- drugs1 %>% 
-#   # 2. Filtering----
-#   filter(episodedatasource == "Administrations" & 
-#            # ismaintenancetherapy == "FALSE" & 
-#            !is.na(amount) &
-#            (days_at_first_drug < 60 | days_at_surg < 60) &
-#            
-#            days_at_first_drug >= 0 &
-#            (is.na(surgerydate) | days_at_surg >= 0)
-#          )
-
-# drugs1 %>% 
-#   filter(linenumber == 1) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(linename) %>% 
-#   tbl_summary(sort = list(everything() ~ "frequency"))
-```
-
-### step 3: Remove chemotherapy only patients
-```{r}
-drugs1 <- drugs1 %>%
-  filter(!is.na(surgerydate))
 drugs1 %>% distinct(patientid) %>% nrow()
@@
   tbl_summary(by = linename)
+# a <- therapy_line %>% 
+#   filter(linenumber_adj == 1)
 therapy_line %>% 
@@
   ggplot(aes(x= line_duration))+
-  geom_histogram(color = "slateblue", aes(fill = route), binwidth = 7) +
+  geom_histogram(aes(fill = route), binwidth = 7) +
   theme_minimal(base_size = 14)+
@@
 Several patients have a short line.  
-`r emo::ji("question_mark")` **Should me remove the patient with a line during less than a cycle** We said during October meeting to check at IP
+`r emo::ji("question_mark")` **Should we remove the patient with a line lasting less than a cycle** We said during October meeting to check if were IP administration....
 
@@
 
-### step 9: Remove too much cycle
+### step 9: Remove Patients with too many cycles
 ```{r more than 9 cycle patients}
@@
     theme_ridges()+
-  theme(text = element_text(size = 14),#axis.text.y = element_blank(),
+  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
         panel.spacing = unit(0.1, "lines"),
-        strip.text.x = element_text(size = 8)
+        strip.text.x = element_text(size = 14)
     ) +
@@
                    ),
-           title = "OS from first treatment pacliatxel \nUpfront Chemo",
+           title = "OS from first treatment paclitaxel \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 # Underdosed: >= 0.75 to <0.85
-# Adequate dosing: >= 0.85 to <1.15
-# Overdosing: >=1.15
+# Adequate dosing: >= 0.85 to <1.10
+# Overdosing: >=1.10
 ```

### 2021-12-01 R/2.data cleaning.R

@@ -543,8 +543,8 @@ write_rds(areaUC, "areaUC.rds")
 #################################################################################################### II ### Clinical Cleaning----
 clinical_data <- clinical_data %>% 
   # Limit to the patients to the ones we have date of surgery when had surgery
-  filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%  # loss 17
-  filter(!(histology == "Unknown/not documented")) %>% # loss 287
+  # filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%  # loss 17 ################## Will do when bind to drugs
+  # filter(!(histology == "Unknown/not documented")) %>% # loss 287 ################## Will do when bind to drugs
   # Recode
   mutate(raceeth = factor(raceeth, levels = c("NHWhite", "NHBlack", "Hispanic", "Other"))) %>% 
   mutate(race = case_when(

### 2021-12-01 Rmd/rdi analysis.Rmd
reorganize code clean up, complete step 2 and start step 3

@@
 
+- Select episodedatasource == "Administrations"
 ```{r drugs episode cleanup}
@@
 
-**We start with a number of `r drugs %>% distinct(patientid) %>% nrow()` patients who received treatment and for who their clinical info are available.**
-
-## 1. step 1: Flatiron recommendation cleanup
-
-This step is to remove patients from the population that don't follow flatiron recommendations.
-
-- 90 days rule between diagnosis and treatment  
-Flatiron propose a conceptual instruction on the 90-day-gap : 90 days between diagnosis and treatment.  
-It is meant to exclude patients who didn't get treatment for 90 days which would most likely mean that some treatment data are missing. Patients left after this step:
-
-- 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis  
-This is something that Flatiron strongly recommends, but does not require. Flatiron proposal reviewers will likely provide comments on this if not incorporated into a proposal.
-
-- Exclude exclude == "1" coded by Lauren
-
-Are excluded :  
--	Borderline cases (not invasive ovarian cancer)  
--	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
--	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)
-
-```{r rule between diagnosis and treatment}
+- Combine multiple administrations of the same drug at the same date
+Flatiron says:
+There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day.
+We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day.
+Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data.
+Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
+For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.  
+Three administrations of the same drug were listed on a Friday.
+The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.
+Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
+```{r combine amount same drug one day}
 drugs1 <- drugs %>% 
-  # 1. 60 days rule between diagnosis and treatment # Loss 1
-  group_by(patientid) %>% 
-  mutate(first_drug_date = first(episodedate)) %>% 
-  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
-           duration(n=1, units = "months")) %>% 
-  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
-           duration(n=1, units = "months")) %>% 
-  ungroup() %>% 
-  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
-           duration(n=1, units = "days")
-  )
-```
-
-```{r}
-drugs1 <- drugs1 %>% 
-  mutate(flatiron_rules = case_when(
-    days_at_first_drug > 90 | 
-      days_at_surg > 90                          ~ "exclude",
-    thirty_days_exclusion <= 30                  ~ "exclude",
-    exclude == "1"                               ~ "exclude"
-  )) %>%
-  group_by(patientid) %>% 
-  fill(flatiron_rules, .direction = "downup")
-
-drugs1 <- drugs1 %>% 
-  filter(is.na(flatiron_rules))
-```
-
-**At the end of the step 1, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
-
-<br>
-
-## 2. step 2: Filter patients with cinical characteristics fitting to the study
-
-- exclude patients whose histology is unknown  
-- remove chemotherapy only patients
-```{r}
-drugs1 <- drugs1 %>% 
-  filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs
-```
-
-```{r}
-drugs1 <- drugs1 %>%
-  filter(!is.na(surgerydate))
-```
-
-**At the end of the step 2, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
-
-<br>
-
-## 3. step 3: Filter out patients with missing data
-
-- exclude the patients who had surgery but we don't have a date of surgery
-
-```{r}
-drugs1 <- drugs1 %>% 
-  filter(!(issurgery == "Yes" & is.na(surgerydate))) 
-```
-
-### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
-We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis.
-Patients left :
-```{r}
-drugs1 <- drugs1 %>% 
-  filter(days_at_first_drug >= 0 &
-           (is.na(surgerydate) | days_at_surg >= 0)
-         )
-drugs1 %>% distinct(patientid) %>% nrow()
-```
-
-#### Combine multiple administrations of the same drug at the same date
-```{r combine amount same drug one day}
-drugs1 <- drugs1 %>% 
-  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
-  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
-  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
-  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory)) %>%
-
   # 3. Combined Multiple Administrations----
@@
   group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, 
-           drugname, units, surgerydate, days_at_first_drug, days_at_surg, 
-           diagnosisdate, ismaintenancetherapy) %>%
+           drugname, units, ismaintenancetherapy) %>%
   summarise_at(vars(route, amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
@@
   mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
-  # mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
-  #        amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
   mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
@@
   # ug need conversion
-  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
+  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 so remove
   mutate(amount =  case_when(
@@
 
-#### Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
+- Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
 ```{r line coding}
 therapy_line <- drugs1 %>% 
+  # bind again with clinical - easier that way
+  inner_join(., clinical_data, 
+          by = "patientid") %>% 
+  arrange(patientid, episodedate) %>% 
   # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
@@
   fill(therapy, .direction = "downup") %>%
-  # mutate(therapy1 = case_when(
-  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
-  # )) %>% 
-  # fill(therapy1, .direction = "downup") %>% 
-  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
-  # select( -therapy1) %>%
 
@@
   group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
-  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
+  mutate(#drugname_count_perline = n(),
+         drugname_count_perline = case_when(
+           str_detect(drugname, "platin|taxel")     ~ n()
+         )
+           ) %>%  # F0000AD999ABF
   ungroup() %>% 
@@
   mutate(lineenddate_new = max(episodedate)) %>% 
+  ungroup()
+```
+
+- Code cycle number
+```{r cycle coding}
+# Code cycle number
+therapy_cycle <- therapy_line %>% 
+  # filter(str_detect(drugname, "taxel|platin")) %>% # Need to that now for patient who got Bev only once per line F02D8628A5394
+
+  arrange(patientid, episodedate) %>% 
+  group_by(patientid, linenumber_new) %>%
+  # Need the number of time of the "major" drug is seen in the line
+  mutate(cycle_count_perline = min(drugname_count_perline, na.rm = TRUE)) %>%
+  mutate(cycle_major_drugname = case_when(
+    cycle_count_perline == drugname_count_perline          ~ cycle_drugname,
+    TRUE                                                   ~ NA_character_
+  )) %>% 
+  # select(-drugname_count_perline) %>% 
+  group_by(patientid, linenumber_new, cycle_major_drugname) %>%
+  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
+  # F01D908A013B7 has more pacli at the end but in the same line
+
+  # + What to do when it is a cycle change F003F2BEEDB37 ,
+
+  # group_by(patientid, linenumber_new, cycle_inc) %>%
+  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
+  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
+  arrange(patientid, episodedate, cycle_increment) %>% 
+  group_by(patientid, linenumber_new) %>%
+  # mutate(cycle_increment = cycle_inc) %>% 
+  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
+  group_by(patientid, chemotherapy_type, cycle_increment) %>% 
+  mutate(is_dose_dense = row_number(cycle_increment),
+         is_dose_dense = ifelse(is_dose_dense == 1, 1, NA_real_)) %>% 
+  group_by(patientid) %>% 
+  mutate(total_cycle_increment = row_number(is_dose_dense)) %>% 
+  fill(total_cycle_increment, .direction = "downup") %>% 
+  # cycle date
+  group_by(patientid, linenumber_new, cycle_increment) %>% 
+  mutate(cycle_start_date = min(episodedate)) %>%
+
+  # Look at dose dense
+  group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
+  mutate(dose_dense = n()) %>% 
+  mutate(dose_dense = max(dose_dense)) %>%  # too much cycle
+  ungroup()
+
+  # # CODE FOR SKIPPED CYCLE
+  # group_by(patientid, linenumber_new) %>% 
+  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
+  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
+  # 
+  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
+  # mutate(n = row_number(drugname)) %>%
+  # 
+  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
+  # fill(base_days_between_cycle, .direction = "downup") %>% 
+  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
+  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
+  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
+  # group_by(patientid, linenumber_new) %>%
+  # mutate(drug_count_perline = n()) %>%
+  # mutate(skipped_cycle_indays1 = ifelse(
+  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
+  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
+  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
+  # group_by(patientid) %>% 
+  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
+  # ungroup()
+therapy_cycle %>% distinct(patientid) %>% nrow()
+
+# rm(drugs, drugs1, therapy_line)
+```
+
+- Bind everything together to calculate target auc/target dose and expected dose
+
+(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and paclitaxel, they are just present in the same column called `target_auc` for a tidy data organisation - You can find the calculations formula at the end of the document)
+When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, and paclitaxel and their `expected_dose`.
+It can be days in between but it can also be more.
+
+`r emo::ji("check")`  
+We decided to take the creatinine, weight, bsa measured within a month of the cycle start date AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line
+
+```{r target_auc and expected dose}
+Treatment <- 
+  # Merge with creatinine
+  left_join(therapy_cycle, creatinine, by = "patientid") %>%
+  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
+                          duration(n=1, unit="days"))) %>% 
+  mutate(interval_creat = case_when(
+    (therapy == "Upfront Surgery" &
+       interval_creat < 31 &
+       # creat_date < lineenddate &
+       creat_date > surgerydate)                  ~ interval_creat,
+
+    therapy == "Upfront Chemo" &
+      (
+        (chemotherapy_type == "Neoadjuvant" &
+           interval_creat < 31 &
+           creat_date < surgerydate) |
+          (chemotherapy_type == "Adjuvant" &
+             interval_creat < 31 &
+             # creat_date < lineenddate &
+             creat_date > surgerydate)
+      )                                          ~ interval_creat,
+    TRUE                                         ~ NA_real_
+  )) %>%
+  arrange(interval_creat) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Merge with height
+  left_join(. , height,  by = "patientid") %>%
+  mutate(interval_height = abs(interval(start= height_date, end= cycle_start_date)/
+           duration(n=1, unit="days"))) %>%
+  arrange(interval_height) %>%
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Merge with weight
+  left_join(. , weight, by = "patientid") %>%
+  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
+                        duration(n=1, unit="days"))) %>%
+  mutate(interval_weight = case_when(
+    (therapy == "Upfront Surgery" &
+       interval_weight < 31 &
+       # weight_date < lineenddate &
+       weight_date > surgerydate)                  ~ interval_weight,
+
+    therapy == "Upfront Chemo" &
+      (
+        (chemotherapy_type == "Neoadjuvant" &
+           interval_weight < 31 &
+           weight_date < surgerydate) |
+          (chemotherapy_type == "Adjuvant" &
+             interval_weight < 31 &
+             # weight_date < lineenddate &
+             weight_date > surgerydate)
+      )                                          ~ interval_weight,
+    TRUE                                         ~ NA_real_
+  )) %>%
+  arrange(interval_weight) %>%
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
+         cycle_start_date, .keep_all = TRUE) %>%
+
+  # Calculate ideal dody weight
+  mutate(ideal_weight = case_when(
+    height <= 1.524               ~ 45.5 + 2.3,
+    height > 1.524                ~ 45.5 + (2.3 * (((height - 1.524) / 0.0254)))
+  )) %>% 
+  mutate(adjusted_weight = ((weight - ideal_weight) * 0.40) + ideal_weight
+  ) %>% 
+  # Calculate bmi
+  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
+  mutate(bmi_cat = case_when(
+    bmi_at_dx < 25                    ~ "Underweight and normal weight",
+    bmi_at_dx >= 25 &
+      bmi_at_dx < 30                  ~ "Overweight",
+    bmi_at_dx >= 30                   ~ "Obese"
+  )) %>%
+  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
+
+  mutate(actual_bmi = weight / (height * height)) %>%
+  mutate(actual_bmi_cat = case_when(
+    actual_bmi < 25                    ~ "Underweight and normal weight",
+    actual_bmi >= 25 &
+      actual_bmi < 30                  ~ "Overweight",
+    actual_bmi >= 30                   ~ "Obese"
+  )) %>%
+  mutate(actual_bmi_cat = factor(actual_bmi_cat, 
+                                  levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
+  # select(patientid, weight, height, bmi_at_dx, ideal_weight, adjusted_weight, adjusted_bmi)
+  # Calculate CrCl
+  # inner_join(., clinical_data %>% select(-surgerydate),
+  #            by = "patientid") %>% 
+  mutate(CrCl = (
+       (
+    ((140 - ageatdx) * weight) /
+    (72 * creatinine)
+       ) *
+    0.85)
+  ) %>% 
+  mutate(CrCl = case_when(
+    CrCl > 125                        ~ 125,
+    TRUE                              ~ CrCl
+  )) %>% 
+  mutate(adjusted_CrCl = case_when(
+    actual_bmi >= 25                  ~ CrCl,
+    actual_bmi < 25                   ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
+  )) %>% 
+  mutate(adjusted_CrCl = case_when(
+    adjusted_CrCl > 125               ~ 125,
+    TRUE                              ~ adjusted_CrCl
+  )) %>%
+
+  # Merge with body_surface_area
+  left_join(., body_surface_area, by = "patientid") %>%
+  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
+                          duration(n=1, unit="days"))) %>%
+  mutate(interval_bsa = case_when(
+    (therapy == "Upfront Surgery" &
+       interval_bsa < 31 &
+       # bsa_date < lineenddate &
+       bsa_date > surgerydate)                  ~ interval_bsa,
+
+    therapy == "Upfront Chemo" &
+      (
+        (chemotherapy_type == "Neoadjuvant" &
+           interval_bsa < 31 &
+           bsa_date < surgerydate) |
+          (chemotherapy_type == "Adjuvant" &
+             interval_bsa < 31 &
+             # bsa_date < lineenddate &
+             bsa_date > surgerydate)
+      )                                          ~ interval_bsa,
+    TRUE                                         ~ NA_real_
+  )) %>%
+  arrange(interval_bsa) %>%
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
+           cycle_start_date, .keep_all = TRUE) %>%
+  # Calculate more bsa value with height and weight using Du Bois formula
+  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
+  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
+  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
+  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
+  select(-bsa_du_bois) %>%
+
+  # Merge with auc
+  left_join(., areaUC, by = c("patientid", "drugname")) %>%
+  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
+                          duration(n=1, unit="days"))) %>% 
+  mutate(interval_auc = case_when(
+    (therapy == "Upfront Surgery" &
+       interval_auc < 31 &
+       # auc_date < lineenddate &
+       auc_date > surgerydate)                  ~ interval_auc,
+
+    therapy == "Upfront Chemo" &
+      (
+        (chemotherapy_type == "Neoadjuvant" &
+           interval_auc < 31 &
+           auc_date < surgerydate) |
+          (chemotherapy_type == "Adjuvant" &
+             interval_auc < 31 &
+             # auc_date < lineenddate &
+             auc_date > surgerydate)
+      )                                          ~ interval_auc,
+    TRUE                                         ~ NA_real_
+  )) %>%
+  arrange(interval_auc) %>% 
+  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+           cycle_start_date, .keep_all = TRUE) %>%
+
+  # Calculate expected dose
+  mutate(expected_dose = case_when(
+    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
+    drugname == "paclitaxel"                  ~ BSA * target_auc 
+    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
+  )) %>% 
+  mutate(expected_dose = case_when(
+    expected_dose > 900 &
+      target_auc == 6              ~ 900,
+    expected_dose > 750 &
+      target_auc == 5              ~ 750,
+    TRUE                           ~ expected_dose
+  )) %>% 
+  mutate(adjusted_expected_dose = case_when(
+    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
+    drugname == "paclitaxel"                  ~ BSA * target_auc 
+    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
+  )) %>% 
+  mutate(adjusted_expected_dose = case_when(
+    adjusted_expected_dose > 900 &
+      target_auc == 6              ~ 900,
+    adjusted_expected_dose > 750 &
+      target_auc == 5              ~ 750,
+    TRUE                           ~ adjusted_expected_dose
+  )) %>% 
+  group_by(patientid) %>%
+  mutate(first_treatment_date = case_when(
+    str_detect(therapy, "Chemo")                      ~ min(episodedate),
+    str_detect(therapy, "Surgery")                    ~ surgerydate,
+  )) %>% 
   ungroup() %>% 
+  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
+                   duration(n=1, units = "months")) %>% 
+  arrange(patientid, episodedate)
+```
+
+```{r plot interval}
+Treatment %>% 
+  ggplot(aes(x= interval_creat)) +
+  geom_bar() #+
+  # coord_cartesian(ylim=c(0,50))
+# Treatment %>% 
+#   ggplot(aes(x= interval_height)) +
+#   geom_bar() +
+#   coord_cartesian(ylim=c(0,50))
+Treatment %>% 
+  ggplot(aes(x= interval_weight)) +
+  geom_bar() #+
+  # coord_cartesian(ylim=c(0,50))
+Treatment %>% 
+  ggplot(aes(x= interval_bsa)) +
+  geom_bar() #+
+  # coord_cartesian(ylim=c(0,50))
+Treatment %>% 
+  ggplot(aes(x= interval_auc)) +
+  geom_bar() #+
+  # coord_cartesian(ylim=c(0,50))
+```
+
+# Variable for filtering
+
+```{r rule between diagnosis and treatment}
+Treatment <- Treatment %>% 
+  # 1. 60 days rule between diagnosis and treatment # Loss 1
+  group_by(patientid) %>% 
+  mutate(first_drug_date = first(episodedate)) %>% 
+  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
+           duration(n=1, units = "days")) %>% 
+  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
+           duration(n=1, units = "days")) %>% 
+  ungroup() %>% 
+  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
+           duration(n=1, units = "days")
+  ) %>% 
+  group_by(patientid) %>% 
+  mutate(had_carbo_pacli = case_when(
+    drugname == "paclitaxel" |
+      drugname == "carboplatin"             ~ "Yes"
+  )) %>% 
+  fill(had_carbo_pacli, .direction = "updown") %>% 
+  ungroup() %>% 
+  mutate(interval_surgery_to_adj_start = case_when(
+      chemotherapy_type == "Adjuvant" &
+        linenumber_adj == 1       
+      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
+    ),
+  )
+```
+
+```{r RDI calculation}
+Frontline <- Treatment %>% 
+  # filter(chemotherapy_type == "Neoadjuvant" |
+  #          (chemotherapy_type == "Adjuvant" &
+  #             linenumber_adj == 1)) %>%
+
+  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
+  ) %>%
+  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
+  #        relative_dose_intensity, linenumber_adj) %>%
+
+  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
+  group_by(patientid, chemotherapy_type, drugname) %>%
+  # mutate(mean_RDI_per_drug = case_when(
+  #   chemotherapy_type == "Adjuvant" &
+  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
+  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  # )) %>% 
+  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  ) %>% 
+  ungroup() %>% 
+  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
+```
+
+```{r RDI calculation group}
+Frontline <- Frontline %>% 
+  # general
+  mutate(RDI_grp = case_when(
+    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
+    mean_RDI_per_drug < 0.85               ~ "Underdosed"
+  )) %>% 
+  mutate(RDI_grp = factor(RDI_grp, 
+                           levels = c("Adequate dosing", "Underdosed"))) %>% 
+  mutate(RDI_grp1 = case_when(
+    mean_RDI_per_drug < 0.75               ~ "Highly underdosed",
+    mean_RDI_per_drug >= 0.75 &
+      mean_RDI_per_drug < 0.85             ~ "Underdosed",
+    mean_RDI_per_drug >= 0.85 &
+      mean_RDI_per_drug < 1.1              ~ "Adequate dosing",
+    mean_RDI_per_drug >= 1.1               ~ "Overdosing"
+  )) %>% 
+  mutate(RDI_grp1 = factor(RDI_grp1, 
+                          levels = c("Adequate dosing",
+                                     "Underdosed", 
+                                     "Highly underdosed",
+                                     "Overdosing"))) %>% 
+  # separated
+  mutate(RDI_carbo_neo = case_when(
+    drugname == "carboplatin" &
+      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
+    TRUE                                    ~ NA_real_
+  )) %>% 
+  mutate(RDI_pacli_neo = case_when(
+    drugname == "paclitaxel" &
+      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
+    TRUE                                    ~ NA_real_
+  )) %>% 
+  mutate(RDI_carbo_adj = case_when(
+    drugname == "carboplatin" &
+      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
+    TRUE                                    ~ NA_real_
+  )) %>% 
+  mutate(RDI_pacli_adj = case_when(
+    drugname == "paclitaxel" &
+      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
+    TRUE                                    ~ NA_real_
+  )) %>%
+
+  mutate(RDI_carbo_neo_grp = case_when(
+    RDI_carbo_neo >= 0.85              ~ "Adequate dosing",
+    RDI_carbo_neo < 0.85               ~ "Underdosed"
+  )) %>% 
+  mutate(RDI_carbo_neo_grp = factor(RDI_carbo_neo_grp, 
+                           levels = c("Adequate dosing", "Underdosed"))) %>% 
+  mutate(RDI_carbo_neo_grp1 = case_when(
+    RDI_carbo_neo < 0.75               ~ "Highly underdosed",
+    RDI_carbo_neo >= 0.75 &
+      RDI_carbo_neo < 0.85             ~ "Underdosed",
+    RDI_carbo_neo >= 0.85 &
+      RDI_carbo_neo < 1.1              ~ "Adequate dosing",
+    RDI_carbo_neo >= 1.1               ~ "Overdosing"
+  )) %>% 
+  mutate(RDI_carbo_neo_grp1 = factor(RDI_carbo_neo_grp1, 
+                          levels = c("Adequate dosing",
+                                     "Underdosed", 
+                                     "Highly underdosed",
+                                     "Overdosing"))) %>% 
+  mutate(RDI_pacli_neo_grp = case_when(
+    RDI_pacli_neo >= 0.85              ~ "Adequate dosing",
+    RDI_pacli_neo < 0.85               ~ "Underdosed"
+  )) %>% 
+  mutate(RDI_pacli_neo_grp = factor(RDI_pacli_neo_grp, 
+                           levels = c("Adequate dosing", "Underdosed"))) %>% 
+  mutate(RDI_pacli_neo_grp1 = case_when(
+    RDI_pacli_neo < 0.75               ~ "Highly underdosed",
+    RDI_pacli_neo >= 0.75 &
+      RDI_pacli_neo < 0.85             ~ "Underdosed",
+    RDI_pacli_neo >= 0.85 &
+      RDI_pacli_neo < 1.1              ~ "Adequate dosing",
+    RDI_pacli_neo >= 1.1               ~ "Overdosing"
+  )) %>% 
+  mutate(RDI_pacli_neo_grp1 = factor(RDI_pacli_neo_grp1, 
+                          levels = c("Adequate dosing",
+                                     "Underdosed", 
+                                     "Highly underdosed",
+                                     "Overdosing"))) %>%
+
+  mutate(RDI_carbo_adj_grp = case_when(
+    RDI_carbo_adj >= 0.85              ~ "Adequate dosing",
+    RDI_carbo_adj < 0.85               ~ "Underdosed"
+  )) %>% 
+  mutate(RDI_carbo_adj_grp = factor(RDI_carbo_adj_grp, 
+                           levels = c("Adequate dosing", "Underdosed"))) %>% 
+  mutate(RDI_carbo_adj_grp1 = case_when(
+    RDI_carbo_adj < 0.75               ~ "Highly underdosed",
+    RDI_carbo_adj >= 0.75 &
+      RDI_carbo_adj < 0.85             ~ "Underdosed",
+    RDI_carbo_adj >= 0.85 &
+      RDI_carbo_adj < 1.1              ~ "Adequate dosing",
+    RDI_carbo_adj >= 1.1               ~ "Overdosing"
+  )) %>% 
+  mutate(RDI_carbo_adj_grp1 = factor(RDI_carbo_adj_grp1, 
+                          levels = c("Adequate dosing",
+                                     "Underdosed", 
+                                     "Highly underdosed",
+                                     "Overdosing"))) %>% 
+  mutate(RDI_pacli_adj_grp = case_when(
+    RDI_pacli_adj >= 0.85              ~ "Adequate dosing",
+    RDI_pacli_adj < 0.85               ~ "Underdosed"
+  )) %>% 
+  mutate(RDI_pacli_adj_grp = factor(RDI_pacli_adj_grp, 
+                           levels = c("Adequate dosing", "Underdosed"))) %>% 
+  mutate(RDI_pacli_adj_grp1 = case_when(
+    RDI_pacli_adj < 0.75               ~ "Highly underdosed",
+    RDI_pacli_adj >= 0.75 &
+      RDI_pacli_adj < 0.85             ~ "Underdosed",
+    RDI_pacli_adj >= 0.85 &
+      RDI_pacli_adj < 1.1              ~ "Adequate dosing",
+    RDI_pacli_adj >= 1.1               ~ "Overdosing"
+  )) %>% 
+  mutate(RDI_pacli_adj_grp1 = factor(RDI_pacli_adj_grp1, 
+                          levels = c("Adequate dosing",
+                                     "Underdosed", 
+                                     "Highly underdosed",
+                                     "Overdosing")))
+```
+
+```{r Frontline_adjusted}
+Frontline_adjusted <- Frontline %>% 
+  group_by(patientid) %>% 
+  fill(RDI_carbo_neo, RDI_carbo_neo_grp, RDI_carbo_neo_grp1, 
+       RDI_pacli_neo, RDI_pacli_neo_grp, RDI_pacli_neo_grp1, 
+       RDI_carbo_adj, RDI_carbo_adj_grp, RDI_carbo_adj_grp1, 
+       RDI_pacli_adj, RDI_pacli_adj_grp, RDI_pacli_adj_grp1, 
+       .direction = "downup") %>% 
+  distinct(patientid, .keep_all = TRUE)
+```
+
+```{r}
+rm(areaUC, body_surface_area, creatinine, clinical_data, drugs, drugs1, 
+   height#, therapy_cycle, therapy_line, Treatment, weight
+   )
+```
+
+<br>
+<br>
+
+# **Number of patients : `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**
+
+######################################################################################################################
+######################################################################################################################
+######################################################################################################################
+######################################################################################################################
+
+<!-- # Variable for filtering -->
+
+<!-- ```{r rule between diagnosis and treatment} -->
+<!-- drugs1 <- Frontline_adjusted %>%  -->
+<!--   # 1. 60 days rule between diagnosis and treatment # Loss 1 -->
+<!--   group_by(patientid) %>%  -->
+<!--   mutate(first_drug_date = first(episodedate)) %>%  -->
+<!--   mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/ -->
+<!--            duration(n=1, units = "days")) %>%  -->
+<!--   mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/ -->
+<!--            duration(n=1, units = "days")) %>%  -->
+<!--   ungroup() %>%  -->
+<!--   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/ -->
+<!--            duration(n=1, units = "days") -->
+<!--   ) -->
+<!-- ``` -->
+
+**We start with a number of `r drugs %>% distinct(patientid) %>% nrow()` patients who received treatment and for who their clinical info are available.**
+
+<br>
+
+## 1. step 1: Flatiron recommendation cleanup
+
+This step is to remove patients from the population that don't follow flatiron recommendations.
+
+- 90 days rule between diagnosis and treatment  
+Flatiron propose a conceptual instruction on the 90-day-gap : 90 days between diagnosis and treatment.  
+It is meant to exclude patients who didn't get treatment for 90 days which would most likely mean that some treatment data are missing. Patients left after this step:
+
+- 30 days rule excluding patient who didn't survive for at least 30 days after diagnosis  
+This is something that Flatiron strongly recommends, but does not require. Flatiron proposal reviewers will likely provide comments on this if not incorporated into a proposal.
+
+- Exclude exclude == "1" coded by Lauren
+
+Are excluded :  
+-	Borderline cases (not invasive ovarian cancer)  
+-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
+-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)
+```{r}
+drugs1 <- Frontline_adjusted %>% 
+  mutate(flatiron_rules = case_when(
+    days_at_first_drug > 90 | 
+      days_at_surg > 90                          ~ "exclude",
+    thirty_days_exclusion <= 30                  ~ "exclude",
+    exclude == "1"                               ~ "exclude"
+  )) %>%
+  group_by(patientid) %>% 
+  fill(flatiron_rules, .direction = "downup")
+
+drugs1 <- drugs1 %>% 
+  filter(is.na(flatiron_rules))
+```
+
+**At the end of the step 1, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
+
+<br>
+
+## 2. step 2: Filter patients with cinical characteristics fitting to the study criteria
+
+- exclude patients whose histology is unknown  
+- remove chemotherapy only patients
+- include only patients who received platin and/or taxane
+```{r}
+drugs1 <- drugs1 %>% 
+  filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs
+```
+
+```{r}
+drugs1 <- drugs1 %>%
+  filter(!is.na(surgerydate))
+```
+
+```{r}
+drugs1 <- drugs1 %>%
+  filter(had_carbo_pacli == "Yes")
+```
+
+**At the end of the step 2, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
+
+<br>
+
+## 3. step 3: Filter out patients with missing data
+
+- exclude the patients who had surgery but we don't have a date of surgery -> NONE anymore
+
+```{r}
+drugs11 <- drugs1 %>% 
+  filter(!(issurgery == "Yes" & is.na(surgerydate))) 
+```
+
+- remove patients with long gap between surgery and adjuvant start -> NONE anymore  
+Did a 3 months gap
+```{r}
+drugs11 <- drugs11 %>%
+  arrange(patientid, episodedate) %>%
+  mutate(ex = case_when(
+    interval_surgery_to_adj_start > 3                  ~ "exclude"
+  )) %>% 
+  filter(is.na(ex))
+
+drugs11 %>% distinct(patientid) %>% nrow()
+```
+
+RESTART HERE ----------------------------------------------------
+
+### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
+We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis.
+Patients left :
+```{r}
+drugs1 <- drugs1 %>% 
+  filter(days_at_first_drug >= 0 &
+           (is.na(surgerydate) | days_at_surg >= 0)
+         )
+drugs1 %>% distinct(patientid) %>% nrow()
+```
+
+```{r}
+therapy_line <- therapy_line %>% 
   filter(treatment_sequence == "neo + surg + adj" |
@@
 
-### step 6: remove patients with long gap between surgery and adjuvant start ????
-Depending on the answers:
-
 #### remove patients with more than 9 cycles total in upfront chemo or upfront surgery
-Did a gap of 3 months
-```{r}
-remove_delayed_drug <- therapy_line %>%
-  mutate(interval = case_when(
-      chemotherapy_type == "Adjuvant" &
-        linenumber_adj == 1       
-      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
-    ),
-  ) %>% 
-  arrange(patientid, episodedate) %>%
-  filter(interval > 3) %>%
-  distinct(patientid, .keep_all = TRUE)
-
-therapy_line <- therapy_line %>%
-  # Remove patients with more than 1 line as Neo
-  filter(!str_detect(patientid, paste(remove_delayed_drug$patientid, collapse = "|")))
-therapy_line %>% distinct(patientid) %>% nrow()
-```
 
@@
 
-#### Code cycle
-```{r cycle coding}
-# Code cycle number
-therapy_cycle <- therapy_line %>% 
-  filter(str_detect(drugname, "taxel|platin")) %>% # Need to that now for patient who got Bev only once per line F02D8628A5394
-
-  arrange(patientid, episodedate) %>% 
-  group_by(patientid, linenumber_new) %>%
-  # Need the number of time of the "major" drug is seen in the line
-  mutate(cycle_count_perline = min(drugname_count_perline)) %>%
-  mutate(cycle_major_drugname = case_when(
-    cycle_count_perline == drugname_count_perline          ~ cycle_drugname,
-    TRUE                                                   ~ NA_character_
-  )) %>% 
-  # select(-drugname_count_perline) %>% 
-  group_by(patientid, linenumber_new, cycle_major_drugname) %>%
-  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
-  # F01D908A013B7 has more pacli at the end but in the same line
-
-  # + What to do when it is a cycle change F003F2BEEDB37 ,
-
-  # group_by(patientid, linenumber_new, cycle_inc) %>%
-  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
-  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
-  arrange(patientid, episodedate, cycle_increment) %>% 
-  group_by(patientid, linenumber_new) %>%
-  # mutate(cycle_increment = cycle_inc) %>% 
-  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
-  group_by(patientid, chemotherapy_type, cycle_increment) %>% 
-  mutate(is_dose_dense = row_number(cycle_increment),
-         is_dose_dense = ifelse(is_dose_dense == 1, 1, NA_real_)) %>% 
-  group_by(patientid) %>% 
-  mutate(total_cycle_increment = row_number(is_dose_dense)) %>% 
-  fill(total_cycle_increment, .direction = "downup") %>% 
-  # cycle date
-  group_by(patientid, linenumber_new, cycle_increment) %>% 
-  mutate(cycle_start_date = min(episodedate)) %>%
-
-  # Look at dose dense
-  group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
-  mutate(dose_dense = n()) %>% 
-  mutate(dose_dense = max(dose_dense)) %>%  # too much cycle
-  ungroup() # %>% 
-  # select(patientid, linename, linenumber_new, drugname, episodedate, chemotherapy_type, cycle_increment, dose_dense, amount, ismaintenancetherapy,
-  #        is_dose_dense,cycle_major_drugname, cycle_drugname,
-  #        cycle_count_perline, cycle_major_drugname, drugname_count_perline, cycle_start_date) #%>%  # F002DD2953889, F003F2BEEDB37 only 1+2
-
-  # # CODE FOR SKIPPED CYCLE
-  # group_by(patientid, linenumber_new) %>% 
-  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
-  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
-  # 
-  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
-  # mutate(n = row_number(drugname)) %>%
-  # 
-  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
-  # fill(base_days_between_cycle, .direction = "downup") %>% 
-  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
-  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
-  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
-  # group_by(patientid, linenumber_new) %>%
-  # mutate(drug_count_perline = n()) %>%
-  # mutate(skipped_cycle_indays1 = ifelse(
-  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
-  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
-  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
-  # group_by(patientid) %>% 
-  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
-  # ungroup()
-therapy_cycle %>% distinct(patientid) %>% nrow()
-
-```
-
 ### step 9: Remove Patients with too many cycles
@@
 ```
-
-### step 10: Bind everything together and calculating target_auc and expected dose
-
-(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column called `target_auc` for a tidy data organisation - You can find the calculations formula at the end of the document)
-When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, cisplatin and taxanes and their `expected_dose`.
-It can be days in between but it can also be more.
-
-`r emo::ji("check")`  
-We decided to take the creatinine, weight, bsa measured within a month of the cycle start date AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line
-
-```{r target_auc and expected dose}
-Treatment <- 
-  # Merge with creatinine
-  left_join(therapy_cycle, creatinine, by = "patientid") %>%
-  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
-                          duration(n=1, unit="days"))) %>% 
-  mutate(interval_creat = case_when(
-    (therapy == "Upfront Surgery" &
-       interval_creat < 31 &
-       # creat_date < lineenddate &
-       creat_date > surgerydate)                  ~ interval_creat,
-
-    therapy == "Upfront Chemo" &
-      (
-        (chemotherapy_type == "Neoadjuvant" &
-           interval_creat < 31 &
-           creat_date < surgerydate) |
-          (chemotherapy_type == "Adjuvant" &
-             interval_creat < 31 &
-             # creat_date < lineenddate &
-             creat_date > surgerydate)
-      )                                          ~ interval_creat,
-    TRUE                                         ~ NA_real_
-  )) %>%
-  arrange(interval_creat) %>% 
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
-           cycle_start_date, .keep_all = TRUE) %>%
-
-  # Merge with height
-  left_join(. , height,  by = "patientid") %>%
-  mutate(interval_height = abs(interval(start= height_date, end= cycle_start_date)/
-           duration(n=1, unit="days"))) %>%
-  arrange(interval_height) %>%
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
-           cycle_start_date, .keep_all = TRUE) %>%
-
-  # Merge with weight
-  left_join(. , weight, by = "patientid") %>%
-  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
-                        duration(n=1, unit="days"))) %>%
-  mutate(interval_weight = case_when(
-    (therapy == "Upfront Surgery" &
-       interval_weight < 31 &
-       # weight_date < lineenddate &
-       weight_date > surgerydate)                  ~ interval_weight,
-
-    therapy == "Upfront Chemo" &
-      (
-        (chemotherapy_type == "Neoadjuvant" &
-           interval_weight < 31 &
-           weight_date < surgerydate) |
-          (chemotherapy_type == "Adjuvant" &
-             interval_weight < 31 &
-             # weight_date < lineenddate &
-             weight_date > surgerydate)
-      )                                          ~ interval_weight,
-    TRUE                                         ~ NA_real_
-  )) %>%
-  arrange(interval_weight) %>%
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
-         cycle_start_date, .keep_all = TRUE) %>%
-
-  # Calculate ideal dody weight
-  mutate(ideal_weight = case_when(
-    height <= 1.524               ~ 45.5 + 2.3,
-    height > 1.524                ~ 45.5 + (2.3 * (((height - 1.524) / 0.0254)))
-  )) %>% 
-  mutate(adjusted_weight = ((weight - ideal_weight) * 0.40) + ideal_weight
-  ) %>% 
-  # Calculate bmi
-  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
-  mutate(bmi_cat = case_when(
-    bmi_at_dx < 25                    ~ "Underweight and normal weight",
-    bmi_at_dx >= 25 &
-      bmi_at_dx < 30                  ~ "Overweight",
-    bmi_at_dx >= 30                   ~ "Obese"
-  )) %>%
-  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
-
-  mutate(actual_bmi = weight / (height * height)) %>%
-  mutate(actual_bmi_cat = case_when(
-    actual_bmi < 25                    ~ "Underweight and normal weight",
-    actual_bmi >= 25 &
-      actual_bmi < 30                  ~ "Overweight",
-    actual_bmi >= 30                   ~ "Obese"
-  )) %>%
-  mutate(actual_bmi_cat = factor(actual_bmi_cat, 
-                                  levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
-  # select(patientid, weight, height, bmi_at_dx, ideal_weight, adjusted_weight, adjusted_bmi)
-  # Calculate CrCl
-  inner_join(., clinical_data %>% select(-surgerydate),
-             by = "patientid") %>% 
-  mutate(CrCl = (
-       (
-    ((140 - ageatdx) * weight) /
-    (72 * creatinine)
-       ) *
-    0.85)
-  ) %>% 
-  mutate(CrCl = case_when(
-    CrCl > 125                        ~ 125,
-    TRUE                              ~ CrCl
-  )) %>% 
-  mutate(adjusted_CrCl = case_when(
-    actual_bmi >= 25                  ~ CrCl,
-    actual_bmi < 25                   ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
-  )) %>% 
-  mutate(adjusted_CrCl = case_when(
-    adjusted_CrCl > 125               ~ 125,
-    TRUE                              ~ adjusted_CrCl
-  )) %>%
-
-  # Merge with body_surface_area
-  left_join(., body_surface_area, by = "patientid") %>%
-  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
-                          duration(n=1, unit="days"))) %>%
-  mutate(interval_bsa = case_when(
-    (therapy == "Upfront Surgery" &
-       interval_bsa < 31 &
-       # bsa_date < lineenddate &
-       bsa_date > surgerydate)                  ~ interval_bsa,
-
-    therapy == "Upfront Chemo" &
-      (
-        (chemotherapy_type == "Neoadjuvant" &
-           interval_bsa < 31 &
-           bsa_date < surgerydate) |
-          (chemotherapy_type == "Adjuvant" &
-             interval_bsa < 31 &
-             # bsa_date < lineenddate &
-             bsa_date > surgerydate)
-      )                                          ~ interval_bsa,
-    TRUE                                         ~ NA_real_
-  )) %>%
-  arrange(interval_bsa) %>%
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
-           cycle_start_date, .keep_all = TRUE) %>%
-  # Calculate more bsa value with height and weight using Du Bois formula
-  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
-  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
-  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
-  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
-  select(-bsa_du_bois) %>%
-
-  # Merge with auc
-  left_join(., areaUC, by = c("patientid", "drugname")) %>%
-  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
-                          duration(n=1, unit="days"))) %>% 
-  mutate(interval_auc = case_when(
-    (therapy == "Upfront Surgery" &
-       interval_auc < 31 &
-       # auc_date < lineenddate &
-       auc_date > surgerydate)                  ~ interval_auc,
-
-    therapy == "Upfront Chemo" &
-      (
-        (chemotherapy_type == "Neoadjuvant" &
-           interval_auc < 31 &
-           auc_date < surgerydate) |
-          (chemotherapy_type == "Adjuvant" &
-             interval_auc < 31 &
-             # auc_date < lineenddate &
-             auc_date > surgerydate)
-      )                                          ~ interval_auc,
-    TRUE                                         ~ NA_real_
-  )) %>%
-  arrange(interval_auc) %>% 
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
-           cycle_start_date, .keep_all = TRUE) %>%
-
-  # Calculate expected dose
-  mutate(expected_dose = case_when(
-    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
-    drugname == "paclitaxel"                  ~ BSA * target_auc 
-    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
-  )) %>% 
-  mutate(expected_dose = case_when(
-    expected_dose > 900 &
-      target_auc == 6              ~ 900,
-    expected_dose > 750 &
-      target_auc == 5              ~ 750,
-    TRUE                           ~ expected_dose
-  )) %>% 
-  mutate(adjusted_expected_dose = case_when(
-    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
-    drugname == "paclitaxel"                  ~ BSA * target_auc 
-    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
-  )) %>% 
-  mutate(adjusted_expected_dose = case_when(
-    adjusted_expected_dose > 900 &
-      target_auc == 6              ~ 900,
-    adjusted_expected_dose > 750 &
-      target_auc == 5              ~ 750,
-    TRUE                           ~ adjusted_expected_dose
-  )) %>% 
-  group_by(patientid) %>%
-  mutate(first_treatment_date = case_when(
-    str_detect(therapy, "Chemo")                      ~ min(episodedate),
-    str_detect(therapy, "Surgery")                    ~ surgerydate,
-  )) %>% 
-  ungroup() %>% 
-  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
-                   duration(n=1, units = "months")) %>% 
-  arrange(patientid, episodedate)
-```
-
-```{r plot interval}
-Treatment %>% 
-  ggplot(aes(x= interval_creat)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
-# Treatment %>% 
-#   ggplot(aes(x= interval_height)) +
-#   geom_bar() +
-#   coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_weight)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_bsa)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_auc)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
-```
-
-### **Number of patients : `r Treatment %>% distinct(patientid) %>% nrow()`**
-
-```{r RDI calculation}
-Frontline <- Treatment %>% 
-  filter(chemotherapy_type == "Neoadjuvant" |
-           (chemotherapy_type == "Adjuvant" &
-              linenumber_adj == 1)) %>%
-
-  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
-  ) %>%
-  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
-  #        relative_dose_intensity, linenumber_adj) %>%
-
-  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
-  group_by(patientid, chemotherapy_type, drugname) %>%
-  # mutate(mean_RDI_per_drug = case_when(
-  #   chemotherapy_type == "Adjuvant" &
-  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
-  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
-  # )) %>% 
-  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
-  ) %>% 
-  ungroup() %>% 
-  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE)
-```
-
-```{r RDI calculation 1 per patient}
-Frontline <- Frontline %>% 
-  group_by(patientid, drugname) %>%
-  mutate(mean_RDI_per_drug = round(mean(mean_RDI_per_drug, na.rm = TRUE), 3)
-  ) %>% 
-  ungroup() %>% 
-  distinct(patientid, drugname_type, .keep_all = TRUE)
-```
-
-```{r RDI calculation continuation}
-Frontline <- Frontline %>% 
-  # general
-  mutate(RDI_grp = case_when(
-    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
-    mean_RDI_per_drug < 0.85               ~ "Underdosed"
-  )) %>% 
-  mutate(RDI_grp = factor(RDI_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
-  mutate(RDI_grp1 = case_when(
-    mean_RDI_per_drug < 0.75               ~ "Highly underdosed",
-    mean_RDI_per_drug >= 0.75 &
-      mean_RDI_per_drug < 0.85             ~ "Underdosed",
-    mean_RDI_per_drug >= 0.85 &
-      mean_RDI_per_drug < 1.1              ~ "Adequate dosing",
-    mean_RDI_per_drug >= 1.1               ~ "Overdosing"
-  )) %>% 
-  mutate(RDI_grp1 = factor(RDI_grp1, 
-                          levels = c("Adequate dosing",
-                                     "Underdosed", 
-                                     "Highly underdosed",
-                                     "Overdosing"))) %>% 
-  # separated
-  mutate(RDI_carbo = case_when(
-    drugname == "carboplatin"               ~ mean_RDI_per_drug,
-    TRUE                                    ~ NA_real_
-  )) %>% 
-  mutate(RDI_pacli = case_when(
-    drugname == "paclitaxel"               ~ mean_RDI_per_drug,
-    TRUE                                    ~ NA_real_
-  )) %>% 
-  mutate(RDI_carbo_grp = case_when(
-    RDI_carbo >= 0.85              ~ "Adequate dosing",
-    RDI_carbo < 0.85               ~ "Underdosed"
-  )) %>% 
-  mutate(RDI_carbo_grp = factor(RDI_carbo_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
-  mutate(RDI_carbo_grp1 = case_when(
-    RDI_carbo < 0.75               ~ "Highly underdosed",
-    RDI_carbo >= 0.75 &
-      RDI_carbo < 0.85             ~ "Underdosed",
-    RDI_carbo >= 0.85 &
-      RDI_carbo < 1.1              ~ "Adequate dosing",
-    RDI_carbo >= 1.1               ~ "Overdosing"
-  )) %>% 
-  mutate(RDI_carbo_grp1 = factor(RDI_carbo_grp1, 
-                          levels = c("Adequate dosing",
-                                     "Underdosed", 
-                                     "Highly underdosed",
-                                     "Overdosing"))) %>% 
-  mutate(RDI_pacli_grp = case_when(
-    RDI_pacli >= 0.85              ~ "Adequate dosing",
-    RDI_pacli < 0.85               ~ "Underdosed"
-  )) %>% 
-  mutate(RDI_pacli_grp = factor(RDI_pacli_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
-  mutate(RDI_pacli_grp1 = case_when(
-    RDI_pacli < 0.75               ~ "Highly underdosed",
-    RDI_pacli >= 0.75 &
-      RDI_pacli < 0.85             ~ "Underdosed",
-    RDI_pacli >= 0.85 &
-      RDI_pacli < 1.1              ~ "Adequate dosing",
-    RDI_pacli >= 1.1               ~ "Overdosing"
-  )) %>% 
-  mutate(RDI_pacli_grp1 = factor(RDI_pacli_grp1, 
-                          levels = c("Adequate dosing",
-                                     "Underdosed", 
-                                     "Highly underdosed",
-                                     "Overdosing")))
-```
-<br>
-<br>
 
@@
 ### RDI group
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_grp + RDI_pacli_grp + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + raceeth + ageatdx + stagecat` 
 ```{r Table 5 HR adjusted rdi group adjusted by other drug}
-Frontline_adjusted <- Frontline %>% 
-  group_by(patientid) %>% 
-  fill(RDI_carbo, RDI_carbo_grp, RDI_carbo_grp1, RDI_pacli, RDI_pacli_grp, RDI_pacli_grp1, .direction = "downup") %>% 
-  distinct(patientid, .keep_all = TRUE)
 
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_grp + RDI_pacli_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_grp + RDI_pacli_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ### Continous
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo + RDI_pacli + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + raceeth + ageatdx + stagecat` 
 ```{r rdi continous adjusted by other drug}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo + RDI_pacli + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo + RDI_pacli + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ### RDI group
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_grp1 + RDI_pacli_grp1 + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` 
 ```{r Table 5 HR adjusted rdi group adjusted by other drug 2}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_grp1 + RDI_pacli_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_grp1 + RDI_pacli_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

### 2021-12-02 Rmd/rdi analysis.Rmd
Update html, re-did tables and more

@@
          drugname_count_perline = case_when(
-           str_detect(drugname, "platin|taxel")     ~ n()
+           str_detect(drugname, "carboplatin|paclitaxel")     ~ n()
          )
@@
 
-- Code cycle number
 ```{r cycle coding}
@@
 therapy_cycle <- therapy_line %>% 
-  # filter(str_detect(drugname, "taxel|platin")) %>% # Need to that now for patient who got Bev only once per line F02D8628A5394
-
-  arrange(patientid, episodedate) %>% 
+  arrange(patientid, episodedate, drugname) %>% 
   group_by(patientid, linenumber_new) %>%
@@
   mutate(cycle_major_drugname = case_when(
-    cycle_count_perline == drugname_count_perline          ~ cycle_drugname,
+    cycle_count_perline == drugname_count_perline &
+      (drugname == "carboplatin" |
+      drugname == "paclitaxel")                            ~ cycle_drugname,
     TRUE                                                   ~ NA_character_
@@
   group_by(patientid) %>% 
-  mutate(total_cycle_increment = row_number(is_dose_dense)) %>% 
+  mutate(total_cycle_increment = #case_when(
+           # ismaintenancetherapy == "FALSE"            ~ 
+           row_number(is_dose_dense)
+         # )
+  ) %>% 
   fill(total_cycle_increment, .direction = "downup") %>% 
@@
   # ungroup()
-therapy_cycle %>% distinct(patientid) %>% nrow()
 
@@
 ```{r target_auc and expected dose}
-Treatment <- 
+Treatment1 <- 
   # Merge with creatinine
@@
 ```{r plot interval}
-Treatment %>% 
-  ggplot(aes(x= interval_creat)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
 # Treatment %>% 
-#   ggplot(aes(x= interval_height)) +
-#   geom_bar() +
-#   coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_weight)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_bsa)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
-Treatment %>% 
-  ggplot(aes(x= interval_auc)) +
-  geom_bar() #+
-  # coord_cartesian(ylim=c(0,50))
-```
-
-# Variable for filtering
+#   ggplot(aes(x= interval_creat)) +
+#   geom_bar() #+
+#   # coord_cartesian(ylim=c(0,50))
+# # Treatment %>% 
+# #   ggplot(aes(x= interval_height)) +
+# #   geom_bar() +
+# #   coord_cartesian(ylim=c(0,50))
+# Treatment %>% 
+#   ggplot(aes(x= interval_weight)) +
+#   geom_bar() #+
+#   # coord_cartesian(ylim=c(0,50))
+# Treatment %>% 
+#   ggplot(aes(x= interval_bsa)) +
+#   geom_bar() #+
+#   # coord_cartesian(ylim=c(0,50))
+# Treatment %>% 
+#   ggplot(aes(x= interval_auc)) +
+#   geom_bar() #+
+#   # coord_cartesian(ylim=c(0,50))
+```
+
+<!-- # Variable for filtering -->
 
 ```{r rule between diagnosis and treatment}
-Treatment <- Treatment %>% 
+Treatment <- Treatment1 %>% 
+  filter(route == "Intravenous") %>% 
   # 1. 60 days rule between diagnosis and treatment # Loss 1
@@
     ),
-  )
+  ) %>% 
+  group_by(patientid) %>% 
+  mutate(neo_more_more_than_1line = case_when(
+    chemotherapy_type == "Neoadjuvant" &
+           linenumber_new != 1                 ~ "exclude"
+  )) %>% 
+  fill(neo_more_more_than_1line, .direction = "updown") %>% 
+  ungroup() %>% 
+  mutate(whole_frontline_is_maintenance = case_when(
+    (linenumber_new == 1 &
+    ismaintenancetherapy == "TRUE") |
+    (linenumber_new == 2 &
+      therapy == "Upfront Chemo" &
+    ismaintenancetherapy == "TRUE")            ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>% 
+  fill(whole_frontline_is_maintenance, .direction = "updown") %>% 
+  ungroup() %>% 
+  mutate(too_many_cycle = case_when(
+    (linenumber_new == 1 &
+       therapy == "Upfront Chemo" &
+       total_cycle_increment > 6) |
+
+      (linenumber_new == 2 &
+         therapy == "Upfront Chemo" &
+         total_cycle_increment > 9) |
+
+      (linenumber_new == 1 &
+         therapy == "Upfront Surgery" &
+         total_cycle_increment > 9)             ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(too_many_cycle, .direction = "updown") %>%
+  ungroup() %>%
+
+  mutate(wrong_pacli_dosedense = case_when(
+    drugname == "paclitaxel" &
+      is.na(too_many_cycle) &
+      (dose_dense == 2 |
+      dose_dense > 3) &
+
+      ((linenumber_new == 1 &
+       therapy == "Upfront Chemo") |
+
+      (linenumber_new == 2 &
+         therapy == "Upfront Chemo") |
+
+      (linenumber_new == 1 &
+         therapy == "Upfront Surgery"))
+    ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
+  ungroup()
+
+  # group_by(patientid, wrong_pacli_dosedense) %>% 
+  # mutate(n_dose_dense = n()) %>% 
+  # 
+  # 
+  # 
+  # is.na(too_many_cycle)
+
 ```
@@
 ```{r}
-rm(areaUC, body_surface_area, creatinine, clinical_data, drugs, drugs1, 
-   height#, therapy_cycle, therapy_line, Treatment, weight
-   )
+# rm(areaUC, body_surface_area, creatinine, clinical_data, drugs, drugs1, 
+#    height#, therapy_cycle, therapy_line, Treatment, weight
+#    )
 ```
@@
 
-**We start with a number of `r drugs %>% distinct(patientid) %>% nrow()` patients who received treatment and for who their clinical info are available.**
-
 <br>
@@
   group_by(patientid) %>% 
-  fill(flatiron_rules, .direction = "downup")
+  fill(flatiron_rules, .direction = "downup") %>% 
+  ungroup()
 
@@
 
-## 2. step 2: Filter patients with cinical characteristics fitting to the study criteria
+## 2. step 2: Filter patients with clinical characteristics fitting to the study criteria
 
@@
 - include only patients who received platin and/or taxane
+- exclude patients who only received neo + surgery
+- include patients with single or dual P/T +/- Bev as frontline treatment
 ```{r}
@@
   filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs
-```
-
-```{r}
+
 drugs1 <- drugs1 %>%
   filter(!is.na(surgerydate))
-```
-
-```{r}
+
 drugs1 <- drugs1 %>%
   filter(had_carbo_pacli == "Yes")
-```
-
-**At the end of the step 2, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
-
-<br>
-
-## 3. step 3: Filter out patients with missing data
-
-- exclude the patients who had surgery but we don't have a date of surgery -> NONE anymore
-
-```{r}
-drugs11 <- drugs1 %>% 
-  filter(!(issurgery == "Yes" & is.na(surgerydate))) 
-```
-
-- remove patients with long gap between surgery and adjuvant start -> NONE anymore  
-Did a 3 months gap
-```{r}
-drugs11 <- drugs11 %>%
-  arrange(patientid, episodedate) %>%
-  mutate(ex = case_when(
-    interval_surgery_to_adj_start > 3                  ~ "exclude"
-  )) %>% 
-  filter(is.na(ex))
-
-drugs11 %>% distinct(patientid) %>% nrow()
-```
-
-RESTART HERE ----------------------------------------------------
-
-### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
-We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis.
-Patients left :
-```{r}
+
 drugs1 <- drugs1 %>% 
-  filter(days_at_first_drug >= 0 &
-           (is.na(surgerydate) | days_at_surg >= 0)
-         )
-drugs1 %>% distinct(patientid) %>% nrow()
-```
-
-```{r}
-therapy_line <- therapy_line %>% 
   filter(treatment_sequence == "neo + surg + adj" |
@@
 
-# Number of patient with a jump line in the first line # 60 would have
-# therapy_line %>% 
-#   filter(linenumber == 1 & linenumber_new == 2) %>% 
-#   arrange(desc(jump_line)) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(jump_line) %>% 
-#   tbl_summary()
-```
-
-```{r}
-therapy_line %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(had_neo, had_adj, therapy) %>% 
-  tbl_summary(by = therapy,
-              type = list(had_neo ~ "dichotomous", 
-                          had_adj ~ "dichotomous"),
-              missing = "no")
-# therapy_line %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(therapy, treatment_sequence) %>% 
-#   tbl_summary(by = therapy)
-```
-
-`r emo::ji("check")`
-
-### step 4: Remove linename that doesn't include platinum or taxanes in first line
-
-Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?
-`r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>
-`r emo::ji("check")`   
-```{r}
 # F0017FB3A8828 starts with gemcitabine then have carbo
 
-therapy_line <- therapy_line %>%
+drugs1 <- drugs1 %>%
   # Remove patients with other linename
@@
 
-First table is frontline Neo, second table is frontline Adj.
+**At the end of the step 2, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
+
+<br>
+
+## 3. step 3: Filter out patients with missing data
+
+- exclude the patients who had surgery but we don't have a date of surgery -> NONE removed anymore  
+- remove patients with long gap between surgery and adjuvant start (3  months) -> NONE removed anymore  
+- exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
+- exclude patients for whose no RDI were available
+
 ```{r}
-therapy_line %>% 
-  filter(linenumber == 1
-         ) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename) %>% 
-  tbl_summary(sort = list(everything() ~ "frequency"))
-
-therapy_line %>% 
-  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename) %>% 
-  tbl_summary(sort = list(everything() ~ "frequency"))
-```
-
-We now have `r therapy_line %>% distinct(patientid) %>% nrow()` patients.
-
-### step 5: remove patients with maintenance as first line adjuvant?????
-`r emo::ji("question_mark")`
-<span style="color:red">**Patients have maintenance as first line Adjuvant then recurrent treatment : Should I remove these patients or keep them for the Neoadjuvant RDI??**</span>
+drugs11 <- drugs1 %>% 
+  filter(!(issurgery == "Yes" & is.na(surgerydate)))
+
+drugs11 <- drugs11 %>%
+  arrange(patientid, episodedate) %>%
+  mutate(ex = case_when(
+    interval_surgery_to_adj_start > 3                  ~ "exclude"
+  )) %>% 
+  filter(is.na(ex))
+
+drugs11 <- drugs11 %>% 
+  filter(days_at_first_drug >= 0 &
+           (is.na(surgerydate) | days_at_surg >= 0)
+         )
+
+drugs11 <- drugs11 %>% 
+  # remove these patients who switched C > C 
+  filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
+            !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) & 
+            therapy == "Upfront Chemo") |
+           (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
+            therapy == "Upfront Surgery")))
+```
+**At the end of the step 3, we have `r drugs11 %>% distinct(patientid) %>% nrow()` patients.**
+
+## 4. step 4: Include patients with treatments following the standart of clinical care
+
+- exclude patients with more than 1 line as Neo
+- exclude patients with maintenance within their frontline
+- exclude patients with more than 6 cycles in Neo, more than 9 cycles **total** in upfront chemo or more than 9 cycles in upfront surgery
 ```{r}
-therapy_line %>% 
-  filter(linenumber_adj == 1) %>% 
-  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
-  select(ismaintenancetherapy, linename) %>% 
-  tbl_summary(by = linename)
-# a <- therapy_line %>% 
-#   filter(linenumber_adj == 1)
-therapy_line %>% 
-  filter(linenumber_adj == 1) %>%
-  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
-  select(ismaintenancetherapy, chemotherapy_type) %>% 
-  tbl_summary(by = chemotherapy_type)
-therapy_line %>% 
-  filter(linenumber_adj == 1, chemotherapy_type == "Neoadjuvant") %>%
-  arrange(desc(ismaintenancetherapy)) %>% 
-  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
-  select(ismaintenancetherapy, chemotherapy_type) %>% 
-  tbl_summary(by = chemotherapy_type)
-```
-
-#### remove only the maintenance line in neo or adj
-```{r remove only the maintenance line in neo or adj}
-# therapy_line <- therapy_line %>% 
-#   filter(!(ismaintenancetherapy == TRUE & linenumber_adj == 1))
-# therapy_line %>% distinct(patientid) %>% nrow()
-```
-
-#### OR remove patients with maintenance in neo
-```{r remove patients with maintenance in neo}
-# remove_neo_patients_maintenance <- therapy_line %>% 
-#   filter(linenumber_adj == 1, chemotherapy_type == "Neoadjuvant", ismaintenancetherapy == TRUE) %>%
-#   arrange(desc(ismaintenancetherapy)) %>% 
+drugs111 <- drugs11 %>% 
+  # Remove patients with more than 1 line as Neo
+  filter(is.na(neo_more_more_than_1line))
+
+drugs111 <- drugs111 %>% 
+  filter(is.na(whole_frontline_is_maintenance))
+
+drugs111 <- drugs111 %>% 
+  filter(is.na(too_many_cycle))
+```
+**We have `r drugs111 %>% distinct(patientid) %>% nrow()` patients.**
+
+- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
+```{r}
+Frontline <- drugs111 %>% 
+  filter(is.na(wrong_pacli_dosedense))
+
+# drugs111 %>% 
+#   mutate(n_dose_dense = factor(n_dose_dense)) %>% 
+#   select(n_dose_dense, therapy) %>% 
+#   tbl_summary(by = therapy)
+
+test <- Frontline %>% 
+  filter(wrong_pacli_dosedense == "exclude")
+
+wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
+  filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
+  select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
+```
+**We have `r Frontline %>% distinct(patientid) %>% nrow()` patients.**
+
+```{r}
+# d <- end_patients_Treatment %>% 
+#   select(patientid, linename, linenumber_new, chemotherapy_type, therapy, cycle_increment, total_cycle_increment, ismaintenancetherapy)
+
+# end_patients_Treatment %>% 
+#   mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
+#   arrange(desc(total_cycle_increment)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(total_cycle_increment, therapy) %>% 
+#   tbl_summary(by = therapy)
+```
+
+- exclude patients who switch drug within a line
+
+`r Frontline %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.  
+`r Frontline %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.
+
+<!-- Patients left: -->
+```{r}
+# switch cispl vs carbo  Car > Cis F1BF7208F0E96
+
+# remove_switch <- therapy_line %>% 
+#   filter(linenumber_adj == 1 &
+#     ((str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
+#   (str_detect(linename, "Cisplatin") & drugname == "carboplatin"))
+#   ) %>%
 #   distinct(patientid)
+# remove_switch <- paste(remove_switch$patientid, collapse = "|")
 # 
 # therapy_line <- therapy_line %>% 
-#   filter(!str_detect(patientid, paste(remove_neo_patients_maintenance$patientid, collapse = "|")))
+#   # remove these patients who switched C > C 
+#   filter(!str_detect(patientid, remove_switch))
 # therapy_line %>% distinct(patientid) %>% nrow()
@@
 
-#### OR remove totally patients with maintenance in frontline neo or adj
-```{r remove totally patients with maintenance in neo or adj}
-remove_patients_maintenance <- therapy_line %>% 
-  filter(linenumber_adj == 1 & ismaintenancetherapy == TRUE) %>%
-  arrange(desc(ismaintenancetherapy)) %>% 
-  distinct(patientid)
-
-therapy_line <- therapy_line %>%
-  filter(!str_detect(patientid, paste(remove_patients_maintenance$patientid, collapse = "|")))
-therapy_line %>% distinct(patientid) %>% nrow()
-```
-
-#### remove patients with more than 9 cycles total in upfront chemo or upfront surgery
-
-### step 7: Remove patients with more than 1 line as Neo
-We are removing the 34 patients who received multiple Neoadjuvant line.   
-`r emo::ji("check")`
-
-<!-- Here the lines for the 34 patient. -->
-```{r, rows.print = 40}
+`r Frontline %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.
+<!-- I am removing these patients   -->
+
+<!-- Patients left: -->
+```{r}
+# remove_switch1 <- therapy_line %>% 
+#   filter(
+#     str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1
+#   ) %>%
+#   distinct(patientid)
+# remove_switch1 <- paste(remove_switch1$patientid, collapse = "|")
+# 
+# therapy_line <- therapy_line %>% 
+#   # remove these patients who switched C > C 
+#   filter(!str_detect(patientid, remove_switch1))
+# therapy_line %>% distinct(patientid) %>% nrow()
+```
+
+<!-- TABLES -->
+
+```{r}
+# drugs11 %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(had_neo, had_adj, therapy) %>% 
+#   tbl_summary(by = therapy,
+#               type = list(had_neo ~ "dichotomous", 
+#                           had_adj ~ "dichotomous"),
+#               missing = "no")
+# # therapy_line %>% 
+# #   distinct(patientid, .keep_all = TRUE) %>% 
+# #   select(therapy, treatment_sequence) %>% 
+# #   tbl_summary(by = therapy)
+```
+
+<!-- First table is frontline Neo, second table is frontline Adj. -->
+```{r}
+# # drugs1 %>% Need to do in Frontline
+#   filter(linenumber == 1
+#          ) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(linename) %>% 
+#   tbl_summary(sort = list(everything() ~ "frequency"))
+# 
+# # drugs11 %>% 
+# #   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
+# #   distinct(patientid, .keep_all = TRUE) %>% 
+# #   select(linename) %>% 
+# #   tbl_summary(sort = list(everything() ~ "frequency"))
+```
+
+<!-- ### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line -->
+```{r Number of patient who switch line}
 # therapy_line %>% 
-#   filter(chemotherapy_type == "Neoadjuvant" &
-#            (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
-#   select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
-#          drugname, episodedate, surgerydate, chemotherapy_type) %>%
-#   arrange(patientid, episodedate) %>% 
-#   distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
-#   select(-linenumber)
-
-remove_morethan1_neo <- therapy_line %>% 
-  filter(chemotherapy_type == "Neoadjuvant" &
-           linenumber_new != 1) %>% 
-  distinct(patientid)
-
-therapy_line <- therapy_line %>% 
-  # Remove patients with more than 1 line as Neo
-  filter(!str_detect(patientid, paste(remove_morethan1_neo$patientid, collapse = "|")))
-```
-
-Patients left:
+#   mutate(change_line = case_when(
+#     linenumber == 1 & 
+#       linenumber_new == 2 &
+#       chemotherapy_type == "Adjuvant" &
+#       therapy == "Upfront Chemo"                   ~ 1,
+#     TRUE                                           ~ 0
+#   )) %>% 
+#   arrange(desc(change_line)) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   select(change_line) %>% 
+#   tbl_summary()
+```
+
+<!-- For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line? -->
 ```{r}
-therapy_line %>% distinct(patientid) %>% nrow()
-```
-
-### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line
-```{r Number of patient who switch line}
-therapy_line %>% 
-  mutate(change_line = case_when(
-    linenumber == 1 & 
-      linenumber_new == 2 &
-      chemotherapy_type == "Adjuvant" &
-      therapy == "Upfront Chemo"                   ~ 1,
-    TRUE                                           ~ 0
-  )) %>% 
-  arrange(desc(change_line)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(change_line) %>% 
-  tbl_summary()
-```
-
-For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line?
+# therapy_line %>% 
+#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
+#            duration(n = 1, units = "days")) %>% 
+#   filter(linenumber == 1 & linenumber_new == 2) %>% 
+#   # select(patientid, linenumber, linenumber_new, linenumber_adj, 
+#   #        drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
+#   distinct(patientid, .keep_all = TRUE) %>% 
+#   ggplot(aes(x= line_duration))+
+#   geom_histogram(aes(fill = route), binwidth = 7) +
+#   theme_minimal(base_size = 14)+
+#   labs(x="Line duration", 
+#        y="Number of Patient",
+#        caption = "Each bar represents 7 days, bottom plot is zoomed in")+
+#   ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
+```
+<!-- Several patients have a short line.   -->
+<!-- `r emo::ji("question_mark")` **Should we remove the patient with a line lasting less than a cycle** We said during October meeting to check if were IP administration.... -->
+
 ```{r}
-therapy_line %>% 
-  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
-           duration(n = 1, units = "days")) %>% 
-  filter(linenumber == 1 & linenumber_new == 2) %>% 
-  # select(patientid, linenumber, linenumber_new, linenumber_adj, 
-  #        drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= line_duration))+
-  geom_histogram(aes(fill = route), binwidth = 7) +
-  theme_minimal(base_size = 14)+
-  labs(x="Line duration", 
-       y="Number of Patient",
-       caption = "Each bar represents 7 days, bottom plot is zoomed in")+
-  ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
-```
-Several patients have a short line.  
-`r emo::ji("question_mark")` **Should we remove the patient with a line lasting less than a cycle** We said during October meeting to check if were IP administration....
-
-```{r}
-therapy_line %>% 
-  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
-           duration(n = 1, units = "days")) %>% 
-  filter(linenumber == 1 & linenumber_new == 2) %>% 
-  select(patientid, surgerydate, episodedate, line_duration, drugname,
-         chemotherapy_type, therapy, 
-         linenumber, linenumber_new, route, amount) %>% 
-  filter(line_duration < 30) %>% 
-  arrange(line_duration, patientid, episodedate)
-```
-
-#### Remove peritoneal administration
-```{r}
-therapy_line <- therapy_line %>% 
-  filter(route == "Intravenous")
+# therapy_line %>% 
+#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
+#            duration(n = 1, units = "days")) %>% 
+#   filter(linenumber == 1 & linenumber_new == 2) %>% 
+#   select(patientid, surgerydate, episodedate, line_duration, drugname,
+#          chemotherapy_type, therapy, 
+#          linenumber, linenumber_new, route, amount) %>% 
+#   filter(line_duration < 30) %>% 
+#   arrange(line_duration, patientid, episodedate)
 ```
@@
 
-<br>
-
-### step 8: Remove patients who switch drug within a line
-
-`r therapy_line %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line and were removed.
-`r therapy_line %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line and were removed.
-
-Patients left:
-```{r}
-# switch cispl vs carbo  Car > Cis F1BF7208F0E96
-
-remove_switch <- therapy_line %>% 
-  filter(linenumber_adj == 1 &
-    ((str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
-  (str_detect(linename, "Cisplatin") & drugname == "carboplatin"))
-  ) %>%
-  distinct(patientid)
-remove_switch <- paste(remove_switch$patientid, collapse = "|")
-
-therapy_line <- therapy_line %>% 
-  # remove these patients who switched C > C 
-  filter(!str_detect(patientid, remove_switch))
-therapy_line %>% distinct(patientid) %>% nrow()
-```
-
-`r therapy_line %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.
-I am removing these patients
-
-Patients left:
-```{r}
-remove_switch1 <- therapy_line %>% 
-  filter(
-    str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1
-  ) %>%
-  distinct(patientid)
-remove_switch1 <- paste(remove_switch1$patientid, collapse = "|")
-
-therapy_line <- therapy_line %>% 
-  # remove these patients who switched C > C 
-  filter(!str_detect(patientid, remove_switch1))
-therapy_line %>% distinct(patientid) %>% nrow()
-```
-
-<br>
-
 <!-- <span style="color:red">**Random question : within 1 cycle we can have taxanes multiple times, is it possible for carboplatin or cisplatin?**</span>   -->
 
-### step 9: Remove Patients with too many cycles
-```{r more than 9 cycle patients}
-therapy_cycle %>% 
-  filter(therapy == "Upfront Chemo") %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment, chemotherapy_type) %>% 
-  tbl_summary(by = chemotherapy_type)
-therapy_cycle %>% 
-  filter(therapy == "Upfront Surgery") %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment, chemotherapy_type) %>% 
-  tbl_summary(by = chemotherapy_type)
-```
-We said to remove patients with more than 9 total cycle but maybe we can save some....
-
-#### What is dose dense / or unnoted maintenance (example in ppt) 
-2 in the dose dense would mean 1 carbo + 2 pacli  
-3 in the dose dense would mean 1 carbo + 3 pacli  
-etc
-```{r what is dose dense}
-therapy_cycle %>% 
-  filter(linenumber_adj == 1) %>% 
-  arrange(patientid, linenumber_new, desc(dose_dense)) %>% 
-  mutate(dose_dense = as.factor(dose_dense)) %>% 
-  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
-  select(dose_dense, linename) %>% 
-  tbl_summary(by = linename)
-```
-
-#### Remove wrong dose dense patients (>3) ???
-```{r remove wrong dose dense patients}
-wrong_dose_dense <- therapy_cycle %>% 
-  filter(linenumber_adj == 1 & dose_dense > 3) %>% 
-  distinct(patientid)
-
-therapy_cycle <- therapy_cycle %>%
-  filter(!str_detect(patientid, paste(wrong_dose_dense$patientid, collapse = "|")))
-therapy_cycle %>% distinct(patientid) %>% nrow()
-```
-
-#### OR Remove only the extra administration from 1+3 dose dense???
-```{r remove only the extra administration from 1+3 dose dense}
-therapy_cycle <- therapy_cycle %>%
-  filter(dose_dense <= 3)
-therapy_cycle %>% distinct(patientid) %>% nrow()
-```
-
-#### Then
-#### Remove totally the patients with more than 9 cycle total
-```{r more than 9 cycle patients same code}
-therapy_cycle %>% 
-  filter(therapy == "Upfront Chemo") %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment, chemotherapy_type) %>% 
-  tbl_summary(by = chemotherapy_type)
-therapy_cycle %>% 
-  filter(therapy == "Upfront Surgery") %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
-  arrange(desc(cycle_increment)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment, chemotherapy_type) %>% 
-  tbl_summary(by = chemotherapy_type)
-```
-
-```{r remove more than 9 cycle patients}
-too_much_cycle <- therapy_cycle %>%
-  filter(
-    (therapy == "Upfront Surgery" & total_cycle_increment > 9) |
-      (therapy == "Upfront Chemo" & chemotherapy_type == "Neoadjuvant" & total_cycle_increment > 9)
-  ) %>%
-  distinct(patientid)
-
-therapy_cycle <- therapy_cycle %>%
-  # remove these patients who switched C > C
-  filter(!str_detect(patientid, paste(too_much_cycle$patientid, collapse = "|")))
-therapy_cycle %>% distinct(patientid) %>% nrow()
-```
-
-#### OR remove only the extra cycle????
-```{r remove only the extra cycle}
-therapy_cycle <- therapy_cycle %>%
-  filter(total_cycle_increment <= 9)
-therapy_cycle %>% distinct(patientid) %>% nrow()
-```
-
-# Remove patients who don't have any RDI
-```{r remove no RDI patients}
-no_rdi <- Frontline %>% 
-  arrange(RDI_grp) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% select(patientid, RDI_grp) %>% 
-  filter(is.na(RDI_grp))
-
-no_rdi <- paste(no_rdi$patientid, collapse = "|")
-
-Frontline <- Frontline %>% 
-  # remove these patients who switched C > C 
-  filter(!str_detect(patientid, no_rdi))
-Frontline %>% distinct(patientid) %>% nrow()
-```
-<br>
-
-### If we keep as is, the
-## **Number of patients in final dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
+<br>
+<br>
+
+## **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
 
@@
 
-## Missingness
-Here some representation of missingness in our data:  
-- In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
+<!-- ## Missingness -->
+<!-- Here some representation of missingness in our data:   -->
+<!-- - In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
 Because these parameters overlap only 25 patients will have missing value for all of them.
-- In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation).
+-->
+<!-- - In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation).
 the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
+-->
 ```{r}
-library(naniar)
-
-Frontline %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
-  gg_miss_upset()
+# library(naniar)
+# 
+# Frontline %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
+#   gg_miss_upset()
 
@@
 ) + guides(colour = guide_legend(ncol = 2))
-
-# # OS by brca1_tumor
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of diagnosis", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by brca2_tumor
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of diagnosis", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by brca_tumor
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of diagnosis", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by brca1_g
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of diagnosis", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by brca2_g
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of diagnosis", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by brca_g
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of diagnosis", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
 ```
@@
 ) + guides(colour = guide_legend(ncol = 2))
-
-# # OS by brca1_tumor
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of first treatment", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by brca2_tumor
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of first treatment", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by brca_tumor
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of first treatment", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# # OS by brca1_g
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of first treatment", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by brca2_g
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of first treatment", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
-# 
-# # OS by brca_g
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of first treatment", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 2))
 ```
@@
   coord_flip()
-
-# Frontline %>% 
-#   arrange(episodedate) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   group_by(chemotherapy_type) %>% 
-#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
-#   geom_bar(stat="identity")+
-#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
-#   theme_minimal(base_size = 14)+
-#   guides(fill = FALSE) +
-#   coord_flip()
-
-# Frontline %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   # group_by(treatment_sequence) %>% 
-#   # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-#   ggplot(aes(x= treatment_sequence))+
-#   geom_bar(
-#     # stat="identity"
-#     )+
-#   labs(x = "", title = "The treatment_sequence") +
-#   theme_minimal(base_size = 14)+
-#   guides(fill = FALSE) +
-#   coord_flip()
-
 ```
@@
   coord_flip()
-
-# Frontline %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   # group_by(treatment_sequence) %>% 
-#   # summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
-#   ggplot(aes(x= raceeth,
-#              # y= percent, 
-#              fill = treatment_sequence))+
-#   geom_bar(
-#     position ="fill"
-#     )+
-#   labs(x = "", title = "The treatment_sequence") +
-#   theme_minimal(base_size = 14)+
-#   # guides(fill = FALSE) +
-#   coord_flip()
 
@@
 
-# OS by residualdiseasestatus
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of diagnosis", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 1))
-
 # OS by therapy
@@
 
-# # OS by residualdiseasestatus
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ residualdiseasestatus, data=Frontline %>% 
-#                      distinct(patientid, .keep_all = TRUE)),
-#            title = "OS from date of from first treatment", 
-#            font.main = c(24, "bold", "black"), 
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-#            size = 1.5,
-#            
-#            pval=TRUE, 
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"), 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-#            
-#            legend.title = "", xlab = "Time (in months)" 
-# ) + guides(colour = guide_legend(ncol = 1))
-
 # OS by therapy
@@
 ```{r rdi plots, fig.height=10, fig.height=9}
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= drugname))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  coord_flip()+
-  facet_wrap(. ~ therapy)
-
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
-  geom_boxplot()+
-  # ylim(c(-.25, 3.5))+
-  geom_jitter(shape=16)+
-  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
-  theme_minimal(base_size = 14)+
-  facet_wrap(.~ drugname, ncol = 2)
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= drugname))+
+#   geom_bar()+
+#   theme_minimal(base_size = 14)+
+#   coord_flip()+
+#   facet_wrap(. ~ therapy)
+# 
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
+#   geom_boxplot()+
+#   # ylim(c(-.25, 3.5))+
+#   geom_jitter(shape=16)+
+#   labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
+#   theme_minimal(base_size = 14)+
+#   facet_wrap(.~ drugname, ncol = 2)
 ```
@@
 ```{r, fig.height=10, fig.height=9}
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= drugname, fill= RDI_grp))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  coord_flip()+
-  facet_wrap(. ~ therapy)
-
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
-  # geom_boxplot()+
-  ylim(c(-.25, 2))+
-  geom_jitter(shape=16, aes(color=RDI_grp))+
-  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
-  theme_minimal(base_size = 14) +
-  guides(color=FALSE)+
-  facet_wrap(.~ drugname, ncol = 2)
-
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= drugname, fill= RDI_grp))+
+#   geom_bar(position = "fill")+
+#   theme_minimal(base_size = 14)+
+#   coord_flip()+
+#   facet_wrap(. ~ therapy)
+# 
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
+#   # geom_boxplot()+
+#   ylim(c(-.25, 2))+
+#   geom_jitter(shape=16, aes(color=RDI_grp))+
+#   labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
+#   theme_minimal(base_size = 14) +
+#   guides(color=FALSE)+
+#   facet_wrap(.~ drugname, ncol = 2)
+```
+</div>
+</div>
+
+```{r}
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= drugname, fill = RDI_grp))+
+#   geom_bar(position = "fill")+
+#   theme_minimal(base_size = 14)+
+#   facet_wrap(.~ therapy)+
+#   coord_flip()
+```
+
+### By Population
+```{r, fig.width=12, fig.height=20}
 # Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
 #   # filter(linenumber_new == "1") %>%
-#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug, color = mean_RDI_per_drug<0.85))+
-#   geom_violin()+
-#   ylim(c(-.25, 2.5))+
-#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
+#   ggplot(aes(x= raceeth, y= mean_RDI_per_drug#, alpha = mean_RDI_per_drug<0.85
+#              ))+
+#   geom_boxplot(aes(fill = drugname))+
+#   ylim(c(0, 2))+
+#   scale_colour_discrete()+
 #   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
 #   theme_minimal(base_size = 14)+
-#   facet_wrap(.~ drugname, ncol = 2)
-
+#   facet_wrap(drugname ~ therapy, ncol = 2, scales = "free")
+```
+
+```{r ggridges, fig.width=16, fig.height=18}
+# library(ggridges)
 # Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   # filter(linenumber_new == "1") %>%
-#   ggplot(aes(x= cycle_drugname, y= mean_RDI_per_drug))+
-#   geom_violin(aes(color=mean_RDI_per_drug<0.85))+
-#   ylim(c(-.25, 2.5))+
-#   scale_colour_discrete(name=NULL, labels=c(">=0.85", "<0.85"))+
-#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
-#   theme_minimal()
-
-```
-</div>
-</div>
-
-```{r}
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug))+
-#   geom_violin()+
-#   # ylim(c(-.25, 2.5))+
-#   theme_minimal(base_size = 14)+
-#   facet_wrap(.~ drugname, ncol = 2, scales = "free_y")
-
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(x= drugname, fill = RDI_grp))+
-#   geom_bar(position = position_dodge())+
-#   theme_minimal(base_size = 14)+
-#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
-#   coord_flip()
-
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   # filter(linenumber_new == "1") %>%
-#   ggplot(aes(x= chemotherapy_type, y= mean_RDI_per_drug, color = chemotherapy_type))+
-#   geom_violin()+
-#   ylim(c(-.25, 3.5))+
-#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
-#   theme_minimal(base_size = 14)+
-#   coord_flip()+
-#   facet_wrap(drugname ~ RDI_grp, ncol = 2)
-
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= drugname, fill = RDI_grp))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  facet_wrap(.~ therapy)+
-  coord_flip()
-```
-
-### By Population
-```{r, fig.width=12, fig.height=20}
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= raceeth, y= mean_RDI_per_drug#, alpha = mean_RDI_per_drug<0.85
-             ))+
-  geom_boxplot(aes(fill = drugname))+
-  ylim(c(0, 2))+
-  scale_colour_discrete()+
-  # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
-  theme_minimal(base_size = 14)+
-  facet_wrap(drugname ~ therapy, ncol = 2, scales = "free")
-```
-
-```{r ggridges, fig.width=16, fig.height=18}
-library(ggridges)
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(y=raceeth, x=mean_RDI_per_drug,  fill=raceeth
-             )) +
-    geom_density_ridges(alpha=0.5) +
-    theme_ridges()+
-  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
-        panel.spacing = unit(0.1, "lines"),
-        strip.text.x = element_text(size = 14)
-    ) +
-  geom_vline(xintercept = 1, color = "red", linetype = 2)+
-
-  facet_wrap(therapy ~ drugname, ncol = 2, scales = "free_x")
+#   ggplot(aes(y=raceeth, x=mean_RDI_per_drug,  fill=raceeth
+#              )) +
+#     geom_density_ridges(alpha=0.5) +
+#     theme_ridges()+
+#   theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
+#         panel.spacing = unit(0.1, "lines"),
+#         strip.text.x = element_text(size = 14)
+#     ) +
+#   geom_vline(xintercept = 1, color = "red", linetype = 2)+
+#   
+#   facet_wrap(therapy ~ drugname, ncol = 2, scales = "free_x")
 ```
@@
 # Treatment & demo
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & 
-                               # chemotherapy_type == "Adjuvant" & 
-                               therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
+tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(RDI_carbo_neo, RDI_carbo_neo_grp)) %>%
   tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+              label = list(RDI_carbo_neo ~ "RDI")) %>%
   bold_labels()
 
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & 
-                               # chemotherapy_type == "Adjuvant" & 
-                               therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
+tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(RDI_carbo_adj, RDI_carbo_adj_grp)) %>%
   tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+              label = list(RDI_carbo_adj ~ "RDI")) %>%
   bold_labels()
 
-# tbl3 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-
-# tbl4 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-# 
-# tbl5 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-# 
-# tbl6 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(
-#               type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-
-tbl_stack(list(tbl1, tbl2),
+tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(RDI_carbo_adj, RDI_carbo_adj_grp)) %>%
+  tbl_summary(
+              label = list(RDI_carbo_adj ~ "RDI")) %>%
+  bold_labels()
+
+tbl_stack(list(tbl1, tbl2, tbl3),
           group_header = c(
-                           "carboplatin/Upfront Surgery", 
-                           "carboplatin/Upfront Chemo"),
+                           "carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery"),
           quiet = TRUE)
@@
 ```{r Table summary Taxanes}
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & 
-                               # chemotherapy_type == "Adjuvant" & 
-                               therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
+tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
+  tbl_summary() %>%
+  bold_labels()
+
+tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
+  tbl_summary() %>%
+  bold_labels()
+
+tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
+  tbl_summary() %>%
+  bold_labels()
+
+####
+# tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo" &
+#                                dose_dense == 3) %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
+#   tbl_summary() %>%
+#   bold_labels()
+
+# tbl5 <- Frontline %>% filter(therapy == "Upfront Chemo" &
+#                                dose_dense == 3) %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
+#   tbl_summary() %>%
+#   bold_labels()
+tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery" &
+                               dose_dense == 3) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
   tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
+              type = list(RDI ~ "continuous")) %>%
   bold_labels()
 
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & 
-                               # chemotherapy_type == "Adjuvant" & 
-                               therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-
-# tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-
-# tbl4 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-# tbl5 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-# tbl6 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-
-# tbl7 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-# tbl8 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-# tbl9 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(#type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels()
-
-####
-tbl3 <- Frontline %>% filter(drugname == "paclitaxel" & 
-                               therapy == "Upfront Surgery" &
-                               dose_dense == 3) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-
-tbl4 <- Frontline %>% filter(drugname == "paclitaxel" & 
-                               therapy == "Upfront Chemo" &
-                               dose_dense == 3) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels()
-
-tbl5 <- tbl_merge(list(tbl1, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))
-tbl6 <- tbl_merge(list(tbl2, tbl4))
-
-tbl_stack(list(tbl5, tbl6),
+# tbl7 <- tbl_merge(list(tbl1, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))
+# tbl8 <- tbl_merge(list(tbl2, tbl4))
+# tbl9 <- tbl_merge(list(tbl3, tbl6), tab_spanner = c("Overall", "Dose dense 1+3"))
+
+tbl_stack(list(tbl1, tbl2, tbl3, tbl6),
           group_header = c(
-                           "paclitaxel/Upfront Surgery", 
-                           "paclitaxel/Upfront Chemo"),
+                           "paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery",
+                           "dose dense paclitaxel Adj/Upfront Surgery"),
           quiet = TRUE)
@@
 <br>
-
-<span style="color:green">**Taxanes dose dense**</span>
 
@@
 ```{r Table4 summary Platin}
-# Treatment & demo
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl3 <-
+tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
+  tbl_summary(by = raceeth) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
+  tbl_summary(by = bmi_cat) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+
+tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
+  tbl_summary(by = raceeth) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
+  tbl_summary(by = bmi_cat) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+
+tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
+  tbl_summary(by = raceeth) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
+  tbl_summary(by = bmi_cat) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+
+tbl7 <-
   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl4 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-# tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl5 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-# tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth,  "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat,  "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl6 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl7 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl8 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl3, tbl4),
+tbl8 <-
+  tbl_merge(list(tbl3, tbl4))
+tbl9 <-
+  tbl_merge(list(tbl6, tbl6))
+
+tbl_stack(list(tbl7, tbl8, tbl9),
           group_header = c(
-                           "carboplatin/Upfront Surgery", 
-                           "carboplatin/Upfront Chemo"),
+                           "carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery"),
           quiet = TRUE)
@@
 ```{r Table4 summary Taxanes}
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl3 <-
+tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
+  tbl_summary(by = raceeth) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
+  tbl_summary(by = bmi_cat) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+
+tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
+  tbl_summary(by = raceeth) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
+  tbl_summary(by = bmi_cat) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+
+tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
+  tbl_summary(by = raceeth) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
+  tbl_summary(by = bmi_cat) %>%
+  bold_labels() %>% 
+  add_p() %>% bold_p(t= 0.05)
+
+tbl7 <-
   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = raceeth,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-  tbl_summary(by = bmi_cat,
-              label = list(mean_RDI_per_drug ~ "RDI")) %>%
-  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-tbl4 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-# tbl1 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(drugname == "paclitaxel" & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl5 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-# tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl6 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl7 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl8 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl9 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl10 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-# 
-# tbl1 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(raceeth, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = raceeth,
-#               # type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl2 <- Frontline %>% filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(bmi_cat, "mean_RDI_per_drug", RDI_grp)) %>%
-#   tbl_summary(by = bmi_cat,
-#               # type = list(mean_RDI_per_drug ~ 'continuous'),
-#               label = list(mean_RDI_per_drug ~ "RDI")) %>%
-#   bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-# tbl11 <-
-#   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-
-tbl_stack(list(tbl3, tbl4),
+tbl8 <-
+  tbl_merge(list(tbl3, tbl4))
+tbl9 <-
+  tbl_merge(list(tbl6, tbl6))
+
+tbl_stack(list(tbl7, tbl8, tbl9),
           group_header = c(
-                           "paclitaxel/Upfront Surgery", 
-                           "paclitaxel/Upfront Chemo"),
+                           "paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery"),
           quiet = TRUE)
@@
 ```{r OS dx RDI, fig.height = 7}
-# OS by RDI_grp
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, data=Frontline %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                      ),
-#            title = "OS from diagnosis Overall RDI",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-# 
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-
-# OS by RDI_grp for platin
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
-#                    data=Frontline %>% 
-#                      filter(str_detect(drugname, "carboplatin") & 
-#                               chemotherapy_type == "Neoadjuvant") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis carboplatin \nNeo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-
-# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
-#                    data=Frontline %>% 
-#                      filter(drugname == "paclitaxel" & 
-#                               chemotherapy_type == "Neoadjuvant") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis paclitaxel \nNeo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_carbo_neo_grp, 
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                             therapy == "Upfront Surgery") %>%
+                     filter(therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis carboplatin \nUpfront Surgery",
+           title = "OS from diagnosis carboplatin \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              therapy == "Upfront Surgery") %>%
+                     filter(therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis paclitaxel \nUpfront Surgery",
+           title = "OS from diagnosis carboplatin \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                              therapy == "Upfront Chemo") %>%
+                     filter(therapy == "Upfront Surgery") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from diagnosis carboplatin \nUpfront Chemo",
+           title = "OS from diagnosis carboplatin \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_pacli_neo_grp, 
                    data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              therapy == "Upfront Chemo") %>%
+                     filter(therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
@@
 ) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
-
-<div class = "col-md-6">
-```{r OS treatment RDI, fig.height = 7}
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-#                    data=Frontline %>% 
-#                      filter(str_detect(drugname, "carboplatin") & 
-#                               chemotherapy_type == "Neoadjuvant") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from first treatment carboplatin \nNeo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
-#                    data=Frontline %>% 
-#                      filter(drugname == "paclitaxel" & 
-#                               chemotherapy_type == "Neoadjuvant") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from first treatment paclitaxel \nNeo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_pacli_adj_grp, 
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                              therapy == "Upfront Surgery") %>%
+                     filter(therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from first treatment carboplatin \nUpfront Surgery",
+           title = "OS from diagnosis paclitaxel \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_pacli_adj_grp, 
                    data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              therapy == "Upfront Surgery") %>%
+                     filter(therapy == "Upfront Surgery") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from first treatment paclitaxel \nUpfront Surgery",
+           title = "OS from diagnosis paclitaxel \nUpfront Surgery",
            font.main = c(24, "bold", "black"),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+```
+</div>
+
+<div class = "col-md-6">
+```{r OS treatment RDI, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_carbo_neo_grp, 
                    data=Frontline %>% 
-                     filter(str_detect(drugname, "carboplatin") & 
-                              therapy == "Upfront Chemo") %>%
+                     filter(therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from first treatment carboplatin \nUpfront Chemo",
+           title = "OS from diagnosis carboplatin \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
-                     filter(drugname == "paclitaxel" & 
-                              therapy == "Upfront Chemo") %>%
+                     filter(therapy == "Upfront Chemo") %>%
                      distinct(patientid, .keep_all = TRUE)
                    ),
-           title = "OS from first treatment paclitaxel \nUpfront Chemo",
+           title = "OS from diagnosis carboplatin \nUpfront Chemo",
            font.main = c(24, "bold", "black"),
@@
 ) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_carbo_adj_grp, 
+                   data=Frontline %>% 
+                     filter(therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis carboplatin \nUpfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_pacli_neo_grp, 
+                   data=Frontline %>% 
+                     filter(therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis paclitaxel \nUpfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_pacli_adj_grp, 
+                   data=Frontline %>% 
+                     filter(therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis paclitaxel \nUpfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_pacli_adj_grp, 
+                   data=Frontline %>% 
+                     filter(therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from diagnosis paclitaxel \nUpfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
 ```
@@
 ```{r Table 5 HR}
-# Carbo
-# tbl1 <- Frontline %>%
-#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-# tbl1 <- tbl1 %>%
-#   select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
-#   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
 tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
+  filter(therapy == "Upfront Chemo")
+tbl1 <- tbl2 %>%
+  select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
+  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
+  filter(therapy == "Upfront Surgery")
 tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
+  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
   bold_labels() %>%
@@
 # Pacli
-# tbl7 <- Frontline %>%
-#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-# tbl7 <- tbl7 %>%
-#   select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
-#   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
-tbl8 <- tbl8 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- tbl2 %>%
+  select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl9 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
-tbl9 <- tbl9 %>%
-  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- tbl2 %>%
+  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl_stack(list(tbl8, tbl9),
-          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- tbl3 %>%
+  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel/Upfront Chemo", 
+                           "paclitaxel/Upfront Chemo",
+                           "paclitaxel/Upfront Surgery")) %>%
   bold_labels() %>%
@@
 ```
+In univariable analysis, higher RDI (continuous) of carboplatin in an Adjuvant / Upfront Chemo setting show a worse outcome which is not seen in the categorical variable.  
+A trend is observed toward a better survival with higher RDI (continuous) of paclitaxel in an Neoadjuvant / Upfront Chemo.
+In the contrary, lower RDI (categorical) of paclitaxel in an Adjuvant / Upfront Surgery shows a 51% increase risk of death when underdosed p = 0.091.
+
 <br>
@@
 ```{r Table 5 HR adjusted rdi group}
-# Carbo
-# tbl1 <- Frontline %>%
-#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-# tbl1 <- 
-#   coxph(Surv(time = tbl1$month_at_os_from_treatment, 
-#              event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl1) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
 tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- 
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
+  filter(therapy == "Upfront Surgery")
 tbl3 <- 
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
   bold_labels() %>%
@@
 # Pacli
-# tbl7 <- Frontline %>%
-#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-# tbl7 <- 
-#   coxph(Surv(time = tbl7$month_at_os_from_treatment, 
-#              event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl7) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
-tbl8 <- 
-  coxph(Surv(time = tbl8$month_at_os_from_treatment, 
-             event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl8) %>%
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl9 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
-tbl9 <- 
-  coxph(Surv(time = tbl9$month_at_os_from_treatment, 
-             event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl9) %>%
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl8, tbl9),
-          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
   bold_labels() %>%
@@
 ```
+In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival.
+
 <br>
@@
 ```{r rdi continous}
-# Carbo
-# tbl1 <- Frontline %>%
-#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-# tbl1 <- 
-#   coxph(Surv(time = tbl1$month_at_os_from_treatment, 
-#              event = tbl1$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl1) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
 tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- 
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
+  filter(therapy == "Upfront Surgery")
 tbl3 <- 
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.  
+RDI for paclitaxel is not a factor associated with survival.
+
+<br>
+<br>
+
+## Adjusted by other drug
+### RDI group
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat` 
+```{r Table 5 HR adjusted rdi group adjusted by other drug}
+tbl2 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl_stack(list(tbl2, tbl3),
-          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
   bold_labels() %>%
   italicize_levels()
-
-# Pacli
-# tbl7 <- Frontline %>%
-#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-# tbl7 <- 
-#   coxph(Surv(time = tbl7$month_at_os_from_treatment, 
-#              event = tbl7$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl7) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
-tbl8 <- 
-  coxph(Surv(time = tbl8$month_at_os_from_treatment, 
-             event = tbl8$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl8) %>%
+```
+When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
+
+<br>
+<br>
+
+### Continous
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat` 
+```{r rdi continous adjusted by other drug}
+tbl2 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl9 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
-tbl9 <- 
-  coxph(Surv(time = tbl9$month_at_os_from_treatment, 
-             event = tbl9$vitalstatus) ~ mean_RDI_per_drug + raceeth + ageatdx + stagecat, data =  tbl9) %>%
+tbl3 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl8, tbl9),
-          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
   bold_labels() %>%
@@
 ```
-<br>
-<br>
-
-## Adjusted by other drug
-### RDI group
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + raceeth + ageatdx + stagecat` 
-```{r Table 5 HR adjusted rdi group adjusted by other drug}
-
-tbl2 <- Frontline_adjusted %>%
-  filter(therapy == "Upfront Surgery")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline_adjusted %>%
-  filter(therapy == "Upfront Chemo")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Surgery", "Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<br>
-<br>
-
-### Continous
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + raceeth + ageatdx + stagecat` 
-```{r rdi continous adjusted by other drug}
-
-tbl2 <- Frontline_adjusted %>%
-  filter(therapy == "Upfront Surgery")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline_adjusted %>%
-  filter(therapy == "Upfront Chemo")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Surgery", "Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
+Continuous RDI for carboplatin or paclitaxel are not factors associated with survival.
+
 <br>
@@
 
-As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed
-
-```{r echo=TRUE}
-# Highly underdosed: < 0.75
-# Underdosed: >= 0.75 to <0.85
-# Adequate dosing: >= 0.85 to <1.10
-# Overdosing: >=1.10
-```
-Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI)
-```{r, fig.width=12, fig.height=12}
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+
-  geom_point(alpha = 0.7, size = 0.75)+
-  theme_minimal(base_size = 10)+
-  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+
-  geom_jitter()+
-  theme_minimal(base_size = 10)+
-  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
-
-```
-Here I just wanted to see if we have more or less underdosing / overdosing with BMI
-```{r, fig.width=12, fig.height=12}
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= RDI_grp1, fill = drugname))+
-  geom_bar(position = position_dodge())+
-  theme_minimal(base_size = 10)+
-  facet_wrap(. ~ therapy, ncol = 2, scales = "free")+
-  coord_flip()
-```
-
-```{r, fig.width=12}
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(x= drugname, fill = RDI_grp1))+
-#   geom_bar(position = position_dodge())+
-#   theme_minimal(base_size = 10)+
-#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
-#   coord_flip()
-```
-
-```{r}
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= drugname, fill = RDI_grp1))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 10)+
-  coord_flip()+
-  facet_wrap(.~ therapy)
-```
-As you can see above in green, we have a lot of patient who are overdose.
-<br>
-<br>
-
-## Hazard Ratio RDI 2
-
-<span style="color:green">**Table HR**</span>
-
-### Univariable
-```{r HR RDI 2}
-# Carbo
-# tbl1 <- Frontline %>%
-#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-# tbl1 <- tbl1 %>%
-#   select(vitalstatus, RDI_grp1) %>% 
-#   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
-tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
-tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-# tbl7 <- Frontline %>%
-#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-# tbl7 <- tbl7 %>%
-#   select(vitalstatus, RDI_grp1) %>% 
-#   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
-tbl8 <- tbl8 %>%
-  select(vitalstatus, RDI_grp1) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl9 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
-tbl9 <- tbl9 %>%
-  select(vitalstatus, RDI_grp1) %>%
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%
-  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
-tbl_stack(list(tbl8, tbl9),
-          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference.
-
-### Multivariable
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp1 + raceeth + ageatdx + stagecat` 
-```{r}
-# Carbo
-# tbl1 <- Frontline %>%
-#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-# tbl1 <- 
-#   coxph(Surv(time = tbl1$month_at_os_from_treatment, 
-#              event = tbl1$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl1) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl2 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-# tbl7 <- Frontline %>%
-#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-# tbl7 <- 
-#   coxph(Surv(time = tbl7$month_at_os_from_treatment, 
-#              event = tbl7$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl7) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl8 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
-tbl8 <- 
-  coxph(Surv(time = tbl8$month_at_os_from_treatment, 
-             event = tbl8$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl8) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl9 <- Frontline %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
-tbl9 <- 
-  coxph(Surv(time = tbl9$month_at_os_from_treatment, 
-             event = tbl9$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl9) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl8, tbl9),
-          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<br>
-<br>
-
-## Adjusted by other drug
-### RDI group
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` 
-```{r Table 5 HR adjusted rdi group adjusted by other drug 2}
-tbl2 <- Frontline_adjusted %>%
-  filter(therapy == "Upfront Surgery")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline_adjusted %>%
-  filter(therapy == "Upfront Chemo")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Surgery", "Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<br>
-<br>
+<!-- As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed -->
+
+<!-- ```{r echo=TRUE} -->
+<!-- # Highly underdosed: < 0.75 -->
+<!-- # Underdosed: >= 0.75 to <0.85 -->
+<!-- # Adequate dosing: >= 0.85 to <1.10 -->
+<!-- # Overdosing: >=1.10 -->
+<!-- ``` -->
+<!-- Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI) -->
+<!-- ```{r, fig.width=12, fig.height=12} -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!--   ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
+<!--   geom_point(alpha = 0.7, size = 0.75)+ -->
+<!--   theme_minimal(base_size = 10)+ -->
+<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!--   ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
+<!--   geom_jitter()+ -->
+<!--   theme_minimal(base_size = 10)+ -->
+<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
+
+<!-- ``` -->
+<!-- Here I just wanted to see if we have more or less underdosing / overdosing with BMI -->
+<!-- ```{r, fig.width=12, fig.height=12} -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!--   ggplot(aes(x= RDI_grp1, fill = drugname))+ -->
+<!--   geom_bar(position = position_dodge())+ -->
+<!--   theme_minimal(base_size = 10)+ -->
+<!--   facet_wrap(. ~ therapy, ncol = 2, scales = "free")+ -->
+<!--   coord_flip() -->
+<!-- ``` -->
+
+<!-- ```{r, fig.width=12} -->
+<!-- # Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!-- #   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
+<!-- #   geom_bar(position = position_dodge())+ -->
+<!-- #   theme_minimal(base_size = 10)+ -->
+<!-- #   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+ -->
+<!-- #   coord_flip() -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!--   # filter(linenumber_new == "1") %>% -->
+<!--   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
+<!--   geom_bar(position = "fill")+ -->
+<!--   theme_minimal(base_size = 10)+ -->
+<!--   coord_flip()+ -->
+<!--   facet_wrap(.~ therapy) -->
+<!-- ``` -->
+<!-- As you can see above in green, we have a lot of patient who are overdose. -->
+<!-- <br> -->
+<!-- <br> -->
+
+<!-- ## Hazard Ratio RDI 2 -->
+
+<!-- <span style="color:green">**Table HR**</span>   -->
+
+<!-- ### Univariable -->
+<!-- ```{r HR RDI 2} -->
+<!-- # Carbo -->
+<!-- # tbl1 <- Frontline %>% -->
+<!-- #   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") -->
+<!-- # tbl1 <- tbl1 %>% -->
+<!-- #   select(vitalstatus, RDI_grp1) %>%  -->
+<!-- #   tbl_uvregression(method = survival::coxph, -->
+<!-- #                  y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)), -->
+<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
+<!-- tbl2 <- Frontline %>% -->
+<!--   filter(drugname == "carboplatin" & therapy == "Upfront Surgery") -->
+<!-- tbl2 <- tbl2 %>% -->
+<!--   select(vitalstatus, RDI_grp1) %>%  -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl3 <- Frontline %>% -->
+<!--   filter(drugname == "carboplatin" & therapy == "Upfront Chemo") -->
+<!-- tbl3 <- tbl3 %>% -->
+<!--   select(vitalstatus, RDI_grp1) %>%  -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl2, tbl3), -->
+<!--           group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+
+<!-- # Pacli -->
+<!-- # tbl7 <- Frontline %>% -->
+<!-- #   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant") -->
+<!-- # tbl7 <- tbl7 %>% -->
+<!-- #   select(vitalstatus, RDI_grp1) %>%  -->
+<!-- #   tbl_uvregression(method = survival::coxph, -->
+<!-- #                  y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)), -->
+<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
+<!-- tbl8 <- Frontline %>% -->
+<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Surgery") -->
+<!-- tbl8 <- tbl8 %>% -->
+<!--   select(vitalstatus, RDI_grp1) %>% -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% -->
+<!--   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**")) -->
+<!-- tbl9 <- Frontline %>% -->
+<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Chemo") -->
+<!-- tbl9 <- tbl9 %>% -->
+<!--   select(vitalstatus, RDI_grp1) %>% -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% -->
+<!--   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**")) -->
+<!-- tbl_stack(list(tbl8, tbl9), -->
+<!--           group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+<!-- ``` -->
+<!-- Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference. -->
+
+<!-- ### Multivariable -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp1 + raceeth + ageatdx + stagecat`  -->
+<!-- ```{r} -->
+<!-- # Carbo -->
+<!-- # tbl1 <- Frontline %>% -->
+<!-- #   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") -->
+<!-- # tbl1 <-  -->
+<!-- #   coxph(Surv(time = tbl1$month_at_os_from_treatment,  -->
+<!-- #              event = tbl1$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl1) %>% -->
+<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
+
+<!-- tbl2 <- Frontline %>% -->
+<!--   filter(drugname == "carboplatin" & therapy == "Upfront Surgery") -->
+<!-- tbl2 <-  -->
+<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
+<!--              event = tbl2$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl3 <- Frontline %>% -->
+<!--   filter(drugname == "carboplatin" & therapy == "Upfront Chemo") -->
+<!-- tbl3 <-  -->
+<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
+<!--              event = tbl3$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl2, tbl3), -->
+<!--           group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+
+<!-- # Pacli -->
+<!-- # tbl7 <- Frontline %>% -->
+<!-- #   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant") -->
+<!-- # tbl7 <-  -->
+<!-- #   coxph(Surv(time = tbl7$month_at_os_from_treatment,  -->
+<!-- #              event = tbl7$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl7) %>% -->
+<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
+<!-- tbl8 <- Frontline %>% -->
+<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Surgery") -->
+<!-- tbl8 <-  -->
+<!--   coxph(Surv(time = tbl8$month_at_os_from_treatment,  -->
+<!--              event = tbl8$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl8) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl9 <- Frontline %>% -->
+<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Chemo") -->
+<!-- tbl9 <-  -->
+<!--   coxph(Surv(time = tbl9$month_at_os_from_treatment,  -->
+<!--              event = tbl9$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl9) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl8, tbl9), -->
+<!--           group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+<!-- ``` -->
+<!-- <br> -->
+<!-- <br> -->
+
+<!-- ## Adjusted by other drug -->
+<!-- ### RDI group -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat`  -->
+<!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug 2} -->
+<!-- tbl2 <- Frontline_adjusted %>% -->
+<!--   filter(therapy == "Upfront Surgery") -->
+<!-- tbl2 <-  -->
+<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
+<!--              event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl3 <- Frontline_adjusted %>% -->
+<!--   filter(therapy == "Upfront Chemo") -->
+<!-- tbl3 <-  -->
+<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
+<!--              event = tbl3$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl2, tbl3), -->
+<!--           group_header = c("Upfront Surgery", "Upfront Chemo")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+<!-- ``` -->
+<!-- <br> -->
+<!-- <br> -->
+
+<!-- *** -->
+
+<!-- # VI. Adjusted by **BMI at DX category** -->
+
+<!-- ```{r} -->
+<!-- Frontline_bmi <- Frontline %>% -->
+<!--   filter(!is.na(bmi_cat)) -->
+<!-- ``` -->
+
+<!-- ## Multivariable -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat`  -->
+<!-- ```{r bmi HR adjusted} -->
+<!-- # Carbo -->
+<!-- # tbl1 <- Frontline_bmi %>% -->
+<!-- #   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") -->
+<!-- # tbl1 <-  -->
+<!-- #   coxph(Surv(time = tbl1$month_at_os_from_treatment,  -->
+<!-- #              event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>% -->
+<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
+
+<!-- tbl2 <- Frontline_bmi %>% -->
+<!--   filter(drugname == "carboplatin" & therapy == "Upfront Surgery") -->
+<!-- tbl2 <-  -->
+<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
+<!--              event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl3 <- Frontline_bmi %>% -->
+<!--   filter(drugname == "carboplatin" & therapy == "Upfront Chemo") -->
+<!-- tbl3 <-  -->
+<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
+<!--              event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl2, tbl3), -->
+<!--           group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+
+<!-- # Pacli -->
+<!-- # tbl7 <- Frontline_bmi %>% -->
+<!-- #   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant") -->
+<!-- # tbl7 <-  -->
+<!-- #   coxph(Surv(time = tbl7$month_at_os_from_treatment,  -->
+<!-- #              event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>% -->
+<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
+<!-- tbl8 <- Frontline_bmi %>% -->
+<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Surgery") -->
+<!-- tbl8 <-  -->
+<!--   coxph(Surv(time = tbl8$month_at_os_from_treatment,  -->
+<!--              event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl9 <- Frontline_bmi %>% -->
+<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Chemo") -->
+<!-- tbl9 <-  -->
+<!--   coxph(Surv(time = tbl9$month_at_os_from_treatment,  -->
+<!--              event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl8, tbl9), -->
+<!--           group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+<!-- ``` -->
+<!-- <br> -->
+<!-- <br> -->
 
 ***
-
-# VI. Adjusted by **BMI at DX category**
-
-```{r}
-Frontline_bmi <- Frontline %>%
-  filter(!is.na(bmi_cat))
-```
-
-## Multivariable
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` 
-```{r bmi HR adjusted}
-# Carbo
-# tbl1 <- Frontline_bmi %>%
-#   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
-# tbl1 <- 
-#   coxph(Surv(time = tbl1$month_at_os_from_treatment, 
-#              event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-
-tbl2 <- Frontline_bmi %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Surgery")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline_bmi %>%
-  filter(drugname == "carboplatin" & therapy == "Upfront Chemo")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-# tbl7 <- Frontline_bmi %>%
-#   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
-# tbl7 <- 
-#   coxph(Surv(time = tbl7$month_at_os_from_treatment, 
-#              event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>%
-#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
-tbl8 <- Frontline_bmi %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Surgery")
-tbl8 <- 
-  coxph(Surv(time = tbl8$month_at_os_from_treatment, 
-             event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl9 <- Frontline_bmi %>%
-  filter(drugname =="paclitaxel" & therapy == "Upfront Chemo")
-tbl9 <- 
-  coxph(Surv(time = tbl9$month_at_os_from_treatment, 
-             event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl8, tbl9),
-          group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<br>
-<br>
-
-***

### 2021-12-03 Rmd/rdi analysis.Rmd
Update rmd

@@
 
+**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
+**We have `r drugs %>% distinct(patientid) %>% nrow()` patients info in clinical data.
+
 - Select episodedatasource == "Administrations"
@@
   arrange(patientid, episodedate)
+
+drugs %>% distinct(patientid) %>% nrow()
 ```
@@
 # rm(drugs, drugs1, therapy_line)
-```
+therapy_cycle %>% distinct(patientid) %>% nrow()
+```
+
+<br>
 
@@
   arrange(patientid, episodedate)
+
+Treatment1 %>% distinct(patientid) %>% nrow()
 ```
@@
 
+Treatment %>% distinct(patientid) %>% nrow()
 ```
@@
                                      "Overdosing")))
+Frontline %>% distinct(patientid) %>% nrow()
 ```
@@
 ```{r}
-drugs1 <- Frontline_adjusted %>% 
+flatiron_rec <- Frontline_adjusted %>% 
   mutate(flatiron_rules = case_when(
@@
 
-drugs1 <- drugs1 %>% 
+flatiron_rec <- flatiron_rec %>% 
   filter(is.na(flatiron_rules))
@@
 
-**At the end of the step 1, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
+**At the end of the step 1, we have `r flatiron_rec %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 ```{r}
-drugs1 <- drugs1 %>% 
+study_criteria <- flatiron_rec %>% 
   filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs
 
-drugs1 <- drugs1 %>%
+study_criteria <- study_criteria %>%
   filter(!is.na(surgerydate))
 
-drugs1 <- drugs1 %>%
+study_criteria <- study_criteria %>%
   filter(had_carbo_pacli == "Yes")
 
-drugs1 <- drugs1 %>% 
+study_criteria <- study_criteria %>% 
   filter(treatment_sequence == "neo + surg + adj" |
@@
 
-drugs1 <- drugs1 %>%
+study_criteria <- study_criteria %>%
   # Remove patients with other linename
@@
 
-**At the end of the step 2, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**
+**At the end of the step 2, we have `r study_criteria %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 ```{r}
-drugs11 <- drugs1 %>% 
+missing_data <- study_criteria %>% 
   filter(!(issurgery == "Yes" & is.na(surgerydate)))
 
-drugs11 <- drugs11 %>%
+missing_data <- missing_data %>%
   arrange(patientid, episodedate) %>%
@@
 
-drugs11 <- drugs11 %>% 
+missing_data <- missing_data %>% 
   filter(days_at_first_drug >= 0 &
@@
 
-drugs11 <- drugs11 %>% 
+missing_data <- missing_data %>% 
   # remove these patients who switched C > C 
@@
 ```
-**At the end of the step 3, we have `r drugs11 %>% distinct(patientid) %>% nrow()` patients.**
+**At the end of the step 3, we have `r missing_data %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 ```{r}
-drugs111 <- drugs11 %>% 
+standart_care <- missing_data %>% 
   # Remove patients with more than 1 line as Neo
@@
 
-drugs111 <- drugs111 %>% 
+standart_care <- standart_care %>% 
   filter(is.na(whole_frontline_is_maintenance))
 
-drugs111 <- drugs111 %>% 
+standart_care <- standart_care %>% 
   filter(is.na(too_many_cycle))
 ```
-**We have `r drugs111 %>% distinct(patientid) %>% nrow()` patients.**
+**We have `r standart_care %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 ```{r}
-Frontline <- drugs111 %>% 
+Frontline <- standart_care %>% 
   filter(is.na(wrong_pacli_dosedense))
 
-# drugs111 %>% 
+# standart_care %>% 
 #   mutate(n_dose_dense = factor(n_dose_dense)) %>% 
@@
 ```{r}
-# drugs11 %>% 
+# missing_data %>% 
 #   distinct(patientid, .keep_all = TRUE) %>% 
@@
 # 
-# # drugs11 %>% 
+# # missing_data %>% 
 # #   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
@@
 
-<!-- As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed -->
-
-<!-- ```{r echo=TRUE} -->
-<!-- # Highly underdosed: < 0.75 -->
-<!-- # Underdosed: >= 0.75 to <0.85 -->
-<!-- # Adequate dosing: >= 0.85 to <1.10 -->
-<!-- # Overdosing: >=1.10 -->
-<!-- ``` -->
-<!-- Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI) -->
-<!-- ```{r, fig.width=12, fig.height=12} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
-<!--   geom_point(alpha = 0.7, size = 0.75)+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
-<!--   geom_jitter()+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
-
-<!-- ``` -->
-<!-- Here I just wanted to see if we have more or less underdosing / overdosing with BMI -->
-<!-- ```{r, fig.width=12, fig.height=12} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   ggplot(aes(x= RDI_grp1, fill = drugname))+ -->
-<!--   geom_bar(position = position_dodge())+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   facet_wrap(. ~ therapy, ncol = 2, scales = "free")+ -->
-<!--   coord_flip() -->
-<!-- ``` -->
-
-<!-- ```{r, fig.width=12} -->
-<!-- # Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!-- #   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
-<!-- #   geom_bar(position = position_dodge())+ -->
-<!-- #   theme_minimal(base_size = 10)+ -->
-<!-- #   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+ -->
-<!-- #   coord_flip() -->
-<!-- ``` -->
+As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed
+
+```{r echo=TRUE}
+# Highly underdosed: < 0.75
+# Underdosed: >= 0.75 to <0.85
+# Adequate dosing: >= 0.85 to <1.10
+# Overdosing: >=1.10
+```
+Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI)
+```{r, fig.width=12, fig.height=12}
+Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+
+  geom_point(alpha = 0.7, size = 0.75)+
+  theme_minimal(base_size = 10)+
+  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
+Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+
+  geom_jitter()+
+  theme_minimal(base_size = 10)+
+  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
+
+```
+Here I just wanted to see if we have more or less underdosing / overdosing with BMI
+```{r, fig.width=12, fig.height=12}
+Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  ggplot(aes(x= RDI_grp1, fill = drugname))+
+  geom_bar(position = position_dodge())+
+  theme_minimal(base_size = 10)+
+  facet_wrap(. ~ therapy, ncol = 2, scales = "free")+
+  coord_flip()
+```
+
+```{r, fig.width=12}
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= drugname, fill = RDI_grp1))+
+#   geom_bar(position = position_dodge())+
+#   theme_minimal(base_size = 10)+
+#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
+#   coord_flip()
+```
+
+```{r}
+Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
+  # filter(linenumber_new == "1") %>%
+  ggplot(aes(x= drugname, fill = RDI_grp1))+
+  geom_bar(position = "fill")+
+  theme_minimal(base_size = 10)+
+  coord_flip()+
+  facet_wrap(.~ therapy)
+```
+As you can see above in green, we have a lot of patient who are overdose.
+<br>
+<br>
+
+## Hazard Ratio RDI 2
+
+<span style="color:green">**Table HR**</span>
+
+### Univariable
+```{r HR RDI 2}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- tbl2 %>%
+  select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- tbl2 %>%
+  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- tbl3 %>%
+  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- tbl2 %>%
+  select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- tbl2 %>%
+  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- tbl3 %>%
+  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel/Upfront Chemo", 
+                           "paclitaxel/Upfront Chemo",
+                           "paclitaxel/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference.
+
+### Multivariable
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp1 + raceeth + ageatdx + stagecat`
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
+## Adjusted by other drug
+### RDI group
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat`
+```{r Table 5 HR adjusted rdi group adjusted by other drug 2}
+tbl2 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline_adjusted %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
+***
+
+<!-- # VI. Adjusted by **BMI at DX category** -->
 
 <!-- ```{r} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   # filter(linenumber_new == "1") %>% -->
-<!--   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
-<!--   geom_bar(position = "fill")+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   coord_flip()+ -->
-<!--   facet_wrap(.~ therapy) -->
-<!-- ``` -->
-<!-- As you can see above in green, we have a lot of patient who are overdose. -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- ## Hazard Ratio RDI 2 -->
-
-<!-- <span style="color:green">**Table HR**</span>   -->
-
-<!-- ### Univariable -->
-<!-- ```{r HR RDI 2} -->
-<!-- # Carbo -->
-<!-- # tbl1 <- Frontline %>% -->
-<!-- #   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") -->
-<!-- # tbl1 <- tbl1 %>% -->
-<!-- #   select(vitalstatus, RDI_grp1) %>%  -->
-<!-- #   tbl_uvregression(method = survival::coxph, -->
-<!-- #                  y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)), -->
-<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(drugname == "carboplatin" & therapy == "Upfront Surgery") -->
-<!-- tbl2 <- tbl2 %>% -->
-<!--   select(vitalstatus, RDI_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(drugname == "carboplatin" & therapy == "Upfront Chemo") -->
-<!-- tbl3 <- tbl3 %>% -->
-<!--   select(vitalstatus, RDI_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-<!-- # tbl7 <- Frontline %>% -->
-<!-- #   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant") -->
-<!-- # tbl7 <- tbl7 %>% -->
-<!-- #   select(vitalstatus, RDI_grp1) %>%  -->
-<!-- #   tbl_uvregression(method = survival::coxph, -->
-<!-- #                  y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)), -->
-<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
-<!-- tbl8 <- Frontline %>% -->
-<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Surgery") -->
-<!-- tbl8 <- tbl8 %>% -->
-<!--   select(vitalstatus, RDI_grp1) %>% -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% -->
-<!--   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**")) -->
-<!-- tbl9 <- Frontline %>% -->
-<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Chemo") -->
-<!-- tbl9 <- tbl9 %>% -->
-<!--   select(vitalstatus, RDI_grp1) %>% -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% -->
-<!--   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**")) -->
-<!-- tbl_stack(list(tbl8, tbl9), -->
-<!--           group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference. -->
-
-<!-- ### Multivariable -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp1 + raceeth + ageatdx + stagecat`  -->
-<!-- ```{r} -->
-<!-- # Carbo -->
-<!-- # tbl1 <- Frontline %>% -->
-<!-- #   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") -->
-<!-- # tbl1 <-  -->
-<!-- #   coxph(Surv(time = tbl1$month_at_os_from_treatment,  -->
-<!-- #              event = tbl1$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl1) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(drugname == "carboplatin" & therapy == "Upfront Surgery") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(drugname == "carboplatin" & therapy == "Upfront Chemo") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-<!-- # tbl7 <- Frontline %>% -->
-<!-- #   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant") -->
-<!-- # tbl7 <-  -->
-<!-- #   coxph(Surv(time = tbl7$month_at_os_from_treatment,  -->
-<!-- #              event = tbl7$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl7) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
-<!-- tbl8 <- Frontline %>% -->
-<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Surgery") -->
-<!-- tbl8 <-  -->
-<!--   coxph(Surv(time = tbl8$month_at_os_from_treatment,  -->
-<!--              event = tbl8$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl8) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl9 <- Frontline %>% -->
-<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Chemo") -->
-<!-- tbl9 <-  -->
-<!--   coxph(Surv(time = tbl9$month_at_os_from_treatment,  -->
-<!--              event = tbl9$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl9) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl8, tbl9), -->
-<!--           group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- ## Adjusted by other drug -->
-<!-- ### RDI group -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat`  -->
-<!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug 2} -->
-<!-- tbl2 <- Frontline_adjusted %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline_adjusted %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("Upfront Surgery", "Upfront Chemo")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- *** -->
-
-<!-- # VI. Adjusted by **BMI at DX category** -->
-
-<!-- ```{r} -->
-<!-- Frontline_bmi <- Frontline %>% -->
+<!-- Frontline_bmi <- Frontline_adjusted %>% -->
 <!--   filter(!is.na(bmi_cat)) -->

### 2021-12-03 Rmd/rdi analysis.Rmd
Fix bug and update

@@
   # 5.Redefine line number based on the original linenumber variable and the surgery date----
-  mutate(linenumber_new = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird
+  mutate(linenumber_n = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  
+  group_by(patientid, linenumber_n, ismaintenancetherapy) %>% 
+  mutate(maint_rank = row_number(ismaintenancetherapy),
+         maint_rank = ifelse(maint_rank == 1, 1, 0)) %>%
+
+  group_by(patientid) %>% 
+  mutate(linenumber_new = cumsum(maint_rank)) %>%  
+  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird F0F1324B863A8
   select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
@@
            duration(n=1, units = "days")) %>% 
+  mutate(days_at_first_treatment = case_when(
+    therapy == "Upfront Chemo" |
+      therapy == "Chemotherapy only"             ~ interval(start = diagnosisdate, end = first_drug_date)/
+           duration(n=1, units = "days"),
+    therapy == "Upfront Surgery" |
+      therapy == "Surgery Only"                  ~ interval(start = diagnosisdate, end = surgerydate)/
+           duration(n=1, units = "days")
+  )) %>% 
   ungroup() %>% 
@@
   fill(wrong_pacli_dosedense, .direction = "updown") %>% 
+  ungroup() %>% 
+  mutate(switch_drugs = case_when(
+    str_detect(linename, "Pacli") & 
+      drugname == "docetaxel" & 
+      linenumber_adj == 1                      ~ "exclude",
+    str_detect(linename, "Car") & 
+      drugname == "cisplatin" & 
+      linenumber_adj == 1                      ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(switch_drugs, .direction = "updown") %>% 
+  ungroup() %>%
+
+  mutate(line_keep = case_when(# F002B429BE6C6
+    (linenumber_adj == 1 &
+           (linename == "Carboplatin,Paclitaxel" |
+           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
+           linename == "Carboplatin" |
+           linename == "Paclitaxel" |
+           linename == "Bevacizumab,Paclitaxel" |
+           linename == "Bevacizumab,Carboplatin"))            ~ "include"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(line_keep, .direction = "updown") %>% 
+  ungroup() %>% 
+  mutate(flatiron_rules = case_when(
+    days_at_first_treatment > 90                          ~ "exclude",
+    thirty_days_exclusion <= 30                  ~ "exclude",
+    exclude == "1"                               ~ "exclude"
+  )) %>%
+  group_by(patientid) %>% 
+  fill(flatiron_rules, .direction = "downup") %>% 
   ungroup()
@@
 ```{r RDI calculation}
-Frontline <- Treatment %>% 
+RDI_data <- Treatment %>% 
   # filter(chemotherapy_type == "Neoadjuvant" |
@@
 ```{r RDI calculation group}
-Frontline <- Frontline %>% 
+RDI_data <- RDI_data %>% 
   # general
@@
                                      "Overdosing")))
-Frontline %>% distinct(patientid) %>% nrow()
+RDI_data %>% distinct(patientid) %>% nrow()
 ```
@@
 ```{r Frontline_adjusted}
-Frontline_adjusted <- Frontline %>% 
+Frontline_adjusted <- RDI_data %>% 
   group_by(patientid) %>% 
@@
        .direction = "downup") %>% 
+  ungroup() %>% 
   distinct(patientid, .keep_all = TRUE)
@@
 flatiron_rec <- Frontline_adjusted %>% 
-  mutate(flatiron_rules = case_when(
-    days_at_first_drug > 90 | 
-      days_at_surg > 90                          ~ "exclude",
-    thirty_days_exclusion <= 30                  ~ "exclude",
-    exclude == "1"                               ~ "exclude"
-  )) %>%
-  group_by(patientid) %>% 
-  fill(flatiron_rules, .direction = "downup") %>% 
-  ungroup()
-
-flatiron_rec <- flatiron_rec %>% 
   filter(is.na(flatiron_rules))
@@
 study_criteria <- flatiron_rec %>% 
-  filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs
+  filter(!is.na(histology))
 
@@
 study_criteria <- study_criteria %>%
+  filter(line_keep == "include")
   # Remove patients with other linename
-  filter((linenumber_new == 1 &
-           (linename == "Carboplatin,Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
-           linename == "Carboplatin" |
-           linename == "Paclitaxel" |
-           linename == "Bevacizumab,Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin")) |
-          (linenumber_new == 2 &
-          therapy == "Upfront Chemo" &
-           (linename == "Carboplatin,Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
-           linename == "Carboplatin" |
-           linename == "Bevacizumab,Paclitaxel" |
-           linename == "Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin"))
-         )
+  # filter((linenumber_new == 1 &
+  #          (linename == "Carboplatin,Paclitaxel" |
+  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
+  #          linename == "Carboplatin" |
+  #          linename == "Paclitaxel" |
+  #          linename == "Bevacizumab,Paclitaxel" |
+  #          linename == "Bevacizumab,Carboplatin")) |
+  #         (linenumber_new == 2 &
+  #         therapy == "Upfront Chemo" &
+  #          (linename == "Carboplatin,Paclitaxel" |
+  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
+  #          linename == "Carboplatin" |
+  #          linename == "Bevacizumab,Paclitaxel" |
+  #          linename == "Paclitaxel" |
+  #          linename == "Bevacizumab,Carboplatin"))
+  #        )
 ```
@@
 
-test <- Frontline %>% 
-  filter(wrong_pacli_dosedense == "exclude")
-
-wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
-  filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
-  select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
+# test <- Frontline %>% 
+#   filter(wrong_pacli_dosedense == "exclude")
+# 
+# wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
+#   filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
+#   select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
 ```
@@
 
-`r Frontline %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.  
-`r Frontline %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.
+<!-- `r Frontline %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.
+-->
+<!-- `r Frontline %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.
+-->
 
@@
 
-`r Frontline %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.
+<!-- `r Frontline %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.
+-->
 <!-- I am removing these patients   -->
@@
 ```{r}
-# remove_switch1 <- therapy_line %>% 
-#   filter(
-#     str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1
-#   ) %>%
-#   distinct(patientid)
-# remove_switch1 <- paste(remove_switch1$patientid, collapse = "|")
-# 
-# therapy_line <- therapy_line %>% 
-#   # remove these patients who switched C > C 
-#   filter(!str_detect(patientid, remove_switch1))
-# therapy_line %>% distinct(patientid) %>% nrow()
+Frontline <- Frontline %>%
+  filter(is.na(switch_drugs))
 ```
@@
 
-## **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
+# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
 
@@
 ```{r}
+RDI_data <- 
   Treatment %>% 
+  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
+  arrange(patientid, episodedate, drugname)
+
+RDI_data %>% 
   filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
@@
   tbl_summary()
-Treatment %>% 
+RDI_data %>% 
   filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
@@
 ```{r}
-Treatment %>% 
+RDI_data %>% 
   filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
@@
 
-Treatment %>% 
+RDI_data %>% 
   filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
@@
 
-Treatment %>% 
+RDI_data %>% 
   filter(therapy == "Upfront Chemo") %>% 
@@
 ```{r}
-Treatment %>% 
+RDI_data %>% 
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
@@
 
-Treatment %>% 
+RDI_data %>% 
   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
@@
 ```{r Table 5 HR adjusted rdi group adjusted by other drug}
-tbl2 <- Frontline_adjusted %>%
+tbl2 <- Frontline %>%
   filter(therapy == "Upfront Chemo")
@@
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline_adjusted %>%
+tbl3 <- Frontline %>%
   filter(therapy == "Upfront Surgery")
@@
 ```{r rdi continous adjusted by other drug}
-tbl2 <- Frontline_adjusted %>%
+tbl2 <- Frontline %>%
   filter(therapy == "Upfront Chemo")
@@
 ```{r, fig.width=12, fig.height=12}
-Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
   ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+
@@
   facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
-Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
   ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+
@@
 ```{r, fig.width=12, fig.height=12}
-Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
   ggplot(aes(x= RDI_grp1, fill = drugname))+
@@
 ```{r}
-Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
+Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
   # filter(linenumber_new == "1") %>%
@@
 ```{r Table 5 HR adjusted rdi group adjusted by other drug 2}
-tbl2 <- Frontline_adjusted %>%
+tbl2 <- Frontline %>%
   filter(therapy == "Upfront Chemo")
@@
 <!-- ```{r} -->
-<!-- Frontline_bmi <- Frontline_adjusted %>% -->
+<!-- Frontline_bmi <- Frontline %>% -->
 <!--   filter(!is.na(bmi_cat)) -->

### 2021-12-07 Rmd/rdi analysis.Rmd
Update and remove more precise rdi

@@
 ```{r rdi plots, fig.height=10, fig.height=9}
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(x= drugname))+
-#   geom_bar()+
-#   theme_minimal(base_size = 14)+
-#   coord_flip()+
+Frontline %>% 
+  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
+  filter(!is.na(value)) %>% 
+  ggplot(aes(x= name))+
+  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
+  theme_minimal(base_size = 14)+
+  coord_flip()
   # facet_wrap(. ~ therapy)
-# 
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
-#   geom_boxplot()+
-#   # ylim(c(-.25, 3.5))+
-#   geom_jitter(shape=16)+
-#   labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
-#   theme_minimal(base_size = 14)+
-#   facet_wrap(.~ drugname, ncol = 2)
+
+Frontline %>% 
+  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
+  filter(!is.na(value)) %>% 
+  ggplot(aes(x= name, y= value))+
+  geom_boxplot()+
+  # ylim(c(-.25, 3.5))+
+  geom_jitter(shape=16)+
+  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
+  theme_minimal(base_size = 14)+
+  coord_flip()+
+  facet_wrap(.~ therapy, ncol = 2)
 ```
@@
 ```{r, fig.height=10, fig.height=9}
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(x= drugname, fill= RDI_grp))+
-#   geom_bar(position = "fill")+
+# Frontline %>% 
+#   select(patientid, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj,
+#          RDI_carbo_neo_grp, RDI_pacli_neo_grp, RDI_carbo_adj_grp, RDI_pacli_adj_grp) %>% 
+#   pivot_longer(cols = -patientid, names_to = c("RDI", "group"), names_prefix = "_grp")
+#   filter(!is.na(value)) %>% 
+#   ggplot(aes(x= name))+
+#   geom_bar(aes(fill = therapy, alpha = RDI_grp), position = position_dodge(preserve = "single"))+
 #   theme_minimal(base_size = 14)+
-#   coord_flip()+
-#   facet_wrap(. ~ therapy)
+  # coord_flip()
 # 
@@
 ```{r, fig.width=12, fig.height=20}
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   # filter(linenumber_new == "1") %>%
-#   ggplot(aes(x= raceeth, y= mean_RDI_per_drug#, alpha = mean_RDI_per_drug<0.85
-#              ))+
-#   geom_boxplot(aes(fill = drugname))+
-#   ylim(c(0, 2))+
-#   scale_colour_discrete()+
-#   # geom_jitter(shape=16, aes(color=mean_RDI_per_drug<0.85))+
-#   theme_minimal(base_size = 14)+
-#   facet_wrap(drugname ~ therapy, ncol = 2, scales = "free")
+Frontline %>% 
+  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
+  filter(!is.na(value)) %>% 
+  ggplot(aes(x= raceeth))+
+  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
+  theme_minimal(base_size = 14)+
+  coord_flip()+
+  facet_wrap(name ~ ., ncol = 1, scales = "free")
 ```
@@
 ## 1.RDI summary table
-Do you want them together in 1 table?
-
-<span style="color:green">**Platin**</span>  
+
+<span style="color:green">**RDI summary table**</span>  
 ```{r Table summary Platin}
 # Treatment & demo
-tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(RDI_carbo_neo, RDI_carbo_neo_grp)) %>%
-  tbl_summary(
-              label = list(RDI_carbo_neo ~ "RDI")) %>%
+tbl1 <- Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI (continous)" = RDI_carbo_neo, "RDI (categorical)" = RDI_carbo_neo_grp, therapy)) %>%
+  tbl_summary(by = therapy) %>% 
   bold_labels()
 
-tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(RDI_carbo_adj, RDI_carbo_adj_grp)) %>%
-  tbl_summary(
-              label = list(RDI_carbo_adj ~ "RDI")) %>%
+tbl2 <- Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI (continous)" = RDI_carbo_adj, "RDI (categorical)" = RDI_carbo_adj_grp, therapy)) %>%
+  tbl_summary(by = therapy) %>%
   bold_labels()
 
-tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(RDI_carbo_adj, RDI_carbo_adj_grp)) %>%
-  tbl_summary(
-              label = list(RDI_carbo_adj ~ "RDI")) %>%
+tbl3 <- Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
+  tbl_summary(by = therapy
+              ) %>%
   bold_labels()
 
-tbl_stack(list(tbl1, tbl2, tbl3),
+tbl4 <- Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
+  tbl_summary(by = therapy
+              ) %>%
+  bold_labels()
+tbl5 <- Frontline %>% filter(dose_dense == 3) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
+  tbl_summary(by = therapy,
+              type = list(`RDI (continous)` ~ "continuous")) %>%
+  bold_labels()
+tbl6 <- Frontline %>% filter(dose_dense == 3) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
+  tbl_summary(by = therapy,
+              type = list(`RDI (continous)` ~ "continuous")) %>%
+  bold_labels()
+
+# tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
+#   modify_spanning_header(everything() ~ NA_character_)
+tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6),
           group_header = c(
-                           "carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery"),
+                           "Carboplatin Neo", 
+                           "Carboplatin Adj",
+                           "Paclitaxel overall Neo",
+                           "Paclitaxel overall Adj",
+                           "Paclitaxel dose dense Neo",
+                           "Paclitaxel dose dense Adj"),
           quiet = TRUE)
@@
 
-<span style="color:green">**Taxanes**</span>  
 ```{r Table summary Taxanes}
-tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
-  tbl_summary() %>%
-  bold_labels()
-
-tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
-  tbl_summary() %>%
-  bold_labels()
-
-tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
-  tbl_summary() %>%
-  bold_labels()
+# tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(RDI_carbo_neo, RDI_carbo_neo_grp, therapy)) %>%
+#   tbl_summary(by = therapy) %>% 
+#   bold_labels()
+# 
+# tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(RDI_carbo_adj, RDI_carbo_adj_grp, therapy)) %>%
+#   tbl_summary(by = therapy) %>%
+#   bold_labels()
+# tbl4 <- tbl_stack(list(tbl1, tbl2),
+#           group_header = c(
+#                            "paclitaxel Neo/Upfront Chemo",
+#                            "paclitaxel Adj/Upfront Chemo"),
+#           quiet = TRUE)
+# 
+# 
+# tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c(RDI_carbo_adj, RDI_carbo_adj_grp, therapy)) %>%
+#   tbl_summary(by = therapy) %>%
+#   bold_labels()
+# tbl_merge(list(tbl4, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))
 
@@
 #   bold_labels()
-tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery" &
-                               dose_dense == 3) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
-  tbl_summary(
-              type = list(RDI ~ "continuous")) %>%
-  bold_labels()
-
-# tbl7 <- tbl_merge(list(tbl1, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))
+# tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery" &
+#                                dose_dense == 3) %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
+#   tbl_summary(
+#               type = list(RDI ~ "continuous")) %>%
+#   bold_labels()
+
 # tbl8 <- tbl_merge(list(tbl2, tbl4))
@@
 
-tbl_stack(list(tbl1, tbl2, tbl3, tbl6),
-          group_header = c(
-                           "paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery",
-                           "dose dense paclitaxel Adj/Upfront Surgery"),
-          quiet = TRUE)
+# tbl_stack(list(tbl1, tbl2, tbl3, tbl6),
+#           group_header = c(
+#                            "paclitaxel Neo/Upfront Chemo", 
+#                            "paclitaxel Adj/Upfront Chemo",
+#                            "paclitaxel Adj/Upfront Surgery",
+#                            "dose dense paclitaxel Adj/Upfront Surgery"),
+#           quiet = TRUE)
 ```
@@
 ```{r Table 5 HR}
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl1 <- tbl2 %>%
+#   select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
+#   tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
+#   add_
+# tbl2 <- tbl2 %>%
+#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+#   tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# 
+# 
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- tbl3 %>%
+#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+#   tbl_uvregression(method = survival::coxph,
+#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
+#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl5 <- tbl_merge(list(tbl2, tbl3))
+# 
+# # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
+# #   modify_spanning_header(everything() ~ NA_character_)
+# 
+# tbl_stack(list(tbl1, tbl5)) %>%
+#   bold_labels() %>%
+#   italicize_levels()
+
+  # trial %>%
+  # select(age, grade, stage, trt) %>%
+  # mutate(grade = paste("Grade", grade)) %>%
+  # # tbl_strata(
+  # #   strata = grade,
+  # #   .tbl_fun =
+  # #     ~ .x %>%
+  #       tbl_summary(by = trt, missing = "no") %>%
+  #       add_n()
+  # )
+
 tbl2 <- Frontline %>%
@@
 ```
-In univariable analysis, higher RDI (continuous) of carboplatin in an Adjuvant / Upfront Chemo setting show a worse outcome which is not seen in the categorical variable.  
-A trend is observed toward a better survival with higher RDI (continuous) of paclitaxel in an Neoadjuvant / Upfront Chemo.
-In the contrary, lower RDI (categorical) of paclitaxel in an Adjuvant / Upfront Surgery shows a 51% increase risk of death when underdosed p = 0.091.
 
@@
 ```
-In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival.
+<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
 
@@
 ```
-In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.  
-RDI for paclitaxel is not a factor associated with survival.
+<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
+<!-- RDI for paclitaxel is not a factor associated with survival. -->
 
@@
 ```
-When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
+<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
+-->
 
@@
 ```
-Continuous RDI for carboplatin or paclitaxel are not factors associated with survival.
+<!-- Continuous RDI for carboplatin or paclitaxel are not factors associated with survival. -->
 
@@
 
-# V.More precise RDI
-
-As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed
-
-```{r echo=TRUE}
-# Highly underdosed: < 0.75
-# Underdosed: >= 0.75 to <0.85
-# Adequate dosing: >= 0.85 to <1.10
-# Overdosing: >=1.10
-```
-Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI)
-```{r, fig.width=12, fig.height=12}
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+
-  geom_point(alpha = 0.7, size = 0.75)+
-  theme_minimal(base_size = 10)+
-  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+
-  geom_jitter()+
-  theme_minimal(base_size = 10)+
-  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
-
-```
-Here I just wanted to see if we have more or less underdosing / overdosing with BMI
-```{r, fig.width=12, fig.height=12}
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  ggplot(aes(x= RDI_grp1, fill = drugname))+
-  geom_bar(position = position_dodge())+
-  theme_minimal(base_size = 10)+
-  facet_wrap(. ~ therapy, ncol = 2, scales = "free")+
-  coord_flip()
-```
-
-```{r, fig.width=12}
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(x= drugname, fill = RDI_grp1))+
-#   geom_bar(position = position_dodge())+
-#   theme_minimal(base_size = 10)+
-#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
-#   coord_flip()
-```
-
-```{r}
-Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-  # filter(linenumber_new == "1") %>%
-  ggplot(aes(x= drugname, fill = RDI_grp1))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 10)+
-  coord_flip()+
-  facet_wrap(.~ therapy)
-```
-As you can see above in green, we have a lot of patient who are overdose.
-<br>
-<br>
-
-## Hazard Ratio RDI 2
-
-<span style="color:green">**Table HR**</span>
-
-### Univariable
-```{r HR RDI 2}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- tbl2 %>%
-  select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- tbl2 %>%
-  select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel/Upfront Chemo", 
-                           "paclitaxel/Upfront Chemo",
-                           "paclitaxel/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference.
-
-### Multivariable
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp1 + raceeth + ageatdx + stagecat`
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<br>
-<br>
-
-## Adjusted by other drug
-### RDI group
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat`
-```{r Table 5 HR adjusted rdi group adjusted by other drug 2}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<br>
-<br>
-
-***
+<!-- # V.More precise RDI -->
+
+<!-- As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed -->
+
+<!-- ```{r echo=TRUE} -->
+<!-- # Highly underdosed: < 0.75 -->
+<!-- # Underdosed: >= 0.75 to <0.85 -->
+<!-- # Adequate dosing: >= 0.85 to <1.10 -->
+<!-- # Overdosing: >=1.10 -->
+<!-- ``` -->
+<!-- Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI) -->
+<!-- ```{r, fig.width=12, fig.height=12} -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!--   ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
+<!--   geom_point(alpha = 0.7, size = 0.75)+ -->
+<!--   theme_minimal(base_size = 10)+ -->
+<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!--   ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
+<!--   geom_jitter()+ -->
+<!--   theme_minimal(base_size = 10)+ -->
+<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
+
+<!-- ``` -->
+<!-- Here I just wanted to see if we have more or less underdosing / overdosing with BMI -->
+<!-- ```{r, fig.width=12, fig.height=12} -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!--   ggplot(aes(x= RDI_grp1, fill = drugname))+ -->
+<!--   geom_bar(position = position_dodge())+ -->
+<!--   theme_minimal(base_size = 10)+ -->
+<!--   facet_wrap(. ~ therapy, ncol = 2, scales = "free")+ -->
+<!--   coord_flip() -->
+<!-- ``` -->
+
+<!-- ```{r, fig.width=12} -->
+<!-- # Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!-- #   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
+<!-- #   geom_bar(position = position_dodge())+ -->
+<!-- #   theme_minimal(base_size = 10)+ -->
+<!-- #   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+ -->
+<!-- #   coord_flip() -->
+<!-- ``` -->
+
+<!-- ```{r} -->
+<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
+<!--   # filter(linenumber_new == "1") %>% -->
+<!--   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
+<!--   geom_bar(position = "fill")+ -->
+<!--   theme_minimal(base_size = 10)+ -->
+<!--   coord_flip()+ -->
+<!--   facet_wrap(.~ therapy) -->
+<!-- ``` -->
+<!-- As you can see above in green, we have a lot of patient who are overdose. -->
+<!-- <br> -->
+<!-- <br> -->
+
+<!-- ## Hazard Ratio RDI 2 -->
+
+<!-- <span style="color:green">**Table HR**</span> -->
+
+<!-- ### Univariable -->
+<!-- ```{r HR RDI 2} -->
+<!-- tbl2 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Chemo") -->
+<!-- tbl1 <- tbl2 %>% -->
+<!--   select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp1) %>%  -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl2 <- tbl2 %>% -->
+<!--   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl3 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Surgery") -->
+<!-- tbl3 <- tbl3 %>% -->
+<!--   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
+<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
+<!--                            "carboplatin Adj/Upfront Chemo", -->
+<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+
+<!-- # Pacli -->
+
+<!-- tbl2 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Chemo") -->
+<!-- tbl1 <- tbl2 %>% -->
+<!--   select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp1) %>%  -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl2 <- tbl2 %>% -->
+<!--   select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl3 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Surgery") -->
+<!-- tbl3 <- tbl3 %>% -->
+<!--   select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
+<!--   tbl_uvregression(method = survival::coxph, -->
+<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)), -->
+<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
+<!--           group_header = c("paclitaxel/Upfront Chemo",  -->
+<!--                            "paclitaxel/Upfront Chemo", -->
+<!--                            "paclitaxel/Upfront Surgery")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+<!-- ``` -->
+<!-- Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference. -->
+
+<!-- ### Multivariable -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp1 + raceeth + ageatdx + stagecat` -->
+<!-- ```{r} -->
+<!-- tbl2 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Chemo") -->
+<!-- tbl1 <-  -->
+<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
+<!--              event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl2 <-  -->
+<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
+<!--              event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl3 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Surgery") -->
+<!-- tbl3 <-  -->
+<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
+<!--              event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
+<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
+<!--                            "carboplatin Adj/Upfront Chemo", -->
+<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+
+<!-- # Pacli -->
+
+<!-- tbl2 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Chemo") -->
+<!-- tbl1 <-  -->
+<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
+<!--              event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl2 <-  -->
+<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
+<!--              event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl3 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Surgery") -->
+<!-- tbl3 <-  -->
+<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
+<!--              event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
+<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
+<!--                            "paclitaxel Adj/Upfront Chemo", -->
+<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+<!-- ``` -->
+<!-- <br> -->
+<!-- <br> -->
+
+<!-- ## Adjusted by other drug -->
+<!-- ### RDI group -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` -->
+<!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug 2} -->
+<!-- tbl2 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Chemo") -->
+<!-- tbl2 <-  -->
+<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
+<!--              event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl3 <- Frontline %>% -->
+<!--   filter(therapy == "Upfront Surgery") -->
+<!-- tbl3 <-  -->
+<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
+<!--              event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
+<!-- tbl_stack(list(tbl2, tbl3), -->
+<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
+<!--   bold_labels() %>% -->
+<!--   italicize_levels() -->
+<!-- ``` -->
+<!-- <br> -->
+<!-- <br> -->
+
+<!-- *** -->
 
@@
 <!-- ``` -->
-<!-- <br> -->
-<!-- <br> -->
+
+<br>
+<br>
 
 ***
+
+```{r echo=FALSE, out.width='500%'}
+knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
+```

### 2021-12-08 Rmd/rdi analysis.Rmd
Update rmd

@@
     cycle_count_perline == drugname_count_perline &
-      (drugname == "carboplatin" |
-      drugname == "paclitaxel")                            ~ cycle_drugname,
+      (cycle_drugname == "carboplatin" |
+      cycle_drugname == "paclitaxel")                      ~ cycle_drugname,
     TRUE                                                   ~ NA_character_
@@
            linename == "Bevacizumab,Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin"))            ~ "include"
+           linename == "Bevacizumab,Carboplatin"))            ~ NA_character_,
+    linenumber_adj == 1                                       ~ "exclude"
   )) %>% 
@@
 ```{r RDI calculation}
-RDI_data <- Treatment %>% 
+Treatment <- Treatment %>% 
   # filter(chemotherapy_type == "Neoadjuvant" |
@@
   ) %>% 
-  ungroup() %>% 
+  ungroup()
+
+RDI_data <- Treatment %>% 
   distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
@@
 
-```{r Frontline_adjusted}
-Frontline_adjusted <- RDI_data %>% 
+```{r RDI_data}
+RDI_data <- RDI_data %>% 
   group_by(patientid) %>% 
@@
        .direction = "downup") %>% 
-  ungroup() %>% 
+  ungroup()
+Frontline_adjusted <- RDI_data %>% 
   distinct(patientid, .keep_all = TRUE)
@@
 study_criteria <- study_criteria %>%
-  filter(line_keep == "include")
+  filter(is.na(line_keep))
   # Remove patients with other linename
@@
 
-### Number of line in treatment and cycle in frontline  
-Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
-in upfront neo
 ```{r}
-RDI_data <- 
+full_data_study_pop <- 
   Treatment %>% 
@@
   arrange(patientid, episodedate, drugname)
-
-RDI_data %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
+```
+
+### Number of line /cycle received by patients in our study population
+
+<span style="color:green">**Table supp 1 Number of total line**</span>
+```{r}
+full_data_study_pop %>% 
   arrange(desc(linenumber_new)) %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new) %>% 
-  tbl_summary()
-RDI_data %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  select(linenumber_new, therapy) %>% 
+  tbl_summary(by = therapy)
+```
+
+<span style="color:green">**Table supp 1 Number of cycle in Neo**</span>
+```{r}
+full_data_study_pop %>% 
+  filter(chemotherapy_type == "Neoadjuvant") %>% 
   arrange(desc(cycle_increment)) %>%
@@
   tbl_summary()
-RDI_data %>% 
-  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
+full_data_study_pop %>% 
+  filter(chemotherapy_type == "Neoadjuvant") %>% 
   arrange(desc(cycle_increment)) %>%
-  mutate(cycle_increment = as.numeric(cycle_increment)) %>% 
   distinct(patientid, .keep_all = TRUE) %>%
   select(cycle_increment) %>% 
-  tbl_summary()
-```
-
-Number of Adjuvant line in patients with upfront neo
+  tbl_summary(type = list(cycle_increment ~ "continuous"))
+```
+
+<span style="color:green">**Table supp 1 Number of cycle in Adj**</span>
 ```{r}
-RDI_data %>% 
-  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
-  arrange(desc(linenumber_adj)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(linenumber_adj) %>% 
-  tbl_summary()
-
-RDI_data %>% 
-  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
-  filter(linenumber_adj == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
+full_data_study_pop %>% 
+  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
   arrange(desc(cycle_increment)) %>%
   distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment) %>% 
-  tbl_summary(label = list(cycle_increment ~ "cycle number during the adjuvant course in Upfront Chemo setting"))
-
-RDI_data %>% 
-  filter(therapy == "Upfront Chemo") %>% 
-  filter(linenumber_adj == 1) %>% 
-  mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
-  arrange(desc(total_cycle_increment)) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(total_cycle_increment) %>% 
-  tbl_summary(label = list(total_cycle_increment ~ "total cycle number in Upfront Chemo setting"))
-```
-Number of Adjuvant line in patients with upfront surgery
-```{r}
-RDI_data %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
-  arrange(desc(linenumber_adj)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(linenumber_adj) %>% 
-  tbl_summary()
-
-RDI_data %>% 
-  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
-  filter(linenumber_adj == 1) %>% 
-  mutate(cycle_increment = factor(cycle_increment)) %>% 
+  select(cycle_increment, therapy) %>% 
+  tbl_summary(by = therapy)
+full_data_study_pop %>% 
+  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
   arrange(desc(cycle_increment)) %>%
   distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment) %>% 
-  tbl_summary()
+  select(cycle_increment, therapy) %>% 
+  tbl_summary(by = therapy,
+              type = list(cycle_increment ~ "continuous"))
 ```
@@
 
+<span style="color:green">**Table 3 Summary demographic/clinical data by bmi**</span>
+```{r Table 3}
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth, "vital",
+           agecat, "ageatdx",
+
+           "bmi_at_dx", bmi_cat, "BSA",
+           "stagecat")) %>% 
+  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+```
+<br>
+
 ## 2.Clinical Plots
@@
   theme_minimal(base_size = 14)+
-  labs(title = "BMI category")+
+  labs(title = "BMI Category at Diagnosis")+
   coord_flip()
@@
   theme_minimal(base_size = 14)+
-  labs(title = "Age cat")+
+  labs(title = "Age Category")+
   coord_flip()
@@
   theme_minimal(base_size = 14)+
-  labs(title = "BMI category")+
+  labs(title = "BMI category at Diagnosis")+
   coord_flip()
@@
 
-<span style="color:green">**Table 3 Summary treatment data by race**</span>
-```{r Table 3}
+<span style="color:green">**Table 4 Summary treatment data by race**</span>
+```{r Table 4}
 # tbl1 <- 
@@
   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+```
+<br>
+
+<span style="color:green">**Table 5 Summary treatment data by bmi**</span>
+```{r Table 5}
+Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat,
+           "debulking", "therapy"
+           )) %>% 
+  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
+  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
 ```
@@
 Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= therapy))+
@@
   coord_flip()
+
+Frontline %>%
+  ggplot(aes(x= bmi_cat, fill= therapy))+
+  geom_bar(position ="fill")+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+Frontline %>%
+  ggplot(aes(x= bmi_cat, fill= debulking))+
+  geom_bar(position ="fill")+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+full_data_study_pop %>% 
+  filter(linenumber_adj == 1) %>% 
+  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
+  ggplot(aes(x= linename, fill= therapy))+
+  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
+  theme_minimal(base_size = 14) + 
+  facet_wrap(. ~ chemotherapy_type)+
+  coord_flip()
+
+full_data_study_pop %>% 
+  filter(linenumber_adj == 1) %>% 
+  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
+  ggplot(aes(x= linename, fill= therapy))+
+  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
+  theme_minimal(base_size = 14) + 
+  facet_wrap(raceeth ~ chemotherapy_type)+
+  coord_flip()
+
+full_data_study_pop %>% 
+  filter(chemotherapy_type == "Neoadjuvant") %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linename) %>% 
+  tbl_summary(label = list(linename ~ "line name received as Neoadujant"))
+full_data_study_pop %>% 
+  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(linename, therapy) %>% 
+  tbl_summary(by = therapy,
+              label = list(linename ~ "line name received as Adjuvant"))
 ```
@@
 Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= raceeth, fill= therapy))+
@@
 Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  ggplot(aes(x= raceeth, fill= therapy))+
+  ggplot(aes(x= debulking))+
+  geom_bar()+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+Frontline %>%
+  ggplot(aes(x= raceeth, fill= debulking))+
   geom_bar(position ="fill")+
   theme_minimal(base_size = 14)+
-  coord_flip()+
-  facet_wrap(. ~ drugname)
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+full_data_study_pop %>% 
+  filter(linenumber_adj == 1) %>% 
+  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
+  ggplot(aes(x= linename, fill= therapy))+
+  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
+  theme_minimal(base_size = 14) + 
+  facet_wrap(bmi_cat ~ chemotherapy_type)+
+  coord_flip()
+
+full_data_study_pop %>% 
+  filter(chemotherapy_type == "Neoadjuvant") %>% 
+  group_by(patientid, drugname) %>% 
+  summarise(CrCl = mean(CrCl),
+            target_auc = mean(target_auc),
+            expected_dose = mean(expected_dose)) %>% 
+  ungroup() %>% 
+  distinct(patientid, drugname, .keep_all = TRUE) %>% 
+  select(CrCl, target_auc, expected_dose, drugname) %>% 
+  tbl_summary(by = drugname,
+              label = list(CrCl ~ "Average CrCl during Neoadujant setting",
+                           target_auc ~ "Target dose (AUC or mg/mg2)",
+                           expected_dose ~ "Expected dose")
+    )
 ```
@@
   coord_flip()
-  # facet_wrap(. ~ therapy)
 
@@
 # 
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
-#   # geom_boxplot()+
-#   ylim(c(-.25, 2))+
-#   geom_jitter(shape=16, aes(color=RDI_grp))+
-#   labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
-#   theme_minimal(base_size = 14) +
-#   guides(color=FALSE)+
-#   facet_wrap(.~ drugname, ncol = 2)
+Frontline %>% 
+  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
+  filter(!is.na(value)) %>% 
+  ggplot(aes(x= name, y= value, color= value < 0.85))+
+  geom_boxplot()+
+  geom_jitter(shape=16)+
+  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
+  theme_minimal(base_size = 14)+
+  coord_flip()+
+  facet_wrap(.~ therapy, ncol = 2)
 ```
@@
 ```{r ggridges, fig.width=16, fig.height=18}
-# library(ggridges)
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(y=raceeth, x=mean_RDI_per_drug,  fill=raceeth
-#              )) +
-#     geom_density_ridges(alpha=0.5) +
-#     theme_ridges()+
-#   theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
-#         panel.spacing = unit(0.1, "lines"),
-#         strip.text.x = element_text(size = 14)
-#     ) +
-#   geom_vline(xintercept = 1, color = "red", linetype = 2)+
-#   
-#   facet_wrap(therapy ~ drugname, ncol = 2, scales = "free_x")
+library(ggridges)
+Frontline %>% 
+  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
+  filter(!is.na(value)) %>% 
+  ggplot(aes(y=raceeth, x=value,  fill=raceeth
+             )) +
+    geom_density_ridges(alpha=0.5) +
+    theme_ridges()+
+  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        strip.text.x = element_text(size = 14)
+    ) +
+  geom_vline(xintercept = 1, color = "red", linetype = 2)+
+
+  facet_wrap(therapy ~ name, ncol = 2, scales = "free_x")
+
+Frontline %>% 
+  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
+  filter(!is.na(value)) %>% 
+  ggplot(aes(y=bmi_cat, x=value,  fill=bmi_cat
+             )) +
+    geom_density_ridges(alpha=0.5) +
+    theme_ridges()+
+  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
+        panel.spacing = unit(0.1, "lines"),
+        strip.text.x = element_text(size = 14)
+    ) +
+  geom_vline(xintercept = 1, color = "red", linetype = 2)+
+
+  facet_wrap(therapy ~ name, ncol = 2, scales = "free_x")
 ```
@@
 <span style="color:green">**RDI summary table**</span>
+
+```{r}
+my_theme <-
+  list(
+    # Some gt customization
+    "as_gt-lst:addl_cmds" = list(
+      # make the font size small
+      tab_spanner = rlang::expr(gt::tab_options(row.striping.background_color = "lightgrey",
+                                                row.striping.include_stub = TRUE,
+                                                row.striping.include_table_body = TRUE,
+                                                row_group.border.top.color = "blue",
+                                                # table.background.color = "white", 
+                                                heading.background.color = "lightblue", 
+                                                # column_labels.background.color = "orange", 
+                                                row_group.background.color = "grey",
+                                                stub.background.color = "slateblue", 
+                                                summary_row.background.color = "tomato", 
+                                                grand_summary_row.background.color = "green")),
+      # add a custom title and subtitle to every table
+      # user_added1 = rlang::expr(gt::tab_header(
+      #   title = "Christelle's Table", subtitle = "Yeap"))#,
+      # add a custom data source note
+      # user_added2 = rlang::expr(gt::tab_source_note(
+      #   source_note = "Source: our data!"))#,
+      # stripe the table rows
+      user_added1 = rlang::expr(gt::opt_row_striping())#,
+      # user_added4 = rlang::expr(gt::opt_table_lines("none"))
+      )
+    )
+
+reset_gtsummary_theme()
+set_gtsummary_theme(my_theme)
+trial %>%
+  select(age, grade, trt) %>%
+  tbl_summary(by = trt) %>%
+  add_stat_label() %>%
+  add_p() %>%
+  as_gt() 
+```
+
 ```{r Table summary Platin}
@@
           quiet = TRUE)
+```
+
+```{r}
+# reset_gtsummary_theme()
 ```
@@
 
-<span style="color:green">**Table 5 HR**</span>
+<span style="color:green">**Table 6 HR**</span>
 
 ## Univariable
-```{r Table 5 HR}
+```{r Table 6 HR}
 # tbl2 <- Frontline %>%
@@
 
-```{r echo=FALSE, out.width='500%'}
+```{r echo=FALSE, out.width='50%'}
 knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')

### 2021-12-15 Rmd/rdi analysis.Rmd
Start imputation

@@
 
-           "histology", "stagecat",
+           "histology", imp_histology, "stagecat", imp_stagecat,
 
@@
            "bmi_at_dx", bmi_cat, "BSA",
-           "stagecat")) %>% 
+           "stagecat", imp_stagecat)) %>% 
   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
            "bmi_at_dx", bmi_cat, "BSA",
-           "stagecat")) %>% 
+           "stagecat", imp_stagecat)) %>% 
   tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= imp_histology))+
+  geom_bar()+
+  theme_minimal(base_size = 14)+
+  labs(title = "Histology")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= stagecat))+
@@
   distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= imp_stagecat))+
+  geom_bar()+
+  theme_minimal(base_size = 14)+
+  labs(title = "Stage")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= agecat))+
@@
   distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill = imp_histology))+
+  geom_bar(position = "fill")+
+  theme_minimal(base_size = 14)+
+  labs(title = "Histology")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= raceeth, fill = stagecat))+
+  geom_bar(position = "fill")+
+  theme_minimal(base_size = 14)+
+  labs(title = "Stage")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill = imp_stagecat))+
   geom_bar(position = "fill")+
@@
 
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ imp_stagecat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 ) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r clinical from first treatment, fig.height = 7}
-# OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
+           title = "OS from date of diagnosis", 
            font.main = c(24, "bold", "black"), 
@@
 ) + guides(colour = guide_legend(ncol = 2))
-
-# OS by tstage
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
+```
+</div>
+
+<div class = "col-md-6">
+```{r clinical from first treatment, fig.height = 7}
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 ) + guides(colour = guide_legend(ncol = 2))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ imp_stagecat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
+
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 2))
 ```
@@
   select(c(raceeth,
-           "debulking", "therapy"
+           "debulking", imp_debulking , "therapy"
            )) %>% 
@@
 
-```{r echo=FALSE, out.width='50%'}
-knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
-```
+```{r echo=FALSE, out.width='30%'}
+# knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
+```

### 2021-12-15 R/2.data cleaning.R

@@ -542,9 +542,6 @@ write_rds(areaUC, "areaUC.rds")
 
 #################################################################################################### II ### Clinical Cleaning----
 clinical_data <- clinical_data %>% 
-  # Limit to the patients to the ones we have date of surgery when had surgery
-  # filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%  # loss 17 ################## Will do when bind to drugs
-  # filter(!(histology == "Unknown/not documented")) %>% # loss 287 ################## Will do when bind to drugs
   # Recode
   mutate(raceeth = factor(raceeth, levels = c("NHWhite", "NHBlack", "Hispanic", "Other"))) %>% 
   mutate(race = case_when(
@@ -554,15 +551,15 @@ clinical_data <- clinical_data %>%
     TRUE                         ~ race
   )) %>% 
   mutate(ethnicity = (str_remove(ethnicity, " or Latino"))) %>% 
-  mutate(new_eth = case_when(
-    is.na(ethnicity) &
-      is.na(race)              ~ "Other or Uk",
-    is.na(ethnicity) &
-      !is.na(race)             ~ "NH",
-    ethnicity == "Hispanic"    ~ "Hispanic"
-  )) %>% 
-  unite(new_raceeth, c(new_eth, race), sep = " ", remove = FALSE, na.rm = TRUE) %>% 
-  mutate(new_raceeth1 = ifelse(str_detect(new_raceeth, "Black|Hispanic"), "Minority", new_raceeth)) %>% 
+  # mutate(new_eth = case_when(
+  #   is.na(ethnicity) &
+  #     is.na(race)              ~ "Other or Uk",
+  #   is.na(ethnicity) &
+  #     !is.na(race)             ~ "NH",
+  #   ethnicity == "Hispanic"    ~ "Hispanic"
+  # )) %>% 
+  # unite(new_raceeth, c(new_eth, race), sep = " ", remove = FALSE, na.rm = TRUE) %>% 
+  # mutate(new_raceeth1 = ifelse(str_detect(new_raceeth, "Black|Hispanic"), "Minority", new_raceeth)) %>% 
   # Lauren recoded followupdate to have the days of death with Flatiron rules
   mutate(dateofdeath = case_when(
     vitalstatus == 1 ~ followupdate,
@@ -576,15 +573,65 @@ clinical_data <- clinical_data %>%
   mutate(month_at_os = interval(start = diagnosisdate, end = followupdate)/
            duration(n=1, units = "months")) %>% 
[…]

### 2021-12-15 R/2.data cleaning.R
Finished multiple imputation

@@ -586,23 +586,20 @@ clinical_data <- clinical_data %>%
     is.na(histology)                            ~ NA_character_,
     TRUE                                        ~ "Others"
   ), histology = factor(histology, levels = c("Serous", "Others"))) %>% 
-  mutate(debulking = str_replace(debulking, "Unknown", NA_character_)) %>% 
-  mutate(across(.cols = c(stagecat, debulking), ~as.factor(.)
-                ))
+  mutate(debulking = str_replace(debulking, "Unknown|No surgery", NA_character_)) %>% 
+  mutate(across(.cols = c(stagecat, debulking), ~as.factor(.)))
 
 # Imputation for stagecat, debulking status, histology
 library(mice)
 imputed_data <- mice(clinical_data %>% select(-contains("date")), 
                      m=5, maxit = 50, seed = 500)
 
-ignore_imp <- clinical_data %>% mutate(vec = !is.na(clinical_data$surgerydate)) %>% select(vec)
+ignore_imp <- clinical_data %>% mutate(vec = clinical_data$issurgery != "Yes")
 # c(ignore_imp$vec)
 # c(rep(FALSE, 3000), rep(TRUE, 3687))
 imputed_data_debul <- mice(clinical_data %>% select(-contains("date"), -diff_surg_dx), 
                            ignore = c(ignore_imp$vec),
                            m=5, maxit = 50, seed = 500)
-https://stackoverflow.com/questions/33500047/r-mice-machine-learning-re-use-imputation-scheme-from-train-to-test-set
-https://stackoverflow.com/questions/62334256/how-do-i-impute-missing-values-only-if-certain-conditions-met-in-mice
 
 summary(imputed_data)
 summary(imputed_data_debul)
@@ -616,21 +613,30 @@ table(imputed_data_debul$imp$debulking[1])
 # Look at proportion
 prop.table(table(imputed_data$imp$histology[2]))*100
 prop.table(table(imputed_data$imp$stagecat[2]))*100
-prop.table(table(imputed_data$imp$debulking[1]))*100
 prop.table(table(imputed_data_debul$imp$debulking[1]))*100
 # get complete data from the best imputation
 imputed_data <- complete(imputed_data,2)
-imputed_data_debul <- complete(imputed_data_debul,2)
+imputed_data_debul <- complete(imputed_data_debul,1)
 
 imputed_data <- imputed_data %>% 
   rename(imp_histology = histology, 
-         imp_stagecat = stagecat,
[…]

### 2021-12-15 Rmd/rdi analysis.Rmd
Update rmd with imputed data, clean up, add ggconsort

@@
   ) %>% 
+  mutate(ex = case_when(
+    interval_surgery_to_adj_start > 3                  ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>% 
+  fill(ex, .direction = "updown") %>% 
+  ungroup() %>%
+
   group_by(patientid) %>% 
@@
 missing_data <- missing_data %>%
-  arrange(patientid, episodedate) %>%
-  mutate(ex = case_when(
-    interval_surgery_to_adj_start > 3                  ~ "exclude"
-  )) %>% 
   filter(is.na(ex))
@@
 
+# Consort diagram
+
+```{r consort}
+library(ggconsort)
+# flatiron_rec <- Frontline_adjusted %>% 
+#   filter(is.na(flatiron_rules))
+# study_criteria <- flatiron_rec %>% 
+#   filter(!is.na(histology))
+# study_criteria <- study_criteria %>%
+#   filter(!is.na(surgerydate))
+# study_criteria <- study_criteria %>%
+#   filter(had_carbo_pacli == "Yes")
+# study_criteria <- study_criteria %>% 
+#   filter(treatment_sequence == "neo + surg + adj" |
+#            treatment_sequence == "surg + adj")
+# study_criteria <- study_criteria %>%
+#   filter(is.na(line_keep))
+#
+
+study_cohorts <- 
+  Frontline_adjusted %>%
+  cohort_start("Assessed for eligibility") %>%
+  # Define cohorts using named expressions
+  # Notice that you can use previously defined cohorts in subsequent steps
+  cohort_define(
+  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),
+
+  study_criteria = flatiron_rec  %>% 
+    filter(!is.na(histology)) %>%
+    filter(!is.na(surgerydate)) %>%
+    filter(had_carbo_pacli == "Yes") %>% 
+    filter(treatment_sequence == "neo + surg + adj" |
+             treatment_sequence == "surg + adj") %>%
+    filter(is.na(line_keep)),
+
+    missing_data = study_criteria  %>% 
+    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
+    filter(is.na(ex)) %>%
+    filter(days_at_first_drug >= 0 &
+             (is.na(surgerydate) | days_at_surg >= 0)) %>%
+    filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) &
+              !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) &
+              therapy == "Upfront Chemo") |
+             (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
+               therapy == "Upfront Surgery"))),
+
+    standart_care = missing_data %>% 
+    filter(is.na(neo_more_more_than_1line)) %>%
+    filter(is.na(whole_frontline_is_maintenance)) %>%
+    filter(is.na(too_many_cycle)),
+
+  Frontline = standart_care %>% 
+    filter(is.na(wrong_pacli_dosedense)),
+  Frontline1 = Frontline %>%
+    filter(is.na(switch_drugs))
+  ) %>%
+  # Provide text labels for cohorts
+  cohort_label(
+    flatiron_rec = "**flatiron_rec**",
+    study_criteria = "*study_criteria*",
+    missing_data = "missing_data",
+    standart_care = "standart_care",
+    Frontline = "Frontline",
+    Frontline1 = "Population Study"
+  )
+study_cohorts
+
+study_consort <- study_cohorts %>%
+  consort_box_add(
+    "full", 0, 50, cohort_count_adorn(study_cohorts, .full)
+  ) %>%
+  consort_box_add(
+    "flatiron_rec", 5, 45, glue::glue(
+      "{cohort_count_adorn(study_cohorts, flatiron_rec)}<br> 
+      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
+      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
+      • Borderline cases (not invasive ovarian cancer) <br>
+      • Data from one PracticeID <br>
+      • historical structured data were not available for <br> patients seen at academic sites prior to 2015
+      ")
+
+  ) %>%
+  consort_box_add(
+    "study_criteria", 5, 40, cohort_count_adorn(study_cohorts, study_criteria)
+  ) %>%
+  consort_box_add(
+    "missing_data", 5, 35, cohort_count_adorn(study_cohorts, missing_data)
+  ) %>%
+  consort_box_add(
+    "standart_care", 5, 30, cohort_count_adorn(study_cohorts, standart_care)
+  ) %>%
+  consort_box_add(
+    "Frontline", 5, 25, cohort_count_adorn(study_cohorts, Frontline)
+  ) %>%
+  consort_box_add(
+    "Frontline1", 0, 20, cohort_count_adorn(study_cohorts, Frontline1)
+  ) %>%
+
+  consort_arrow_add(
+    end = "flatiron_rec", end_side = "left", start_x = 0, start_y = 45
+  ) %>%
+  consort_arrow_add(
+    end = "study_criteria", end_side = "left", start_x = 0, start_y = 40
+  ) %>%
+  consort_arrow_add(
+    end = "missing_data", end_side = "left", start_x = 0, start_y = 35
+  ) %>%
+  consort_arrow_add(
+    end = "standart_care", end_side = "left", start_x = 0, start_y = 30
+  ) %>%
+  consort_arrow_add(
+    end = "Frontline", end_side = "left", start_x = 0, start_y = 25
+  ) %>%
+  consort_arrow_add(
+    end = "Frontline1", end_side = "top", start_x = 0, start_y = 50
+  )
+
+study_consort %>%
+  ggplot() + 
+  geom_consort() +
+  theme_consort(margin_h = 18, margin_v = 1)
+```
+
+<br>
+
+***
+
 # II.Data analysis
@@
 
+<br>
+<br>
+
+***
+
 # Clinical Analysis
@@
            )) %>% 
-  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   select(c(bmi_cat,
-           "debulking", "therapy"
-           )) %>% 
-  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
+           "debulking", imp_debulking, "therapy"
+           )) %>% 
   tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
 
+Frontline %>%
+  ggplot(aes(x= bmi_cat, fill= imp_debulking))+
+  geom_bar(position ="fill")+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
 full_data_study_pop %>% 
@@
 Frontline %>%
+  ggplot(aes(x= imp_debulking))+
+  geom_bar()+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+Frontline %>%
   ggplot(aes(x= raceeth, fill= debulking))+
+  geom_bar(position ="fill")+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+Frontline %>%
+  ggplot(aes(x= raceeth, fill= imp_debulking))+
   geom_bar(position ="fill")+
@@
 
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ imp_debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
+           title = "OS from date of diagnosis", 
            font.main = c(24, "bold", "black"), 
@@
 ) + guides(colour = guide_legend(ncol = 1))
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment", 
+           font.main = c(24, "bold", "black"), 
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
+           size = 1.5,
+
+           pval=TRUE, 
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"), 
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)" 
+) + guides(colour = guide_legend(ncol = 1))
 
 ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ debulking, data=Frontline %>%
+                     distinct(patientid, .keep_all = TRUE)),
+           title = "OS from date of from first treatment",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ imp_debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 ### RDI group
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking` 
 ```{r Table 5 HR adjusted rdi group}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ### Continous
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking` 
 ```{r rdi continous}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ### RDI group
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking`
 ```{r Table 5 HR adjusted rdi group adjusted by other drug}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 
-<br>
-<br>
-
-***
-
 ```{r echo=FALSE, out.width='30%'}
-# knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
-```
+knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
+```

### 2021-12-16 Rmd/rdi analysis.Rmd
check and clean code rmd

@@
 
+- Select episodedatasource == "Administrations"
+
 **We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
@@
 
-- Select episodedatasource == "Administrations"
 ```{r drugs episode cleanup}
 drugs <- drugs %>% 
-  filter(episodedatasource == "Administrations" #& 
-           # ismaintenancetherapy == "FALSE" # keep maintenance for a correct recoding of line number
-         ) %>%
+  # Select only records for administration
+  filter(episodedatasource == "Administrations") %>%
   # bind with clinical
@@
   arrange(patientid, episodedate)
-
-drugs %>% distinct(patientid) %>% nrow()
-```
+```
+But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical informations who received drugs.
 
@@
 ```{r combine amount same drug one day}
-drugs1 <- drugs %>% 
-  # 3. Combined Multiple Administrations----
+combined_drugs <- drugs %>% 
+  # Combined Multiple Administrations----
   # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
-# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day.
-We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day.
-Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data.
-Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
-# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
-# Three administrations of the same drug were listed on a Friday.
-The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.
-# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
   group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate,
            drugname, units, ismaintenancetherapy) %>%
-  summarise_at(vars(route, amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
+  summarise_at(vars(route, amount), paste, collapse = ";") %>% # keep them in the data then do sum
   mutate(route = case_when(
-    str_detect(route, ";")            ~ "Intravenous",
+    str_detect(route, ";")            ~ "Intravenous", # I checked that all the combined administration are IV
     TRUE                              ~ route
@@
   mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
-  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
+  mutate(amount = rowSums(select(.,starts_with("amount_")), na.rm = TRUE)) %>%
   # Found ug, ml, Ea, and NA they are all good, but 
@@
     TRUE                        ~ amount
-  )) %>%
-
-  mutate(drugname_type = case_when(
-    str_detect(drugname, "platin")       ~ "platin",
-    str_detect(drugname, "taxel")        ~ "taxel"
-  ))
+  ))# %>%
+
+  # mutate(drugname_type = case_when(
+  #   str_detect(drugname, "platin")       ~ "platin",
+  #   str_detect(drugname, "taxel")        ~ "taxel"
+  # ))
 ```
@@
 ```{r line coding}
-therapy_line <- drugs1 %>% 
-  # bind again with clinical - easier that way
+therapy_line <- combined_drugs %>% 
+  # bind again with clinical - was lost while summarizing
   inner_join(., clinical_data, 
@@
   arrange(patientid, episodedate) %>% 
-  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
+  # Define Adjuvant, Neoadjuvant, chemo or surgery
   mutate(chemotherapy_type = case_when(
@@
   mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
-  fill(had_neo, .direction = "updown") %>% 
   mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
-  fill(had_adj, .direction = "updown") %>% 
+  fill(had_neo, had_adj, .direction = "updown") %>% 
   mutate(treatment_sequence = case_when(
@@
 
-  # 5.Redefine line number based on the original linenumber variable and the surgery date----
+  # Redefine line number based on the original linenumber variable and the surgery date
   mutate(linenumber_n = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  
+  # Redefine line number based on the new linenumber variable and if a switch 
+  # to maintenance is detected within the line
   group_by(patientid, linenumber_n, ismaintenancetherapy) %>% 
@@
          maint_rank = ifelse(maint_rank == 1, 1, 0)) %>% 
-
   group_by(patientid) %>% 
   mutate(linenumber_new = cumsum(maint_rank)) %>%  
-  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird F0F1324B863A8
-  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
+  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 F0F1324B863A8
+  select(patientid, linename, linenumber, linenumber_new, drugname, 
+         episodedate, surgerydate, chemotherapy_type, everything()) %>% 
   ungroup() %>% 
-
+  # Define line number restarting to 1 for each chemotherapy_type
   group_by(patientid, chemotherapy_type) %>% 
@@
   ungroup() %>% 
+  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
+  # Redefine line dates
+  group_by(patientid, linenumber_new) %>% 
+  mutate(linestartdate = min(episodedate)) %>% 
+  mutate(lineenddate = max(episodedate)) %>% 
+  ungroup() %>% 
+  select(-c(linenumber_n, maint_rank))
+
   # 6.Add a 30 day rule to switch linenumber----
@@
 
-  # 7.Calculate cycle for each line----
-  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
-  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
-  mutate(#drugname_count_perline = n(),
-         drugname_count_perline = case_when(
+```
+
+```{r cycle coding}
+therapy_cycle <- therapy_line %>% 
+  # Define cycle for each line
+  # F003F2BEEDB37 need to change drugname pacli = pacli bp
+  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  
+  # Need the number of time of the "major" drug is seen in the line
+  group_by(patientid, linenumber_new, cycle_drugname) %>%
+  mutate(drugname_count_perline = case_when(
            str_detect(drugname, "carboplatin|paclitaxel")     ~ n()
-         )
-           ) %>%  # F0000AD999ABF
+         )) %>%
   ungroup() %>% 
-  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
-  group_by(patientid, linenumber_new) %>% 
-  mutate(linestartdate_new = min(episodedate)) %>% 
-  mutate(lineenddate_new = max(episodedate)) %>% 
-  ungroup()
-```
-
-```{r cycle coding}
-# Code cycle number
-therapy_cycle <- therapy_line %>% 
   arrange(patientid, episodedate, drugname) %>% 
   group_by(patientid, linenumber_new) %>%
-  # Need the number of time of the "major" drug is seen in the line
+  # Take the major drugname as a mark of new cycle start
   mutate(cycle_count_perline = min(drugname_count_perline, na.rm = TRUE)) %>%
@@
   # select(-drugname_count_perline) %>% 
-  group_by(patientid, linenumber_new, cycle_major_drugname) %>%
-  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
-  # F01D908A013B7 has more pacli at the end but in the same line
-
-  # + What to do when it is a cycle change F003F2BEEDB37 ,
-
-  # group_by(patientid, linenumber_new, cycle_inc) %>%
-  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
-  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
+  # Code cycle number based on when major drug name appear again
+  group_by(patientid, linenumber_new, drugname, cycle_major_drugname) %>%
+  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 inversed dose dense------------------
+  # F01D908A013B7 weird dose dense
+
+  # F003F2BEEDB37 change of dose dense 50% ok? ---------------------------------------------------------------
+
   arrange(patientid, episodedate, cycle_increment) %>% 
   group_by(patientid, linenumber_new) %>%
-  # mutate(cycle_increment = cycle_inc) %>% 
-  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
+  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9 ok, FE593EDF5586A has a switched drugs will be removed
   group_by(patientid, chemotherapy_type, cycle_increment) %>% 
+  # Code is_dose_dense to be 1 for the first drug in the cycle
   mutate(is_dose_dense = row_number(cycle_increment),
@@
   group_by(patientid) %>% 
-  mutate(total_cycle_increment = #case_when(
-           # ismaintenancetherapy == "FALSE"            ~ 
-           row_number(is_dose_dense)
-         # )
+  mutate(total_cycle_increment = row_number(is_dose_dense)
          ) %>% 
+  group_by(patientid, linenumber_adj) %>% 
   fill(total_cycle_increment, .direction = "downup") %>% 
@@
   # Look at dose dense
+  # Code how many time a drug comes up in a cycle
   group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
@@
   filter(route == "Intravenous") %>% 
-  # 1. 60 days rule between diagnosis and treatment # Loss 1
+  # step 1: Flatiron recommendation cleanup
+  # 90 days rule between diagnosis and treatment
   group_by(patientid) %>% 
   mutate(first_drug_date = first(episodedate)) %>% 
+  ungroup() %>% 
   mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
@@
   )) %>% 
-  ungroup() %>% 
+  # 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis
   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
@@
   ) %>% 
+  mutate(flatiron_rules = case_when(
+    days_at_first_treatment > 90                 ~ "exclude",
+    thirty_days_exclusion <= 30                  ~ "exclude",
+    exclude == "1"                               ~ "exclude"
+  )) %>%
   group_by(patientid) %>% 
+  fill(flatiron_rules, .direction = "downup") %>% 
+  ungroup() %>%
+
+  # step 2: Filter patients with clinical characteristics fitting to the study criteria
+  # include only patients who received platin and/or taxane
   mutate(had_carbo_pacli = case_when(
@@
   )) %>% 
+  group_by(patientid) %>% 
   fill(had_carbo_pacli, .direction = "updown") %>% 
   ungroup() %>% 
-  mutate(interval_surgery_to_adj_start = case_when(
-      chemotherapy_type == "Adjuvant" &
-        linenumber_adj == 1       
-      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
-    ),
-  ) %>% 
-  mutate(ex = case_when(
-    interval_surgery_to_adj_start > 3                  ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(ex, .direction = "updown") %>% 
-  ungroup() %>%
-
-  group_by(patientid) %>% 
-  mutate(neo_more_more_than_1line = case_when(
-    chemotherapy_type == "Neoadjuvant" &
-           linenumber_new != 1                 ~ "exclude"
-  )) %>% 
-  fill(neo_more_more_than_1line, .direction = "updown") %>% 
-  ungroup() %>% 
-  mutate(whole_frontline_is_maintenance = case_when(
-    (linenumber_new == 1 &
-    ismaintenancetherapy == "TRUE") |
-    (linenumber_new == 2 &
-      therapy == "Upfront Chemo" &
-    ismaintenancetherapy == "TRUE")            ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(whole_frontline_is_maintenance, .direction = "updown") %>% 
-  ungroup() %>% 
-  mutate(too_many_cycle = case_when(
-    (linenumber_new == 1 &
-       therapy == "Upfront Chemo" &
-       total_cycle_increment > 6) |
-
-      (linenumber_new == 2 &
-         therapy == "Upfront Chemo" &
-         total_cycle_increment > 9) |
-
-      (linenumber_new == 1 &
-         therapy == "Upfront Surgery" &
-         total_cycle_increment > 9)             ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(too_many_cycle, .direction = "updown") %>%
-  ungroup() %>%
-
-  mutate(wrong_pacli_dosedense = case_when(
-    drugname == "paclitaxel" &
-      is.na(too_many_cycle) &
-      (dose_dense == 2 |
-      dose_dense > 3) &
-
-      ((linenumber_new == 1 &
-       therapy == "Upfront Chemo") |
-
-      (linenumber_new == 2 &
-         therapy == "Upfront Chemo") |
-
-      (linenumber_new == 1 &
-         therapy == "Upfront Surgery"))
-    ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
-  ungroup() %>% 
-  mutate(switch_drugs = case_when(
-    str_detect(linename, "Pacli") & 
-      drugname == "docetaxel" & 
-      linenumber_adj == 1                      ~ "exclude",
-    str_detect(linename, "Car") & 
-      drugname == "cisplatin" & 
-      linenumber_adj == 1                      ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(switch_drugs, .direction = "updown") %>% 
-  ungroup() %>%
-
+  # include patients with single or dual P/T +/- Bev as frontline treatment
   mutate(line_keep = case_when(# F002B429BE6C6
@@
   ungroup() %>%
-  mutate(flatiron_rules = case_when(
-    days_at_first_treatment > 90                          ~ "exclude",
-    thirty_days_exclusion <= 30                  ~ "exclude",
-    exclude == "1"                               ~ "exclude"
+
+  # step 3: Filter out patients with missing data
+  # remove patients with long gap between surgery and adjuvant start (3 months)
+  mutate(interval_surgery_to_adj_start = case_when(
+      chemotherapy_type == "Adjuvant" &
+        linenumber_adj == 1       
+      ~ interval(start = surgerydate, end = linestartdate) / duration(n = 1, units = "months")
+    )) %>% 
+  mutate(gap_surg_drugs = case_when(
+    interval_surgery_to_adj_start > 3                  ~ "exclude"
   )) %>% 
   group_by(patientid) %>% 
-  fill(flatiron_rules, .direction = "downup") %>% 
+  fill(gap_surg_drugs, .direction = "updown") %>% 
+  ungroup() %>%
+
+  # step 4: Include patients with treatments following the standard of clinical care
+  # exclude patients with more than 1 line as Neo
+  mutate(neo_more_more_than_1line = case_when(
+    chemotherapy_type == "Neoadjuvant" &
+           linenumber_new != 1                 ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>% 
+  fill(neo_more_more_than_1line, .direction = "updown") %>% 
+  ungroup() %>% 
+  # exclude patients with maintenance within their frontline
+  mutate(frontline_has_maintenance = case_when(
+    linenumber_adj == 1 &
+    ismaintenancetherapy == "TRUE"             ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>% 
+  fill(frontline_has_maintenance, .direction = "updown") %>% 
+  ungroup() %>% 
+  # exclude patients with more than 6 cycles in Neo, more than 9 cycles total 
+  # in upfront chemo or more than 9 cycles in upfront surgery
+  mutate(too_many_cycle = case_when(
+    (linenumber_new == 1 &
+       therapy == "Upfront Chemo" &
+       total_cycle_increment > 6) |
+
+      (linenumber_new == 2 &
+         therapy == "Upfront Chemo" &
+         total_cycle_increment > 9) |
+
+      (linenumber_new == 1 &
+         therapy == "Upfront Surgery" &
+         total_cycle_increment > 9)             ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(too_many_cycle, .direction = "updown") %>%
+  ungroup() %>% 
+  # Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
+  # Removes also the patients who has only carbo or only pacli
+  # dose_dense will need to be changed if we change and include these patients
+  arrange(patientid, episodedate, drugname) %>% 
+  mutate(wrong_pacli_dosedense = case_when(
+    drugname == "paclitaxel" &
+      is.na(too_many_cycle) &
+      (dose_dense == 2 |
+      dose_dense > 3) &
+      linenumber_adj == 1
+      # ((linenumber_new == 1 &
+      #  therapy == "Upfront Chemo") |
+      # (linenumber_new == 2 &
+      #    therapy == "Upfront Chemo") |
+      # (linenumber_new == 1 &
+      #    therapy == "Upfront Surgery"))
+    ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
+  ungroup() %>% 
+  # Exclude patients who switch drug within a line
+  mutate(switch_drugs = case_when(
+    str_detect(linename, "Pacli") & 
+      drugname == "docetaxel" & 
+      linenumber_adj == 1                      ~ "exclude",
+    str_detect(linename, "Car") & 
+      drugname == "cisplatin" & 
+      linenumber_adj == 1                      ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(switch_drugs, .direction = "updown") %>% 
   ungroup()
@@
 missing_data <- missing_data %>%
-  filter(is.na(ex))
+  filter(is.na(gap_surg_drugs))
 
@@
 
-## 4. step 4: Include patients with treatments following the standart of clinical care
+## 4. step 4: Include patients with treatments following the standard of clinical care
 
@@
 ```{r}
-standart_care <- missing_data %>% 
+standard_care <- missing_data %>% 
   # Remove patients with more than 1 line as Neo
@@
 
-standart_care <- standart_care %>% 
-  filter(is.na(whole_frontline_is_maintenance))
-
-standart_care <- standart_care %>% 
+standard_care <- standard_care %>% 
+  filter(is.na(frontline_has_maintenance))
+
+standard_care <- standard_care %>% 
   filter(is.na(too_many_cycle))
 ```
-**We have `r standart_care %>% distinct(patientid) %>% nrow()` patients.**
+**We have `r standard_care %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 ```{r}
-Frontline <- standart_care %>% 
+Frontline <- standard_care %>% 
   filter(is.na(wrong_pacli_dosedense))
 
-# standart_care %>% 
+# standard_care %>% 
 #   mutate(n_dose_dense = factor(n_dose_dense)) %>% 
@@
     filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
-    filter(is.na(ex)) %>%
+    filter(is.na(gap_surg_drugs)) %>%
     filter(days_at_first_drug >= 0 &
@@
 
-    standart_care = missing_data %>% 
+    standard_care = missing_data %>% 
     filter(is.na(neo_more_more_than_1line)) %>%
-    filter(is.na(whole_frontline_is_maintenance)) %>%
+    filter(is.na(frontline_has_maintenance)) %>%
     filter(is.na(too_many_cycle)),
 
-  Frontline = standart_care %>% 
+  Frontline = standard_care %>% 
     filter(is.na(wrong_pacli_dosedense)),
@@
     missing_data = "missing_data",
-    standart_care = "standart_care",
+    standard_care = "standard_care",
     Frontline = "Frontline",
@@
   consort_box_add(
-    "standart_care", 5, 30, cohort_count_adorn(study_cohorts, standart_care)
+    "standard_care", 5, 30, cohort_count_adorn(study_cohorts, standard_care)
   ) %>%
@@
   consort_arrow_add(
-    end = "standart_care", end_side = "left", start_x = 0, start_y = 30
+    end = "standard_care", end_side = "left", start_x = 0, start_y = 30
   ) %>%
@@
   geom_consort() +
-  theme_consort(margin_h = 18, margin_v = 1)
+  theme_consort(margin_h = 8, margin_v = 1)
 ```

### 2021-12-16 Rmd/rdi analysis.Rmd
Update imputation

@@
 library(ggconsort)
-# flatiron_rec <- Frontline_adjusted %>% 
-#   filter(is.na(flatiron_rules))
-# study_criteria <- flatiron_rec %>% 
-#   filter(!is.na(histology))
-# study_criteria <- study_criteria %>%
-#   filter(!is.na(surgerydate))
-# study_criteria <- study_criteria %>%
-#   filter(had_carbo_pacli == "Yes")
-# study_criteria <- study_criteria %>% 
-#   filter(treatment_sequence == "neo + surg + adj" |
-#            treatment_sequence == "surg + adj")
-# study_criteria <- study_criteria %>%
-#   filter(is.na(line_keep))
-#
-
 study_cohorts <- 
@@
   consort_box_add(
-    "study_criteria", 5, 40, cohort_count_adorn(study_cohorts, study_criteria)
+    "study_criteria", 5, 35, cohort_count_adorn(study_cohorts, study_criteria)
   ) %>%
   consort_box_add(
-    "missing_data", 5, 35, cohort_count_adorn(study_cohorts, missing_data)
+    "missing_data", 5, 30, cohort_count_adorn(study_cohorts, missing_data)
   ) %>%
   consort_box_add(
-    "standard_care", 5, 30, cohort_count_adorn(study_cohorts, standard_care)
+    "standard_care", 5, 25, cohort_count_adorn(study_cohorts, standard_care)
   ) %>%
   consort_box_add(
-    "Frontline", 5, 25, cohort_count_adorn(study_cohorts, Frontline)
+    "Frontline", 5, 20, cohort_count_adorn(study_cohorts, Frontline)
   ) %>%
   consort_box_add(
-    "Frontline1", 0, 20, cohort_count_adorn(study_cohorts, Frontline1)
+    "Frontline1", 0, 15, cohort_count_adorn(study_cohorts, Frontline1)
   ) %>%
@@
   consort_arrow_add(
-    end = "study_criteria", end_side = "left", start_x = 0, start_y = 40
+    end = "study_criteria", end_side = "left", start_x = 0, start_y = 35
   ) %>%
   consort_arrow_add(
-    end = "missing_data", end_side = "left", start_x = 0, start_y = 35
+    end = "missing_data", end_side = "left", start_x = 0, start_y = 30
   ) %>%
   consort_arrow_add(
-    end = "standard_care", end_side = "left", start_x = 0, start_y = 30
+    end = "standard_care", end_side = "left", start_x = 0, start_y = 25
   ) %>%
   consort_arrow_add(
-    end = "Frontline", end_side = "left", start_x = 0, start_y = 25
+    end = "Frontline", end_side = "left", start_x = 0, start_y = 20
   ) %>%
@@
   geom_consort() +
-  theme_consort(margin_h = 8, margin_v = 1)
+  theme_consort(margin_h = 18, margin_v = 1)
 ```
@@
 
-           "histology", imp_histology, "stagecat", imp_stagecat,
+           "histology", "stagecat", imp_stagecat,
 
@@
   distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= imp_histology))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Histology")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= stagecat))+
@@
   ggplot(aes(x= raceeth, fill = histology))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Histology")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = imp_histology))+
   geom_bar(position = "fill")+
@@
 
-<span style="color:green">**RDI summary table**</span>
+<span style="color:green">**Table 6: RDI summary table**</span>
 
@@
 set_gtsummary_theme(my_theme)
-trial %>%
-  select(age, grade, trt) %>%
-  tbl_summary(by = trt) %>%
-  add_stat_label() %>%
-  add_p() %>%
-  as_gt() 
+
+# trial %>%
+#   select(age, grade, trt) %>%
+#   tbl_summary(by = trt) %>%
+#   add_stat_label() %>%
+#   add_p() %>%
+#   as_gt() 
 ```
@@
   tbl_summary(by = therapy) %>% 
-  bold_labels()
+  bold_labels() %>% add_n() %>% add_overall()
 
@@
   tbl_summary(by = therapy) %>%
-  bold_labels()
+  bold_labels() %>% add_n() %>% add_overall()
 
@@
               ) %>%
-  bold_labels()
+  bold_labels() %>% add_n() %>% add_overall()
 
@@
               ) %>%
-  bold_labels()
+  bold_labels() %>% add_n() %>% add_overall()
 tbl5 <- Frontline %>% filter(dose_dense == 3) %>%
@@
               type = list(`RDI (continous)` ~ "continuous")) %>%
-  bold_labels()
+  bold_labels() %>% add_n() %>% add_overall()
 tbl6 <- Frontline %>% filter(dose_dense == 3) %>%
@@
               type = list(`RDI (continous)` ~ "continuous")) %>%
-  bold_labels()
+  bold_labels() %>% add_n() %>% add_overall()
 
@@
 
-<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
+<span style="color:green">**Table 7: Summary RDI data by race and bmi**</span>  
 Removing the overall on the right side? Or do you want the tables separated?
@@
 
-<span style="color:green">**Table 6 HR**</span>
+<span style="color:green">**Table 8 HR Univariable**</span>
 
@@
 ### RDI group
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking` 
+<span style="color:green">**Table 9 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
 ```{r Table 5 HR adjusted rdi group}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ### Continous
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking` 
+<span style="color:green">**Table 10 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
 ```{r rdi continous}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ### RDI group
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking`
+<span style="color:green">**Table 11 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
 ```{r Table 5 HR adjusted rdi group adjusted by other drug}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ### Continous
+<span style="color:green">**Table 12 HR Multivariable**</span>
+
 `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat` 
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

### 2021-12-16 R/2.data cleaning.R

@@ -591,13 +591,15 @@ clinical_data <- clinical_data %>%
 
 # Imputation for stagecat, debulking status, histology
 library(mice)
-imputed_data <- mice(clinical_data %>% select(-contains("date")), 
+imputed_data <- mice(clinical_data %>% 
+                       select(-contains("date")), 
                      m=5, maxit = 50, seed = 500)
 
 ignore_imp <- clinical_data %>% mutate(vec = clinical_data$issurgery != "Yes")
 # c(ignore_imp$vec)
 # c(rep(FALSE, 3000), rep(TRUE, 3687))
-imputed_data_debul <- mice(clinical_data %>% select(-contains("date"), -diff_surg_dx), 
+imputed_data_debul <- mice(clinical_data %>% 
+                             select(-contains("date")), 
                            ignore = c(ignore_imp$vec),
                            m=5, maxit = 50, seed = 500)
 
@@ -605,13 +607,11 @@ summary(imputed_data)
 summary(imputed_data_debul)
 # Look at original data
 clinical_data %>% 
-  select(histology, stagecat, debulking) %>%
+  select(stagecat, debulking) %>%
   tbl_summary()
 # Look at results
-table(imputed_data$imp$histology[1])
 table(imputed_data_debul$imp$debulking[1])
 # Look at proportion
-prop.table(table(imputed_data$imp$histology[2]))*100
 prop.table(table(imputed_data$imp$stagecat[2]))*100
 prop.table(table(imputed_data_debul$imp$debulking[1]))*100
 # get complete data from the best imputation
@@ -619,8 +619,7 @@ imputed_data <- complete(imputed_data,2)
 imputed_data_debul <- complete(imputed_data_debul,1)
 
 imputed_data <- imputed_data %>% 
-  rename(imp_histology = histology, 
-         imp_stagecat = stagecat)
+  rename(imp_stagecat = stagecat)
 imputed_data_debul <- imputed_data_debul %>% 
   rename(imp_debulking = debulking)
 

### 2021-12-17 Rmd/rdi analysis.Rmd
Modify imputation

@@
 # **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
+
+# Imputation for stagecat and debulking status
+
+https://bookdown.org/mwheymans/bookmi/data-analysis-after-multiple-imputation.html#data-analysis-in-spss
+https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf
+
+Select the variables that may be important for predicting stagecat and debulking status:  
+patientid, month_at_os, vitalstatus, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, therapy.  
+Look at the Cox regression model before imputation.
+```{r}
+data <- Frontline %>% select(patientid, month_at_os, vitalstatus, 
+                                 raceeth, diagnosisdate, surgerydate,
+                                 ageatdx, stagecat, debulking, histology,
+                                 therapy)
+nonimp_cox_model <-
+  coxph(Surv(month_at_os, vitalstatus) ~ raceeth + ageatdx + stagecat + debulking + histology + therapy,
+        data = data)
+nonimp_cox_model
+
+Hazard <- nelsonaalen(data, month_at_os, vitalstatus)
+dataset <- data.frame(data, Hazard)
+```
+
+Start imputation to look at matrix
+```{r}
+Cox.imp <- mice(dataset, m=1, maxit=0, seed=2795, printFlag=F)
+# summary(Cox.imp)
+Pred <- Cox.imp$predictorMatrix
+# Pred["debulking", "month_at_os"] <- 0
+Pred
+```
+
+Humm  
+patientid is not used which is good. But therapy is not. -> fix that
+```{r}
+Pred[, "therapy"] <- 1
+Pred["therapy", "therapy"] <- 0
+Pred
+```
+
+Imputation and cox regression model on imputed data using the new predictor matrix.
+```{r}
+# Start imputations using mice
+Cox.imp <- mice(dataset, m=5, maxit=50, 
+                predictorMatrix=Pred,
+                seed=123, printFlag=F)
+check1 <- with(data = Cox.imp,
+       exp = coxph(
+         Surv(month_at_os, vitalstatus) ~ raceeth + ageatdx + stagecat + debulking + histology + therapy
+       ))
+pool(check1)$pooled
+```
+
+Do m = 36
+```{r}
+Cox.imp <- mice(dataset, m=36, maxit=50, 
+                predictorMatrix=Pred,
+                seed=123, printFlag=F)
+
+fit.Cox <-
+  with(data = Cox.imp,
+       exp = coxph(
+         Surv(month_at_os, vitalstatus) ~ raceeth + ageatdx + stagecat + debulking + histology + therapy
+       ))
+
+summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
+  kableExtra::kable() %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
+```
+Results is exponentiated.
+
+Complete the data and merge with original
+```{r}
+imputed_data <- complete(Cox.imp, include = FALSE) %>% 
+  rename(imp_stagecat = stagecat, imp_debulking = debulking)
+
+Frontline <- 
+  full_join(Frontline, imputed_data %>% 
+              select(patientid, starts_with("imp_")), 
+            by = "patientid") 
+Frontline_adjusted <- 
+  full_join(Frontline_adjusted, imputed_data %>% 
+              select(patientid, starts_with("imp_")), 
+            by = "patientid") 
+```
 

### 2021-12-17 R/2.data cleaning.R

@@ -591,37 +591,107 @@ clinical_data <- clinical_data %>%
 
 # Imputation for stagecat, debulking status, histology
 library(mice)
-imputed_data <- mice(clinical_data %>% 
-                       select(-contains("date")), 
-                     m=5, maxit = 50, seed = 500)
+# imputed_data <- mice(clinical_data %>% 
+#                        select(-contains("date")), 
+#                      m=5, maxit = 50, seed = 500)
+# 
+# ignore_imp <- clinical_data %>% mutate(vec = clinical_data$issurgery != "Yes")
+# # c(ignore_imp$vec)
+# # c(rep(FALSE, 3000), rep(TRUE, 3687))
+# imputed_data_debul <- mice(clinical_data %>% 
+#                              select(-contains("date")), 
+#                            ignore = c(ignore_imp$vec),
+#                            m=5, maxit = 50, seed = 500)
+# 
+# summary(imputed_data)
+# summary(imputed_data_debul)
+# # Look at original data
+# clinical_data %>% 
+#   select(stagecat, debulking) %>%
+#   tbl_summary()
+# # Look at results
+# table(imputed_data_debul$imp$debulking[1])
+# # Look at proportion
+# prop.table(table(imputed_data$imp$stagecat[2]))*100
+# prop.table(table(imputed_data_debul$imp$debulking[1]))*100
+# # get complete data from the best imputation
+# imputed_data <- complete(imputed_data,2)
+# imputed_data_debul <- complete(imputed_data_debul,1)
+# 
+# imputed_data <- imputed_data %>% 
+#   rename(imp_stagecat = stagecat)
+# imputed_data_debul <- imputed_data_debul %>% 
+#   rename(imp_debulking = debulking)
 
-ignore_imp <- clinical_data %>% mutate(vec = clinical_data$issurgery != "Yes")
-# c(ignore_imp$vec)
-# c(rep(FALSE, 3000), rep(TRUE, 3687))
-imputed_data_debul <- mice(clinical_data %>% 
-                             select(-contains("date")), 
-                           ignore = c(ignore_imp$vec),
-                           m=5, maxit = 50, seed = 500)
 
-summary(imputed_data)
-summary(imputed_data_debul)
-# Look at original data
-clinical_data %>% 
-  select(stagecat, debulking) %>%
-  tbl_summary()
[…]

### 2021-12-22 Rmd/rdi analysis.Rmd
Fix imputation

--- 2021-12-16 Rmd/rdi analysis.Rmd
@@
 library(survival)
+library(mice)
 ```
@@
 RDI_data <- Treatment %>% 
-  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
+  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
+  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))
 ```
@@
   # remove these patients who switched C > C 
-  filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
-            !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) & 
-            therapy == "Upfront Chemo") |
-           (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
-            therapy == "Upfront Surgery")))
+  filter((
+    therapy == "Upfront Chemo" &
+      (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
+         !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
+  ) | (
+    therapy == "Upfront Surgery" &
+      (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
+  )
+  )
 ```
@@
 ```{r}
-Frontline <- standard_care %>% 
+Frontline_adjusted <- standard_care %>% 
   filter(is.na(wrong_pacli_dosedense))
@@
 ```
-**We have `r Frontline %>% distinct(patientid) %>% nrow()` patients.**
+**We have `r Frontline_adjusted %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 - exclude patients who switch drug within a line
-
-<!-- `r Frontline %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.
--->
-<!-- `r Frontline %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.
--->
 
@@
 
-<!-- `r Frontline %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.
--->
-<!-- I am removing these patients   -->
-
 <!-- Patients left: -->
 ```{r}
-Frontline <- Frontline %>%
+Frontline_adjusted <- Frontline_adjusted %>%
   filter(is.na(switch_drugs))
@@
 
-# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
+# **The final number of patients in the dataset is `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**
+
+# Imputation for stagecat and debulking status
+
+https://bookdown.org/mwheymans/bookmi/data-analysis-after-multiple-imputation.html#data-analysis-in-spss
+https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf
+
+Select the variables that may be important for predicting stagecat and debulking status:  
+patientid, month_at_os, vitalstatus, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
+Look at the Cox regression model before imputation.
+
+### For Upfront Chemo
+```{r}
+data <- Frontline_adjusted %>% 
+  filter(therapy == "Upfront Chemo") %>% 
+  select(patientid, month_at_os, vitalstatus, 
+         raceeth, diagnosisdate, surgerydate,
+         ageatdx, stagecat, debulking, histology,
+         RDI_carbo_neo, RDI_pacli_neo, 
+         RDI_carbo_adj, RDI_pacli_adj
+         # therapy
+  )
+nonimp_cox_model <-
+  coxph(Surv(month_at_os, vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+        data = data)
+nonimp_cox_model
+
+Hazard <- nelsonaalen(data, month_at_os, vitalstatus)
+dataset <- data.frame(data, Hazard)
+```
+
+Start imputation to look at matrix
+```{r}
+Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
+# summary(Cox.imp)
+Pred <- Cox.imp$predictorMatrix
+# Pred["debulking", "month_at_os"] <- 0
+Pred
+```
+
+patientid is not used which is good. But SURGERYDATE IS NOT.
+```{r}
+Pred[, "surgerydate"] <- 1
+Pred["surgerydate", "surgerydate"] <- 0
+Pred
+```
+
+Imputation and cox regression model on imputed data using the new predictor matrix.
+```{r}
+# Start imputations using mice
+Cox.imp <- mice(dataset, m=5, maxit=50, 
+                predictorMatrix=Pred,
+                seed=123, printFlag=F)
+check1 <- with(data = Cox.imp,
+       exp = coxph(
+         Surv(month_at_os, vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+       ))
+pool(check1)$pooled
+```
+
+Do m = 30 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.30 that we multiply by 100)
+```{r}
+Cox.imp <- mice(dataset, m=30, maxit=50, 
+                predictorMatrix=Pred,
+                seed=123, printFlag=F)
+
+fit.Cox <-
+  with(data = Cox.imp,
+       exp = coxph(
+         Surv(month_at_os, vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+       ))
+
+summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
+  kableExtra::kable() %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
+```
+Above results are exponentiated (imputed data).  
+As a reminder before imputation results are :
+```{r}
+nonimp_cox_model
+```
+
+Complete the chemo data and merge with original
+```{r}
+imputed_data_chemo <- complete(Cox.imp, include = FALSE) %>% 
+  rename(imp_stagecat = stagecat, imp_debulking = debulking)
+```
+
+Select the variables that may be important for predicting stagecat and debulking status:  
+patientid, month_at_os, vitalstatus, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
+
+### For Upfront Surgery
+```{r}
+data <- Frontline_adjusted %>% 
+  filter(therapy == "Upfront Surgery") %>% 
+  select(patientid, month_at_os, vitalstatus, 
+         raceeth, diagnosisdate, surgerydate,
+         ageatdx, stagecat, debulking, histology,
+         RDI_carbo_adj, RDI_pacli_adj
+         # therapy
+  )
+nonimp_cox_model <-
+  coxph(Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+        data = data)
+nonimp_cox_model
+
+Hazard <- nelsonaalen(data, month_at_os, vitalstatus)
+dataset <- data.frame(data, Hazard)
+```
+
+Start imputation to look at matrix
+```{r}
+Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
+# summary(Cox.imp)
+Pred <- Cox.imp$predictorMatrix
+# Pred["debulking", "month_at_os"] <- 0
+Pred
+```
+
+patientid is not used which is good. But SURGERYDATE IS NOT
+```{r}
+Pred[, "surgerydate"] <- 1
+Pred["surgerydate", "surgerydate"] <- 0
+Pred
+```
+
+Imputation and cox regression model on imputed data using the new predictor matrix.
+```{r}
+# Start imputations using mice
+Cox.imp <- mice(dataset, m=5, maxit=50, 
+                predictorMatrix=Pred,
+                seed=123, printFlag=F)
+check1 <- with(data = Cox.imp,
+       exp = coxph(
+         Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+       ))
+pool(check1)$pooled
+```
+
+Do m = 10 (The max fmi = 0.099 that we multiply by 100)
+```{r}
+Cox.imp <- mice(dataset, m=10, maxit=50, 
+                predictorMatrix=Pred,
+                seed=123, printFlag=F)
+
+fit.Cox <-
+  with(data = Cox.imp,
+       exp = coxph(
+         Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+       ))
+
+summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
+  kableExtra::kable() %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
+```
+Above results are exponentiated (imputed data).  
+As a reminder before imputation results are :
+```{r}
+nonimp_cox_model
+```
+
+Complete the data and merge with original
+```{r}
+imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
+  rename(imp_stagecat = stagecat, imp_debulking = debulking)
+
+imputed_data <- bind_rows(imputed_data_chemo, imputed_data_surg)
+
+# Frontline <- 
+#   full_join(Frontline, imputed_data %>% 
+#               select(patientid, starts_with("imp_")), 
+#             by = "patientid") 
+Frontline_adjusted <- 
+  full_join(Frontline_adjusted, imputed_data %>% 
+              select(patientid, starts_with("imp_")), 
+            by = "patientid") 
+```
 
@@
   Treatment %>% 
-  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
+  filter(str_detect(patientid, paste(Frontline_adjusted$patientid, collapse = "|"))) %>% 
   arrange(patientid, episodedate, drugname)
@@
 <br>
+
+```{r}
+Frontline <- Frontline_adjusted
+```
 
@@
 ```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
 <!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
@@
 ```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
 <!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
@@
 ```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
 <!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
 ```{r rdi continous adjusted by other drug}
@@
              event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 
+# Complete case HR analysis
+
 ```{r echo=FALSE, out.width='30%'}

### 2021-12-22 R/2.data cleaning.R

@@ -589,124 +589,6 @@ clinical_data <- clinical_data %>%
   mutate(debulking = str_replace(debulking, "Unknown|No surgery", NA_character_)) %>% 
   mutate(across(.cols = c(stagecat, debulking), ~as.factor(.)))
 
-# Imputation for stagecat, debulking status, histology
-library(mice)
-# imputed_data <- mice(clinical_data %>% 
-#                        select(-contains("date")), 
-#                      m=5, maxit = 50, seed = 500)
-# 
-# ignore_imp <- clinical_data %>% mutate(vec = clinical_data$issurgery != "Yes")
-# # c(ignore_imp$vec)
-# # c(rep(FALSE, 3000), rep(TRUE, 3687))
-# imputed_data_debul <- mice(clinical_data %>% 
-#                              select(-contains("date")), 
-#                            ignore = c(ignore_imp$vec),
-#                            m=5, maxit = 50, seed = 500)
-# 
-# summary(imputed_data)
-# summary(imputed_data_debul)
-# # Look at original data
-# clinical_data %>% 
-#   select(stagecat, debulking) %>%
-#   tbl_summary()
-# # Look at results
-# table(imputed_data_debul$imp$debulking[1])
-# # Look at proportion
-# prop.table(table(imputed_data$imp$stagecat[2]))*100
-# prop.table(table(imputed_data_debul$imp$debulking[1]))*100
-# # get complete data from the best imputation
-# imputed_data <- complete(imputed_data,2)
-# imputed_data_debul <- complete(imputed_data_debul,1)
-# 
-# imputed_data <- imputed_data %>% 
-#   rename(imp_stagecat = stagecat)
-# imputed_data_debul <- imputed_data_debul %>% 
-#   rename(imp_debulking = debulking)
-
-
-# Imputation using Cox regression models
-
-# Compute the cumulative hazard, attach it to the dataset
-# and omit the ID variable (first column)
-# data <- clinical_data %>% select(-followuptime, 
-#                                  -followuptime_yr#, 
-#                                  # -followupdate
-#                                  )
-# 
-# data <- clinical_data %>% select(patientid, month_at_os, vitalstatus, 
-#                                  raceeth,
[…]

### 2021-12-22 Rmd/rdi analysis.Rmd
Add complete case analysis

@@
 
+## Multivariable
+### RDI group
+<span style="color:green">**Table 9 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat + histology + debulking` 
+```{r Table 5 HR adjusted rdi group}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
+
+<br>
+<br>
+
+### Continous
+<span style="color:green">**Table 10 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology + debulking` 
+```{r rdi continous}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
+<!-- RDI for paclitaxel is not a factor associated with survival. -->
+
+<br>
+<br>
+
+## Adjusted by other drug
+### RDI group
+<span style="color:green">**Table 11 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
+```{r Table 5 HR adjusted rdi group adjusted by other drug}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
+-->
+
+<br>
+<br>
+
+### Continous
+<span style="color:green">**Table 12 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking` 
+```{r rdi continous adjusted by other drug}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
 ```{r echo=FALSE, out.width='30%'}

### 2021-12-22 R/00.create main data.R
Load and recode new data

@@ -1,0 +1,197 @@
+# Import library
+library(tidyverse)
+
+#################################
+### Create main vital data ###
+#################################
+# Load data
+path <- fs::path("", "Volumes", "Peres_Research")
+vitals <- 
+  read_csv(paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/Vitals.csv"
+  ))
+labs <-
+  read_csv(paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/Lab.csv"
+  ))
+labs <-
+  read_csv("/Volumes/Peres_Research/Flatiron/Data from Flatiron/ovarian/Lab.csv")
+
+
+# Filter
+# Restricting vitals to only data on body height, body surface, and body weight
+vitals_anthro <-
+  vitals %>%
+  filter(
+    TestBaseName == "body height" |
+      TestBaseName == "body weight" |
+      TestBaseName == "body surface") %>% 
+  select(-c(LOINC)) %>% 
+  `colnames<-`(str_to_lower(colnames(.)))
+write_csv(
+  vitals_anthro,
+  paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/NEW_vitals_anthro.csv"
+  )
+)
+# Restricting labs to only creatinine
+labs_creat <- 
+  labs %>% 
+  filter(TestBaseName == "creatinine") %>% 
+  select(-c(LOINC, LabSource)) %>% 
+  `colnames<-`(str_to_lower(colnames(.)))
+write_csv(
+  labs_creat, 
+  paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/NEW_labs_creatinine.csv"
+  )
+)
+
+
+#################################
+### Create main clinical data ###
+#################################
+# Load data
+demos <- 
+  read_csv(paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/Demographics.csv"
+  ))
+mort <- 
+  read_csv(paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/Enhanced_Mortality_V2.csv"
+  ))
+dx <- 
+  read_csv(paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/Enhanced_Ovarian.csv"
+  ))
+visit <- 
[…]

### 2021-12-23 R/00.create main data.R
Finish creating new clinical

@@ -1,5 +1,6 @@
 # Import library
 library(tidyverse)
+library(lubridate)
 
 #################################
 ### Create main vital data ###
@@ -16,8 +17,6 @@ labs <-
     path,
     "/Flatiron/Data from Flatiron/edm_ovarian_472021/Lab.csv"
   ))
-labs <-
-  read_csv("/Volumes/Peres_Research/Flatiron/Data from Flatiron/ovarian/Lab.csv")
 
 
 # Filter
@@ -81,27 +80,240 @@ orals <-
     path,
     "/Flatiron/Data from Flatiron/edm_ovarian_472021/Enhanced_Ovarian_Orals.csv"
   ))
+episode <- 
+  read_csv(paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/DrugEpisode.csv"
+  ))
+biom <- 
+  read_csv(paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/Enhanced_OvarianBiomarkers.csv"
+  )) %>% 
+  `colnames<-`(str_to_lower(colnames(.)))
 
-# Create last visit date for censoring
-visit <- 
+# Prep biomarkers
+hrd <- biom %>% filter(biomarkername == "HRD")
+gis <- biom %>% filter(biomarkername == "GIS")
+brca <- biom %>% filter(biomarkername == "BRCA")
+
+######### BRCA data cleaning ##############
+brca <- brca %>% 
+  # recoding unknown tissue for BRCA using lab and test name
+  mutate(sampletype = case_when( 
+    sampletype == "Unknown/not documented" & 
+      (brca$testname == "Caris Life Sciences" |
+         testname == "Foundation Focus CDxBRCA" |
+         testname == "Foundation One" |
+         testname == "In-house pathology lab")             ~ "Tissue",
+    sampletype == "Unknown/not documented" & 
+      (testname == "GeneDx" |
+         testname == "Integrated Oncology/LabCorp" |
+         testname == "Invitae" |
+         testname == "Myriad MyRisk" |
+         testname == "Quest BRCAvantage")                  ~ "Blood",
+    TRUE                                                   ~ sampletype
+  ))
+
+# Creating different brca datasets
+brca_germ <- brca %>% filter(sampletype == "Blood" | sampletype == "Saliva")
+brca_tumor <- brca %>% filter(sampletype == "Tissue")
[…]

### 2021-12-23 R/function.R
Update drake

@@ -8,31 +8,31 @@ path <- fs::path("","Volumes","Peres_Research")
 # }
 data_import <- function(path){
   read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/NEW_ovarianCLEANwithbiom.csv"))
+                  "/Flatiron/Data from Flatiron/edm_ovarian_472021/NEW_ovarianCLEANwithbiom.csv"))
 }
 vitals_import <- function(path){
   read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/NEW_vitals_anthro.csv"))
+                  "/Flatiron/Data from Flatiron/edm_ovarian_472021/NEW_vitals_anthro.csv"))
 }
 
 cr_import <- function(path){
   read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/NEW_labs_creatinine.csv"))
+                  "/Flatiron/Data from Flatiron/edm_ovarian_472021/NEW_labs_creatinine.csv"))
 }
 
 auc_import <- function(path){
   read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/ovarian_medicationorder.csv"))
+                  "/Flatiron/Data from Flatiron/edm_ovarian_472021/MedicationOrder.csv"))
 }
 
 drugs_import <- function(path){
   read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/ovarian_drugepisode.csv"))
+                  "/Flatiron/Data from Flatiron/edm_ovarian_472021/DrugEpisode.csv"))
 }
 
 orderdrug_import <- function(path){
   read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/ovarian_medicationadministration.csv"))
+                  "/Flatiron/Data from Flatiron/edm_ovarian_472021/MedicationAdministration.csv"))
 }
 
 

### 2021-12-23 Rmd/rdi analysis.Rmd
Update cleaning and rmd with new data + add PH assumption

--- 2021-12-17 Rmd/rdi analysis.Rmd
@@
 **We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
-**We have `r drugs %>% distinct(patientid) %>% nrow()` patients info in clinical data.
+**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in clinical data.
 
@@
 drugs <- drugs %>% 
+  `colnames<-`(str_to_lower(colnames(.))) %>% 
   # Select only records for administration
@@
 
-# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
+# **The final number of patients in the dataset is `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**
 
@@
 Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os, vitalstatus, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, therapy.  
+patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
 Look at the Cox regression model before imputation.
-```{r}
-data <- Frontline %>% select(patientid, month_at_os, vitalstatus, 
+
+### For Upfront Chemo
+```{r}
+data <- Frontline_adjusted %>% 
+  filter(therapy == "Upfront Chemo") %>% 
+  select(patientid, month_at_os, vital_status, 
          raceeth, diagnosisdate, surgerydate,
          ageatdx, stagecat, debulking, histology,
-                                 therapy)
+         RDI_carbo_neo, RDI_pacli_neo, 
+         RDI_carbo_adj, RDI_pacli_adj
+         # therapy
+  )
 nonimp_cox_model <-
-  coxph(Surv(month_at_os, vitalstatus) ~ raceeth + ageatdx + stagecat + debulking + histology + therapy,
+  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
         data = data)
@@
 
-Hazard <- nelsonaalen(data, month_at_os, vitalstatus)
+Hazard <- nelsonaalen(data, month_at_os, vital_status)
 dataset <- data.frame(data, Hazard)
@@
 ```{r}
-Cox.imp <- mice(dataset, m=1, maxit=0, seed=2795, printFlag=F)
+Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
 # summary(Cox.imp)
@@
 
-Humm  
-patientid is not used which is good. But therapy is not. -> fix that
-```{r}
-Pred[, "therapy"] <- 1
-Pred["therapy", "therapy"] <- 0
+patientid is not used which is good. But SURGERYDATE IS NOT.
+```{r}
+Pred[, "surgerydate"] <- 1
+Pred["surgerydate", "surgerydate"] <- 0
 Pred
@@
        exp = coxph(
-         Surv(month_at_os, vitalstatus) ~ raceeth + ageatdx + stagecat + debulking + histology + therapy
+         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
        ))
@@
 
-Do m = 36
-```{r}
-Cox.imp <- mice(dataset, m=36, maxit=50, 
+Do m = 34 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.339 that we multiply by 100)
+```{r}
+Cox.imp <- mice(dataset, m=34, maxit=50, 
                 predictorMatrix=Pred,
@@
 ```
-Results is exponentiated.
+Above results are exponentiated (imputed data).  
+As a reminder before imputation results are :
+```{r}
+nonimp_cox_model
+```
+
+Complete the chemo data and merge with original
+```{r}
+imputed_data_chemo <- complete(Cox.imp, include = FALSE) %>% 
+  rename(imp_stagecat = stagecat, imp_debulking = debulking)
+```
+
+Select the variables that may be important for predicting stagecat and debulking status:  
+patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
+
+### For Upfront Surgery
+```{r}
+data <- Frontline_adjusted %>% 
+  filter(therapy == "Upfront Surgery") %>% 
+  select(patientid, month_at_os, vital_status, 
+         raceeth, diagnosisdate, surgerydate,
+         ageatdx, stagecat, debulking, histology,
+         RDI_carbo_adj, RDI_pacli_adj
+         # therapy
+  )
+nonimp_cox_model <-
+  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+        data = data)
+nonimp_cox_model
+
+Hazard <- nelsonaalen(data, month_at_os, vital_status)
+dataset <- data.frame(data, Hazard)
+```
+
+Start imputation to look at matrix
+```{r}
+Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
+# summary(Cox.imp)
+Pred <- Cox.imp$predictorMatrix
+# Pred["debulking", "month_at_os"] <- 0
+Pred
+```
+
+patientid is not used which is good. But SURGERYDATE IS NOT
+```{r}
+Pred[, "surgerydate"] <- 1
+Pred["surgerydate", "surgerydate"] <- 0
+Pred
+```
+
+Imputation and cox regression model on imputed data using the new predictor matrix.
+```{r}
+# Start imputations using mice
+Cox.imp <- mice(dataset, m=5, maxit=50, 
+                predictorMatrix=Pred,
+                seed=123, printFlag=F)
+check1 <- with(data = Cox.imp,
+       exp = coxph(
+         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+       ))
+pool(check1)$pooled
+```
+
+Do m = 17 (The max fmi = 0.166 that we multiply by 100)
+```{r}
+Cox.imp <- mice(dataset, m=17, maxit=50, 
+                predictorMatrix=Pred,
+                seed=123, printFlag=F)
+
+fit.Cox <-
+  with(data = Cox.imp,
+       exp = coxph(
+         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+       ))
+
+summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
+  kableExtra::kable() %>%
+  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
+```
+Above results are exponentiated (imputed data).  
+As a reminder before imputation results are :
+```{r}
+nonimp_cox_model
+```
 
@@
 ```{r}
-imputed_data <- complete(Cox.imp, include = FALSE) %>% 
+imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
   rename(imp_stagecat = stagecat, imp_debulking = debulking)
 
-Frontline <- 
-  full_join(Frontline, imputed_data %>% 
-              select(patientid, starts_with("imp_")), 
-            by = "patientid") 
+imputed_data <- bind_rows(imputed_data_chemo, imputed_data_surg)
+
+# Frontline <- 
+#   full_join(Frontline, imputed_data %>% 
+#               select(patientid, starts_with("imp_")), 
+#             by = "patientid") 
 Frontline_adjusted <- 
@@
 
+```{r}
+Frontline <- Frontline_adjusted
+```
+
 <!-- ## Missingness -->
@@
 # OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ raceeth, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 # OS by tstage
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ stagecat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ imp_stagecat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_stagecat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 # OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ bmi_cat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 # OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ raceeth, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 # OS by tstage
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ stagecat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ imp_stagecat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_stagecat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 # OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ bmi_cat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 ```{r treatment survival, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ 1, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ 1, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ debulking, data=Frontline %>%
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ imp_debulking, data=Frontline %>%
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 # OS by therapy
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ therapy, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 ```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ 1, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ debulking, data=Frontline %>%
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ imp_debulking, data=Frontline %>%
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
@@
 # OS by therapy
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ therapy, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 ```{r OS dx RDI, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_carbo_neo_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_neo_grp, 
                    data=Frontline %>% 
@@
 ) + guides(colour = guide_legend(ncol = 1))
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_pacli_neo_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_neo_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_pacli_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_adj_grp, 
                    data=Frontline %>% 
@@
 ```{r OS treatment RDI, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_carbo_neo_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo_grp, 
                    data=Frontline %>% 
@@
 ) + guides(colour = guide_legend(ncol = 1))
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_carbo_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_carbo_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_pacli_neo_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_neo_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_pacli_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_adj_grp, 
                    data=Frontline %>% 
@@
 # tbl1 <- tbl2 %>%
-#   select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
+#   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
 #   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
 #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
@@
 # tbl2 <- tbl2 %>%
-#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
 #   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
 #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 # tbl3 <- tbl3 %>%
-#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
 #   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
+#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
 #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 tbl1 <- tbl2 %>%
-  select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
+  select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 tbl1 <- tbl2 %>%
-  select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
+  select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- tbl2 %>%
-  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
+  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 tbl3 <- tbl3 %>%
-  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
+  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
 ```{r Table 5 HR adjusted rdi group}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ```
-<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-### Continous
-<span style="color:green">**Table 10 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
-```{r rdi continous}
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology` 
+```{r}
 tbl2 <- Frontline %>%
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ```
-<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
-<!-- RDI for paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-## Adjusted by other drug
-### RDI group
-<span style="color:green">**Table 11 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
-```{r Table 5 HR adjusted rdi group adjusted by other drug}
+<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
+
+<br>
+<br>
+
+### Continous
+<span style="color:green">**Table 10 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
+```{r rdi continous}
 tbl2 <- Frontline %>%
   filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- 
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
+<!-- RDI for paclitaxel is not a factor associated with survival. -->
+
+<br>
+<br>
+
+## Adjusted by other drug
+### RDI group
+<span style="color:green">**Table 11 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
+```{r Table 5 HR adjusted rdi group adjusted by other drug}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+PH assumption Upfront Chemo
+```{r prop H}
+coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%
+  cox.zph()
+```
+
+PH assumption Upfront Surgery
+```{r}
+coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+  cox.zph()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
 ```{r rdi continous adjusted by other drug}
@@
   filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+PH assumption Upfront Chemo
+```{r prop H c}
+coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%
+  cox.zph()
+```
+
+PH assumption Upfront Surgery
+```{r}
+coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+  cox.zph()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
 tbl2 <- 
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 <!-- tbl1 <- tbl2 %>% -->
-<!--   select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp1) %>%  -->
+<!--   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
 <!-- tbl2 <- tbl2 %>% -->
-<!--   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
+<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- tbl3 <- tbl3 %>% -->
-<!--   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
+<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)), -->
+<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- tbl1 <- tbl2 %>% -->
-<!--   select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp1) %>%  -->
+<!--   select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
 <!-- tbl2 <- tbl2 %>% -->
-<!--   select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
+<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- tbl3 <- tbl3 %>% -->
-<!--   select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
+<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)), -->
+<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- ### Multivariable -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp1 + raceeth + ageatdx + stagecat` -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_grp1 + raceeth + ageatdx + stagecat` -->
 <!-- ```{r} -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vital_status) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--              event = tbl3$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- ### RDI group -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` -->
 <!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug 2} -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- ## Multivariable -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` -->
 <!-- ```{r bmi HR adjusted} -->
@@
 <!-- #   coxph(Surv(time = tbl1$month_at_os_from_treatment, -->
-<!-- #              event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>% -->
+<!-- #              event = tbl1$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>% -->
 <!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
-<!--              event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>% -->
+<!--              event = tbl2$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
-<!--              event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>% -->
+<!--              event = tbl3$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- #   coxph(Surv(time = tbl7$month_at_os_from_treatment, -->
-<!-- #              event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>% -->
+<!-- #              event = tbl7$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>% -->
 <!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl8$month_at_os_from_treatment, -->
-<!--              event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>% -->
+<!--              event = tbl8$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl9$month_at_os_from_treatment, -->
-<!--              event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>% -->
+<!--              event = tbl9$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 
+# Complete case HR analysis
+
+## Multivariable
+### RDI group
+<span style="color:green">**Table 9 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology + debulking` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
+
+<br>
+<br>
+
+### Continous
+<span style="color:green">**Table 10 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology + debulking` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo",
+                           "paclitaxel Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
+<!-- RDI for paclitaxel is not a factor associated with survival. -->
+
+<br>
+<br>
+
+## Adjusted by other drug
+### RDI group
+<span style="color:green">**Table 11 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+PH assumption Upfront Chemo
+```{r prop H complete case}
+coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>% 
+  cox.zph()
+```
+
+PH assumption Upfront Surgery
+```{r}
+coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  cox.zph()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
+-->
+
+<br>
+<br>
+
+### Continous
+<span style="color:green">**Table 12 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking` 
+```{r }
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+PH assumption Upfront Chemo
+```{r prop H complete case c}
+coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>% 
+  cox.zph()
+```
+
+PH assumption Upfront Surgery
+```{r}
+coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  cox.zph()
+```
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
 ```{r echo=FALSE, out.width='30%'}

### 2021-12-23 R/2.data cleaning.R

@@ -8,6 +8,8 @@ creatinine <- creatinine %>%
     testresultcleaned > 3          ~ NA_real_, # F006DBE0C7A5E is an example of slow increase past 3, F641A8DC820C7 super high
     TRUE                           ~ testresultcleaned
   )) %>% 
+  mutate(testresult = str_remove(testresult, "<"),
+         testresult = as.numeric(testresult)) %>% 
   # F092F8B827DDC kept umol/L as they actually are mg/dL range 45 to 90 μmol/L (0.5 to 1.0 mg/dL) for women.
   mutate(creatinine1 = case_when(
     testresult < 0.7               ~ 0.7,
@@ -35,8 +37,8 @@ write_rds(creatinine, "creatinine.rds")
 
 # body_surface_area, height and weight are all coming from vitals
 vitals <- vitals %>% 
-  mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
-  select(-c(loinc, test, testbasename, resultdate, minnorm, maxnorm, minnormcleaned, maxnormcleaned))
+  # mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
+  select(-c(test, testbasename, resultdate, minnorm, maxnorm, minnormcleaned, maxnormcleaned))
 
 
 #################################################################################################### 2 ### Cleanup of BSA----
@@ -295,6 +297,7 @@ rm(weight1, weight2, vitals)
 #################################################################################################### 5 ### Cleanup of AUC----
 # Clean orderdrug for duplicated rows
 orderdrug <- orderdrug %>% 
+  `colnames<-`(str_to_lower(colnames(.))) %>% 
   filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>%
   select("patientid", "orderid", "drugname", "administereddate", "administeredamount", "administeredunits") %>%
   # 4 patients have duplicated order, need to keep the ones which are not NA 
@@ -357,6 +360,7 @@ orderdrug <- orderdrug %>%
 
 
 areaUC <- auc %>% 
+  `colnames<-`(str_to_lower(colnames(.))) %>% 
   filter(str_detect(drugname, "taxel|platin") & is.na(iscanceled)) %>% 
   # 1. bind with orderdrug to get only the order administered, no duplicated order and more relativeorderedamount
   inner_join(., orderdrug, 
[…]

### 2022-01-05 Rmd/rdi analysis.Rmd
Update HR with strata

@@
 **We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
-**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in clinical data.
+**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.
 
@@
 ```
-But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical informations who received drugs.
+But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.
 
@@
 
-(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and paclitaxel, they are just present in the same column called `target_auc` for a tidy data organisation - You can find the calculations formula at the end of the document)
+(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and paclitaxel, they are just present in the same column called `target_auc` for a tidy data organization - You can find the calculations formula at the end of the document)
 When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, and paclitaxel and their `expected_dose`.
@@
 
-- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
+- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
 ```{r}
@@
 
-## Univariable
+## Univariable and drug only adjusted analysis
 ```{r Table 6 HR}
@@
   # )
-
+```
+
+<div class = "row">
+<div class = "col-md-6">
+```{r Table 61 HR}
 tbl2 <- Frontline %>%
@@
 ```
+</div>
+
+<div class = "col-md-6">
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <-
+  coxph(Surv(time = tbl2$month_at_os_from_treatment,
+             event = tbl2$vital_status
+             ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status
+             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp,
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+</div>
+</div>
 
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%
+             event = tbl2$vital_status
+           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, 
+      data =  tbl2)  %>% 
   cox.zph()
@@
 coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status
+           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  
+        tbl3) %>%
   cox.zph()
@@
 
-## Multivariable
-### RDI group
-<span style="color:green">**Table 9 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology + debulking` 
-```{r}
+## Univariable and drug only adjusted analysis
+
+<span style="color:green">**Table  HR Univariable**</span>
+
+<div class = "row">
+<div class = "col-md-6">
+```{r Table  HR}
 tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+  filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking))
+tbl1 <- tbl2 %>%
+  select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- tbl2 %>%
+  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+  filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking))
+tbl3 <- tbl3 %>%
+  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl_stack(list(tbl1, tbl2, tbl3),
@@
 tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking))
+tbl1 <- tbl2 %>%
+  select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- tbl2 %>%
+  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking))
+tbl3 <- tbl3 %>%
+  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
+  tbl_uvregression(method = survival::coxph,
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
+                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("paclitaxel/Upfront Chemo", 
+                           "paclitaxel/Upfront Chemo",
+                           "paclitaxel/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking))
+tbl21 <-
+  coxph(Surv(time = tbl2$month_at_os_from_treatment,
+             event = tbl2$vital_status
+             ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking))
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status
+             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp,
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+</div>
+</div>
+
+<br>
+<br>
+
+## Multivariable
+### RDI group
+<span style="color:green">**Table 9 HR Multivariable**</span>
+
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology + debulking` 
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl1 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl1, tbl2, tbl3),
+          group_header = c("carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo",
+                           "carboplatin Adj/Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+
+# Pacli
+
+tbl2 <- Frontline %>%
   filter(therapy == "Upfront Chemo")
@@
 tbl3 <- Frontline %>%
+
   filter(therapy == "Upfront Surgery")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+             event = tbl3$vital_status
+             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+
 tbl_stack(list(tbl21, tbl31),
@@
 coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>% 
+             event = tbl2$vital_status
+           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, 
+      data =  tbl2)  %>% 
   cox.zph()
@@
 coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+             event = tbl3$vital_status
+           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
+      data =  tbl3) %>%
   cox.zph()
@@
 ```
+<br>
+<br>
+
+***
 

### 2022-01-06 Rmd/rdi analysis.Rmd
Update rdi analysis

@@
 
-Then I calculate $$relative\_dose\_intensity = \frac{amount}{expected\_dose}$$
+Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ given}{expected\ dose}$$
 
@@
 **We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
-**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.
+We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.**
 
@@
 ```
-But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.
+**But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.**
 
@@
 study_criteria <- study_criteria %>%
-  filter(!is.na(surgerydate))
+  filter(!is.na(surgerydate)) %>% 
+  mutate(chemotherapy_type = factor(chemotherapy_type))
 
@@
 ```{r}
-Frontline_adjusted <- standard_care %>% 
+standard_care <- standard_care %>% 
   filter(is.na(wrong_pacli_dosedense))
@@
 ```
-**We have `r Frontline_adjusted %>% distinct(patientid) %>% nrow()` patients.**
+**We have `r standard_care %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 
-<!-- Patients left: -->
-```{r}
-Frontline_adjusted <- Frontline_adjusted %>%
+```{r}
+Frontline <- standard_care %>%
   filter(is.na(switch_drugs))
@@
 
-# **The final number of patients in the dataset is `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**
+# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
 
@@
 ```{r}
-data <- Frontline_adjusted %>% 
+data <- Frontline %>% 
   filter(therapy == "Upfront Chemo") %>% 
@@
 ```{r}
-data <- Frontline_adjusted %>% 
+data <- Frontline %>% 
   filter(therapy == "Upfront Surgery") %>% 
@@
 #             by = "patientid") 
-Frontline_adjusted <- 
-  full_join(Frontline_adjusted, imputed_data %>% 
+Frontline <- 
+  full_join(Frontline, imputed_data %>% 
               select(patientid, starts_with("imp_")), 
@@
 
-```{r consort}
+```{r consort, fig.width=12}
 library(ggconsort)
@@
   Frontline_adjusted %>%
-  cohort_start("Assessed for eligibility") %>%
+  cohort_start("**Assessed for eligibility**") %>%
   # Define cohorts using named expressions
@@
              (is.na(surgerydate) | days_at_surg >= 0)) %>%
-    filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) &
-              !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) &
-              therapy == "Upfront Chemo") |
-             (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
-               therapy == "Upfront Surgery"))),
+    filter((
+      therapy == "Upfront Chemo" &
+        (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
+           !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
+    ) | (
+      therapy == "Upfront Surgery" &
+        (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
+    )
+    ),
 
@@
     filter(is.na(frontline_has_maintenance)) %>%
-    filter(is.na(too_many_cycle)),
-
-  Frontline = standard_care %>% 
-    filter(is.na(wrong_pacli_dosedense)),
-  Frontline1 = Frontline %>%
-    filter(is.na(switch_drugs))
+    filter(is.na(too_many_cycle)) %>% 
+    filter(is.na(wrong_pacli_dosedense)) %>%
+    filter(is.na(switch_drugs)),
+
+    Frontline = standard_care,
+
+  # anti_join is useful for counting exclusions -------------
+    excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
+    excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"),
+    excluded3 = anti_join(study_criteria, missing_data, by = "patientid"),
+    excluded4 = anti_join(missing_data, standard_care, by = "patientid")
   ) %>%
@@
   cohort_label(
-    flatiron_rec = "**flatiron_rec**",
-    study_criteria = "*study_criteria*",
-    missing_data = "missing_data",
-    standard_care = "standard_care",
-    Frontline = "Frontline",
-    Frontline1 = "Population Study"
+    excluded1 = "excluded albeit flatiron recommendation",
+    excluded2 = "<span style='color:darkblue'>no study criteria</span>",
+    excluded3 = "<span style='color:darkblue'>no missing_data</span>",
+    excluded4 = "<span style='color:darkblue'>no standard_care</span>",
+    flatiron_rec = "**Fit flatiron rec**",
+    study_criteria = "**Fit study criteria**",
+    missing_data = "**Non missing data**",
+    Frontline = "**Population Study**"
   )
-study_cohorts
 
@@
   consort_box_add(
-    "full", 0, 50, cohort_count_adorn(study_cohorts, .full)
+    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
   ) %>%
   consort_box_add(
-    "flatiron_rec", 5, 45, glue::glue(
-      "{cohort_count_adorn(study_cohorts, flatiron_rec)}<br> 
+    "exc_flatiron_rec", 0.2, 35, glue::glue(
+      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
       • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
@@
       • Borderline cases (not invasive ovarian cancer) <br>
-      • Data from one PracticeID <br>
-      • historical structured data were not available for <br> patients seen at academic sites prior to 2015
+      • (Data from one PracticeID) <br>
+      • (historical structured data were not available for <br> patients seen at academic sites prior to 2015)
       ")
-
   ) %>%
   consort_box_add(
-    "study_criteria", 5, 35, cohort_count_adorn(study_cohorts, study_criteria)
+    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
   ) %>%
   consort_box_add(
-    "missing_data", 5, 30, cohort_count_adorn(study_cohorts, missing_data)
+    "exc_study_criteria", 0.2, 25, glue::glue(
+      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
+      • exclude patients whose histology is unknown <br>
+      • remove chemotherapy only patients <br>
+      • include only patients who received platin and/or taxane <br>
+      • exclude patients who only received neo + surgery <br>
+      • include patients with single or dual P/T +/- Bev as frontline treatment
+      ")
   ) %>%
   consort_box_add(
-    "standard_care", 5, 25, cohort_count_adorn(study_cohorts, standard_care)
+    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
   ) %>%
   consort_box_add(
-    "Frontline", 5, 20, cohort_count_adorn(study_cohorts, Frontline)
+    "exc_missing_data", 0.2, 15, glue::glue(
+      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
+      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
+      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
+      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
+      • exclude patients for whose no RDI were available
+      ")
   ) %>%
   consort_box_add(
-    "Frontline1", 0, 15, cohort_count_adorn(study_cohorts, Frontline1)
+    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
   ) %>%
+  consort_box_add(
+    "exc_standard_care", 0.2, 5, glue::glue(
+      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
+      • exclude patients with more than 1 line as Neo <br> 
+      • exclude patients with maintenance within their frontline <br> 
+      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
+      ")
+  ) %>%
+  consort_box_add(
+    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
+  ) %>%
 
   consort_arrow_add(
-    end = "flatiron_rec", end_side = "left", start_x = 0, start_y = 45
+    end = "exc_flatiron_rec", end_side = "left", start_x = 0, start_y = 35
   ) %>%
   consort_arrow_add(
-    end = "study_criteria", end_side = "left", start_x = 0, start_y = 35
+    end = "exc_study_criteria", end_side = "left", start_x = 0, start_y = 25
   ) %>%
   consort_arrow_add(
-    end = "missing_data", end_side = "left", start_x = 0, start_y = 30
+    end = "exc_missing_data", end_side = "left", start_x = 0, start_y = 15
   ) %>%
   consort_arrow_add(
-    end = "standard_care", end_side = "left", start_x = 0, start_y = 25
+    end = "exc_standard_care", end_side = "left", start_x = 0, start_y = 5
   ) %>%
   consort_arrow_add(
-    end = "Frontline", end_side = "left", start_x = 0, start_y = 20
-  ) %>%
-  consort_arrow_add(
-    end = "Frontline1", end_side = "top", start_x = 0, start_y = 50
+    end = "Frontline", end_side = "top", start_x = 0, start_y = 40
   )
@@
   geom_consort() +
-  theme_consort(margin_h = 18, margin_v = 1)
+  theme_consort(margin_h = c(1,6), margin_v = c(0,30))
 ```
@@
   Treatment %>% 
-  filter(str_detect(patientid, paste(Frontline_adjusted$patientid, collapse = "|"))) %>% 
+  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
   arrange(patientid, episodedate, drugname)
@@
 
-```{r}
-Frontline <- Frontline_adjusted
-```
-
 <!-- ## Missingness -->
@@
 
-           "histology", "stagecat", imp_stagecat,
+           histology1, "histology", "stagecat", imp_stagecat,
 
@@
   tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+```
+
+<span style="color:green">**Table  Summary of the expected, actual dose, and RDI**</span>
+```{r Summary of the expected, actual dose, and RDI}
+rdi_study <- 
+  RDI_data %>% 
+  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
+  arrange(patientid, episodedate, drugname) %>% 
+  mutate(chemotherapy_type = factor(chemotherapy_type))
+
+tbl1 <- rdi_study %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>% 
+  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity, chemotherapy_type) %>% 
+  tbl_summary(by = chemotherapy_type) %>% bold_labels()
+
+tbl2 <- rdi_study %>% filter(drugname == "paclitaxel" & therapy == "Upfront Chemo") %>% 
+  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity, chemotherapy_type) %>% 
+  tbl_summary(by = chemotherapy_type) %>% bold_labels()
+
+tbl_stack(list(tbl1, tbl2),
+          group_header = c(
+                           "Carboplatin Upfront Chemo", 
+                           "Paclitaxel Upfront Chemo"),
+          quiet = TRUE)
+
+tbl1 <- rdi_study %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>% 
+  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity) %>% 
+  tbl_summary() %>% bold_labels()
+
+tbl2 <- rdi_study %>% filter(drugname == "paclitaxel" & therapy == "Upfront Surgery") %>% 
+  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity) %>% 
+  tbl_summary() %>% bold_labels()
+
+tbl_stack(list(tbl1, tbl2),
+          group_header = c(
+                           "Carboplatin Upfront Surgery", 
+                           "Paclitaxel Upfront Surgery"),
+          quiet = TRUE)
+
+# rdi_study %>% filter(drugname == "paclitaxel" & is_dose_dense == 1) %>% 
+#   select(target_auc, expected_dose, amount,  relative_dose_intensity, therapy) %>% 
+#   tbl_summary(by = therapy) %>% bold_labels()
+
 ```
@@
 # RDI_grp = case_when(
-#     mean_RDI_per_drug >= 0.85              ~ "correct",
+#     mean_RDI_per_drug >= 0.85              ~ "adequate",
 #     mean_RDI_per_drug < 0.85               ~ "underdose"
@@
   geom_vline(xintercept = 1, color = "red", linetype = 2)+
+  geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+
 
@@
 
-## 1.RDI summary table
+## 2.RDI summary table
 
@@
 Platin  
-```{r Table4 summary Platin}
+```{r Table 7 Summary RDI data by race and bmi}
 tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
@@
 
+tbl7 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+tbl8 <-
+  tbl_merge(list(tbl3, tbl4))
+tbl_stack(list(tbl7, tbl8),
+          group_header = c(
+                           "carboplatin Neo/Upfront Chemo", 
+                           "carboplatin Adj/Upfront Chemo"),
+          quiet = TRUE)
+
 tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
@@
 
-tbl7 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-tbl8 <-
-  tbl_merge(list(tbl3, tbl4))
-tbl9 <-
-  tbl_merge(list(tbl6, tbl6))
-
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c(
-                           "carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery"),
-          quiet = TRUE)
+# tbl9 <-
+  tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
+  modify_caption("**Upfront Surgery**")
 ```
@@
   add_p() %>% bold_p(t= 0.05)
-
+tbl7 <-
+  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
+tbl8 <-
+  tbl_merge(list(tbl3, tbl4))
+tbl_stack(list(tbl7, tbl8),
+          group_header = c(
+                           "paclitaxel Neo/Upfront Chemo", 
+                           "paclitaxel Adj/Upfront Chemo"),
+          quiet = TRUE)
 tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
@@
 
-tbl7 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-tbl8 <-
-  tbl_merge(list(tbl3, tbl4))
-tbl9 <-
-  tbl_merge(list(tbl6, tbl6))
-
-tbl_stack(list(tbl7, tbl8, tbl9),
-          group_header = c(
-                           "paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery"),
-          quiet = TRUE)
+tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
+  modify_caption("**Upfront Surgery**")
 ```
@@
 
+```{r}
+Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+  mutate(comp_cases = case_when(
+    is.na(stagecat) |
+      is.na(debulking)                     ~ "excluded",
+    TRUE                                   ~ "complete cases"
+  )) %>% 
+  select(c(vital, raceeth, 
+           agecat, "ageatdx",
+
+           bmi_at_dx, bmi_cat, 
+           weight_at_dx, height_at_dx, bsa_at_dx,
+
+           histology1, "histology", "stagecat", imp_stagecat,
+
+           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
+           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
+           comp_cases)) %>% 
+  tbl_summary(by = comp_cases) %>% 
+  bold_labels() %>% add_p() %>% bold_p()
+```
+<br>
+
 ## Univariable and drug only adjusted analysis

### 2022-01-06 R/2.data cleaning.R

@@ -575,7 +575,8 @@ clinical_data <- clinical_data %>%
       stagecat == "Stage 4"              ~ "Late stage"
   )) %>% 
   mutate(across(.cols = c(histology), ~na_if(., "Unknown/not documented"))) %>% 
-  mutate(histology = case_when(
+  mutate(histology1 = histology,
+         histology = case_when(
     histology == "Serous"                       ~ "Serous",
     is.na(histology)                            ~ NA_character_,
     TRUE                                        ~ "Others"

### 2022-01-06 Rmd/Adjusted weight rdi analysis.Rmd
Create new adjusted weight rmd

--- 2022-01-06 Rmd/rdi analysis.Rmd
@@
 
-# `r emo::ji("spiral_notepad")` This report is using **actual weight**
+# `r emo::ji("spiral_notepad")` This report is using **adjusted weight**
 
@@
 
+ideal_weight is calculated :
+- height <= 1.524               ~ 45.5 + 2.3,
+- height > 1.524                ~ 45.5 + (2.3 * (((`height` - 1.524) / 0.0254)))
+
+adjusted_weight :
+- ((`weight` - `ideal_weight`) * 0.40) + `ideal_weight`
+
+actual_bmi = weight / (height * height)
+
 CrCl calculation :
 
+IF actual_bmi >= 25 :
 $$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
-and is capped at 125.  
+IF actual_bmi < 25 :
+
+$$adjusted\_CrCl = \frac{(140 - ageatdx) * adjusted\_weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
+In both cases CrCl is capped at 125.  
 <br>
@@
 
-`expected_dose` is:  
--`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
--`BSA` * `target_auc`           -> for `drugname` == "taxel" or "cisplatin"  
+<!-- mutate(adjusted_expected_dose = case_when( -->
+<!--     drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25), -->
+<!--     drugname == "paclitaxel"                  ~ BSA * target_auc  -->
+<!--     # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug -->
+<!--   )) %>%  -->
+<!--   mutate(adjusted_expected_dose = case_when( -->
+<!--     adjusted_expected_dose > 900 & -->
+<!--       target_auc == 6              ~ 900, -->
+<!--     adjusted_expected_dose > 750 & -->
+<!--       target_auc == 5              ~ 750, -->
+<!--     TRUE                           ~ adjusted_expected_dose -->
+<!--   )) -->
+
+`adjusted_expected_dose` is:  
+-`target_auc` * (`adjusted CrCl` + 25)   -> for `drugname` == "carboplatin"  
+-`BSA` * `target_auc`                    -> for `drugname` == "paclitaxel"
 (Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
@@
 
-Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ given}{expected\ dose}$$
+<!-- relative_dose_intensity = amount / adjusted_expected_dose -->
+
+Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ received}{adjusted\ expected\ dose}$$
 
@@
 
-  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
+  mutate(relative_dose_intensity = amount / adjusted_expected_dose # adjusted_expected_dose
   ) %>%
@@
 <br>
-
-# Consort diagram
-
-```{r consort, fig.width=12}
-library(ggconsort)
-study_cohorts <- 
-  Frontline_adjusted %>%
-  cohort_start("**Assessed for eligibility**") %>%
-  # Define cohorts using named expressions
-  # Notice that you can use previously defined cohorts in subsequent steps
-  cohort_define(
-  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),
-
-  study_criteria = flatiron_rec  %>% 
-    filter(!is.na(histology)) %>%
-    filter(!is.na(surgerydate)) %>%
-    filter(had_carbo_pacli == "Yes") %>% 
-    filter(treatment_sequence == "neo + surg + adj" |
-             treatment_sequence == "surg + adj") %>%
-    filter(is.na(line_keep)),
-
-    missing_data = study_criteria  %>% 
-    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
-    filter(is.na(gap_surg_drugs)) %>%
-    filter(days_at_first_drug >= 0 &
-             (is.na(surgerydate) | days_at_surg >= 0)) %>%
-    filter((
-      therapy == "Upfront Chemo" &
-        (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
-           !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
-    ) | (
-      therapy == "Upfront Surgery" &
-        (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
-    )
-    ),
-
-    standard_care = missing_data %>% 
-    filter(is.na(neo_more_more_than_1line)) %>%
-    filter(is.na(frontline_has_maintenance)) %>%
-    filter(is.na(too_many_cycle)) %>% 
-    filter(is.na(wrong_pacli_dosedense)) %>%
-    filter(is.na(switch_drugs)),
-
-    Frontline = standard_care,
-
-  # anti_join is useful for counting exclusions -------------
-    excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
-    excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"),
-    excluded3 = anti_join(study_criteria, missing_data, by = "patientid"),
-    excluded4 = anti_join(missing_data, standard_care, by = "patientid")
-  ) %>%
-  # Provide text labels for cohorts
-  cohort_label(
-    excluded1 = "excluded albeit flatiron recommendation",
-    excluded2 = "<span style='color:darkblue'>no study criteria</span>",
-    excluded3 = "<span style='color:darkblue'>no missing_data</span>",
-    excluded4 = "<span style='color:darkblue'>no standard_care</span>",
-    flatiron_rec = "**Fit flatiron rec**",
-    study_criteria = "**Fit study criteria**",
-    missing_data = "**Non missing data**",
-    Frontline = "**Population Study**"
-  )
-
-study_consort <- study_cohorts %>%
-  consort_box_add(
-    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
-  ) %>%
-  consort_box_add(
-    "exc_flatiron_rec", 0.2, 35, glue::glue(
-      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
-      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
-      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
-      • Borderline cases (not invasive ovarian cancer) <br>
-      • (Data from one PracticeID) <br>
-      • (historical structured data were not available for <br> patients seen at academic sites prior to 2015)
-      ")
-  ) %>%
-  consort_box_add(
-    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
-  ) %>%
-  consort_box_add(
-    "exc_study_criteria", 0.2, 25, glue::glue(
-      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
-      • exclude patients whose histology is unknown <br>
-      • remove chemotherapy only patients <br>
-      • include only patients who received platin and/or taxane <br>
-      • exclude patients who only received neo + surgery <br>
-      • include patients with single or dual P/T +/- Bev as frontline treatment
-      ")
-  ) %>%
-  consort_box_add(
-    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
-  ) %>%
-  consort_box_add(
-    "exc_missing_data", 0.2, 15, glue::glue(
-      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
-      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
-      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
-      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
-      • exclude patients for whose no RDI were available
-      ")
-  ) %>%
-  consort_box_add(
-    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
-  ) %>%
-  consort_box_add(
-    "exc_standard_care", 0.2, 5, glue::glue(
-      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
-      • exclude patients with more than 1 line as Neo <br> 
-      • exclude patients with maintenance within their frontline <br> 
-      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
-      ")
-  ) %>%
-  consort_box_add(
-    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
-  ) %>%
-
-  consort_arrow_add(
-    end = "exc_flatiron_rec", end_side = "left", start_x = 0, start_y = 35
-  ) %>%
-  consort_arrow_add(
-    end = "exc_study_criteria", end_side = "left", start_x = 0, start_y = 25
-  ) %>%
-  consort_arrow_add(
-    end = "exc_missing_data", end_side = "left", start_x = 0, start_y = 15
-  ) %>%
-  consort_arrow_add(
-    end = "exc_standard_care", end_side = "left", start_x = 0, start_y = 5
-  ) %>%
-  consort_arrow_add(
-    end = "Frontline", end_side = "top", start_x = 0, start_y = 40
-  )
-
-study_consort %>%
-  ggplot() + 
-  geom_consort() +
-  theme_consort(margin_h = c(1,6), margin_v = c(0,30))
-```
-
-<br>
-
-***
 

### 2022-01-06 Rmd/Adjusted weight rdi analysis1.Rmd
Create new adjusted weight rmd

--- 2022-01-06 Rmd/Adjusted weight rdi analysis.Rmd
@@
 **We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
-We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.**
+**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.
 
@@
 ```
-**But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.**
+But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.
 
@@
 ```{r}
-standard_care <- standard_care %>% 
+Frontline_adjusted <- standard_care %>% 
   filter(is.na(wrong_pacli_dosedense))
@@
 ```
-**We have `r standard_care %>% distinct(patientid) %>% nrow()` patients.**
+**We have `r Frontline_adjusted %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 
-```{r}
-Frontline <- standard_care %>%
+<!-- Patients left: -->
+```{r}
+Frontline_adjusted <- Frontline_adjusted %>%
   filter(is.na(switch_drugs))
@@
 ```{r}
-data <- Frontline %>% 
+data <- Frontline_adjusted %>% 
   filter(therapy == "Upfront Chemo") %>% 
@@
 ```{r}
-data <- Frontline %>% 
+data <- Frontline_adjusted %>% 
   filter(therapy == "Upfront Surgery") %>% 
@@
 #             by = "patientid") 
-Frontline <- 
-  full_join(Frontline, imputed_data %>% 
+Frontline_adjusted <- 
+  full_join(Frontline_adjusted, imputed_data %>% 
               select(patientid, starts_with("imp_")), 
@@
 
+# Consort diagram
+
+```{r consort}
+library(ggconsort)
+study_cohorts <- 
+  Frontline_adjusted %>%
+  cohort_start("Assessed for eligibility") %>%
+  # Define cohorts using named expressions
+  # Notice that you can use previously defined cohorts in subsequent steps
+  cohort_define(
+  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),
+
+  study_criteria = flatiron_rec  %>% 
+    filter(!is.na(histology)) %>%
+    filter(!is.na(surgerydate)) %>%
+    filter(had_carbo_pacli == "Yes") %>% 
+    filter(treatment_sequence == "neo + surg + adj" |
+             treatment_sequence == "surg + adj") %>%
+    filter(is.na(line_keep)),
+
+    missing_data = study_criteria  %>% 
+    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
+    filter(is.na(gap_surg_drugs)) %>%
+    filter(days_at_first_drug >= 0 &
+             (is.na(surgerydate) | days_at_surg >= 0)) %>%
+    filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) &
+              !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) &
+              therapy == "Upfront Chemo") |
+             (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
+               therapy == "Upfront Surgery"))),
+
+    standard_care = missing_data %>% 
+    filter(is.na(neo_more_more_than_1line)) %>%
+    filter(is.na(frontline_has_maintenance)) %>%
+    filter(is.na(too_many_cycle)),
+
+  Frontline = standard_care %>% 
+    filter(is.na(wrong_pacli_dosedense)),
+  Frontline1 = Frontline %>%
+    filter(is.na(switch_drugs))
+  ) %>%
+  # Provide text labels for cohorts
+  cohort_label(
+    flatiron_rec = "**flatiron_rec**",
+    study_criteria = "*study_criteria*",
+    missing_data = "missing_data",
+    standard_care = "standard_care",
+    Frontline = "Frontline",
+    Frontline1 = "Population Study"
+  )
+study_cohorts
+
+study_consort <- study_cohorts %>%
+  consort_box_add(
+    "full", 0, 50, cohort_count_adorn(study_cohorts, .full)
+  ) %>%
+  consort_box_add(
+    "flatiron_rec", 5, 45, glue::glue(
+      "{cohort_count_adorn(study_cohorts, flatiron_rec)}<br> 
+      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
+      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
+      • Borderline cases (not invasive ovarian cancer) <br>
+      • Data from one PracticeID <br>
+      • historical structured data were not available for <br> patients seen at academic sites prior to 2015
+      ")
+
+  ) %>%
+  consort_box_add(
+    "study_criteria", 5, 35, cohort_count_adorn(study_cohorts, study_criteria)
+  ) %>%
+  consort_box_add(
+    "missing_data", 5, 30, cohort_count_adorn(study_cohorts, missing_data)
+  ) %>%
+  consort_box_add(
+    "standard_care", 5, 25, cohort_count_adorn(study_cohorts, standard_care)
+  ) %>%
+  consort_box_add(
+    "Frontline", 5, 20, cohort_count_adorn(study_cohorts, Frontline)
+  ) %>%
+  consort_box_add(
+    "Frontline1", 0, 15, cohort_count_adorn(study_cohorts, Frontline1)
+  ) %>%
+
+  consort_arrow_add(
+    end = "flatiron_rec", end_side = "left", start_x = 0, start_y = 45
+  ) %>%
+  consort_arrow_add(
+    end = "study_criteria", end_side = "left", start_x = 0, start_y = 35
+  ) %>%
+  consort_arrow_add(
+    end = "missing_data", end_side = "left", start_x = 0, start_y = 30
+  ) %>%
+  consort_arrow_add(
+    end = "standard_care", end_side = "left", start_x = 0, start_y = 25
+  ) %>%
+  consort_arrow_add(
+    end = "Frontline", end_side = "left", start_x = 0, start_y = 20
+  ) %>%
+  consort_arrow_add(
+    end = "Frontline1", end_side = "top", start_x = 0, start_y = 50
+  )
+
+study_consort %>%
+  ggplot() + 
+  geom_consort() +
+  theme_consort(margin_h = 18, margin_v = 1)
+```
+
+<br>
+
+***
+
 # II.Data analysis
@@
   RDI_data %>% 
-  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
+  filter(str_detect(patientid, paste(Frontline_adjusted$patientid, collapse = "|"))) %>% 
   arrange(patientid, episodedate, drugname) %>% 
@@
 
-## 2.RDI summary table
+## 1.RDI summary table
 
@@
 
-           histology1, "histology", "stagecat", imp_stagecat,
+           "histology", "stagecat", imp_stagecat,
 

### 2022-01-06 Rmd/rdi analysis adjus weight older.Rmd
Create new adjusted weight rmd

--- 2021-12-23 Rmd/rdi analysis.Rmd
@@
 library(survival)
-library(mice)
 ```
@@
 
+**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
+**We have `r drugs %>% distinct(patientid) %>% nrow()` patients info in clinical data.
+
 - Select episodedatasource == "Administrations"
-
-**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
-**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in clinical data.
-
 ```{r drugs episode cleanup}
 drugs <- drugs %>% 
-  `colnames<-`(str_to_lower(colnames(.))) %>% 
-  # Select only records for administration
-  filter(episodedatasource == "Administrations") %>%
+  filter(episodedatasource == "Administrations" #& 
+           # ismaintenancetherapy == "FALSE" # keep maintenance for a correct recoding of line number
+         ) %>%
   # bind with clinical
@@
   arrange(patientid, episodedate)
-```
-But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical informations who received drugs.
+
+drugs %>% distinct(patientid) %>% nrow()
+```
 
@@
 ```{r combine amount same drug one day}
-combined_drugs <- drugs %>% 
-  # Combined Multiple Administrations----
+drugs1 <- drugs %>% 
+  # 3. Combined Multiple Administrations----
   # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
+# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day.
+We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day.
+Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data.
+Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
+# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
+# Three administrations of the same drug were listed on a Friday.
+The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.
+# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
   group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, 
            drugname, units, ismaintenancetherapy) %>%
-  summarise_at(vars(route, amount), paste, collapse = ";") %>% # keep them in the data then do sum
+  summarise_at(vars(route, amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
   mutate(route = case_when(
-    str_detect(route, ";")            ~ "Intravenous", # I checked that all the combined administration are IV
+    str_detect(route, ";")            ~ "Intravenous",
     TRUE                              ~ route
@@
   mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
-  mutate(amount = rowSums(select(.,starts_with("amount_")), na.rm = TRUE)) %>%
+  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
   # Found ug, ml, Ea, and NA they are all good, but 
@@
     TRUE                        ~ amount
-  ))# %>%
-
-  # mutate(drugname_type = case_when(
-  #   str_detect(drugname, "platin")       ~ "platin",
-  #   str_detect(drugname, "taxel")        ~ "taxel"
-  # ))
+  )) %>%
+
+  mutate(drugname_type = case_when(
+    str_detect(drugname, "platin")       ~ "platin",
+    str_detect(drugname, "taxel")        ~ "taxel"
+  ))
 ```
@@
 ```{r line coding}
-therapy_line <- combined_drugs %>% 
-  # bind again with clinical - was lost while summarizing
+therapy_line <- drugs1 %>% 
+  # bind again with clinical - easier that way
   inner_join(., clinical_data, 
@@
   arrange(patientid, episodedate) %>% 
-  # Define Adjuvant, Neoadjuvant, chemo or surgery
+  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
   mutate(chemotherapy_type = case_when(
@@
   mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
+  fill(had_neo, .direction = "updown") %>% 
   mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
-  fill(had_neo, had_adj, .direction = "updown") %>% 
+  fill(had_adj, .direction = "updown") %>% 
   mutate(treatment_sequence = case_when(
@@
 
-  # Redefine line number based on the original linenumber variable and the surgery date
+  # 5.Redefine line number based on the original linenumber variable and the surgery date----
   mutate(linenumber_n = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  
-  # Redefine line number based on the new linenumber variable and if a switch 
-  # to maintenance is detected within the line
   group_by(patientid, linenumber_n, ismaintenancetherapy) %>% 
@@
          maint_rank = ifelse(maint_rank == 1, 1, 0)) %>%
+
   group_by(patientid) %>% 
   mutate(linenumber_new = cumsum(maint_rank)) %>%  
-  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 F0F1324B863A8
-  select(patientid, linename, linenumber, linenumber_new, drugname, 
-         episodedate, surgerydate, chemotherapy_type, everything()) %>% 
+  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 still weird F0F1324B863A8
+  select(patientid, linename, linenumber, linenumber_new, drugname, episodedate, surgerydate, chemotherapy_type, everything()) %>% 
   ungroup() %>%
-  # Define line number restarting to 1 for each chemotherapy_type
+
   group_by(patientid, chemotherapy_type) %>% 
@@
   ungroup() %>% 
-  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
-  # Redefine line dates
-  group_by(patientid, linenumber_new) %>% 
-  mutate(linestartdate = min(episodedate)) %>% 
-  mutate(lineenddate = max(episodedate)) %>% 
-  ungroup() %>% 
-  select(-c(linenumber_n, maint_rank))
-
   # 6.Add a 30 day rule to switch linenumber----
@@
 
+  # 7.Calculate cycle for each line----
+  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
+  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
+  mutate(#drugname_count_perline = n(),
+         drugname_count_perline = case_when(
+           str_detect(drugname, "carboplatin|paclitaxel")     ~ n()
+         )
+           ) %>%  # F0000AD999ABF
+  ungroup() %>% 
+  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
+  group_by(patientid, linenumber_new) %>% 
+  mutate(linestartdate_new = min(episodedate)) %>% 
+  mutate(lineenddate_new = max(episodedate)) %>% 
+  ungroup()
 ```
@@
 ```{r cycle coding}
+# Code cycle number
 therapy_cycle <- therapy_line %>% 
-  # Define cycle for each line
-  # F003F2BEEDB37 need to change drugname pacli = pacli bp
-  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  
-  # Need the number of time of the "major" drug is seen in the line
-  group_by(patientid, linenumber_new, cycle_drugname) %>%
-  mutate(drugname_count_perline = case_when(
-           str_detect(drugname, "carboplatin|paclitaxel")     ~ n()
-         )) %>%
-  ungroup() %>% 
   arrange(patientid, episodedate, drugname) %>% 
   group_by(patientid, linenumber_new) %>%
-  # Take the major drugname as a mark of new cycle start
+  # Need the number of time of the "major" drug is seen in the line
   mutate(cycle_count_perline = min(drugname_count_perline, na.rm = TRUE)) %>%
@@
     cycle_count_perline == drugname_count_perline &
-      (cycle_drugname == "carboplatin" |
-      cycle_drugname == "paclitaxel")                      ~ cycle_drugname,
+      (drugname == "carboplatin" |
+      drugname == "paclitaxel")                            ~ cycle_drugname,
     TRUE                                                   ~ NA_character_
@@
   # select(-drugname_count_perline) %>% 
-  # Code cycle number based on when major drug name appear again
-  group_by(patientid, linenumber_new, drugname, cycle_major_drugname) %>%
-  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 inversed dose dense------------------
-  # F01D908A013B7 weird dose dense
-
-  # F003F2BEEDB37 change of dose dense 50% ok? ---------------------------------------------------------------
-
+  group_by(patientid, linenumber_new, cycle_major_drugname) %>%
+  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 had a long time without one drug------------------
+  # F01D908A013B7 has more pacli at the end but in the same line
+
+  # + What to do when it is a cycle change F003F2BEEDB37 ,
+
+  # group_by(patientid, linenumber_new, cycle_inc) %>%
+  # mutate(cycle_count_1 = row_number(cycle_inc)) %>% 
+  # mutate(cycle_c = ifelse(cycle_count_1 == 1, cycle_inc, NA_real_)) %>% 
   arrange(patientid, episodedate, cycle_increment) %>% 
   group_by(patientid, linenumber_new) %>%
-  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9 ok, FE593EDF5586A has a switched drugs will be removed
+  # mutate(cycle_increment = cycle_inc) %>% 
+  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9, FE593EDF5586A
   group_by(patientid, chemotherapy_type, cycle_increment) %>% 
-  # Code is_dose_dense to be 1 for the first drug in the cycle
   mutate(is_dose_dense = row_number(cycle_increment),
@@
   group_by(patientid) %>% 
-  mutate(total_cycle_increment = row_number(is_dose_dense)
+  mutate(total_cycle_increment = #case_when(
+           # ismaintenancetherapy == "FALSE"            ~ 
+           row_number(is_dose_dense)
+         # )
   ) %>% 
-  group_by(patientid, linenumber_adj) %>% 
   fill(total_cycle_increment, .direction = "downup") %>% 
@@
   # Look at dose dense
-  # Code how many time a drug comes up in a cycle
   group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
@@
   filter(route == "Intravenous") %>% 
-  # step 1: Flatiron recommendation cleanup
-  # 90 days rule between diagnosis and treatment
+  # 1. 60 days rule between diagnosis and treatment # Loss 1
   group_by(patientid) %>% 
   mutate(first_drug_date = first(episodedate)) %>% 
-  ungroup() %>% 
   mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
@@
   )) %>% 
-  # 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis
+  ungroup() %>% 
   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
@@
   ) %>% 
-  mutate(flatiron_rules = case_when(
-    days_at_first_treatment > 90                 ~ "exclude",
-    thirty_days_exclusion <= 30                  ~ "exclude",
-    exclude == "1"                               ~ "exclude"
-  )) %>%
   group_by(patientid) %>% 
-  fill(flatiron_rules, .direction = "downup") %>% 
-  ungroup() %>%
-
-  # step 2: Filter patients with clinical characteristics fitting to the study criteria
-  # include only patients who received platin and/or taxane
   mutate(had_carbo_pacli = case_when(
@@
   )) %>% 
-  group_by(patientid) %>% 
   fill(had_carbo_pacli, .direction = "updown") %>% 
   ungroup() %>% 
-  # include patients with single or dual P/T +/- Bev as frontline treatment
+  mutate(interval_surgery_to_adj_start = case_when(
+      chemotherapy_type == "Adjuvant" &
+        linenumber_adj == 1       
+      ~ interval(start = surgerydate, end = linestartdate_new) / duration(n = 1, units = "months")
+    ),
+  ) %>% 
+  group_by(patientid) %>% 
+  mutate(neo_more_more_than_1line = case_when(
+    chemotherapy_type == "Neoadjuvant" &
+           linenumber_new != 1                 ~ "exclude"
+  )) %>% 
+  fill(neo_more_more_than_1line, .direction = "updown") %>% 
+  ungroup() %>% 
+  mutate(whole_frontline_is_maintenance = case_when(
+    (linenumber_new == 1 &
+    ismaintenancetherapy == "TRUE") |
+    (linenumber_new == 2 &
+      therapy == "Upfront Chemo" &
+    ismaintenancetherapy == "TRUE")            ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>% 
+  fill(whole_frontline_is_maintenance, .direction = "updown") %>% 
+  ungroup() %>% 
+  mutate(too_many_cycle = case_when(
+    (linenumber_new == 1 &
+       therapy == "Upfront Chemo" &
+       total_cycle_increment > 6) |
+
+      (linenumber_new == 2 &
+         therapy == "Upfront Chemo" &
+         total_cycle_increment > 9) |
+
+      (linenumber_new == 1 &
+         therapy == "Upfront Surgery" &
+         total_cycle_increment > 9)             ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(too_many_cycle, .direction = "updown") %>%
+  ungroup() %>%
+
+  mutate(wrong_pacli_dosedense = case_when(
+    drugname == "paclitaxel" &
+      is.na(too_many_cycle) &
+      (dose_dense == 2 |
+      dose_dense > 3) &
+
+      ((linenumber_new == 1 &
+       therapy == "Upfront Chemo") |
+
+      (linenumber_new == 2 &
+         therapy == "Upfront Chemo") |
+
+      (linenumber_new == 1 &
+         therapy == "Upfront Surgery"))
+    ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
+  ungroup() %>% 
+  mutate(switch_drugs = case_when(
+    str_detect(linename, "Pacli") & 
+      drugname == "docetaxel" & 
+      linenumber_adj == 1                      ~ "exclude",
+    str_detect(linename, "Car") & 
+      drugname == "cisplatin" & 
+      linenumber_adj == 1                      ~ "exclude"
+  )) %>% 
+  group_by(patientid) %>%
+  fill(switch_drugs, .direction = "updown") %>% 
+  ungroup() %>%
+
   mutate(line_keep = case_when(# F002B429BE6C6
@@
            linename == "Bevacizumab,Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin"))            ~ NA_character_,
-    linenumber_adj == 1                                       ~ "exclude"
+           linename == "Bevacizumab,Carboplatin"))            ~ "include"
   )) %>% 
@@
   ungroup() %>% 
-
-  # step 3: Filter out patients with missing data
-  # remove patients with long gap between surgery and adjuvant start (3 months)
-  mutate(interval_surgery_to_adj_start = case_when(
-      chemotherapy_type == "Adjuvant" &
-        linenumber_adj == 1       
-      ~ interval(start = surgerydate, end = linestartdate) / duration(n = 1, units = "months")
-    )) %>% 
-  mutate(gap_surg_drugs = case_when(
-    interval_surgery_to_adj_start > 3                  ~ "exclude"
+  mutate(flatiron_rules = case_when(
+    days_at_first_treatment > 90                          ~ "exclude",
+    thirty_days_exclusion <= 30                  ~ "exclude",
+    exclude == "1"                               ~ "exclude"
   )) %>%
   group_by(patientid) %>% 
-  fill(gap_surg_drugs, .direction = "updown") %>% 
-  ungroup() %>%
-
-  # step 4: Include patients with treatments following the standard of clinical care
-  # exclude patients with more than 1 line as Neo
-  mutate(neo_more_more_than_1line = case_when(
-    chemotherapy_type == "Neoadjuvant" &
-           linenumber_new != 1                 ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(neo_more_more_than_1line, .direction = "updown") %>% 
-  ungroup() %>% 
-  # exclude patients with maintenance within their frontline
-  mutate(frontline_has_maintenance = case_when(
-    linenumber_adj == 1 &
-    ismaintenancetherapy == "TRUE"             ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(frontline_has_maintenance, .direction = "updown") %>% 
-  ungroup() %>% 
-  # exclude patients with more than 6 cycles in Neo, more than 9 cycles total 
-  # in upfront chemo or more than 9 cycles in upfront surgery
-  mutate(too_many_cycle = case_when(
-    (linenumber_new == 1 &
-       therapy == "Upfront Chemo" &
-       total_cycle_increment > 6) |
-
-      (linenumber_new == 2 &
-         therapy == "Upfront Chemo" &
-         total_cycle_increment > 9) |
-
-      (linenumber_new == 1 &
-         therapy == "Upfront Surgery" &
-         total_cycle_increment > 9)             ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(too_many_cycle, .direction = "updown") %>%
-  ungroup() %>% 
-  # Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
-  # Removes also the patients who has only carbo or only pacli
-  # dose_dense will need to be changed if we change and include these patients
-  arrange(patientid, episodedate, drugname) %>% 
-  mutate(wrong_pacli_dosedense = case_when(
-    drugname == "paclitaxel" &
-      is.na(too_many_cycle) &
-      (dose_dense == 2 |
-      dose_dense > 3) &
-      linenumber_adj == 1
-      # ((linenumber_new == 1 &
-      #  therapy == "Upfront Chemo") |
-      # (linenumber_new == 2 &
-      #    therapy == "Upfront Chemo") |
-      # (linenumber_new == 1 &
-      #    therapy == "Upfront Surgery"))
-    ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
-  ungroup() %>% 
-  # Exclude patients who switch drug within a line
-  mutate(switch_drugs = case_when(
-    str_detect(linename, "Pacli") & 
-      drugname == "docetaxel" & 
-      linenumber_adj == 1                      ~ "exclude",
-    str_detect(linename, "Car") & 
-      drugname == "cisplatin" & 
-      linenumber_adj == 1                      ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(switch_drugs, .direction = "updown") %>% 
+  fill(flatiron_rules, .direction = "downup") %>% 
   ungroup()
@@
 ```{r RDI calculation}
-Treatment <- Treatment %>% 
+RDI_data <- Treatment %>% 
   # filter(chemotherapy_type == "Neoadjuvant" |
@@
   ) %>% 
-  ungroup()
-
-RDI_data <- Treatment %>% 
-  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
-  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))
+  ungroup() %>% 
+  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
 ```
@@
 
-```{r RDI_data}
-RDI_data <- RDI_data %>% 
+```{r Frontline_adjusted}
+Frontline_adjusted <- RDI_data %>% 
   group_by(patientid) %>% 
@@
        .direction = "downup") %>% 
-  ungroup()
-Frontline_adjusted <- RDI_data %>% 
+  ungroup() %>% 
   distinct(patientid, .keep_all = TRUE)
@@
 study_criteria <- study_criteria %>%
-  filter(is.na(line_keep))
+  filter(line_keep == "include")
   # Remove patients with other linename
@@
 missing_data <- missing_data %>%
-  filter(is.na(gap_surg_drugs))
+  arrange(patientid, episodedate) %>%
+  mutate(ex = case_when(
+    interval_surgery_to_adj_start > 3                  ~ "exclude"
+  )) %>% 
+  filter(is.na(ex))
 
@@
   # remove these patients who switched C > C 
-  filter((
-    therapy == "Upfront Chemo" &
-      (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
-         !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
-  ) | (
-    therapy == "Upfront Surgery" &
-      (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
-  )
-  )
+  filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
+            !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) & 
+            therapy == "Upfront Chemo") |
+           (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
+            therapy == "Upfront Surgery")))
 ```
@@
 
-## 4. step 4: Include patients with treatments following the standard of clinical care
+## 4. step 4: Include patients with treatments following the standart of clinical care
 
@@
 ```{r}
-standard_care <- missing_data %>% 
+standart_care <- missing_data %>% 
   # Remove patients with more than 1 line as Neo
@@
 
-standard_care <- standard_care %>% 
-  filter(is.na(frontline_has_maintenance))
-
-standard_care <- standard_care %>% 
+standart_care <- standart_care %>% 
+  filter(is.na(whole_frontline_is_maintenance))
+
+standart_care <- standart_care %>% 
   filter(is.na(too_many_cycle))
 ```
-**We have `r standard_care %>% distinct(patientid) %>% nrow()` patients.**
+**We have `r standart_care %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 ```{r}
-Frontline_adjusted <- standard_care %>% 
+Frontline <- standart_care %>% 
   filter(is.na(wrong_pacli_dosedense))
 
-# standard_care %>% 
+# standart_care %>% 
 #   mutate(n_dose_dense = factor(n_dose_dense)) %>% 
@@
 ```
-**We have `r Frontline_adjusted %>% distinct(patientid) %>% nrow()` patients.**
+**We have `r Frontline %>% distinct(patientid) %>% nrow()` patients.**
 
@@
 - exclude patients who switch drug within a line
+
+<!-- `r Frontline %>% filter(str_detect(linename, "Car") & drugname == "cisplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had carboplatin switched to cisplatin within a line.
+-->
+<!-- `r Frontline %>% filter(str_detect(linename, "Cisplatin") & drugname == "carboplatin" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had cisplatin switched to carboplatin within a line.
+-->
 
@@
 
+<!-- `r Frontline %>% filter(str_detect(linename, "Pacli") & drugname == "docetaxel" & linenumber_adj == 1) %>% distinct(patientid) %>% nrow()` patients had paclitaxel switched to docetaxel within a line.
+-->
+<!-- I am removing these patients   -->
+
 <!-- Patients left: -->
 ```{r}
-Frontline_adjusted <- Frontline_adjusted %>%
+Frontline <- Frontline %>%
   filter(is.na(switch_drugs))
@@
 
-# **The final number of patients in the dataset is `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**
-
-# Imputation for stagecat and debulking status
-
-https://bookdown.org/mwheymans/bookmi/data-analysis-after-multiple-imputation.html#data-analysis-in-spss
-https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf
-
-Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
-Look at the Cox regression model before imputation.
-
-### For Upfront Chemo
-```{r}
-data <- Frontline_adjusted %>% 
-  filter(therapy == "Upfront Chemo") %>% 
-  select(patientid, month_at_os, vital_status, 
-         raceeth, diagnosisdate, surgerydate,
-         ageatdx, stagecat, debulking, histology,
-         RDI_carbo_neo, RDI_pacli_neo, 
-         RDI_carbo_adj, RDI_pacli_adj
-         # therapy
-  )
-nonimp_cox_model <-
-  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
-        data = data)
-nonimp_cox_model
-
-Hazard <- nelsonaalen(data, month_at_os, vital_status)
-dataset <- data.frame(data, Hazard)
-```
-
-Start imputation to look at matrix
-```{r}
-Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
-# summary(Cox.imp)
-Pred <- Cox.imp$predictorMatrix
-# Pred["debulking", "month_at_os"] <- 0
-Pred
-```
-
-patientid is not used which is good. But SURGERYDATE IS NOT.
-```{r}
-Pred[, "surgerydate"] <- 1
-Pred["surgerydate", "surgerydate"] <- 0
-Pred
-```
-
-Imputation and cox regression model on imputed data using the new predictor matrix.
-```{r}
-# Start imputations using mice
-Cox.imp <- mice(dataset, m=5, maxit=50, 
-                predictorMatrix=Pred,
-                seed=123, printFlag=F)
-check1 <- with(data = Cox.imp,
-       exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
-       ))
-pool(check1)$pooled
-```
-
-Do m = 34 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.339 that we multiply by 100)
-```{r}
-Cox.imp <- mice(dataset, m=34, maxit=50, 
-                predictorMatrix=Pred,
-                seed=123, printFlag=F)
-
-fit.Cox <-
-  with(data = Cox.imp,
-       exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
-       ))
-
-summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
-  kableExtra::kable() %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
-```
-Above results are exponentiated (imputed data).  
-As a reminder before imputation results are :
-```{r}
-nonimp_cox_model
-```
-
-Complete the chemo data and merge with original
-```{r}
-imputed_data_chemo <- complete(Cox.imp, include = FALSE) %>% 
-  rename(imp_stagecat = stagecat, imp_debulking = debulking)
-```
-
-Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
-
-### For Upfront Surgery
-```{r}
-data <- Frontline_adjusted %>% 
-  filter(therapy == "Upfront Surgery") %>% 
-  select(patientid, month_at_os, vital_status, 
-         raceeth, diagnosisdate, surgerydate,
-         ageatdx, stagecat, debulking, histology,
-         RDI_carbo_adj, RDI_pacli_adj
-         # therapy
-  )
-nonimp_cox_model <-
-  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
-        data = data)
-nonimp_cox_model
-
-Hazard <- nelsonaalen(data, month_at_os, vital_status)
-dataset <- data.frame(data, Hazard)
-```
-
-Start imputation to look at matrix
-```{r}
-Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
-# summary(Cox.imp)
-Pred <- Cox.imp$predictorMatrix
-# Pred["debulking", "month_at_os"] <- 0
-Pred
-```
-
-patientid is not used which is good. But SURGERYDATE IS NOT
-```{r}
-Pred[, "surgerydate"] <- 1
-Pred["surgerydate", "surgerydate"] <- 0
-Pred
-```
-
-Imputation and cox regression model on imputed data using the new predictor matrix.
-```{r}
-# Start imputations using mice
-Cox.imp <- mice(dataset, m=5, maxit=50, 
-                predictorMatrix=Pred,
-                seed=123, printFlag=F)
-check1 <- with(data = Cox.imp,
-       exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
-       ))
-pool(check1)$pooled
-```
-
-Do m = 17 (The max fmi = 0.166 that we multiply by 100)
-```{r}
-Cox.imp <- mice(dataset, m=17, maxit=50, 
-                predictorMatrix=Pred,
-                seed=123, printFlag=F)
-
-fit.Cox <-
-  with(data = Cox.imp,
-       exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
-       ))
-
-summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
-  kableExtra::kable() %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
-```
-Above results are exponentiated (imputed data).  
-As a reminder before imputation results are :
-```{r}
-nonimp_cox_model
-```
-
-Complete the data and merge with original
-```{r}
-imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
-  rename(imp_stagecat = stagecat, imp_debulking = debulking)
-
-imputed_data <- bind_rows(imputed_data_chemo, imputed_data_surg)
-
-# Frontline <- 
-#   full_join(Frontline, imputed_data %>% 
-#               select(patientid, starts_with("imp_")), 
-#             by = "patientid") 
-Frontline_adjusted <- 
-  full_join(Frontline_adjusted, imputed_data %>% 
-              select(patientid, starts_with("imp_")), 
-            by = "patientid") 
-```
+# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
 
@@
 <br>
-
-# Consort diagram
-
-```{r consort}
-library(ggconsort)
-study_cohorts <- 
-  Frontline_adjusted %>%
-  cohort_start("Assessed for eligibility") %>%
-  # Define cohorts using named expressions
-  # Notice that you can use previously defined cohorts in subsequent steps
-  cohort_define(
-  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),
-
-  study_criteria = flatiron_rec  %>% 
-    filter(!is.na(histology)) %>%
-    filter(!is.na(surgerydate)) %>%
-    filter(had_carbo_pacli == "Yes") %>% 
-    filter(treatment_sequence == "neo + surg + adj" |
-             treatment_sequence == "surg + adj") %>%
-    filter(is.na(line_keep)),
-
-    missing_data = study_criteria  %>% 
-    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
-    filter(is.na(gap_surg_drugs)) %>%
-    filter(days_at_first_drug >= 0 &
-             (is.na(surgerydate) | days_at_surg >= 0)) %>%
-    filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) &
-              !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) &
-              therapy == "Upfront Chemo") |
-             (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
-               therapy == "Upfront Surgery"))),
-
-    standard_care = missing_data %>% 
-    filter(is.na(neo_more_more_than_1line)) %>%
-    filter(is.na(frontline_has_maintenance)) %>%
-    filter(is.na(too_many_cycle)),
-
-  Frontline = standard_care %>% 
-    filter(is.na(wrong_pacli_dosedense)),
-  Frontline1 = Frontline %>%
-    filter(is.na(switch_drugs))
-  ) %>%
-  # Provide text labels for cohorts
-  cohort_label(
-    flatiron_rec = "**flatiron_rec**",
-    study_criteria = "*study_criteria*",
-    missing_data = "missing_data",
-    standard_care = "standard_care",
-    Frontline = "Frontline",
-    Frontline1 = "Population Study"
-  )
-study_cohorts
-
-study_consort <- study_cohorts %>%
-  consort_box_add(
-    "full", 0, 50, cohort_count_adorn(study_cohorts, .full)
-  ) %>%
-  consort_box_add(
-    "flatiron_rec", 5, 45, glue::glue(
-      "{cohort_count_adorn(study_cohorts, flatiron_rec)}<br> 
-      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
-      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
-      • Borderline cases (not invasive ovarian cancer) <br>
-      • Data from one PracticeID <br>
-      • historical structured data were not available for <br> patients seen at academic sites prior to 2015
-      ")
-
-  ) %>%
-  consort_box_add(
-    "study_criteria", 5, 35, cohort_count_adorn(study_cohorts, study_criteria)
-  ) %>%
-  consort_box_add(
-    "missing_data", 5, 30, cohort_count_adorn(study_cohorts, missing_data)
-  ) %>%
-  consort_box_add(
-    "standard_care", 5, 25, cohort_count_adorn(study_cohorts, standard_care)
-  ) %>%
-  consort_box_add(
-    "Frontline", 5, 20, cohort_count_adorn(study_cohorts, Frontline)
-  ) %>%
-  consort_box_add(
-    "Frontline1", 0, 15, cohort_count_adorn(study_cohorts, Frontline1)
-  ) %>%
-
-  consort_arrow_add(
-    end = "flatiron_rec", end_side = "left", start_x = 0, start_y = 45
-  ) %>%
-  consort_arrow_add(
-    end = "study_criteria", end_side = "left", start_x = 0, start_y = 35
-  ) %>%
-  consort_arrow_add(
-    end = "missing_data", end_side = "left", start_x = 0, start_y = 30
-  ) %>%
-  consort_arrow_add(
-    end = "standard_care", end_side = "left", start_x = 0, start_y = 25
-  ) %>%
-  consort_arrow_add(
-    end = "Frontline", end_side = "left", start_x = 0, start_y = 20
-  ) %>%
-  consort_arrow_add(
-    end = "Frontline1", end_side = "top", start_x = 0, start_y = 50
-  )
-
-study_consort %>%
-  ggplot() + 
-  geom_consort() +
-  theme_consort(margin_h = 18, margin_v = 1)
-```
-
-<br>
-
-***
 
@@
 
+### Number of line in treatment and cycle in frontline  
+Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
+in upfront neo
 ```{r}
-full_data_study_pop <- 
+RDI_data <- 
   Treatment %>% 
-  filter(str_detect(patientid, paste(Frontline_adjusted$patientid, collapse = "|"))) %>% 
+  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
   arrange(patientid, episodedate, drugname)
-```
-
-### Number of line /cycle received by patients in our study population
-
-<span style="color:green">**Table supp 1 Number of total line**</span>
-```{r}
-full_data_study_pop %>% 
+
+RDI_data %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
   arrange(desc(linenumber_new)) %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new, therapy) %>% 
-  tbl_summary(by = therapy)
-```
-
-<span style="color:green">**Table supp 1 Number of cycle in Neo**</span>
-```{r}
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
+  select(linenumber_new) %>% 
+  tbl_summary()
+RDI_data %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
   arrange(desc(cycle_increment)) %>%
@@
   tbl_summary()
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
+RDI_data %>% 
+  filter(chemotherapy_type == "Neoadjuvant" & therapy == "Upfront Chemo") %>% 
   arrange(desc(cycle_increment)) %>% 
+  mutate(cycle_increment = as.numeric(cycle_increment)) %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
   select(cycle_increment) %>% 
-  tbl_summary(type = list(cycle_increment ~ "continuous"))
-```
-
-<span style="color:green">**Table supp 1 Number of cycle in Adj**</span>
+  tbl_summary()
+```
+
+Number of Adjuvant line in patients with upfront neo
 ```{r}
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
+RDI_data %>% 
+  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
+  arrange(desc(linenumber_adj)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(linenumber_adj) %>% 
+  tbl_summary()
+
+RDI_data %>% 
+  filter(chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>% 
+  filter(linenumber_adj == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
   arrange(desc(cycle_increment)) %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment, therapy) %>% 
-  tbl_summary(by = therapy)
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
+  select(cycle_increment) %>% 
+  tbl_summary(label = list(cycle_increment ~ "cycle number during the adjuvant course in Upfront Chemo setting"))
+
+RDI_data %>% 
+  filter(therapy == "Upfront Chemo") %>% 
+  filter(linenumber_adj == 1) %>% 
+  mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
+  arrange(desc(total_cycle_increment)) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(total_cycle_increment) %>% 
+  tbl_summary(label = list(total_cycle_increment ~ "total cycle number in Upfront Chemo setting"))
+```
+Number of Adjuvant line in patients with upfront surgery
+```{r}
+RDI_data %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
+  arrange(desc(linenumber_adj)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(linenumber_adj) %>% 
+  tbl_summary()
+
+RDI_data %>% 
+  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
+  filter(linenumber_adj == 1) %>% 
+  mutate(cycle_increment = factor(cycle_increment)) %>% 
   arrange(desc(cycle_increment)) %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
-  select(cycle_increment, therapy) %>% 
-  tbl_summary(by = therapy,
-              type = list(cycle_increment ~ "continuous"))
-```
-<br>
-
-```{r}
-Frontline <- Frontline_adjusted
-```
+  select(cycle_increment) %>% 
+  tbl_summary()
+```
+<br>
 
@@
 
-<br>
-<br>
-
-***
-
 # Clinical Analysis
@@
 
-           "histology", "stagecat", imp_stagecat,
+           "histology", "stagecat",
 
@@
            "bmi_at_dx", bmi_cat, "BSA",
-           "stagecat", imp_stagecat)) %>% 
+           "stagecat")) %>% 
   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
            "bmi_at_dx", bmi_cat, "BSA",
-           "stagecat", imp_stagecat)) %>% 
+           "stagecat")) %>% 
   tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
@@
   theme_minimal(base_size = 14)+
-  labs(title = "BMI Category at Diagnosis")+
+  labs(title = "BMI category")+
   coord_flip()
@@
   distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= imp_stagecat))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Stage")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= agecat))+
@@
   theme_minimal(base_size = 14)+
-  labs(title = "Age Category")+
+  labs(title = "Age cat")+
   coord_flip()
@@
   theme_minimal(base_size = 14)+
-  labs(title = "BMI category at Diagnosis")+
+  labs(title = "BMI category")+
   coord_flip()
@@
   distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = imp_stagecat))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Stage")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
   ggplot(aes(x= raceeth, fill = agecat))+
@@
 # OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ raceeth, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 # OS by tstage
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ stagecat, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_stagecat, data=Frontline %>% 
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 ) + guides(colour = guide_legend(ncol = 2))
-
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ bmi_cat, data=Frontline %>% 
+```
+</div>
+
+<div class = "col-md-6">
+```{r clinical from first treatment, fig.height = 7}
+# OS by raceeth
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
+           title = "OS from date of first treatment", 
            font.main = c(24, "bold", "black"), 
@@
 ) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r clinical from first treatment, fig.height = 7}
-# OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ raceeth, data=Frontline %>% 
+
+# OS by tstage
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 
-# OS by tstage
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ stagecat, data=Frontline %>% 
+# OS by bmi_cat
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 ) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_stagecat, data=Frontline %>% 
+```
+</div>
+</div>
+
+<br>
+<br>
+
+***
+
+<br>
+
+# II.Treatment Analysis
+
+## 1.Treatment summary table
+
+<span style="color:green">**Table 4 Summary treatment data by race**</span>
+```{r Table 4}
+# tbl1 <- 
+  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(raceeth,
+           "debulking", "therapy"
+           )) %>% 
+  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
+  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+```
+<br>
+
+<span style="color:green">**Table 5 Summary treatment data by bmi**</span>
+```{r Table 5}
+# tbl1 <- 
+  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+  select(c(bmi_cat,
+           "debulking", "therapy"
+           )) %>% 
+  mutate(debulking = factor(debulking, levels = c("Suboptimal", "Optimal"))) %>% 
+  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
+```
+<br>
+
+## 2.Treatment Plots
+<div class = "row">
+<div class = "col-md-6">
+```{r treatment plots}
+Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= therapy))+
+  geom_bar()+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+```
+</div>
+
+<div class = "col-md-6">
+```{r}
+Frontline %>%
+  distinct(patientid, .keep_all = TRUE) %>% 
+  ggplot(aes(x= raceeth, fill= therapy))+
+  geom_bar(position ="fill")+
+  theme_minimal(base_size = 14)+
+  labs(title = "Frontline treatment")+
+  coord_flip()
+
+Frontline %>% 
+  distinct(patientid, .keep_all = TRUE) %>%
+  ggplot(aes(x= raceeth, fill= therapy))+
+  geom_bar(position ="fill")+
+  theme_minimal(base_size = 14)+
+  coord_flip()+
+  facet_wrap(. ~ drugname)
+```
+</div>
+</div>
+
+<br>
+
+## 3.Survivals by treatment
+
+<div class = "row">
+<div class = "col-md-6">
+```{r treatment survival, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ 1, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
+           title = "OS from date of diagnosis", 
            font.main = c(24, "bold", "black"), 
@@
            legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ bmi_cat, data=Frontline %>% 
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
+           title = "OS from date of diagnosis",
            font.main = c(24, "bold", "black"),
@@
            legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-</div>
-
-<br>
-<br>
-
-***
-
-<br>
-
-# II.Treatment Analysis
-
-## 1.Treatment summary table
-
-<span style="color:green">**Table 4 Summary treatment data by race**</span>
-```{r Table 4}
-# tbl1 <- 
-  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth,
-           "debulking", imp_debulking , "therapy"
-           )) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-```
-<br>
-
-<span style="color:green">**Table 5 Summary treatment data by bmi**</span>
-```{r Table 5}
-Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat,
-           "debulking", imp_debulking, "therapy"
-           )) %>% 
-  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-```
-<br>
-
-## 2.Treatment Plots
-<div class = "row">
-<div class = "col-md-6">
-```{r treatment plots}
-Frontline %>%
-  ggplot(aes(x= therapy))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= bmi_cat, fill= therapy))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= bmi_cat, fill= debulking))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= bmi_cat, fill= imp_debulking))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(linenumber_adj == 1) %>% 
-  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
-  ggplot(aes(x= linename, fill= therapy))+
-  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
-  theme_minimal(base_size = 14) + 
-  facet_wrap(. ~ chemotherapy_type)+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(linenumber_adj == 1) %>% 
-  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
-  ggplot(aes(x= linename, fill= therapy))+
-  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
-  theme_minimal(base_size = 14) + 
-  facet_wrap(raceeth ~ chemotherapy_type)+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename) %>% 
-  tbl_summary(label = list(linename ~ "line name received as Neoadujant"))
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename, therapy) %>% 
-  tbl_summary(by = therapy,
-              label = list(linename ~ "line name received as Adjuvant"))
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-Frontline %>%
-  ggplot(aes(x= raceeth, fill= therapy))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= debulking))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= imp_debulking))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= raceeth, fill= debulking))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= raceeth, fill= imp_debulking))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(linenumber_adj == 1) %>% 
-  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
-  ggplot(aes(x= linename, fill= therapy))+
-  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
-  theme_minimal(base_size = 14) + 
-  facet_wrap(bmi_cat ~ chemotherapy_type)+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
-  group_by(patientid, drugname) %>% 
-  summarise(CrCl = mean(CrCl),
-            target_auc = mean(target_auc),
-            expected_dose = mean(expected_dose)) %>% 
-  ungroup() %>% 
-  distinct(patientid, drugname, .keep_all = TRUE) %>% 
-  select(CrCl, target_auc, expected_dose, drugname) %>% 
-  tbl_summary(by = drugname,
-              label = list(CrCl ~ "Average CrCl during Neoadujant setting",
-                           target_auc ~ "Target dose (AUC or mg/mg2)",
-                           expected_dose ~ "Expected dose")
-    )
-```
-</div>
-</div>
-
-<br>
-
-## 3.Survivals by treatment
-
-<div class = "row">
-<div class = "col-md-6">
-```{r treatment survival, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ 1, data=Frontline %>% 
+) + guides(colour = guide_legend(ncol = 1))
+
+# OS by therapy
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ therapy, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
@@
 ) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ debulking, data=Frontline %>%
+```
+</div>
+
+<div class = "col-md-6">
+```{r, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ 1, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis",
+           title = "OS from date of from first treatment", 
            font.main = c(24, "bold", "black"), 
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_debulking, data=Frontline %>%
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ debulking, data=Frontline %>%
                      distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis",
+           title = "OS from date of from first treatment",
            font.main = c(24, "bold", "black"),
@@
 # OS by therapy
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ therapy, data=Frontline %>% 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ therapy, data=Frontline %>% 
                      distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
+           title = "OS from date of from first treatment", 
            font.main = c(24, "bold", "black"), 
@@
 </div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ 1, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ debulking, data=Frontline %>%
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_debulking, data=Frontline %>%
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ therapy, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
 </div>
@@
   coord_flip()
+  # facet_wrap(. ~ therapy)
 
@@
 # 
-Frontline %>% 
-  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
-  filter(!is.na(value)) %>% 
-  ggplot(aes(x= name, y= value, color= value < 0.85))+
-  geom_boxplot()+
-  geom_jitter(shape=16)+
-  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
-  theme_minimal(base_size = 14)+
-  coord_flip()+
-  facet_wrap(.~ therapy, ncol = 2)
+# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
+#   ggplot(aes(x= therapy, y= mean_RDI_per_drug))+
+#   # geom_boxplot()+
+#   ylim(c(-.25, 2))+
+#   geom_jitter(shape=16, aes(color=RDI_grp))+
+#   labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
+#   theme_minimal(base_size = 14) +
+#   guides(color=FALSE)+
+#   facet_wrap(.~ drugname, ncol = 2)
 ```
@@
 
-<span style="color:green">**Table 6: RDI summary table**</span>
+<span style="color:green">**RDI summary table**</span>
 
@@
 set_gtsummary_theme(my_theme)
-
-# trial %>%
-#   select(age, grade, trt) %>%
-#   tbl_summary(by = trt) %>%
-#   add_stat_label() %>%
-#   add_p() %>%
-#   as_gt() 
+trial %>%
+  select(age, grade, trt) %>%
+  tbl_summary(by = trt) %>%
+  add_stat_label() %>%
+  add_p() %>%
+  as_gt() 
 ```
@@
   tbl_summary(by = therapy) %>% 
-  bold_labels() %>% add_n() %>% add_overall()
+  bold_labels()
 
@@
   tbl_summary(by = therapy) %>%
-  bold_labels() %>% add_n() %>% add_overall()
+  bold_labels()
 
@@
               ) %>%
-  bold_labels() %>% add_n() %>% add_overall()
+  bold_labels()
 
@@
               ) %>%
-  bold_labels() %>% add_n() %>% add_overall()
+  bold_labels()
 tbl5 <- Frontline %>% filter(dose_dense == 3) %>%
@@
               type = list(`RDI (continous)` ~ "continuous")) %>%
-  bold_labels() %>% add_n() %>% add_overall()
+  bold_labels()
 tbl6 <- Frontline %>% filter(dose_dense == 3) %>%
@@
               type = list(`RDI (continous)` ~ "continuous")) %>%
-  bold_labels() %>% add_n() %>% add_overall()
+  bold_labels()
 
@@
 
-<span style="color:green">**Table 7: Summary RDI data by race and bmi**</span>  
+<span style="color:green">**Table 4 Summary RDI data by race and bmi**</span>  
 Removing the overall on the right side? Or do you want the tables separated?
@@
 ```{r OS dx RDI, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_neo_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_carbo_neo_grp, 
                    data=Frontline %>% 
@@
 ) + guides(colour = guide_legend(ncol = 1))
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_neo_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_pacli_neo_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ RDI_pacli_adj_grp, 
                    data=Frontline %>% 
@@
 ```{r OS treatment RDI, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_carbo_neo_grp, 
                    data=Frontline %>% 
@@
 ) + guides(colour = guide_legend(ncol = 1))
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_carbo_adj_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_neo_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_pacli_neo_grp, 
                    data=Frontline %>% 
@@
 
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_adj_grp, 
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ RDI_pacli_adj_grp, 
                    data=Frontline %>% 
@@
 
-<span style="color:green">**Table 8 HR Univariable**</span>
+<span style="color:green">**Table 6 HR**</span>
 
@@
 # tbl1 <- tbl2 %>%
-#   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
+#   select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
 #   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
 #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
@@
 # tbl2 <- tbl2 %>%
-#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
 #   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
 #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 # tbl3 <- tbl3 %>%
-#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+#   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
 #   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
+#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
 #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 tbl1 <- tbl2 %>%
-  select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
+  select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- tbl2 %>%
-  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 tbl3 <- tbl3 %>%
-  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 tbl1 <- tbl2 %>%
-  select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
+  select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- tbl2 %>%
-  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
+  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
+                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 tbl3 <- tbl3 %>%
-  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
+  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
+                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ### RDI group
-<span style="color:green">**Table 9 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
 ```{r Table 5 HR adjusted rdi group}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology` 
-```{r}
+<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
+
+<br>
+<br>
+
+### Continous
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat` 
+```{r rdi continous}
 tbl2 <- Frontline %>%
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ```
-<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-### Continous
-<span style="color:green">**Table 10 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
-```{r rdi continous}
+<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
+<!-- RDI for paclitaxel is not a factor associated with survival. -->
+
+<br>
+<br>
+
+## Adjusted by other drug
+### RDI group
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat` 
+```{r Table 5 HR adjusted rdi group adjusted by other drug}
 tbl2 <- Frontline %>%
   filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- 
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
   bold_labels() %>%
   italicize_levels()
-
-# Pacli
-
+```
+<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
+-->
+
+<br>
+<br>
+
+### Continous
+`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat` 
+```{r rdi continous adjusted by other drug}
 tbl2 <- Frontline %>%
   filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
 tbl2 <- 
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vitalstatus) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
-<!-- RDI for paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-## Adjusted by other drug
-### RDI group
-<span style="color:green">**Table 11 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
-```{r Table 5 HR adjusted rdi group adjusted by other drug}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  cox.zph()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
--->
-
-<br>
-<br>
-
-### Continous
-<span style="color:green">**Table 12 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
-```{r rdi continous adjusted by other drug}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H c}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  cox.zph()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vitalstatus) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 <!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp1) %>%  -->
+<!--   select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
 <!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
+<!--   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
+<!--   select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
+<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp1) %>%  -->
+<!--   select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
 <!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
+<!--   select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
+<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
+<!--   select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
 <!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
+<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)), -->
 <!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- ### Multivariable -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_grp1 + raceeth + ageatdx + stagecat` -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp1 + raceeth + ageatdx + stagecat` -->
 <!-- ```{r} -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--              event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vitalstatus) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--              event = tbl3$vitalstatus) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- ### RDI group -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` -->
 <!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug 2} -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
+<!--              event = tbl2$vitalstatus) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
+<!--              event = tbl3$vitalstatus) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- ## Multivariable -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` -->
+<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` -->
 <!-- ```{r bmi HR adjusted} -->
@@
 <!-- #   coxph(Surv(time = tbl1$month_at_os_from_treatment, -->
-<!-- #              event = tbl1$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>% -->
+<!-- #              event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>% -->
 <!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
-<!--              event = tbl2$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>% -->
+<!--              event = tbl2$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
-<!--              event = tbl3$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>% -->
+<!--              event = tbl3$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!-- #   coxph(Surv(time = tbl7$month_at_os_from_treatment, -->
-<!-- #              event = tbl7$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>% -->
+<!-- #              event = tbl7$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>% -->
 <!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl8$month_at_os_from_treatment, -->
-<!--              event = tbl8$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>% -->
+<!--              event = tbl8$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 <!--   coxph(Surv(time = tbl9$month_at_os_from_treatment, -->
-<!--              event = tbl9$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>% -->
+<!--              event = tbl9$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>% -->
 <!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
@@
 
-# Complete case HR analysis
-
-## Multivariable
-### RDI group
-<span style="color:green">**Table 9 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology + debulking` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-### Continous
-<span style="color:green">**Table 10 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology + debulking` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
-<!-- RDI for paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-## Adjusted by other drug
-### RDI group
-<span style="color:green">**Table 11 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H complete case}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>% 
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  cox.zph()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
--->
-
-<br>
-<br>
-
-### Continous
-<span style="color:green">**Table 12 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking` 
-```{r }
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H complete case c}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>% 
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  cox.zph()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-```{r echo=FALSE, out.width='30%'}
+<br>
+<br>
+
+***
+
+```{r echo=FALSE, out.width='500%'}
 knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')

### 2022-02-02 Rmd/Investigate bsa diferences.Rmd
Investigate bsa difference between raw data and du bois formula

--- 2022-01-06 Rmd/Adjusted weight rdi analysis.Rmd
@@
 ---
-title: "Flatiron cleaning"
+title: "Investigate bsa differences"
 author: "Christelle Colin-Leitzinger"
@@
 
+## Investigate bsa differences
+
 ***
@@
 clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
-```
-
-# `r emo::ji("spiral_notepad")` This report is using **adjusted weight**
-
-***
-
-# `r emo::ji("spiral_notepad")` Reminders of each capping and formula:
-
-Creatinine data are capped as :  
-- creat < 0.7 was set at 0.7  
-- creat > 3 are eliminated
-
-ideal_weight is calculated :
-- height <= 1.524               ~ 45.5 + 2.3,
-- height > 1.524                ~ 45.5 + (2.3 * (((`height` - 1.524) / 0.0254)))
-
-adjusted_weight :
-- ((`weight` - `ideal_weight`) * 0.40) + `ideal_weight`
-
-actual_bmi = weight / (height * height)
-
-CrCl calculation :
-
-IF actual_bmi >= 25 :
-$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
-IF actual_bmi < 25 :
-
-$$adjusted\_CrCl = \frac{(140 - ageatdx) * adjusted\_weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
-In both cases CrCl is capped at 125.  
-<br>
-
-Calculating more BSA values :
-$$bsa\_du\_bois = 0.007184 * (height*100)^{0.725} * weight^{0.425}$$
-<br>
-
-I clean the data up by keeping the `relativeorderedamount`:  
-- >= 50 & <= 175 for taxel and cisplatin  and with a unit in `mg/m2`  
-- >= 2  & <= 6   for platin and with a unit in `AUC`
-
-<br>
-
-<!-- mutate(adjusted_expected_dose = case_when( -->
-<!--     drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25), -->
-<!--     drugname == "paclitaxel"                  ~ BSA * target_auc  -->
-<!--     # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug -->
-<!--   )) %>%  -->
-<!--   mutate(adjusted_expected_dose = case_when( -->
-<!--     adjusted_expected_dose > 900 & -->
-<!--       target_auc == 6              ~ 900, -->
-<!--     adjusted_expected_dose > 750 & -->
-<!--       target_auc == 5              ~ 750, -->
-<!--     TRUE                           ~ adjusted_expected_dose -->
-<!--   )) -->
-
-`adjusted_expected_dose` is:  
--`target_auc` * (`adjusted CrCl` + 25)   -> for `drugname` == "carboplatin"  
--`BSA` * `target_auc`                    -> for `drugname` == "paclitaxel"
-(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
-It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).
-
-<br>
-
-<!-- relative_dose_intensity = amount / adjusted_expected_dose -->
-
-Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ received}{adjusted\ expected\ dose}$$
-
-<br>
-
-<span style="color:red">**Please confirm everything is correct**</span>
-
-***
-
-# I. Drug episode cleaning
-
-- Select episodedatasource == "Administrations"
-
-**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
-We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.**
+Frontline <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/Frontline.rds")
+```
+
+```{r}
+
+```
 
@@
 ```
-**But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.**
-
-- Combine multiple administrations of the same drug at the same date
-Flatiron says:
-There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day.
-We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day.
-Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data.
-Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
-For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.  
-Three administrations of the same drug were listed on a Friday.
-The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.
-Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
+
 ```{r combine amount same drug one day}
@@
 
-- Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
 ```{r line coding}
@@
 
-  # 6.Add a 30 day rule to switch linenumber----
-  # group_by(patientid, linenumber_new) %>% 
-  # arrange(episodedate) %>% 
-  # mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
-  # mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
-  # ungroup() %>% 
-  # group_by(patientid) %>% 
-  # mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
-  # mutate(linenumber_new = linenumber_new + jump_line) %>% 
-  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37
-
 ```
@@
   ungroup()
-
-  # # CODE FOR SKIPPED CYCLE
-  # group_by(patientid, linenumber_new) %>% 
-  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
-  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
-  # 
-  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
-  # mutate(n = row_number(drugname)) %>%
-  # 
-  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
-  # fill(base_days_between_cycle, .direction = "downup") %>% 
-  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
-  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
-  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
-  # group_by(patientid, linenumber_new) %>%
-  # mutate(drug_count_perline = n()) %>%
-  # mutate(skipped_cycle_indays1 = ifelse(
-  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
-  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
-  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
-  # group_by(patientid) %>% 
-  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
-  # ungroup()
-
-# rm(drugs, drugs1, therapy_line)
-therapy_cycle %>% distinct(patientid) %>% nrow()
-```
-
-<br>
-
-- Bind everything together to calculate target auc/target dose and expected dose
-
-(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and paclitaxel, they are just present in the same column called `target_auc` for a tidy data organization - You can find the calculations formula at the end of the document)
-When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, and paclitaxel and their `expected_dose`.
-It can be days in between but it can also be more.
-
-`r emo::ji("check")`  
-We decided to take the creatinine, weight, bsa measured within a month of the cycle start date AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line
+```
 
@@
   mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
-  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
-  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
-  select(-bsa_du_bois) %>%
+  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425))# %>% # get pretty close results 4269 patients result
+  # mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
+  # select(-bsa_du_bois) %>%
 
   # Merge with auc
-  left_join(., areaUC, by = c("patientid", "drugname")) %>%
-  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
-                          duration(n=1, unit="days"))) %>% 
-  mutate(interval_auc = case_when(
-    (therapy == "Upfront Surgery" &
-       interval_auc < 31 &
-       # auc_date < lineenddate &
-       auc_date > surgerydate)                  ~ interval_auc,
-
-    therapy == "Upfront Chemo" &
-      (
-        (chemotherapy_type == "Neoadjuvant" &
-           interval_auc < 31 &
-           auc_date < surgerydate) |
-          (chemotherapy_type == "Adjuvant" &
-             interval_auc < 31 &
-             # auc_date < lineenddate &
-             auc_date > surgerydate)
-      )                                          ~ interval_auc,
-    TRUE                                         ~ NA_real_
-  )) %>%
-  arrange(interval_auc) %>% 
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
-           cycle_start_date, .keep_all = TRUE) %>%
-
-  # Calculate expected dose
-  mutate(expected_dose = case_when(
-    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
-    drugname == "paclitaxel"                  ~ BSA * target_auc 
-    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
-  )) %>% 
-  mutate(expected_dose = case_when(
-    expected_dose > 900 &
-      target_auc == 6              ~ 900,
-    expected_dose > 750 &
-      target_auc == 5              ~ 750,
-    TRUE                           ~ expected_dose
-  )) %>% 
-  mutate(adjusted_expected_dose = case_when(
-    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
-    drugname == "paclitaxel"                  ~ BSA * target_auc 
-    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
-  )) %>% 
-  mutate(adjusted_expected_dose = case_when(
-    adjusted_expected_dose > 900 &
-      target_auc == 6              ~ 900,
-    adjusted_expected_dose > 750 &
-      target_auc == 5              ~ 750,
-    TRUE                           ~ adjusted_expected_dose
-  )) %>% 
-  group_by(patientid) %>%
-  mutate(first_treatment_date = case_when(
-    str_detect(therapy, "Chemo")                      ~ min(episodedate),
-    str_detect(therapy, "Surgery")                    ~ surgerydate,
-  )) %>% 
-  ungroup() %>% 
-  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
-                   duration(n=1, units = "months")) %>% 
-  arrange(patientid, episodedate)
-
-Treatment1 %>% distinct(patientid) %>% nrow()
-```
-
-```{r plot interval}
-# Treatment %>% 
-#   ggplot(aes(x= interval_creat)) +
-#   geom_bar() #+
-#   # coord_cartesian(ylim=c(0,50))
-# # Treatment %>% 
-# #   ggplot(aes(x= interval_height)) +
-# #   geom_bar() +
-# #   coord_cartesian(ylim=c(0,50))
-# Treatment %>% 
-#   ggplot(aes(x= interval_weight)) +
-#   geom_bar() #+
-#   # coord_cartesian(ylim=c(0,50))
-# Treatment %>% 
-#   ggplot(aes(x= interval_bsa)) +
-#   geom_bar() #+
-#   # coord_cartesian(ylim=c(0,50))
-# Treatment %>% 
-#   ggplot(aes(x= interval_auc)) +
-#   geom_bar() #+
-#   # coord_cartesian(ylim=c(0,50))
-```
-
-<!-- # Variable for filtering -->
-
-```{r rule between diagnosis and treatment}
-Treatment <- Treatment1 %>% 
-  filter(route == "Intravenous") %>% 
-  # step 1: Flatiron recommendation cleanup
-  # 90 days rule between diagnosis and treatment
-  group_by(patientid) %>% 
-  mutate(first_drug_date = first(episodedate)) %>% 
-  ungroup() %>% 
-  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
-           duration(n=1, units = "days")) %>% 
-  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
-           duration(n=1, units = "days")) %>% 
-  mutate(days_at_first_treatment = case_when(
-    therapy == "Upfront Chemo" |
-      therapy == "Chemotherapy only"             ~ interval(start = diagnosisdate, end = first_drug_date)/
-           duration(n=1, units = "days"),
-    therapy == "Upfront Surgery" |
-      therapy == "Surgery Only"                  ~ interval(start = diagnosisdate, end = surgerydate)/
-           duration(n=1, units = "days")
-  )) %>% 
-  # 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis
-  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
-           duration(n=1, units = "days")
-  ) %>% 
-  mutate(flatiron_rules = case_when(
-    days_at_first_treatment > 90                 ~ "exclude",
-    thirty_days_exclusion <= 30                  ~ "exclude",
-    exclude == "1"                               ~ "exclude"
-  )) %>%
-  group_by(patientid) %>% 
-  fill(flatiron_rules, .direction = "downup") %>% 
-  ungroup() %>%
-
-  # step 2: Filter patients with clinical characteristics fitting to the study criteria
-  # include only patients who received platin and/or taxane
-  mutate(had_carbo_pacli = case_when(
-    drugname == "paclitaxel" |
-      drugname == "carboplatin"             ~ "Yes"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(had_carbo_pacli, .direction = "updown") %>% 
-  ungroup() %>% 
-  # include patients with single or dual P/T +/- Bev as frontline treatment
-  mutate(line_keep = case_when(# F002B429BE6C6
-    (linenumber_adj == 1 &
-           (linename == "Carboplatin,Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
-           linename == "Carboplatin" |
-           linename == "Paclitaxel" |
-           linename == "Bevacizumab,Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin"))            ~ NA_character_,
-    linenumber_adj == 1                                       ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(line_keep, .direction = "updown") %>% 
-  ungroup() %>%
-
-  # step 3: Filter out patients with missing data
-  # remove patients with long gap between surgery and adjuvant start (3 months)
-  mutate(interval_surgery_to_adj_start = case_when(
-      chemotherapy_type == "Adjuvant" &
-        linenumber_adj == 1       
-      ~ interval(start = surgerydate, end = linestartdate) / duration(n = 1, units = "months")
-    )) %>% 
-  mutate(gap_surg_drugs = case_when(
-    interval_surgery_to_adj_start > 3                  ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(gap_surg_drugs, .direction = "updown") %>% 
-  ungroup() %>%
-
-  # step 4: Include patients with treatments following the standard of clinical care
-  # exclude patients with more than 1 line as Neo
-  mutate(neo_more_more_than_1line = case_when(
-    chemotherapy_type == "Neoadjuvant" &
-           linenumber_new != 1                 ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(neo_more_more_than_1line, .direction = "updown") %>% 
-  ungroup() %>% 
-  # exclude patients with maintenance within their frontline
-  mutate(frontline_has_maintenance = case_when(
-    linenumber_adj == 1 &
-    ismaintenancetherapy == "TRUE"             ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(frontline_has_maintenance, .direction = "updown") %>% 
-  ungroup() %>% 
-  # exclude patients with more than 6 cycles in Neo, more than 9 cycles total 
-  # in upfront chemo or more than 9 cycles in upfront surgery
-  mutate(too_many_cycle = case_when(
-    (linenumber_new == 1 &
-       therapy == "Upfront Chemo" &
-       total_cycle_increment > 6) |
-
-      (linenumber_new == 2 &
-         therapy == "Upfront Chemo" &
-         total_cycle_increment > 9) |
-
-      (linenumber_new == 1 &
-         therapy == "Upfront Surgery" &
-         total_cycle_increment > 9)             ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(too_many_cycle, .direction = "updown") %>%
-  ungroup() %>% 
-  # Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
-  # Removes also the patients who has only carbo or only pacli
-  # dose_dense will need to be changed if we change and include these patients
-  arrange(patientid, episodedate, drugname) %>% 
-  mutate(wrong_pacli_dosedense = case_when(
-    drugname == "paclitaxel" &
-      is.na(too_many_cycle) &
-      (dose_dense == 2 |
-      dose_dense > 3) &
-      linenumber_adj == 1
-      # ((linenumber_new == 1 &
-      #  therapy == "Upfront Chemo") |
-      # (linenumber_new == 2 &
-      #    therapy == "Upfront Chemo") |
-      # (linenumber_new == 1 &
-      #    therapy == "Upfront Surgery"))
-    ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
-  ungroup() %>% 
-  # Exclude patients who switch drug within a line
-  mutate(switch_drugs = case_when(
-    str_detect(linename, "Pacli") & 
-      drugname == "docetaxel" & 
-      linenumber_adj == 1                      ~ "exclude",
-    str_detect(linename, "Car") & 
-      drugname == "cisplatin" & 
-      linenumber_adj == 1                      ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(switch_drugs, .direction = "updown") %>% 
-  ungroup()
-
-  # group_by(patientid, wrong_pacli_dosedense) %>% 
-  # mutate(n_dose_dense = n()) %>% 
+  # left_join(., areaUC, by = c("patientid", "drugname")) %>%
+  # mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
+  #                         duration(n=1, unit="days"))) %>% 
+  # mutate(interval_auc = case_when(
+  #   (therapy == "Upfront Surgery" &
+  #      interval_auc < 31 &
+  #      # auc_date < lineenddate &
+  #      auc_date > surgerydate)                  ~ interval_auc,
   #   
+  #   therapy == "Upfront Chemo" &
+  #     (
+  #       (chemotherapy_type == "Neoadjuvant" &
+  #          interval_auc < 31 &
+  #          auc_date < surgerydate) |
+  #         (chemotherapy_type == "Adjuvant" &
+  #            interval_auc < 31 &
+  #            # auc_date < lineenddate &
+  #            auc_date > surgerydate)
+  #     )                                          ~ interval_auc,
+  #   TRUE                                         ~ NA_real_
+  # )) %>%
+  # arrange(interval_auc) %>% 
+  # distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
+  #          cycle_start_date, .keep_all = TRUE) %>% 
   # 
-  # 
-  # is.na(too_many_cycle)
-
-Treatment %>% distinct(patientid) %>% nrow()
-```
-
-```{r RDI calculation}
-Treatment <- Treatment %>% 
-  # filter(chemotherapy_type == "Neoadjuvant" |
-  #          (chemotherapy_type == "Adjuvant" &
-  #             linenumber_adj == 1)) %>%
-
-  mutate(relative_dose_intensity = amount / adjusted_expected_dose # adjusted_expected_dose
-  ) %>%
-  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
-  #        relative_dose_intensity, linenumber_adj) %>%
-
-  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
-  group_by(patientid, chemotherapy_type, drugname) %>%
-  # mutate(mean_RDI_per_drug = case_when(
-  #   chemotherapy_type == "Adjuvant" &
-  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
-  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  # # Calculate expected dose
+  # mutate(expected_dose = case_when(
+  #   drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
+  #   drugname == "paclitaxel"                  ~ BSA * target_auc 
+  #   # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
   # )) %>% 
-  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
-  ) %>% 
-  ungroup()
-
-RDI_data <- Treatment %>% 
-  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
-  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))
-```
-
-```{r RDI calculation group}
-RDI_data <- RDI_data %>% 
-  # general
-  mutate(RDI_grp = case_when(
-    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
-    mean_RDI_per_drug < 0.85               ~ "Underdosed"
-  )) %>% 
-  mutate(RDI_grp = factor(RDI_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
-  mutate(RDI_grp1 = case_when(
-    mean_RDI_per_drug < 0.75               ~ "Highly underdosed",
-    mean_RDI_per_drug >= 0.75 &
-      mean_RDI_per_drug < 0.85             ~ "Underdosed",
-    mean_RDI_per_drug >= 0.85 &
-      mean_RDI_per_drug < 1.1              ~ "Adequate dosing",
-    mean_RDI_per_drug >= 1.1               ~ "Overdosing"
-  )) %>% 
-  mutate(RDI_grp1 = factor(RDI_grp1, 
-                          levels = c("Adequate dosing",
-                                     "Underdosed", 
-                                     "Highly underdosed",
-                                     "Overdosing"))) %>% 
-  # separated
-  mutate(RDI_carbo_neo = case_when(
-    drugname == "carboplatin" &
-      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
-    TRUE                                    ~ NA_real_
-  )) %>% 
-  mutate(RDI_pacli_neo = case_when(
-    drugname == "paclitaxel" &
-      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
-    TRUE                                    ~ NA_real_
-  )) %>% 
-  mutate(RDI_carbo_adj = case_when(
-    drugname == "carboplatin" &
-      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
-    TRUE                                    ~ NA_real_
-  )) %>% 
-  mutate(RDI_pacli_adj = case_when(
-    drugname == "paclitaxel" &
-      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
-    TRUE                                    ~ NA_real_
-  )) %>%
-
-  mutate(RDI_carbo_neo_grp = case_when(
-    RDI_carbo_neo >= 0.85              ~ "Adequate dosing",
-    RDI_carbo_neo < 0.85               ~ "Underdosed"
-  )) %>% 
-  mutate(RDI_carbo_neo_grp = factor(RDI_carbo_neo_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
-  mutate(RDI_carbo_neo_grp1 = case_when(
-    RDI_carbo_neo < 0.75               ~ "Highly underdosed",
-    RDI_carbo_neo >= 0.75 &
-      RDI_carbo_neo < 0.85             ~ "Underdosed",
-    RDI_carbo_neo >= 0.85 &
-      RDI_carbo_neo < 1.1              ~ "Adequate dosing",
-    RDI_carbo_neo >= 1.1               ~ "Overdosing"
-  )) %>% 
-  mutate(RDI_carbo_neo_grp1 = factor(RDI_carbo_neo_grp1, 
-                          levels = c("Adequate dosing",
-                                     "Underdosed", 
-                                     "Highly underdosed",
-                                     "Overdosing"))) %>% 
-  mutate(RDI_pacli_neo_grp = case_when(
-    RDI_pacli_neo >= 0.85              ~ "Adequate dosing",
-    RDI_pacli_neo < 0.85               ~ "Underdosed"
-  )) %>% 
-  mutate(RDI_pacli_neo_grp = factor(RDI_pacli_neo_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
-  mutate(RDI_pacli_neo_grp1 = case_when(
-    RDI_pacli_neo < 0.75               ~ "Highly underdosed",
-    RDI_pacli_neo >= 0.75 &
-      RDI_pacli_neo < 0.85             ~ "Underdosed",
-    RDI_pacli_neo >= 0.85 &
-      RDI_pacli_neo < 1.1              ~ "Adequate dosing",
-    RDI_pacli_neo >= 1.1               ~ "Overdosing"
-  )) %>% 
-  mutate(RDI_pacli_neo_grp1 = factor(RDI_pacli_neo_grp1, 
-                          levels = c("Adequate dosing",
-                                     "Underdosed", 
-                                     "Highly underdosed",
-                                     "Overdosing"))) %>%
-
-  mutate(RDI_carbo_adj_grp = case_when(
-    RDI_carbo_adj >= 0.85              ~ "Adequate dosing",
-    RDI_carbo_adj < 0.85               ~ "Underdosed"
-  )) %>% 
-  mutate(RDI_carbo_adj_grp = factor(RDI_carbo_adj_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
-  mutate(RDI_carbo_adj_grp1 = case_when(
-    RDI_carbo_adj < 0.75               ~ "Highly underdosed",
-    RDI_carbo_adj >= 0.75 &
-      RDI_carbo_adj < 0.85             ~ "Underdosed",
-    RDI_carbo_adj >= 0.85 &
-      RDI_carbo_adj < 1.1              ~ "Adequate dosing",
-    RDI_carbo_adj >= 1.1               ~ "Overdosing"
-  )) %>% 
-  mutate(RDI_carbo_adj_grp1 = factor(RDI_carbo_adj_grp1, 
-                          levels = c("Adequate dosing",
-                                     "Underdosed", 
-                                     "Highly underdosed",
-                                     "Overdosing"))) %>% 
-  mutate(RDI_pacli_adj_grp = case_when(
-    RDI_pacli_adj >= 0.85              ~ "Adequate dosing",
-    RDI_pacli_adj < 0.85               ~ "Underdosed"
-  )) %>% 
-  mutate(RDI_pacli_adj_grp = factor(RDI_pacli_adj_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
-  mutate(RDI_pacli_adj_grp1 = case_when(
-    RDI_pacli_adj < 0.75               ~ "Highly underdosed",
-    RDI_pacli_adj >= 0.75 &
-      RDI_pacli_adj < 0.85             ~ "Underdosed",
-    RDI_pacli_adj >= 0.85 &
-      RDI_pacli_adj < 1.1              ~ "Adequate dosing",
-    RDI_pacli_adj >= 1.1               ~ "Overdosing"
-  )) %>% 
-  mutate(RDI_pacli_adj_grp1 = factor(RDI_pacli_adj_grp1, 
-                          levels = c("Adequate dosing",
-                                     "Underdosed", 
-                                     "Highly underdosed",
-                                     "Overdosing")))
-RDI_data %>% distinct(patientid) %>% nrow()
-```
-
-```{r RDI_data}
-RDI_data <- RDI_data %>% 
-  group_by(patientid) %>% 
-  fill(RDI_carbo_neo, RDI_carbo_neo_grp, RDI_carbo_neo_grp1, 
-       RDI_pacli_neo, RDI_pacli_neo_grp, RDI_pacli_neo_grp1, 
-       RDI_carbo_adj, RDI_carbo_adj_grp, RDI_carbo_adj_grp1, 
-       RDI_pacli_adj, RDI_pacli_adj_grp, RDI_pacli_adj_grp1, 
-       .direction = "downup") %>% 
-  ungroup()
-Frontline_adjusted <- RDI_data %>% 
-  distinct(patientid, .keep_all = TRUE)
-```
+  # mutate(expected_dose = case_when(
+  #   expected_dose > 900 &
+  #     target_auc == 6              ~ 900,
+  #   expected_dose > 750 &
+  #     target_auc == 5              ~ 750,
+  #   TRUE                           ~ expected_dose
+  # )) %>% 
+  # mutate(adjusted_expected_dose = case_when(
+  #   drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
+  #   drugname == "paclitaxel"                  ~ BSA * target_auc 
+  #   # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
+  # )) %>% 
+  # mutate(adjusted_expected_dose = case_when(
+  #   adjusted_expected_dose > 900 &
+  #     target_auc == 6              ~ 900,
+  #   adjusted_expected_dose > 750 &
+  #     target_auc == 5              ~ 750,
+  #   TRUE                           ~ adjusted_expected_dose
+  # )) %>% 
+  # group_by(patientid) %>%
+  # mutate(first_treatment_date = case_when(
+  #   str_detect(therapy, "Chemo")                      ~ min(episodedate),
+  #   str_detect(therapy, "Surgery")                    ~ surgerydate,
+  # )) %>% 
+  # ungroup() %>% 
+  # mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
+  #                  duration(n=1, units = "months")) %>% 
+  # arrange(patientid, episodedate)
+
+```
+
+# Correlation BSA
 
 ```{r}
-# rm(areaUC, body_surface_area, creatinine, clinical_data, drugs, drugs1, 
-#    height#, therapy_cycle, therapy_line, Treatment, weight
-#    )
-```
-
-<br>
-<br>
-
-# **Number of patients : `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**
-
-######################################################################################################################
-######################################################################################################################
-######################################################################################################################
-######################################################################################################################
-
-<!-- # Variable for filtering -->
-
-<!-- ```{r rule between diagnosis and treatment} -->
-<!-- drugs1 <- Frontline_adjusted %>%  -->
-<!--   # 1. 60 days rule between diagnosis and treatment # Loss 1 -->
-<!--   group_by(patientid) %>%  -->
-<!--   mutate(first_drug_date = first(episodedate)) %>%  -->
-<!--   mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/ -->
-<!--            duration(n=1, units = "days")) %>%  -->
-<!--   mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/ -->
-<!--            duration(n=1, units = "days")) %>%  -->
-<!--   ungroup() %>%  -->
-<!--   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/ -->
-<!--            duration(n=1, units = "days") -->
-<!--   ) -->
-<!-- ``` -->
-
-<br>
-
-## 1. step 1: Flatiron recommendation cleanup
-
-This step is to remove patients from the population that don't follow flatiron recommendations.
-
-- 90 days rule between diagnosis and treatment  
-Flatiron propose a conceptual instruction on the 90-day-gap : 90 days between diagnosis and treatment.  
-It is meant to exclude patients who didn't get treatment for 90 days which would most likely mean that some treatment data are missing. Patients left after this step:
-
-- 30 days rule excluding patient who didn't survive for at least 30 days after diagnosis  
-This is something that Flatiron strongly recommends, but does not require. Flatiron proposal reviewers will likely provide comments on this if not incorporated into a proposal.
-
-- Exclude exclude == "1" coded by Lauren
-
-Are excluded :  
--	Borderline cases (not invasive ovarian cancer)  
--	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
--	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)
-```{r}
-flatiron_rec <- Frontline_adjusted %>% 
-  filter(is.na(flatiron_rules))
-```
-
-**At the end of the step 1, we have `r flatiron_rec %>% distinct(patientid) %>% nrow()` patients.**
-
-<br>
-
-## 2. step 2: Filter patients with clinical characteristics fitting to the study criteria
-
-- exclude patients whose histology is unknown  
-- remove chemotherapy only patients
-- include only patients who received platin and/or taxane
-- exclude patients who only received neo + surgery
-- include patients with single or dual P/T +/- Bev as frontline treatment
-```{r}
-study_criteria <- flatiron_rec %>% 
-  filter(!is.na(histology))
-
-study_criteria <- study_criteria %>%
-  filter(!is.na(surgerydate)) %>% 
-  mutate(chemotherapy_type = factor(chemotherapy_type))
-
-study_criteria <- study_criteria %>%
-  filter(had_carbo_pacli == "Yes")
-
-study_criteria <- study_criteria %>% 
-  filter(treatment_sequence == "neo + surg + adj" |
-           treatment_sequence == "surg + adj")
-
-# F0017FB3A8828 starts with gemcitabine then have carbo
-
-study_criteria <- study_criteria %>%
-  filter(is.na(line_keep))
-  # Remove patients with other linename
-  # filter((linenumber_new == 1 &
-  #          (linename == "Carboplatin,Paclitaxel" |
-  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
-  #          linename == "Carboplatin" |
-  #          linename == "Paclitaxel" |
-  #          linename == "Bevacizumab,Paclitaxel" |
-  #          linename == "Bevacizumab,Carboplatin")) |
-  #         (linenumber_new == 2 &
-  #         therapy == "Upfront Chemo" &
-  #          (linename == "Carboplatin,Paclitaxel" |
-  #          linename == "Bevacizumab,Carboplatin,Paclitaxel" |
-  #          linename == "Carboplatin" |
-  #          linename == "Bevacizumab,Paclitaxel" |
-  #          linename == "Paclitaxel" |
-  #          linename == "Bevacizumab,Carboplatin"))
-  #        )
-```
-
-**At the end of the step 2, we have `r study_criteria %>% distinct(patientid) %>% nrow()` patients.**
-
-<br>
-
-## 3. step 3: Filter out patients with missing data
-
-- exclude the patients who had surgery but we don't have a date of surgery -> NONE removed anymore  
-- remove patients with long gap between surgery and adjuvant start (3  months) -> NONE removed anymore  
-- exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
-- exclude patients for whose no RDI were available
-
-```{r}
-missing_data <- study_criteria %>% 
-  filter(!(issurgery == "Yes" & is.na(surgerydate)))
-
-missing_data <- missing_data %>%
-  filter(is.na(gap_surg_drugs))
-
-missing_data <- missing_data %>% 
-  filter(days_at_first_drug >= 0 &
-           (is.na(surgerydate) | days_at_surg >= 0)
-         )
-
-missing_data <- missing_data %>% 
-  # remove these patients who switched C > C 
-  filter((
-    therapy == "Upfront Chemo" &
-      (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
-         !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
-  ) | (
-    therapy == "Upfront Surgery" &
-      (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
-  )
-  )
-```
-**At the end of the step 3, we have `r missing_data %>% distinct(patientid) %>% nrow()` patients.**
-
-## 4. step 4: Include patients with treatments following the standard of clinical care
-
-- exclude patients with more than 1 line as Neo
-- exclude patients with maintenance within their frontline
-- exclude patients with more than 6 cycles in Neo, more than 9 cycles **total** in upfront chemo or more than 9 cycles in upfront surgery
-```{r}
-standard_care <- missing_data %>% 
-  # Remove patients with more than 1 line as Neo
-  filter(is.na(neo_more_more_than_1line))
-
-standard_care <- standard_care %>% 
-  filter(is.na(frontline_has_maintenance))
-
-standard_care <- standard_care %>% 
-  filter(is.na(too_many_cycle))
-```
-**We have `r standard_care %>% distinct(patientid) %>% nrow()` patients.**
-
-- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
-```{r}
-standard_care <- standard_care %>% 
-  filter(is.na(wrong_pacli_dosedense))
-
-# standard_care %>% 
-#   mutate(n_dose_dense = factor(n_dose_dense)) %>% 
-#   select(n_dose_dense, therapy) %>% 
-#   tbl_summary(by = therapy)
-
-# test <- Frontline %>% 
-#   filter(wrong_pacli_dosedense == "exclude")
-# 
-# wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
-#   filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
-#   select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
-```
-**We have `r standard_care %>% distinct(patientid) %>% nrow()` patients.**
-
-```{r}
-# d <- end_patients_Treatment %>% 
-#   select(patientid, linename, linenumber_new, chemotherapy_type, therapy, cycle_increment, total_cycle_increment, ismaintenancetherapy)
-
-# end_patients_Treatment %>% 
-#   mutate(total_cycle_increment = factor(total_cycle_increment)) %>% 
-#   arrange(desc(total_cycle_increment)) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(total_cycle_increment, therapy) %>% 
-#   tbl_summary(by = therapy)
-```
-
-- exclude patients who switch drug within a line
-
-<!-- Patients left: -->
-```{r}
-# switch cispl vs carbo  Car > Cis F1BF7208F0E96
-
-# remove_switch <- therapy_line %>% 
-#   filter(linenumber_adj == 1 &
-#     ((str_detect(linename, "Carboplatin") & drugname == "cisplatin") |
-#   (str_detect(linename, "Cisplatin") & drugname == "carboplatin"))
-#   ) %>%
-#   distinct(patientid)
-# remove_switch <- paste(remove_switch$patientid, collapse = "|")
-# 
-# therapy_line <- therapy_line %>% 
-#   # remove these patients who switched C > C 
-#   filter(!str_detect(patientid, remove_switch))
-# therapy_line %>% distinct(patientid) %>% nrow()
-```
-
-```{r}
-Frontline <- standard_care %>%
-  filter(is.na(switch_drugs))
-```
-
-<!-- TABLES -->
-
-```{r}
-# missing_data %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(had_neo, had_adj, therapy) %>% 
-#   tbl_summary(by = therapy,
-#               type = list(had_neo ~ "dichotomous", 
-#                           had_adj ~ "dichotomous"),
-#               missing = "no")
-# # therapy_line %>% 
-# #   distinct(patientid, .keep_all = TRUE) %>% 
-# #   select(therapy, treatment_sequence) %>% 
-# #   tbl_summary(by = therapy)
-```
-
-<!-- First table is frontline Neo, second table is frontline Adj. -->
-```{r}
-# # drugs1 %>% Need to do in Frontline
-#   filter(linenumber == 1
-#          ) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(linename) %>% 
-#   tbl_summary(sort = list(everything() ~ "frequency"))
-# 
-# # missing_data %>% 
-# #   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
-# #   distinct(patientid, .keep_all = TRUE) %>% 
-# #   select(linename) %>% 
-# #   tbl_summary(sort = list(everything() ~ "frequency"))
-```
-
-<!-- ### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line -->
-```{r Number of patient who switch line}
-# therapy_line %>% 
-#   mutate(change_line = case_when(
-#     linenumber == 1 & 
-#       linenumber_new == 2 &
-#       chemotherapy_type == "Adjuvant" &
-#       therapy == "Upfront Chemo"                   ~ 1,
-#     TRUE                                           ~ 0
-#   )) %>% 
-#   arrange(desc(change_line)) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   select(change_line) %>% 
-#   tbl_summary()
-```
-
-<!-- For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line? -->
-```{r}
-# therapy_line %>% 
-#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
-#            duration(n = 1, units = "days")) %>% 
-#   filter(linenumber == 1 & linenumber_new == 2) %>% 
-#   # select(patientid, linenumber, linenumber_new, linenumber_adj, 
-#   #        drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   ggplot(aes(x= line_duration))+
-#   geom_histogram(aes(fill = route), binwidth = 7) +
-#   theme_minimal(base_size = 14)+
-#   labs(x="Line duration", 
-#        y="Number of Patient",
-#        caption = "Each bar represents 7 days, bottom plot is zoomed in")+
-#   ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
-```
-<!-- Several patients have a short line.   -->
-<!-- `r emo::ji("question_mark")` **Should we remove the patient with a line lasting less than a cycle** We said during October meeting to check if were IP administration.... -->
-
-```{r}
-# therapy_line %>% 
-#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
-#            duration(n = 1, units = "days")) %>% 
-#   filter(linenumber == 1 & linenumber_new == 2) %>% 
-#   select(patientid, surgerydate, episodedate, line_duration, drugname,
-#          chemotherapy_type, therapy, 
-#          linenumber, linenumber_new, route, amount) %>% 
-#   filter(line_duration < 30) %>% 
-#   arrange(line_duration, patientid, episodedate)
-```
-
-<!-- Here a real example of this type of patient : initial `linenumber` = 1 but had surgery in 09/2019 so part of this line in moved to `linenumber_new` = 2 and then coded as adjuvant line.   -->
-<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle. <span style="color:red">**Is that correct?**</span>   -->
-```{r Number of patient who switch line2, rows.print=30}
-# Problem F0000AD999ABF but would be good for F003F2BEEDB37
-# therapy_line %>% 
-#   filter(str_detect(patientid, "F41E15E18E008")) %>% 
-#   arrange(patientid, episodedate) %>% 
-#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
-```
-
-<!-- Here an example a little more complicated because the patient had surgery 05/2017 and the same type of switch but then had a 3rd line (used to be line 2 in flatiron).     -->
-<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle switched to adjuvant and not the longer line witch was coded 2 by flatiron.
-<span style="color:red">**Is that correct?**</span>   -->
-```{r, rows.print=30}
-# therapy_line %>% 
-#   filter(str_detect(patientid, "FC9D28216FEBE")) %>% 
-#   arrange(patientid, episodedate) %>% 
-#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
-
-# therapy_line %>% 
-#   mutate(change_line = case_when(
-#     linenumber == 1 & 
-#       linenumber_new == 2 &
-#       chemotherapy_type == "Adjuvant" &
-#       treatment_sequence == "neo + surg + adj"     ~ 1,
-#     TRUE                                           ~ 0
-#   )) %>% 
-#   filter(change_line == 1) %>% 
-#   group_by(patientid) %>% 
-#   mutate(firstdate = first(episodedate)) %>% 
-#   mutate(lastdate = last(episodedate)) %>% 
-#   ungroup() %>% 
-#   mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
-#   distinct(patientid, .keep_all = TRUE) %>% 
-#   ggplot(aes(x=time_of_switch_line, fill = ..count..))+
-#   geom_histogram(binwidth = 7)+
-#   theme_minimal(base_size = 14)+
-#   ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
-#   scale_y_continuous(#breaks=c(0, 50, 100, 150),
-#                      minor_breaks=c(10, 20, 30, 40)#,
-#                      #labels = c(0, 50, 100, 150)
-#   )
-```
-<!-- `r emo::ji("question_mark")`   -->
-<!-- <span style="color:red">**So the bigger question is : Is it acceptable to include the patients who have a switched line?**</span> -->
-
-<!-- <span style="color:red">**Random question : within 1 cycle we can have taxanes multiple times, is it possible for carboplatin or cisplatin?**</span>   -->
-
-<br>
-<br>
-
-# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**
-
-# Imputation for stagecat and debulking status
-
-https://bookdown.org/mwheymans/bookmi/data-analysis-after-multiple-imputation.html#data-analysis-in-spss
-https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf
-
-Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
-Look at the Cox regression model before imputation.
-
-### For Upfront Chemo
-```{r}
-data <- Frontline %>% 
-  filter(therapy == "Upfront Chemo") %>% 
-  select(patientid, month_at_os, vital_status, 
-         raceeth, diagnosisdate, surgerydate,
-         ageatdx, stagecat, debulking, histology,
-         RDI_carbo_neo, RDI_pacli_neo, 
-         RDI_carbo_adj, RDI_pacli_adj
-         # therapy
-  )
-nonimp_cox_model <-
-  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
-        data = data)
-nonimp_cox_model
-
-Hazard <- nelsonaalen(data, month_at_os, vital_status)
-dataset <- data.frame(data, Hazard)
-```
-
-Start imputation to look at matrix
-```{r}
-Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
-# summary(Cox.imp)
-Pred <- Cox.imp$predictorMatrix
-# Pred["debulking", "month_at_os"] <- 0
-Pred
-```
-
-patientid is not used which is good. But SURGERYDATE IS NOT.
-```{r}
-Pred[, "surgerydate"] <- 1
-Pred["surgerydate", "surgerydate"] <- 0
-Pred
-```
-
-Imputation and cox regression model on imputed data using the new predictor matrix.
-```{r}
-# Start imputations using mice
-Cox.imp <- mice(dataset, m=5, maxit=50, 
-                predictorMatrix=Pred,
-                seed=123, printFlag=F)
-check1 <- with(data = Cox.imp,
-       exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
-       ))
-pool(check1)$pooled
-```
-
-Do m = 34 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.339 that we multiply by 100)
-```{r}
-Cox.imp <- mice(dataset, m=34, maxit=50, 
-                predictorMatrix=Pred,
-                seed=123, printFlag=F)
-
-fit.Cox <-
-  with(data = Cox.imp,
-       exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
-       ))
-
-summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
-  kableExtra::kable() %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
-```
-Above results are exponentiated (imputed data).  
-As a reminder before imputation results are :
-```{r}
-nonimp_cox_model
-```
-
-Complete the chemo data and merge with original
-```{r}
-imputed_data_chemo <- complete(Cox.imp, include = FALSE) %>% 
-  rename(imp_stagecat = stagecat, imp_debulking = debulking)
-```
-
-Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
-
-### For Upfront Surgery
-```{r}
-data <- Frontline %>% 
-  filter(therapy == "Upfront Surgery") %>% 
-  select(patientid, month_at_os, vital_status, 
-         raceeth, diagnosisdate, surgerydate,
-         ageatdx, stagecat, debulking, histology,
-         RDI_carbo_adj, RDI_pacli_adj
-         # therapy
-  )
-nonimp_cox_model <-
-  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
-        data = data)
-nonimp_cox_model
-
-Hazard <- nelsonaalen(data, month_at_os, vital_status)
-dataset <- data.frame(data, Hazard)
-```
-
-Start imputation to look at matrix
-```{r}
-Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
-# summary(Cox.imp)
-Pred <- Cox.imp$predictorMatrix
-# Pred["debulking", "month_at_os"] <- 0
-Pred
-```
-
-patientid is not used which is good. But SURGERYDATE IS NOT
-```{r}
-Pred[, "surgerydate"] <- 1
-Pred["surgerydate", "surgerydate"] <- 0
-Pred
-```
-
-Imputation and cox regression model on imputed data using the new predictor matrix.
-```{r}
-# Start imputations using mice
-Cox.imp <- mice(dataset, m=5, maxit=50, 
-                predictorMatrix=Pred,
-                seed=123, printFlag=F)
-check1 <- with(data = Cox.imp,
-       exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
-       ))
-pool(check1)$pooled
-```
-
-Do m = 17 (The max fmi = 0.166 that we multiply by 100)
-```{r}
-Cox.imp <- mice(dataset, m=17, maxit=50, 
-                predictorMatrix=Pred,
-                seed=123, printFlag=F)
-
-fit.Cox <-
-  with(data = Cox.imp,
-       exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
-       ))
-
-summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
-  kableExtra::kable() %>%
-  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
-```
-Above results are exponentiated (imputed data).  
-As a reminder before imputation results are :
-```{r}
-nonimp_cox_model
-```
-
-Complete the data and merge with original
-```{r}
-imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
-  rename(imp_stagecat = stagecat, imp_debulking = debulking)
-
-imputed_data <- bind_rows(imputed_data_chemo, imputed_data_surg)
-
-# Frontline <- 
-#   full_join(Frontline, imputed_data %>% 
-#               select(patientid, starts_with("imp_")), 
-#             by = "patientid") 
-Frontline <- 
-  full_join(Frontline, imputed_data %>% 
-              select(patientid, starts_with("imp_")), 
-            by = "patientid") 
-```
-
-***
-
-<br>
-
-# II.Data analysis
-## Explore the dataset
-
-```{r}
-full_data_study_pop <- 
-  Treatment %>% 
+library(ggcorrplot)
+Treatment1 <- Treatment1 %>% 
   filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
   arrange(patientid, episodedate, drugname)
-```
-
-### Number of line /cycle received by patients in our study population
-
-<span style="color:green">**Table supp 1 Number of total line**</span>
-```{r}
-full_data_study_pop %>% 
-  arrange(desc(linenumber_new)) %>% 
+
+# coalesce(bsa_at_dx, bsa_du_bois)
+a <- Treatment1 %>% 
+  distinct(patientid, cycle_increment, .keep_all = TRUE) %>% 
+  select(BSA, bsa_du_bois)
+head(a)
+# p.mat <- cor_pmat(a)
+mat <- cor(a, use = "pairwise.complete.obs")
+ggcorrplot(mat, hc.order = TRUE, method = "square",
+           insig = "blank", # Leave blank on no significant coefficient
+           type = "lower",
+           lab = TRUE,
+           title = "Correlation",
+           show.legend = TRUE, legend.title = "Correlation", show.diag = TRUE,
+           lab_col = "darkblue", lab_size = 3,
+           sig.level = 0.05, #insig = c("pch", "blank"), pch = 4, pch.col = "black", pch.cex = 10,
+           tl.cex = 10,
+           tl.srt = 90,
+           # digits = 1,
+           outline.color = "white",
+  ggtheme = ggplot2::theme_gray,
+  colors = c("blue", "white", "#E46726")
+)
+
+a <-Treatment1 %>% 
   distinct(patientid, .keep_all = TRUE) %>% 
-  select(linenumber_new, therapy) %>% 
-  tbl_summary(by = therapy)
-```
-
-<span style="color:green">**Table supp 1 Number of cycle in Neo**</span>
-```{r}
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
-  arrange(desc(cycle_increment)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment) %>% 
-  tbl_summary()
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
-  arrange(desc(cycle_increment)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment) %>% 
-  tbl_summary(type = list(cycle_increment ~ "continuous"))
-```
-
-<span style="color:green">**Table supp 1 Number of cycle in Adj**</span>
-```{r}
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
-  arrange(desc(cycle_increment)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment, therapy) %>% 
-  tbl_summary(by = therapy)
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
-  arrange(desc(cycle_increment)) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(cycle_increment, therapy) %>% 
-  tbl_summary(by = therapy,
-              type = list(cycle_increment ~ "continuous"))
-```
-<br>
-
-<!-- ## Missingness -->
-<!-- Here some representation of missingness in our data:   -->
-<!-- - In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx).
-Because these parameters overlap only 25 patients will have missing value for all of them.
--->
-<!-- - In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation).
-the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
--->
-```{r}
-# library(naniar)
-# 
-# Frontline %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
-#   gg_miss_upset()
-
-# is.na(Frontline$CrCl) %>% sum()
-# is.na(Frontline$amount) %>% sum()
-# is.na(Frontline$target_auc) %>% sum()
-
-# Frontline %>% filter(is.na(amount)) %>%
-#     distinct(patientid, .keep_all = TRUE) %>% nrow()
-# 
-# Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
-#     distinct(patientid, .keep_all = TRUE) %>% nrow()
-```
-<!-- If we remove patients who have at least 1 missing amount administered, we lose `r Frontline %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.   -->
-
-<!-- If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.
--->
-
-<br>
-<br>
-
-***
-
-# Clinical Analysis
-
-## 1.Clinical summary table
-
-<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
-```{r Table 1}
-Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(vital, raceeth, 
-           agecat, "ageatdx",
-
-           bmi_at_dx, bmi_cat, 
-           weight_at_dx, height_at_dx, bsa_at_dx,
-
-           histology1, "histology", "stagecat", imp_stagecat,
-
-           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
-           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown")) %>% 
-  tbl_summary() %>% bold_labels()
-```
-
-<span style="color:green">**Table 2 Summary demographic/clinical data by race**</span>
-```{r Table 2}
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "vital",
-           agecat, "ageatdx",
-
-           "bmi_at_dx", bmi_cat, "BSA",
-           "stagecat", imp_stagecat)) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-```
-<br>
-
-<span style="color:green">**Table 3 Summary demographic/clinical data by bmi**</span>
-```{r Table 3}
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth, "vital",
-           agecat, "ageatdx",
-
-           "bmi_at_dx", bmi_cat, "BSA",
-           "stagecat", imp_stagecat)) %>% 
-  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-```
-<br>
-
-## 2.Clinical Plots
-<div class = "row">
-<div class = "col-md-6">
-```{r plot clinical}
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= bmi_cat))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "BMI Category at Diagnosis")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= histology))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Histology")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= stagecat))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Stage")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= imp_stagecat))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Stage")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= agecat))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Age Category")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= brca_germline))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "BRCA gernline")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= brca_tumor))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "BRCA tumor")+
-  coord_flip()
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = bmi_cat))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "BMI category at Diagnosis")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = histology))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Histology")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = stagecat))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Stage")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = imp_stagecat))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Stage")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = agecat))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Age Category")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = brca_germline))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "BRCA germline")+
-  coord_flip()
-
-Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  ggplot(aes(x= raceeth, fill = brca_tumor))+
-  geom_bar(position = "fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "BRCA tumor")+
-  coord_flip()
-```
-</div>
-</div>
-
-<br>
-
-## 3.Survivals by clinical
-
-<span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the right**</span>
-
-<div class = "row">
-<div class = "col-md-6">
-```{r clinical from dx, fig.height = 7}
-# OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ raceeth, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by tstage
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ stagecat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_stagecat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ bmi_cat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-
-<div class = "col-md-6">
-```{r clinical from first treatment, fig.height = 7}
-# OS by raceeth
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ raceeth, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by tstage
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ stagecat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_stagecat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-
-# OS by bmi_cat
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ bmi_cat, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 2))
-```
-</div>
-</div>
-
-<br>
-<br>
-
-***
-
-<br>
-
-# II.Treatment Analysis
-
-## 1.Treatment summary table
-
-<span style="color:green">**Table 4 Summary treatment data by race**</span>
-```{r Table 4}
-# tbl1 <- 
-  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(raceeth,
-           "debulking", imp_debulking , "therapy"
-           )) %>% 
-  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-```
-<br>
-
-<span style="color:green">**Table 5 Summary treatment data by bmi**</span>
-```{r Table 5}
-Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-  select(c(bmi_cat,
-           "debulking", imp_debulking, "therapy"
-           )) %>% 
-  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
-```
-
-<span style="color:green">**Table  Summary of the expected, actual dose, and RDI**</span>
-```{r Summary of the expected, actual dose, and RDI}
-rdi_study <- 
-  RDI_data %>% 
-  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
-  arrange(patientid, episodedate, drugname) %>% 
-  mutate(chemotherapy_type = factor(chemotherapy_type))
-
-tbl1 <- rdi_study %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>% 
-  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity, chemotherapy_type) %>% 
-  tbl_summary(by = chemotherapy_type) %>% bold_labels()
-
-tbl2 <- rdi_study %>% filter(drugname == "paclitaxel" & therapy == "Upfront Chemo") %>% 
-  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity, chemotherapy_type) %>% 
-  tbl_summary(by = chemotherapy_type) %>% bold_labels()
-
-tbl_stack(list(tbl1, tbl2),
-          group_header = c(
-                           "Carboplatin Upfront Chemo", 
-                           "Paclitaxel Upfront Chemo"),
-          quiet = TRUE)
-
-tbl1 <- rdi_study %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>% 
-  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity) %>% 
-  tbl_summary() %>% bold_labels()
-
-tbl2 <- rdi_study %>% filter(drugname == "paclitaxel" & therapy == "Upfront Surgery") %>% 
-  select(target_auc, expected_dose, "dose received" = amount,  "RDI" = relative_dose_intensity) %>% 
-  tbl_summary() %>% bold_labels()
-
-tbl_stack(list(tbl1, tbl2),
-          group_header = c(
-                           "Carboplatin Upfront Surgery", 
-                           "Paclitaxel Upfront Surgery"),
-          quiet = TRUE)
-
-# rdi_study %>% filter(drugname == "paclitaxel" & is_dose_dense == 1) %>% 
-#   select(target_auc, expected_dose, amount,  relative_dose_intensity, therapy) %>% 
-#   tbl_summary(by = therapy) %>% bold_labels()
-
-```
-<br>
-
-## 2.Treatment Plots
-<div class = "row">
-<div class = "col-md-6">
-```{r treatment plots}
-Frontline %>%
-  ggplot(aes(x= therapy))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= bmi_cat, fill= therapy))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= bmi_cat, fill= debulking))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= bmi_cat, fill= imp_debulking))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(linenumber_adj == 1) %>% 
-  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
-  ggplot(aes(x= linename, fill= therapy))+
-  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
-  theme_minimal(base_size = 14) + 
-  facet_wrap(. ~ chemotherapy_type)+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(linenumber_adj == 1) %>% 
-  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
-  ggplot(aes(x= linename, fill= therapy))+
-  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
-  theme_minimal(base_size = 14) + 
-  facet_wrap(raceeth ~ chemotherapy_type)+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename) %>% 
-  tbl_summary(label = list(linename ~ "line name received as Neoadujant"))
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
-  select(linename, therapy) %>% 
-  tbl_summary(by = therapy,
-              label = list(linename ~ "line name received as Adjuvant"))
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-Frontline %>%
-  ggplot(aes(x= raceeth, fill= therapy))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= debulking))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= imp_debulking))+
-  geom_bar()+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= raceeth, fill= debulking))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-Frontline %>%
-  ggplot(aes(x= raceeth, fill= imp_debulking))+
-  geom_bar(position ="fill")+
-  theme_minimal(base_size = 14)+
-  labs(title = "Frontline treatment")+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(linenumber_adj == 1) %>% 
-  distinct(patientid, chemotherapy_type, .keep_all = TRUE) %>% 
-  ggplot(aes(x= linename, fill= therapy))+
-  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
-  theme_minimal(base_size = 14) + 
-  facet_wrap(bmi_cat ~ chemotherapy_type)+
-  coord_flip()
-
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
-  group_by(patientid, drugname) %>% 
-  summarise(CrCl = mean(CrCl),
-            target_auc = mean(target_auc),
-            expected_dose = mean(expected_dose)) %>% 
-  ungroup() %>% 
-  distinct(patientid, drugname, .keep_all = TRUE) %>% 
-  select(CrCl, target_auc, expected_dose, drugname) %>% 
-  tbl_summary(by = drugname,
-              label = list(CrCl ~ "Average CrCl during Neoadujant setting",
-                           target_auc ~ "Target dose (AUC or mg/mg2)",
-                           expected_dose ~ "Expected dose")
+  select(BSA, bsa_du_bois)
+head(a)
+mat <- cor(a, use = "pairwise.complete.obs")
+ggcorrplot(mat, hc.order = TRUE, method = "square",
+           insig = "blank", # Leave blank on no significant coefficient
+           type = "lower",
+           lab = TRUE,
+           title = "Correlation",
+           show.legend = TRUE, legend.title = "Correlation", show.diag = TRUE,
+           lab_col = "darkblue", lab_size = 3,
+           sig.level = 0.05, #insig = c("pch", "blank"), pch = 4, pch.col = "black", pch.cex = 10,
+           tl.cex = 10,
+           tl.srt = 90,
+           # digits = 1,
+           outline.color = "white",
+  ggtheme = ggplot2::theme_gray,
+  colors = c("blue", "white", "#E46726")
 )
-```
-</div>
-</div>
-
-<br>
-
-## 3.Survivals by treatment
-
-<div class = "row">
-<div class = "col-md-6">
-```{r treatment survival, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ 1, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ debulking, data=Frontline %>%
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_debulking, data=Frontline %>%
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ therapy, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of diagnosis", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ 1, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ debulking, data=Frontline %>%
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_debulking, data=Frontline %>%
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-# OS by therapy
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ therapy, data=Frontline %>% 
-                     distinct(patientid, .keep_all = TRUE)),
-           title = "OS from date of from first treatment", 
-           font.main = c(24, "bold", "black"), 
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
-           size = 1.5,
-
-           pval=TRUE, 
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"), 
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)" 
-) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
-</div>
-
-<br>
-<br>
-
-***
-
-<br>
-
-# III.RDI
-RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.
-
-```{r echo=TRUE}
-# RDI_grp = case_when(
-#     mean_RDI_per_drug >= 0.85              ~ "adequate",
-#     mean_RDI_per_drug < 0.85               ~ "underdose"
-#   ))
-```
-Start with plotting :
-
-## 1.Plots RDI
-
-<div class = "row">
-<div class = "col-md-6">
-```{r rdi plots, fig.height=10, fig.height=9}
-Frontline %>% 
-  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
-  filter(!is.na(value)) %>% 
-  ggplot(aes(x= name))+
-  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
-  theme_minimal(base_size = 14)+
-  coord_flip()
-
-Frontline %>% 
-  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
-  filter(!is.na(value)) %>% 
-  ggplot(aes(x= name, y= value))+
-  geom_boxplot()+
-  # ylim(c(-.25, 3.5))+
-  geom_jitter(shape=16)+
-  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
-  theme_minimal(base_size = 14)+
-  coord_flip()+
-  facet_wrap(.~ therapy, ncol = 2)
-```
-</div>
-
-<div class = "col-md-6">
-```{r, fig.height=10, fig.height=9}
-# Frontline %>%
-#   select(patientid, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj,
-#          RDI_carbo_neo_grp, RDI_pacli_neo_grp, RDI_carbo_adj_grp, RDI_pacli_adj_grp) %>%
-#   pivot_longer(cols = -patientid, names_to = c("RDI", "group"), names_prefix = "_grp")
-#   filter(!is.na(value)) %>%
-#   ggplot(aes(x= name))+
-#   geom_bar(aes(fill = therapy, alpha = RDI_grp), position = position_dodge(preserve = "single"))+
-#   theme_minimal(base_size = 14)+
-# coord_flip()
-# 
-Frontline %>% 
-  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
-  filter(!is.na(value)) %>% 
-  ggplot(aes(x= name, y= value, color= value < 0.85))+
-  geom_boxplot()+
-  geom_jitter(shape=16)+
-  labs(x = "", caption = "Warning 1 dot = RDI for 1 patient") +
-  theme_minimal(base_size = 14)+
-  coord_flip()+
-  facet_wrap(.~ therapy, ncol = 2)
-```
-</div>
-</div>
-
-```{r}
-# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
-#   ggplot(aes(x= drugname, fill = RDI_grp))+
-#   geom_bar(position = "fill")+
-#   theme_minimal(base_size = 14)+
-#   facet_wrap(.~ therapy)+
-#   coord_flip()
-```
-
-### By Population
-```{r, fig.width=12, fig.height=20}
-Frontline %>% 
-  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
-  filter(!is.na(value)) %>% 
-  ggplot(aes(x= raceeth))+
-  geom_bar(aes(fill = therapy), position = position_dodge(preserve = "single"))+
-  theme_minimal(base_size = 14)+
-  coord_flip()+
-  facet_wrap(name ~ ., ncol = 1, scales = "free")
-```
-
-```{r ggridges, fig.width=16, fig.height=18}
-library(ggridges)
-Frontline %>% 
-  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
-  filter(!is.na(value)) %>% 
-  ggplot(aes(y=raceeth, x=value,  fill=raceeth
-             )) +
-    geom_density_ridges(alpha=0.5) +
-    theme_ridges()+
-  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
-        panel.spacing = unit(0.1, "lines"),
-        strip.text.x = element_text(size = 14)
-    ) +
-  geom_vline(xintercept = 1, color = "red", linetype = 2)+
-  geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+
-
-  facet_wrap(therapy ~ name, ncol = 2, scales = "free_x")
-
-Frontline %>% 
-  pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
-  filter(!is.na(value)) %>% 
-  ggplot(aes(y=bmi_cat, x=value,  fill=bmi_cat
-             )) +
-    geom_density_ridges(alpha=0.5) +
-    theme_ridges()+
-  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
-        panel.spacing = unit(0.1, "lines"),
-        strip.text.x = element_text(size = 14)
-    ) +
-  geom_vline(xintercept = 1, color = "red", linetype = 2)+
-  geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+
-
-  facet_wrap(therapy ~ name, ncol = 2, scales = "free_x")
-```
-
-## 2.RDI summary table
-
-<span style="color:green">**Table 6: RDI summary table**</span>
-
-```{r}
-my_theme <-
-  list(
-    # Some gt customization
-    "as_gt-lst:addl_cmds" = list(
-      # make the font size small
-      tab_spanner = rlang::expr(gt::tab_options(row.striping.background_color = "lightgrey",
-                                                row.striping.include_stub = TRUE,
-                                                row.striping.include_table_body = TRUE,
-                                                row_group.border.top.color = "blue",
-                                                # table.background.color = "white", 
-                                                heading.background.color = "lightblue", 
-                                                # column_labels.background.color = "orange", 
-                                                row_group.background.color = "grey",
-                                                stub.background.color = "slateblue", 
-                                                summary_row.background.color = "tomato", 
-                                                grand_summary_row.background.color = "green")),
-      # add a custom title and subtitle to every table
-      # user_added1 = rlang::expr(gt::tab_header(
-      #   title = "Christelle's Table", subtitle = "Yeap"))#,
-      # add a custom data source note
-      # user_added2 = rlang::expr(gt::tab_source_note(
-      #   source_note = "Source: our data!"))#,
-      # stripe the table rows
-      user_added1 = rlang::expr(gt::opt_row_striping())#,
-      # user_added4 = rlang::expr(gt::opt_table_lines("none"))
-      )
-    )
-
-reset_gtsummary_theme()
-set_gtsummary_theme(my_theme)
-
-# trial %>%
-#   select(age, grade, trt) %>%
-#   tbl_summary(by = trt) %>%
-#   add_stat_label() %>%
-#   add_p() %>%
-#   as_gt() 
-```
-
-```{r Table summary Platin}
-# Treatment & demo
-tbl1 <- Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI (continous)" = RDI_carbo_neo, "RDI (categorical)" = RDI_carbo_neo_grp, therapy)) %>%
-  tbl_summary(by = therapy) %>% 
-  bold_labels() %>% add_n() %>% add_overall()
-
-tbl2 <- Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI (continous)" = RDI_carbo_adj, "RDI (categorical)" = RDI_carbo_adj_grp, therapy)) %>%
-  tbl_summary(by = therapy) %>%
-  bold_labels() %>% add_n() %>% add_overall()
-
-tbl3 <- Frontline %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
-  tbl_summary(by = therapy
-              ) %>%
-  bold_labels() %>% add_n() %>% add_overall()
-
-tbl4 <- Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
-  tbl_summary(by = therapy
-              ) %>%
-  bold_labels() %>% add_n() %>% add_overall()
-tbl5 <- Frontline %>% filter(dose_dense == 3) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
-  tbl_summary(by = therapy,
-              type = list(`RDI (continous)` ~ "continuous")) %>%
-  bold_labels() %>% add_n() %>% add_overall()
-tbl6 <- Frontline %>% filter(dose_dense == 3) %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
-  tbl_summary(by = therapy,
-              type = list(`RDI (continous)` ~ "continuous")) %>%
-  bold_labels() %>% add_n() %>% add_overall()
-
-# tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
-#   modify_spanning_header(everything() ~ NA_character_)
-tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6),
-          group_header = c(
-                           "Carboplatin Neo", 
-                           "Carboplatin Adj",
-                           "Paclitaxel overall Neo",
-                           "Paclitaxel overall Adj",
-                           "Paclitaxel dose dense Neo",
-                           "Paclitaxel dose dense Adj"),
-          quiet = TRUE)
-```
-
-```{r}
-# reset_gtsummary_theme()
-```
-
-```{r Table summary Taxanes}
-# tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(RDI_carbo_neo, RDI_carbo_neo_grp, therapy)) %>%
-#   tbl_summary(by = therapy) %>% 
-#   bold_labels()
-# 
-# tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(RDI_carbo_adj, RDI_carbo_adj_grp, therapy)) %>%
-#   tbl_summary(by = therapy) %>%
-#   bold_labels()
-# tbl4 <- tbl_stack(list(tbl1, tbl2),
-#           group_header = c(
-#                            "paclitaxel Neo/Upfront Chemo",
-#                            "paclitaxel Adj/Upfront Chemo"),
-#           quiet = TRUE)
-# 
-# 
-# tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c(RDI_carbo_adj, RDI_carbo_adj_grp, therapy)) %>%
-#   tbl_summary(by = therapy) %>%
-#   bold_labels()
-# tbl_merge(list(tbl4, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))
-
-####
-# tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo" &
-#                                dose_dense == 3) %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
-#   tbl_summary() %>%
-#   bold_labels()
-
-# tbl5 <- Frontline %>% filter(therapy == "Upfront Chemo" &
-#                                dose_dense == 3) %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
-#   tbl_summary() %>%
-#   bold_labels()
-# tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery" &
-#                                dose_dense == 3) %>%
-#   distinct(patientid, .keep_all = TRUE) %>%
-#   select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
-#   tbl_summary(
-#               type = list(RDI ~ "continuous")) %>%
-#   bold_labels()
-
-# tbl8 <- tbl_merge(list(tbl2, tbl4))
-# tbl9 <- tbl_merge(list(tbl3, tbl6), tab_spanner = c("Overall", "Dose dense 1+3"))
-
-# tbl_stack(list(tbl1, tbl2, tbl3, tbl6),
-#           group_header = c(
-#                            "paclitaxel Neo/Upfront Chemo", 
-#                            "paclitaxel Adj/Upfront Chemo",
-#                            "paclitaxel Adj/Upfront Surgery",
-#                            "dose dense paclitaxel Adj/Upfront Surgery"),
-#           quiet = TRUE)
-```
-<br>
-
-<span style="color:green">**Table 7: Summary RDI data by race and bmi**</span>  
-Removing the overall on the right side? Or do you want the tables separated?
-Platin  
-```{r Table 7 Summary RDI data by race and bmi}
-tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
-  tbl_summary(by = raceeth) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
-  tbl_summary(by = bmi_cat) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-
-tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
-  tbl_summary(by = raceeth) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
-  tbl_summary(by = bmi_cat) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-
-tbl7 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-tbl8 <-
-  tbl_merge(list(tbl3, tbl4))
-tbl_stack(list(tbl7, tbl8),
-          group_header = c(
-                           "carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo"),
-          quiet = TRUE)
-
-tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
-  tbl_summary(by = raceeth) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
-  tbl_summary(by = bmi_cat) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-
-# tbl9 <-
-  tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
-  modify_caption("**Upfront Surgery**")
-```
-<br>
-
-Taxanes
-```{r Table4 summary Taxanes}
-tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
-  tbl_summary(by = raceeth) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
-  tbl_summary(by = bmi_cat) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-
-tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
-  tbl_summary(by = raceeth) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
-  tbl_summary(by = bmi_cat) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-tbl7 <-
-  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
-tbl8 <-
-  tbl_merge(list(tbl3, tbl4))
-tbl_stack(list(tbl7, tbl8),
-          group_header = c(
-                           "paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo"),
-          quiet = TRUE)
-tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
-  tbl_summary(by = raceeth) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
-  distinct(patientid, .keep_all = TRUE) %>%
-  select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
-  tbl_summary(by = bmi_cat) %>%
-  bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-
-tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
-  modify_caption("**Upfront Surgery**")
-```
-<br>
-<br>
-
-***
-
-<br>
-
-## 3.Survivals by RDI
-
-### Survivals RDI by chemotherapy type
-<div class = "row">
-<div class = "col-md-6">
-```{r OS dx RDI, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_neo_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis carboplatin \nUpfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis carboplatin \nUpfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis carboplatin \nUpfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_neo_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis paclitaxel \nUpfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_adj_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis paclitaxel \nUpfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_adj_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis paclitaxel \nUpfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
-
-<div class = "col-md-6">
-```{r OS treatment RDI, fig.height = 7}
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis carboplatin \nUpfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis carboplatin \nUpfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis carboplatin \nUpfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_neo_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis paclitaxel \nUpfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_adj_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Chemo") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis paclitaxel \nUpfront Chemo",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-
-ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_adj_grp, 
-                   data=Frontline %>% 
-                     filter(therapy == "Upfront Surgery") %>%
-                     distinct(patientid, .keep_all = TRUE)
-                   ),
-           title = "OS from diagnosis paclitaxel \nUpfront Surgery",
-           font.main = c(24, "bold", "black"),
-           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-           size = 1.5,
-
-           pval=TRUE,
-           # legend.labs=c(""),
-           # palette = c("black", "green","blue", "red"),
-           # Add risk table
-           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-           tables.theme = theme_survminer(base_size = 5,
-                                          font.main = c(16, "bold", "black"),
-                                          font.x = c(16, "bold", "black"),
-                                          font.y = c(16, "bold", "transparent"),
-                                          font.tickslab = c(19, "bold", "black")
-           ),
-
-           legend.title = "", xlab = "Time (in months)"
-) + guides(colour = guide_legend(ncol = 1))
-```
-</div>
-</div>
-
-<br>
-<br>
-
-***
-
-# IV.Hazard Ratio
-
-<span style="color:green">**Table 8 HR Univariable**</span>
-
-## Univariable and drug only adjusted analysis
-```{r Table 6 HR}
-# tbl2 <- Frontline %>%
-#   filter(therapy == "Upfront Chemo")
-# tbl1 <- tbl2 %>%
-#   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
-#   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% 
-#   add_
-# tbl2 <- tbl2 %>%
-#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
-#   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-# 
-# 
-# tbl3 <- Frontline %>%
-#   filter(therapy == "Upfront Surgery")
-# tbl3 <- tbl3 %>%
-#   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
-#   tbl_uvregression(method = survival::coxph,
-#                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
-#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-# tbl5 <- tbl_merge(list(tbl2, tbl3))
-# 
-# # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
-# #   modify_spanning_header(everything() ~ NA_character_)
-# 
-# tbl_stack(list(tbl1, tbl5)) %>%
-#   bold_labels() %>%
-#   italicize_levels()
-
-  # trial %>%
-  # select(age, grade, stage, trt) %>%
-  # mutate(grade = paste("Grade", grade)) %>%
-  # # tbl_strata(
-  # #   strata = grade,
-  # #   .tbl_fun =
-  # #     ~ .x %>%
-  #       tbl_summary(by = trt, missing = "no") %>%
-  #       add_n()
-  # )
-```
-
-<div class = "row">
-<div class = "col-md-6">
-```{r Table 61 HR}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- tbl2 %>%
-  select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- tbl2 %>%
-  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- tbl3 %>%
-  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- tbl2 %>%
-  select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- tbl2 %>%
-  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- tbl3 %>%
-  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel/Upfront Chemo", 
-                           "paclitaxel/Upfront Chemo",
-                           "paclitaxel/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <-
-  coxph(Surv(time = tbl2$month_at_os_from_treatment,
-             event = tbl2$vital_status
-             ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,
-        data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status
-             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp,
-        data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-</div>
-</div>
-
-<br>
-<br>
-
-## Multivariable
-### RDI group
-<span style="color:green">**Table 9 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
-```{r Table 5 HR adjusted rdi group}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-### Continous
-<span style="color:green">**Table 10 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
-```{r rdi continous}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
-<!-- RDI for paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-## Adjusted by other drug
-### RDI group
-<span style="color:green">**Table 11 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
-```{r Table 5 HR adjusted rdi group adjusted by other drug}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status
-           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, 
-      data =  tbl2)  %>% 
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status
-           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  
-        tbl3) %>%
-  cox.zph()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
--->
-
-<br>
-<br>
-
-### Continous
-<span style="color:green">**Table 12 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
-```{r rdi continous adjusted by other drug}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H c}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  cox.zph()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- Continuous RDI for carboplatin or paclitaxel are not factors associated with survival. -->
-
-<br>
-<br>
-
-***
-
-<br>
-
-<!-- # V.More precise RDI -->
-
-<!-- As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed -->
-
-<!-- ```{r echo=TRUE} -->
-<!-- # Highly underdosed: < 0.75 -->
-<!-- # Underdosed: >= 0.75 to <0.85 -->
-<!-- # Adequate dosing: >= 0.85 to <1.10 -->
-<!-- # Overdosing: >=1.10 -->
-<!-- ``` -->
-<!-- Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI) -->
-<!-- ```{r, fig.width=12, fig.height=12} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
-<!--   geom_point(alpha = 0.7, size = 0.75)+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
-<!--   geom_jitter()+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
-
-<!-- ``` -->
-<!-- Here I just wanted to see if we have more or less underdosing / overdosing with BMI -->
-<!-- ```{r, fig.width=12, fig.height=12} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   ggplot(aes(x= RDI_grp1, fill = drugname))+ -->
-<!--   geom_bar(position = position_dodge())+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   facet_wrap(. ~ therapy, ncol = 2, scales = "free")+ -->
-<!--   coord_flip() -->
-<!-- ``` -->
-
-<!-- ```{r, fig.width=12} -->
-<!-- # Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!-- #   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
-<!-- #   geom_bar(position = position_dodge())+ -->
-<!-- #   theme_minimal(base_size = 10)+ -->
-<!-- #   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+ -->
-<!-- #   coord_flip() -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   # filter(linenumber_new == "1") %>% -->
-<!--   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
-<!--   geom_bar(position = "fill")+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   coord_flip()+ -->
-<!--   facet_wrap(.~ therapy) -->
-<!-- ``` -->
-<!-- As you can see above in green, we have a lot of patient who are overdose. -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- ## Hazard Ratio RDI 2 -->
-
-<!-- <span style="color:green">**Table HR**</span> -->
-
-<!-- ### Univariable -->
-<!-- ```{r HR RDI 2} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel/Upfront Chemo",  -->
-<!--                            "paclitaxel/Upfront Chemo", -->
-<!--                            "paclitaxel/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference. -->
-
-<!-- ### Multivariable -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_grp1 + raceeth + ageatdx + stagecat` -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!--                            "paclitaxel Adj/Upfront Chemo", -->
-<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- ## Adjusted by other drug -->
-<!-- ### RDI group -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` -->
-<!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug 2} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- *** -->
-
-<!-- # VI. Adjusted by **BMI at DX category** -->
-
-<!-- ```{r} -->
-<!-- Frontline_bmi <- Frontline %>% -->
-<!--   filter(!is.na(bmi_cat)) -->
-<!-- ``` -->
-
-<!-- ## Multivariable -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` -->
-<!-- ```{r bmi HR adjusted} -->
-<!-- # Carbo -->
-<!-- # tbl1 <- Frontline_bmi %>% -->
-<!-- #   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") -->
-<!-- # tbl1 <- -->
-<!-- #   coxph(Surv(time = tbl1$month_at_os_from_treatment, -->
-<!-- #              event = tbl1$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
-
-<!-- tbl2 <- Frontline_bmi %>% -->
-<!--   filter(drugname == "carboplatin" & therapy == "Upfront Surgery") -->
-<!-- tbl2 <- -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
-<!--              event = tbl2$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline_bmi %>% -->
-<!--   filter(drugname == "carboplatin" & therapy == "Upfront Chemo") -->
-<!-- tbl3 <- -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
-<!--              event = tbl3$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-<!-- # tbl7 <- Frontline_bmi %>% -->
-<!-- #   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant") -->
-<!-- # tbl7 <- -->
-<!-- #   coxph(Surv(time = tbl7$month_at_os_from_treatment, -->
-<!-- #              event = tbl7$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
-<!-- tbl8 <- Frontline_bmi %>% -->
-<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Surgery") -->
-<!-- tbl8 <- -->
-<!--   coxph(Surv(time = tbl8$month_at_os_from_treatment, -->
-<!--              event = tbl8$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl9 <- Frontline_bmi %>% -->
-<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Chemo") -->
-<!-- tbl9 <- -->
-<!--   coxph(Surv(time = tbl9$month_at_os_from_treatment, -->
-<!--              event = tbl9$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl8, tbl9), -->
-<!--           group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-# Complete case HR analysis
-
-```{r}
-Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
-  mutate(comp_cases = case_when(
-    is.na(stagecat) |
-      is.na(debulking)                     ~ "excluded",
-    TRUE                                   ~ "complete cases"
-  )) %>% 
-  select(c(vital, raceeth, 
-           agecat, "ageatdx",
-
-           bmi_at_dx, bmi_cat, 
-           weight_at_dx, height_at_dx, bsa_at_dx,
-
-           histology1, "histology", "stagecat", imp_stagecat,
-
-           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
-           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown",
-           comp_cases)) %>% 
-  tbl_summary(by = comp_cases) %>% 
-  bold_labels() %>% add_p() %>% bold_p()
-```
-<br>
-
-## Univariable and drug only adjusted analysis
-
-<span style="color:green">**Table  HR Univariable**</span>
-
-<div class = "row">
-<div class = "col-md-6">
-```{r Table  HR}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking))
-tbl1 <- tbl2 %>%
-  select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- tbl2 %>%
-  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking))
-tbl3 <- tbl3 %>%
-  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking))
-tbl1 <- tbl2 %>%
-  select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- tbl2 %>%
-  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking))
-tbl3 <- tbl3 %>%
-  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
-  tbl_uvregression(method = survival::coxph,
-                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)),
-                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel/Upfront Chemo", 
-                           "paclitaxel/Upfront Chemo",
-                           "paclitaxel/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-</div>
-
-<div class = "col-md-6">
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking))
-tbl21 <-
-  coxph(Surv(time = tbl2$month_at_os_from_treatment,
-             event = tbl2$vital_status
-             ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,
-        data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking))
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status
-             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp,
-        data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-</div>
-</div>
-
-<br>
-<br>
-
-## Multivariable
-### RDI group
-<span style="color:green">**Table 9 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology + debulking` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- In multivariable analysis, categorical RDI for carboplatin or paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-### Continous
-<span style="color:green">**Table 10 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology + debulking` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- In multivariable analysis, a higher RDI for carboplatin shows a worse survival (p<0.001) in an Adjuvant / Upfront Chemo setting as seen in the univariable analysis.   -->
-<!-- RDI for paclitaxel is not a factor associated with survival. -->
-
-<br>
-<br>
-
-## Adjusted by other drug
-### RDI group
-<span style="color:green">**Table 11 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status
-             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
-        data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% 
-  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H complete case}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status
-           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, 
-      data =  tbl2)  %>% 
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status
-           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
-      data =  tbl3) %>%
-  cox.zph()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<!-- When adjusting by each drugs, we observe a 61% increased risk of death for a underdosing of carboplatin in the Neoadjuvant / Upfront Chemo setting (p=0.059) and a 32% increased risk of death for a underdosing of paclitaxel in the Adjuvant / Upfront Surgery setting (p=0.059).
--->
-
-<br>
-<br>
-
-### Continous
-<span style="color:green">**Table 12 HR Multivariable**</span>
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking` 
-```{r }
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H complete case c}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>% 
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  cox.zph()
-```
-
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
-```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<br>
-<br>
-
-***
-
-```{r echo=FALSE, out.width='30%'}
-knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
-```
+# mat <- matrix(c(1,2,3), nrow = 1, ncol = 3, byrow = TRUE,
+#                dimnames = list(c("row1"),
+#                                c("C.1", "C.2", "C.3")))
+# cor(mat)
+```

### 2022-02-02 Rmd/rdi analysis including chemo patients.Rmd
Start new analyses / Chemo only patients inclusion

--- 2022-01-06 Rmd/rdi analysis.Rmd
@@
     chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
-    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
+    chemotherapy_type == "Chemotherapy only" |
+      treatment_sequence == "neo + surg"         ~ "Did not receive Adjuvant",
     chemotherapy_type == "Surgery only"          ~ "Surgery only",
-    is.na(had_neo) &
-      had_adj == "Yes"                           ~ "Upfront Surgery"
+    treatment_sequence == "surg + adj"           ~ "Upfront Surgery"
   )) %>% 

### 2022-02-04 R/02.data cleaning.R
Update and clean code

@@ -1,0 +1,427 @@
+#################################################################################################### I ### Clinical Cleaning----
+############# 1 ### Cleanup of creatinine----
+creatinine <- creatinine %>%
+  # remove creatine urine
+  filter(str_detect(labcomponent, "blood|serum")) %>% 
+  mutate(creatinine = case_when(
+    testresultcleaned < 0.7                   ~ 0.7,
+    testresultcleaned > 3                     ~ NA_real_, # F006DBE0C7A5E is an example of slow increase past 3, F641A8DC820C7 super high
+    TRUE                                      ~ testresultcleaned
+  )) %>% 
+  mutate(testresult = str_remove(testresult, "<"),
+         testresult = as.numeric(testresult)) %>% 
+  # F092F8B827DDC kept umol/L as they actually are mg/dL range 45 to 90 μmol/L (0.5 to 1.0 mg/dL) for women.
+  mutate(creatinine1 = case_when(
+    testresult < 0.7                          ~ 0.7,
+    testresult > 3                            ~ NA_real_,
+    TRUE                                      ~ testresult
+  )) %>% 
+  mutate(creatinine = coalesce(creatinine, creatinine1)) %>% 
+  filter(!is.na(creatinine)) %>% 
+  mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
+  # Bind to clinical to calculate value closest to dx
+  left_join(., clinical_data %>% 
+              select(patientid, diagnosisdate), 
+            by = "patientid") %>% 
+  mutate(interval = abs(interval(start= testdate, end= diagnosisdate)/
+                          duration(n=1, unit="days"))) %>%
+  group_by(patientid) %>% 
+  mutate(interval_creat_x = min(interval)) %>% 
+  mutate(creatinine_at_dx = case_when(
+    interval == interval_creat_x          ~ creatinine
+  )) %>% 
+  fill(creatinine_at_dx, .direction = "updown") %>% 
+  select(c(patientid, creat_date = "testdate", creatinine, 
+           creat_units = "testunitscleaned", creatinine_at_dx))
+write_rds(creatinine, "creatinine.rds")
+
+
+############# 2 ### body_surface_area, height and weight prep----
+vitals <- vitals %>% 
+  select(-c(test, testbasename, resultdate, minnorm, maxnorm, minnormcleaned, maxnormcleaned))
+
+
+############# 3 ### Cleanup of BSA----
[…]

### 2022-02-04 R/2.data cleaning.R

@@ -1,1071 +1,0 @@
-#################################################################################################### I ### Basic Clinical Cleaning----
-#################################################################################################### 1 ### Cleanup of creatinine----
-creatinine <- creatinine %>%
-  # remove creatine urine
-  filter(str_detect(labcomponent, "blood|serum")) %>% 
-  mutate(creatinine = case_when(
-    testresultcleaned < 0.7        ~ 0.7,
-    testresultcleaned > 3          ~ NA_real_, # F006DBE0C7A5E is an example of slow increase past 3, F641A8DC820C7 super high
-    TRUE                           ~ testresultcleaned
-  )) %>% 
-  mutate(testresult = str_remove(testresult, "<"),
-         testresult = as.numeric(testresult)) %>% 
-  # F092F8B827DDC kept umol/L as they actually are mg/dL range 45 to 90 μmol/L (0.5 to 1.0 mg/dL) for women.
-  mutate(creatinine1 = case_when(
-    testresult < 0.7               ~ 0.7,
-    testresult > 3                 ~ NA_real_,
-    TRUE                           ~ testresult
-  )) %>% 
-  mutate(creatinine = coalesce(creatinine, creatinine1)) %>% 
-  filter(!is.na(creatinine)) %>% 
-  mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
-  left_join(., clinical_data %>% 
-              select(patientid, diagnosisdate), 
-            by = "patientid") %>% 
-  mutate(interval = abs(interval(start= testdate, end= diagnosisdate)/
-                          duration(n=1, unit="days"))) %>%
-  group_by(patientid) %>% 
-  mutate(interval_creat_x = min(interval)) %>% 
-  mutate(creatinine_at_dx = case_when(
-    interval == interval_creat_x          ~ creatinine
-  )) %>% 
-  fill(creatinine_at_dx, .direction = "updown") %>% 
-  select(c(patientid, creat_date = "testdate", creatinine, 
-           creat_units = "testunitscleaned", creatinine_at_dx, interval_creat_x))
-write_rds(creatinine, "creatinine.rds")
-
-
-# body_surface_area, height and weight are all coming from vitals
-vitals <- vitals %>% 
-  # mutate(testdate = as.Date(testdate, format = "%m/%d/%y")) %>% 
-  select(-c(test, testbasename, resultdate, minnorm, maxnorm, minnormcleaned, maxnormcleaned))
-
-
[…]

### 2022-02-04 R/temp questions.R

@@ -1,10 +1,0 @@
-# How many patients had the last Neoadj cycle switch to Adjuvant?
-
-a <- therapy %>% filter(!is.na(surgerydate) & chemotherapy_type == "Adjuvant" & linenumber == 1 & linenumber_new == 2 & therapy == "Upfront Chemo") %>% 
-  distinct(patientid)
-
-# Patients who switch between cisplatin to carbo
-
-a <- therapy %>% filter((str_detect(linename, "Cis") & drugname == "carboplatin")) %>% distinct(patientid)
-
-b <- therapy %>% filter((str_detect(linename, "Carbo") & drugname == "cisplatin")) %>% distinct(patientid)

### 2022-02-04 Rmd/rdi analysis including chemo patients.Rmd
Update rmd and fix bug

--- 2022-01-06 Rmd/rdi analysis.Rmd
@@
     is.na(surgerydate) &
-      !is.na(episodedate)             ~ "Chemotherapy only",
+      !is.na(episodedate)             ~ "Neoadjuvant",
     !is.na(surgerydate) &
@@
            factor(chemotherapy_type, levels = 
-                    c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
+                    c("Neoadjuvant", "Adjuvant", "Surgery only"))) %>%
   group_by(patientid) %>% 
@@
     had_neo == "Yes" &
-      is.na(had_adj)                             ~ "neo + surg",
+      is.na(had_adj)                             ~ "neo + surg or neo only",
     is.na(had_neo) &
       had_adj == "Yes"                           ~ "surg + adj",
-    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
     chemotherapy_type == "Surgery only"          ~ "Surgery only"
@@
   mutate(therapy = case_when(
+    treatment_sequence == "neo + surg or neo only"  ~ "Upfront Chemo",
     chemotherapy_type == "Neoadjuvant"              ~ "Upfront Chemo",
-    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
     chemotherapy_type == "Surgery only"             ~ "Surgery only",
-    is.na(had_neo) &
-      had_adj == "Yes"                           ~ "Upfront Surgery"
+    treatment_sequence == "surg + adj"              ~ "Upfront Surgery"
   )) %>% 
@@
       )                                          ~ interval_creat,
+    # therapy == "Did not receive Adjuvant" &
+    #   interval_creat < 31 &
+    #   (creat_date < surgerydate |
+    #      is.na(surgerydate))                     ~ interval_creat,
     TRUE                                         ~ NA_real_
@@
       )                                          ~ interval_weight,
+    # therapy == "Did not receive Adjuvant" &
+    #   interval_weight < 31 &
+    #   (weight_date < surgerydate |
+    #      is.na(surgerydate))                     ~ interval_weight,
     TRUE                                         ~ NA_real_
@@
       )                                          ~ interval_bsa,
+    # therapy == "Did not receive Adjuvant" &
+    #   interval_bsa < 31 &
+    #   (bsa_date < surgerydate |
+    #      is.na(surgerydate))                     ~ interval_bsa,
     TRUE                                         ~ NA_real_
@@
       )                                          ~ interval_auc,
+    # therapy == "Did not receive Adjuvant" &
+    #   interval_auc < 31 &
+    #   (auc_date < surgerydate |
+    #      is.na(surgerydate))                     ~ interval_auc,
     TRUE                                         ~ NA_real_
@@
   arrange(patientid, episodedate)
-
-Treatment1 %>% distinct(patientid) %>% nrow()
 ```
@@
   mutate(days_at_first_treatment = case_when(
-    therapy == "Upfront Chemo" |
-      therapy == "Chemotherapy only"             ~ interval(start = diagnosisdate, end = first_drug_date)/
+    therapy == "Upfront Chemo"                   ~ interval(start = diagnosisdate, end = first_drug_date)/
            duration(n=1, units = "days"),
@@
   mutate(neo_more_more_than_1line = case_when(
+    treatment_sequence == "neo + surg + adj" &
       chemotherapy_type == "Neoadjuvant" &
@@
     (linenumber_new == 1 &
-       therapy == "Upfront Chemo" &
+       treatment_sequence == "neo + surg + adj" &
        total_cycle_increment > 6) |
@@
       (linenumber_new == 2 &
-         therapy == "Upfront Chemo" &
+         treatment_sequence == "neo + surg + adj" &
          total_cycle_increment > 9) |
@@
          therapy == "Upfront Surgery" &
+         total_cycle_increment > 9) |
+
+      (linenumber_new == 1 &
+         treatment_sequence == "neo + surg or neo only" &
          total_cycle_increment > 9)                ~ "exclude"
@@
   # general
-  mutate(RDI_grp = case_when(
-    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
-    mean_RDI_per_drug < 0.85               ~ "Underdosed"
-  )) %>% 
-  mutate(RDI_grp = factor(RDI_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
-  mutate(RDI_grp1 = case_when(
-    mean_RDI_per_drug < 0.75               ~ "Highly underdosed",
-    mean_RDI_per_drug >= 0.75 &
-      mean_RDI_per_drug < 0.85             ~ "Underdosed",
-    mean_RDI_per_drug >= 0.85 &
-      mean_RDI_per_drug < 1.1              ~ "Adequate dosing",
-    mean_RDI_per_drug >= 1.1               ~ "Overdosing"
-  )) %>% 
-  mutate(RDI_grp1 = factor(RDI_grp1, 
-                          levels = c("Adequate dosing",
-                                     "Underdosed", 
-                                     "Highly underdosed",
-                                     "Overdosing"))) %>% 
+  # mutate(RDI_grp = case_when(
+  #   mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
+  #   mean_RDI_per_drug < 0.85               ~ "Underdosed"
+  # )) %>% 
+  # mutate(RDI_grp = factor(RDI_grp, 
+  #                          levels = c("Adequate dosing", "Underdosed"))) %>% 
+  # mutate(RDI_grp1 = case_when(
+  #   mean_RDI_per_drug < 0.75               ~ "Highly underdosed",
+  #   mean_RDI_per_drug >= 0.75 &
+  #     mean_RDI_per_drug < 0.85             ~ "Underdosed",
+  #   mean_RDI_per_drug >= 0.85 &
+  #     mean_RDI_per_drug < 1.1              ~ "Adequate dosing",
+  #   mean_RDI_per_drug >= 1.1               ~ "Overdosing"
+  # )) %>% 
+  # mutate(RDI_grp1 = factor(RDI_grp1, 
+  #                         levels = c("Adequate dosing",
+  #                                    "Underdosed", 
+  #                                    "Highly underdosed",
+  #                                    "Overdosing"))) %>% 
   # separated
@@
   )) %>%
+
+  # mutate(RDI_carbo_chem = case_when(
+  #   drugname == "carboplatin" &
+  #     therapy == "Did not receive Adjuvant"    ~ mean_RDI_per_drug,
+  #   TRUE                                    ~ NA_real_
+  # )) %>% 
+  # mutate(RDI_pacli_chem = case_when(
+  #   drugname == "paclitaxel" &
+  #     therapy == "Did not receive Adjuvant"    ~ mean_RDI_per_drug,
+  #   TRUE                                    ~ NA_real_
+  # )) %>%
+
+  # mutate(RDI_carbo_chem_grp = case_when(
+  #   RDI_carbo_chem >= 0.85              ~ "Adequate dosing",
+  #   RDI_carbo_chem < 0.85               ~ "Underdosed"
+  # )) %>% 
+  # mutate(RDI_carbo_chem_grp = factor(RDI_carbo_chem_grp, 
+  #                          levels = c("Adequate dosing", "Underdosed"))) %>%
+  # mutate(RDI_pacli_chem_grp = case_when(
+  #   RDI_pacli_chem >= 0.85              ~ "Adequate dosing",
+  #   RDI_pacli_chem < 0.85               ~ "Underdosed"
+  # )) %>% 
+  # mutate(RDI_pacli_chem_grp = factor(RDI_pacli_chem_grp, 
+  #                          levels = c("Adequate dosing", "Underdosed"))) %>%
 
@@
     RDI_carbo_adj >= 0.85              ~ "Adequate dosing",
-    RDI_carbo_adj < 0.85               ~ "Underdosed"
+    RDI_carbo_adj < 0.85               ~ "Underdosed",
+    is.na(RDI_carbo_adj) &
+      treatment_sequence == "neo + surg or neo only"     ~ "Did not receive adjuvant"
   )) %>% 
   mutate(RDI_carbo_adj_grp = factor(RDI_carbo_adj_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
+                           levels = c("Adequate dosing", "Underdosed", "Did not receive adjuvant"))) %>% 
   mutate(RDI_carbo_adj_grp1 = case_when(
@@
     RDI_pacli_adj >= 0.85              ~ "Adequate dosing",
-    RDI_pacli_adj < 0.85               ~ "Underdosed"
+    RDI_pacli_adj < 0.85               ~ "Underdosed",
+    is.na(RDI_pacli_adj) &
+      treatment_sequence == "neo + surg or neo only"     ~ "Did not receive adjuvant"
   )) %>% 
   mutate(RDI_pacli_adj_grp = factor(RDI_pacli_adj_grp, 
-                           levels = c("Adequate dosing", "Underdosed"))) %>% 
+                           levels = c("Adequate dosing", "Underdosed", "Did not receive adjuvant"))) %>% 
   mutate(RDI_pacli_adj_grp1 = case_when(
@@
                                      "Overdosing")))
-RDI_data %>% distinct(patientid) %>% nrow()
 ```
@@
 - exclude patients whose histology is unknown  
-- remove chemotherapy only patients
+<!-- - remove chemotherapy only patients -->
 - include only patients who received platin and/or taxane
-- exclude patients who only received neo + surgery
+<!-- - exclude patients who only received neo + surgery -->
 - include patients with single or dual P/T +/- Bev as frontline treatment
@@
 study_criteria <- study_criteria %>%
-  filter(!is.na(surgerydate)) %>% 
+  # filter(!is.na(surgerydate)) %>% 
   mutate(chemotherapy_type = factor(chemotherapy_type))
@@
 
-study_criteria <- study_criteria %>% 
-  filter(treatment_sequence == "neo + surg + adj" |
-           treatment_sequence == "surg + adj")
+# study_criteria <- study_criteria %>% 
+#   filter(treatment_sequence == "neo + surg + adj" |
+#            treatment_sequence == "surg + adj")
 
@@
     therapy == "Upfront Chemo" &
-      (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
-         !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
+      (!is.na(RDI_carbo_neo_grp) & !is.na(RDI_pacli_neo_grp) &
+         !is.na(RDI_carbo_adj_grp) & !is.na(RDI_pacli_adj_grp))
   ) | (
     therapy == "Upfront Surgery" &
-      (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
+      (!is.na(RDI_carbo_adj_grp) & !is.na(RDI_pacli_adj_grp))
   )
@@
   select(patientid, month_at_os, vital_status, 
-         raceeth, diagnosisdate, surgerydate,
+         raceeth, diagnosisdate,
          ageatdx, stagecat, debulking, histology,
-         RDI_carbo_neo, RDI_pacli_neo, 
-         RDI_carbo_adj, RDI_pacli_adj
+         RDI_carbo_neo_grp, RDI_pacli_neo_grp, 
+         RDI_carbo_adj_grp, RDI_pacli_adj_grp
          # therapy
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + debulking + histology,
         data = data)
@@
 ```{r}
-Pred[, "surgerydate"] <- 1
-Pred["surgerydate", "surgerydate"] <- 0
+Pred[, "RDI_carbo_adj_grp"] <- 1
+Pred["RDI_carbo_adj_grp", "RDI_carbo_adj_grp"] <- 0
+Pred[, "RDI_pacli_adj_grp"] <- 1
+Pred["RDI_pacli_adj_grp", "RDI_pacli_adj_grp"] <- 0
 Pred
@@
        exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os, vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + debulking + histology
        ))
@@
 
-Do m = 34 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.339 that we multiply by 100)
-```{r}
-Cox.imp <- mice(dataset, m=34, maxit=50, 
+Do m = 76 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.762 that we multiply by 100)
+```{r}
+Cox.imp <- mice(dataset, m=76, maxit=50, 
                 predictorMatrix=Pred,
@@
          ageatdx, stagecat, debulking, histology,
-         RDI_carbo_adj, RDI_pacli_adj
+         RDI_carbo_adj_grp, RDI_pacli_adj_grp
          # therapy
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + debulking + histology,
         data = data)
@@
        exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + debulking + histology
        ))
@@
 
-Do m = 17 (The max fmi = 0.166 that we multiply by 100)
-```{r}
-Cox.imp <- mice(dataset, m=17, maxit=50, 
+Do m = 13 (The max fmi = 0.131 that we multiply by 100)
+```{r}
+Cox.imp <- mice(dataset, m=13, maxit=50, 
                 predictorMatrix=Pred,
@@
       • exclude patients whose histology is unknown <br>
-      • remove chemotherapy only patients <br>
-      • include only patients who received platin and/or taxane <br>
-      • exclude patients who only received neo + surgery <br>
+      • include only patients who received platin and taxane <br>
       • include patients with single or dual P/T +/- Bev as frontline treatment
@@
 tbl2 <- tbl2 %>%
-  select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>% 
+  select(vital_status, RDI_carbo_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 tbl2 <- tbl2 %>%
-  select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>% 
+  select(vital_status, RDI_pacli_adj_grp) %>% 
   tbl_uvregression(method = survival::coxph,
@@
 ```{r rdi continous}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl1 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl1, tbl2, tbl3),
+#           group_header = c("carboplatin Neo/Upfront Chemo", 
+#                            "carboplatin Adj/Upfront Chemo",
+#                            "carboplatin Adj/Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
+# 
+# # Pacli
+# 
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl1 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl1, tbl2, tbl3),
+#           group_header = c("paclitaxel Neo/Upfront Chemo", 
+#                            "paclitaxel Adj/Upfront Chemo",
+#                            "paclitaxel Adj/Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
 ```
@@
 ```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl1 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl1, tbl2, tbl3),
+#           group_header = c("carboplatin Neo/Upfront Chemo", 
+#                            "carboplatin Adj/Upfront Chemo",
+#                            "carboplatin Adj/Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
+# 
+# # Pacli
+# 
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl1 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl1, tbl2, tbl3),
+#           group_header = c("paclitaxel Neo/Upfront Chemo", 
+#                            "paclitaxel Adj/Upfront Chemo",
+#                            "paclitaxel Adj/Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
 ```
@@
 ```{r rdi continous adjusted by other drug}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H c}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
-  cox.zph()
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl21 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl31 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl21, tbl31),
+#           group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
 ```
@@
 ```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl2, tbl3),
+#           group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
 ```
@@
 ```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl1 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl1, tbl2, tbl3),
+#           group_header = c("carboplatin Neo/Upfront Chemo", 
+#                            "carboplatin Adj/Upfront Chemo",
+#                            "carboplatin Adj/Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
+# 
+# # Pacli
+# 
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl1 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl1, tbl2, tbl3),
+#           group_header = c("paclitaxel Neo/Upfront Chemo", 
+#                            "paclitaxel Adj/Upfront Chemo",
+#                            "paclitaxel Adj/Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
 ```
@@
 ```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("carboplatin Neo/Upfront Chemo", 
-                           "carboplatin Adj/Upfront Chemo",
-                           "carboplatin Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-
-# Pacli
-
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl1 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl1, tbl2, tbl3),
-          group_header = c("paclitaxel Neo/Upfront Chemo", 
-                           "paclitaxel Adj/Upfront Chemo",
-                           "paclitaxel Adj/Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl1 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl1, tbl2, tbl3),
+#           group_header = c("carboplatin Neo/Upfront Chemo", 
+#                            "carboplatin Adj/Upfront Chemo",
+#                            "carboplatin Adj/Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
+# 
+# # Pacli
+# 
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl1 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl1, tbl2, tbl3),
+#           group_header = c("paclitaxel Neo/Upfront Chemo", 
+#                            "paclitaxel Adj/Upfront Chemo",
+#                            "paclitaxel Adj/Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
 ```
@@
 PH assumption Upfront Chemo  
+Error in solve.default(imat, u) :   
+  Lapack routine dgesv: system is exactly singular: U[3,3] = 0  
+The error message is telling you that your matrix is singular and cannot be inverted.
+
 ```{r prop H complete case}
@@
 ```{r }
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl21 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl31 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl21, tbl31),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-
-PH assumption Upfront Chemo
-```{r prop H complete case c}
-coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>% 
-  cox.zph()
-```
-
-PH assumption Upfront Surgery
-```{r}
-coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
-  cox.zph()
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl21 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl31 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl21, tbl31),
+#           group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
 ```
@@
 ```{r}
-tbl2 <- Frontline %>%
-  filter(therapy == "Upfront Chemo")
-tbl2 <- 
-  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-  filter(therapy == "Upfront Surgery")
-tbl3 <- 
-  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
-  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl_stack(list(tbl2, tbl3),
-          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
-  bold_labels() %>%
-  italicize_levels()
-```
-<br>
-<br>
+# tbl2 <- Frontline %>%
+#   filter(therapy == "Upfront Chemo")
+# tbl2 <- 
+#   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+#              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl3 <- Frontline %>%
+#   filter(therapy == "Upfront Surgery")
+# tbl3 <- 
+#   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+#              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+#   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+# tbl_stack(list(tbl2, tbl3),
+#           group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+#   bold_labels() %>%
+#   italicize_levels()
+```
+<br>
+<br>
+
+***
+# Question from Jeannie
+Of the patients who are paclitaxel underdosed, how many are carboplatin underdosed?
+```{r}
+Frontline %>% filter(RDI_pacli_adj_grp == "Underdosed" | RDI_pacli_neo_grp == "Underdosed") %>% 
+  select(RDI_carbo_neo_grp, RDI_carbo_adj_grp, therapy) %>% 
+  tbl_summary(by= therapy)
+
+Frontline %>% filter(RDI_pacli_adj_grp == "Underdosed" | RDI_pacli_neo_grp == "Underdosed") %>% 
+  select(RDI_carbo_neo_grp, RDI_carbo_adj_grp, therapy, treatment_sequence) %>% 
+  tbl_strata(
+    strata = treatment_sequence,
+    .tbl_fun =
+      ~ .x %>%
+        tbl_summary(by = therapy, 
+                    missing = "no") %>%
+        add_p(),
+    .header = "**{strata}**, N = {n}"
+  ) 
+```
 

### 2022-02-04 R/01.Load data.R

@@ -1,57 +1,59 @@
-# library(drake)
-library(tidyverse)
-library(data.table)
-library(lubridate)
-# library(gtsummary)
-# library(survival)
-# library(survminer)
+# RUN DRAKE INSTEAD-THIS SCRIPT IS RUNNING OLDER FILES-----
 
-
-#################################################################################################### I ### Load data
-path <- fs::path("","Volumes","Peres_Research")
-
-# demo_data <-
+# # library(drake)
+# library(tidyverse)
+# library(data.table)
+# library(lubridate)
+# # library(gtsummary)
+# # library(survival)
+# # library(survminer)
+# 
+# 
+# #################################################################################################### I ### Load data
+# path <- fs::path("","Volumes","Peres_Research")
+# 
+# # demo_data <-
+# #   read_csv(paste0(path,
+# #                   "/Flatiron/Data from Flatiron/ovarian/ovarian_demographics.csv")) %>% 
+# #   select(-c("practiceid", "practicetype", "primaryphysicianid"))
+# clinical_data <- # For Dx date, histo, stage, surgerydate
 #   read_csv(paste0(path,
-#                   "/Flatiron/Data from Flatiron/ovarian/ovarian_demographics.csv")) %>% 
-#   select(-c("practiceid", "practicetype", "primaryphysicianid"))
-clinical_data <- # For Dx date, histo, stage, surgerydate
-  read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/NEW_ovarianCLEANwithbiom.csv"))
-creatinine <-
-  read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/NEW_labs_creatinine.csv"))
-vitals <-
-  read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/NEW_vitals_anthro.csv"))
-# visit <- # For all the visit date, may need it to know the treatment date (no drug name)
+#                   "/Flatiron/Data from Flatiron/ovarian/NEW_ovarianCLEANwithbiom.csv"))
+# creatinine <-
 #   read_csv(paste0(path,
-#                   "/Flatiron/Data from Flatiron/ovarian/ovarian_visit.csv"))
-
-
-
-drug <- # For each drug date
-  read_csv(paste0(path,
-                  "/Flatiron/Data from Flatiron/ovarian/ovarian_drugepisode.csv"))
-
[…]

### 2022-02-24 Rmd/Adjusted weight rdi analysis.Rmd
Fix adjusted CrCl

@@
 
+IF actual_bmi < 25 :
+$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
 IF actual_bmi >= 25 :
-$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
-IF actual_bmi < 25 :
 
@@
   # Calculate CrCl
-  # inner_join(., clinical_data %>% select(-surgerydate),
-  #            by = "patientid") %>% 
   mutate(CrCl = (
@@
   mutate(adjusted_CrCl = case_when(
-    actual_bmi >= 25                  ~ CrCl,
-    actual_bmi < 25                   ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
+    actual_bmi < 25                   ~ CrCl,
+    actual_bmi >= 25                  ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
   )) %>% 
@@
     drugname == "paclitaxel"                  ~ BSA * target_auc 
-    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
   )) %>% 

### 2022-03-03 Rmd/rdi analysis.Rmd
Add carbo only adjusted HR

@@
 
+### Carbo only
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology`
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
 <br>
@@
 
+## Carbo only
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status
+             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology`
+```{r}
+tbl2 <- Frontline %>%
+  filter(therapy == "Upfront Chemo")
+tbl2 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- Frontline %>%
+  filter(therapy == "Upfront Surgery")
+tbl3 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl2, tbl3),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
 <br>

### 2022-03-31 Rmd/Actual weight rdi analysis.Rmd
Simplify Rmd: transfer stable code for drugs cleaning in R script 02.data cleaning and call the cleaned rds in the Rmd

--- 2022-03-03 Rmd/rdi analysis.Rmd
@@
 ```{r library, include=FALSE}
-library(drake)
+# library(drake)
 library(tidyverse)
@@
 ```{r loadd}
-loadd(drugs)
+# loadd(drugs)
 creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
@@
 clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
+Treatment <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/Treatment.rds")
 ```
@@
 **We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
-We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.**
+We have `r Treatment %>% distinct(PatientID) %>% nrow()` patients with cleaned info in drug data.**
 
 ```{r drugs episode cleanup}
-drugs <- drugs %>% 
-  `colnames<-`(str_to_lower(colnames(.))) %>% 
-  # Select only records for administration
-  filter(episodedatasource == "Administrations") %>%
-  # bind with clinical
-  inner_join(., clinical_data, 
-          by = "patientid") %>% 
-  arrange(patientid, episodedate)
-```
-**But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.**
+
+```
 
@@
 ```{r combine amount same drug one day}
-combined_drugs <- drugs %>% 
-  # Combined Multiple Administrations----
-  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
-  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate,
-           drugname, units, ismaintenancetherapy) %>%
-  summarise_at(vars(route, amount), paste, collapse = ";") %>% # keep them in the data then do sum
-  mutate(route = case_when(
-    str_detect(route, ";")            ~ "Intravenous", # I checked that all the combined administration are IV
-    TRUE                              ~ route
-  )) %>% 
-  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
-           fill = "right") %>%
-  ungroup() %>% 
-  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
-  purrr::keep(~!all(is.na(.))) %>%
-  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
-  mutate(amount = rowSums(select(.,starts_with("amount_")), na.rm = TRUE)) %>%
-  # Found ug, ml, Ea, and NA they are all good, but 
-  # ug need conversion
-  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 so remove
-  mutate(amount =  case_when(
-    units == "ug"               ~ amount / 10, # I checked all of them
-    units == "AUC" &
-      amount < 10               ~ NA_real_,
-    TRUE                        ~ amount
-  ))# %>%
-
-  # mutate(drugname_type = case_when(
-  #   str_detect(drugname, "platin")       ~ "platin",
-  #   str_detect(drugname, "taxel")        ~ "taxel"
-  # ))
-```
-
-- Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
+
+```
+
+- 
 ```{r line coding}
-therapy_line <- combined_drugs %>% 
-  # bind again with clinical - was lost while summarizing
-  inner_join(., clinical_data, 
-          by = "patientid") %>% 
-  arrange(patientid, episodedate) %>% 
-  # Define Adjuvant, Neoadjuvant, chemo or surgery
-  mutate(chemotherapy_type = case_when(
-    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
-    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
-    episodedate > surgerydate         ~ "Adjuvant",
-    is.na(surgerydate) &
-      !is.na(episodedate)             ~ "Chemotherapy only",
-    !is.na(surgerydate) &
-      is.na(episodedate)              ~ "Surgery only"
-    )) %>% 
-  mutate(chemotherapy_type = 
-           factor(chemotherapy_type, levels = 
-                    c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
-  group_by(patientid) %>% 
-  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
-  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
-  fill(had_neo, had_adj, .direction = "updown") %>% 
-  mutate(treatment_sequence = case_when(
-    had_neo == "Yes" &
-      had_adj == "Yes"                           ~ "neo + surg + adj",
-    had_neo == "Yes" &
-      is.na(had_adj)                             ~ "neo + surg",
-    is.na(had_neo) &
-      had_adj == "Yes"                           ~ "surg + adj",
-    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
-    chemotherapy_type == "Surgery only"          ~ "Surgery only"
-  )) %>% 
-  mutate(therapy = case_when(
-    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
-    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
-    chemotherapy_type == "Surgery only"          ~ "Surgery only",
-    is.na(had_neo) &
-      had_adj == "Yes"                           ~ "Upfront Surgery"
-  )) %>% 
-  fill(therapy, .direction = "downup") %>%
-
-  # Redefine line number based on the original linenumber variable and the surgery date
-  mutate(linenumber_n = dense_rank(interaction(linenumber, chemotherapy_type))) %>%  
-  # Redefine line number based on the new linenumber variable and if a switch 
-  # to maintenance is detected within the line
-  group_by(patientid, linenumber_n, ismaintenancetherapy) %>% 
-  mutate(maint_rank = row_number(ismaintenancetherapy),
-         maint_rank = ifelse(maint_rank == 1, 1, 0)) %>% 
-  group_by(patientid) %>% 
-  mutate(linenumber_new = cumsum(maint_rank)) %>%  
-  # F0000AD999ABF, F1C68CFAC2AF3, FBCF69031DFF8, F0040EA299CF0, FAACDC7205803,  FA019D2071321 no has big jump F95D860690A93 F0F1324B863A8
-  select(patientid, linename, linenumber, linenumber_new, drugname, 
-         episodedate, surgerydate, chemotherapy_type, everything()) %>% 
-  ungroup() %>% 
-  # Define line number restarting to 1 for each chemotherapy_type
-  group_by(patientid, chemotherapy_type) %>% 
-  mutate(linenumber_adj = dense_rank(linenumber_new)) %>% 
-  ungroup() %>% 
-  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor)) %>% 
-  # Redefine line dates
-  group_by(patientid, linenumber_new) %>% 
-  mutate(linestartdate = min(episodedate)) %>% 
-  mutate(lineenddate = max(episodedate)) %>% 
-  ungroup() %>% 
-  select(-c(linenumber_n, maint_rank))
-
-  # 6.Add a 30 day rule to switch linenumber----
-  # group_by(patientid, linenumber_new) %>% 
-  # arrange(episodedate) %>% 
-  # mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
-  # mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
-  # ungroup() %>% 
-  # group_by(patientid) %>% 
-  # mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
-  # mutate(linenumber_new = linenumber_new + jump_line) %>% 
-  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37
 
@@
 ```{r cycle coding}
-therapy_cycle <- therapy_line %>% 
-  # Define cycle for each line
-  # F003F2BEEDB37 need to change drugname pacli = pacli bp
-  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  
-  # Need the number of time of the "major" drug is seen in the line
-  group_by(patientid, linenumber_new, cycle_drugname) %>%
-  mutate(drugname_count_perline = case_when(
-           str_detect(drugname, "carboplatin|paclitaxel")     ~ n()
-         )) %>%
-  ungroup() %>% 
-  arrange(patientid, episodedate, drugname) %>% 
-  group_by(patientid, linenumber_new) %>%
-  # Take the major drugname as a mark of new cycle start
-  mutate(cycle_count_perline = min(drugname_count_perline, na.rm = TRUE)) %>%
-  mutate(cycle_major_drugname = case_when(
-    cycle_count_perline == drugname_count_perline &
-      (cycle_drugname == "carboplatin" |
-      cycle_drugname == "paclitaxel")                      ~ cycle_drugname,
-    TRUE                                                   ~ NA_character_
-  )) %>% 
-  # select(-drugname_count_perline) %>% 
-  # Code cycle number based on when major drug name appear again
-  group_by(patientid, linenumber_new, drugname, cycle_major_drugname) %>%
-  mutate(cycle_increment = row_number(cycle_major_drugname)) %>% # Look at F002DD2953889 inversed dose dense------------------
-  # F01D908A013B7 weird dose dense
-
-  # F003F2BEEDB37 change of dose dense 50% ok? ---------------------------------------------------------------
-
-  arrange(patientid, episodedate, cycle_increment) %>% 
-  group_by(patientid, linenumber_new) %>%
-  fill(cycle_increment, .direction = "downup") %>%  # make sure I can do up for have one new drug compare to the linename FBB5186A15CD9 ok, FE593EDF5586A has a switched drugs will be removed
-  group_by(patientid, chemotherapy_type, cycle_increment) %>% 
-  # Code is_dose_dense to be 1 for the first drug in the cycle
-  mutate(is_dose_dense = row_number(cycle_increment),
-         is_dose_dense = ifelse(is_dose_dense == 1, 1, NA_real_)) %>% 
-  group_by(patientid) %>% 
-  mutate(total_cycle_increment = row_number(is_dose_dense)
-         ) %>% 
-  group_by(patientid, linenumber_adj) %>% 
-  fill(total_cycle_increment, .direction = "downup") %>% 
-  # cycle date
-  group_by(patientid, linenumber_new, cycle_increment) %>% 
-  mutate(cycle_start_date = min(episodedate)) %>%
-
-  # Look at dose dense
-  # Code how many time a drug comes up in a cycle
-  group_by(patientid, linenumber_new, cycle_increment, cycle_drugname) %>%  # weird dose dense F064D9EB733B3 F050B815FC126
-  mutate(dose_dense = n()) %>% 
-  mutate(dose_dense = max(dose_dense)) %>%  # too much cycle
-  ungroup()
-
-  # # CODE FOR SKIPPED CYCLE
-  # group_by(patientid, linenumber_new) %>% 
-  # mutate(cycle_interval = cycle_start_date - lag(cycle_start_date), 
-  #        cycle_interval = ifelse(cycle_interval == 0, NA_real_, cycle_interval)) %>%  # FDB58481AFFBB 48 days
-  # 
-  # # take for granted that the cycle interval days are the routine cycle for the rest of the line FAACDC7205803
-  # mutate(n = row_number(drugname)) %>%
-  # 
-  # mutate(base_days_between_cycle = ifelse(n==2 , cycle_interval, NA_real_)) %>%
-  # fill(base_days_between_cycle, .direction = "downup") %>% 
-  # mutate(skipped_cycle_indays = ifelse(((cycle_interval - base_days_between_cycle) != 0) ,
-  #                                      (cycle_interval - base_days_between_cycle), NA_real_)) %>% # weird FDB58481AFFBB
-  # # Fix skipped_cycle_indays when only 1 drug FDB58481AFFBB skipped_cycle_indays = NA, no other choice...
-  # group_by(patientid, linenumber_new) %>%
-  # mutate(drug_count_perline = n()) %>%
-  # mutate(skipped_cycle_indays1 = ifelse(
-  #   (cycle_count_perline == drug_count_perline), NA_real_, skipped_cycle_indays 
-  # )) %>% # F001443D8B85C Pb with when different pattern by cycle => May not be able to have the skipped cycle
-  # # or need to compare with dose like if 100 should be 7 days and if 200 should be 14 days....
-  # group_by(patientid) %>% 
-  # mutate(mean_skipped_cycle_indays = mean(skipped_cycle_indays, na.rm = TRUE)) %>% 
-  # ungroup()
-
-# rm(drugs, drugs1, therapy_line)
-therapy_cycle %>% distinct(patientid) %>% nrow()
+
 ```
@@
 ```{r target_auc and expected dose}
-Treatment1 <- 
-  # Merge with creatinine
-  left_join(therapy_cycle, creatinine, by = "patientid") %>%
-  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
-                          duration(n=1, unit="days"))) %>% 
-  mutate(interval_creat = case_when(
-    (therapy == "Upfront Surgery" &
-       interval_creat < 31 &
-       # creat_date < lineenddate &
-       creat_date > surgerydate)                  ~ interval_creat,
-
-    therapy == "Upfront Chemo" &
-      (
-        (chemotherapy_type == "Neoadjuvant" &
-           interval_creat < 31 &
-           creat_date < surgerydate) |
-          (chemotherapy_type == "Adjuvant" &
-             interval_creat < 31 &
-             # creat_date < lineenddate &
-             creat_date > surgerydate)
-      )                                          ~ interval_creat,
-    TRUE                                         ~ NA_real_
-  )) %>%
-  arrange(interval_creat) %>% 
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
-           cycle_start_date, .keep_all = TRUE) %>%
-
-  # Merge with height
-  left_join(. , height,  by = "patientid") %>%
-  mutate(interval_height = abs(interval(start= height_date, end= cycle_start_date)/
-           duration(n=1, unit="days"))) %>%
-  arrange(interval_height) %>%
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
-           cycle_start_date, .keep_all = TRUE) %>%
-
-  # Merge with weight
-  left_join(. , weight, by = "patientid") %>%
-  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
-                        duration(n=1, unit="days"))) %>%
-  mutate(interval_weight = case_when(
-    (therapy == "Upfront Surgery" &
-       interval_weight < 31 &
-       # weight_date < lineenddate &
-       weight_date > surgerydate)                  ~ interval_weight,
-
-    therapy == "Upfront Chemo" &
-      (
-        (chemotherapy_type == "Neoadjuvant" &
-           interval_weight < 31 &
-           weight_date < surgerydate) |
-          (chemotherapy_type == "Adjuvant" &
-             interval_weight < 31 &
-             # weight_date < lineenddate &
-             weight_date > surgerydate)
-      )                                          ~ interval_weight,
-    TRUE                                         ~ NA_real_
-  )) %>%
-  arrange(interval_weight) %>%
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
-         cycle_start_date, .keep_all = TRUE) %>%
-
-  # Calculate ideal dody weight
-  mutate(ideal_weight = case_when(
-    height <= 1.524               ~ 45.5 + 2.3,
-    height > 1.524                ~ 45.5 + (2.3 * (((height - 1.524) / 0.0254)))
-  )) %>% 
-  mutate(adjusted_weight = ((weight - ideal_weight) * 0.40) + ideal_weight
-  ) %>% 
-  # Calculate bmi
-  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
-  mutate(bmi_cat = case_when(
-    bmi_at_dx < 25                    ~ "Underweight and normal weight",
-    bmi_at_dx >= 25 &
-      bmi_at_dx < 30                  ~ "Overweight",
-    bmi_at_dx >= 30                   ~ "Obese"
-  )) %>%
-  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
-
-  mutate(actual_bmi = weight / (height * height)) %>%
-  mutate(actual_bmi_cat = case_when(
-    actual_bmi < 25                    ~ "Underweight and normal weight",
-    actual_bmi >= 25 &
-      actual_bmi < 30                  ~ "Overweight",
-    actual_bmi >= 30                   ~ "Obese"
-  )) %>%
-  mutate(actual_bmi_cat = factor(actual_bmi_cat, 
-                                  levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
-  # select(patientid, weight, height, bmi_at_dx, ideal_weight, adjusted_weight, adjusted_bmi)
-  # Calculate CrCl
-  # inner_join(., clinical_data %>% select(-surgerydate),
-  #            by = "patientid") %>% 
-  mutate(CrCl = (
-       (
-    ((140 - ageatdx) * weight) /
-    (72 * creatinine)
-       ) *
-    0.85)
-  ) %>% 
-  mutate(CrCl = case_when(
-    CrCl > 125                        ~ 125,
-    TRUE                              ~ CrCl
-  )) %>% 
-  mutate(adjusted_CrCl = case_when(
-    actual_bmi >= 25                  ~ CrCl,
-    actual_bmi < 25                   ~ (((140 - ageatdx) * adjusted_weight) / (72 * creatinine)) * 0.85
-  )) %>% 
-  mutate(adjusted_CrCl = case_when(
-    adjusted_CrCl > 125               ~ 125,
-    TRUE                              ~ adjusted_CrCl
-  )) %>%
-
-  # Merge with body_surface_area
-  left_join(., body_surface_area, by = "patientid") %>%
-  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
-                          duration(n=1, unit="days"))) %>%
-  mutate(interval_bsa = case_when(
-    (therapy == "Upfront Surgery" &
-       interval_bsa < 31 &
-       # bsa_date < lineenddate &
-       bsa_date > surgerydate)                  ~ interval_bsa,
-
-    therapy == "Upfront Chemo" &
-      (
-        (chemotherapy_type == "Neoadjuvant" &
-           interval_bsa < 31 &
-           bsa_date < surgerydate) |
-          (chemotherapy_type == "Adjuvant" &
-             interval_bsa < 31 &
-             # bsa_date < lineenddate &
-             bsa_date > surgerydate)
-      )                                          ~ interval_bsa,
-    TRUE                                         ~ NA_real_
-  )) %>%
-  arrange(interval_bsa) %>%
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
-           cycle_start_date, .keep_all = TRUE) %>%
-  # Calculate more bsa value with height and weight using Du Bois formula
-  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
-  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
-  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
-  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
-  select(-bsa_du_bois) %>%
-
-  # Merge with auc
-  left_join(., areaUC, by = c("patientid", "drugname")) %>%
-  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
-                          duration(n=1, unit="days"))) %>% 
-  mutate(interval_auc = case_when(
-    (therapy == "Upfront Surgery" &
-       interval_auc < 31 &
-       # auc_date < lineenddate &
-       auc_date > surgerydate)                  ~ interval_auc,
-
-    therapy == "Upfront Chemo" &
-      (
-        (chemotherapy_type == "Neoadjuvant" &
-           interval_auc < 31 &
-           auc_date < surgerydate) |
-          (chemotherapy_type == "Adjuvant" &
-             interval_auc < 31 &
-             # auc_date < lineenddate &
-             auc_date > surgerydate)
-      )                                          ~ interval_auc,
-    TRUE                                         ~ NA_real_
-  )) %>%
-  arrange(interval_auc) %>% 
-  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
-           cycle_start_date, .keep_all = TRUE) %>%
-
-  # Calculate expected dose
-  mutate(expected_dose = case_when(
-    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
-    drugname == "paclitaxel"                  ~ BSA * target_auc 
-    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
-  )) %>% 
-  mutate(expected_dose = case_when(
-    expected_dose > 900 &
-      target_auc == 6              ~ 900,
-    expected_dose > 750 &
-      target_auc == 5              ~ 750,
-    TRUE                           ~ expected_dose
-  )) %>% 
-  mutate(adjusted_expected_dose = case_when(
-    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
-    drugname == "paclitaxel"                  ~ BSA * target_auc 
-    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
-  )) %>% 
-  mutate(adjusted_expected_dose = case_when(
-    adjusted_expected_dose > 900 &
-      target_auc == 6              ~ 900,
-    adjusted_expected_dose > 750 &
-      target_auc == 5              ~ 750,
-    TRUE                           ~ adjusted_expected_dose
-  )) %>% 
-  group_by(patientid) %>%
-  mutate(first_treatment_date = case_when(
-    str_detect(therapy, "Chemo")                      ~ min(episodedate),
-    str_detect(therapy, "Surgery")                    ~ surgerydate,
-  )) %>% 
-  ungroup() %>% 
-  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
-                   duration(n=1, units = "months")) %>% 
-  arrange(patientid, episodedate)
-
-Treatment1 %>% distinct(patientid) %>% nrow()
+
 ```
@@
 ```{r rule between diagnosis and treatment}
-Treatment <- Treatment1 %>% 
-  filter(route == "Intravenous") %>% 
-  # step 1: Flatiron recommendation cleanup
-  # 90 days rule between diagnosis and treatment
-  group_by(patientid) %>% 
-  mutate(first_drug_date = first(episodedate)) %>% 
-  ungroup() %>% 
-  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
-           duration(n=1, units = "days")) %>% 
-  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
-           duration(n=1, units = "days")) %>% 
-  mutate(days_at_first_treatment = case_when(
-    therapy == "Upfront Chemo" |
-      therapy == "Chemotherapy only"             ~ interval(start = diagnosisdate, end = first_drug_date)/
-           duration(n=1, units = "days"),
-    therapy == "Upfront Surgery" |
-      therapy == "Surgery Only"                  ~ interval(start = diagnosisdate, end = surgerydate)/
-           duration(n=1, units = "days")
-  )) %>% 
-  # 30 days rule excluding patient who didn’t survive for at least 30 days after diagnosis
-  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
-           duration(n=1, units = "days")
-  ) %>% 
-  mutate(flatiron_rules = case_when(
-    days_at_first_treatment > 90                 ~ "exclude",
-    thirty_days_exclusion <= 30                  ~ "exclude",
-    exclude == "1"                               ~ "exclude"
-  )) %>%
-  group_by(patientid) %>% 
-  fill(flatiron_rules, .direction = "downup") %>% 
-  ungroup() %>%
-
-  # step 2: Filter patients with clinical characteristics fitting to the study criteria
-  # include only patients who received platin and/or taxane
-  mutate(had_carbo_pacli = case_when(
-    drugname == "paclitaxel" |
-      drugname == "carboplatin"             ~ "Yes"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(had_carbo_pacli, .direction = "updown") %>% 
-  ungroup() %>% 
-  # include patients with single or dual P/T +/- Bev as frontline treatment
-  mutate(line_keep = case_when(# F002B429BE6C6
-    (linenumber_adj == 1 &
-           (linename == "Carboplatin,Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
-           linename == "Carboplatin" |
-           linename == "Paclitaxel" |
-           linename == "Bevacizumab,Paclitaxel" |
-           linename == "Bevacizumab,Carboplatin"))            ~ NA_character_,
-    linenumber_adj == 1                                       ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(line_keep, .direction = "updown") %>% 
-  ungroup() %>%
-
-  # step 3: Filter out patients with missing data
-  # remove patients with long gap between surgery and adjuvant start (3 months)
-  mutate(interval_surgery_to_adj_start = case_when(
-      chemotherapy_type == "Adjuvant" &
-        linenumber_adj == 1       
-      ~ interval(start = surgerydate, end = linestartdate) / duration(n = 1, units = "months")
-    )) %>% 
-  mutate(gap_surg_drugs = case_when(
-    interval_surgery_to_adj_start > 3                  ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(gap_surg_drugs, .direction = "updown") %>% 
-  ungroup() %>%
-
-  # step 4: Include patients with treatments following the standard of clinical care
-  # exclude patients with more than 1 line as Neo
-  mutate(neo_more_more_than_1line = case_when(
-    chemotherapy_type == "Neoadjuvant" &
-           linenumber_new != 1                 ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(neo_more_more_than_1line, .direction = "updown") %>% 
-  ungroup() %>% 
-  # exclude patients with maintenance within their frontline
-  mutate(frontline_has_maintenance = case_when(
-    linenumber_adj == 1 &
-    ismaintenancetherapy == "TRUE"             ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>% 
-  fill(frontline_has_maintenance, .direction = "updown") %>% 
-  ungroup() %>% 
-  # exclude patients with more than 6 cycles in Neo, more than 9 cycles total 
-  # in upfront chemo or more than 9 cycles in upfront surgery
-  mutate(too_many_cycle = case_when(
-    (linenumber_new == 1 &
-       therapy == "Upfront Chemo" &
-       total_cycle_increment > 6) |
-
-      (linenumber_new == 2 &
-         therapy == "Upfront Chemo" &
-         total_cycle_increment > 9) |
-
-      (linenumber_new == 1 &
-         therapy == "Upfront Surgery" &
-         total_cycle_increment > 9)             ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(too_many_cycle, .direction = "updown") %>%
-  ungroup() %>% 
-  # Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
-  # Removes also the patients who has only carbo or only pacli
-  # dose_dense will need to be changed if we change and include these patients
-  arrange(patientid, episodedate, drugname) %>% 
-  mutate(wrong_pacli_dosedense = case_when(
-    drugname == "paclitaxel" &
-      is.na(too_many_cycle) &
-      (dose_dense == 2 |
-      dose_dense > 3) &
-      linenumber_adj == 1
-      # ((linenumber_new == 1 &
-      #  therapy == "Upfront Chemo") |
-      # (linenumber_new == 2 &
-      #    therapy == "Upfront Chemo") |
-      # (linenumber_new == 1 &
-      #    therapy == "Upfront Surgery"))
-    ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(wrong_pacli_dosedense, .direction = "updown") %>% 
-  ungroup() %>% 
-  # Exclude patients who switch drug within a line
-  mutate(switch_drugs = case_when(
-    str_detect(linename, "Pacli") & 
-      drugname == "docetaxel" & 
-      linenumber_adj == 1                      ~ "exclude",
-    str_detect(linename, "Car") & 
-      drugname == "cisplatin" & 
-      linenumber_adj == 1                      ~ "exclude"
-  )) %>% 
-  group_by(patientid) %>%
-  fill(switch_drugs, .direction = "updown") %>% 
-  ungroup()
-
-  # group_by(patientid, wrong_pacli_dosedense) %>% 
-  # mutate(n_dose_dense = n()) %>% 
-  # 
-  # 
-  # 
-  # is.na(too_many_cycle)
-
-Treatment %>% distinct(patientid) %>% nrow()
+
 ```
@@
 Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
+patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
 Look at the Cox regression model before imputation.
@@
   filter(therapy == "Upfront Chemo") %>% 
-  select(patientid, month_at_os, vital_status, 
+  select(patientid, month_at_os_from_treatment, vital_status, 
          raceeth, diagnosisdate, surgerydate,
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
         data = data)
@@
 
-Hazard <- nelsonaalen(data, month_at_os, vital_status)
+Hazard <- nelsonaalen(data, month_at_os_from_treatment, vital_status)
 dataset <- data.frame(data, Hazard)
@@
 Pred <- Cox.imp$predictorMatrix
-# Pred["debulking", "month_at_os"] <- 0
+# Pred["debulking", "month_at_os_from_treatment"] <- 0
 Pred
@@
        exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
        ))
@@
 ```{r}
+hggjgjgkj change the m number
 Cox.imp <- mice(dataset, m=34, maxit=50, 
@@
 Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
+patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
 
@@
   filter(therapy == "Upfront Surgery") %>% 
-  select(patientid, month_at_os, vital_status, 
+  select(patientid, month_at_os_from_treatment, vital_status, 
          raceeth, diagnosisdate, surgerydate,
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
         data = data)
@@
        exp = coxph(
-         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
        ))

### 2022-03-31 R/02.data cleaning.R

@@ -425,3 +425,568 @@ write_rds(clinical_data, "clinical_data.rds")
 
 
 #################################################################################################### III ### Treatment Cleaning----
+# Select episodedatasource == "Administrations"-----
+drugs <- drugs %>% 
+  `colnames<-`(str_to_lower(colnames(.))) %>% 
+  # Select only records for administration
+  filter(episodedatasource == "Administrations") %>%
+  # bind with clinical
+  inner_join(., clinical_data, 
+             by = "patientid") %>% 
+  arrange(patientid, episodedate)
+
+# Combine multiple administrations of the same drug at the same date-----
+combined_drugs <- drugs %>% 
+  # Combined Multiple Administrations----
+# combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
+group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate,
+         drugname, units, ismaintenancetherapy) %>%
+  summarise_at(vars(route, amount), paste, collapse = ";") %>% # keep them in the data then do sum
+  mutate(route = case_when(
+    str_detect(route, ";")            ~ "Intravenous", # I checked that all the combined administration are IV
+    TRUE                              ~ route
+  )) %>% 
+  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
+           fill = "right") %>%
+  ungroup() %>% 
+  mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
+  purrr::keep(~!all(is.na(.))) %>%
+  mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
+  mutate(amount = rowSums(select(.,starts_with("amount_")), na.rm = TRUE)) %>%
+  # Found ug, ml, Ea, and NA they are all good, but 
+  # ug need conversion
+  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 so remove
+  mutate(amount =  case_when(
+    units == "ug"               ~ amount / 10, # I checked all of them
+    units == "AUC" &
+      amount < 10               ~ NA_real_,
+    TRUE                        ~ amount
+  ))# %>% 
+
+# mutate(drugname_type = case_when(
[…]

### 2022-03-31 Rmd/Actual weight rdi analysis.Rmd
Simplify Rmd: transfer stable code for drugs cleaning in R script 02.data cleaning and call the cleaned rds in the Rmd

@@
 Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
+patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
 Look at the Cox regression model before imputation.
@@
   filter(therapy == "Upfront Chemo") %>% 
-  select(patientid, month_at_os_from_treatment, vital_status, 
+  select(patientid, month_at_os, vital_status, 
          raceeth, diagnosisdate, surgerydate,
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
         data = data)
@@
 
-Hazard <- nelsonaalen(data, month_at_os_from_treatment, vital_status)
+Hazard <- nelsonaalen(data, month_at_os, vital_status)
 dataset <- data.frame(data, Hazard)
@@
 Pred <- Cox.imp$predictorMatrix
-# Pred["debulking", "month_at_os_from_treatment"] <- 0
+# Pred["debulking", "month_at_os"] <- 0
 Pred
@@
        exp = coxph(
-         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
        ))
@@
 ```{r}
-hggjgjgkj change the m number
 Cox.imp <- mice(dataset, m=34, maxit=50, 
@@
 Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
+patientid, month_at_os, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
 
@@
   filter(therapy == "Upfront Surgery") %>% 
-  select(patientid, month_at_os_from_treatment, vital_status, 
+  select(patientid, month_at_os, vital_status, 
          raceeth, diagnosisdate, surgerydate,
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
         data = data)
@@
        exp = coxph(
-         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
        ))

### 2022-04-06 Rmd/Actual weight rdi analysis.Rmd
Add Rmd for limited analysis on serous histology OC + fix carbo only analysis

--- 2022-03-31 Rmd/Actual weight rdi analysis.Rmd
@@
 ```{r library, include=FALSE}
-# library(drake)
 library(tidyverse)
@@
 ```{r loadd}
-# loadd(drugs)
 creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
@@
 
-**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
-We have `r Treatment %>% distinct(PatientID) %>% nrow()` patients with cleaned info in drug data.**
+<!-- **We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.   -->
 
@@
 
-- 
 ```{r line coding}
@@
        ))
-pool(check1)$pooled
-```
-
-Do m = 34 (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = 0.339 that we multiply by 100)
-```{r}
-hggjgjgkj change the m number
-Cox.imp <- mice(dataset, m=34, maxit=50, 
+# pool(check1)$pooled
+multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
+```
+
+Do m = `r multiple_imputations_number` (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi.
+The max fmi = `r multiple_imputations_number / 100` that we multiply by 100)
+```{r}
+Cox.imp <- mice(dataset, m= multiple_imputations_number, maxit=50, 
                 predictorMatrix=Pred,
@@
        ))
-pool(check1)$pooled
-```
-
-Do m = 17 (The max fmi = 0.166 that we multiply by 100)
-```{r}
-Cox.imp <- mice(dataset, m=17, maxit=50, 
+# pool(check1)$pooled
+multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
+```
+
+Do m = `r multiple_imputations_number` (The max fmi = `r multiple_imputations_number / 100` that we multiply by 100)
+```{r}
+Cox.imp <- mice(dataset, m= multiple_imputations_number, maxit=50, 
                 predictorMatrix=Pred,
@@
 
+Left is univariable, right is adjusted by each drugs `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,` but not by clinicals.
+
 <div class = "row">
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
+`imp_stagecat + histology + imp_debulking` 
 ```{r Table 5 HR adjusted rdi group}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + imp_stagecat + histology` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
+`imp_stagecat + histology` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
+`imp_stagecat + histology + imp_debulking` 
 ```{r rdi continous}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + imp_stagecat + histology` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
+`imp_stagecat + histology` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ `
+`RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +`
+`raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
 ```{r Table 5 HR adjusted rdi group adjusted by other drug}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ `
+`RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + `
+`raceeth + ageatdx + imp_stagecat + histology` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
+`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
+`raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
 ```{r rdi continous adjusted by other drug}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
+`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
+`raceeth + ageatdx + stagecat + histology` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology + debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp +`
+`raceeth + ageatdx + stagecat + histology + debulking` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + histology` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + `
+`raceeth + ageatdx + stagecat + histology` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology + debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + `
+`raceeth + ageatdx + stagecat + histology + debulking` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx + stagecat + histology` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + `
+`raceeth + ageatdx + stagecat + histology` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ `
+`RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +`
+`raceeth + ageatdx + stagecat + histology + debulking` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ `
+`RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + `
+`raceeth + ageatdx + stagecat + histology` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
+`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
+`raceeth + ageatdx + stagecat + histology + debulking` 
 ```{r }
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
+`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
+`raceeth + ageatdx + stagecat + histology` 
 ```{r}

### 2022-04-06 Rmd/Serous Actual weight rdi analysis.Rmd
Add Rmd for limited analysis on serous histology OC + fix carbo only analysis

--- 2022-04-06 Rmd/Actual weight rdi analysis.Rmd
@@
 
-# `r emo::ji("spiral_notepad")` This report is using **actual weight**
+# `r emo::ji("spiral_notepad")` This report is using **actual weight** in OC with **SEROUS** histology.
 
@@
 
-- exclude patients whose histology is unknown  
+- include patients whose histology of SEROUS CANCER    
 - remove chemotherapy only patients
@@
 study_criteria <- flatiron_rec %>% 
-  filter(!is.na(histology))
+  filter(!is.na(histology)) %>% 
+  filter(histology == "Serous")
 
@@
 Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
+patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
 Look at the Cox regression model before imputation.
@@
          raceeth, diagnosisdate, surgerydate,
-         ageatdx, stagecat, debulking, histology,
+         ageatdx, stagecat, debulking,
          RDI_carbo_neo, RDI_pacli_neo, 
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking,
         data = data)
@@
        exp = coxph(
-         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking
        ))
@@
 Select the variables that may be important for predicting stagecat and debulking status:  
-patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
+patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.
 
@@
          raceeth, diagnosisdate, surgerydate,
-         ageatdx, stagecat, debulking, histology,
+         ageatdx, stagecat, debulking,
          RDI_carbo_adj, RDI_pacli_adj
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking,
         data = data)
@@
        exp = coxph(
-         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking
        ))
@@
     filter(!is.na(histology)) %>%
+    filter(histology == "Serous") %>% 
     filter(!is.na(surgerydate)) %>%
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
-`imp_stagecat + histology + imp_debulking` 
+`imp_stagecat + imp_debulking` 
 ```{r Table 5 HR adjusted rdi group}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
-`imp_stagecat + histology` 
+`imp_stagecat` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
-`imp_stagecat + histology + imp_debulking` 
+`imp_stagecat + imp_debulking` 
 ```{r rdi continous}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
-`imp_stagecat + histology` 
+`imp_stagecat` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +`
-`raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
+`raceeth + ageatdx + imp_stagecat + imp_debulking` 
 ```{r Table 5 HR adjusted rdi group adjusted by other drug}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
              event = tbl2$vital_status
-           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, 
+           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, 
       data =  tbl2)  %>% 
@@
              event = tbl3$vital_status
-           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  
+           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + imp_debulking, data =  
         tbl3) %>%
@@
 `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + `
-`raceeth + ageatdx + imp_stagecat + histology` 
+`raceeth + ageatdx + imp_stagecat` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ### Carbo only
-`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking`
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 
-`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology`
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat`
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
-`raceeth + ageatdx + imp_stagecat + histology + imp_debulking` 
+`raceeth + ageatdx + imp_stagecat + imp_debulking` 
 ```{r rdi continous adjusted by other drug}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl2)  %>%
   cox.zph()
@@
 coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + imp_debulking, data =  tbl3) %>%
   cox.zph()
@@
 `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
-`raceeth + ageatdx + stagecat + histology` 
+`raceeth + ageatdx + stagecat` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp +`
-`raceeth + ageatdx + stagecat + histology + debulking` 
+`raceeth + ageatdx + stagecat + debulking` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + `
-`raceeth + ageatdx + stagecat + histology` 
+`raceeth + ageatdx + stagecat` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + `
-`raceeth + ageatdx + stagecat + histology + debulking` 
+`raceeth + ageatdx + stagecat + debulking` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + `
-`raceeth + ageatdx + stagecat + histology` 
+`raceeth + ageatdx + stagecat` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +`
-`raceeth + ageatdx + stagecat + histology + debulking` 
+`raceeth + ageatdx + stagecat + debulking` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
              event = tbl3$vital_status
-             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
+             ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + debulking, 
         data =  tbl3) %>%
@@
              event = tbl2$vital_status
-           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, 
+           ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + debulking, 
       data =  tbl2)  %>% 
@@
              event = tbl3$vital_status
-           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
+           ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + debulking, 
       data =  tbl3) %>%
@@
 `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + `
-`raceeth + ageatdx + stagecat + histology` 
+`raceeth + ageatdx + stagecat` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 ## Carbo only
-`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking`
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
              event = tbl3$vital_status
-             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, 
+             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(stagecat) + debulking, 
         data =  tbl3) %>%
@@
 ```
-`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology`
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat`
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
-`raceeth + ageatdx + stagecat + histology + debulking` 
+`raceeth + ageatdx + stagecat + debulking` 
 ```{r }
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
 coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>% 
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking, data =  tbl2)  %>% 
   cox.zph()
@@
 coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking, data =  tbl3) %>%
   cox.zph()
@@
 `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
-`raceeth + ageatdx + stagecat + histology` 
+`raceeth + ageatdx + stagecat` 
 ```{r}
@@
   coxph(Surv(time = tbl2$month_at_os_from_treatment, 
-             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>%
+             event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl2) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
@@
   coxph(Surv(time = tbl3$month_at_os_from_treatment, 
-             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>%
+             event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat, data =  tbl3) %>%
   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

### 2022-04-06 Rmd/Serous Adjusted weight rdi analysis.Rmd
Add Rmd for limited analysis on serous histology OC + fix carbo only analysis

--- 2022-04-06 Rmd/Serous Actual weight rdi analysis.Rmd
@@
 
-# `r emo::ji("spiral_notepad")` This report is using **actual weight** in OC with **SEROUS** histology.
+# `r emo::ji("spiral_notepad")` This report is using **adjusted weight** in OC with **SEROUS** histology.
 
@@
 
+ideal_weight is calculated :
+- height <= 1.524               ~ 45.5 + 2.3,
+- height > 1.524                ~ 45.5 + (2.3 * (((`height` - 1.524) / 0.0254)))
+
+adjusted_weight :
+- ((`weight` - `ideal_weight`) * 0.40) + `ideal_weight`
+
+actual_bmi = weight / (height * height)
+
 CrCl calculation :
 
+IF actual_bmi < 25 :
 $$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
-and is capped at 125.  
+IF actual_bmi >= 25 :
+
+$$adjusted\_CrCl = \frac{(140 - ageatdx) * adjusted\_weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
+In both cases CrCl is capped at 125.  
 <br>
@@
 
-<!-- **We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.   -->
+**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.
 
@@
 
-```{r plot interval}
-# Treatment %>% 
-#   ggplot(aes(x= interval_creat)) +
-#   geom_bar() #+
-#   # coord_cartesian(ylim=c(0,50))
-# # Treatment %>% 
-# #   ggplot(aes(x= interval_height)) +
-# #   geom_bar() +
-# #   coord_cartesian(ylim=c(0,50))
-# Treatment %>% 
-#   ggplot(aes(x= interval_weight)) +
-#   geom_bar() #+
-#   # coord_cartesian(ylim=c(0,50))
-# Treatment %>% 
-#   ggplot(aes(x= interval_bsa)) +
-#   geom_bar() #+
-#   # coord_cartesian(ylim=c(0,50))
-# Treatment %>% 
-#   ggplot(aes(x= interval_auc)) +
-#   geom_bar() #+
-#   # coord_cartesian(ylim=c(0,50))
-```
-
 <!-- # Variable for filtering -->
@@
 
-- include patients whose histology of SEROUS CANCER    
+- exclude patients whose histology is unknown  
 - remove chemotherapy only patients
@@
 <br>
-
-# Consort diagram
-
-```{r consort, fig.width=12}
-library(ggconsort)
-study_cohorts <- 
-  Frontline_adjusted %>%
-  cohort_start("**Assessed for eligibility**") %>%
-  # Define cohorts using named expressions
-  # Notice that you can use previously defined cohorts in subsequent steps
-  cohort_define(
-  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),
-
-  study_criteria = flatiron_rec  %>% 
-    filter(!is.na(histology)) %>%
-    filter(histology == "Serous") %>% 
-    filter(!is.na(surgerydate)) %>%
-    filter(had_carbo_pacli == "Yes") %>% 
-    filter(treatment_sequence == "neo + surg + adj" |
-             treatment_sequence == "surg + adj") %>%
-    filter(is.na(line_keep)),
-
-    missing_data = study_criteria  %>% 
-    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
-    filter(is.na(gap_surg_drugs)) %>%
-    filter(days_at_first_drug >= 0 &
-             (is.na(surgerydate) | days_at_surg >= 0)) %>%
-    filter((
-      therapy == "Upfront Chemo" &
-        (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
-           !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
-    ) | (
-      therapy == "Upfront Surgery" &
-        (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
-    )
-    ),
-
-    standard_care = missing_data %>% 
-    filter(is.na(neo_more_more_than_1line)) %>%
-    filter(is.na(frontline_has_maintenance)) %>%
-    filter(is.na(too_many_cycle)) %>% 
-    filter(is.na(wrong_pacli_dosedense)) %>%
-    filter(is.na(switch_drugs)),
-
-    Frontline = standard_care,
-
-  # anti_join is useful for counting exclusions -------------
-    excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
-    excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"),
-    excluded3 = anti_join(study_criteria, missing_data, by = "patientid"),
-    excluded4 = anti_join(missing_data, standard_care, by = "patientid")
-  ) %>%
-  # Provide text labels for cohorts
-  cohort_label(
-    excluded1 = "excluded albeit flatiron recommendation",
-    excluded2 = "<span style='color:darkblue'>no study criteria</span>",
-    excluded3 = "<span style='color:darkblue'>no missing_data</span>",
-    excluded4 = "<span style='color:darkblue'>no standard_care</span>",
-    flatiron_rec = "**Fit flatiron rec**",
-    study_criteria = "**Fit study criteria**",
-    missing_data = "**Non missing data**",
-    Frontline = "**Population Study**"
-  )
-
-study_consort <- study_cohorts %>%
-  consort_box_add(
-    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
-  ) %>%
-  consort_box_add(
-    "exc_flatiron_rec", 0.2, 35, glue::glue(
-      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
-      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
-      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
-      • Borderline cases (not invasive ovarian cancer) <br>
-      • (Data from one PracticeID) <br>
-      • (historical structured data were not available for <br> patients seen at academic sites prior to 2015)
-      ")
-  ) %>%
-  consort_box_add(
-    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
-  ) %>%
-  consort_box_add(
-    "exc_study_criteria", 0.2, 25, glue::glue(
-      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
-      • exclude patients whose histology is unknown <br>
-      • remove chemotherapy only patients <br>
-      • include only patients who received platin and/or taxane <br>
-      • exclude patients who only received neo + surgery <br>
-      • include patients with single or dual P/T +/- Bev as frontline treatment
-      ")
-  ) %>%
-  consort_box_add(
-    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
-  ) %>%
-  consort_box_add(
-    "exc_missing_data", 0.2, 15, glue::glue(
-      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
-      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
-      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
-      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
-      • exclude patients for whose no RDI were available
-      ")
-  ) %>%
-  consort_box_add(
-    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
-  ) %>%
-  consort_box_add(
-    "exc_standard_care", 0.2, 5, glue::glue(
-      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
-      • exclude patients with more than 1 line as Neo <br> 
-      • exclude patients with maintenance within their frontline <br> 
-      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
-      ")
-  ) %>%
-  consort_box_add(
-    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
-  ) %>%
-
-  consort_arrow_add(
-    end = "exc_flatiron_rec", end_side = "left", start_x = 0, start_y = 35
-  ) %>%
-  consort_arrow_add(
-    end = "exc_study_criteria", end_side = "left", start_x = 0, start_y = 25
-  ) %>%
-  consort_arrow_add(
-    end = "exc_missing_data", end_side = "left", start_x = 0, start_y = 15
-  ) %>%
-  consort_arrow_add(
-    end = "exc_standard_care", end_side = "left", start_x = 0, start_y = 5
-  ) %>%
-  consort_arrow_add(
-    end = "Frontline", end_side = "top", start_x = 0, start_y = 40
-  )
-
-study_consort %>%
-  ggplot() + 
-  geom_consort() +
-  theme_consort(margin_h = c(1,6), margin_v = c(0,30))
-```
-
-<br>
-
-***
 
@@
 
-Left is univariable, right is adjusted by each drugs `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,` but not by clinicals.
-
 <div class = "row">
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
-`imp_stagecat + imp_debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp +`
+`raceeth + ageatdx + imp_stagecat + imp_debulking` 
 ```{r Table 5 HR adjusted rdi group}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + `
-`imp_stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + `
+`raceeth + ageatdx + imp_stagecat` 
 ```{r}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
-`imp_stagecat + imp_debulking` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug +`
+`raceeth + ageatdx + imp_stagecat + imp_debulking` 
 ```{r rdi continous}
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +`
-`imp_stagecat` 
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug +`
+`raceeth + ageatdx + imp_stagecat` 
 ```{r}
@@
 
+<br>
+<br>
+
 ### Carbo only
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
-`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
+`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
 `raceeth + ageatdx + imp_stagecat + imp_debulking` 
@@
 `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
-`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
+`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
 `raceeth + ageatdx + stagecat` 
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + `
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug +`
 `raceeth + ageatdx + stagecat` 
@@
 
+<br>
+<br>
+
 ## Carbo only
@@
 
-`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ `
-`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + `
+`coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~`
+`RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +`
 `raceeth + ageatdx + stagecat` 

### 2022-05-18 Rmd/Manuscript rdi analysis.Rmd
Start updated html for manuscript

---
title: "Flatiron cleaning"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 1px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```
<br>

***

```{r library, include=FALSE}
library(tidyverse)
library(data.table)
library(lubridate)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
library(mice)
```

```{r loadd}
creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
weight <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/weight.rds")
height <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/height.rds")
body_surface_area <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/body_surface_area.rds")
areaUC <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/areaUC.rds")
clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
Treatment <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/Treatment.rds")
```

# `r emo::ji("spiral_notepad")` This report is using **actual weight**  
<!-- For serous and non serous histology un-comment line 414 -->
***

# `r emo::ji("spiral_notepad")` Reminders of each capping and formula:

Creatinine data are capped as :  
- creat < 0.7 was set at 0.7  
- creat > 3 are eliminated

CrCl calculation :

$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
and is capped at 125.  
<br>

Calculating more BSA values :
$$bsa\_du\_bois = 0.007184 * (height*100)^{0.725} * weight^{0.425}$$
<br>

I clean the data up by keeping the `relativeorderedamount`:  
- >= 50 & <= 175 for taxel and cisplatin  and with a unit in `mg/m2`  
- >= 2  & <= 6   for platin and with a unit in `AUC`

<br>

`expected_dose` is:  
-`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
-`BSA` * `target_auc`           -> for `drugname` == "taxel" or "cisplatin"  
(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).

<br>

Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ given}{expected\ dose}$$

<br>

<span style="color:red">**Please confirm everything is correct**</span>

***

# I. Drug episode cleaning

- Select episodedatasource == "Administrations"

- Combine multiple administrations of the same drug at the same date
Flatiron says:
There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.  
For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.  
Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.   
Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.

<br>

- Bind everything together to calculate target auc/target dose and expected dose

(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and paclitaxel, they are just present in the same column called `target_auc` for a tidy data organization - You can find the calculations formula at the end of the document)  
When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, and paclitaxel and their `expected_dose`. It can be days in between but it can also be more.

`r emo::ji("check")`  
We decided to take the creatinine, weight, bsa measured within a month of the cycle start date AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line

<!-- # Variable for filtering -->

```{r RDI calculation}
Treatment <- Treatment %>% 
  # filter(chemotherapy_type == "Neoadjuvant" |
  #          (chemotherapy_type == "Adjuvant" &
  #             linenumber_adj == 1)) %>%

  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
  ) %>%
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup()

RDI_data <- Treatment %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))
```

```{r RDI calculation group}
RDI_data <- RDI_data %>% 
  # general
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
    mean_RDI_per_drug < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  # separated
  mutate(RDI_carbo_neo = case_when(
    drugname == "carboplatin" &
      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_pacli_neo = case_when(
    drugname == "paclitaxel" &
      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_carbo_adj = case_when(
    drugname == "carboplatin" &
      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_pacli_adj = case_when(
    drugname == "paclitaxel" &
      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>%

  mutate(RDI_carbo_neo_grp = case_when(
    RDI_carbo_neo >= 0.85              ~ "Adequate dosing",
    RDI_carbo_neo < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_carbo_neo_grp = factor(RDI_carbo_neo_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_pacli_neo_grp = case_when(
    RDI_pacli_neo >= 0.85              ~ "Adequate dosing",
    RDI_pacli_neo < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_pacli_neo_grp = factor(RDI_pacli_neo_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_carbo_adj_grp = case_when(
    RDI_carbo_adj >= 0.85              ~ "Adequate dosing",
    RDI_carbo_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_carbo_adj_grp = factor(RDI_carbo_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_pacli_adj_grp = case_when(
    RDI_pacli_adj >= 0.85              ~ "Adequate dosing",
    RDI_pacli_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_pacli_adj_grp = factor(RDI_pacli_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed")))
RDI_data %>% distinct(patientid) %>% nrow()
```

```{r RDI_data}
RDI_data <- RDI_data %>% 
  group_by(patientid) %>% 
  fill(RDI_carbo_neo, RDI_carbo_neo_grp, 
       RDI_pacli_neo, RDI_pacli_neo_grp, 
       RDI_carbo_adj, RDI_carbo_adj_grp, 
       RDI_pacli_adj, RDI_pacli_adj_grp, 
       .direction = "downup") %>% 
  ungroup()
Frontline_adjusted <- RDI_data %>% 
  distinct(patientid, .keep_all = TRUE)
```
<br>
<br>

# **Number of patients : `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**

######################################################################################################################
######################################################################################################################
######################################################################################################################
######################################################################################################################

<!-- # Variable for filtering -->

<!-- ```{r rule between diagnosis and treatment} -->
<!-- drugs1 <- Frontline_adjusted %>%  -->
<!--   # 1. 60 days rule between diagnosis and treatment # Loss 1 -->
<!--   group_by(patientid) %>%  -->
<!--   mutate(first_drug_date = first(episodedate)) %>%  -->
<!--   mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/ -->
<!--            duration(n=1, units = "days")) %>%  -->
<!--   mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/ -->
<!--            duration(n=1, units = "days")) %>%  -->
<!--   ungroup() %>%  -->
<!--   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/ -->
<!--            duration(n=1, units = "days") -->
<!--   ) -->
<!-- ``` -->

<br>

## 1. step 1: Flatiron recommendation cleanup

This step is to remove patients from the population that don't follow flatiron recommendations.

- 90 days rule between diagnosis and treatment  
Flatiron propose a conceptual instruction on the 90-day-gap : 90 days between diagnosis and treatment.  
It is meant to exclude patients who didn't get treatment for 90 days which would most likely mean that some treatment data are missing. Patients left after this step:

- 30 days rule excluding patient who didn't survive for at least 30 days after diagnosis  
This is something that Flatiron strongly recommends, but does not require. Flatiron proposal reviewers will likely provide comments on this if not incorporated into a proposal.

- Exclude exclude == "1" coded by Lauren

Are excluded :  
-	Borderline cases (not invasive ovarian cancer)  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
flatiron_rec <- Frontline_adjusted %>% 
  filter(is.na(flatiron_rules))
```

**At the end of the step 1, we have `r flatiron_rec %>% distinct(patientid) %>% nrow()` patients.**

<br>

## 2. step 2: Filter patients with clinical characteristics fitting to the study criteria

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(!is.na(histology)) # %>% 
  # filter(histology == "Serous")

study_criteria <- study_criteria %>%
  filter(!is.na(surgerydate)) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type))

study_criteria <- study_criteria %>%
  filter(had_carbo_pacli == "Yes")

study_criteria <- study_criteria %>% 
  filter(treatment_sequence == "neo + surg + adj" |
           treatment_sequence == "surg + adj")

study_criteria <- study_criteria %>%
  filter(is.na(line_keep))
```

**At the end of the step 2, we have `r study_criteria %>% distinct(patientid) %>% nrow()` patients.**

<br>

## 3. step 3: Filter out patients with missing data

- exclude the patients who had surgery but we don't have a date of surgery -> NONE removed anymore  
- remove patients with long gap between surgery and adjuvant start (3  months) -> NONE removed anymore  
- exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
- exclude patients for whose no RDI were available

```{r}
missing_data <- study_criteria %>% 
  filter(!(issurgery == "Yes" & is.na(surgerydate)))

missing_data <- missing_data %>%
  filter(is.na(gap_surg_drugs))

missing_data <- missing_data %>% 
  filter(days_at_first_drug >= 0 &
           (is.na(surgerydate) | days_at_surg >= 0)
         )

missing_data <- missing_data %>% 
  # remove these patients who switched C > C 
  filter((
    therapy == "Upfront Chemo" &
      (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
         !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
  ) | (
    therapy == "Upfront Surgery" &
      (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
  )
  )
```
**At the end of the step 3, we have `r missing_data %>% distinct(patientid) %>% nrow()` patients.**

## 4. step 4: Include patients with treatments following the standard of clinical care

- exclude patients with more than 1 line as Neo
- exclude patients with maintenance within their frontline
- exclude patients with more than 6 cycles in Neo, more than 9 cycles **total** in upfront chemo or more than 9 cycles in upfront surgery
- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
- exclude patients who switch drug within a line
```{r}
standard_care <- missing_data %>% 
  # Remove patients with more than 1 line as Neo
  filter(is.na(neo_more_more_than_1line))

standard_care <- standard_care %>% 
  filter(is.na(frontline_has_maintenance))

standard_care <- standard_care %>% 
  filter(is.na(too_many_cycle))

standard_care <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

Frontline <- standard_care %>%
  filter(is.na(switch_drugs))
```

<!-- TABLES -->

```{r}
# missing_data %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(had_neo, had_adj, therapy) %>% 
#   tbl_summary(by = therapy,
#               type = list(had_neo ~ "dichotomous", 
#                           had_adj ~ "dichotomous"),
#               missing = "no")
# # therapy_line %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(therapy, treatment_sequence) %>% 
# #   tbl_summary(by = therapy)
```

<!-- First table is frontline Neo, second table is frontline Adj. -->
```{r}
# # drugs1 %>% Need to do in Frontline
#   filter(linenumber == 1
#          ) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))
# 
# # missing_data %>% 
# #   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(linename) %>% 
# #   tbl_summary(sort = list(everything() ~ "frequency"))
```

<!-- ### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line -->
```{r Number of patient who switch line}
# therapy_line %>% 
#   mutate(change_line = case_when(
#     linenumber == 1 & 
#       linenumber_new == 2 &
#       chemotherapy_type == "Adjuvant" &
#       therapy == "Upfront Chemo"                   ~ 1,
#     TRUE                                           ~ 0
#   )) %>% 
#   arrange(desc(change_line)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(change_line) %>% 
#   tbl_summary()
```

<!-- For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line? -->
```{r}
# therapy_line %>% 
#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
#            duration(n = 1, units = "days")) %>% 
#   filter(linenumber == 1 & linenumber_new == 2) %>% 
#   # select(patientid, linenumber, linenumber_new, linenumber_adj, 
#   #        drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x= line_duration))+
#   geom_histogram(aes(fill = route), binwidth = 7) +
#   theme_minimal(base_size = 14)+
#   labs(x="Line duration", 
#        y="Number of Patient",
#        caption = "Each bar represents 7 days, bottom plot is zoomed in")+
#   ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
```
<!-- Several patients have a short line.   -->
<!-- `r emo::ji("question_mark")` **Should we remove the patient with a line lasting less than a cycle** We said during October meeting to check if were IP administration.... -->

```{r}
# therapy_line %>% 
#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
#            duration(n = 1, units = "days")) %>% 
#   filter(linenumber == 1 & linenumber_new == 2) %>% 
#   select(patientid, surgerydate, episodedate, line_duration, drugname,
#          chemotherapy_type, therapy, 
#          linenumber, linenumber_new, route, amount) %>% 
#   filter(line_duration < 30) %>% 
#   arrange(line_duration, patientid, episodedate)
```

<!-- Here a real example of this type of patient : initial `linenumber` = 1 but had surgery in 09/2019 so part of this line in moved to `linenumber_new` = 2 and then coded as adjuvant line.   -->
<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle. <span style="color:red">**Is that correct?**</span>   -->
```{r Number of patient who switch line2, rows.print=30}
# Problem F0000AD999ABF but would be good for F003F2BEEDB37
# therapy_line %>% 
#   filter(str_detect(patientid, "F41E15E18E008")) %>% 
#   arrange(patientid, episodedate) %>% 
#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
```

<!-- Here an example a little more complicated because the patient had surgery 05/2017 and the same type of switch but then had a 3rd line (used to be line 2 in flatiron).     -->
<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle switched to adjuvant and not the longer line witch was coded 2 by flatiron. <span style="color:red">**Is that correct?**</span>   -->
```{r, rows.print=30}
# therapy_line %>% 
#   filter(str_detect(patientid, "FC9D28216FEBE")) %>% 
#   arrange(patientid, episodedate) %>% 
#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)

# therapy_line %>% 
#   mutate(change_line = case_when(
#     linenumber == 1 & 
#       linenumber_new == 2 &
#       chemotherapy_type == "Adjuvant" &
#       treatment_sequence == "neo + surg + adj"     ~ 1,
#     TRUE                                           ~ 0
#   )) %>% 
#   filter(change_line == 1) %>% 
#   group_by(patientid) %>% 
#   mutate(firstdate = first(episodedate)) %>% 
#   mutate(lastdate = last(episodedate)) %>% 
#   ungroup() %>% 
#   mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x=time_of_switch_line, fill = ..count..))+
#   geom_histogram(binwidth = 7)+
#   theme_minimal(base_size = 14)+
#   ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
#   scale_y_continuous(#breaks=c(0, 50, 100, 150),
#                      minor_breaks=c(10, 20, 30, 40)#,
#                      #labels = c(0, 50, 100, 150)
#   )
```
<!-- `r emo::ji("question_mark")`   -->
<!-- <span style="color:red">**So the bigger question is : Is it acceptable to include the patients who have a switched line?**</span> -->

<!-- <span style="color:red">**Random question : within 1 cycle we can have taxanes multiple times, is it possible for carboplatin or cisplatin?**</span>   -->

<br>
<br>

# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**

Imputation for stagecat and debulking status

https://bookdown.org/mwheymans/bookmi/data-analysis-after-multiple-imputation.html#data-analysis-in-spss
https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
Look at the Cox regression model before imputation.

### For Upfront Chemo
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
# nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os_from_treatment, vital_status)
dataset <- data.frame(data, Hazard)
```

<!-- Start imputation to look at matrix -->
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os_from_treatment"] <- 0
# Pred
```

<!-- patientid is not used which is good. But SURGERYDATE IS NOT. -->
```{r}
Pred[, "surgerydate"] <- 1
Pred["surgerydate", "surgerydate"] <- 0
# Pred
```

<!-- Imputation and cox regression model on imputed data using the new predictor matrix. -->
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

Do m = `r multiple_imputations_number` (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = `r multiple_imputations_number / 100` that we multiply by 100)
```{r}
Cox.imp <- mice(dataset, m= multiple_imputations_number, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

# summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
#   kableExtra::kable() %>%
#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
<!-- Above results are exponentiated (imputed data).   -->
<!-- As a reminder before imputation results are : -->
```{r}
# nonimp_cox_model
```

<!-- Complete the chemo data and merge with original -->
```{r}
imputed_data_chemo <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_stagecat = stagecat, imp_debulking = debulking)
```

### For Upfront Surgery
Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.

```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
# nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os_from_treatment, vital_status)
dataset <- data.frame(data, Hazard)
```

<!-- Start imputation to look at matrix -->
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os_from_treatment"] <- 0
# Pred
```

<!-- patientid is not used which is good. But SURGERYDATE IS NOT -->
```{r}
Pred[, "surgerydate"] <- 1
Pred["surgerydate", "surgerydate"] <- 0
# Pred
```

<!-- Imputation and cox regression model on imputed data using the new predictor matrix. -->
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

Do m = `r multiple_imputations_number` (The max fmi = `r multiple_imputations_number / 100` that we multiply by 100)
```{r}
Cox.imp <- mice(dataset, m= multiple_imputations_number, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

# summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
#   kableExtra::kable() %>%
#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
<!-- Above results are exponentiated (imputed data).   -->
<!-- As a reminder before imputation results are : -->
<!-- ```{r} -->
<!-- nonimp_cox_model -->
<!-- ``` -->

<!-- Complete the data and merge with original -->
```{r}
imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_stagecat = stagecat, imp_debulking = debulking)

imputed_data <- bind_rows(imputed_data_chemo, imputed_data_surg)

Frontline <- 
  full_join(Frontline, imputed_data %>% 
              select(patientid, starts_with("imp_")), 
            by = "patientid") 
```
<br>

***

<br>

# <span style="color:green">**Consort diagram**</span>

```{r consort, fig.width=12}
library(ggconsort)
study_cohorts <- 
  Frontline_adjusted %>%
  cohort_start("**Assessed for eligibility**") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

  study_criteria = flatiron_rec  %>% 
    filter(!is.na(histology)) %>%
    filter(!is.na(surgerydate)) %>%
    filter(had_carbo_pacli == "Yes") %>% 
    filter(treatment_sequence == "neo + surg + adj" |
             treatment_sequence == "surg + adj") %>%
    filter(is.na(line_keep)),

    missing_data = study_criteria  %>% 
    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
    filter(is.na(gap_surg_drugs)) %>%
    filter(days_at_first_drug >= 0 &
             (is.na(surgerydate) | days_at_surg >= 0)) %>%
    filter((
      therapy == "Upfront Chemo" &
        (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
           !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
    ) | (
      therapy == "Upfront Surgery" &
        (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
    )
    ),

    standard_care = missing_data %>% 
    filter(is.na(neo_more_more_than_1line)) %>%
    filter(is.na(frontline_has_maintenance)) %>%
    filter(is.na(too_many_cycle)) %>% 
    filter(is.na(wrong_pacli_dosedense)) %>%
    filter(is.na(switch_drugs)),

    Frontline = standard_care,

  # anti_join is useful for counting exclusions -------------
    excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
    excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"),
    excluded3 = anti_join(study_criteria, missing_data, by = "patientid"),
    excluded4 = anti_join(missing_data, standard_care, by = "patientid")
  ) %>%
  # Provide text labels for cohorts
  cohort_label(
    excluded1 = "excluded albeit flatiron recommendation",
    excluded2 = "<span style='color:darkblue'>no study criteria</span>",
    excluded3 = "<span style='color:darkblue'>no missing_data</span>",
    excluded4 = "<span style='color:darkblue'>no standard_care</span>",
    flatiron_rec = "**Fit flatiron rec**",
    study_criteria = "**Fit study criteria**",
    missing_data = "**Non missing data**",
    Frontline = "**Population Study**"
  )

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "exc_flatiron_rec", 0.2, 35, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
      • Borderline cases (not invasive ovarian cancer) <br>
      • (Data from one PracticeID) <br>
      • (historical structured data were not available for <br> patients seen at academic sites prior to 2015)
      ")
  ) %>%
  consort_box_add(
    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
  ) %>%
  consort_box_add(
    "exc_study_criteria", 0.2, 25, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
      • exclude patients whose histology is unknown <br>
      • remove chemotherapy only patients <br>
      • include only patients who received platin and/or taxane <br>
      • exclude patients who only received neo + surgery <br>
      • include patients with single or dual P/T +/- Bev as frontline treatment
      ")
  ) %>%
  consort_box_add(
    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "exc_missing_data", 0.2, 15, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
      • exclude patients for whose no RDI were available
      ")
  ) %>%
  consort_box_add(
    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "exc_standard_care", 0.2, 5, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
      • exclude patients with more than 1 line as Neo <br> 
      • exclude patients with maintenance within their frontline <br> 
      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
      ")
  ) %>%
  consort_box_add(
    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%

  consort_arrow_add(
    end = "exc_flatiron_rec", end_side = "left", start_x = 0, start_y = 35
  ) %>%
  consort_arrow_add(
    end = "exc_study_criteria", end_side = "left", start_x = 0, start_y = 25
  ) %>%
  consort_arrow_add(
    end = "exc_missing_data", end_side = "left", start_x = 0, start_y = 15
  ) %>%
  consort_arrow_add(
    end = "exc_standard_care", end_side = "left", start_x = 0, start_y = 5
  ) %>%
  consort_arrow_add(
    end = "Frontline", end_side = "top", start_x = 0, start_y = 40
  )

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = c(1,6), margin_v = c(0,30))
```
<br>

***

# II.Data analysis
## Explore the dataset

```{r}
full_data_study_pop <- 
  Treatment %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname)
```

<!-- ### Number of line /cycle received by patients in our study population  -->

<!-- <span style="color:green">**Table supp X Number of total line**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>%  -->
<!--   arrange(desc(linenumber_new)) %>%  -->
<!--   distinct(patientid, .keep_all = TRUE) %>%  -->
<!--   select(linenumber_new, therapy) %>%  -->
<!--   tbl_summary(by = therapy) -->
<!-- ``` -->

<!-- <span style="color:green">**Table supp X Number of cycle in Neo**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>%  -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment) %>%  -->
<!--   tbl_summary() -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>%  -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment) %>%  -->
<!--   tbl_summary(type = list(cycle_increment ~ "continuous")) -->
<!-- ``` -->

<!-- <span style="color:green">**Table supp X Number of cycle in Adj**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>%  -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment, therapy) %>%  -->
<!--   tbl_summary(by = therapy) -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>%  -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment, therapy) %>%  -->
<!--   tbl_summary(by = therapy, -->
<!--               type = list(cycle_increment ~ "continuous")) -->
<!-- ``` -->
<!-- <br> -->

<!-- ## Missingness -->
<!-- Here some representation of missingness in our data:   -->
<!-- - In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx). Because these parameters overlap only 25 patients will have missing value for all of them.    -->
<!-- - In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation). the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose. -->
```{r}
# library(naniar)
# 
# Frontline %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
#   gg_miss_upset()

# is.na(Frontline$CrCl) %>% sum()
# is.na(Frontline$amount) %>% sum()
# is.na(Frontline$target_auc) %>% sum()

# Frontline %>% filter(is.na(amount)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
# 
# Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>%
#     distinct(patientid, .keep_all = TRUE) %>% nrow()
```
<!-- If we remove patients who have at least 1 missing amount administered, we lose `r Frontline %>% filter(is.na(amount)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.   -->

<!-- If we remove patients who are missing at least 1 target_auc or 1 expected dose we lose `r Frontline %>% filter(is.na(target_auc) | is.na(expected_dose)) %>% distinct(patientid, .keep_all = TRUE) %>% nrow()` patients.   -->

<br>
<br>

***

# Clinical Analysis

## ICC between cycles
```{r}
full_data_study_pop

```

## 1.Clinical summary table

<span style="color:green">**Table X Overall summary demographic/clinical data**</span>
```{r Table 1}
Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(vital, raceeth, 
           agecat, "ageatdx",

           bmi_at_dx, bmi_cat, 
           weight_at_dx, height_at_dx, bsa_at_dx,

           histology1, "histology", "stagecat", imp_stagecat,

           "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor",
           "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown")) %>% 
  tbl_summary() %>% bold_labels()
```

<span style="color:green">**Table X Summary demographic/clinical data by race**</span>
```{r Table 2}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",

           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat", imp_stagecat)) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

## <span style="color:green">**Table 1 Summary demographic/clinical data by bmi**</span>
```{r Table 3}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, "vital",
           agecat, "ageatdx",
            histology1, "histology",
           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat", imp_stagecat,
           therapy, debulking, imp_debulking)) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

<!-- ## 2.Clinical Plots -->

<br>

<!-- ## 3.Survivals by clinical -->

<!-- <span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the right**</span>   -->

<!-- <div class = "row"> -->
<!-- <div class = "col-md-6"> -->
<!-- ```{r clinical from dx, fig.height = 7} -->
<!-- # OS by raceeth -->
<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ raceeth, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 2)) -->

<!-- # OS by tstage -->
<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ stagecat, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 2)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_stagecat, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 2)) -->

<!-- # OS by bmi_cat -->
<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ bmi_cat, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 2)) -->
<!-- ``` -->
<!-- </div> -->

<!-- <div class = "col-md-6"> -->
<!-- ```{r clinical from first treatment, fig.height = 7} -->
<!-- # OS by raceeth -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ raceeth, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of first treatment",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 2)) -->

<!-- # OS by tstage -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ stagecat, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of first treatment",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 2)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_stagecat, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of first treatment",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 2)) -->

<!-- # OS by bmi_cat -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ bmi_cat, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of first treatment",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 2)) -->
<!-- ``` -->
<!-- </div> -->
<!-- </div> -->

<!-- <br> -->
<!-- <br> -->

***

<br>

# II.Treatment Analysis

## 1.Treatment summary table

<span style="color:green">**Table X Summary treatment data by race**</span>
```{r Table 4}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth,
           "debulking", imp_debulking , "therapy"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```
<br>

<span style="color:green">**Table X Summary treatment data by bmi**</span>
```{r Table 5}
Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(bmi_cat,
           "debulking", imp_debulking, "therapy"
           )) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
```

## <span style="color:green">**Table S0 Summary of the expected, actual dose, and RDI, Crcl, ...**</span>
Here we calculated the mean of amount, CrCl, BSA, height, weight, creatinine,
         target_auc, expected_dose, dose received, 
         RDI per patient/therapy/settings for each drug name.  
The tables show the median IQR for carboplatin calculated over patients with the same therapy (Upfront C or S) and setting (Neo or Adj).
```{r Summary of the expected, actual dose, and RDI}
tbl <- full_data_study_pop %>% 
  group_by(patientid, therapy, chemotherapy_type, drugname) %>% 
  summarise(amount = mean(amount), 
            BSA = mean(BSA), 
            height = mean(height), 
            weight = mean(weight), 
            creatinine = mean(creatinine),
            CrCl = mean(CrCl),
            target_auc = mean(target_auc),
            expected_dose = mean(expected_dose),
            relative_dose_intensity = mean(mean_RDI_per_drug)) %>% 
  ungroup() %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant")))

tbl %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>% 
  select(amount, CrCl, BSA, height, weight, creatinine,
         target_auc, expected_dose, "dose received" = amount, 
         "RDI" = relative_dose_intensity, chemotherapy_type) %>% 
  tbl_summary(by = chemotherapy_type) %>% bold_labels() %>%
  modify_caption("**Upfront Chemo**")

tbl %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>% 
  select(amount, CrCl, BSA, height, weight, creatinine,
         target_auc, expected_dose, "dose received" = amount, 
         "RDI" = relative_dose_intensity) %>% 
  tbl_summary() %>% bold_labels() %>%
  modify_caption("**Upfront Surgery**")
```
<br>

<!-- ## 2.Treatment Plots -->
<div class = "row">
<div class = "col-md-6">
```{r treatment plots}
full_data_study_pop %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(label = list(linename ~ "line name received as Neoadujant"))
full_data_study_pop %>% 
  filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename, therapy) %>% 
  tbl_summary(by = therapy,
              label = list(linename ~ "line name received as Adjuvant"))
```
</div>

<div class = "col-md-6">
```{r}
full_data_study_pop %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  group_by(patientid, drugname) %>% 
  summarise(CrCl = mean(CrCl),
            target_auc = mean(target_auc),
            expected_dose = mean(expected_dose)) %>% 
  ungroup() %>% 
  distinct(patientid, drugname, .keep_all = TRUE) %>% 
  select(CrCl, target_auc, expected_dose, drugname) %>% 
  tbl_summary(by = drugname,
              label = list(CrCl ~ "Average CrCl during Neoadujant setting",
                           target_auc ~ "Target dose (AUC or mg/mg2)",
                           expected_dose ~ "Expected dose")
    )
```
</div>
</div>

<br>

## 3.Survivals by treatment

<div class = "row">
<div class = "col-md-6">
```{r treatment survival, fig.height = 7}
ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ 1, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ debulking, data=Frontline %>%
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_debulking, data=Frontline %>%
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 1))

# OS by therapy
ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ therapy, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))
```
</div>

<div class = "col-md-6">
```{r, fig.height = 7}
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ 1, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of from first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ debulking, data=Frontline %>%
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of from first treatment",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_debulking, data=Frontline %>%
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of from first treatment",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 1))

# OS by therapy
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ therapy, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of from first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 1))
```
</div>
</div>

<br>
<br>

***

<br>

# III.RDI
RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.

```{r echo=TRUE}
# RDI_grp = case_when(
#     mean_RDI_per_drug >= 0.85              ~ "adequate",
#     mean_RDI_per_drug < 0.85               ~ "underdose"
#   ))
```
Start with plotting :

## 1.Plots RDI
## <span style="color:green">**Figure 1: Ridge**</span>  
You said to limint the x axis at 2 but we will lose the little bump....Do you want 2?  
Do you want the blue and red lines?
```{r ggridges, fig.width=16, fig.height=18}
library(ggridges)
# Frontline %>% 
#   pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>% 
#   filter(!is.na(value)) %>% 
#   ggplot(aes(y=raceeth, x=value,  fill=raceeth
#              )) +
#     geom_density_ridges(alpha=0.5) +
#     theme_ridges()+
#   theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
#         panel.spacing = unit(0.1, "lines"),
#         strip.text.x = element_text(size = 14)
#     ) +
#   geom_vline(xintercept = 1, color = "red", linetype = 2)+
#   geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+
# 
#   facet_wrap(therapy ~ name, ncol = 2, scales = "free_x")

Frontline %>% 
  pivot_longer(cols = c(RDI_carbo_neo, RDI_carbo_adj),
               values_to = "RDI") %>% 
  filter(!is.na(RDI)) %>% 
  ggplot(aes(y=bmi_cat, x=RDI,  fill=bmi_cat
             )) +
    geom_density_ridges(alpha=0.5) +
    theme_ridges()+
  theme(#text = element_text(size = 14),#axis.text.y = element_blank(),
        panel.spacing = unit(0.1, "lines"),
        strip.text.x = element_text(size = 14)
    ) +
  geom_vline(xintercept = 1, color = "red", linetype = 2)+
  geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+

  facet_wrap(therapy ~ name, ncol = 1)
```

## 2.RDI summary table

```{r}
my_theme <-
  list(
    # Some gt customization
    "as_gt-lst:addl_cmds" = list(
      # make the font size small
      tab_spanner = rlang::expr(gt::tab_options(row.striping.background_color = "lightgrey",
                                                row.striping.include_stub = TRUE,
                                                row.striping.include_table_body = TRUE,
                                                row_group.border.top.color = "blue",
                                                # table.background.color = "white", 
                                                heading.background.color = "lightblue", 
                                                # column_labels.background.color = "orange", 
                                                row_group.background.color = "grey",
                                                stub.background.color = "slateblue", 
                                                summary_row.background.color = "tomato", 
                                                grand_summary_row.background.color = "green")),
      # add a custom title and subtitle to every table
      # user_added1 = rlang::expr(gt::tab_header(
      #   title = "Christelle's Table", subtitle = "Yeap"))#,
      # add a custom data source note
      # user_added2 = rlang::expr(gt::tab_source_note(
      #   source_note = "Source: our data!"))#,
      # stripe the table rows
      user_added1 = rlang::expr(gt::opt_row_striping())#,
      # user_added4 = rlang::expr(gt::opt_table_lines("none"))
      )
    )

reset_gtsummary_theme()
set_gtsummary_theme(my_theme)

# trial %>%
#   select(age, grade, trt) %>%
#   tbl_summary(by = trt) %>%
#   add_stat_label() %>%
#   add_p() %>%
#   as_gt() 
```

<!-- <span style="color:green">**Table X: RDI summary table**</span>   -->
```{r Table summary Platin}
# tbl1 <- Frontline %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI (continous)" = RDI_carbo_neo, "RDI (categorical)" = RDI_carbo_neo_grp, therapy)) %>%
#   tbl_summary(by = therapy) %>% 
#   bold_labels() %>% add_n() %>% add_overall()
# 
# tbl2 <- Frontline %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI (continous)" = RDI_carbo_adj, "RDI (categorical)" = RDI_carbo_adj_grp, therapy)) %>%
#   tbl_summary(by = therapy) %>%
#   bold_labels() %>% add_n() %>% add_overall()
# 
# tbl3 <- Frontline %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
#   tbl_summary(by = therapy
#               ) %>%
#   bold_labels() %>% add_n() %>% add_overall()
# 
# tbl4 <- Frontline %>% 
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
#   tbl_summary(by = therapy
#               ) %>%
#   bold_labels() %>% add_n() %>% add_overall()
# tbl5 <- Frontline %>% filter(dose_dense == 3) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI (continous)" = RDI_pacli_neo, "RDI (categorical)" = RDI_pacli_neo_grp, therapy)) %>%
#   tbl_summary(by = therapy,
#               type = list(`RDI (continous)` ~ "continuous")) %>%
#   bold_labels() %>% add_n() %>% add_overall()
# tbl6 <- Frontline %>% filter(dose_dense == 3) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI (continous)" = RDI_pacli_adj, "RDI (categorical)" = RDI_pacli_adj_grp, therapy)) %>%
#   tbl_summary(by = therapy,
#               type = list(`RDI (continous)` ~ "continuous")) %>%
#   bold_labels() %>% add_n() %>% add_overall()
# 
# # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>%
# #   modify_spanning_header(everything() ~ NA_character_)
# tbl_stack(list(tbl1, tbl2, tbl3, tbl4, tbl5, tbl6),
#           group_header = c(
#                            "Carboplatin Neo", 
#                            "Carboplatin Adj",
#                            "Paclitaxel overall Neo",
#                            "Paclitaxel overall Adj",
#                            "Paclitaxel dose dense Neo",
#                            "Paclitaxel dose dense Adj"),
#           quiet = TRUE)
```

```{r}
# reset_gtsummary_theme()
```

```{r Table summary Taxanes}
# tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c(RDI_carbo_neo, RDI_carbo_neo_grp, therapy)) %>%
#   tbl_summary(by = therapy) %>% 
#   bold_labels()
# 
# tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c(RDI_carbo_adj, RDI_carbo_adj_grp, therapy)) %>%
#   tbl_summary(by = therapy) %>%
#   bold_labels()
# tbl4 <- tbl_stack(list(tbl1, tbl2),
#           group_header = c(
#                            "paclitaxel Neo/Upfront Chemo",
#                            "paclitaxel Adj/Upfront Chemo"),
#           quiet = TRUE)
# 
# 
# tbl3 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c(RDI_carbo_adj, RDI_carbo_adj_grp, therapy)) %>%
#   tbl_summary(by = therapy) %>%
#   bold_labels()
# tbl_merge(list(tbl4, tbl3), tab_spanner = c("Overall", "Dose dense 1+3"))

####
# tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo" &
#                                dose_dense == 3) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>%
#   tbl_summary() %>%
#   bold_labels()

# tbl5 <- Frontline %>% filter(therapy == "Upfront Chemo" &
#                                dose_dense == 3) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
#   tbl_summary() %>%
#   bold_labels()
# tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery" &
#                                dose_dense == 3) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(c("RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>%
#   tbl_summary(
#               type = list(RDI ~ "continuous")) %>%
#   bold_labels()

# tbl8 <- tbl_merge(list(tbl2, tbl4))
# tbl9 <- tbl_merge(list(tbl3, tbl6), tab_spanner = c("Overall", "Dose dense 1+3"))

# tbl_stack(list(tbl1, tbl2, tbl3, tbl6),
#           group_header = c(
#                            "paclitaxel Neo/Upfront Chemo", 
#                            "paclitaxel Adj/Upfront Chemo",
#                            "paclitaxel Adj/Upfront Surgery",
#                            "dose dense paclitaxel Adj/Upfront Surgery"),
#           quiet = TRUE)
```
<br>

## <span style="color:green">**Table 2: Summary RDI data by race and bmi**</span>  
Platin  
```{r Table 7 Summary RDI data by race and bmi}
tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
  modify_caption("**Upfront Chemo**")
tbl8 <-
  tbl_merge(list(tbl3, tbl4))
tbl_stack(list(tbl7, tbl8),
          group_header = c(
                           "carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo"),
          quiet = TRUE)

tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)
tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05)

# tbl9 <-
  tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
  modify_caption("**Upfront Surgery**")
```
<br>

<!-- Taxanes -->
<!-- ```{r Table4 summary Taxanes} -->
<!-- tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(c(raceeth, "RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>% -->
<!--   tbl_summary(by = raceeth) %>% -->
<!--   bold_labels() %>%  -->
<!--   add_p() %>% bold_p(t= 0.05) -->
<!-- tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(c(bmi_cat, "RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>% -->
<!--   tbl_summary(by = bmi_cat) %>% -->
<!--   bold_labels() %>%  -->
<!--   add_p() %>% bold_p(t= 0.05) -->

<!-- tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>% -->
<!--   tbl_summary(by = raceeth) %>% -->
<!--   bold_labels() %>%  -->
<!--   add_p() %>% bold_p(t= 0.05) -->
<!-- tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>% -->
<!--   tbl_summary(by = bmi_cat) %>% -->
<!--   bold_labels() %>%  -->
<!--   add_p() %>% bold_p(t= 0.05) -->
<!-- tbl7 <- -->
<!--   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI")) -->
<!-- tbl8 <- -->
<!--   tbl_merge(list(tbl3, tbl4)) -->
<!-- tbl_stack(list(tbl7, tbl8), -->
<!--           group_header = c( -->
<!--                            "paclitaxel Neo/Upfront Chemo",  -->
<!--                            "paclitaxel Adj/Upfront Chemo"), -->
<!--           quiet = TRUE) -->
<!-- tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>% -->
<!--   tbl_summary(by = raceeth) %>% -->
<!--   bold_labels() %>%  -->
<!--   add_p() %>% bold_p(t= 0.05) -->
<!-- tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>% -->
<!--   tbl_summary(by = bmi_cat) %>% -->
<!--   bold_labels() %>%  -->
<!--   add_p() %>% bold_p(t= 0.05) -->

<!-- tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>% -->
<!--   modify_caption("**Upfront Surgery**") -->
<!-- ``` -->
<br>
<br>

***

<br>

## 3.Survivals by RDI

### Survivals RDI by chemotherapy type

### <span style="color:green">**Figure 2: KM 3 panel figure**</span>

<!-- <div class = "row"> -->
<!-- <div class = "col-md-6"> -->
```{r OS dx RDI, fig.height = 7}
# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_neo_grp, 
#                    data=Frontline %>% 
#                      filter(therapy == "Upfront Chemo") %>%
#                      distinct(patientid, .keep_all = TRUE)
#                    ),
#            title = "OS from diagnosis carboplatin \nUpfront Chemo",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
# 
#            pval=TRUE,
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"),
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
# 
#            legend.title = "", xlab = "Time (in months)"
# ) + guides(colour = guide_legend(ncol = 1))
# 
# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
#                    data=Frontline %>% 
#                      filter(therapy == "Upfront Chemo") %>%
#                      distinct(patientid, .keep_all = TRUE)
#                    ),
#            title = "OS from diagnosis carboplatin \nUpfront Chemo",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
# 
#            pval=TRUE,
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"),
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
# 
#            legend.title = "", xlab = "Time (in months)"
# ) + guides(colour = guide_legend(ncol = 1))
# 
# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
#                    data=Frontline %>% 
#                      filter(therapy == "Upfront Surgery") %>%
#                      distinct(patientid, .keep_all = TRUE)
#                    ),
#            title = "OS from diagnosis carboplatin \nUpfront Surgery",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
# 
#            pval=TRUE,
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"),
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
# 
#            legend.title = "", xlab = "Time (in months)"
# ) + guides(colour = guide_legend(ncol = 1))

# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_neo_grp, 
#                    data=Frontline %>% 
#                      filter(therapy == "Upfront Chemo") %>%
#                      distinct(patientid, .keep_all = TRUE)
#                    ),
#            title = "OS from diagnosis paclitaxel \nUpfront Chemo",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
# 
#            pval=TRUE,
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"),
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
# 
#            legend.title = "", xlab = "Time (in months)"
# ) + guides(colour = guide_legend(ncol = 1))
# 
# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_adj_grp, 
#                    data=Frontline %>% 
#                      filter(therapy == "Upfront Chemo") %>%
#                      distinct(patientid, .keep_all = TRUE)
#                    ),
#            title = "OS from diagnosis paclitaxel \nUpfront Chemo",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
# 
#            pval=TRUE,
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"),
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
# 
#            legend.title = "", xlab = "Time (in months)"
# ) + guides(colour = guide_legend(ncol = 1))
# 
# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_adj_grp, 
#                    data=Frontline %>% 
#                      filter(therapy == "Upfront Surgery") %>%
#                      distinct(patientid, .keep_all = TRUE)
#                    ),
#            title = "OS from diagnosis paclitaxel \nUpfront Surgery",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
# 
#            pval=TRUE,
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"),
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
# 
#            legend.title = "", xlab = "Time (in months)"
# ) + guides(colour = guide_legend(ncol = 1))
```
<!-- </div> -->

<!-- <div class = "col-md-6"> -->
```{r OS treatment RDI, fig.height = 7}
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo_grp, 
                   data=Frontline %>% 
                     filter(therapy == "Upfront Chemo") %>%
                     distinct(patientid, .keep_all = TRUE)
                   ),
           title = "OS from treatment carboplatin \nUpfront Chemo",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
                   data=Frontline %>% 
                     filter(therapy == "Upfront Chemo") %>%
                     distinct(patientid, .keep_all = TRUE)
                   ),
           title = "OS from treatment carboplatin \nUpfront Chemo",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 1))

ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
                   data=Frontline %>% 
                     filter(therapy == "Upfront Surgery") %>%
                     distinct(patientid, .keep_all = TRUE)
                   ),
           title = "OS from treatment carboplatin \nUpfront Surgery",
           font.main = c(24, "bold", "black"),
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
           size = 1.5,

           pval=TRUE,
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"),
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)"
) + guides(colour = guide_legend(ncol = 1))

# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_neo_grp, 
#                    data=Frontline %>% 
#                      filter(therapy == "Upfront Chemo") %>%
#                      distinct(patientid, .keep_all = TRUE)
#                    ),
#            title = "OS from diagnosis paclitaxel \nUpfront Chemo",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
# 
#            pval=TRUE,
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"),
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
# 
#            legend.title = "", xlab = "Time (in months)"
# ) + guides(colour = guide_legend(ncol = 1))
# 
# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_adj_grp, 
#                    data=Frontline %>% 
#                      filter(therapy == "Upfront Chemo") %>%
#                      distinct(patientid, .keep_all = TRUE)
#                    ),
#            title = "OS from diagnosis paclitaxel \nUpfront Chemo",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
# 
#            pval=TRUE,
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"),
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
# 
#            legend.title = "", xlab = "Time (in months)"
# ) + guides(colour = guide_legend(ncol = 1))
# 
# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_adj_grp, 
#                    data=Frontline %>% 
#                      filter(therapy == "Upfront Surgery") %>%
#                      distinct(patientid, .keep_all = TRUE)
#                    ),
#            title = "OS from diagnosis paclitaxel \nUpfront Surgery",
#            font.main = c(24, "bold", "black"),
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
#            size = 1.5,
# 
#            pval=TRUE,
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"),
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
# 
#            legend.title = "", xlab = "Time (in months)"
# ) + guides(colour = guide_legend(ncol = 1))
```
<!-- </div> -->
<!-- </div> -->

<br>
<br>

***

# IV.Hazard Ratio

<!-- <span style="color:green">**Table X HR Univariable**</span>   -->

<!-- ## Univariable and drug only adjusted analysis -->
<!-- ```{r Table 6 HR} -->
<!-- # tbl2 <- Frontline %>% -->
<!-- #   filter(therapy == "Upfront Chemo") -->
<!-- # tbl1 <- tbl2 %>% -->
<!-- #   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>%  -->
<!-- #   tbl_uvregression(method = survival::coxph, -->
<!-- #                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%  -->
<!-- #   add_ -->
<!-- # tbl2 <- tbl2 %>% -->
<!-- #   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
<!-- #   tbl_uvregression(method = survival::coxph, -->
<!-- #                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- #  -->
<!-- #  -->
<!-- # tbl3 <- Frontline %>% -->
<!-- #   filter(therapy == "Upfront Surgery") -->
<!-- # tbl3 <- tbl3 %>% -->
<!-- #   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
<!-- #   tbl_uvregression(method = survival::coxph, -->
<!-- #                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- # tbl5 <- tbl_merge(list(tbl2, tbl3)) -->
<!-- #  -->
<!-- # # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>% -->
<!-- # #   modify_spanning_header(everything() ~ NA_character_) -->
<!-- #  -->
<!-- # tbl_stack(list(tbl1, tbl5)) %>% -->
<!-- #   bold_labels() %>% -->
<!-- #   italicize_levels() -->

<!--   # trial %>% -->
<!--   # select(age, grade, stage, trt) %>% -->
<!--   # mutate(grade = paste("Grade", grade)) %>% -->
<!--   # # tbl_strata( -->
<!--   # #   strata = grade, -->
<!--   # #   .tbl_fun = -->
<!--   # #     ~ .x %>% -->
<!--   #       tbl_summary(by = trt, missing = "no") %>% -->
<!--   #       add_n() -->
<!--   # ) -->
<!-- ``` -->

<!-- Left is univariable, right is adjusted by each drugs `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,` but not by clinicals. -->

<!-- <div class = "row"> -->
<!-- <div class = "col-md-6"> -->
<!-- ```{r Table 61 HR} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <- tbl2 %>% -->
<!--   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <- tbl2 %>% -->
<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <- tbl3 %>% -->
<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <- tbl2 %>% -->
<!--   select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <- tbl2 %>% -->
<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <- tbl3 %>% -->
<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel/Upfront Chemo",  -->
<!--                            "paclitaxel/Upfront Chemo", -->
<!--                            "paclitaxel/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<!-- </div> -->

<!-- <div class = "col-md-6"> -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl21 <- -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
<!--              event = tbl2$vital_status -->
<!--              ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp, -->
<!--         data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl31 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status -->
<!--              ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp, -->
<!--         data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl21, tbl31), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<!-- </div> -->
<!-- </div> -->

<br>
<br>

## Multivariable
<!-- ### RDI group -->
<!-- <span style="color:green">**Table 9 HR Multivariable**</span>   -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + ` -->
<!-- `imp_stagecat + histology + imp_debulking`  -->
<!-- ```{r Table 5 HR adjusted rdi group} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # # Pacli -->
<!-- #  -->
<!-- # tbl2 <- Frontline %>% -->
<!-- #   filter(therapy == "Upfront Chemo") -->
<!-- # tbl1 <-  -->
<!-- #   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!-- #              event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- # tbl2 <-  -->
<!-- #   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!-- #              event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- # tbl3 <- Frontline %>% -->
<!-- #   filter(therapy == "Upfront Surgery") -->
<!-- # tbl3 <-  -->
<!-- #   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!-- #              event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- # tbl_stack(list(tbl1, tbl2, tbl3), -->
<!-- #           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
<!-- #                            "paclitaxel Adj/Upfront Chemo", -->
<!-- #                            "paclitaxel Adj/Upfront Surgery")) %>% -->
<!-- #   bold_labels() %>% -->
<!-- #   italicize_levels() -->
<!-- ``` -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + ` -->
<!-- `imp_stagecat + histology`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # # Pacli -->
<!-- #  -->
<!-- # tbl2 <- Frontline %>% -->
<!-- #   filter(therapy == "Upfront Chemo") -->
<!-- # tbl1 <-  -->
<!-- #   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!-- #              event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- # tbl2 <-  -->
<!-- #   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!-- #              event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- # tbl3 <- Frontline %>% -->
<!-- #   filter(therapy == "Upfront Surgery") -->
<!-- # tbl3 <-  -->
<!-- #   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!-- #              event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- # tbl_stack(list(tbl1, tbl2, tbl3), -->
<!-- #           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
<!-- #                            "paclitaxel Adj/Upfront Chemo", -->
<!-- #                            "paclitaxel Adj/Upfront Surgery")) %>% -->
<!-- #   bold_labels() %>% -->
<!-- #   italicize_levels() -->
<!-- ``` -->
<br>
<br>

<!-- ### Continous -->
<!-- <span style="color:green">**Table 10 HR Multivariable**</span>   -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +` -->
<!-- `imp_stagecat + histology + imp_debulking`  -->
<!-- ```{r rdi continous} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
<!--                            "paclitaxel Adj/Upfront Chemo", -->
<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +` -->
<!-- `imp_stagecat + histology`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
<!--                            "paclitaxel Adj/Upfront Chemo", -->
<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<br>
<br>

## Adjusted by other drug
### RDI group
## <span style="color:green">**Table 3 HR Multivariable**</span>

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ ` -->
<!-- `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +` -->
<!-- `raceeth + ageatdx + imp_stagecat + histology + imp_debulking`  -->
<!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl21 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl31 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl21, tbl31), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

<!-- PH assumption Upfront Chemo -->
<!-- ```{r prop H} -->
<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status -->
<!--            ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking,  -->
<!--       data =  tbl2)  %>%  -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- PH assumption Upfront Surgery -->
<!-- ```{r} -->
<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =   -->
<!--         tbl3) %>% -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ ` -->
<!-- `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + ` -->
<!-- `raceeth + ageatdx + imp_stagecat + histology`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl2, tbl3), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

### Carbo only
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H Table 3 HR Multivariable adj deb}
coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, 
      data =  tbl2)  %>% 
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + #strata(
        imp_stagecat#) 
      + #strata(
        histology#) 
      + imp_debulking,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + #strata(
        imp_stagecat + strata(histology) + imp_debulking,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
        strata(imp_stagecat) + strata(histology) + imp_debulking,
      data = tbl3) %>%
  cox.zph()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ 
          RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology)
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H Table 3 HR Multivariable non adj deb}
coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, 
      data = tbl2)  %>% 
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, 
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
        imp_stagecat + strata(histology),
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
        strata(imp_stagecat) + strata(histology),
      data = tbl3) %>%
  cox.zph()
```

<br>
<br>

<!-- ### Continous -->
<!-- <span style="color:green">**Table 12 HR Multivariable**</span>   -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ ` -->
<!-- `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +` -->
<!-- `raceeth + ageatdx + imp_stagecat + histology + imp_debulking`  -->
<!-- ```{r rdi continous adjusted by other drug} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl21 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl31 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl21, tbl31), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

<!-- PH assumption Upfront Chemo -->
<!-- ```{r prop H c} -->
<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%  -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- PH assumption Upfront Surgery -->
<!-- ```{r} -->
<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ ` -->
<!-- `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +` -->
<!-- `raceeth + ageatdx + stagecat + histology`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl2, tbl3), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<br>
<br>

***

<br>

<!-- # V.More precise RDI -->

<!-- As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed -->

<!-- ```{r echo=TRUE} -->
<!-- # Highly underdosed: < 0.75 -->
<!-- # Underdosed: >= 0.75 to <0.85 -->
<!-- # Adequate dosing: >= 0.85 to <1.10 -->
<!-- # Overdosing: >=1.10 -->
<!-- ``` -->
<!-- Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI) -->
<!-- ```{r, fig.width=12, fig.height=12} -->
<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!--   ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
<!--   geom_point(alpha = 0.7, size = 0.75)+ -->
<!--   theme_minimal(base_size = 10)+ -->
<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!--   ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
<!--   geom_jitter()+ -->
<!--   theme_minimal(base_size = 10)+ -->
<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->

<!-- ``` -->
<!-- Here I just wanted to see if we have more or less underdosing / overdosing with BMI -->
<!-- ```{r, fig.width=12, fig.height=12} -->
<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!--   ggplot(aes(x= RDI_grp1, fill = drugname))+ -->
<!--   geom_bar(position = position_dodge())+ -->
<!--   theme_minimal(base_size = 10)+ -->
<!--   facet_wrap(. ~ therapy, ncol = 2, scales = "free")+ -->
<!--   coord_flip() -->
<!-- ``` -->

<!-- ```{r, fig.width=12} -->
<!-- # Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!-- #   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
<!-- #   geom_bar(position = position_dodge())+ -->
<!-- #   theme_minimal(base_size = 10)+ -->
<!-- #   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+ -->
<!-- #   coord_flip() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!--   # filter(linenumber_new == "1") %>% -->
<!--   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
<!--   geom_bar(position = "fill")+ -->
<!--   theme_minimal(base_size = 10)+ -->
<!--   coord_flip()+ -->
<!--   facet_wrap(.~ therapy) -->
<!-- ``` -->
<!-- As you can see above in green, we have a lot of patient who are overdose. -->
<!-- <br> -->
<!-- <br> -->

<!-- ## Hazard Ratio RDI 2 -->

<!-- <span style="color:green">**Table HR**</span> -->

<!-- ### Univariable -->
<!-- ```{r HR RDI 2} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <- tbl2 %>% -->
<!--   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp1) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <- tbl2 %>% -->
<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <- tbl3 %>% -->
<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <- tbl2 %>% -->
<!--   select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp1) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <- tbl2 %>% -->
<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <- tbl3 %>% -->
<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel/Upfront Chemo",  -->
<!--                            "paclitaxel/Upfront Chemo", -->
<!--                            "paclitaxel/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<!-- Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference. -->

<!-- ### Multivariable -->
<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_grp1 + raceeth + ageatdx + stagecat` -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
<!--                            "paclitaxel Adj/Upfront Chemo", -->
<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<!-- <br> -->
<!-- <br> -->

<!-- ## Adjusted by other drug -->
<!-- ### RDI group -->
<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` -->
<!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug 2} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl2, tbl3), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<!-- <br> -->
<!-- <br> -->

<!-- *** -->

<!-- # VI. Adjusted by **BMI at DX category** -->

<!-- ```{r} -->
<!-- Frontline_bmi <- Frontline %>% -->
<!--   filter(!is.na(bmi_cat)) -->
<!-- ``` -->

<!-- ## Multivariable -->
<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` -->
<!-- ```{r bmi HR adjusted} -->
<!-- # Carbo -->
<!-- # tbl1 <- Frontline_bmi %>% -->
<!-- #   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") -->
<!-- # tbl1 <- -->
<!-- #   coxph(Surv(time = tbl1$month_at_os_from_treatment, -->
<!-- #              event = tbl1$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>% -->
<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->

<!-- tbl2 <- Frontline_bmi %>% -->
<!--   filter(drugname == "carboplatin" & therapy == "Upfront Surgery") -->
<!-- tbl2 <- -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
<!--              event = tbl2$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline_bmi %>% -->
<!--   filter(drugname == "carboplatin" & therapy == "Upfront Chemo") -->
<!-- tbl3 <- -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl2, tbl3), -->
<!--           group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->
<!-- # tbl7 <- Frontline_bmi %>% -->
<!-- #   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant") -->
<!-- # tbl7 <- -->
<!-- #   coxph(Surv(time = tbl7$month_at_os_from_treatment, -->
<!-- #              event = tbl7$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>% -->
<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
<!-- tbl8 <- Frontline_bmi %>% -->
<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Surgery") -->
<!-- tbl8 <- -->
<!--   coxph(Surv(time = tbl8$month_at_os_from_treatment, -->
<!--              event = tbl8$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl9 <- Frontline_bmi %>% -->
<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Chemo") -->
<!-- tbl9 <- -->
<!--   coxph(Surv(time = tbl9$month_at_os_from_treatment, -->
<!--              event = tbl9$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl8, tbl9), -->
<!--           group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

# Complete case HR analysis
## <span style="color:green">**Table S1 HR patient characteristics by inclusion in complete-case**</span>

```{r}
Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  mutate(comp_cases = case_when(
    is.na(stagecat) |
      is.na(debulking)                     ~ "excluded",
    TRUE                                   ~ "complete cases"
  )) %>% 
  select(c(raceeth, 
           ageatdx,

           bmi_at_dx, bmi_cat,

           histology1, "histology",
           "stagecat", imp_stagecat,
           therapy, 
           debulking, imp_debulking,
           comp_cases)) %>% 
  tbl_summary(by = comp_cases) %>% 
  bold_labels() %>% add_p() %>% bold_p()
```
<br>

<!-- ## Univariable and drug only adjusted analysis -->

<!-- <span style="color:green">**Table  HR Univariable**</span>   -->

<!-- <div class = "row"> -->
<!-- <div class = "col-md-6"> -->
<!-- ```{r Table  HR} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking)) -->
<!-- tbl1 <- tbl2 %>% -->
<!--   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <- tbl2 %>% -->
<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking)) -->
<!-- tbl3 <- tbl3 %>% -->
<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking)) -->
<!-- tbl1 <- tbl2 %>% -->
<!--   select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <- tbl2 %>% -->
<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking)) -->
<!-- tbl3 <- tbl3 %>% -->
<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel/Upfront Chemo",  -->
<!--                            "paclitaxel/Upfront Chemo", -->
<!--                            "paclitaxel/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<!-- </div> -->

<!-- <div class = "col-md-6"> -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking)) -->
<!-- tbl21 <- -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
<!--              event = tbl2$vital_status -->
<!--              ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp, -->
<!--         data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking)) -->
<!-- tbl31 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status -->
<!--              ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp, -->
<!--         data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- tbl_stack(list(tbl21, tbl31), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<!-- </div> -->
<!-- </div> -->

<!-- <br> -->
<!-- <br> -->

## Multivariable
### RDI group
<!-- ## <span style="color:green">**Table  HR Multivariable**</span>   -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp +` -->
<!-- `raceeth + ageatdx + stagecat + histology + debulking`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
<!--                            "paclitaxel Adj/Upfront Chemo", -->
<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + ` -->
<!-- `raceeth + ageatdx + stagecat + histology`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
<!--                            "paclitaxel Adj/Upfront Chemo", -->
<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

<!-- <br> -->
<!-- <br> -->

<!-- ### Continous -->
<!-- <span style="color:green">**Table 10 HR Multivariable**</span>   -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + ` -->
<!-- `raceeth + ageatdx + stagecat + histology + debulking`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
<!--                            "paclitaxel Adj/Upfront Chemo", -->
<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + ` -->
<!-- `raceeth + ageatdx + stagecat + histology`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
<!--                            "carboplatin Adj/Upfront Chemo", -->
<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->

<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl1 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
<!--                            "paclitaxel Adj/Upfront Chemo", -->
<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<!-- <br> -->
<!-- <br> -->

<!-- ## Adjusted by other drug -->
<!-- ### RDI group -->
<!-- <span style="color:green">**Table  HR Multivariable complete cases**</span>   -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ ` -->
<!-- `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +` -->
<!-- `raceeth + ageatdx + stagecat + histology + debulking`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl21 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking,  -->
<!--         data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->

<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl31 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status -->
<!--              ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking,  -->
<!--         data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>%  -->
<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- tbl_stack(list(tbl21, tbl31), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

<!-- PH assumption Upfront Chemo -->
<!-- ```{r prop H complete case} -->
<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status -->
<!--            ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking,  -->
<!--       data =  tbl2)  %>%  -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- PH assumption Upfront Surgery -->
<!-- ```{r} -->
<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking,  -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ ` -->
<!-- `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + ` -->
<!-- `raceeth + ageatdx + stagecat + histology`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl2, tbl3), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

## <span style="color:green">**Table S2 HR Multivariable complete cases**</span>

## Carbo only
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%

  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + strata(histology) + debulking, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
PH assumption Upfront Chemo
```{r prop H Table S2 HR Multivariable complete cases adj deb}
coxph(Surv(time = tbl2$month_at_os_from_treatment,
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking,
      data =  tbl2)  %>%
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking,
      data =  tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + strata(histology) + debulking,
      data =  tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking,
      data =  tbl3) %>%
  cox.zph()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + strata(histology), 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H Table S2 HR Multivariable complete cases non adj debonly}
coxph(Surv(time = tbl2$month_at_os_from_treatment,
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology,
      data =  tbl2)  %>%
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology,
      data =  tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
        stagecat + strata(histology),
      data =  tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
        strata(stagecat) + strata(histology),
      data =  tbl3) %>%
  cox.zph()
```
<br>
<br>

<!-- ### Continous -->
<!-- <span style="color:green">**Table 12 HR Multivariable**</span>   -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ ` -->
<!-- `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + ` -->
<!-- `raceeth + ageatdx + stagecat + histology + debulking`  -->
<!-- ```{r } -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl21 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl31 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl21, tbl31), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->

<!-- PH assumption Upfront Chemo -->
<!-- ```{r prop H complete case c} -->
<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>%  -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- PH assumption Upfront Surgery -->
<!-- ```{r} -->
<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ ` -->
<!-- `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + ` -->
<!-- `raceeth + ageatdx + stagecat + histology`  -->
<!-- ```{r} -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Chemo") -->
<!-- tbl2 <-  -->
<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(therapy == "Upfront Surgery") -->
<!-- tbl3 <-  -->
<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl2, tbl3), -->
<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<br>
<br>

***

```{r echo=FALSE, out.width='30%'}
knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
```

### 2022-05-19 Rmd/Manuscript rdi analysis.Rmd
Update for carbo only analysis

@@
 library(lubridate)
+library(irr)
 library(ggplot2)
@@
   ) %>% 
-  ungroup()
+  ungroup() %>% 
+  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))
 
 RDI_data <- Treatment %>% 
-  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
-  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))
+  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
 ```
@@
   ungroup()
-Frontline_adjusted <- RDI_data %>% 
-  distinct(patientid, .keep_all = TRUE)
-```
-<br>
-<br>
-
-# **Number of patients : `r Frontline_adjusted %>% distinct(patientid) %>% nrow()`**
+RDI_data_per_patients <- RDI_data %>% 
+  mutate(carbo_arrange_variable = case_when(
+    drugname == "carboplatin"           ~ 1
+  )) %>% 
+  arrange(carbo_arrange_variable) %>% 
+  distinct(patientid, .keep_all = TRUE) %>% 
+  select(-c(linename, linenumber, linenumber_adj, 
+            linenumber_new, linestartdate, lineenddate,
+            cycle_drugname, cycle_increment, cycle_start_date,
+            cycle_count_perline, cycle_major_drugname))
+```
+<br>
+<br>
+
+# **Number of patients : `r RDI_data_per_patients %>% distinct(patientid) %>% nrow()`**
 
@@
 <!-- ```{r rule between diagnosis and treatment} -->
-<!-- drugs1 <- Frontline_adjusted %>%  -->
+<!-- drugs1 <- RDI_data_per_patients %>%  -->
 <!--   # 1. 60 days rule between diagnosis and treatment # Loss 1 -->
@@
 Are excluded :  
--	Borderline cases (not invasive ovarian cancer)  
 -	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
@@
 ```{r}
-flatiron_rec <- Frontline_adjusted %>% 
+flatiron_rec <- RDI_data_per_patients %>% 
   filter(is.na(flatiron_rules))
@@
 
+-	exclude borderline cases (not invasive ovarian cancer)  
 - exclude patients whose histology is unknown  
 - remove chemotherapy only patients  
-- include only patients who received platin and/or taxane
+- include only patients who received platin and/or taxane (exclude patients who didn't received carboplatin)  
 - exclude patients who only received neo + surgery  
@@
 study_criteria <- flatiron_rec %>% 
+  filter(is.na(borderline))
+
+study_criteria <- study_criteria %>% 
   filter(!is.na(histology)) # %>% 
   # filter(histology == "Serous") 
+  # filter(histology == "Others")
 
@@
 study_criteria <- study_criteria %>%
-  filter(had_carbo_pacli == "Yes")
+  filter(had_carbo == "Yes")
 
@@
 - exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
-- exclude patients for whose no RDI were available
+- exclude patients for whose no RDI were available FOR CARBOPLATIN
 
@@
     therapy == "Upfront Chemo" &
-      (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
-         !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
+      (!is.na(RDI_carbo_neo) & 
+         !is.na(RDI_carbo_adj)) 
   ) | (
     therapy == "Upfront Surgery" &
-      (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
+      (!is.na(RDI_carbo_adj))
   )
@@
 study_cohorts <- 
-  Frontline_adjusted %>%
+  RDI_data_per_patients %>%
   cohort_start("**Assessed for eligibility**") %>%
@@
   study_criteria = flatiron_rec  %>% 
+    filter(is.na(borderline)) %>% 
     filter(!is.na(histology)) %>%
@@
 
-  # anti_join is useful for counting exclusions -------------
+  # anti_join is useful for counting exclusions
     excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
@@
       • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
-      • Borderline cases (not invasive ovarian cancer) <br>
-      • (Data from one PracticeID) <br>
-      • (historical structured data were not available for <br> patients seen at academic sites prior to 2015)
+      • **(Data from one PracticeID)** <br>
+      • **(historical structured data were not available for <br> patients seen at academic sites prior to 2015)**
       ")
@@
       "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
+      • Borderline cases (not invasive ovarian cancer) <br>
       • exclude patients whose histology is unknown <br>
       • remove chemotherapy only patients <br>
-      • include only patients who received platin and/or taxane <br>
-      • exclude patients who only received neo + surgery <br>
-      • include patients with single or dual P/T +/- Bev as frontline treatment
+      • include patients who received carboplatin +/- taxane +/- Bev in a adj +/- neo settings
       ")
@@
 ## Explore the dataset
+## <span style="color:green">**ICC between cycles**</span>
+
+Used the ICC for a single rater, two-way mixed effects model with a measure for absolute agreement (two-way mixed-effects model and the absolute agreement are recommended for both test-retest and intra-rater reliability studies (Koo et al., 2016).
+<!-- **For ICC, a value of 0.9 is considered as excellent.**  -->
+```{r}
+# Need to recalculate the average per cycle as we did it by line (was comaing back to same because we limit our study to 1+1 or 1+3 cycle type)
+# What I did :
+# Treatment <- Treatment %>% 
+#   mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
+#   ) %>%
+#   group_by(patientid, chemotherapy_type, drugname) %>%
+#   mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+#   ) %>% 
+#   ungroup()
+
+Treatment_ICC <- 
+  Treatment %>% 
+  # Limit to the patietns after exclusion criteria
+  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
+  filter(linenumber_adj == 1) %>% 
+  filter(had_carbo == "Yes") %>% 
+  arrange(patientid, episodedate) %>% 
+  # group to have RDI by cycle for each drug 
+  group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>%
+  mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  ) %>% 
+  ungroup() %>%
+  arrange(patientid, episodedate) %>% 
+  distinct(patientid, chemotherapy_type, cycle_increment, drugname, .keep_all = TRUE) %>% 
+  filter(drugname == "carboplatin")
+```
+
+```{r}
+ICC_df <- Treatment_ICC %>% select(patientid, chemotherapy_type, cycle_increment, mean_RDI_per_cycledrug) %>% 
+  unite(patientid, c(patientid:chemotherapy_type)) %>%
+      pivot_wider(names_from = cycle_increment, values_from = mean_RDI_per_cycledrug) %>%
+      select(-patientid)
+
+icc_value <- round(icc(
+      ICC_df, model = "twoway", 
+      type = "agreement", unit = "single"
+    )$value, 3)
+head(ICC_df, 10)
+
+# mutate(reliability = case_when(
+#   value < 0.5 ~ "poor",
+#   value >= 0.5 &
+#     value < 0.75 ~ "moderate",
+#   value >= 0.75 &
+#     value < 0.9 ~ "good",
+#   value >= 0.9 ~ "excellent"
+# ))
+```
+The ICC value is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`
 
@@
   filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>%
-  arrange(patientid, episodedate, drugname)
-```
-
-<!-- ### Number of line /cycle received by patients in our study population  -->
+  arrange(patientid, episodedate, drugname) %>% 
+  filter(had_carbo == "Yes") %>% 
+  filter(linenumber_adj == 1)
+```
+
+### Number of cycle received by patients in our study population
 
 <!-- <span style="color:green">**Table supp X Number of total line**</span> -->
-<!-- ```{r} -->
-<!-- full_data_study_pop %>%  -->
-<!--   arrange(desc(linenumber_new)) %>%  -->
-<!--   distinct(patientid, .keep_all = TRUE) %>%  -->
-<!--   select(linenumber_new, therapy) %>%  -->
-<!--   tbl_summary(by = therapy) -->
-<!-- ``` -->
-
-<!-- <span style="color:green">**Table supp X Number of cycle in Neo**</span> -->
-<!-- ```{r} -->
-<!-- full_data_study_pop %>%  -->
-<!--   filter(chemotherapy_type == "Neoadjuvant") %>%  -->
-<!--   arrange(desc(cycle_increment)) %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(cycle_increment) %>%  -->
-<!--   tbl_summary() -->
-<!-- full_data_study_pop %>%  -->
-<!--   filter(chemotherapy_type == "Neoadjuvant") %>%  -->
-<!--   arrange(desc(cycle_increment)) %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(cycle_increment) %>%  -->
-<!--   tbl_summary(type = list(cycle_increment ~ "continuous")) -->
-<!-- ``` -->
-
-<!-- <span style="color:green">**Table supp X Number of cycle in Adj**</span> -->
-<!-- ```{r} -->
-<!-- full_data_study_pop %>%  -->
-<!--   filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>%  -->
-<!--   arrange(desc(cycle_increment)) %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(cycle_increment, therapy) %>%  -->
-<!--   tbl_summary(by = therapy) -->
-<!-- full_data_study_pop %>%  -->
-<!--   filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>%  -->
-<!--   arrange(desc(cycle_increment)) %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(cycle_increment, therapy) %>%  -->
-<!--   tbl_summary(by = therapy, -->
-<!--               type = list(cycle_increment ~ "continuous")) -->
-<!-- ``` -->
+```{r}
+# full_data_study_pop %>%
+#   arrange(desc(linenumber_new)) %>%
+#   distinct(patientid, .keep_all = TRUE) %>%
+#   select(linenumber_new, therapy) %>%
+#   tbl_summary(by = therapy)
+```
+
+<span style="color:green">**Table supp X Number of cycle in Neo**</span>
+```{r}
+full_data_study_pop %>%
+  filter(chemotherapy_type == "Neoadjuvant") %>%
+  arrange(desc(cycle_increment)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(cycle_increment) %>%
+  tbl_summary()
+full_data_study_pop %>%
+  filter(chemotherapy_type == "Neoadjuvant") %>%
+  arrange(desc(cycle_increment)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(cycle_increment) %>%
+  tbl_summary(type = list(cycle_increment ~ "continuous"))
+
+full_data_study_pop %>%
+  filter(chemotherapy_type == "Neoadjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(linename) %>%
+  tbl_summary()
+```
+
+<span style="color:green">**Table supp X Number of cycle in Adj**</span>
+```{r}
+full_data_study_pop %>%
+  filter(chemotherapy_type == "Adjuvant") %>%
+  arrange(desc(cycle_increment)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(cycle_increment, therapy) %>%
+  tbl_summary(by = therapy)
+full_data_study_pop %>%
+  filter(chemotherapy_type == "Adjuvant") %>%
+  arrange(desc(cycle_increment)) %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(cycle_increment, therapy) %>%
+  tbl_summary(by = therapy,
+              type = list(cycle_increment ~ "continuous"))
+
+full_data_study_pop %>%
+  filter(chemotherapy_type == "Adjuvant") %>%
+  distinct(patientid, .keep_all = TRUE) %>%
+  select(linename, therapy) %>%
+  tbl_summary(by = therapy)
+```
 <!-- <br> -->
@@
 # Clinical Analysis
-
-## ICC between cycles
-```{r}
-full_data_study_pop
-
-```
-
 ## 1.Clinical summary table
@@
 ```{r Table 1}
-Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+Frontline %>% 
   select(c(vital, raceeth, 
@@
 Frontline %>% 
-  distinct(patientid, .keep_all = TRUE) %>% 
   select(c(raceeth, "vital",
@@
 ```{r Table 4}
-# tbl1 <- 
-  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+Frontline %>% 
   select(c(raceeth,
@@
 ```{r Table 5}
-Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+Frontline %>% 
   select(c(bmi_cat,
@@
 ```{r Summary of the expected, actual dose, and RDI}
-tbl <- full_data_study_pop %>% 
+tbl <- 
+  Treatment %>% 
+  # Limit to the patietns after exclusion criteria
+  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
+  arrange(patientid, episodedate, drugname) %>% 
+  # group to have RDI by cycle for each drug 
+  # group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>%
+  # mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  # ) %>% 
+  # ungroup() %>% 
+  filter(drugname == "carboplatin") %>% 
+  filter(linenumber_adj == 1) %>%
+
   group_by(patientid, therapy, chemotherapy_type, drugname) %>% 
@@
              event = tbl3$vital_status
-           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + #strata(
-        imp_stagecat#) 
-      + #strata(
-        histology#) 
-      + imp_debulking,
+           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking,
       data = tbl3) %>%
@@
              event = tbl3$vital_status
-           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + #strata(
+           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
         imp_stagecat + strata(histology) + imp_debulking,
@@
           RDI_carbo_adj_grp + raceeth + ageatdx + 
-          strata(imp_stagecat) + strata(histology)
+          strata(imp_stagecat) + strata(histology),
         data =  tbl3) %>%

### 2022-05-19 R/02.data cleaning.R

@@ -452,7 +452,11 @@ group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedat
   mutate(across(starts_with("amount"), ~ na_if(., "NA"))) %>% 
   purrr::keep(~!all(is.na(.))) %>%
   mutate(across(starts_with("amount"), ~ as.numeric(.))) %>% 
-  mutate(amount = rowSums(select(.,starts_with("amount_")), na.rm = TRUE)) %>%
+  mutate(amount = rowSums(select(.,starts_with("amount_")), na.rm = TRUE),
+         amount = case_when(
+           is.na(amount_1)           ~ NA_real_,
+           TRUE                      ~ amount
+         )) %>%
   # Found ug, ml, Ea, and NA they are all good, but 
   # ug need conversion
   # the AUC are mostly correct (real mg) but are actual AUC when < at 10 so remove
@@ -857,21 +861,27 @@ Treatment <- Treatment1 %>%
   ) %>% 
   mutate(flatiron_rules = case_when(
     days_at_first_treatment > 90                 ~ "exclude",
-    thirty_days_exclusion <= 30                  ~ "exclude",
-    exclude == "1"                               ~ "exclude"
+    thirty_days_exclusion <= 30                  ~ "exclude"
   )) %>%
   group_by(patientid) %>% 
   fill(flatiron_rules, .direction = "downup") %>% 
   ungroup() %>% 
   
   # step 2: Filter patients with clinical characteristics fitting to the study criteria
+  # exclude borderline cases
+  mutate(borderline = case_when(
+    exclude == "1"                               ~ "exclude"
+  )) %>% 
   # include only patients who received platin and/or taxane
   mutate(had_carbo_pacli = case_when(
     drugname == "paclitaxel" |
       drugname == "carboplatin"             ~ "Yes"
   )) %>% 
+  mutate(had_carbo = case_when(
+    drugname == "carboplatin"               ~ "Yes"
+  )) %>% 
   group_by(patientid) %>% 
-  fill(had_carbo_pacli, .direction = "updown") %>% 
+  fill(had_carbo_pacli, had_carbo, .direction = "updown") %>% 
   ungroup() %>% 
   # include patients with single or dual P/T +/- Bev as frontline treatment
   mutate(line_keep = case_when(# F002B429BE6C6
@@ -879,6 +889,7 @@ Treatment <- Treatment1 %>%
        (linename == "Carboplatin,Paclitaxel" |
[…]

### 2022-05-20 Rmd/Manuscript rdi analysis.Rmd
Add stratified analysis for histology

@@
 library(lubridate)
-library(irr)
+library(psych)
 library(ggplot2)
@@
 -	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)
-```{r}
+```{r flatiron_rec}
 flatiron_rec <- RDI_data_per_patients %>% 
@@
 - include patients with single or dual P/T +/- Bev as frontline treatment
-```{r}
+```{r study_criteria}
 study_criteria <- flatiron_rec %>% 
@@
 
-```{r}
+```{r missing_data}
 missing_data <- study_criteria %>% 
@@
 
+- exclude patients with other than intravenous drugs
 - exclude patients with more than 1 line as Neo
@@
 - exclude patients who switch drug within a line
-```{r}
+```{r standard_care}
 standard_care <- missing_data %>% 
   # Remove patients with more than 1 line as Neo
-  filter(is.na(neo_more_more_than_1line))
+  filter(is.na(neo_more_more_than_1line)) %>% 
+  filter(is.na(intravenous_rule))
 
@@
 ### For Upfront Chemo
-```{r}
+```{r imputation up Chemo}
 data <- Frontline %>% 
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology,
         data = data)
@@
        exp = coxph(
-         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
        ))
@@
 
-```{r}
+```{r imputation up Surgery}
 data <- Frontline %>% 
@@
 nonimp_cox_model <-
-  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
+  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology,
         data = data)
@@
        exp = coxph(
-         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology
+         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
        ))
@@
 <!-- Complete the data and merge with original -->
-```{r}
+```{r combine imputed data}
 imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
@@
   cohort_define(
-  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),
+  flatiron_rec = .full %>% 
+    filter(is.na(flatiron_rules)),
 
@@
       therapy == "Upfront Chemo" &
-        (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
-           !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
+        (!is.na(RDI_carbo_neo) & 
+           !is.na(RDI_carbo_adj)) 
     ) | (
       therapy == "Upfront Surgery" &
-        (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
+        (!is.na(RDI_carbo_adj))
     )
@@
     filter(is.na(neo_more_more_than_1line)) %>%
+    filter(is.na(intravenous_rule)) %>% 
     filter(is.na(frontline_has_maintenance)) %>%
@@
       • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
-      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
-      • **(Data from one PracticeID)** <br>
-      • **(historical structured data were not available for <br> patients seen at academic sites prior to 2015)**
+      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis
       ")
@@
 
-Used the ICC for a single rater, two-way mixed effects model with a measure for absolute agreement (two-way mixed-effects model and the absolute agreement are recommended for both test-retest and intra-rater reliability studies (Koo et al., 2016).
+Used the ICC for a average raters, two-way mixed effects model with a measure for absolute agreement (two-way mixed-effects model and the absolute agreement are recommended for intra-rater reliability studies (Koo et al., 2016).
 <!-- **For ICC, a value of 0.9 is considered as excellent.**  -->
-```{r}
-# Need to recalculate the average per cycle as we did it by line (was comaing back to same because we limit our study to 1+1 or 1+3 cycle type)
+```{r ICC data prep}
+# Need to recalculate the average per cycle as we did it by line (it was more simple and was coming back to same because we limit our study to 1+1 or 1+3 cycle type)
 # What I did :
@@
 
-```{r}
-ICC_df <- Treatment_ICC %>% select(patientid, chemotherapy_type, cycle_increment, mean_RDI_per_cycledrug) %>% 
-  unite(patientid, c(patientid:chemotherapy_type)) %>%
+### Upfront Chemo Neo
+```{r ICC}
+ICC_df <- Treatment_ICC %>% 
+  filter(therapy == "Upfront Chemo" & chemotherapy_type == "Neoadjuvant") %>% 
+  select(patientid, cycle_increment, mean_RDI_per_cycledrug) %>% 
       pivot_wider(names_from = cycle_increment, values_from = mean_RDI_per_cycledrug) %>%
@@
 
-icc_value <- round(icc(
-      ICC_df, model = "twoway", 
-      type = "agreement", unit = "single"
-    )$value, 3)
-head(ICC_df, 10)
-
+icc_value <- ICC(ICC_df)$results[4, 2]
+lb_value <- ICC(ICC_df)$results[4, 7]
+up_value <- ICC(ICC_df)$results[4, 8]
 # mutate(reliability = case_when(
@@
 ```
-The ICC value is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`
-
-```{r}
+The ICC value in Upfront Chemo Neo setting is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`.
+Lower bound and higher bound are `r lb_value` - `r up_value` respectively.
+
+### Upfront Chemo Adj
+```{r}
+ICC_df <- Treatment_ICC %>% 
+  filter(therapy == "Upfront Chemo" & chemotherapy_type == "Adjuvant") %>% 
+  select(patientid, chemotherapy_type, cycle_increment, mean_RDI_per_cycledrug) %>% 
+  unite(patientid, c(patientid:chemotherapy_type)) %>%
+      pivot_wider(names_from = cycle_increment, values_from = mean_RDI_per_cycledrug) %>%
+      select(-patientid)
+
+icc_value <- ICC(ICC_df)$results[4, 2]
+lb_value <- ICC(ICC_df)$results[4, 7]
+up_value <- ICC(ICC_df)$results[4, 8]
+```
+The ICC value in Upfront Chemo Adj setting is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`.
+Lower bound and higher bound are `r lb_value` - `r up_value` respectively.
+
+### Upfront Surgery
+```{r}
+ICC_df <- Treatment_ICC %>% 
+  filter(therapy == "Upfront Surgery") %>% 
+  select(patientid, chemotherapy_type, cycle_increment, mean_RDI_per_cycledrug) %>% 
+  unite(patientid, c(patientid:chemotherapy_type)) %>%
+      pivot_wider(names_from = cycle_increment, values_from = mean_RDI_per_cycledrug) %>%
+      select(-patientid)
+
+icc_value <- ICC(ICC_df)$results[4, 2]
+lb_value <- ICC(ICC_df)$results[4, 7]
+up_value <- ICC(ICC_df)$results[4, 8]
+```
+The ICC value in Upfront Surgery setting is equal to `r icc_value` which means that `r paste("the reliability is", ifelse(icc_value < 0.5, "poor", ifelse( icc_value <0.75, "moderate",ifelse(icc_value<0.9, "good", "excelent"))))`.
+Lower bound and higher bound are `r lb_value` - `r up_value` respectively.
+
+```{r exploratory data analysis}
 full_data_study_pop <-
@@
   filter(linenumber_adj == 1)
+
 ```
@@
 ```{r Summary of the expected, actual dose, and RDI}
-tbl <- 
-  Treatment %>% 
-  # Limit to the patietns after exclusion criteria
-  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
-  arrange(patientid, episodedate, drugname) %>% 
-  # group to have RDI by cycle for each drug 
-  # group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>%
-  # mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
-  # ) %>% 
-  # ungroup() %>% 
-  filter(drugname == "carboplatin") %>% 
-  filter(linenumber_adj == 1) %>%
+tbl <- full_data_study_pop %>% 
+  # Treatment %>% 
+  # # Limit to the patietns after exclusion criteria
+  # filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
+  # arrange(patientid, episodedate, drugname) %>% 
+  # # group to have RDI by cycle for each drug 
+  # # group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>%
+  # # mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
+  # # ) %>% 
+  # # ungroup() %>% 
+  # filter(drugname == "carboplatin") %>% 
+  # filter(linenumber_adj == 1) %>%
 
   group_by(patientid, therapy, chemotherapy_type, drugname) %>% 
-  summarise(amount = mean(amount), 
+  summarise(amount = mean(amount, na.rm = TRUE), 
             BSA = mean(BSA), 
@@
 <!-- ## 2.Treatment Plots -->
-<div class = "row">
-<div class = "col-md-6">
+
 ```{r treatment plots}
@@
 ```
-</div>
-
-<div class = "col-md-6">
-```{r}
-full_data_study_pop %>% 
-  filter(chemotherapy_type == "Neoadjuvant") %>% 
-  group_by(patientid, drugname) %>% 
-  summarise(CrCl = mean(CrCl),
-            target_auc = mean(target_auc),
-            expected_dose = mean(expected_dose)) %>% 
-  ungroup() %>% 
-  distinct(patientid, drugname, .keep_all = TRUE) %>% 
-  select(CrCl, target_auc, expected_dose, drugname) %>% 
-  tbl_summary(by = drugname,
-              label = list(CrCl ~ "Average CrCl during Neoadujant setting",
-                           target_auc ~ "Target dose (AUC or mg/mg2)",
-                           expected_dose ~ "Expected dose")
-    )
-```
-</div>
-</div>
+
+```{r}
+# full_data_study_pop %>% 
+#   filter(chemotherapy_type == "Neoadjuvant") %>% 
+#   group_by(patientid, drugname) %>% 
+#   summarise(CrCl = mean(CrCl),
+#             target_auc = mean(target_auc),
+#             expected_dose = mean(expected_dose)) %>% 
+#   ungroup() %>% 
+#   distinct(patientid, drugname, .keep_all = TRUE) %>% 
+#   select(CrCl, target_auc, expected_dose, drugname) %>% 
+#   tbl_summary(by = drugname,
+#               label = list(CrCl ~ "Average CrCl during Neoadujant setting",
+#                            target_auc ~ "Target dose (AUC or mg/mg2)",
+#                            expected_dose ~ "Expected dose")
+#     )
+```
 
@@
 ## <span style="color:green">**Figure 1: Ridge**</span>  
-You said to limint the x axis at 2 but we will lose the little bump....Do you want 2?  
-Do you want the blue and red lines?
 ```{r ggridges, fig.width=16, fig.height=18}
@@
   bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
+  add_p() %>% bold_p(t= 0.05) %>% add_overall()
 tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
@@
   bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
+  add_p() %>% bold_p(t= 0.05) %>% add_overall()
 
@@
   bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
+  add_p() %>% bold_p(t= 0.05) %>% add_overall()
 tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
@@
   bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
+  add_p() %>% bold_p(t= 0.05) %>% add_overall()
 tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
@@
   bold_labels() %>% 
-  add_p() %>% bold_p(t= 0.05)
-
-# tbl9 <-
+  add_p() %>% bold_p(t= 0.05) %>% add_overall()
+
 tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
@@
 <br>
-
-<!-- Taxanes -->
-<!-- ```{r Table4 summary Taxanes} -->
-<!-- tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(c(raceeth, "RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>% -->
-<!--   tbl_summary(by = raceeth) %>% -->
-<!--   bold_labels() %>%  -->
-<!--   add_p() %>% bold_p(t= 0.05) -->
-<!-- tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(c(bmi_cat, "RDI" = RDI_pacli_neo, "RDI cat" = RDI_pacli_neo_grp)) %>% -->
-<!--   tbl_summary(by = bmi_cat) %>% -->
-<!--   bold_labels() %>%  -->
-<!--   add_p() %>% bold_p(t= 0.05) -->
-
-<!-- tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>% -->
-<!--   tbl_summary(by = raceeth) %>% -->
-<!--   bold_labels() %>%  -->
-<!--   add_p() %>% bold_p(t= 0.05) -->
-<!-- tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>% -->
-<!--   tbl_summary(by = bmi_cat) %>% -->
-<!--   bold_labels() %>%  -->
-<!--   add_p() %>% bold_p(t= 0.05) -->
-<!-- tbl7 <- -->
-<!--   tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI")) -->
-<!-- tbl8 <- -->
-<!--   tbl_merge(list(tbl3, tbl4)) -->
-<!-- tbl_stack(list(tbl7, tbl8), -->
-<!--           group_header = c( -->
-<!--                            "paclitaxel Neo/Upfront Chemo",  -->
-<!--                            "paclitaxel Adj/Upfront Chemo"), -->
-<!--           quiet = TRUE) -->
-<!-- tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(c(raceeth, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>% -->
-<!--   tbl_summary(by = raceeth) %>% -->
-<!--   bold_labels() %>%  -->
-<!--   add_p() %>% bold_p(t= 0.05) -->
-<!-- tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>% -->
-<!--   distinct(patientid, .keep_all = TRUE) %>% -->
-<!--   select(c(bmi_cat, "RDI" = RDI_pacli_adj, "RDI cat" = RDI_pacli_adj_grp)) %>% -->
-<!--   tbl_summary(by = bmi_cat) %>% -->
-<!--   bold_labels() %>%  -->
-<!--   add_p() %>% bold_p(t= 0.05) -->
-
-<!-- tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>% -->
-<!--   modify_caption("**Upfront Surgery**") -->
-<!-- ``` -->
-<br>
 <br>
@@
 ## 3.Survivals by RDI
-
 ### Survivals RDI by chemotherapy type
-
 ### <span style="color:green">**Figure 2: KM 3 panel figure**</span>
 
-<!-- <div class = "row"> -->
-<!-- <div class = "col-md-6"> -->
-```{r OS dx RDI, fig.height = 7}
-# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_neo_grp, 
-#                    data=Frontline %>% 
-#                      filter(therapy == "Upfront Chemo") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis carboplatin \nUpfront Chemo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
-#                    data=Frontline %>% 
-#                      filter(therapy == "Upfront Chemo") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis carboplatin \nUpfront Chemo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_carbo_adj_grp, 
-#                    data=Frontline %>% 
-#                      filter(therapy == "Upfront Surgery") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis carboplatin \nUpfront Surgery",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-
-# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_neo_grp, 
-#                    data=Frontline %>% 
-#                      filter(therapy == "Upfront Chemo") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis paclitaxel \nUpfront Chemo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_adj_grp, 
-#                    data=Frontline %>% 
-#                      filter(therapy == "Upfront Chemo") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis paclitaxel \nUpfront Chemo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ RDI_pacli_adj_grp, 
-#                    data=Frontline %>% 
-#                      filter(therapy == "Upfront Surgery") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis paclitaxel \nUpfront Surgery",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-```
-<!-- </div> -->
-
-<!-- <div class = "col-md-6"> -->
 ```{r OS treatment RDI, fig.height = 7}
@@
 ) + guides(colour = guide_legend(ncol = 1))
-
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_neo_grp, 
-#                    data=Frontline %>% 
-#                      filter(therapy == "Upfront Chemo") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis paclitaxel \nUpfront Chemo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_adj_grp, 
-#                    data=Frontline %>% 
-#                      filter(therapy == "Upfront Chemo") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis paclitaxel \nUpfront Chemo",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-# 
-# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_pacli_adj_grp, 
-#                    data=Frontline %>% 
-#                      filter(therapy == "Upfront Surgery") %>%
-#                      distinct(patientid, .keep_all = TRUE)
-#                    ),
-#            title = "OS from diagnosis paclitaxel \nUpfront Surgery",
-#            font.main = c(24, "bold", "black"),
-#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
-#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
-#            size = 1.5,
-# 
-#            pval=TRUE,
-#            # legend.labs=c(""),
-#            # palette = c("black", "green","blue", "red"),
-#            # Add risk table
-#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
-#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
-#            tables.theme = theme_survminer(base_size = 5,
-#                                           font.main = c(16, "bold", "black"),
-#                                           font.x = c(16, "bold", "black"),
-#                                           font.y = c(16, "bold", "transparent"),
-#                                           font.tickslab = c(19, "bold", "black")
-#            ),
-# 
-#            legend.title = "", xlab = "Time (in months)"
-# ) + guides(colour = guide_legend(ncol = 1))
-```
-<!-- </div> -->
-<!-- </div> -->
-
+```
 <br>
@@
 # IV.Hazard Ratio
-
-<!-- <span style="color:green">**Table X HR Univariable**</span>   -->
-
-<!-- ## Univariable and drug only adjusted analysis -->
-<!-- ```{r Table 6 HR} -->
-<!-- # tbl2 <- Frontline %>% -->
-<!-- #   filter(therapy == "Upfront Chemo") -->
-<!-- # tbl1 <- tbl2 %>% -->
-<!-- #   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>%  -->
-<!-- #   tbl_uvregression(method = survival::coxph, -->
-<!-- #                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>%  -->
-<!-- #   add_ -->
-<!-- # tbl2 <- tbl2 %>% -->
-<!-- #   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
-<!-- #   tbl_uvregression(method = survival::coxph, -->
-<!-- #                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- #  -->
-<!-- #  -->
-<!-- # tbl3 <- Frontline %>% -->
-<!-- #   filter(therapy == "Upfront Surgery") -->
-<!-- # tbl3 <- tbl3 %>% -->
-<!-- #   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
-<!-- #   tbl_uvregression(method = survival::coxph, -->
-<!-- #                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
-<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- # tbl5 <- tbl_merge(list(tbl2, tbl3)) -->
-<!-- #  -->
-<!-- # # tbl4 <- tbl_merge(list(tbl4_1, tbl4_2)) %>% -->
-<!-- # #   modify_spanning_header(everything() ~ NA_character_) -->
-<!-- #  -->
-<!-- # tbl_stack(list(tbl1, tbl5)) %>% -->
-<!-- #   bold_labels() %>% -->
-<!-- #   italicize_levels() -->
-
-<!--   # trial %>% -->
-<!--   # select(age, grade, stage, trt) %>% -->
-<!--   # mutate(grade = paste("Grade", grade)) %>% -->
-<!--   # # tbl_strata( -->
-<!--   # #   strata = grade, -->
-<!--   # #   .tbl_fun = -->
-<!--   # #     ~ .x %>% -->
-<!--   #       tbl_summary(by = trt, missing = "no") %>% -->
-<!--   #       add_n() -->
-<!--   # ) -->
-<!-- ``` -->
-
-<!-- Left is univariable, right is adjusted by each drugs `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp,` but not by clinicals. -->
-
-<!-- <div class = "row"> -->
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r Table 61 HR} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel/Upfront Chemo",  -->
-<!--                            "paclitaxel/Upfront Chemo", -->
-<!--                            "paclitaxel/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- </div> -->
-
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl21 <- -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
-<!--              event = tbl2$vital_status -->
-<!--              ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp, -->
-<!--         data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>%  -->
-<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl31 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status -->
-<!--              ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp, -->
-<!--         data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>%  -->
-<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl21, tbl31), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- </div> -->
-<!-- </div> -->
-
-<br>
-<br>
-
 ## Multivariable
-<!-- ### RDI group -->
-<!-- <span style="color:green">**Table 9 HR Multivariable**</span>   -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + ` -->
-<!-- `imp_stagecat + histology + imp_debulking`  -->
-<!-- ```{r Table 5 HR adjusted rdi group} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # # Pacli -->
-<!-- #  -->
-<!-- # tbl2 <- Frontline %>% -->
-<!-- #   filter(therapy == "Upfront Chemo") -->
-<!-- # tbl1 <-  -->
-<!-- #   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!-- #              event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- # tbl2 <-  -->
-<!-- #   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!-- #              event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- # tbl3 <- Frontline %>% -->
-<!-- #   filter(therapy == "Upfront Surgery") -->
-<!-- # tbl3 <-  -->
-<!-- #   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!-- #              event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- # tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!-- #           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!-- #                            "paclitaxel Adj/Upfront Chemo", -->
-<!-- #                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!-- #   bold_labels() %>% -->
-<!-- #   italicize_levels() -->
-<!-- ``` -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + ` -->
-<!-- `imp_stagecat + histology`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # # Pacli -->
-<!-- #  -->
-<!-- # tbl2 <- Frontline %>% -->
-<!-- #   filter(therapy == "Upfront Chemo") -->
-<!-- # tbl1 <-  -->
-<!-- #   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!-- #              event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- # tbl2 <-  -->
-<!-- #   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!-- #              event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- # tbl3 <- Frontline %>% -->
-<!-- #   filter(therapy == "Upfront Surgery") -->
-<!-- # tbl3 <-  -->
-<!-- #   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!-- #              event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- # tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!-- #           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!-- #                            "paclitaxel Adj/Upfront Chemo", -->
-<!-- #                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!-- #   bold_labels() %>% -->
-<!-- #   italicize_levels() -->
-<!-- ``` -->
-<br>
-<br>
-
-<!-- ### Continous -->
-<!-- <span style="color:green">**Table 10 HR Multivariable**</span>   -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +` -->
-<!-- `imp_stagecat + histology + imp_debulking`  -->
-<!-- ```{r rdi continous} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!--                            "paclitaxel Adj/Upfront Chemo", -->
-<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + raceeth + ageatdx +` -->
-<!-- `imp_stagecat + histology`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!--                            "paclitaxel Adj/Upfront Chemo", -->
-<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<br>
-<br>
-
 ## Adjusted by other drug
-### RDI group
 ## <span style="color:green">**Table 3 HR Multivariable**</span>
 
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ ` -->
-<!-- `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +` -->
-<!-- `raceeth + ageatdx + imp_stagecat + histology + imp_debulking`  -->
-<!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl21 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl31 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl21, tbl31), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-<!-- PH assumption Upfront Chemo -->
-<!-- ```{r prop H} -->
-<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status -->
-<!--            ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking,  -->
-<!--       data =  tbl2)  %>%  -->
-<!--   cox.zph() -->
-<!-- ``` -->
-
-<!-- PH assumption Upfront Surgery -->
-<!-- ```{r} -->
-<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status -->
-<!--            ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(imp_stagecat) + strata(histology) + imp_debulking, data =   -->
-<!--         tbl3) %>% -->
-<!--   cox.zph() -->
-<!-- ``` -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ ` -->
-<!-- `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + ` -->
-<!-- `raceeth + ageatdx + imp_stagecat + histology`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-### Carbo only
 `RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking`
@@
 ```
-
-<br>
-<br>
-
-<!-- ### Continous -->
-<!-- <span style="color:green">**Table 12 HR Multivariable**</span>   -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ ` -->
-<!-- `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +` -->
-<!-- `raceeth + ageatdx + imp_stagecat + histology + imp_debulking`  -->
-<!-- ```{r rdi continous adjusted by other drug} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl21 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl31 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl21, tbl31), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-<!-- PH assumption Upfront Chemo -->
-<!-- ```{r prop H c} -->
-<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl2)  %>%  -->
-<!--   cox.zph() -->
-<!-- ``` -->
-
-<!-- PH assumption Upfront Surgery -->
-<!-- ```{r} -->
-<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology + imp_debulking, data =  tbl3) %>% -->
-<!--   cox.zph() -->
-<!-- ``` -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ ` -->
-<!-- `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj +` -->
-<!-- `raceeth + ageatdx + stagecat + histology`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + imp_stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
 <br>
@@
 
-<!-- # V.More precise RDI -->
-
-<!-- As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed -->
-
-<!-- ```{r echo=TRUE} -->
-<!-- # Highly underdosed: < 0.75 -->
-<!-- # Underdosed: >= 0.75 to <0.85 -->
-<!-- # Adequate dosing: >= 0.85 to <1.10 -->
-<!-- # Overdosing: >=1.10 -->
-<!-- ``` -->
-<!-- Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI) -->
-<!-- ```{r, fig.width=12, fig.height=12} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
-<!--   geom_point(alpha = 0.7, size = 0.75)+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
-<!--   geom_jitter()+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
-
-<!-- ``` -->
-<!-- Here I just wanted to see if we have more or less underdosing / overdosing with BMI -->
-<!-- ```{r, fig.width=12, fig.height=12} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   ggplot(aes(x= RDI_grp1, fill = drugname))+ -->
-<!--   geom_bar(position = position_dodge())+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   facet_wrap(. ~ therapy, ncol = 2, scales = "free")+ -->
-<!--   coord_flip() -->
-<!-- ``` -->
-
-<!-- ```{r, fig.width=12} -->
-<!-- # Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!-- #   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
-<!-- #   geom_bar(position = position_dodge())+ -->
-<!-- #   theme_minimal(base_size = 10)+ -->
-<!-- #   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+ -->
-<!-- #   coord_flip() -->
-<!-- ``` -->
-
-<!-- ```{r} -->
-<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
-<!--   # filter(linenumber_new == "1") %>% -->
-<!--   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
-<!--   geom_bar(position = "fill")+ -->
-<!--   theme_minimal(base_size = 10)+ -->
-<!--   coord_flip()+ -->
-<!--   facet_wrap(.~ therapy) -->
-<!-- ``` -->
-<!-- As you can see above in green, we have a lot of patient who are overdose. -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- ## Hazard Ratio RDI 2 -->
-
-<!-- <span style="color:green">**Table HR**</span> -->
-
-<!-- ### Univariable -->
-<!-- ```{r HR RDI 2} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp1) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel/Upfront Chemo",  -->
-<!--                            "paclitaxel/Upfront Chemo", -->
-<!--                            "paclitaxel/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference. -->
-
-<!-- ### Multivariable -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ RDI_grp1 + raceeth + ageatdx + stagecat` -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!--                            "paclitaxel Adj/Upfront Chemo", -->
-<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- ## Adjusted by other drug -->
-<!-- ### RDI group -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + raceeth + ageatdx + stagecat` -->
-<!-- ```{r Table 5 HR adjusted rdi group adjusted by other drug 2} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp1 + RDI_pacli_neo_grp1 + RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp1 + RDI_pacli_adj_grp1 + raceeth + ageatdx + stagecat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- *** -->
-
-<!-- # VI. Adjusted by **BMI at DX category** -->
-
-<!-- ```{r} -->
-<!-- Frontline_bmi <- Frontline %>% -->
-<!--   filter(!is.na(bmi_cat)) -->
-<!-- ``` -->
-
-<!-- ## Multivariable -->
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + raceeth + ageatdx + stagecat + bmi_cat` -->
-<!-- ```{r bmi HR adjusted} -->
-<!-- # Carbo -->
-<!-- # tbl1 <- Frontline_bmi %>% -->
-<!-- #   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") -->
-<!-- # tbl1 <- -->
-<!-- #   coxph(Surv(time = tbl1$month_at_os_from_treatment, -->
-<!-- #              event = tbl1$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl1) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
-
-<!-- tbl2 <- Frontline_bmi %>% -->
-<!--   filter(drugname == "carboplatin" & therapy == "Upfront Surgery") -->
-<!-- tbl2 <- -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
-<!--              event = tbl2$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline_bmi %>% -->
-<!--   filter(drugname == "carboplatin" & therapy == "Upfront Chemo") -->
-<!-- tbl3 <- -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
-<!--              event = tbl3$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-<!-- # tbl7 <- Frontline_bmi %>% -->
-<!-- #   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant") -->
-<!-- # tbl7 <- -->
-<!-- #   coxph(Surv(time = tbl7$month_at_os_from_treatment, -->
-<!-- #              event = tbl7$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl7) %>% -->
-<!-- #   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
-<!-- tbl8 <- Frontline_bmi %>% -->
-<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Surgery") -->
-<!-- tbl8 <- -->
-<!--   coxph(Surv(time = tbl8$month_at_os_from_treatment, -->
-<!--              event = tbl8$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl8) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl9 <- Frontline_bmi %>% -->
-<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Chemo") -->
-<!-- tbl9 <- -->
-<!--   coxph(Surv(time = tbl9$month_at_os_from_treatment, -->
-<!--              event = tbl9$vital_status) ~ RDI_grp + raceeth + ageatdx + stagecat + bmi_cat, data =  tbl9) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl8, tbl9), -->
-<!--           group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
 # Complete case HR analysis
-## <span style="color:green">**Table S1 HR patient characteristics by inclusion in complete-case**</span>
-
-```{r}
-Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
+```{r}
+Frontline <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
   mutate(comp_cases = case_when(
@@
     TRUE                                   ~ "complete cases"
-  )) %>% 
+  ))
+complete_cases <- Frontline %>% filter(comp_cases == "complete cases")
+```
+
+## <span style="color:green">**Table S1 HR patient characteristics by inclusion in complete-case**</span>  
+```{r}
+Frontline %>% 
   select(c(raceeth, 
            ageatdx,
-
            bmi_at_dx, bmi_cat, 
-
            histology1, "histology",
@@
 
-<!-- ## Univariable and drug only adjusted analysis -->
-
-<!-- <span style="color:green">**Table  HR Univariable**</span>   -->
-
-<!-- <div class = "row"> -->
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r Table  HR} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking)) -->
-<!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_neo, RDI_carbo_neo_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking)) -->
-<!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_carbo_adj, RDI_carbo_adj_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking)) -->
-<!-- tbl1 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_neo, RDI_pacli_neo_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <- tbl2 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking)) -->
-<!-- tbl3 <- tbl3 %>% -->
-<!--   select(vital_status, RDI_pacli_adj, RDI_pacli_adj_grp) %>%  -->
-<!--   tbl_uvregression(method = survival::coxph, -->
-<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vital_status)), -->
-<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel/Upfront Chemo",  -->
-<!--                            "paclitaxel/Upfront Chemo", -->
-<!--                            "paclitaxel/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- </div> -->
-
-<!-- <div class = "col-md-6"> -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo", !is.na(stagecat), !is.na(debulking)) -->
-<!-- tbl21 <- -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
-<!--              event = tbl2$vital_status -->
-<!--              ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp, -->
-<!--         data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>%  -->
-<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery", !is.na(stagecat), !is.na(debulking)) -->
-<!-- tbl31 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status -->
-<!--              ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp, -->
-<!--         data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>%  -->
-<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-
-<!-- tbl_stack(list(tbl21, tbl31), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- </div> -->
-<!-- </div> -->
-
-<!-- <br> -->
-<!-- <br> -->
-
 ## Multivariable
 ### RDI group
-<!-- ## <span style="color:green">**Table  HR Multivariable**</span>   -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp +` -->
-<!-- `raceeth + ageatdx + stagecat + histology + debulking`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!--                            "paclitaxel Adj/Upfront Chemo", -->
-<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~RDI_grp + ` -->
-<!-- `raceeth + ageatdx + stagecat + histology`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_neo_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!--                            "paclitaxel Adj/Upfront Chemo", -->
-<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- ### Continous -->
-<!-- <span style="color:green">**Table 10 HR Multivariable**</span>   -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + ` -->
-<!-- `raceeth + ageatdx + stagecat + histology + debulking`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!--                            "paclitaxel Adj/Upfront Chemo", -->
-<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ mean_RDI_per_drug + ` -->
-<!-- `raceeth + ageatdx + stagecat + histology`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("carboplatin Neo/Upfront Chemo",  -->
-<!--                            "carboplatin Adj/Upfront Chemo", -->
-<!--                            "carboplatin Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-
-<!-- # Pacli -->
-
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl1 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_neo + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl1, tbl2, tbl3), -->
-<!--           group_header = c("paclitaxel Neo/Upfront Chemo",  -->
-<!--                            "paclitaxel Adj/Upfront Chemo", -->
-<!--                            "paclitaxel Adj/Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-<!-- <br> -->
-<!-- <br> -->
-
-<!-- ## Adjusted by other drug -->
-<!-- ### RDI group -->
-<!-- <span style="color:green">**Table  HR Multivariable complete cases**</span>   -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ ` -->
-<!-- `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp +` -->
-<!-- `raceeth + ageatdx + stagecat + histology + debulking`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl21 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking,  -->
-<!--         data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>%  -->
-<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl31 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status -->
-<!--              ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking,  -->
-<!--         data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>%  -->
-<!--   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-
-<!-- tbl_stack(list(tbl21, tbl31), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-<!-- PH assumption Upfront Chemo -->
-<!-- ```{r prop H complete case} -->
-<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status -->
-<!--            ) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology + debulking,  -->
-<!--       data =  tbl2)  %>%  -->
-<!--   cox.zph() -->
-<!-- ``` -->
-
-<!-- PH assumption Upfront Surgery -->
-<!-- ```{r} -->
-<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status -->
-<!--            ) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking,  -->
-<!--       data =  tbl3) %>% -->
-<!--   cox.zph() -->
-<!-- ``` -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status)~ ` -->
-<!-- `RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + ` -->
-<!-- `raceeth + ageatdx + stagecat + histology`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_pacli_neo_grp + RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj_grp + RDI_pacli_adj_grp + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
 ## <span style="color:green">**Table S2 HR Multivariable complete cases**</span>
 
-## Carbo only
 `RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking`
 ```{r}
-tbl2 <- Frontline %>%
+tbl2 <- complete_cases %>%
   filter(therapy == "Upfront Chemo")
@@
   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
-
+tbl3 <- complete_cases %>%
   filter(therapy == "Upfront Surgery")
@@
 ```{r}
-tbl2 <- Frontline %>%
+tbl2 <- complete_cases %>%
   filter(therapy == "Upfront Chemo")
@@
   bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
-tbl3 <- Frontline %>%
+tbl3 <- complete_cases %>%
   filter(therapy == "Upfront Surgery")
@@
 
-<!-- ### Continous -->
-<!-- <span style="color:green">**Table 12 HR Multivariable**</span>   -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ ` -->
-<!-- `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + ` -->
-<!-- `raceeth + ageatdx + stagecat + histology + debulking`  -->
-<!-- ```{r } -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl21 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl31 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl21, tbl31), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
-
-<!-- PH assumption Upfront Chemo -->
-<!-- ```{r prop H complete case c} -->
-<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl2)  %>%  -->
-<!--   cox.zph() -->
-<!-- ``` -->
-
-<!-- PH assumption Upfront Surgery -->
-<!-- ```{r} -->
-<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology + debulking, data =  tbl3) %>% -->
-<!--   cox.zph() -->
-<!-- ``` -->
-
-<!-- `coxph(Surv(time = month_at_os_from_treatment, event = vital_status) ~ ` -->
-<!-- `RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + ` -->
-<!-- `raceeth + ageatdx + stagecat + histology`  -->
-<!-- ```{r} -->
-<!-- tbl2 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Chemo") -->
-<!-- tbl2 <-  -->
-<!--   coxph(Surv(time = tbl2$month_at_os_from_treatment,  -->
-<!--              event = tbl2$vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl2) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl3 <- Frontline %>% -->
-<!--   filter(therapy == "Upfront Surgery") -->
-<!-- tbl3 <-  -->
-<!--   coxph(Surv(time = tbl3$month_at_os_from_treatment,  -->
-<!--              event = tbl3$vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + histology, data =  tbl3) %>% -->
-<!--   tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
-<!-- tbl_stack(list(tbl2, tbl3), -->
-<!--           group_header = c("Upfront Chemo", "Upfront Surgery")) %>% -->
-<!--   bold_labels() %>% -->
-<!--   italicize_levels() -->
-<!-- ``` -->
+***
+<br>
+
+# Serous histology
+```{r serous filter}
+serous <- Frontline %>% filter(histology == "Serous") 
+```
+
+## KM
+```{r serous KM, fig.height = 7}
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo_grp, 
+                   data=serous %>% 
+                     filter(therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from treatment carboplatin \nUpfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
+                   data=serous %>% 
+                     filter(therapy == "Upfront Chemo") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from treatment carboplatin \nUpfront Chemo",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+
+ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp, 
+                   data=serous %>% 
+                     filter(therapy == "Upfront Surgery") %>%
+                     distinct(patientid, .keep_all = TRUE)
+                   ),
+           title = "OS from treatment carboplatin \nUpfront Surgery",
+           font.main = c(24, "bold", "black"),
+           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),
+           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),
+           size = 1.5,
+
+           pval=TRUE,
+           # legend.labs=c(""),
+           # palette = c("black", "green","blue", "red"),
+           # Add risk table
+           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
+           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
+           tables.theme = theme_survminer(base_size = 5,
+                                          font.main = c(16, "bold", "black"),
+                                          font.x = c(16, "bold", "black"),
+                                          font.y = c(16, "bold", "transparent"),
+                                          font.tickslab = c(19, "bold", "black")
+           ),
+
+           legend.title = "", xlab = "Time (in months)"
+) + guides(colour = guide_legend(ncol = 1))
+```
+
+## HR
+### Imputed data
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking`
+```{r}
+tbl2 <- serous %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, 
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- serous %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
+          strata(imp_stagecat) + imp_debulking, 
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat`
+```{r}
+tbl2 <- serous %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, 
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- serous %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ 
+          RDI_carbo_adj_grp + raceeth + ageatdx + 
+          strata(imp_stagecat),
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
+### Complete cases
+```{r}
+serous_complete <- complete_cases %>% filter(histology == "Serous")
+```
+
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking`
+```{r}
+tbl2 <- serous_complete %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking, 
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- serous_complete %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status
+             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
+          strata(stagecat) + debulking, 
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat`
+```{r}
+tbl2 <- serous_complete %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, 
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- serous_complete %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
+          strata(stagecat), 
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
+***
+<br>
+
+# Others histology
+```{r other filter}
+other_hist <- Frontline %>% filter(histology == "Others")
+```
+
+## HR
+### Imputed data
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking`
+```{r}
+tbl2 <- other_hist %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking, 
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- other_hist %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
+          strata(imp_stagecat) + imp_debulking, 
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat`
+```{r}
+tbl2 <- other_hist %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat, 
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- other_hist %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ 
+          RDI_carbo_adj_grp + raceeth + ageatdx + 
+          strata(imp_stagecat),
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+<br>
+<br>
+
+### Complete cases
+```{r}
+others_complete <- complete_cases %>% filter(histology == "Others")
+```
+
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking`
+```{r}
+tbl2 <- others_complete %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking, 
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- others_complete %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status
+             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
+          strata(stagecat) + debulking, 
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
+
+`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat`
+```{r}
+tbl2 <- others_complete %>%
+  filter(therapy == "Upfront Chemo")
+tbl21 <- 
+  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
+             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat, 
+        data =  tbl2) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl3 <- others_complete %>%
+  filter(therapy == "Upfront Surgery")
+tbl31 <- 
+  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
+             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
+          strata(stagecat), 
+        data =  tbl3) %>%
+  tbl_regression(exponentiate = TRUE) %>% 
+  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
+tbl_stack(list(tbl21, tbl31),
+          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
+  bold_labels() %>%
+  italicize_levels()
+```
 <br>

### 2022-05-20 R/02.data cleaning.R

@@ -465,7 +465,8 @@ group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedat
     units == "AUC" &
       amount < 10               ~ NA_real_,
     TRUE                        ~ amount
-  ))# %>% 
+  )) %>%
+  arrange(patientid, episodedate)
 
 # mutate(drugname_type = case_when(
 #   str_detect(drugname, "platin")       ~ "platin",
@@ -537,7 +538,9 @@ therapy_line <- combined_drugs %>%
   mutate(linestartdate = min(episodedate)) %>% 
   mutate(lineenddate = max(episodedate)) %>% 
   ungroup() %>% 
-  select(-c(linenumber_n, maint_rank))
+  select(patientid, linename, linenumber, linenumber_new, 
+         linenumber_adj, everything(),
+         -c(linenumber_n, maint_rank))
 
 # 6.Add a 30 day rule to switch linenumber----
 # group_by(patientid, linenumber_new) %>% 
@@ -837,7 +840,16 @@ Treatment1 %>% distinct(patientid) %>% nrow()
 
 # Create variables for filtering patients
 Treatment <- Treatment1 %>% 
-  filter(route == "Intravenous") %>% 
+  # Rule to remove patients who have a line 1 with route != Intravenous
+  mutate(intravenous_rule = case_when(
+    linenumber_adj == 1 &
+      str_detect(drugname, "carboplatin|paclitaxel") & 
+      route != "Intravenous"                     ~ "exclude"
+  )) %>%
+  group_by(patientid) %>% 
+  fill(intravenous_rule, .direction = "downup") %>% 
+  ungroup() %>% 
+  # filter(route == "Intravenous") %>% 
   # step 1: Flatiron recommendation cleanup
   # 90 days rule between diagnosis and treatment
   group_by(patientid) %>% 
@@ -890,7 +902,7 @@ Treatment <- Treatment1 %>%
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Carboplatin,Paclitaxel Protein-Bound" |
-          linename == "Paclitaxel" |
+          # linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))            ~ NA_character_,
     linenumber_adj == 1                                       ~ "exclude"

### 2022-05-20 R/_drake.R

@@ -9,7 +9,7 @@ source("R/plan.R")
 config <- drake_config(plan, parallelism = "future", jobs = 4, verbose = 1)
 if (!interactive()) config
 
-make(plan)
+# make(plan)
 loadd(clinical_data, vitals, drugs, auc, orderdrug,
       creatinine
       )

### 2022-05-26 Rmd/Manuscript rdi analysis.Rmd
Add practice type analysis

@@
 library(tidyverse)
+library(here)
 library(data.table)
@@
 ```{r loadd}
-creatinine <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/creatinine.rds")
-weight <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/weight.rds")
-height <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/height.rds")
-body_surface_area <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/body_surface_area.rds")
-areaUC <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/areaUC.rds")
-clinical_data <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/clinical_data.rds")
-Treatment <- read_rds("/Users/colinccm/Documents/GitHub/Peres/Treatment_Flatiron/Treatment.rds")
+creatinine <- read_rds(paste0(here(), "/creatinine.rds"))
+weight <- read_rds(paste0(here(), "/weight.rds"))
+height <- read_rds(paste0(here(), "/height.rds"))
+body_surface_area <- read_rds(paste0(here(), "/body_surface_area.rds"))
+areaUC <- read_rds(paste0(here(), "/areaUC.rds"))
+clinical_data <- read_rds(paste0(here(), "/clinical_data.rds"))
+Treatment <- read_rds(paste0(here(), "/Treatment.rds"))
+practice <- read_rds(paste0(here(), "/practice.rds"))
 ```
@@
   theme_consort(margin_h = c(1,6), margin_v = c(0,30))
+```
+<br>
+```{r}
+practice %>% 
+  # Limit to the patietns after exclusion criteria
+  filter(str_detect(PatientID, paste(Frontline$patientid, collapse = "|"))) %>% 
+  select(PracticeType) %>%
+  tbl_summary()
 ```

### 2022-05-26 R/00.create main data.R

@@ -417,6 +417,16 @@ write_csv(
     "/Flatiron/Data from Flatiron/edm_ovarian_472021/NEW_ovarianCLEANwithbiom.csv"
   ))
 
+# Quick add-up for community/academic
+practice <- 
+  read_csv(paste0(
+    path,
+    "/Flatiron/Data from Flatiron/edm_ovarian_472021/Practice.csv"
+  )) 
+practice <- practice %>% 
+  select(PatientID, PracticeType) %>% 
+  distinct()
+write_rds(practice, "practice.rds")
 
 # End creating full clinical data
 

### 2023-01-06 Rmd/Response to reviewers.Rmd
Response to reviewers rmd

---
title: "Flatiron cleaning"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
.figure {
   margin-top: 25px;
   margin-bottom: 100px;
}

table {
    margin-top: 1px;
    margin-bottom: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```
<br>

***

```{r library, include=FALSE}
library(tidyverse)
library(here)
library(data.table)
library(lubridate)
library(psych)
library(ggplot2)
library(gtsummary)
library(survminer)
library(survival)
library(mice)
```

```{r loadd}
creatinine <- read_rds(paste0(here(), "/creatinine.rds"))
weight <- read_rds(paste0(here(), "/weight.rds"))
height <- read_rds(paste0(here(), "/height.rds"))
body_surface_area <- read_rds(paste0(here(), "/body_surface_area.rds"))
areaUC <- read_rds(paste0(here(), "/areaUC.rds"))
clinical_data <- read_rds(paste0(here(), "/clinical_data.rds"))
Treatment <- read_rds(paste0(here(), "/Treatment.rds"))
practice <- read_rds(paste0(here(), "/practice.rds"))
```

# `r emo::ji("spiral_notepad")` This report is using **actual weight**  
<!-- For serous and non serous histology un-comment line 414 -->
***

# `r emo::ji("spiral_notepad")` Reminders of each capping and formula:

Creatinine data are capped as :  
- creat < 0.7 was set at 0.7  
- creat > 3 are eliminated

CrCl calculation :

$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
and is capped at 125.  
<br>

Calculating more BSA values :
$$bsa\_du\_bois = 0.007184 * (height*100)^{0.725} * weight^{0.425}$$
<br>

I clean the data up by keeping the `relativeorderedamount`:  
- >= 50 & <= 175 for taxel and cisplatin  and with a unit in `mg/m2`  
- >= 2  & <= 6   for platin and with a unit in `AUC`

<br>

`expected_dose` is:  
-`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
-`BSA` * `target_auc`           -> for `drugname` == "taxel" or "cisplatin"  
(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).

<br>

Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ given}{expected\ dose}$$

<br>

<span style="color:red">**Please confirm everything is correct**</span>

***

# I. Drug episode cleaning

- Select episodedatasource == "Administrations"

- Combine multiple administrations of the same drug at the same date
Flatiron says:
There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.  
For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.  
Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend.   
Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.

<br>

- Bind everything together to calculate target auc/target dose and expected dose

(hold on to the thought that what I call `target_auc` include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and paclitaxel, they are just present in the same column called `target_auc` for a tidy data organization - You can find the calculations formula at the end of the document)  
When I bind the data together (drug + corresponding creatinine + ...), I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` for Carboplatin, and paclitaxel and their `expected_dose`. It can be days in between but it can also be more.

`r emo::ji("check")`  
We decided to take the creatinine, weight, bsa measured within a month of the cycle start date AND before surgery when Neoadjuvant line, after surgery but before end of line when Adjuvant line

<!-- # Variable for filtering -->

```{r RDI calculation}
Treatment <- Treatment %>% 
  # filter(chemotherapy_type == "Neoadjuvant" |
  #          (chemotherapy_type == "Adjuvant" &
  #             linenumber_adj == 1)) %>%

  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
  ) %>%
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

  # Average RDI by drug by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname) %>%
  # mutate(mean_RDI_per_drug = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
  #   chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  # )) %>% 
  mutate(mean_RDI_per_drug = round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  ) %>% 
  ungroup() %>% 
  mutate(mean_RDI_per_drug = na_if(mean_RDI_per_drug, "NaN"))

RDI_data <- Treatment %>% 
  distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE)
```

```{r RDI calculation group}
RDI_data <- RDI_data %>% 
  # general
  mutate(RDI_grp = case_when(
    mean_RDI_per_drug >= 0.85              ~ "Adequate dosing",
    mean_RDI_per_drug < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  # separated
  mutate(RDI_carbo_neo = case_when(
    drugname == "carboplatin" &
      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_pacli_neo = case_when(
    drugname == "paclitaxel" &
      chemotherapy_type == "Neoadjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_carbo_adj = case_when(
    drugname == "carboplatin" &
      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>% 
  mutate(RDI_pacli_adj = case_when(
    drugname == "paclitaxel" &
      chemotherapy_type == "Adjuvant"    ~ mean_RDI_per_drug,
    TRUE                                    ~ NA_real_
  )) %>%

  mutate(RDI_carbo_neo_grp = case_when(
    RDI_carbo_neo >= 0.85              ~ "Adequate dosing",
    RDI_carbo_neo < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_carbo_neo_grp = factor(RDI_carbo_neo_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_pacli_neo_grp = case_when(
    RDI_pacli_neo >= 0.85              ~ "Adequate dosing",
    RDI_pacli_neo < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_pacli_neo_grp = factor(RDI_pacli_neo_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_carbo_adj_grp = case_when(
    RDI_carbo_adj >= 0.85              ~ "Adequate dosing",
    RDI_carbo_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_carbo_adj_grp = factor(RDI_carbo_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_pacli_adj_grp = case_when(
    RDI_pacli_adj >= 0.85              ~ "Adequate dosing",
    RDI_pacli_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_pacli_adj_grp = factor(RDI_pacli_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed")))
RDI_data %>% distinct(patientid) %>% nrow()
```

```{r RDI_data}
RDI_data <- RDI_data %>% 
  group_by(patientid) %>% 
  fill(RDI_carbo_neo, RDI_carbo_neo_grp, 
       RDI_pacli_neo, RDI_pacli_neo_grp, 
       RDI_carbo_adj, RDI_carbo_adj_grp, 
       RDI_pacli_adj, RDI_pacli_adj_grp, 
       .direction = "downup") %>% 
  ungroup()
RDI_data_per_patients <- RDI_data %>% 
  mutate(carbo_arrange_variable = case_when(
    drugname == "carboplatin"           ~ 1
  )) %>% 
  arrange(carbo_arrange_variable) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(-c(linename, linenumber, linenumber_adj, 
            linenumber_new, linestartdate, lineenddate,
            cycle_drugname, cycle_increment, cycle_start_date,
            cycle_count_perline, cycle_major_drugname))
```
<br>
<br>

# **Number of patients : `r RDI_data_per_patients %>% distinct(patientid) %>% nrow()`**

######################################################################################################################
######################################################################################################################
######################################################################################################################
######################################################################################################################

<!-- # Variable for filtering -->

<!-- ```{r rule between diagnosis and treatment} -->
<!-- drugs1 <- RDI_data_per_patients %>%  -->
<!--   # 1. 60 days rule between diagnosis and treatment # Loss 1 -->
<!--   group_by(patientid) %>%  -->
<!--   mutate(first_drug_date = first(episodedate)) %>%  -->
<!--   mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/ -->
<!--            duration(n=1, units = "days")) %>%  -->
<!--   mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/ -->
<!--            duration(n=1, units = "days")) %>%  -->
<!--   ungroup() %>%  -->
<!--   mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/ -->
<!--            duration(n=1, units = "days") -->
<!--   ) -->
<!-- ``` -->

<br>

## 1. step 1: Flatiron recommendation cleanup

This step is to remove patients from the population that don't follow flatiron recommendations.

- 90 days rule between diagnosis and treatment  
Flatiron propose a conceptual instruction on the 90-day-gap : 90 days between diagnosis and treatment.  
It is meant to exclude patients who didn't get treatment for 90 days which would most likely mean that some treatment data are missing. Patients left after this step:

- 30 days rule excluding patient who didn't survive for at least 30 days after diagnosis  
This is something that Flatiron strongly recommends, but does not require. Flatiron proposal reviewers will likely provide comments on this if not incorporated into a proposal.

- Exclude exclude == "1" coded by Lauren

Are excluded :  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r flatiron_rec}
flatiron_rec <- RDI_data_per_patients %>% 
  filter(is.na(flatiron_rules))
```

**At the end of the step 1, we have `r flatiron_rec %>% distinct(patientid) %>% nrow()` patients.**

<br>

## 2. step 2: Filter patients with clinical characteristics fitting to the study criteria

-	exclude borderline cases (not invasive ovarian cancer)  
- exclude patients whose histology is unknown  
- remove chemotherapy only patients  
- include only patients who received platin and/or taxane (exclude patients who didn't received carboplatin)  
- exclude patients who only received neo + surgery  
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r study_criteria}
study_criteria <- flatiron_rec %>% 
  filter(is.na(borderline))

study_criteria <- study_criteria %>% 
  filter(!is.na(histology)) # %>% 
  # filter(histology == "Serous") 
  # filter(histology == "Others")

study_criteria <- study_criteria %>%
  filter(!is.na(surgerydate)) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type))

study_criteria <- study_criteria %>%
  filter(had_carbo == "Yes")

study_criteria <- study_criteria %>% 
  filter(treatment_sequence == "neo + surg + adj" |
           treatment_sequence == "surg + adj")

study_criteria <- study_criteria %>%
  filter(is.na(line_keep))
```

**At the end of the step 2, we have `r study_criteria %>% distinct(patientid) %>% nrow()` patients.**

<br>

## 3. step 3: Filter out patients with missing data

- exclude the patients who had surgery but we don't have a date of surgery -> NONE removed anymore  
- remove patients with long gap between surgery and adjuvant start (3  months) -> NONE removed anymore  
- exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded)
- exclude patients for whose no RDI were available FOR CARBOPLATIN

```{r missing_data}
missing_data <- study_criteria %>% 
  filter(!(issurgery == "Yes" & is.na(surgerydate)))

missing_data <- missing_data %>%
  filter(is.na(gap_surg_drugs))

missing_data <- missing_data %>% 
  filter(days_at_first_drug >= 0 &
           (is.na(surgerydate) | days_at_surg >= 0)
         )

missing_data <- missing_data %>% 
  # remove these patients who switched C > C 
  filter((
    therapy == "Upfront Chemo" &
      (!is.na(RDI_carbo_neo) & 
         !is.na(RDI_carbo_adj)) 
  ) | (
    therapy == "Upfront Surgery" &
      (!is.na(RDI_carbo_adj))
  )
  )
```
**At the end of the step 3, we have `r missing_data %>% distinct(patientid) %>% nrow()` patients.**

## 4. step 4: Include patients with treatments following the standard of clinical care

- exclude patients with other than intravenous drugs
- exclude patients with more than 1 line as Neo
- exclude patients with maintenance within their frontline
- exclude patients with more than 6 cycles in Neo, more than 9 cycles **total** in upfront chemo or more than 9 cycles in upfront surgery
- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
- exclude patients who switch drug within a line
```{r standard_care}
standard_care <- missing_data %>% 
  # Remove patients with more than 1 line as Neo
  filter(is.na(neo_more_more_than_1line)) %>% 
  filter(is.na(intravenous_rule))

standard_care <- standard_care %>% 
  filter(is.na(frontline_has_maintenance))

standard_care <- standard_care %>% 
  filter(is.na(too_many_cycle))

standard_care <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

Frontline <- standard_care %>%
  filter(is.na(switch_drugs))
```

<!-- TABLES -->

```{r}
# missing_data %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(had_neo, had_adj, therapy) %>% 
#   tbl_summary(by = therapy,
#               type = list(had_neo ~ "dichotomous", 
#                           had_adj ~ "dichotomous"),
#               missing = "no")
# # therapy_line %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(therapy, treatment_sequence) %>% 
# #   tbl_summary(by = therapy)
```

<!-- First table is frontline Neo, second table is frontline Adj. -->
```{r}
# # drugs1 %>% Need to do in Frontline
#   filter(linenumber == 1
#          ) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))
# 
# # missing_data %>% 
# #   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(linename) %>% 
# #   tbl_summary(sort = list(everything() ~ "frequency"))
```

<!-- ### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line -->
```{r Number of patient who switch line}
# therapy_line %>% 
#   mutate(change_line = case_when(
#     linenumber == 1 & 
#       linenumber_new == 2 &
#       chemotherapy_type == "Adjuvant" &
#       therapy == "Upfront Chemo"                   ~ 1,
#     TRUE                                           ~ 0
#   )) %>% 
#   arrange(desc(change_line)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(change_line) %>% 
#   tbl_summary()
```

<!-- For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line? -->
```{r}
# therapy_line %>% 
#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
#            duration(n = 1, units = "days")) %>% 
#   filter(linenumber == 1 & linenumber_new == 2) %>% 
#   # select(patientid, linenumber, linenumber_new, linenumber_adj, 
#   #        drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x= line_duration))+
#   geom_histogram(aes(fill = route), binwidth = 7) +
#   theme_minimal(base_size = 14)+
#   labs(x="Line duration", 
#        y="Number of Patient",
#        caption = "Each bar represents 7 days, bottom plot is zoomed in")+
#   ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)
```
<!-- Several patients have a short line.   -->
<!-- `r emo::ji("question_mark")` **Should we remove the patient with a line lasting less than a cycle** We said during October meeting to check if were IP administration.... -->

```{r}
# therapy_line %>% 
#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
#            duration(n = 1, units = "days")) %>% 
#   filter(linenumber == 1 & linenumber_new == 2) %>% 
#   select(patientid, surgerydate, episodedate, line_duration, drugname,
#          chemotherapy_type, therapy, 
#          linenumber, linenumber_new, route, amount) %>% 
#   filter(line_duration < 30) %>% 
#   arrange(line_duration, patientid, episodedate)
```

<!-- Here a real example of this type of patient : initial `linenumber` = 1 but had surgery in 09/2019 so part of this line in moved to `linenumber_new` = 2 and then coded as adjuvant line.   -->
<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle. <span style="color:red">**Is that correct?**</span>   -->
```{r Number of patient who switch line2, rows.print=30}
# Problem F0000AD999ABF but would be good for F003F2BEEDB37
# therapy_line %>% 
#   filter(str_detect(patientid, "F41E15E18E008")) %>% 
#   arrange(patientid, episodedate) %>% 
#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)
```

<!-- Here an example a little more complicated because the patient had surgery 05/2017 and the same type of switch but then had a 3rd line (used to be line 2 in flatiron).     -->
<!-- So when we will calculate RDI for frontline adjuvant, it will only include this 1 cycle switched to adjuvant and not the longer line witch was coded 2 by flatiron. <span style="color:red">**Is that correct?**</span>   -->
```{r, rows.print=30}
# therapy_line %>% 
#   filter(str_detect(patientid, "FC9D28216FEBE")) %>% 
#   arrange(patientid, episodedate) %>% 
#   select(linenumber, linenumber_new, episodedate, chemotherapy_type, drugname)

# therapy_line %>% 
#   mutate(change_line = case_when(
#     linenumber == 1 & 
#       linenumber_new == 2 &
#       chemotherapy_type == "Adjuvant" &
#       treatment_sequence == "neo + surg + adj"     ~ 1,
#     TRUE                                           ~ 0
#   )) %>% 
#   filter(change_line == 1) %>% 
#   group_by(patientid) %>% 
#   mutate(firstdate = first(episodedate)) %>% 
#   mutate(lastdate = last(episodedate)) %>% 
#   ungroup() %>% 
#   mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x=time_of_switch_line, fill = ..count..))+
#   geom_histogram(binwidth = 7)+
#   theme_minimal(base_size = 14)+
#   ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
#   scale_y_continuous(#breaks=c(0, 50, 100, 150),
#                      minor_breaks=c(10, 20, 30, 40)#,
#                      #labels = c(0, 50, 100, 150)
#   )
```
<!-- `r emo::ji("question_mark")`   -->
<!-- <span style="color:red">**So the bigger question is : Is it acceptable to include the patients who have a switched line?**</span> -->

<!-- <span style="color:red">**Random question : within 1 cycle we can have taxanes multiple times, is it possible for carboplatin or cisplatin?**</span>   -->

<br>
<br>

# **The final number of patients in the dataset is `r Frontline %>% distinct(patientid) %>% nrow()`**

Imputation for stagecat and debulking status

https://bookdown.org/mwheymans/bookmi/data-analysis-after-multiple-imputation.html#data-analysis-in-spss
https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf

Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.  
Look at the Cox regression model before imputation.

### For Upfront Chemo
```{r imputation up Chemo}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
# nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os_from_treatment, vital_status)
dataset <- data.frame(data, Hazard)
```

<!-- Start imputation to look at matrix -->
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os_from_treatment"] <- 0
# Pred
```

<!-- patientid is not used which is good. But SURGERYDATE IS NOT. -->
```{r}
Pred[, "surgerydate"] <- 1
Pred["surgerydate", "surgerydate"] <- 0
# Pred
```

<!-- Imputation and cox regression model on imputed data using the new predictor matrix. -->
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

Do m = `r multiple_imputations_number` (how to choose is explained in https://www.ebpi.uzh.ch/dam/jcr:dc0cef17-29c7-4e61-8d33-e690561ab7ae/mi_intro20191001.pdf depends of the fmi. The max fmi = `r multiple_imputations_number / 100` that we multiply by 100)
```{r}
Cox.imp <- mice(dataset, m= multiple_imputations_number, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo + RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

# summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
#   kableExtra::kable() %>%
#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
<!-- Above results are exponentiated (imputed data).   -->
<!-- As a reminder before imputation results are : -->
```{r}
# nonimp_cox_model
```

<!-- Complete the chemo data and merge with original -->
```{r}
imputed_data_chemo <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_stagecat = stagecat, imp_debulking = debulking)
```

### For Upfront Surgery
Select the variables that may be important for predicting stagecat and debulking status:  
patientid, month_at_os_from_treatment, vital_status, raceeth, ageatdx, stagecat, debulking, histology, diagnosisdate, surgerydate, RDI_carbo_adj, RDI_pacli_adj BUT NOT therapy.

```{r imputation up Surgery}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os_from_treatment, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
# nonimp_cox_model

Hazard <- nelsonaalen(data, month_at_os_from_treatment, vital_status)
dataset <- data.frame(data, Hazard)
```

<!-- Start imputation to look at matrix -->
```{r}
Cox.imp <- mice(dataset, m=1, maxit=0, seed=123, printFlag=F)
# summary(Cox.imp)
Pred <- Cox.imp$predictorMatrix
# Pred["debulking", "month_at_os_from_treatment"] <- 0
# Pred
```

<!-- patientid is not used which is good. But SURGERYDATE IS NOT -->
```{r}
Pred[, "surgerydate"] <- 1
Pred["surgerydate", "surgerydate"] <- 0
# Pred
```

<!-- Imputation and cox regression model on imputed data using the new predictor matrix. -->
```{r}
# Start imputations using mice
Cox.imp <- mice(dataset, m=5, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)
check1 <- with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))
# pool(check1)$pooled
multiple_imputations_number <- round(max(pool(check1)$pooled$fmi),2)*100
```

Do m = `r multiple_imputations_number` (The max fmi = `r multiple_imputations_number / 100` that we multiply by 100)
```{r}
Cox.imp <- mice(dataset, m= multiple_imputations_number, maxit=50, 
                predictorMatrix=Pred,
                seed=123, printFlag=F)

fit.Cox <-
  with(data = Cox.imp,
       exp = coxph(
         Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj + raceeth + ageatdx + stagecat + debulking + histology
       ))

# summary(pool(fit.Cox), conf.int = TRUE, exponentiate = TRUE) %>%
#   kableExtra::kable() %>%
#   kableExtra::kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```
<!-- Above results are exponentiated (imputed data).   -->
<!-- As a reminder before imputation results are : -->
<!-- ```{r} -->
<!-- nonimp_cox_model -->
<!-- ``` -->

<!-- Complete the data and merge with original -->
```{r combine imputed data}
imputed_data_surg <- complete(Cox.imp, include = FALSE) %>% 
  rename(imp_stagecat = stagecat, imp_debulking = debulking)

imputed_data <- bind_rows(imputed_data_chemo, imputed_data_surg)

Frontline <- 
  full_join(Frontline, imputed_data %>% 
              select(patientid, starts_with("imp_")), 
            by = "patientid") 
```
<br>

***

<br>

<!-- # <span style="color:green">**Consort diagram**</span> -->

<!-- ```{r consort, fig.width=12} -->
<!-- library(ggconsort) -->
<!-- study_cohorts <-  -->
<!--   RDI_data_per_patients %>% -->
<!--   cohort_start("**Assessed for eligibility**") %>% -->
<!--   # Define cohorts using named expressions -->
<!--   # Notice that you can use previously defined cohorts in subsequent steps -->
<!--   cohort_define( -->
<!--   flatiron_rec = .full %>%  -->
<!--     filter(is.na(flatiron_rules)), -->

<!--   study_criteria = flatiron_rec  %>%  -->
<!--     filter(is.na(borderline)) %>%  -->
<!--     filter(!is.na(histology)) %>% -->
<!--     filter(!is.na(surgerydate)) %>% -->
<!--     filter(had_carbo_pacli == "Yes") %>%  -->
<!--     filter(treatment_sequence == "neo + surg + adj" | -->
<!--              treatment_sequence == "surg + adj") %>% -->
<!--     filter(is.na(line_keep)), -->

<!--     missing_data = study_criteria  %>%  -->
<!--     filter(!(issurgery == "Yes" & is.na(surgerydate))) %>% -->
<!--     filter(is.na(gap_surg_drugs)) %>% -->
<!--     filter(days_at_first_drug >= 0 & -->
<!--              (is.na(surgerydate) | days_at_surg >= 0)) %>% -->
<!--     filter(( -->
<!--       therapy == "Upfront Chemo" & -->
<!--         (!is.na(RDI_carbo_neo) &  -->
<!--            !is.na(RDI_carbo_adj))  -->
<!--     ) | ( -->
<!--       therapy == "Upfront Surgery" & -->
<!--         (!is.na(RDI_carbo_adj)) -->
<!--     ) -->
<!--     ), -->

<!--     standard_care = missing_data %>%  -->
<!--     filter(is.na(neo_more_more_than_1line)) %>% -->
<!--     filter(is.na(intravenous_rule)) %>%  -->
<!--     filter(is.na(frontline_has_maintenance)) %>% -->
<!--     filter(is.na(too_many_cycle)) %>%  -->
<!--     filter(is.na(wrong_pacli_dosedense)) %>% -->
<!--     filter(is.na(switch_drugs)), -->

<!--     Frontline = standard_care, -->

<!--   # anti_join is useful for counting exclusions -->
<!--     excluded1 = anti_join(.full, flatiron_rec, by = "patientid"), -->
<!--     excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"), -->
<!--     excluded3 = anti_join(study_criteria, missing_data, by = "patientid"), -->
<!--     excluded4 = anti_join(missing_data, standard_care, by = "patientid") -->
<!--   ) %>% -->
<!--   # Provide text labels for cohorts -->
<!--   cohort_label( -->
<!--     excluded1 = "excluded albeit flatiron recommendation", -->
<!--     excluded2 = "<span style='color:darkblue'>no study criteria</span>", -->
<!--     excluded3 = "<span style='color:darkblue'>no missing_data</span>", -->
<!--     excluded4 = "<span style='color:darkblue'>no standard_care</span>", -->
<!--     flatiron_rec = "**Fit flatiron rec**", -->
<!--     study_criteria = "**Fit study criteria**", -->
<!--     missing_data = "**Non missing data**", -->
<!--     Frontline = "**Population Study**" -->
<!--   ) -->

<!-- study_consort <- study_cohorts %>% -->
<!--   consort_box_add( -->
<!--     "full", 0, 40, cohort_count_adorn(study_cohorts, .full) -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "exc_flatiron_rec", 0.2, 35, glue::glue( -->
<!--       "{cohort_count_adorn(study_cohorts, excluded1)}<br>  -->
<!--       • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br> -->
<!--       • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis -->
<!--       ") -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec) -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "exc_study_criteria", 0.2, 25, glue::glue( -->
<!--       "{cohort_count_adorn(study_cohorts, excluded2)}<br>  -->
<!--       • Borderline cases (not invasive ovarian cancer) <br> -->
<!--       • exclude patients whose histology is unknown <br> -->
<!--       • remove chemotherapy only patients <br> -->
<!--       • include patients who received carboplatin +/- taxane +/- Bev in a adj +/- neo settings -->
<!--       ") -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria) -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "exc_missing_data", 0.2, 15, glue::glue( -->
<!--       "{cohort_count_adorn(study_cohorts, excluded3)}<br>  -->
<!--       • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br>  -->
<!--       • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br>  -->
<!--       • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br>  -->
<!--       • exclude patients for whose no RDI were available -->
<!--       ") -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data) -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "exc_standard_care", 0.2, 5, glue::glue( -->
<!--       "{cohort_count_adorn(study_cohorts, excluded4)}<br>  -->
<!--       • exclude patients with more than 1 line as Neo <br>  -->
<!--       • exclude patients with maintenance within their frontline <br>  -->
<!--       • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery -->
<!--       ") -->
<!--   ) %>% -->
<!--   consort_box_add( -->
<!--     "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline) -->
<!--   ) %>% -->

<!--   consort_arrow_add( -->
<!--     end = "exc_flatiron_rec", end_side = "left", start_x = 0, start_y = 35 -->
<!--   ) %>% -->
<!--   consort_arrow_add( -->
<!--     end = "exc_study_criteria", end_side = "left", start_x = 0, start_y = 25 -->
<!--   ) %>% -->
<!--   consort_arrow_add( -->
<!--     end = "exc_missing_data", end_side = "left", start_x = 0, start_y = 15 -->
<!--   ) %>% -->
<!--   consort_arrow_add( -->
<!--     end = "exc_standard_care", end_side = "left", start_x = 0, start_y = 5 -->
<!--   ) %>% -->
<!--   consort_arrow_add( -->
<!--     end = "Frontline", end_side = "top", start_x = 0, start_y = 40 -->
<!--   ) -->

<!-- study_consort %>% -->
<!--   ggplot() +  -->
<!--   geom_consort() + -->
<!--   theme_consort(margin_h = c(1,6), margin_v = c(0,30)) -->
<!-- ``` -->
<!-- <br> -->
<!-- ```{r} -->
<!-- practice %>%  -->
<!--   # Limit to the patietns after exclusion criteria -->
<!--   filter(str_detect(PatientID, paste(Frontline$patientid, collapse = "|"))) %>%  -->
<!--   select(PracticeType) %>% -->
<!--   tbl_summary() -->
<!-- ``` -->
<!-- <br> -->

<!-- *** -->

# II.Data analysis
## Explore the dataset

```{r exploratory data analysis}
full_data_study_pop <-
  Treatment %>%
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>%
  arrange(patientid, episodedate, drugname) %>% 
  filter(had_carbo == "Yes") %>% 
  filter(linenumber_adj == 1)

```

<!-- ### Number of cycle received by patients in our study population -->

<!-- <span style="color:green">**Table supp X Number of cycle in Neo**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>% -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment) %>% -->
<!--   tbl_summary() -->
<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>% -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment) %>% -->
<!--   tbl_summary(type = list(cycle_increment ~ "continuous")) -->

<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(linename) %>% -->
<!--   tbl_summary() -->
<!-- ``` -->

<!-- <span style="color:green">**Table supp X Number of cycle in Adj**</span> -->
<!-- ```{r} -->
<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Adjuvant") %>% -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment, therapy) %>% -->
<!--   tbl_summary(by = therapy) -->
<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Adjuvant") %>% -->
<!--   arrange(desc(cycle_increment)) %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(cycle_increment, therapy) %>% -->
<!--   tbl_summary(by = therapy, -->
<!--               type = list(cycle_increment ~ "continuous")) -->

<!-- full_data_study_pop %>% -->
<!--   filter(chemotherapy_type == "Adjuvant") %>% -->
<!--   distinct(patientid, .keep_all = TRUE) %>% -->
<!--   select(linename, therapy) %>% -->
<!--   tbl_summary(by = therapy) -->
<!-- ``` -->
<!-- <br> -->
<br>

***

# Clinical Analysis
## 1.Clinical summary table

<!-- <span style="color:green">**Table X Overall summary demographic/clinical data**</span> -->
<!-- ```{r Table 1} -->
<!-- Frontline %>%  -->
<!--   select(c(vital, raceeth,  -->
<!--            agecat, "ageatdx", -->

<!--            bmi_at_dx, bmi_cat,  -->
<!--            weight_at_dx, height_at_dx, bsa_at_dx, -->

<!--            histology1, "histology", "stagecat", imp_stagecat, -->

<!--            "brca1_germline", "brca2_germline", "brca_germline", "brca1_tumor", -->
<!--            "brca2_tumor", "brca_tumor", "brca1_unknown", "brca2_unknown", "brca_unknown")) %>%  -->
<!--   tbl_summary() %>% bold_labels() -->
<!-- ``` -->

<!-- <span style="color:green">**Table X Summary demographic/clinical data by race**</span> -->
<!-- ```{r Table 2} -->
<!-- Frontline %>%  -->
<!--   select(c(raceeth, "vital", -->
<!--            agecat, "ageatdx", -->

<!--            "bmi_at_dx", bmi_cat, "BSA", -->
<!--            "stagecat", imp_stagecat)) %>%  -->
<!--   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05) -->
<!-- ``` -->
<!-- <br> -->

## <span style="color:green">**Table 1 Summary demographic/clinical data by bmi**</span>
```{r Table 3}
Frontline <- Frontline %>% 
  mutate(year_diagnosis = year(Frontline$diagnosisdate)) %>% 
  mutate(dx_year_cat = case_when(
    year_diagnosis %in% c(2011, 2012, 2013, 2014, 2015)        ~ "2011-2015",
    year_diagnosis %in% c(2016, 2017, 2018)                    ~ "2016-2018",
    year_diagnosis %in% c(2019, 2020, 2021)                    ~ "2019-2021"
  ))

summary(Frontline$year_diagnosis)
table(Frontline$year_diagnosis)
table(Frontline$dx_year_cat)

Frontline %>% 
  select(c(dx_year_cat, month_at_os, month_at_os_from_treatment,
           raceeth, "vital",
           agecat, "ageatdx",
            histology1, "histology",
           "bmi_at_dx", bmi_cat, "BSA",
           "stagecat", imp_stagecat,
           therapy, debulking, imp_debulking)) %>% 
  tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)

Frontline %>% 
  select(c(dx_year_cat, 
           therapy)) %>% 
  tbl_summary(by = therapy) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)

```
<br>
<br>

***

<br>

# II.Treatment Analysis

<!-- ## 1.Treatment summary table -->

<!-- <span style="color:green">**Table X Summary treatment data by race**</span> -->
<!-- ```{r Table 4} -->
<!-- Frontline %>%  -->
<!--   select(c(raceeth, -->
<!--            "debulking", imp_debulking , "therapy" -->
<!--            )) %>%  -->
<!--   tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05) -->
<!-- ``` -->
<!-- <br> -->

<!-- <span style="color:green">**Table X Summary treatment data by bmi**</span> -->
<!-- ```{r Table 5} -->
<!-- Frontline %>%  -->
<!--   select(c(bmi_cat, -->
<!--            "debulking", imp_debulking, "therapy" -->
<!--            )) %>%  -->
<!--   tbl_summary(by = bmi_cat) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05) -->
<!-- ``` -->

<!-- ## <span style="color:green">**Table S0 Summary of the expected, actual dose, and RDI, Crcl, ...**</span> -->
<!-- Here we calculated the mean of amount, CrCl, BSA, height, weight, creatinine, -->
<!--          target_auc, expected_dose, dose received,  -->
<!--          RDI per patient/therapy/settings for each drug name.   -->
<!-- The tables show the median IQR for carboplatin calculated over patients with the same therapy (Upfront C or S) and setting (Neo or Adj). -->
<!-- ```{r Summary of the expected, actual dose, and RDI} -->
<!-- tbl <- full_data_study_pop %>%  -->
<!--   # Treatment %>%  -->
<!--   # # Limit to the patietns after exclusion criteria -->
<!--   # filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>%  -->
<!--   # arrange(patientid, episodedate, drugname) %>%  -->
<!--   # # group to have RDI by cycle for each drug  -->
<!--   # # group_by(patientid, chemotherapy_type, cycle_increment, drugname) %>% -->
<!--   # # mutate(mean_RDI_per_cycledrug = round(mean(relative_dose_intensity, na.rm = TRUE), 3) -->
<!--   # # ) %>%  -->
<!--   # # ungroup() %>%  -->
<!--   # filter(drugname == "carboplatin") %>%  -->
<!--   # filter(linenumber_adj == 1) %>%  -->

<!--   group_by(patientid, therapy, chemotherapy_type, drugname) %>%  -->
<!--   summarise(amount = mean(amount, na.rm = TRUE),  -->
<!--             BSA = mean(BSA),  -->
<!--             height = mean(height),  -->
<!--             weight = mean(weight),  -->
<!--             creatinine = mean(creatinine), -->
<!--             CrCl = mean(CrCl), -->
<!--             target_auc = mean(target_auc), -->
<!--             expected_dose = mean(expected_dose), -->
<!--             relative_dose_intensity = mean(mean_RDI_per_drug)) %>%  -->
<!--   ungroup() %>%  -->
<!--   mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant"))) -->

<!-- tbl %>% filter(drugname == "carboplatin" & therapy == "Upfront Chemo") %>%  -->
<!--   select(amount, CrCl, BSA, height, weight, creatinine, -->
<!--          target_auc, expected_dose, "dose received" = amount,  -->
<!--          "RDI" = relative_dose_intensity, chemotherapy_type) %>%  -->
<!--   tbl_summary(by = chemotherapy_type) %>% bold_labels() %>% -->
<!--   modify_caption("**Upfront Chemo**") -->

<!-- tbl %>% filter(drugname == "carboplatin" & therapy == "Upfront Surgery") %>%  -->
<!--   select(amount, CrCl, BSA, height, weight, creatinine, -->
<!--          target_auc, expected_dose, "dose received" = amount,  -->
<!--          "RDI" = relative_dose_intensity) %>%  -->
<!--   tbl_summary() %>% bold_labels() %>% -->
<!--   modify_caption("**Upfront Surgery**") -->
<!-- ``` -->
<!-- <br> -->

<!-- <!-- ## 2.Treatment Plots --> -->

<!-- ```{r treatment plots} -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Neoadjuvant") %>%  -->
<!--   distinct(patientid, .keep_all = TRUE) %>%  -->
<!--   select(linename) %>%  -->
<!--   tbl_summary(label = list(linename ~ "line name received as Neoadujant")) -->
<!-- full_data_study_pop %>%  -->
<!--   filter(chemotherapy_type == "Adjuvant" & linenumber_adj == 1) %>%  -->
<!--   distinct(patientid, .keep_all = TRUE) %>%  -->
<!--   select(linename, therapy) %>%  -->
<!--   tbl_summary(by = therapy, -->
<!--               label = list(linename ~ "line name received as Adjuvant")) -->
<!-- ``` -->
<!-- <br> -->

<!-- ## 3.Survivals by treatment -->

<!-- <div class = "row"> -->
<!-- <div class = "col-md-6"> -->
<!-- ```{r treatment survival, fig.height = 7} -->
<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ 1, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ debulking, data=Frontline %>% -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ imp_debulking, data=Frontline %>% -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- # OS by therapy -->
<!-- ggsurvplot(survfit(Surv(month_at_os, vital_status) ~ therapy, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of diagnosis",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->
<!-- </div> -->

<!-- <div class = "col-md-6"> -->
<!-- ```{r, fig.height = 7} -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ 1, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of from first treatment",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ debulking, data=Frontline %>% -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of from first treatment", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ imp_debulking, data=Frontline %>% -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of from first treatment", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- # OS by therapy -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ therapy, data=Frontline %>%  -->
<!--                      distinct(patientid, .keep_all = TRUE)), -->
<!--            title = "OS from date of from first treatment",  -->
<!--            font.main = c(24, "bold", "black"),  -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"),  -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"),  -->
<!--            size = 1.5, -->

<!--            pval=TRUE,  -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"),  -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)"  -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->
<!-- </div> -->
<!-- </div> -->

<br>
<br>

***

<br>

# III.RDI
RDI is calculated by drug so 1 for each Carboplatin, Cisplatin, Oxaloplatin, Paclitaxel, Paclitaxel protein bound, Docetaxel.

```{r echo=TRUE}
# RDI_grp = case_when(
#     mean_RDI_per_drug >= 0.85              ~ "adequate",
#     mean_RDI_per_drug < 0.85               ~ "underdose"
#   ))
```
Start with plotting :

<!-- ## 1.Plots RDI -->
<!-- ## <span style="color:green">**Figure 1: Ridge**</span>   -->
<!-- ```{r ggridges, fig.width=16, fig.height=18} -->
<!-- library(ggridges) -->
<!-- # Frontline %>%  -->
<!-- #   pivot_longer(cols = c(RDI_carbo_neo, RDI_pacli_neo, RDI_carbo_adj, RDI_pacli_adj)) %>%  -->
<!-- #   filter(!is.na(value)) %>%  -->
<!-- #   ggplot(aes(y=raceeth, x=value,  fill=raceeth -->
<!-- #              )) + -->
<!-- #     geom_density_ridges(alpha=0.5) + -->
<!-- #     theme_ridges()+ -->
<!-- #   theme(#text = element_text(size = 14),#axis.text.y = element_blank(), -->
<!-- #         panel.spacing = unit(0.1, "lines"), -->
<!-- #         strip.text.x = element_text(size = 14) -->
<!-- #     ) + -->
<!-- #   geom_vline(xintercept = 1, color = "red", linetype = 2)+ -->
<!-- #   geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+ -->
<!-- #  -->
<!-- #   facet_wrap(therapy ~ name, ncol = 2, scales = "free_x") -->

<!-- Frontline %>%  -->
<!--   pivot_longer(cols = c(RDI_carbo_neo, RDI_carbo_adj), -->
<!--                values_to = "RDI") %>%  -->
<!--   filter(!is.na(RDI)) %>%  -->
<!--   ggplot(aes(y=bmi_cat, x=RDI,  fill=bmi_cat -->
<!--              )) + -->
<!--     geom_density_ridges(alpha=0.5) + -->
<!--     theme_ridges()+ -->
<!--   theme(#text = element_text(size = 14),#axis.text.y = element_blank(), -->
<!--         panel.spacing = unit(0.1, "lines"), -->
<!--         strip.text.x = element_text(size = 14) -->
<!--     ) + -->
<!--   geom_vline(xintercept = 1, color = "red", linetype = 2)+ -->
<!--   geom_vline(xintercept = 0.85, color = "blue", linetype = 2)+ -->

<!--   facet_wrap(therapy ~ name, ncol = 1) -->
<!-- ``` -->

## 2.RDI summary table

```{r}
my_theme <-
  list(
    # Some gt customization
    "as_gt-lst:addl_cmds" = list(
      # make the font size small
      tab_spanner = rlang::expr(gt::tab_options(row.striping.background_color = "lightgrey",
                                                row.striping.include_stub = TRUE,
                                                row.striping.include_table_body = TRUE,
                                                row_group.border.top.color = "blue",
                                                # table.background.color = "white", 
                                                heading.background.color = "lightblue", 
                                                # column_labels.background.color = "orange", 
                                                row_group.background.color = "grey",
                                                stub.background.color = "slateblue", 
                                                summary_row.background.color = "tomato", 
                                                grand_summary_row.background.color = "green")),
      # add a custom title and subtitle to every table
      # user_added1 = rlang::expr(gt::tab_header(
      #   title = "Christelle's Table", subtitle = "Yeap"))#,
      # add a custom data source note
      # user_added2 = rlang::expr(gt::tab_source_note(
      #   source_note = "Source: our data!"))#,
      # stripe the table rows
      user_added1 = rlang::expr(gt::opt_row_striping())#,
      # user_added4 = rlang::expr(gt::opt_table_lines("none"))
      )
    )

reset_gtsummary_theme()
set_gtsummary_theme(my_theme)
```

<br>

## <span style="color:green">**Table 2: Summary RDI data by race and bmi**</span>  
Platin  
```{r Table 7 Summary RDI data by race and bmi}
Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c("RDI Neo" = RDI_carbo_neo, "RDI Neo cat" = RDI_carbo_neo_grp,
           "RDI Adj" = RDI_carbo_adj, "RDI Adj cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary() %>%
  bold_labels() %>% 
  modify_caption("**Upfront Chemo**")

Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c("RDI Neo cat" = RDI_carbo_neo_grp,
           "RDI Adj cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = "RDI Adj cat") %>%
  bold_labels() %>% add_overall() %>% 
  modify_caption("**Upfront Chemo**") %>% 
  modify_spanning_header(all_stat_cols() ~ "**RDI Adj cat**")

tbl1 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
tbl2 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_neo, "RDI cat" = RDI_carbo_neo_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()

tbl3 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
tbl4 <- Frontline %>% filter(therapy == "Upfront Chemo") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()

tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
  modify_caption("**Upfront Chemo**")
tbl8 <-
  tbl_merge(list(tbl3, tbl4))
tbl_stack(list(tbl7, tbl8),
          group_header = c(
                           "carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo"),
          quiet = TRUE)

tbl5 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(raceeth, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = raceeth) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()
tbl6 <- Frontline %>% filter(therapy == "Upfront Surgery") %>%
  select(c(bmi_cat, "RDI" = RDI_carbo_adj, "RDI cat" = RDI_carbo_adj_grp)) %>%
  tbl_summary(by = bmi_cat) %>%
  bold_labels() %>% 
  add_p() %>% bold_p(t= 0.05) %>% add_overall()

tbl_merge(list(tbl5, tbl6), tab_spanner = c("Race/Ethnicity", "BMI")) %>%
  modify_caption("**Upfront Surgery**")
```
<br>
<br>

***

<br>

<!-- ## 3.Survivals by RDI -->
<!-- ### Survivals RDI by chemotherapy type -->
<!-- ### <span style="color:green">**Figure 2: KM 3 panel figure**</span>   -->

<!-- ```{r OS treatment RDI, fig.height = 7} -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo_grp,  -->
<!--                    data=Frontline %>%  -->
<!--                      filter(therapy == "Upfront Chemo") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Chemo", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp,  -->
<!--                    data=Frontline %>%  -->
<!--                      filter(therapy == "Upfront Chemo") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Chemo", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp,  -->
<!--                    data=Frontline %>%  -->
<!--                      filter(therapy == "Upfront Surgery") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Surgery", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->
<!-- <br> -->
<!-- <br> -->

***

# IV.Hazard Ratio
## Multivariable
## Adjusted by other drug
## <span style="color:green">**Table 3 HR Multivariable**</span>

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking+ dx_year_cat`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H Table 3 HR Multivariable adj deb}
coxph(Surv(time = tbl2$month_at_os_from_treatment,
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking,
      data =  tbl2)  %>%
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
        imp_stagecat + strata(histology) + imp_debulking,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
        strata(imp_stagecat) + strata(histology) + imp_debulking,
      data = tbl3) %>%
  cox.zph()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + dx_year_cat`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ 
          RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + dx_year_cat,
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H Table 3 HR Multivariable non adj deb}
coxph(Surv(time = tbl2$month_at_os_from_treatment,
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology,
      data = tbl2)  %>%
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
        imp_stagecat + strata(histology),
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
        strata(imp_stagecat) + strata(histology),
      data = tbl3) %>%
  cox.zph()
```
<br>
<br>

***

<br>

# Complete case HR analysis
```{r}
Frontline <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  mutate(comp_cases = case_when(
    is.na(stagecat) |
      is.na(debulking)                     ~ "excluded",
    TRUE                                   ~ "complete cases"
  ))
complete_cases <- Frontline %>% filter(comp_cases == "complete cases")
```

## <span style="color:green">**Table S1 HR patient characteristics by inclusion in complete-case**</span>
```{r}
Frontline %>%
  select(c(dx_year_cat, raceeth,
           ageatdx,
           bmi_at_dx, bmi_cat,
           histology1, "histology",
           "stagecat", imp_stagecat,
           therapy,
           debulking, imp_debulking,
           comp_cases)) %>%
  tbl_summary(by = comp_cases) %>%
  bold_labels() %>% add_p() %>% bold_p()
```
<br>

## Multivariable
### RDI group
## <span style="color:green">**Table S2 HR Multivariable complete cases**</span>

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking + dx_year_cat`
```{r}
tbl2 <- complete_cases %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- complete_cases %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + strata(histology) + debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- PH assumption Upfront Chemo -->
<!-- ```{r prop H Table S2 HR Multivariable complete cases adj deb} -->
<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
<!--              event = tbl2$vital_status -->
<!--            ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, -->
<!--       data =  tbl2)  %>% -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- PH assumption Upfront Surgery -->
<!-- ```{r} -->
<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->

<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + strata(histology) + debulking, -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->

<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->
<!-- ``` -->

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + dx_year_cat`
```{r}
tbl2 <- complete_cases %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- complete_cases %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + strata(histology) + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

<!-- PH assumption Upfront Chemo -->
<!-- ```{r prop H Table S2 HR Multivariable complete cases non adj debonly} -->
<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
<!--              event = tbl2$vital_status -->
<!--            ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, -->
<!--       data =  tbl2)  %>% -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- PH assumption Upfront Surgery -->
<!-- ```{r} -->
<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->

<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +  -->
<!--         stagecat + strata(histology), -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->

<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +  -->
<!--         strata(stagecat) + strata(histology), -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->
<!-- ``` -->
<br>
<br>

***
<br>

# Serous histology
```{r serous filter}
serous <- Frontline %>% filter(histology == "Serous") 
```

<!-- ## KM -->
<!-- ```{r serous KM, fig.height = 7} -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo_grp,  -->
<!--                    data=serous %>%  -->
<!--                      filter(therapy == "Upfront Chemo") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Chemo", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp,  -->
<!--                    data=serous %>%  -->
<!--                      filter(therapy == "Upfront Chemo") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Chemo", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp,  -->
<!--                    data=serous %>%  -->
<!--                      filter(therapy == "Upfront Surgery") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Surgery", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->

## HR
### Imputed data
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking + dx_year_cat`
```{r}
tbl2 <- serous %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- serous %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + dx_year_cat`
```{r}
tbl2 <- serous %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- serous %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ 
          RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + dx_year_cat,
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

### Complete cases
```{r}
serous_complete <- complete_cases %>% filter(histology == "Serous")
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking + dx_year_cat`
```{r}
tbl2 <- serous_complete %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- serous_complete %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + dx_year_cat`
```{r}
tbl2 <- serous_complete %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- serous_complete %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

***
<br>

# Others histology
```{r other filter}
other_hist <- Frontline %>% filter(histology == "Others")
```

## HR
### Imputed data
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking + dx_year_cat`
```{r}
tbl2 <- other_hist %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- other_hist %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + dx_year_cat`
```{r}
tbl2 <- other_hist %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- other_hist %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ 
          RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + dx_year_cat,
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

### Complete cases
```{r}
others_complete <- complete_cases %>% filter(histology == "Others")
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking + dx_year_cat`
```{r}
tbl2 <- others_complete %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- others_complete %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + dx_year_cat`
```{r}
tbl2 <- others_complete %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- others_complete %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

# Stratified by BMI
## Underweight and normal weight + Overweight vs Obese
```{r}
Frontline <- Frontline %>% 
  mutate(bmi_strat = case_when(
    bmi_cat == "Underweight and normal weight" |
    bmi_cat == "Overweight"                          ~ "not obese",
    bmi_cat == "Obese"                               ~ "obese"
  )) %>% 
  mutate(bmi_strat2 = case_when(
    bmi_cat == "Underweight and normal weight"       ~ "Underweight and normal weight",
    bmi_cat == "Overweight" |
    bmi_cat == "Obese"                               ~ "Overweight or obese"
  ))
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking+ dx_year_cat`
```{r}
not_obese <- Frontline %>% 
  filter(bmi_strat == "not obese")
obese <- Frontline %>% 
  filter(bmi_strat == "obese")

tbl2 <- not_obese %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- not_obese %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl4 <- obese %>%
  filter(therapy == "Upfront Chemo")
tbl41 <- 
  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
             event = tbl4$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl4) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- obese %>%
  filter(therapy == "Upfront Surgery")
tbl51 <- 
  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
             event = tbl5$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl5) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

a <- tbl_merge(list(tbl21, tbl41), tab_spanner = c("not obese", "obese"))
b <- tbl_merge(list(tbl31, tbl51))
tbl_stack(list(a, b),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

## Underweight and normal weight vs Overweight + Obese
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking+ dx_year_cat`
```{r}
normal <- Frontline %>% 
  filter(bmi_strat2 == "Underweight and normal weight")
overweight <- Frontline %>% 
  filter(bmi_strat2 == "Overweight or obese")

tbl2 <- normal %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- normal %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl4 <- overweight %>%
  filter(therapy == "Upfront Chemo")
tbl41 <- 
  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
             event = tbl4$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl4) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- overweight %>%
  filter(therapy == "Upfront Surgery")
tbl51 <- 
  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
             event = tbl5$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl5) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

a <- tbl_merge(list(tbl21, tbl41), tab_spanner = c("Underweight and normal weight", "Overweight or obese"))
b <- tbl_merge(list(tbl31, tbl51))
tbl_stack(list(a, b),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

## Association with BMI
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking+ dx_year_cat`  
stratified by therapy  
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ bmi_cat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ bmi_cat + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

Overall
```{r}
coxph(Surv(time = Frontline$month_at_os_from_treatment, 
             event = Frontline$vital_status) ~ bmi_cat + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  Frontline) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
```

***

```{r echo=FALSE, out.width='30%'}
knitr::include_graphics('/Users/colinccm/Documents/GitHub/Peres/lab_logo/Peres hex.png')
```
